### 2020-11-09 main.tex
init commit

\documentclass{article}
\usepackage{basic}

\title{mvybdcluster}
% \author{Roger Bai, Anne Dranowski, Joel Kamnitzer}
\date{October 2020}

\begin{document}

\maketitle

\section{Background}

The BD Grassmannian. The convolution Grassmannian. Distinguished orbits, slices therein.

\subsection{The case $n=2$ or $1$}

In this case $\Grbd = G(\CC\xT[t^{-1}]/G(\CC[t])$. 
$\Grbd^{\lambda_1,\lambda_2}\to\AA^1$ has 
\begin{itemize}
    \item special fibre $\overline{\Gr^{\lambda_1 + \lambda_2}}$
    \item general fibre $\overline{\Gr^{\lambda_1}}\times\overline{\Gr^{\lambda_2}}$
\end{itemize}
% 
and $S^{\mu_1,\mu_2}_{\mathrm{BD}}\to\AA^1$ has 
\begin{itemize}
    \item special fibre $\overline{S^{\mu_1+\mu_2}}$
    \item general fibre $\overline{S^{\mu_1}}\times \overline{S^{\mu_2}}$
\end{itemize}

Given $s\in \AA^1$ take $t^{\mu_1}(t-s)^{\mu_2} \in \Grbd$ and note that 
\begin{itemize}
    \item[$s\ne 0\Rightarrow$] $S^{\mu_1}\times S^{\mu_2} = N(\CC\xT[t^{-1}])t^{\mu_1}(t-s)^{\mu_2}$
    \item[$s = 0\Rightarrow$] $S^{\mu_1+\mu_2} = N(\CC\xT[t^{-1}])t^{\mu_1 + \mu_2}$
\end{itemize}

\jcom{Replace $\CC\xT[t^{-1}]$ by $\CC[t,t^{-1},(t-s)^{-1}]$ everywhere though it won't matter shortly.}

We're interested in
\begin{equation}
\label{eq:topmvy2}
    \tilde\phi_{\mathrm{MVy}}:\Grbd^{\lambda_1,\lambda_2}\cap S^{\mu_1,\mu_2}_{\mathrm{BD}} \to \{\text{some matrices}\}
\end{equation}

\section{Main results}

\begin{claim}
$\widetilde{T_x^a}\to\pi^{-1}(\overline{\Gr^\lambda}\cap\Gr_\mu)$ (this does depend on $b$! we get something like a springer fibre where the action of [what] on either side has eigenvalues a permutation of $b$.)
\end{claim}

\begin{claim}
Let $\cW^\mu_{\rm BD} = G_1\xT[t^{-1}]t^\mu$. Then $S^{\mu_1 + \mu_2}$ is contained in $\cW^\mu_{\rm BD}$ if $\mu$ is dominant. \jcom{And $\mu_1$, $\mu_2$ are dominant also?} \acom{Roger has a proof.}
\end{claim}

\begin{definition}
    Say $\mu_1$ and $\mu_2$ are \new{disjoint} if $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
\end{definition}

\begin{claim}
Let $a = (0,s)$ and suppose $\mu_1$ and $\mu_2$ are disjoint \sout{``transverse''} 
% i.e.\ $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
Let $\mu = \mu_1 + \mu_2$. Then $X\in\widetilde{T_x^a}$ is a $\mu\times\mu$ block matrix, with $(\mu_1)_k\times(\mu_1)_k$ diagonal block conjugate to a $(\mu_1)_k$ Jordan block and $(\mu_2)_k\times (\mu_2)_k$ diagonal block conjugate to $(\mu_2)_k$ Jordan block plus $sI$.
\end{claim}

\begin{question}
If $\mu_i$ is not a permutation of $\lambda_i$ and $\lambda_i$ are not ``homogeneous'' how do we proceed? E.g.\ if $\mu_1 = (3,0,2)$, $\mu_2 = (0,2,0)$ and $\lambda_1 = (4,1)$, $\lambda_2 = (2,0,0)$. 
\end{question}

\begin{question}
If $\mu_1$ and $\mu_2$ are not disjoint how do we proceed? E.g.\ if $\mu_1 = (2,2,0)$, $\mu_2 = (1,0,2)$; $\mu_1 = (2,2,1)$, $\mu_2 = (1,0,1)$.
\end{question}

\section{Examples}

\begin{example}
$\lambda_1 = (1,0,0)$, $\lambda_2 = (1,1,0)$, $\mu_1 = (0,1,0)$, $\mu_2 = (1,0,1)$. \jcom{$\mu = \mu_1 + \mu_2$ determines the blocks we have on the RHS of the BD MVy isomorphism of Equation~\ref{eq:topmvy2}.}

In the non-BD case, MVy establish
$$
\overline{\Gr^\lambda}\cap \cW^\mu \to 
\left\{ X = 
\left[\begin{BMAT}{cc|cc|c}{cc|cc|c}
0 & 1 & 0 & 0 & 0 \\
* & * & * & * & * \\
0 & 0 & 0 & 1 & 0 \\
* & * & * & * & * \\
* & 0 & * & 0 & * 
\end{BMAT}\right] \big| X \in \overline{\OO}_\lambda
\right\}
$$

In the BD case the RHS will consist of the same block like matrices $X$ but now having eigenvalues $s, 0$ such that $X - s\big|_{E_s}\in \OO_{\lambda_2}$ 
\end{example}

\begin{example}
Do Joel's exercise: It would be good to do an example where we will see some multiplicity in the fusion product.  I think that the simplest example would be the fusion product of the MV cycles for $\SL_3$ of weights $2\alpha_1$ and $2\alpha_2$.  Following the notation from the mvbasis paper, this would correspond to the following multiplication:
$x^2 y^2 = (xy-z)^2 + 2(xy - z) z + z^2$. 
For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. 
\end{example}

\begin{example}
    Let 
    \[
    \begin{aligned}
        \mu_1 &= (2) & \lambda_1 &= & \mu &= (5) \\
        \mu_2 &= (3) & \lambda_2 &= & \lambda &= 
    \end{aligned}
    \]
    Consider the companion matrix $C(p)$ of 
    $$p(t) = (t-s)^3t^2 = (t^3 - 3t^2 s + 3t s^2 - s^3)t^2 = t^5 - 3 t^4 s + 3t^3 s^2 - t^2 s^3$$ 
    Let $X = C(p)^T$ so 
    \[
    X = \left[\begin{BMAT}(e){ccccc}{ccccc}
        0 & 1 & & & \\ 
        & 0 & 1 & & \\
        &   & 0 & 1 & \\ 
        &   &   & 0 & 1 \\
       0 & 0 & s^3 & -3s^2  & 3s  
    \end{BMAT}\right]    
    \]
    Ask that $X\big|_{E_0}$ has Jordan type $\lambda_1$ and $X-s\big|_{E_s}$ has Jordan type $\lambda_2$. In this rank 1 case we are forced to take $\lambda_i = \mu_i$.

    So what are the generalized eigenspaces $E_i$ ($i = 1,2$)? Note $\dim E_0 = 2$ and $\dim E_s = 3$.

    \acom{The basis
    \[
     [1], [t], [\bf 1], [\bf t], [\bf t^2]    
    \] 
    with $t[t] = 0$ and $t[{\bf t^2}] =   s^3 [{\bf 1}] - 3s^2 [{\bf t}] + 3s[{\bf t^2}]$ \textit{is not the correct basis to consider}.
    Hence my confusion of yore: what we would like is $t[t] = 0$ no? what the matrix is telling us is that $t[t] = [{\bf 1}]$. Can we still speak of \textit{two} generalized eigenspaces?}  % [3st^2 - 3s^2 t + s^3]

    Rather, take $B$ to be the basis $b_1 = e_1$, $b_2 = e_2$, $b_5 = e_5$, $b_4 = Xe_5$, $b_3 = X^2e_5)$. In this basis
    \[
    X_B = [X(b_i)] = \begin{bmatrix}
        0 & 1 & 0 & 0 & 0 \\
        0 & 0 & 0 & 0 & 0 \\
        0 & 0 & s & 1 & 0 \\
        0 & 0 & 0 & s & 1 \\
        0 & 0 & 0 & 0 & s
    \end{bmatrix}
    \]

    % I think this demonstrates why Roger's idea is probably the right thing to do. Namely, consider instead $T_{\mu_1,\mu_2}$ whose elements are 
    % \[
    %     X = \left[\begin{BMAT}(e){cc|ccc}{cc|ccc}
    %         0 & 1 & & & \\ 
    %         & 0 & x & y & z \\
    %         &   & 0 & 1 & \\ 
    %         &   &   & 0 & 1 \\
    %        0 & 0 & s^3 & -3s^2  & 3s  
    %     \end{BMAT}\right]    
    % \] 
    % such that $T_{\mu_1,\mu_2}\big|_{s = 0} = T_\mu$ whatever that means... 
\end{example}

\begin{example}
    Let 
    \[
    \begin{aligned}
        \mu_1 &= (3,1,1) & \lambda_1 &= (3,2,0) & \mu = (3,3,1) \\
        \mu_2 &= (0,2,0) & \lambda_2 &= (2,0,0) & \lambda = (5,2,0)
    \end{aligned}    
    \]
    and consider the companion matrices of 
    $$
    \begin{aligned}
        p_1(t) &= t^3 & p_2(t) &= t(t-s)^2 = t^3 - 2st^2 + s^2 t & p_3(t) &= t
    \end{aligned} % = t(t^2 - 2st + s^2) 
    $$
    \[
    X = \left[
        \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c}
            0 & 1 & 0 & 0 & 0 & 0 & 0 \\
            0 & 0 & 1 & 0 & 0 & 0 & 0 \\
            % a & b & c & d & e & f & g \\ 
            0 & 0 & 0 & d & e & f & g \\ 
            0 & 0 & 0 & 0 & 1 & 0 & 0 \\
            0 & 0 & 0 & 0 & 0 & 1 & 0 \\
            0 & 0 & 0 & 0 & -s^2 & 2s & k \\
            0 & 0 & 0 & 0 & 0 & 0 & 0
        \end{BMAT}
        \right]    
    \]
\end{example}
\end{document}

### 2020-11-09 mvynote.tex
init commit

\documentclass[11pt]{amsart}
%
\usepackage{basic}
\newcommand{\ad}{\text{ad}}
% 
% scattegories
\newcommand{\vect}{\text{\bf vect}}
\newcommand{\set}{\text{\bf set}}
\newcommand{\tpl}{\text{\bf top}}
%
\begin{document}
%
\begin{definition}
    \new{Lusztig's stratification} of \(\g\) 
\end{definition}
% 
\begin{definition}
    \label{def:normalS}
    \(S\subset\g\) is a \new{transverse} or \new{normal} slice to a nilpotent orbit \(\alpha \equiv \OO_e\) at the element \(e\in \g\) if 
    \begin{enumerate}
        \item \label{enum:normalS1} \(T_e\alpha\oplus T_e S = \g\)
        \item \label{enum:normalS2} there is a \(\GG_m\) action on \(S\) 
        \begin{enumerate}
            \item contracting it to \(e\), and
            \item preserving \new{Lusztig's stratification} of \(\g\)
        \end{enumerate} 
    \end{enumerate}
\end{definition}
% 
\begin{lemma} Let \(L\) be a Lusztig stratum. 
    \begin{itemize}
        \item \(S\cap\alpha=\{e\}\)
        \item \(S\cap L\ne\varnothing \iff \alpha \subset \overline{L}\)
        \item \(S\) intersects \(L\) transversely, i.e.\ for each \(x\in S\cap L\), \(T_x S \oplus T_x L = \g \)
    \end{itemize}
\end{lemma}
% 
\begin{proof}
    \begin{itemize}
        \item The first point is a consequence of Definition~\ref{def:normalS}~(\ref{enum:normalS2})? 
    \end{itemize}
\end{proof}
% 
\begin{lemma}
The following data specifies a normal slice \(S\) to \(\alpha\) at \(e\).
\begin{itemize}
    \item \(h\in\g^{ss}\) such that \(\ad(h)\) has integer eigenvalues, and \(\ad(h)(e) = 2e\)
    \item \(C\overset{\vect}{\subset}\g\) such that \(C\cap T_e(\alpha) = C\cap [\g,e] = 0 \), \(\ad(h)(C) = C\), and if \(\ad(h)(x) = nx\) for some \(x\in C\), then \(n\le 1\)
\end{itemize}
\end{lemma}
% 
\begin{proof}
    \acom{See Lemma 5.2.1, 5.4.2, but most importantly Lemma 4.3.1 of Riche's Kostant section and universal centralizer.}
    \begin{equation}
        e = \sum_\Delta e_\alpha; \quad 
        \check\lambda_\circ := \sum{\tilde\Phi^+} \check\alpha; \quad 
        t\cdot x := t^{-2}\check\lambda_\circ(t) \cdot x 
    \end{equation}
    Apparently, we can lift the action of \(h\) on \(\g\) to a map \(\GG_m\to G\) and hence an action of \(\GG_m\) on \(\g\) which fixes \(e\) and preserves \(e+C\). The element \(h\) defines a 1-parameter subgroup \(e^{sh}\) in \(G\). 
    % x`    
    % We can consider \(\Ad(e^{sh})(x)\). Does it fix \(e\)? 
    % \[
    %     \begin{aligned}
    % (1 + sh &+ \frac{s^2 h^2}{2} + \cdots ) x (1 - sh + \frac{s^2 h^2}{2} - \cdots ) = \\
    % &= x + s[h,x] + s^2(-hxh + \frac 1 2 h^2 x + \frac 1 2 x h^2 ) + \cdots \\ 
    % &= e + 2se + s^2(-heh + \frac 1 2 (h^2 e + e h^2) + \cdots ) \qquad x = e
    %     \end{aligned}
    % \]
    % Nope. 
\end{proof}
% 
MVy construct an isomorphism \(\psi:T_x\cap\cN\to T_b\cap\Gr_N\) where 
\begin{itemize}
    \item \(T_x = \{x + f \big| f \in \End(D), \text{[conditions]}\}\)
    \item \(\cN \) is the nilpotent cone in \(\End(D)\)
    \item \(T_b := L^{<0}G(\cK) L_b \) which is the same as to use the notation that we're used to \(\Gr_\mu \) as \(L^{<0}G(\cK) = \ker(G(\CC[z^{-1}])\xrightarrow{z^{-1}\mapsto 0} G)\)
    \item \(\Gr_N = \{L\supset L_0 \big| \dim L/L_0 = N\} \)
\end{itemize}
%
% import bibliography from tex.bib file
%
\bibliographystyle{plain}
\bibliography{tex}
%
% for bundling, bbl file contains
%
% \begin{thebibliography}{E-G-S}

% \bibitem[A1]{Anderson00}
% J.~E.~Anderson, \textit{On Mirkovi\'c and Vilonen's Intersection Homology cycles for the Loop Grassmannian.} PhD thesis, Princeton University, 2000.

% \end{thebibliography}
%
\end{document}

### 2020-11-09 main.tex
Roger's computation

@@
 \end{example}
+
+\begin{example}
+    Let
+    \[
+    \begin{aligned}
+        \lambda_1 &= (3,2,0) & \mu_1 &= (3,1,1) \\
+        \lambda_2 &= (2,0,0) & \mu_2 &= (1,1,0)
+    \end{aligned}
+    \]
+    so the first MV cycle $Z_1 \cong \PP^1$ has MV polytope $\Conv\{0, \alpha_1\}$ and the second MV cycle $Z_2 \cong \PP^1$ has MV polytope $\Conv\{0, \alpha_2\}$.
+Their fusion product corresponds to two $\PP^2$'s intersecting along a $\PP^1$.
+That is, we have the fusion product
+    \[
+    Z_1 * Z_2 = Z_+ + Z_-
+    \]
+    where $Z_+ \cong Z_- \cong \PP^2$.
+    We have 
+    \[
+    X = \begin{bmatrix}
+    0 & 1 \\
+      & 0 & 1 \\
+      &   & 0 & 1 \\
+      &   &   & s & a & b & c \\
+      &   &   &   & 0 & 1 & 0 \\
+      &   &   &   & 0 & s & d \\
+      &   &   &   &   &   & 0
+    \end{bmatrix}
+    \]
+    The $0$-generalized eigenspace $E_0$ of $X$ is $5$-dimensional, containing a 3-cycle and a 2-cycle.
+    The 3-cycle is 
+    \[
+    \{X^2 e_3 , X e_3, e_3\} = \{e_1, e_2, e_3\}.
+    \]
+    To obtain another vector in $\ker X$, either $a = 0$ or $c = d = 0$, but the latter case cannot give a 2-cycle as $e_7 \notin \im X$. Then $a = 0$ and we obtain a 2-cycle
+    \[
+    \left\{X \left( e_6 -\frac{s}{d}e_7 \right), e_6 - \frac{s}{d}e_7 \right\}
+    = \left\{e_5, e_6 - \frac{s}{d}e_7 \right\}.
+    \]
+    We also obtain the equations $b \neq 0$, $d \neq 0$, and $sc - bd = 0$ from this.
+
+    For the $s$-generalized eigenspace $E_s$, we need $a + sb \neq 0$ to obtain a 2-cycle, which can be taken as 
+    \[
+    \begin{split}
+    & \left\{ 
+    (X -sI) \left( e_2 + 2s e_3 + 3s^2 e_4 + \frac{s^3}{a+sb} e_5 + \frac{s^4}{a+sb} e_6 \right), 
+    e_2 + 2s e_3 + 3s^2 e_4 + \frac{s^3}{a+sb} e_5 + \frac{s^4}{a+sb} e_6 
+    \right\} \\
+    = & \left\{ 
+    e_1 + s e_2 + s^2 e_3 + s^3 e_4, 
+    e_2 + 2s e_3 + 3s^2 e_4 + \frac{s^3}{a+sb} e_5 + \frac{s^4}{a+sb} e_6
+    \right\}
+    \end{split}
+    \]
+    The minimal polymonial is $X^3 (X-sI)^2$, which when equated to 0 gives again the equation $cs-bd = 0$.
+    Thus the defining equations are 
+    \[
+    \{ a = 0, cs-bd = 0\}.
+    \]
+    When we take $s = 0$, we get the equations
+    \[
+    \{a = 0, bd = 0\}
+    \]
+    which corresponds to two $\AA^2$'s intersecting along an $\AA^1$. This is indeed an open subset of $\PP^2 \cup_{\PP_1} \PP^2$, as required.
+\end{example}
 \end{document}

### 2020-11-22 main.tex
Added new section for the main results. Added a proof for my lemma and outlined structure of the main theorem.

@@
 \end{example}
+
+\section{Statements and Proofs of Results}
+Define
+\[
+S_{\mu_1, \mu_2} = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2}
+\]
+and
+\[
+W_\mu = G_1 [[t^{-1}]]t^\mu.
+\]
+Let $|\lambda| = |\lambda_1 + \lambda_2|$ and $|\mu| = |\mu_1 + \mu_2|$.
+
+\begin{lemma}[Proof in Proposition 2.6 of KWWY]
+Suppose $\mu$ is dominant. Then 
+\[
+N((t^{-1})) t^\mu = N_1[[t^{-1}]] t^\mu.
+\]
+\end{lemma}
+
+\begin{lemma}
+For dominant $\mu_1,\mu_2$, we have
+\[
+S_{\mu_1, \mu_2} \subset W_{\mu_1 + \mu_2}.
+\]
+\end{lemma}
+
+\begin{proof}
+We have
+\[
+\begin{split}
+    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
+     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
+     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
+     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
+     & = W_{\mu_1 + \mu_2}
+\end{split}
+\]
+where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
+\[
+\frac{t}{t-s} = 
+1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
+\in B_1[[t^{-1}]].
+\]
+\end{proof}
+
+Define $Gr^{\lambda_1, \lambda_2} \subset Gr_{BD}$ to be the family with generic fibre $Gr^{\lambda_1} \times Gr^{\lambda_2}$ and 0-fibre $Gr^{\lambda_1 + \lambda_2}$.
+
+Define $\OO_{\lambda_1, \lambda_2}$ to be matrices $X$ of size $|\lambda| \times |\lambda|$ such that 
+\[
+X|_{E_0} \in \OO_{\lambda_1} \text{ and } (X-sI)|_{E_s} \in \OO_{\lambda_2}.
+\]
+
+Let 
+\[
+\mu = (\mu^{(1)}, \mu^{(2)}, ..., \mu^{(n)}).
+\]
+Define $\TT_{\mu_1, \mu_2}$ to be $|\mu| \times |\mu|$ matrices $X$ such that $X$ consists of block matrices where the size of the $i$-th diagonal block is $|\mu^{(i)}| \times |\mu^{(i)}|$, for $1\leq i \leq n$.
+
+\begin{theorem}
+We have an isomorphism
+\[
+\overline{Gr^{\lambda_1, \lambda_2}} \cap S_{\mu_1, \mu_2} \cong
+\overline{\OO_{\lambda_1, \lambda_2}} \cap \TT_{\mu_1, \mu_2} \cap \n.
+\]
+\end{theorem}
+
+\begin{proof}
+We will prove this similarly to how the usual Mirkovi\'c-Vybornov isomorphism is proven.
+\begin{enumerate}[label = Step \arabic*:]
+    \item Define a map $\TT_{\mu_1, \mu_2} \cap \cN \rightarrow G_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+
+    \item If $A \in \TT_{\mu_1,\mu_2} \cap \n$ then $A$ is sent to $(N_-)_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+
+    \item Conversely, given $L \in W_{\mu_1 + \mu_2}$, something happens.
+\end{enumerate}
+\end{proof}
 \end{document}

### 2020-11-22 examples.tex
moved examples to a separate file

--- 2020-11-09 main.tex
@@
-\documentclass{article}
-\usepackage{basic}
-
-\title{mvybdcluster}
-% \author{Roger Bai, Anne Dranowski, Joel Kamnitzer}
-\date{October 2020}
-
-\begin{document}
-
-\maketitle
-
-\section{Background}
-
-The BD Grassmannian. The convolution Grassmannian. Distinguished orbits, slices therein.
-
-\subsection{The case $n=2$ or $1$}
-
-In this case $\Grbd = G(\CC\xT[t^{-1}]/G(\CC[t])$. 
-$\Grbd^{\lambda_1,\lambda_2}\to\AA^1$ has 
-\begin{itemize}
-    \item special fibre $\overline{\Gr^{\lambda_1 + \lambda_2}}$
-    \item general fibre $\overline{\Gr^{\lambda_1}}\times\overline{\Gr^{\lambda_2}}$
-\end{itemize}
-% 
-and $S^{\mu_1,\mu_2}_{\mathrm{BD}}\to\AA^1$ has 
-\begin{itemize}
-    \item special fibre $\overline{S^{\mu_1+\mu_2}}$
-    \item general fibre $\overline{S^{\mu_1}}\times \overline{S^{\mu_2}}$
-\end{itemize}
-
-Given $s\in \AA^1$ take $t^{\mu_1}(t-s)^{\mu_2} \in \Grbd$ and note that 
-\begin{itemize}
-    \item[$s\ne 0\Rightarrow$] $S^{\mu_1}\times S^{\mu_2} = N(\CC\xT[t^{-1}])t^{\mu_1}(t-s)^{\mu_2}$
-    \item[$s = 0\Rightarrow$] $S^{\mu_1+\mu_2} = N(\CC\xT[t^{-1}])t^{\mu_1 + \mu_2}$
-\end{itemize}
-
-\jcom{Replace $\CC\xT[t^{-1}]$ by $\CC[t,t^{-1},(t-s)^{-1}]$ everywhere though it won't matter shortly.}
-
-We're interested in
-\begin{equation}
-\label{eq:topmvy2}
-    \tilde\phi_{\mathrm{MVy}}:\Grbd^{\lambda_1,\lambda_2}\cap S^{\mu_1,\mu_2}_{\mathrm{BD}} \to \{\text{some matrices}\}
-\end{equation}
-
-\section{Main results}
-
-\begin{claim}
-$\widetilde{T_x^a}\to\pi^{-1}(\overline{\Gr^\lambda}\cap\Gr_\mu)$ (this does depend on $b$!
-we get something like a springer fibre where the action of [what] on either side has eigenvalues a permutation of $b$.)
-\end{claim}
-
-\begin{claim}
-Let $\cW^\mu_{\rm BD} = G_1\xT[t^{-1}]t^\mu$. Then $S^{\mu_1 + \mu_2}$ is contained in $\cW^\mu_{\rm BD}$ if $\mu$ is dominant. \jcom{And $\mu_1$, $\mu_2$ are dominant also?} \acom{Roger has a proof.}
-\end{claim}
-
-\begin{definition}
-    Say $\mu_1$ and $\mu_2$ are \new{disjoint} if $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
-\end{definition}
-
-\begin{claim}
-Let $a = (0,s)$ and suppose $\mu_1$ and $\mu_2$ are disjoint \sout{``transverse''} 
-% i.e.\ $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
-Let $\mu = \mu_1 + \mu_2$.
-Then $X\in\widetilde{T_x^a}$ is a $\mu\times\mu$ block matrix, with $(\mu_1)_k\times(\mu_1)_k$ diagonal block conjugate to a $(\mu_1)_k$ Jordan block and $(\mu_2)_k\times (\mu_2)_k$ diagonal block conjugate to $(\mu_2)_k$ Jordan block plus $sI$.
-\end{claim}
-
-\begin{question}
-If $\mu_i$ is not a permutation of $\lambda_i$ and $\lambda_i$ are not ``homogeneous'' how do we proceed? E.g.\ if $\mu_1 = (3,0,2)$, $\mu_2 = (0,2,0)$ and $\lambda_1 = (4,1)$, $\lambda_2 = (2,0,0)$. 
-\end{question}
-
-\begin{question}
-If $\mu_1$ and $\mu_2$ are not disjoint how do we proceed? E.g.\ if $\mu_1 = (2,2,0)$, $\mu_2 = (1,0,2)$; $\mu_1 = (2,2,1)$, $\mu_2 = (1,0,1)$.
-\end{question}
+% !TeX root = ./main.tex
 
@@
 \end{example}
-\end{document}

### 2020-11-22 main.tex
Changed Step 3 of Theorem.
some comments on Rogers changes plus excisions, minor additions

--- 2020-11-09 main.tex
@@
 
-The BD Grassmannian. The convolution Grassmannian. Distinguished orbits, slices therein.
+The BD Grassmannian. The convolution Grassmannian. Distinguished orbits, slices therein. Mirkovi\'c--Vybornov.
 
-\subsection{The case $n=2$ or $1$}
+\section{Notation}
 
-In this case $\Grbd = G(\CC\xT[t^{-1}]/G(\CC[t])$. 
-$\Grbd^{\lambda_1,\lambda_2}\to\AA^1$ has 
-\begin{itemize}
-    \item special fibre $\overline{\Gr^{\lambda_1 + \lambda_2}}$
-    \item general fibre $\overline{\Gr^{\lambda_1}}\times\overline{\Gr^{\lambda_2}}$
-\end{itemize}
-% 
-and $S^{\mu_1,\mu_2}_{\mathrm{BD}}\to\AA^1$ has 
-\begin{itemize}
-    \item special fibre $\overline{S^{\mu_1+\mu_2}}$
-    \item general fibre $\overline{S^{\mu_1}}\times \overline{S^{\mu_2}}$
-\end{itemize}
+\begin{definition}
+    Say $\mu_1$ and $\mu_2$ are \new{disjoint} if $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
+\end{definition}
 
-Given $s\in \AA^1$ take $t^{\mu_1}(t-s)^{\mu_2} \in \Grbd$ and note that 
-\begin{itemize}
-    \item[$s\ne 0\Rightarrow$] $S^{\mu_1}\times S^{\mu_2} = N(\CC\xT[t^{-1}])t^{\mu_1}(t-s)^{\mu_2}$
-    \item[$s = 0\Rightarrow$] $S^{\mu_1+\mu_2} = N(\CC\xT[t^{-1}])t^{\mu_1 + \mu_2}$
-\end{itemize}
-
-\jcom{Replace $\CC\xT[t^{-1}]$ by $\CC[t,t^{-1},(t-s)^{-1}]$ everywhere though it won't matter shortly.}
-
-We're interested in
-\begin{equation}
-\label{eq:topmvy2}
-    \tilde\phi_{\mathrm{MVy}}:\Grbd^{\lambda_1,\lambda_2}\cap S^{\mu_1,\mu_2}_{\mathrm{BD}} \to \{\text{some matrices}\}
-\end{equation}
+\acom{I propose ``anodyne'' as another candidate for the above property after Kapranov--Shechtman.}
 
@@
 \end{claim}
-
-\begin{definition}
-    Say $\mu_1$ and $\mu_2$ are \new{disjoint} if $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
-\end{definition}
 
@@
 
-\section{Examples}
+\section{Statements and Proofs of Results}
+\acom{Maybe split for now into a Notation section and a Proofs section}
 
-\begin{example}
-$\lambda_1 = (1,0,0)$, $\lambda_2 = (1,1,0)$, $\mu_1 = (0,1,0)$, $\mu_2 = (1,0,1)$.
-\jcom{$\mu = \mu_1 + \mu_2$ determines the blocks we have on the RHS of the BD MVy isomorphism of Equation~\ref{eq:topmvy2}.}
+Define
+\[
+S_{\mu_1, \mu_2} = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2}
+\]
+and
+\[
+W_\mu = G_1 [[t^{-1}]]t^\mu.
+\]
+Let $|\lambda| = |\lambda_1 + \lambda_2|$ and $|\mu| = |\mu_1 + \mu_2|$.
 
-In the non-BD case, MVy establish
-$$
-\overline{\Gr^\lambda}\cap \cW^\mu \to 
-\left\{ X = 
-\left[\begin{BMAT}{cc|cc|c}{cc|cc|c}
-0 & 1 & 0 & 0 & 0 \\
-* & * & * & * & * \\
-0 & 0 & 0 & 1 & 0 \\
-* & * & * & * & * \\
-* & 0 & * & 0 & * 
-\end{BMAT}\right] \big| X \in \overline{\OO}_\lambda
-\right\}
-$$
+\acom{Why not $\lambda = \lambda_1 + \lambda_2$ and recall $\lvert \nu \rvert$ in general.}
 
-In the BD case the RHS will consist of the same block like matrices $X$ but now having eigenvalues $s, 0$ such that $X - s\big|_{E_s}\in \OO_{\lambda_2}$ 
-\end{example}
+\begin{lemma}[Proof in Proposition 2.6 of KWWY]
+Suppose $\mu$ is dominant. Then 
+\[
+N((t^{-1})) t^\mu = N_1[[t^{-1}]] t^\mu.
+\]
+\end{lemma}
 
-\begin{example}
-Do Joel's exercise: It would be good to do an example where we will see some multiplicity in the fusion product.
-I think that the simplest example would be the fusion product of the MV cycles for $\SL_3$ of weights $2\alpha_1$ and $2\alpha_2$.
-Following the notation from the mvbasis paper, this would correspond to the following multiplication:
-$x^2 y^2 = (xy-z)^2 + 2(xy - z) z + z^2$. 
-For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. 
-\end{example}
+\begin{lemma}
+For dominant $\mu_1,\mu_2$, we have
+\[
+S_{\mu_1, \mu_2} \subset W_{\mu_1 + \mu_2}.
+\]
+\end{lemma}
 
-\begin{example}
+\begin{proof}
+We have
+\[
+\begin{split}
+    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
+     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
+     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
+     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
+     & = W_{\mu_1 + \mu_2}
+\end{split}
+\]
+where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
+\[
+\frac{t}{t-s} = 
+1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
+\in B_1[[t^{-1}]].
+\]
+\end{proof}
+
+Define $\Gr^{\lambda_1, \lambda_2} \subset \Gr_{BD}$ to be the family with generic fibre $\Gr^{\lambda_1} \times \Gr^{\lambda_2}$ and 0-fibre $\Gr^{\lambda_1 + \lambda_2}$.
+
+Define $\OO_{\lambda_1, \lambda_2}$ to be matrices $X$ of size $|\lambda| \times |\lambda|$ such that 
+\[
+    % \begin{cases}
+        X\big|_{E_0} \in \OO_{\lambda_1} 
+        % \\
+        \text{ and }
+        (X-sI)\big|_{E_s} \in \OO_{\lambda_2}
+    % \end{cases}
+\]
+
 Let 
 \[
-    \begin{aligned}
-        \mu_1 &= (2) & \lambda_1 &= & \mu &= (5) \\
-        \mu_2 &= (3) & \lambda_2 &= & \lambda &= 
-    \end{aligned}
+\mu = (\mu^{(1)}, \mu^{(2)}, ..., \mu^{(n)}).
 \]
-    Consider the companion matrix $C(p)$ of 
-    $$p(t) = (t-s)^3t^2 = (t^3 - 3t^2 s + 3t s^2 - s^3)t^2 = t^5 - 3 t^4 s + 3t^3 s^2 - t^2 s^3$$ 
-    Let $X = C(p)^T$ so 
+Define $\TT_{\mu_1, \mu_2}$ to be $|\mu| \times |\mu|$ matrices $X$ such that $X$ consists of block matrices where the size of the $i$-th diagonal block is $|\mu^{(i)}| \times |\mu^{(i)}|$, for $1\leq i \leq n$.
+
+\begin{theorem}
+We have an isomorphism
 \[
-    X = \left[\begin{BMAT}(e){ccccc}{ccccc}
-        0 & 1 & & & \\ 
-        & 0 & 1 & & \\
-        &   & 0 & 1 & \\ 
-        &   &   & 0 & 1 \\
-       0 & 0 & s^3 & -3s^2  & 3s  
-    \end{BMAT}\right]    
+    \overline{\Gr^{\lambda_1, \lambda_2}} \cap S_{\mu_1, \mu_2} \cong
+    \overline{\OO_{\lambda_1, \lambda_2}} \cap \TT_{\mu_1, \mu_2} \cap \n.
 \]
-    Ask that $X\big|_{E_0}$ has Jordan type $\lambda_1$ and $X-s\big|_{E_s}$ has Jordan type $\lambda_2$. In this rank 1 case we are forced to take $\lambda_i = \mu_i$.
+\end{theorem}
 
-    So what are the generalized eigenspaces $E_i$ ($i = 1,2$)? Note $\dim E_0 = 2$ and $\dim E_s = 3$.
+\begin{proof}
+We will prove this similarly to how the usual Mirkovi\'c--Vybornov isomorphism is proven.
+\begin{enumerate}[label = Step \arabic*:]
+    \item Define a map $\TT_{\mu_1, \mu_2} \cap \cN \rightarrow G_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
 
-    \acom{The basis
-    \[
-     [1], [t], [\bf 1], [\bf t], [\bf t^2]    
-    \] 
-    with $t[t] = 0$ and $t[{\bf t^2}] =   s^3 [{\bf 1}] - 3s^2 [{\bf t}] + 3s[{\bf t^2}]$ \textit{is not the correct basis to consider}.
-    Hence my confusion of yore: what we would like is $t[t] = 0$ no?
-what the matrix is telling us is that $t[t] = [{\bf 1}]$.
-Can we still speak of \textit{two} generalized eigenspaces?}  % [3st^2 - 3s^2 t + s^3]
+    \item If $A \in \TT_{\mu_1,\mu_2} \cap \n$ then $A$ is sent to $(N_-)_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
 
-    Rather, take $B$ to be the basis $b_1 = e_1$, $b_2 = e_2$, $b_5 = e_5$, $b_4 = Xe_5$, $b_3 = X^2e_5)$. In this basis
-    \[
-    X_B = [X(b_i)] = \begin{bmatrix}
-        0 & 1 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & s & 1 & 0 \\
-        0 & 0 & 0 & s & 1 \\
-        0 & 0 & 0 & 0 & s
-    \end{bmatrix}
-    \]
-
-    % I think this demonstrates why Roger's idea is probably the right thing to do. Namely, consider instead $T_{\mu_1,\mu_2}$ whose elements are 
-    % \[
-    %     X = \left[\begin{BMAT}(e){cc|ccc}{cc|ccc}
-    %         0 & 1 & & & \\ 
-    %         & 0 & x & y & z \\
-    %         &   & 0 & 1 & \\ 
-    %         &   &   & 0 & 1 \\
-    %        0 & 0 & s^3 & -3s^2  & 3s  
-    %     \end{BMAT}\right]    
-    % \] 
-    % such that $T_{\mu_1,\mu_2}\big|_{s = 0} = T_\mu$ whatever that means... 
-\end{example}
-
-\begin{example}
-    Let 
-    \[
-    \begin{aligned}
-        \mu_1 &= (3,1,1) & \lambda_1 &= (3,2,0) & \mu = (3,3,1) \\
-        \mu_2 &= (0,2,0) & \lambda_2 &= (2,0,0) & \lambda = (5,2,0)
-    \end{aligned}    
-    \]
-    and consider the companion matrices of 
-    $$
-    \begin{aligned}
-        p_1(t) &= t^3 & p_2(t) &= t(t-s)^2 = t^3 - 2st^2 + s^2 t & p_3(t) &= t
-    \end{aligned} % = t(t^2 - 2st + s^2) 
-    $$
-    \[
-    X = \left[
-        \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c}
-            0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-            0 & 0 & 1 & 0 & 0 & 0 & 0 \\
-            % a & b & c & d & e & f & g \\ 
-            0 & 0 & 0 & d & e & f & g \\ 
-            0 & 0 & 0 & 0 & 1 & 0 & 0 \\
-            0 & 0 & 0 & 0 & 0 & 1 & 0 \\
-            0 & 0 & 0 & 0 & -s^2 & 2s & k \\
-            0 & 0 & 0 & 0 & 0 & 0 & 0
-        \end{BMAT}
-        \right]    
-    \]
-\end{example}
+    \item Conversely, given $L \in W_{\mu_1 + \mu_2}$, want to show surjectivity.
+\end{enumerate}
+\end{proof}
 \end{document}

### 2020-11-24 main.tex
adding a bg on mvy section is all i can member

@@
 
-\title{mvybdcluster}
+\title{Working title: Mirkovi\'c--Vybornov fusion in Beilinson--Drinfeld Grassmannian}
+% \title{mvybdcluster}
 % \author{Roger Bai, Anne Dranowski, Joel Kamnitzer}
@@
 \end{question}
+
+\section{Background on MVy}
+
+What they do. What they stop short of doing.
+
+\begin{itemize}
+    \item Their slice $T_x$ or $T_\lambda$
+    \item Their embedding $T_x\to\mathfrak G_N$
+    \item $N$-dim $D$
+    \item The map $\tilde {\bf m}:\tilde{\mathfrak g}^{n}\to\End(D)$
+    \item The map ${\bf m} : \tilde{\mathcal N}^n\to\mathcal N$ sending $(x,F_\bullet)$ to $x$
+    \item The map $\pi: \tilde{\mathfrak G}^n\to \mathfrak G$ sending $\mathcal L_\bullet$ to $\mathcal L_n$
+\end{itemize}
+
+The special case $b = \vec 0$.
+In this case $0$ in the affine quiver variety goes to the point $L_\lambda$ in the affine Grassmannian, and the preimage of zero in the smooth quiver variety (the core?) is identified with the preimage of $L_\lambda$ in the BD Grassmannian.
+
+\[
+\begin{tikzcd}
+    \mathfrak L(\vec v,\vec w) \ar[r] \ar[d] & \pi^{-1} (L_\lambda)\ar[d] \\
+     0 \ar[r] & L_\lambda
+\end{tikzcd}    
+\]
+
+MVy write: ``we believe that one should be able to generalize this to arbitrary [$b$]'' and that's where we come in!
+
+Recall the Mirkovi\'c--Vybornov immersion \cite[Theorems 1.2 and 5.3]{mirkovic2007quiver}.
+
+% \acom{All this time it was only an immersion! So our result will be a Theorem and not simply a reformulation plus corollary. Never mind.}
+
+\begin{theorem}(\cite[Theorem 1.2 and 5.3]{mirkovic2007quiver})
+    There exists an algebraic immersion $\tilde\psi$ 
+    $$\widetilde{\bf m}^{-1}(T_\lambda)\cap\tilde\g^{n,a,E,\tilde\mu}\xrightarrow{\tilde\psi}\tilde{\mathfrak G}^{n,a}_{b}(P)$$
+\end{theorem}
+
+% Where to begin? How to tell this story? Left to right?
+
+% Here
+% \begin{itemize}
+%     \item $T_\lambda \equiv \TT_\lambda$
+%     \item 
+% \end{itemize}
 
@@
 
+\acom{Rather, corollary?}
+
 \begin{proof}
@@
 
-    \item If $A \in \TT_{\mu_1,\mu_2} \cap \n$ then $A$ is sent to $(N_-)_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+    \item If $A \in \TT_{\mu_1,\mu_2} \cap \n$ then $A$ is sent to $(N_-)_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$. \acom{Requires MVyBD!}
 
@@
 \end{proof}
+
+\bibliographystyle{alpha}
+\bibliography{mvybd}
 \end{document}

### 2020-11-28 main.tex
mess of little meeting notes

@@
     \item Define a map $\TT_{\mu_1, \mu_2} \cap \cN \rightarrow G_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+    % 
+    $$
+    A \mapsto t^{\mu_1} (t-s)^{\mu_2} + a(t, t-s) \mapsto (L_1 \subset L_2) : (t-s)\big|_{L_2/L_1} = A\big|_{E_s}  , t\big|_{L_1/L_0} = A\big|_{E_0}
+    $$
+    % 
+    Question: 1. is the middle matrix similar to a block matrix? 2. is the composition of these maps some intermediate level of MVy's $\psi$'s
+
+    BD Gr as lattices?
+$(L_1,L_2)\in\Gr\times\Gr$ corresponds to $L$ such that $L\otimes\CC\xt\cong L_1\otimes\CC\xt$ and $L\otimes\CC\xt[t-s]\cong L_2\otimes\CC\xt[t-s]$ where $\otimes = \otimes_{\CC[t]}$ or $\otimes_{\CC[t-s]}$ respectively even though Roger believes $\CC[t] = \CC[t-s]$.
 

### 2020-12-14 main.tex
last weeks discussion

@@
 \usepackage{basic}
+\newcommand{\anne}[2]{\colorbox{pink!75!blue}{#1}\marginpar[]{\tiny\textbf{\color{pink!50!blue}#2}}}
 
@@
 
-\section{Background}
+\section{Introduction}
 
@@
 \section{Notation}
+
+Let $\Gr$ denote the ordinary affine Grassmannian, $\Grbd$ the Beilinson--Drinfeld affine Grassmannian, and $\Grc$ the convolution affine Grassmannian.
 
@@
 
-\section{Background on MVy}
+\section{Convolution vs BD}
+% aka, our result vs MVy's results
+% aka, what they do, and what they stop short of doing
 
-What they do. What they stop short of doing.
+Fix $G = \GL(U) \cong \GL_m\CC$ and $\{e_1,\dots,e_m\}$ a basis of $U$. 
+% 
+Recall $\Gr = G(\cK) / G(\cO)$ where $\cK,\cO$\dots
+
+\begin{definition}[Beilinson--Drinfeld loop Grassmannians]
+    Denoted $\Grbd_{C^{(n)}}$ with $C$ a smooth curve (or formal neighbourhood of a finite subset thereof) and $C^{(n)}$ its $n$th symmetric power.
+It is a reduced ind-scheme $\Grbd_{C^{(n)}}\to C^{(n)}$ with fibres of $C$-lattices $\Grbd_b = \{(b,\cL) : b \in C^{(n)}\}$ made up of vector bundles \anne{such that}{Not sure what $\cO_C$ means} $\cL \cong U\otimes\cO_C$ off $b$ (i.e.\ over $C - \underline b$).
+The standard \anne{lattice}{Notation} is the pair $(\varnothing,\cL_0)$ with $\cL_0 = U\otimes \cO_C$.
+\end{definition}
+
+{\bf The case $n = 1$.} Fix $b\in C$ and $t$ a choice of formal parameter. \anne{Then}{Why is this called ``its group-theoretic realization''} $\Grbd_b\cong\Gr$.
+
+Furthermore, in this case, $C$-lattices $(b,\cL)$ are identified with $\cO$-submodules $L = \Gamma(\hat b, \cL)$ of $U_\cK = U\otimes\cK$ such that $L\otimes_\cO\cK \cong U_\cK$.
+
+Under this identification, we associate to a given $\lambda\in\ZZ^m$ the lattice (a priori a $\cO$-submodule) $L_\lambda = \oplus_1^m t^{\lambda_i}e_i\cO$.
+Nb.
+our lattices will be contained in the standard lattice $L_0$ whereas MVy's lattices contain.
+
+Connected components of $\Gr$ are
+
+% Distinguished orbits. 
+$G(\cO)$-orbits are indexed by coweights $\lambda = (\lambda_1\ge\lambda_2\ge\cdots\ge\lambda_n)$ of $G$. In terms of lattices 
+\begin{equation}
+    \label{eq:grlambdalat}
+    \Gr^\lambda = \left\{L\supset L_0 \,\big|\, t\big|_{L/L_0} \in \OO_\lambda \right\}
+\end{equation} in the connected component $\Gr_N$ are indexed
+
+\cite{mirkovic2007quiver} define a map 
+\begin{equation}
+    \label{eq:grbdingrc}
+    \Grbd \to \Grc
+\end{equation}
 
@@
 The special case $b = \vec 0$.
-In this case $0$ in the affine quiver variety goes to the point $L_\lambda$ in the affine Grassmannian, and the preimage of zero in the smooth quiver variety (the core?) is identified with the preimage of $L_\lambda$ in the BD Grassmannian.
-
+In this case $0$ in the affine quiver variety goes to the point $L_\lambda$ in the affine Grassmannian, and the preimage of zero in the smooth quiver variety ($=$ the core?) is identified with the preimage of $L_\lambda$ in the BD Grassmannian.
+% 
 \[
@@
 
-MVy write: ``we believe that one should be able to generalize this to arbitrary [$b$]'' and that's where we come in!
+MVy write: ``we believe that one should be able to generalize this to arbitrary $b$'' and that's where we come in!
 
@@
 
+\include{examplesp}
+
 \bibliographystyle{alpha}

### 2020-12-20 main.tex
Updates from Overleaf
todo
bib and stuff

@@
 
-The BD Grassmannian. The convolution Grassmannian. Distinguished orbits, slices therein. Mirkovi\'c--Vybornov.
+The BD Grassmannian.
+The convolution Grassmannian.
+Distinguished orbits, slices therein.
+Mirkovi\'c--Vybornov \cite{mirkovic2007quiver,mirkovic2019comparison}, Cautis--Kamnitzer \cite{cautis2018categorical}, Anderson--Kogan \cite{anderson2005algebra}.
 
@@
 \begin{definition}
+    The \new{BD Grassmannian} is the set 
+    \begin{equation}
+        \label{eq:grbd}
+    \begin{aligned}
+        \{(V,\sigma) : V &\text{ is a rank } m \text{ vector bundle on }\PP^1 \\ &\text{and } \sigma: V \dashrightarrow \scO_{\PP^1}^m \text{ is a trivialization} \\
+        &\text{defined away from finitely many points in }\AA^1\}
+    \end{aligned}
+    \end{equation}
+    More generally, one can define a BD grassmannian over any smooth curve $C$ as the reduced ind-scheme $\Grbd_C$ fibered over a finite symmetric power of $C$ such that the fibre over the point $\vec p$ is a collection of vector bundles over $C$ which are trivial away from $\vec p$ viewed also as a subset of $C$.
+To \cite{mirkovic2019comparison} the rank $m$ of the trivial fibres $\scO_C^m$ is the of the group $\GL_m\CC$.
+\end{definition}
+
+To quote \cite{baumann2020bases} the BD Grassmannian is a relative version of the affine Grassmannian where the base is the space of effective divisors on a smooth curve.
+The choice of $\AA^1$ amply satisfies our needs and offers three advantages: there is a natural global coordinate it, every $G$-torsor on it is trivializable, and the monodromy of any local system is trivial.
+Formally, $\Grbd$ is the functor on the category of commutative $\CC$-algebras that assigns to an algebra $R$ the set of isomorphism classes of triples $(\vec p,V,\sigma)$ where $\vec p\in \AA^n(R)$, $V$ is a $G^\vee$-torsor over $\AA^1_R$ and $\sigma$ is a trivialization of $V$ away from $\vec p$.
+They denote by $\pi$ the fibration $\Grbd\to\AA^n$ (forgetting $V$ and $\sigma$).
+
+Their simplified description is: it's the set of pairs $(\vec p,[\sigma])$ where $\vec p\in\CC^n$ and $[\sigma]$ is an element of the homogeneous space 
+\[
+G^\vee(\CC[z,(z-p_1)^{-1},\dots,(z-p_n)^{-1}])/G^\vee(\CC[z])    
+\]
+Their example, our setting: 
+\begin{example}
+    When $G = \GL_m\CC$ the datum of $[\sigma]$ is equivalent to the datum of the $\CC[z]$-lattice $\sigma(L_0)$ in $\CC(z)^m$ with $L_0 = \CC[z]^m$ denoting the \new{standard lattice}.
+Set $f_{\vec p} = (z - p_1)\cdots (z-p_n)$.
+Then a lattice $L$ is of the form $\sigma(L_0)$ if and only if there exists a positive integer $k$ such that $f^k_{\vec p}(L_0) \subseteq L\subseteq f^{-k}_{\vec p}(L_0)$ and for each $k$ they denote by $\Grbd_k$ the subset of $\Grbd$ consisting of pairs $(\vec p,L)$ such that this sandwhich condition holds.
+They identify $\CC[z]/(f_{\vec p}^{2k})$ with the vector space of polynomials of degree strictly less than $2kn$, and $L_0/f_{\vec p}^{2k}L_0$ with its $N$th product.
+Then
+    \[
+    \Grbd_k \overset{\text{Zariski closed}}{\subset} \CC^n\times\bigcup_{d=0}^{2knN} G_d(L_0/f_{\vec p}^{2k}L_0)  
+    \]
+    where $G_d(?)$ denotes the ordinary Grassmann manifold of $d$-planes in the argument.
+\end{example}
+
+\begin{definition}
+    The \new{deformed convolution Grassmannian} is [not needed?]
+    pairs $(\vec p,[\vec\sigma])$ where $\vec p\in\CC^n$ and $\vec\sigma$ is in 
+    \[
+    G^\vee(\CC[z,(z-p_1)^{-1}]) \times^{G^\vee(\CC[z])}\cdots\times^{G^\vee(\CC[z])} G^\vee(\CC[z,(z-p_n)^{-1}])/G^\vee(\CC[z])
+    \] with a map down to $\Grbd$ defined by $(\vec p,[\vec \sigma])\mapsto (\vec p,[\sigma_1\cdots\sigma_n])$. 
+\end{definition}
+To steal the follow-up example in \cite{baumann2020bases} where the above definition is also copied from\dots 
+\begin{example}
+    When $G = \GL_m\CC$ this deformation is described by the datum of $\vec p\in\CC^n$ and a sequence $(L_1,\dots,L_n)$ of $\CC[z]$-lattices in $\CC(z)^m$ such that for some $k\in\ZZ$ and for all $j \in \{1\dots n\}$
+    \[
+    (z-p_j)^kL_{j-1}\subset L_j\subset (z-p_j)^{-k} L_{j-1}    
+    \]
+    where again $L_0 = \CC[z]^m$ denotes the standard lattice, and now $L_j = (\sigma_1\cdots\sigma_j)(L_0)$.
+Very nice.
+Very concrete.
+They can partition the deformation into \new{cells} by specifying the \new{relative positions} of the pairs $(L_{j-1},L_j)$ in terms of \new{invariant factors}.
+\end{example}
+To be continued: \cite{baumann2020bases} go on to describe the fibres of the composition deformation to $\Grbd$ to $\CC^n$ and their description maybe helpful.
+
+For $\mu\in P$ and $p\in\CC$ they define 
+\[
+    \tilde S_{\mu | p} = (z-p)^\mu N^\vee (\CC[z,(z-p)^{-1}]) = N^\vee (\CC[z,(z-p)^{-1}])(z-p)^\mu
+\]
+They note that $\CC\xT[z-p]$ is the completion of $\CC(z)$ at ``the place defined by p'' and identify $\CC\xt[z-p]$ with $\CC\xt[z]$ and $\CC\xT[z-p]$ with $\CC\xT[z]$.
+
+They claim that 
+\[
+    N^\vee (\CC[z,(z-p)^{-1}])/N^\vee (\CC[z]) \to N^\vee(\CC\xT[z-p])/N^\vee(\CC\xt[z-p]) \cong N^\vee(\cK)/N^\vee(\cO)
+\]
+is bijective, and that mapping $\Gr$ and multiplying by $(z-p)^\mu$ one gets 
+\[
+\tilde S_{\mu | p}/N^\vee(\CC[z])\cong S_\mu
+\]
+They go on to describe the fusion product (section 5.3) a probably worthwhile read.
+
+\begin{definition}
     Say $\mu_1$ and $\mu_2$ are \new{disjoint} if $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
@@
 
-\acom{I propose ``anodyne'' as another candidate for the above property after Kapranov--Shechtman.}
+% \acom{I propose ``anodyne'' as another candidate for the above property after Kapranov--Shechtman.}
 
@@
 Define $\TT_{\mu_1, \mu_2}$ to be $|\mu| \times |\mu|$ matrices $X$ such that $X$ consists of block matrices where the size of the $i$-th diagonal block is $|\mu^{(i)}| \times |\mu^{(i)}|$, for $1\leq i \leq n$.
+Each diagonal block is the companion matrix for $t^{\mu_1}(t-s)^{\mu_2}$.
 
@@
 
+% 2020-12-13 19:13:45
+Last meeting's todos:
+\begin{itemize}
+    \item make sure that the image of our map is in the $G_1$ orbit
+    \item more generally, define the map, check that the map is well-defined
+    \item Anne: say what little a is, i.e.\ insert the MVy theorem as stated in CK, or thesis
+    \item Roger: check it
+\end{itemize}
+
 \include{examplesp}

### 2020-12-23 examples.tex
sorry i was confusing it

@@
     & \left\{ 
-    (X -sI) \left( e_2 + 2s e_3 + 3s^2 e_4 + \frac{s^3}{a+sb} e_5 + \frac{s^4}{a+sb} e_6 \right), 
-    e_2 + 2s e_3 + 3s^2 e_4 + \frac{s^3}{a+sb} e_5 + \frac{s^4}{a+sb} e_6 
+    (X -sI) \left( e_2 + 2s e_3 + 3s^2 e_4 + \frac{s^3}{a+sb} e_5 + \frac{s^4}{a+sb} e_6 \right), \right. \\ 
+    & \quad \qquad \qquad  \left. e_2 + 2s e_3 + 3s^2 e_4 + \frac{s^3}{a+sb} e_5 + \frac{s^4}{a+sb} e_6 
     \right\} \\
@@
 \end{example}
+
+\begin{example}[Example 7 continued\dots]
+    The matrix $X$ from the previous example defines (under MVy) the matrix 
+    \[
+        g = \begin{bmatrix}
+            (t-s)t^3 \\
+            -bt & (t-s)t \\
+            -c & -d & t 
+        \end{bmatrix}
+    \]
+    in $G(\cO)$. 
+    Indeed the various blocks of $X$ are in a precise sense the companion matrices of the polynomial entries of $g$
+    % First let's double check the inverse map.
+
+    In $\Gr$ the element $g$ defines the lattice 
+    \[
+        gL_0 = \CC[t]\langle
+        (t-s)t^3e_1 - bt e_2 - ce_3 , (t-s)te_2 - de_3, te_3 
+        \rangle
+    \]
+    and computing the matrix of the action of $t$ on the quotient $L_0/L$ in the basis 
+    \[
+    \{
+        [e_1],[te_1],[t^2e_1],[t^3e_1],[e_2],[te_2],[e_3]
+    \}    
+    \]
+    recovers $X$ up to a transpose of course.
+
+    Now let's see what we get when we invert $t$ and $t-s$ respectively. First let's find $ L_s = L\otimes\CC\xt$. 
+    \[
+        L_s  = \CC[t]\langle(t-s) e_1 - be_2 - ce_3 , (t-s) e_2 , e_3 \rangle = \CC[t]\langle(t-s) e_1 - be_2, (t-s) e_2, e_3 \rangle
+    \]
+    so 
+    \[
+    \left[t\big|_{L_0/L_s}\right]_{\{[e_1],[e_2]\}} = \begin{bmatrix}
+        s \\
+        -b & s 
+    \end{bmatrix}
+    \]
+    which has block type $\mu_2$ and Jordan type $\lambda_2$ as expected.
+
+    Next let's find $L_0 = L\otimes\CC\xt[t-s]$. 
+    \[
+        L_0 = \CC[t]\langle
+        t^3 e_1 - bte_2 - ce_3, te_2 - de_3 , te_3 
+        \rangle 
+    \]
+    so 
+    \[
+    \left[t\big|_{L_0/L_s}\right]_{\{[e_1],[te_1],[t^2e_1],[e_2],[e_3]\}} = \begin{bmatrix}
+        0 \\
+        1 & 0 \\
+        0 & 1 & 0 \\
+          & & & 0 \\
+          & & & d & 0  
+    \end{bmatrix}
+    \]
+    which has block type $\mu_1$ and Jordan type $\lambda_1$ as expected. 
+\end{example}

### 2020-12-23 main.tex
uncomment examples
sorry i was confusing it

@@
 The convolution Grassmannian.
-Distinguished orbits, slices therein.
-Mirkovi\'c--Vybornov \cite{mirkovic2007quiver,mirkovic2019comparison}, Cautis--Kamnitzer \cite{cautis2018categorical}, Anderson--Kogan \cite{anderson2005algebra}.
+Distinguished orbits and slices.
+Connections to Mirkovi\'c--Vybornov \cite{mirkovic2007quiver,mirkovic2019comparison}, Cautis--Kamnitzer \cite{cautis2018categorical}, Anderson--Kogan \cite{anderson2005algebra}.
 
@@
 
-Let $\Gr$ denote the ordinary affine Grassmannian, $\Grbd$ the Beilinson--Drinfeld affine Grassmannian, and $\Grc$ the convolution affine Grassmannian.
+Let $\Gr$ denote the ordinary \new{affine Grassmannian} $\Gch(\cK)/\Gch(\cO)$, $\Grbd$ the \new{Beilinson--Drinfeld affine Grassmannian}, and $\Grc$ the \new{convolution affine Grassmannian}.
 
@@
     \end{equation}
-    More generally, one can define a BD grassmannian over any smooth curve $C$ as the reduced ind-scheme $\Grbd_C$ fibered over a finite symmetric power of $C$ such that the fibre over the point $\vec p$ is a collection of vector bundles over $C$ which are trivial away from $\vec p$ viewed also as a subset of $C$.
-To \cite{mirkovic2019comparison} the rank $m$ of the trivial fibres $\scO_C^m$ is the of the group $\GL_m\CC$.
+    The rank of the $m$ in the definition of $\Grbd$ is the dimension of the maximal torus of $\Gch$. For $\Gch =\GL_m = G$.
+
+    More generally, one can define a BD grassmannian of $\GL_m$ over any smooth curve $C$ as the reduced ind-scheme $\Grbd[n,C]$ fibered over a finite symmetric power of $C$ --- $C^{(n)}$ --- such that the fibre over the point $\vec p = (p_1,\dots,p_n)\in C^n$ is a collection of rank $m$ vector bundles $V$ over $C$ which are trivial away from $\vec p$ viewed also as a subset --- $\{p_1,\dots,p_n\}$ --- of $C$.
+Trivial means $\scO_C^m\cong V$.
 \end{definition}
 
-To quote \cite{baumann2020bases} the BD Grassmannian is a relative version of the affine Grassmannian where the base is the space of effective divisors on a smooth curve.
-The choice of $\AA^1$ amply satisfies our needs and offers three advantages: there is a natural global coordinate it, every $G$-torsor on it is trivializable, and the monodromy of any local system is trivial.
-Formally, $\Grbd$ is the functor on the category of commutative $\CC$-algebras that assigns to an algebra $R$ the set of isomorphism classes of triples $(\vec p,V,\sigma)$ where $\vec p\in \AA^n(R)$, $V$ is a $G^\vee$-torsor over $\AA^1_R$ and $\sigma$ is a trivialization of $V$ away from $\vec p$.
+To quote \cite{baumann2020bases} the BD Grassmannian is a relative version of the affine Grassmannian where the base is the space of effective divisors on a smooth curve $C$.
+The choice $C = \AA^1$ ``amply satisfies our needs and offers three advantages: there is a natural global coordinate it, every \anne{$G$-torsor}{i.e.
+principal $G$ bundle?} on it is trivializable, and the monodromy of any local system is trivial.
+Formally, $\Grbd$ is the functor on the category of commutative $\CC$-algebras that assigns to an algebra $R$ the set of isomorphism classes of triples $(\vec p,V,\sigma)$ where $\vec p\in \AA^n(R)$, $V$ is a $G^\vee$-torsor over $\AA^1_R$ and $\sigma$ is a trivialization of $V$ away from $\vec p$.''
+
 They denote by $\pi$ the fibration $\Grbd\to\AA^n$ (forgetting $V$ and $\sigma$).
-
+% 
 Their simplified description is: it's the set of pairs $(\vec p,[\sigma])$ where $\vec p\in\CC^n$ and $[\sigma]$ is an element of the homogeneous space 
@@
 \]
-Their example, our setting: 
+Their example, (almost) our setting: 
 \begin{example}
@@
 
+Our setting is $G= \GL_m$ and $n = 2$.
+
 \begin{definition}
@@
 \begin{example}
-    When $G = \GL_m\CC$ this deformation is described by the datum of $\vec p\in\CC^n$ and a sequence $(L_1,\dots,L_n)$ of $\CC[z]$-lattices in $\CC(z)^m$ such that for some $k\in\ZZ$ and for all $j \in \{1\dots n\}$
+    When $G = \GL_m\CC$ this deformation is described by the datum of $\vec p\in\CC^n$ and a sequence $(L_1,\dots,L_n)$ of $\CC[z]$-lattices in \anne{$\CC(z)^m$}{Why Laurent polynomials for the convolution?} such that for some $k\in\ZZ$ and for all $j \in \{1\dots n\}$
     \[
@@
     \]
-    where again $L_0 = \CC[z]^m$ denotes the standard lattice, and now $L_j = (\sigma_1\cdots\sigma_j)(L_0)$.
+    where again $L_0 = \CC[z]^m$ denotes the standard lattice, while $L_j = (\sigma_1\cdots\sigma_j)(L_0)$.
 Very nice.
@@
 \end{example}
-To be continued: \cite{baumann2020bases} go on to describe the fibres of the composition deformation to $\Grbd$ to $\CC^n$ and their description maybe helpful.
+To be continued: \cite{baumann2020bases} go on to describe the fibres of the \anne{composition}{Not to $\CC^{(n)}$? Or to $\CC$?}
+\[
+    \Grc \to \Grbd \to \CC^n = \AA^n_\CC 
+\] 
+their description may be helpful.
 
@@
 They go on to describe the fusion product (section 5.3) a probably worthwhile read.
+
+Going forward, we'll use $t$ to denote the coordinate on $\AA^1_\CC = \CC$ instead of $z$.
+Then by $t^\mu \in \Gch(\cK)$ we'll denote the point defined by the coweight $\mu \in \Hom(\CC^\times,T^\vee) = T^\vee(\cK)$ and by $L_\mu$ its image $t^\mu \Gch(\cO)$ in $\Gr$.
+
+\begin{definition}
+    Given $\mu_1,\mu_2$ such that $\mu = \mu_1 +\mu_2$ is a partition of $N$ we define $T_{\mu_1,\mu_2}\subset \mat_N$ to be the set of $\mu\times\mu$ block matrices that are zero everywhere except possibly in the last $\min(\mu_i,\mu_j)$ columns of the last row of the $\mu_i\times\mu_j$th block \textit{plus} the block diagonal matrix whose $\mu_i\times\mu_i$ diagonal block is the companion matrix of $t^{\mu_{1,i}}(t-s)^{\mu_{2,i}}$ for each $i\in\{1,2,\dots,m\}$.
+We call this set \new{name}.
+\end{definition}
+
+\begin{remark}
+    While we limit ourselves to the case of dominant partitions, the definition above makes sense for arbitrary partitions.
+\end{remark}
+\begin{remark}
+    Speak to whether or not this slice appears in \cite{mirkovic2007quiver}. We don't think it does. But its ``lift'' might. 
+\end{remark}
+
+\begin{definition}
+    Given $\lambda_1,\lambda_2$ such that $\lambda = \lambda_1 + \lambda_2$ is a partition of $N$ we define $\OO_{\lambda_1,\lambda_2}$ to be the set of $N\times N$ \anne{\new{semi-nilpotent}}{Cute?} matrices $X$ with spectrum in $\{0,s\}$ for some $s\in\CC^\times$ such that
+    $X\big|_{E_0} \in \OO_{\lambda_1}$ and $(X-s)\big|_{E_S}\in\OO_{\lambda_2}$ meaning TODO. 
+    % restricted to its generalized $0$ eigenspace $X$ is nilpotent of Jordan type $\lambda_1$ and restricted to its generalized $s$ eigenspace $X - s$...
+\end{definition}
+
+Correspondingly we have 
+\begin{itemize}
+    \item $W_{\mu_1,\mu_2} = \Gch_1 [t^{-1},(t-s)^{-1}]t^{\mu_1} (t-s)^{\mu_2} \Gch(\cO)$ as a subset of $\Grbd[2]$ where recall the subscript 2 records the fact that we are fixing two points $0,s\in\CC$
+    \item Does $\Grbd[2]^{\lambda_1,\lambda_2}$ admit such an orbit description?
+As a fibration it is pairs $(V,\sigma)$ such that is trivialized away from $(0,s)$ by $\sigma$ and $\sigma$ has type $(\lambda_1,\lambda_2)$ --- the data of the trivialization is equivalent to the data of pairs of lattices $(L_1,L_2)$ such that $L_i \in \Gr^{\lambda_i}$ away from $0$ and $L_1 = L_2\in\Gr^{\lambda}$ at 0?
+    \item In the deformed convolution Gr we have the subset $\Grc[2]^{\lambda_1,\lambda_2}$ of pairs $((0,s),[\sigma_1,\sigma_2])$ (really want arbitrary $(p_1,p_2)$ in place of $(0,s)$ which is the specialization that we make when we work in $\Grbd[2]$ sort of?) with $\sigma_i\in\Gch(\CC[t])(t-p_i)^{\lambda_i}\Gch(\CC[z])$ but this is not important?
+\end{itemize}
+
+\begin{question}
+    Can we describe $W_{\mu_1,\mu_2}\cap \overline{\Gr^{\lambda_1,\lambda_2}}$ as the set of lattices $L$ such that 
+    \[
+        t^{\lambda_{1,1}}(t-s)^{\lambda_{2,1}}L_0 \subset L \subset t^{-\lambda_{1,1}}(t-s)^{-\lambda_{2,1}}L_0
+    \]
+    and $\lim_{s\to 0} \rho^\vee (s)\cdot L = L_\mu$
+\end{question}
 
@@
 Each diagonal block is the companion matrix for $t^{\mu_1}(t-s)^{\mu_2}$.
+Each off-diagonal block is zero everywhere except possibly in the last $\min(\mu_i,\mu_j)$ columns of the last row.
 
@@
 
-\include{examplesp}
+\include{examples}
 

### 2020-12-23 main.tex
more lattice descriptions

@@
 
+Address limitations outside of type $A$?
+
 \section{Notation}
+
+In ordinary $\Gr$ we have the following lattice descriptions valid only in type \(A\).  
+%   Let \(T\) be a maximal torus. 
+%   Denote \(\cO = \CC[t]\) and \(\cK =\CC(t) \).  
+  Given \(\mu\in X^\bullet(T)\), write \(t^\mu\) for its image in \(G(\cK)\) and 
+  % 
+  % E.g.\ \(t^\mu = \diag (t^{\mu_1},\dots,t^{\mu_m})\) in \(GL_m(\cK)\)  and 
+  \(L_\mu\) for its image in 
+  \[
+    \Gr = G(\cK)/G(\cO)  \overset{A}{=}  \{L\overset{\text{free}}{\underset{\text{rank } m}{\subset}} \cO^m : tL \subset L \}
+  \]   % (orbit-stabilizer).
+% 
+Example: \(L_\mu = \Sp_{\cO}(e_it^j : 0\le j <\mu_i)\).  
+  Fact: \(\Gr^T = X^\bullet(T)\)  
+  and other distinguished subsets (needed for the definition of MV cycles and later open subset thereof) are all orbits of fixed points  
+  \[
+    \begin{aligned}
+  % \Gr &= G(\cK)/G(\cO) & & = \{L\subset \CC[t]^m : tL \subset L \} \\
+  \Gr^\lambda &= G(\cO) L_\lambda & & = \{L\in\Gr : t\big|_{\cO^m/L} \text{ has Jordan type } \lambda\} \\
+      \Gr_\mu & = G_1[t^{-1}] L_\mu & & = \{L\in \Gr : L = \Sp_{\cO}(v_1,\dots,v_m) \text{ such that } \\
+        & & & \qquad\quad  v_j = t^{\mu_j} e_j + \sum p_{ij} e_i \text{ with  } \deg p_{ij} < \mu_j \} \\
+  S^\mu_- &= U_-(\cK) L_\mu & & = \{L\in \Gr_\mu : \dim (\cO^k / L\cap \cO^k) = \mu_1 + \dots + \mu_k \}
+    \end{aligned}
+  \]
 

### 2020-12-24 examples.tex
more lattice descriptions
corrected typo in example 7

@@
         gL_0 = \CC[t]\langle
-        (t-s)t^3e_1 - bt e_2 - ce_3 , (t-s)te_2 - de_3, te_3 
+        (t-s)t^3e_1 - (a+bt) e_2 - ce_3 , (t-s)te_2 - de_3, te_3 
         \rangle
@@
     \]
-    which has block type $\mu_1$ and Jordan type $\lambda_1$ as expected. 
+    which has block type $\mu_1$ and Jordan type $\lambda_1$ as expected!
 \end{example}

### 2020-12-26 examples.tex
find the mistake

@@
 
-    Now let's see what we get when we invert $t$ and $t-s$ respectively. First let's find $ L_s = L\otimes\CC\xt$. 
+    Now let's see what we get when we invert $t$ and $t-s$ respectively.
+
+    First let's invert $t$ by considering $L_2 = L\otimes\CC\xt[t-s]$. 
     \[
-        L_s  = \CC[t]\langle(t-s) e_1 - be_2 - ce_3 , (t-s) e_2 , e_3 \rangle = \CC[t]\langle(t-s) e_1 - be_2, (t-s) e_2, e_3 \rangle
+        L_2  = \CC[t,t^{-1}]\langle(t-s) e_1 -\frac{a+bt}{t^3} e_2 - \frac c {t^3} e_3, (t-s) e_2 - \frac d t e_3, e_3 \rangle
     \]
-    so 
+    so in $L_0/L_2$ we have 
     \[
-    \left[t\big|_{L_0/L_s}\right]_{\{[e_1],[e_2]\}} = \begin{bmatrix}
+    t[e_1] = s[e_1] + \frac{a+bt}{t^3} [e_2] + \frac c {t^3}  [e_3] \qquad t[e_2] = s[e_2] + \frac d t[e_3]    \qquad [e_3] = 0 
+    \]
+    and
+    \[
+    \left[t\big|_{L_0/L_2}\right]_{\{[e_1],[e_2]\}} = \begin{bmatrix}
         s \\
-        -b & s 
+        \frac{a+bt}{t^3} & s 
     \end{bmatrix}
     \]
-    which has block type $\mu_2$ and Jordan type $\lambda_2$ as expected.
+    which upon subtracting $s I$ gives a matrix having block type $\mu_2$ and Jordan type $\lambda_2 = (2)$ assuming $\frac{a+bt}{t^3}\ne 0$.
 
-    Next let's find $L_0 = L\otimes\CC\xt[t-s]$. 
+    Next let's invert $t-s$ by considering $L_1 = L\otimes\CC\xt$. 
     \[
-        L_0 = \CC[t]\langle
-        t^3 e_1 - bte_2 - ce_3, te_2 - de_3 , te_3 
+        L_1 = \CC[t,(t-s)^{-1}]\langle
+        t^3 e_1 - \frac{a+bt}{t-s}e_2 - \frac c {t-s} e_3, te_2 - \frac d {t-s} e_3 , te_3 
         \rangle 
     \]
-    so 
+    so in $L_0/L_1$ we have 
+    \begin{align*}
+        t[e_1] &= [te_1] \\
+        t[te_1] &= [t^2 e_1] \\ 
+        t[t^2e_1] & = \frac{a+bt}{t-s}[e_2] + \frac c {t-s} [e_3] \\
+        t[e_2] &= \frac d {t-s} [e_3] \\ 
+        t[e_3] &= 0 
+    \end{align*}
+    and 
     \[
-    \left[t\big|_{L_0/L_s}\right]_{\{[e_1],[te_1],[t^2e_1],[e_2],[e_3]\}} = \begin{bmatrix}
+    \left[t\big|_{L_0/L_1}\right]_{\{[e_1],[te_1],[t^2e_1],[e_2],[e_3]\}} = \begin{bmatrix}
         0 \\
@@
         0 & 1 & 0 \\
-          & & & 0 \\
-          & & & d & 0  
+          & & \frac{a+bt}{t-s} & 0 \\
+          & & \frac c {t-s} & \frac d {t-s} & 0  
     \end{bmatrix}
     \]
-    which has block type $\mu_1$ and Jordan type $\lambda_1$ as expected!
+    taking transpose 
+    \[
+        \begin{bmatrix}
+            0 & 1\\
+              & 0 & 1\\
+              &   & 0 & \frac{a+bt}{t-s} & \frac c {t-s} \\
+              & & & 0 & \frac d {t-s} \\
+              & & & & 0  
+        \end{bmatrix}
+    \]
+    which has block type $\mu_1$ and Jordan type $\lambda_1 = (3,2)$ assuming $\frac{a+bt}{t-s}=0$ and one of the entries in the last column is not zero!?
+
+    We found $a = 0$ and $cs - bd = 0$ above. So actually $\frac{a+bt}{t^3} = \frac b{t^2} \ne 0$ and $\frac{a + bt}{t-s} = \frac{bt}{t-s}$...Roger find my mistake. 
 \end{example}

### 2020-12-26 examples.tex
fixed tings

@@
     \[
-        L_1 = \CC[t,(t-s)^{-1}]\langle
+    \begin{aligned}
+        L_1 &= \CC[t,(t-s)^{-1}]\langle
         t^3 e_1 - \frac{a+bt}{t-s}e_2 - \frac c {t-s} e_3, te_2 - \frac d {t-s} e_3 , te_3 
+        \rangle \\
+        &= \langle
+        t^3 e_1 - \frac{a}{t-s}e_2 - \frac b{t-s} te_2 - \frac c {t-s} e_3, te_2 - \frac d {t-s} e_3 , te_3 
         \rangle
+    \end{aligned}
     \]
@@
         t[te_1] &= [t^2 e_1] \\ 
-        t[t^2e_1] & = \frac{a+bt}{t-s}[e_2] + \frac c {t-s} [e_3] \\
+        t[t^2e_1] &= \frac{a}{t-s}[e_2] + \frac{b}{t-s} t[e_2] + \frac c {t-s} [e_3] \\
+                  &= \frac b{t-s} \frac d{t-s} [e_3] + \frac c {t-s} [e_3] \\ 
+                  &= \frac {bd + (t-s) c} {(t-s)^2} [e_3] \\
+                  &= \frac{bd - sc}{(t-s)^2}[e_3] + \frac c {(t-s)^2} t[e_3] = 0 \\ 
         t[e_2] &= \frac d {t-s} [e_3] \\ 
@@
         0 & 1 & 0 \\
-          & & \frac{a+bt}{t-s} & 0 \\
-          & & \frac c {t-s} & \frac d {t-s} & 0  
+          & & 0 & 0 \\
+          & & 0 & \frac d {t-s} & 0  
     \end{bmatrix}
@@
               & 0 & 1\\
-              &   & 0 & \frac{a+bt}{t-s} & \frac c {t-s} \\
+              &   & 0 &  &  \\
               & & & 0 & \frac d {t-s} \\
@@
     \]
-    which has block type $\mu_1$ and Jordan type $\lambda_1 = (3,2)$ assuming $\frac{a+bt}{t-s}=0$ and one of the entries in the last column is not zero!?
+    which has block type $\mu_1$ and Jordan type $\lambda_1 = (3,2)$ assuming $d\ne 0$.
 
-    We found $a = 0$ and $cs - bd = 0$ above. So actually $\frac{a+bt}{t^3} = \frac b{t^2} \ne 0$ and $\frac{a + bt}{t-s} = \frac{bt}{t-s}$...Roger find my mistake. 
+    I have used the relations Roger found (and I checked) $a = 0$ and $cs - bd = 0$ above.
+
+    To sum up the pair of matrices above should contain the same information as the matrix from the previous example 
+    \[
+    \begin{bmatrix}
+    0 & 1 \\
+      & 0 & 1 \\
+      &   & 0 & 1 \\
+      &   &   & s &  & b & c \\
+      &   &   &   & 0 & 1 & 0 \\
+      &   &   &   & 0 & s & d \\
+      &   &   &   &   &   & 0
+    \end{bmatrix} \Leftrightarrow \left( \begin{bmatrix}
+            0 & 1\\
+              & 0 & 1\\
+              &   & 0 &  &  \\
+              & & & 0 & \frac d {t-s} \\
+              & & & & 0  
+        \end{bmatrix} , \begin{bmatrix}
+        s & \frac b {t^2} \\ & s 
+        \end{bmatrix}\right) 
+    \] 
 \end{example}
+
+{\bf Wish.} Given $L$ in $\Grbd$ define a map to $T_\mu$ just like MVy by taking $[t\big|_{L_0/L}]$ and use the fact that $[t\big|_{L_0/L_i]$ for $i = 1,2$ are companion matrices of the right type/piece together two MVy isomorphisms to make a BD MVy iso.
+
+Lin alg question: if $p(t,t-s) = p_1(t)p_2(t-s)$ how are $C(p_1),C(p_2),C(p)$ related.
+I think it's basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain}

### 2020-12-26 examples.tex
typos

@@
 
-    I have used the relations Roger found (and I checked) $a = 0$ and $cs - bd = 0$ above.
+    I have used the relations Roger found (and I checked) $a = 0$ and $cs - bd = 0$ in the calculations above.
 
-    To sum up the pair of matrices above should contain the same information as the matrix from the previous example 
+    To sum up, the pair of matrices above should contain the same information as the matrix from the previous example 
     \[
@@
 
-{\bf Wish.} Given $L$ in $\Grbd$ define a map to $T_\mu$ just like MVy by taking $[t\big|_{L_0/L}]$ and use the fact that $[t\big|_{L_0/L_i]$ for $i = 1,2$ are companion matrices of the right type/piece together two MVy isomorphisms to make a BD MVy iso.
+{\bf Wish.} Given $L$ in $\Grbd$ define a map to $T_\mu$ just like MVy by taking $[t\big|_{L_0/L}]$ and use the fact that $[t\big|_{L_0/L_i}]$ for $i = 1,2$ are companion matrices of the right type, piece together two MVy isomorphisms to make a BD MVy iso.
 
-Lin alg question: if $p(t,t-s) = p_1(t)p_2(t-s)$ how are $C(p_1),C(p_2),C(p)$ related.
+Equivalent lin alg question: If $p(t,t-s) = p_1(t)p_2(t-s)$ then how are $C(p_1)$, $C(p_2)$, and $C(p)$ related?
 I think it's basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain}

### 2020-12-26 main.tex
Added proof of step 1

@@
 
+    Proof of Step 1: Let $\mu_1 = (\mu_{1,1}, \mu_{1,2}, ..., \mu_{1,n})$, $\mu_2 = (\mu_{2,1}, ..., \mu_{2,n})$, and $\mu = (\mu^{(1)}, \mu^{(2)}, ..., \mu^{(n)})$. Consider the matrix 
+\[
+\sbox0{$\begin{matrix}1&2&3\\0&1&1\\0&0&1\end{matrix}$}
+A = \left[
+\begin{array}{c|c|c|c|c}
+    \vphantom{\usebox{0}}\makebox[\wd0]{\large $C_1$}& \begin{matrix} \\ \\ a_{12}^1 & ...
+& a_{12}^{\mu^{(2)}} \end{matrix} & \makebox[\wd0]{\cdots} & \makebox[\wd0]{\cdots} &  \begin{matrix} \\ \\ a_{1n}^1 & ...
+& a_{1n}^{\mu^{(n)}} \end{matrix} \\ \hline
+     & \vphantom{\usebox{0}}\makebox[\wd0]{\large $C_2$} & \begin{matrix} \\ \\ a_{23}^1 & ... & a_{23}^{\mu^{(3)}}  \end{matrix} & \makebox[\wd0]{\cdots} & \makebox[\wd0]{\vdots} \\ \hline
+     & & \vphantom{\usebox{0}}\makebox[\wd0]{\ddots} & \vphantom{\usebox{0}}\makebox[\wd0]{\ddots} & \makebox[\wd0]{\vdots} \\ \hline
+     & & & C_{n-1} & \begin{matrix} \\ \\ a_{n-1,n}^1 & ... & a_{n-1,n}^{\mu^{(n)}} \end{matrix} \\ \hline
+     & & & & \vphantom{\usebox{0}}\makebox[\wd0]{$C_n$}
+\end{array}
+\right]
+\]
+where $C_i$ is the $\mu^{(i)} \times \mu^{(i)}$ companion matrix of $t^{\mu_{1,i}}(t-s)^{\mu_{2,i}}$. We send this matrix to the matrix 
+\[
+\begin{bmatrix}
+    t^{\mu_{1,1}}(t-s)^{\mu_{2,1}} \\
+    -\sum_{k=1}^{\mu^{(2)}} a_{12}^k t^{k-1} & t^{\mu_{1,2}}(t-s)^{\mu_{2,2}} \\
+    \vdots & \ddots & \ddots \\
+    -\sum_{k=1}^{\mu^{(n)}} a_{1n}^k t^{k-1} & \cdots & -\sum_{k=1}^{\mu^{(n)}} a_{n-1,n}^k t^{k-1} & t^{\mu_{1,n}} (t-s)^{\mu_{2,n}}
+\end{bmatrix}
+\]
+\[
+= \begin{bmatrix}
+    1 \\
+    p_{1,2}(t) & 1 \\
+    \vdots & \ddots & \ddots \\
+    p_{1,n}(t) & \cdots & p_{n-1,n}(t) & 1
+\end{bmatrix}
+\begin{bmatrix}
+    t^{\mu_{1,1}}(t-s)^{\mu_{2,1}} \\
+     & \ddots \\
+     & & t^{\mu_{1,n}} (t-s)^{\mu_{2,n}}
+\end{bmatrix}
+\]
+where 
+\[p_{i,j}(t) = \frac{-\sum_{k=1}^{\mu^{(j)}} a_{i,j}^k t^{k-1}} {t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}}\]
+As $\mu_1$ and $\mu_2$ are dominant, we have $p_{i,j}(t) \rightarrow 0$ as $t \rightarrow \infty$ so this matrix is indeed in $G_1[t^{-1},(t-s)^{-1}]t^{\mu_1}(t-s)^{\mu_2}$.
+
     \item If $A \in \TT_{\mu_1,\mu_2} \cap \n$ then $A$ is sent to $(N_-)_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$. \acom{Requires MVyBD!}

### 2020-12-27 draft.tex
draft begun

\documentclass{article}
\usepackage{basic}
% Working title: 
\title{How to compute the fusion product of MV cycles in type A}
% & , Joel Kamnitzer?
\author{Roger Bai, Anne Dranowski} 
\date{October 2020}

\begin{document}

\maketitle

\section{Players}

$G = \GL_m$.

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr$
    \item The Beilinson--Drinfeld Grassmannian $\Grbd\to C$
    \item Partitions $\mu_i\le\lambda_i$ of $N_i$ ($i=1,2$) and $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of $N = \sum N_i$
    \item The slices $\Gr_\mu$ and $\cW_{\mu_1,\mu_2}$ to the orbits $\Gr^\lambda$ and $(\Grbd[2])^{\lambda_1,\lambda_2}$
    \item The nilpotent and semi-nilpotent cones $\cN$ and $\cN_s$ (of matrices with eigenvalues 0 and 0 or $s\ne 0$)
    \item The slices $\TT_\mu$ and $\TT_{\mu_1,\mu_2}$ to the orbits $\OO_\lambda$ and $\OO_{\lambda_1,\lambda_2}$ 
\end{itemize}

New (?) definitions among these are as follows.
%

The [family of] slices [with $s$-fibre?]
\begin{equation}
    \cW_{\mu_1,\mu_2} = G_1 [t^{-1},(t-s)^{-1}]L_{\mu_1,\mu_2}
\end{equation}
where $L_{\mu_1,\mu_2}\in\Grbd[2]$ is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$; i.e.\
\begin{equation}
    \label{eq:defWBD}
    \begin{split}
        L_{\mu_1,\mu_2}\otimes \CC[(t-s)^{-1}] = L_{\mu_1,\mu_2}\otimes \CC\xt &= L_{\mu_2} \text{ and } \\
        L_{\mu_1,\mu_2}\otimes\CC[t^{-1}] = L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] &= L_{\mu_1}
    \end{split}
\end{equation}
where $L_{\mu_i}$ denotes the point $t^{\mu_i}G(\cO)\in\Gr$. 
%

The family of semi-infinite orbits \acom{Maybe doesn't make sense before specialization?}
\begin{equation}
    S_{\mu_1,\mu_2} = N_-(\cK) L_{\mu_1,\mu_2}\,. 
\end{equation}

The orbit of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as follows
\begin{equation}
    \label{eq:defGrBDlambda}
    \begin{split}
        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : L\otimes\CC[t^{-1}] &\in \Gr^{\lambda_2} \text{ and } \\
        L\otimes\CC[(s-t)^{-1}] &\in \Gr^{\lambda_1}\}\,.
    \end{split}
\end{equation}
% 
\acom{These defining conditions are again just telling us that in the fibre over the fixed point $(0,s)\in C^{(2)}$ this set is pairs of lattices; note that we invert the indeterminates $t$ and $(t-s)$ \textit{after} specializing $(0,s)$. Could we give a more explicit characterization like $t^{N_1}(t-s)^{N_2} L_0 \subseteq L\subseteq t^{-N_1}(t-s)^{-N_2}$?}

The [family ``$\cN\otimes\CC[s]$? $\cN\times\CC$?'' of] semi-nilpotent cone[s fibred over $C = \AA^1$ with $s$-fibre] 
\begin{equation}
    \cN_s = \{A \in \mat(N) : \text{eigenvalues of } A \text{ are } 0 \text{ or }s\}\,.
\end{equation}

The [family of] slice[s $\TT_{\mu_1,\mu_2}$ fibred over $C=\AA^1$ with $s$-fibre]
\begin{equation}
    \begin{split}
        \TT_{\mu_1,\mu_2}^s = \{ B + C_s: B &\text{ is a }\mu\times\mu \text{ block matrix of zeros} \\
        &\text{except possibly in the last }\min(\mu_i,\mu_j) \\ 
        &\text{columns of the last row of each }\mu_i\times\mu_j \text{ block} \\
        &\text{and } C_s \text{ is the block diagonal matrix of}\\
        &\text{companion matrices of } t^{\mu_{1,k}}(t-s)^{\mu_{2,k}}\}\,.
    \end{split}
\end{equation}

The uppertriangular subfamily $\TT_{\mu_1,\mu_2}^{+}$ with $s$-fibre
\begin{equation}
    \TT_{\mu_1,\mu_2}^{+,s} = \{B + C_s \in \TT_{\mu_1,\mu_2} : B \in\n\}
\end{equation}
where $\n\subset\mat(N)$ is the unipotent subalgebra of uppertriangular matrices.

The [family of] orbit[s $\OO_{\lambda_1,\lambda_2}$ fibred over $C = \AA^1$ with $s$-fibre]  
\begin{equation}
    \OO_{\lambda_1,\lambda_2}^s = \{A \in \cN_s : A \text{ is conjugate to } J_{\lambda_1}\oplus (sI_{N_2} + J_{\lambda_2})\}
\end{equation}
where $J_{\lambda_i}$ is the Jordan normal form of block type $\lambda_i$ and $I_{N_2}$ is the identity matrix in $\mat(N_2)$.
% 
\section{Exposition}

\section{Rising Action} % Problem

\section{Climax}

\section{Falling Action} % Resolution

\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu_1 +\mu_2$, and $\lambda =\lambda_1+\lambda_2$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2} \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap \cW_{\mu_1,\mu_2}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda_1,\lambda_2}^s}\cap\TT_{\mu_1,\mu_2}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu_1} (t-s)^{\mu_2} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

Let's call this the MVyBD isomorphism.

\begin{proof}
    The proof is fibre by fibre, so fix $s\ne 0$. \acom{Emphasize in the intro later (because this always confuses me) that by the $s$-fibre we really mean the $(0,s)$-fibre; i.e.\ its the BD Grassmannian over the second symmetric power of $C = \AA^1$; better just replace $s$-fibre by $(0,s)$-fibre everywhere it occurs.}
    \begin{enumerate}
        \item The map is well defined. In particular, it defines $\CC[t]$-lattices in $\CC(t)^m$. Moreover, these lattices break down to give pairs of lattices upon inverting $t$ or $t-s$ that have the right properties. [Copy Roger's proof]
        \item The inverse map is got by taking the matrix of multiplication by $t$ on the quotient $\CC[t]^m/L$ just as in the ordinary MVy isomorphism---the only difference being $\CC\xt$ is replaced by $\CC[t]$.
\begin{enumerate}
    \item $[t]$ will have the right block type with respect to the basis 
    \begin{equation}
        \{[e_i],[te_i],\dots,[t^{\mu_{i}-1}e_i] : 1\le i \le m\}
    \end{equation}
    of $\CC[t]^m/t^{\mu_1}(t-s)^{\mu_2}\CC[t]^m$. 
    We can show this if we can show that $\CC[t]$-lattices satisfying Equation~\ref{eq:defWBD} have a basis of the form 
    \begin{equation}
        v_i = t^{\mu_{1,i}}(t-s)^{\mu_{2,i}} + \sum_{j>i} p_{ij}(t) e_j 
    \end{equation}
    with $\deg p_{ij}(t) < \mu_i = \mu_{1,i} + \mu_{2,i}$ ($1\le i\le m$).
    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu_1,\mu_2}$ in this way?}
    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda_1$ while its generalized $s$-eigenspace will have block type $\le \lambda_2$. 
    This should follow from the defining fact that lattices satisfying Equation~\ref{eq:defGrBDlambda} equivalently satisfy 
    \begin{equation}
        \begin{split}
            t\big|_{\CC\xt^m/L_1}\text{ has Jordan type} \le \lambda_1 \\
            t\big|_{\CC\xt^m/L_2}\text{ has Jordan type} \le \lambda_2 
        \end{split}
    \end{equation}
    where recall $L_i = L\otimes \CC[(t-p_i)^{-1}]$ and $p_1 = s$ while $p_2 = 0$. \acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue? Basic linear algebra? Joel?}
\end{enumerate}
    \end{enumerate}
\end{proof}

\begin{corollary}
    The MVyBD isomorphism restricts to an isomorphism of subfamilies 
    \begin{equation}
        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+ \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}\,. 
    \end{equation}
\end{corollary}

Define $S_{\mu_1,\mu_2}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

\acom{is it a fibre of $S_{\mu_1,\mu_2}$ defined above?}

\begin{lemma}[KWWY14]
    Let $\mu$ be dominant. Then 
    \begin{equation}
        N_{-}\xT[t^{-1}] L_\mu = N_1\xt[t^{-1}]L_\mu
    \end{equation}
    \acom{where I am not sure about the double brackets.}
\end{lemma}

\begin{lemma}%[Roger's lemma]
    Let $\mu_1,\mu_2$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
    \begin{equation}
        S_{\mu_1,\mu_2}^s \subset \Gr_\mu 
    \end{equation}
    where $\mu = \mu_1 + \mu_2$.
\end{lemma}

\begin{proof}
    Copy Roger's proof.
\end{proof}

\section{Denouement}

\end{document}

### 2020-12-30 main.tex
draft begun
Joels comments?

@@
 
+\jcom{Careful: you can define it over $C^n$ or $C^{(n)}$, these are two different things.}
+
 To quote \cite{baumann2020bases} the BD Grassmannian is a relative version of the affine Grassmannian where the base is the space of effective divisors on a smooth curve $C$.
@@
 Formally, $\Grbd$ is the functor on the category of commutative $\CC$-algebras that assigns to an algebra $R$ the set of isomorphism classes of triples $(\vec p,V,\sigma)$ where $\vec p\in \AA^n(R)$, $V$ is a $G^\vee$-torsor over $\AA^1_R$ and $\sigma$ is a trivialization of $V$ away from $\vec p$.''
+\jcom{Yes, $G$-torsor is the same thing as a principal $G$-bundle.}
 
@@
 
+\jcom{This is not correct since, you don't use all information in $ \lambda_1, \lambda_2$.  You need to describe the Jordan type of the quotients, or something equivalent.}
+
 \begin{definition}
@@
 
+\jcom{I think that we figured this out.  We just need to take the matrix corresponding to $ z^{\mu_1}(z-s)^{\mu_2} $ under the MVy isomorphism.}
 \section{Convolution vs BD}
@@
     Proof of Step 1: Let $\mu_1 = (\mu_{1,1}, \mu_{1,2}, ..., \mu_{1,n})$, $\mu_2 = (\mu_{2,1}, ..., \mu_{2,n})$, and $\mu = (\mu^{(1)}, \mu^{(2)}, ..., \mu^{(n)})$. Consider the matrix 
+% TODO: remember to uncomment Roger's matrix 
+\begin{comment}
 \[
@@
 \]
+\end{comment}
 where $C_i$ is the $\mu^{(i)} \times \mu^{(i)}$ companion matrix of $t^{\mu_{1,i}}(t-s)^{\mu_{2,i}}$. We send this matrix to the matrix 

### 2020-12-30 draft.tex
Joels comments?
alternate thm 1

@@
 
+\acom{or---as Joel pointed out, may be ok with:
+The slice $\TT_\mu$ as defined in MVy, no change, \text{and} the family of slices $$\TT_{\mu_1,\mu_2}^{+,s} = \TT_\mu \cap \n + C_{\mu_1,\mu_2}^s$$ where 
+% 
+\begin{equation}
+    C_s \text{ is the block diagonal matrix of companion matrices of } t^{\mu_{1,k}}(t-s)^{\mu_{2,k}}
+\end{equation}
+% not sure about notation
+
+}
+
 The [family of] orbit[s $\OO_{\lambda_1,\lambda_2}$ fibred over $C = \AA^1$ with $s$-fibre]  
@@
 \begin{enumerate}
-    \item $[t]$ will have the right block type with respect to the basis 
+    \item The matrix of $t$ will have the right block type with respect to the basis 
     \begin{equation}
@@
 
+We could also make the following claim. 
+\begin{theorem}[Theorem 1 version 2]
+    Let $\lambda_1,\lambda_2$ and $\mu$ be dominant, such that $\lambda = \lambda_1 + \lambda_2 \ge \mu$. Then there is an isomorphism 
+    \begin{equation}
+        \overline{\OO_{\lambda_1,\lambda_2}} \cap \TT_\mu \to \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu 
+    \end{equation}
+    defined by the same map as in Theorem 1. 
+    Note $\cW_\mu = \Gr_\mu$. 
+\end{theorem}
+
 \begin{lemma}[KWWY14]

### 2020-12-30 draft.tex
application
Joels changes

@@
 
-The [family of] slices [with $s$-fibre?]
+%The [family of] slices [with $s$-fibre?]
+%\begin{equation}
+%    \cW_{\mu_1,\mu_2} = G_1 [t^{-1},(t-s)^{-1}]L_{\mu_1,\mu_2}
+%\end{equation}
+
 \begin{equation}
-    \cW_{\mu_1,\mu_2} = G_1 [t^{-1},(t-s)^{-1}]L_{\mu_1,\mu_2}
+    \cW_\mu = G_1[t^{-1}]L_\mu
 \end{equation}
-where $L_{\mu_1,\mu_2}\in\Grbd[2]$ is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$; i.e.\
+
+Note that $ L_{\mu_1, \mu_2} = (t-s)^{\mu_2} t^{-\mu_2} L_{\mu} \in \cW_\mu$
+and that  $L_{\mu_1,\mu_2}\in\Grbd[2]$ is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$; i.e.\
 \begin{equation}
@@
     \begin{split}
-        L_{\mu_1,\mu_2}\otimes \CC[(t-s)^{-1}] = L_{\mu_1,\mu_2}\otimes \CC\xt &= L_{\mu_2} \text{ and } \\
-        L_{\mu_1,\mu_2}\otimes\CC[t^{-1}] = L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] &= L_{\mu_1}
+        %L_{\mu_1,\mu_2}\otimes \CC[(t-s)^{-1}] =
+        L_{\mu_1,\mu_2}\otimes \CC\xt &= L_{\mu_2} \otimes \CC\xt \text{ and } \\
+        %L_{\mu_1,\mu_2}\otimes\CC[t^{-1}] =
+        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] &= L_{\mu_1} \otimes \CC\xt[t-s]
     \end{split}
@@
 \begin{equation}
-    S_{\mu_1,\mu_2} = N_-(\cK) L_{\mu_1,\mu_2}\,. 
+    S_{\mu_1,\mu_2} = N_-(\CC[t,t^{-1}, (t-s)^{-1}]) L_{\mu_1,\mu_2}\,. 
 \end{equation}
@@
     \begin{split}
-        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : L\otimes\CC[t^{-1}] &\in \Gr^{\lambda_2} \text{ and } \\
-        L\otimes\CC[(s-t)^{-1}] &\in \Gr^{\lambda_1}\}\,.
+        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : 
+        %L\otimes\CC[t^{-1}] 
+        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] 
+        &\in \Gr^{\lambda_2} \text{ and } \\
+        % L\otimes\CC[(s-t)^{-1}] 
+        L_{\mu_1,\mu_2}\otimes \CC\xt &\in \Gr^{\lambda_1}\}\,.
     \end{split}
@@
 [Copy Roger's proof]
-        \item The inverse map is got by taking the matrix of multiplication by $t$ on the quotient $\CC[t]^m/L$ just as in the ordinary MVy isomorphism---the only difference being $\CC\xt$ is replaced by $\CC[t]$.
+        \item The inverse map is got by taking the matrix of multiplication by $t$.
+More precisely, let $ L \in Gr^{BD} \cap \cW_\mu$.
+We work with the quotient $\CC[t]^m/L$ just as in the ordinary MVy isomorphism---the only difference being $\CC\xt$ is replaced by $\CC[t]$.
 \begin{enumerate}
-    \item The matrix of $t$ will have the right block type with respect to the basis 
+    \item 
+    We claim that 
     \begin{equation}
@@
     \end{equation}
-    of $\CC[t]^m/t^{\mu_1}(t-s)^{\mu_2}\CC[t]^m$. 
-    We can show this if we can show that $\CC[t]$-lattices satisfying Equation~\ref{eq:defWBD} have a basis of the form 
+    is a $\CC$-basis of $\CC[t]^m/L$.
+
+    To see this, we use that $ L $ 
+ has a $\CC[t]$-basis of the form 
     \begin{equation}
-        v_i = t^{\mu_{1,i}}(t-s)^{\mu_{2,i}} + \sum_{j>i} p_{ij}(t) e_j 
+        v_i = t^{\mu_i} + \sum_{j>i} p_{ij}(t) e_j 
     \end{equation}
@@
     \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda_1$ while its generalized $s$-eigenspace will have block type $\le \lambda_2$.
-    This should follow from the defining fact that lattices satisfying Equation~\ref{eq:defGrBDlambda} equivalently satisfy 
+    To see this, note that there is a natural isomorphism
+    $$\CC[[t]]^m/(L \otimes_{\CC[t]} \CC[[t]]) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
+    carrying the action of $t $ to the action of $t$.
+
+    The left hand side is the same thing as
+    $$ \CC[[t]]^m / (L \otimes_{\CC[t]} \CC[[t]]) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC[[t]] $$
+
+    the defining fact that lattices satisfying Equation~\ref{eq:defGrBDlambda} equivalently satisfy 
     \begin{equation}
@@
     \end{equation}
-    where recall $L_i = L\otimes \CC[(t-p_i)^{-1}]$ and $p_1 = s$ while $p_2 = 0$.
-\acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue?
-Basic linear algebra?
-Joel?}
+    where recall 
+    $L_i = L\otimes \CC\xt$ ??? 
+    % $L_i = L\otimes \CC[(t-p_i)^{-1}]$ 
+    and $p_1 = s$ while $p_2 = 0$. \acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue? Basic linear algebra? Joel?}
 \end{enumerate}
@@
 \end{proof}
+
+Let
+$\cW_\mu = G_1[t^{-1}]t^\mu $ and $\hat \cW_\mu = G_1[[t^{-1}]] t^\mu$.
+
+\begin{theorem}[Theorem 1 version 2]
+    Let $\lambda_1,\lambda_2$ and $\mu$ 
+    %be dominant
+    be arbitrary, such that $\lambda = \lambda_1 + \lambda_2 \ge \mu$. Then there is an isomorphism 
+    \begin{equation}
+        \overline{\OO_{\lambda_1,\lambda_2}} \cap \TT_\mu \to \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu 
+    \end{equation}
+    defined by the same map as in Theorem 1.
+\end{theorem}
 
@@
 
-Define $S_{\mu_1,\mu_2}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+\begin{proof}
+    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.
+Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
+    $$ g = (g t^{-\mu_1}(t-s)^{-\mu_2}) t^{\mu_1}(t-s)^{\mu_2} \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$$
+    So we get containment in one direction.
+\end{proof}
+
+% Define $S_{\mu_1,\mu_2}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
 
@@
 We could also make the following claim.
-\begin{theorem}[Theorem 1 version 2]
-    Let $\lambda_1,\lambda_2$ and $\mu$ be dominant, such that $\lambda = \lambda_1 + \lambda_2 \ge \mu$. Then there is an isomorphism 
-    \begin{equation}
-        \overline{\OO_{\lambda_1,\lambda_2}} \cap \TT_\mu \to \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu 
-    \end{equation}
-    defined by the same map as in Theorem 1. 
-    Note $\cW_\mu = \Gr_\mu$. 
-\end{theorem}
 
@@
     \begin{equation}
-        S_{\mu_1,\mu_2}^s \subset \Gr_\mu 
+        S_{\mu_1,\mu_2}^s \subset \hat \cW_\mu 
     \end{equation}
@@
 \begin{proof}
-    Copy Roger's proof.
+    % Copy Roger's proof.
+    We have
+\[
+\begin{split}
+    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
+     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
+     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
+     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
+     & = W_{\mu_1 + \mu_2}
+\end{split}
+\]
+where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
+\[
+\frac{t}{t-s} = 
+1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
+\in B_1[[t^{-1}]].
+\]
 \end{proof}
@@
 
+As an application we can compute fusion of stable MV cycles of type $\alpha_i$ for any $i \in I$. What about more general weights? Having $\kpf > 1$.
+
+\begin{proposition}
+    Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
+    \begin{equation}
+        Z_\tau\ast Z_\sigma 
+    \end{equation}
+    is found by??? 
+\end{proposition}
+
 \end{document}

### 2020-12-30 examples.tex
a more intersting example
more examples

@@
-% !TeX root = ./main.tex
+\documentclass{article}
+\usepackage{basic}
+
+\title{Examples}
+\author{Roger Bai, Anne Dranowski, Joel Kamnitzer}
+% \date{October 2020}
+\date{Last edit: \today}
+
+\begin{document}
+
+\maketitle
 
@@
 $x^2 y^2 = (xy-z)^2 + 2(xy - z) z + z^2$.
+
 For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$.
+
+Adding 2020-12-30 14:03:05: Let's take 
+\[
+\begin{aligned}
+    \lambda_2 &= (4,0,0) & \lambda_1 &= (4,4,0) & \lambda &= (8,4,0)\\
+    \mu_2 &= (2,2,0)     & \mu_1 &= (4,2,2)     & \mu &= (6,4,2)
+\end{aligned}    
+\]
+Note that there is only one SSYT of shape $\lambda_i$ and weight $\mu_i$
+\[
+\tau_2 = \young(1122) \qquad \tau_1 = \young(1111,2233)    
+\]
+Note also that 
+$$\begin{aligned}
+    t^4(t-s)^2 &= t^4 (t^2 - 2st + s^2) = t^6 - 2st^5 + s^2 t^4 \\
+    t^2 (t-s)^2 &= t^4 - 2st^3 + s^2 t^2  % \\
+    % t^2 &= t^2 
+\end{aligned}$$
+Elements of $\TT_{\mu_1,\mu_2}^+$ will take the form 
+\[
+A = \left[\begin{BMAT}(e){cccccc:cccc:cc}{cccccc:cccc:cc}
+    & 1 & & & & & & & & & & \\
+    & & 1 & & & & & & & & & \\
+    & & & 1 & & & & & & & & \\
+    & & & & 1 & & & & & & & \\
+    & & & & & 1 & & & & & & \\
+    & & & & -s^2 & 2s & 0 & 0 & a_3 & a_4 & b_1 & b_2 \\
+    & & & & & & & 1 & & & & \\
+    & & & & & & & & 1 & & & \\
+    & & & & & & & & & 1 & & \\
+    & & & & & & & & -s^2 & 2s & c_1 & c_2 \\
+    & & & & & & & & & & & 1 \\
+    & & & & & & & & & & & 
+\end{BMAT}\right]
+\]
+The tableau tells us for each $1\le i\le 12$
+\[
+    \text{Jordan type of } A\big|_{\Sp(e_1,\dots,e_i)\cap E_0} \text{ is shape of }\tau_1\big|_{\text{first $i$ boxes}}
+\]
+So take $i = 10$. Then $A$ restricted to $\CC^{10} \cap E_0$ should have Jordan type $(4,2)$. 
+\acom{How to do it box by box? $s$ columns somehow correspond to $\tau_2$ boxes.}
+Therefore $a_1 = 0$. The 4-cycle is obvious. For the 2-cycle we require $a_2 = 0$. 
+\[
+    \begin{aligned}
+e_1 &\leftarrow e_2 \leftarrow e_3 \leftarrow e_4 \\
+e_7 &\leftarrow e_8 \\
+% e_{11} &\leftarrow e_{12} 
+    \end{aligned}    
+\]
+Now looking at all of $A$ we have continue our 2-cycle to a 4-cycle. Roger found 
+\[
+    e_{10} - \left(\frac{2s}{c_1}  + \frac{s^2 c_2}{c_1^2}\right) e_{11} + \frac{s^2}{c_1} e_{12}
+\]
+This requires $c_1^2 a_4 + c_1b_2s^2 - 2sc_1b_1-s^2 c_2 = 0$ and $a_3 c_1 + s^2 b_1 = 0$.
+
+Now looking for the $s$-eigenspace, we expect $A-s\big|_{\CC^6\cap E_s}$ to have Jordan type $2$. The kernel is spanned by 
+$e_1 + se_2 + s^2 e_3 + s^3 e_4 + s^4 e_5 + s^5 e_6$. It is continued to a 2-cycle by/the 2-cycle is generated by
+$-\frac 5 s e_1 - 4 e_2 - 3 s e_3 - 2 s^2 e_4 - s^3 e_5$. 
+The 3-cycle is maybe 
+$(1/s^2, -4/s, -8, 5s, 3s^2, 2s^3, -s^2/a_3, -s^3/a_3, -s^4/a_3, -s^5/a_3)$ padded with zeros. 
+% The vectors $e_5,e_6, e_9, e_{10}$ are left to form the $s$-eigenspace. 
+% Let's figure this out next.
+
+\[
+A-s = \left[\begin{BMAT}(e){cccccc:cccc:cc}{cccccc:cccc:cc}
+    -s & 1 & & & & & & & & & & \\
+    & -s & 1 & & & & & & & & & \\
+    & & -s & 1 & & & & & & & & \\
+    & & & -s & 1 & & & & & & & \\
+    & & & & -s & 1 & & & & & & \\
+    & & & & -s^2 & s & 0 & 0 & a_3 & a_4 & b_1 & b_2 \\
+    & & & & & & -s & 1 & & & & \\
+    & & & & & & & -s & 1 & & & \\
+    & & & & & & & & -s & 1 & & \\
+    & & & & & & & & -s^2 & s & c_1 & c_2 \\
+    & & & & & & & & & & -s & 1 \\
+    & & & & & & & & & & & -s 
+\end{BMAT}\right]
+\]
 \end{example}
@@
 I think it's basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain}
+
+\begin{example}
+    Let $G = \SL_3$ and $\uvi = 121$.
+    Take $n_\bullet^1 = (1,0,0)$, and $n_\bullet^2 = (1,0,1)$ or $(0,1,0)$.
+So $\mu_1, = (2,2,1)$, $\lambda_1 = (3,1,1)$ and $\mu_2 = (1,1,1)$, $\lambda_2 = (2,1,0)$.
+\acom{We should show that order does not matter.}
+    Then $\TT_{\mu_1,\mu_2}^+\cap\OO_{\lambda_1,\lambda_2}$ is made up of elements 
+    \[
+    \begin{bmatrix}
+        0 & 1 & 0 \\
+        0 & 0 & 1 \\
+        0 & 0 & s & 0 & a_2 & a_3 & b_1 & b_2 \\
+          &   &   & 0 & 1 & 0 \\
+          &   &   & 0 & 0 & 1 \\
+          &   &   & 0 & 0 & s & c_1 & 0 \\
+          &   &   &   &   &   & 0 & 1 \\
+          &   &   &   &   &   & 0 & s 
+    \end{bmatrix}    
+    \]
+    and zero eigenspace conforming to the shape 
+    \[
+    \lambda_1 = \yng(3,1,1)    
+    \] 
+    is made of three cycles
+    \begin{align*}
+        a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
+        e_4 & \\
+        e_7 & 
+    \end{align*}
+    while the $s$-eigenspace confirming to the shape 
+    \[
+    \lambda_2 = \yng(2,1)    
+    \]
+    is made of the two cycles 
+    \begin{align*}
+        e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
+        e_4 + s e_5 + s^2 e_6 & 
+    \end{align*}
+    assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
+\end{example}
+\end{document}

### 2020-12-30 draft.tex

@@
 
+We define
+$$L_\mu = t^\mu, L_{\mu_1, \mu_2} = t^{\mu_1} (t-s)^{\mu_2} \in G((t^{-1}))/G[t]$$
+
 \begin{equation}
-    \cW_\mu = G_1[t^{-1}]L_\mu
+    \cW_\mu = G_1[[t^{-1}]]L_\mu \subset G((t^{-1}))/G[t]
 \end{equation}
+a subscheme of the thick affine Grassmannian
 
@@
 
-The family of semi-infinite orbits \acom{Maybe doesn't make sense before specialization?}
+The family of semi-infinite orbits 
 \begin{equation}
-    S_{\mu_1,\mu_2} = N_-(\CC[t,t^{-1}, (t-s)^{-1}]) L_{\mu_1,\mu_2}\,. 
+    S_{\mu_1,\mu_2} = N_-(\CC((t^{-1}))) L_{\mu_1,\mu_2}\,. 
 \end{equation}
@@
         %L\otimes\CC[t^{-1}] 
-        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] 
+        L \otimes_{\CC[t]} \CC\xt[t-s] 
         &\in \Gr^{\lambda_2} \text{ and } \\
         % L\otimes\CC[(s-t)^{-1}] 
-        L_{\mu_1,\mu_2}\otimes \CC\xt &\in \Gr^{\lambda_1}\}\,.
+        L\otimes_{\CC[t]} \CC\xt &\in \Gr^{\lambda_1} \text{ and } \\ 
+        L \otimes_{\C[t]} \CC\xt[t-a] = L_0 \text{ for all $ a \ne 0, s$} \}\,.
     \end{split}
 \end{equation}
+
+\jcom{It is important to add the condition that the lattices are trivial at $ a $.}
 % 
@@
 
-Let
-$\cW_\mu = G_1[t^{-1}]t^\mu $ and $\hat \cW_\mu = G_1[[t^{-1}]] t^\mu$.
-
 \begin{theorem}[Theorem 1 version 2]
@@
 
+\jcom{This is true as stated with the ``larger'' definition of $ \cW_\mu $.
+In fact, for any $\lambda_1, \lambda_2$, it is true $ \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu $ is contained in a subset that we could call $ \cW_\mu^s$ which we could define as
+$$
+\cW_\mu^s = G_1[[t^{-1}]]t^\mu \cap G[t,t^{-1}, (t-s)^{-1}] / G[t]
+$$
+where we regard $G[t,t^{-1}, (t-s)^{-1}] / G[t] \subset G((t^{-1}))/G[t] $
+
+The way to think about this is as follows: inside the thick affine Grassmannian we can consider the $G$-bundles trivialized away from just 0, $s$, or equivalently those lattices which become the standard lattice after tensoring with $ \CC[[t-a]] $ for any $ a \ne 0, s$.
+}
 \begin{corollary}
@@
     So we get containment in one direction.
+
+    For the reverse containment, we choose $ [g] \in G\overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}$.
+By the lemma below, $[g] \in \cW_\mu$ and thus it lies in the image of our map and we are done.
 \end{proof}
@@
     \begin{equation}
-        S_{\mu_1,\mu_2}^s \subset \hat \cW_\mu 
+        S_{\mu_1,\mu_2}^s \subset \cW_\mu 
     \end{equation}

### 2021-01-03 sage/slicy.py
slice maker

@@ -1,0 +1,105 @@
+# !/opt/sage/sage -python
+
+# Given a sequence $\mu = (\mu_0,\ldots,\mu_m-1)\vdash N$ we wish to output an N by N matrix which takes the form that is predicted by the 
+from sage.all import *
+
+# returns matrix in
+# Mirkovic-Vybornov slice
+# for effective dominant weight \mu
+def mvy(blocktype):
+    numblocks = len(blocktype)
+    # N = sum(blocktype[i] for i in range(numblocks))
+    indices = [(a,b,k) for a in range(numblocks-1) for b in range(a+1,numblocks) for k in range(blocktype[b])]
+    stars = list(var('A_%d' % (i)) for i in range(len(indices)))
+    D = [jordan_block(0,blocktype[i]) for i in range(numblocks)]
+    # T = block_diagonal_matrix(D)
+    P = PolynomialRing(QQ,stars)
+    T = matrix(P,block_diagonal_matrix(D))
+    counter=0
+    for a in range(numblocks-1):
+        for b in range(a+1,numblocks):
+            for k in range(blocktype[b]):
+                # print (a,b,k)
+                # print(sum(blocktype[i] for  i in range(a+1))-1,sum(blocktype[i] for  i in range(b))+k)
+                T[sum(blocktype[i] for  i in range(a+1))-1,sum(blocktype[i] for  i in range(b))+k] = stars[counter]
+                counter+=1
+    return T
+
+# TODO: add support for B = companion_matrix(poly, format='bottom');
+
+def bdmvy(blocktypes):
+    numblocks = len(blocktypes[0])
+    # check that len(blocktypes[0]) == len(blocktypes[1]) 
+    aggregate = [sum(blocktypes[i][j] for i in range(2)) for j in range(numblocks)]
+    # blocktype[0]) + len(blocktype[1]
+    indices = [(a,b,k) for a in range(numblocks-1) for b in range(a+1,numblocks) for k in range(aggregate[b])]
+    stars = list(var('A_%d' % (i)) for i in range(len(indices)))
+    stars.append(var('s'))
+    stars.append(var('t'))
+    # L.<t,s> = LaurentPolynomialRing(QQ)
+    P = PolynomialRing(QQ,stars)
+    p = [(t**blocktypes[0][i]*(t-s)**blocktypes[1][i]).expand() for i in range(numblocks)]
[…]

### 2021-01-03 examples.tex

@@
 \end{example}
+
+\begin{example}
+Let
+    \[
+    \begin{aligned}
+        \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
+        \lambda_2 &= (2,2,1,0) & \mu_2 &= (3,2,1,1)
+    \end{aligned}
+    \]
+so $\lambda_1 - \mu_1 = \alpha_1$ and $\lambda_2 - \mu_2 = \alpha_2 + \alpha_3$. We have the following young tableaux:
+\[
+\tau_1 = \young(12) \hspace{5mm}
+\tau_2 = \young(11,23,4) \hspace{5mm}
+\tau_2' = \young(11,24,3)
+\]
+where $\tau_1$ corresponds to the module $S_1$, $\tau_2$ corresponds to the module $2\rightarrow 3$, and $\tau'_2$ corresponds to the module $2 \leftarrow 3$.
+
+The matrix we are considering is 
+\[
+X = \begin{bmatrix}
+    0 & 1 \\
+     & 0 & 1 \\
+     & -s^2 & 2s & a & b & c & d \\
+     & & & 0 & 1 \\
+     & & & & s & e & f \\
+     & & & & & s & g \\
+     & & & & & & s
+\end{bmatrix}
+\]
+such that $\dim E_0 = 2$, $\dim \ker X = 1$, $\dim E_s = 5$, and $\dim \ker (X-sI) = 3$ where $E_0$ and $E_s$ are the $0$- and $s$-generalized eigenspaces.
+
+We see that the two-cycle in $E_0$ is 
+\[
+\left\{ X\left(e_2 + \frac{s^2}{a}e_4\right), e_2 + \frac{s^2}{a}e_4 \right\}
+= \left\{e_1, e_2 + \frac{s^2}{a}e_4 \right\}.
+\]
+
+As $\tau_2$ and $\tau'_2$ both share $\young(11,2)$, we can find a 2-cycle from just the upper-left $3\times3$ block, and an additional vector in $\ker(X-sI)$ from the upper-left $5\times5$-submatrix.
+The 2-cycle from the $3 \times 3$ block is
+\[
+\left\{e_1 + se_2 + s^2e_3, -\frac{2}{s}e_1 - e_2 \right\}.
+\]
+The additional vector in $\ker(X-sI)$ is $e_4 + se_5$ and this requires $a+sb=0$.
+
+Now consider the case that the young diagram we are working with is $\tau_2$.
+Then we have $e_4 + se_5$ part of a 2-cycle that can be found by looking at the upper-left $6 \times 6$-submatrix.
+We find that the 2-cycle is
+\[
+\left\{e_4 + se_5, -\frac{1}{s}e_4 + \frac{s}{e}e_6 \right\}
+\]
+and this requires that $ae - s^2c = 0$.
+
+The last vector in $\ker(X-sI)$ comes from the entire $X-sI$ and we see it is $-fe_6 + ee_7$, which requires $g=0$ and $ed-cf=0$.
+
+For the case $\tau'_2$, we start with find the third vector in $\ker(X-sI)$ from the upper-left $6 \times 6$-submatrix. We see that it is $e_6$, which requires $c = 0$ and $e = 0$.
+
+For the remaining 2-cycle, we note that $e_4 + se_5 \notin \col(X-sI)$ but $e_6 \in \col(X-sI)$ so our 2-cycle is
+\[
+\left\{ e_6, \frac{1}{g} e_7 \right\}
+\]
+which requires $d = 0$ and $f = 0$.
+
+From the minimal polynomial, we have $X^2 (X-sI)^2 = 0$ which gives us the equations
+\[
+a+sb = cs+eb = bf+cg+ds = esg = 0.
+\]
+Taking $s\rightarrow 0$, we have the following equations for our two cases of $\tau_2$ and $\tau'_2$:
+\[
+\begin{array}{c|c}
+    \tau_2 & \tau'_2 \\ \hline
+    a = 0 & a = 0 \\
+    g = 0 & c = 0 \\
+    eb = 0 & d = 0 \\
+    bf = 0 & e = 0 \\
+    ed-cf = 0 & f = 0
+\end{array}
+\]
+
+For the $\tau_2$ case, the coordinate ring is 
+\[
+\frac{\CC[a,b,c,d,e,f,g]}{\langle a,g,eb,bf,ed-cf \rangle}
+\cong \frac{\CC[b,c,d,e,f]}{\langle eb,bf,ed-cf \rangle}
+= \frac{\CC[b,c,d,e,f]}{\langle e,f \rangle \cap \langle b,ed-cf \rangle}
+\]
+Hence the associated algebraic set is reducible with two irreducible components.
+The component corresponding to the ideal $\langle e,f \rangle$ is $\AA^3$, which corresponds to $\PP^3$, while the ideal $\langle b,ed-cf \rangle$ corresponds to the toric variety whose toric polytope is a square-based pyramid.
+
+As $\tau_2$ corresponds to the module $2 \rightarrow 3$, the irreducible components should correspond to the modules $P_1 = 1 \rightarrow 2 \rightarrow 3$ and $1 \leftarrow 2 \rightarrow 3$.
+Indeed, the MV cycle corresponding to $P_1$ is the Grassmannian $Gr(1,4) \cong \PP^3$ and for $1 \leftarrow 2 \rightarrow 3$, we do get a toric variety with polytope the square-based pyramid.
+
+However for the $\tau'_2$ case, the coordinate ring is 
+\[
+\frac {\CC[a,b,c,d,e,f,g]}{\langle a,c,d,e,f \rangle}
+\cong \CC[b,g]
+\]
+which corresponds to $\AA^2$.
+Since $\tau'_2$ corresponds to the module $2\leftarrow 3$, we expect two irreducible components corresponding to the modules $P_3 = 1 \leftarrow 2 \leftarrow 3$ and $1 \rightarrow 2 \leftarrow 3$.
+$P_3$ corresponds to the variety $Gr(3,4) \cong \PP^3$ and $1 \rightarrow 2 \leftarrow 3$ also corresponds to a toric variety whose polytope is a square-based pyramid (?).
+\end{example}
 \end{document}

### 2021-01-03 examples.tex
just stylin

@@
 
-\title{Examples}
-\author{Roger Bai, Anne Dranowski, Joel Kamnitzer}
+\title{Examples Compendium}
+\author{Roger Bai, Anne Dranowski}
 % \date{October 2020}
-\date{Last edit: \today}
+% , Joel Kamnitzer
+\date{Last edit: approx.\ \today}
 
@@
 
-\section{Examples}
+% \section{Examples}
+\section*{Disjoint, non-dominant $\mu$}
 
@@
 
-\begin{example}
-Do Joel's exercise: It would be good to do an example where we will see some multiplicity in the fusion product.
+\section*{Some multiplicity}
+
+\begin{example}[Joel's exercise] 
+    It would be good to do an example where we will see some multiplicity in the fusion product.
 I think that the simplest example would be the fusion product of the MV cycles for $\SL_3$ of weights $2\alpha_1$ and $2\alpha_2$.
 Following the notation from the mvbasis paper, this would correspond to the following multiplication:
-$x^2 y^2 = (xy-z)^2 + 2(xy - z) z + z^2$.
+$$x^2 y^2 = (xy-z)^2 + 2(xy - z) z + z^2\,.$$
 
@@
 
-Adding 2020-12-30 14:03:05: Let's take 
+% Adding 2020-12-30 14:03:05: 
+Let's also try  
 \[
@@
 
+\begin{comment}
+\section*{Getting a feel for things}
 \begin{example}
@@
 \end{example}
+\end{comment}
 
+\section*{Simple root weights, things working}
 \begin{example}
@@
 
-\begin{example}[Example 7 continued\dots]
+\begin{example}[Continued\dots]
     The matrix $X$ from the previous example defines (under MVy) the matrix 
@@
 
-Equivalent lin alg question: If $p(t,t-s) = p_1(t)p_2(t-s)$ then how are $C(p_1)$, $C(p_2)$, and $C(p)$ related?
-I think it's basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain}
+Equivalent linear algebra question(?): If $p(t,t-s) = p_1(t)p_2(t-s)$ then how are $C(p_1)$, $C(p_2)$, and $C(p)$ related? 
+% I think the answer is basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain}
 
-\begin{example}
+\section*{Non simple root weights}
+\begin{example}[Anne]
     Let $G = \SL_3$ and $\uvi = 121$.
@@
 
-\begin{example}
+\begin{example}[Roger]
 Let

### 2021-01-03 sage/slicy.py
start bmatify, add bdphi

@@ -25,8 +25,6 @@ def mvy(blocktype):
                 counter+=1
     return T
 
-# TODO: add support for B = companion_matrix(poly, format='bottom');
-
 def bdmvy(blocktypes):
     numblocks = len(blocktypes[0])
     # check that len(blocktypes[0]) == len(blocktypes[1]) 
@@ -87,6 +85,22 @@ def sagefy(rows):
     s2 += "]"
     return s2
 
+def ezbmatify(rows,blocktype):
+    N = len(rows)
+    bmat = ""
+
+# Generates output like: 
+# \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c}
+#             0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+#             0 & 0 & 1 & 0 & 0 & 0 & 0 \\
+#             % a & b & c & d & e & f & g \\ 
+#             0 & 0 & 0 & d & e & f & g \\ 
+#             0 & 0 & 0 & 0 & 1 & 0 & 0 \\
+#             0 & 0 & 0 & 0 & 0 & 1 & 0 \\
+#             0 & 0 & 0 & 0 & -s^2 & 2s & k \\
+#             0 & 0 & 0 & 0 & 0 & 0 & 0
+#         \end{BMAT}
+
 # return image of mvy in Gr
 def phi(blocktype):
     m = len(blocktype)
@@ -102,4 +116,24 @@ def phi(blocktype):
                 g[a,b] -= stars[counter]*t**k
                 counter+=1
     g += diagonal_matrix(t**blocktype[i] for i in range(m))
+    return g.transpose()
+
+# return image of mvy in Gr
+def bdphi(blocktypes):
+    m = len(blocktypes[0])
+    # check that len(blocktypes[0]) == len(blocktypes[1]) 
+    aggregate = [sum(blocktypes[i][j] for i in range(2)) for j in range(numblocks)]
+    indices = [(a,b,k) for a in range(m-1) for b in range(a+1,m) for k in range(aggregate[b])]
+    stars = list(var('A_%d' % (i)) for i in range(len(indices)))    
+    stars.append(var('t'))
+    stars.append(var('s'))
+    P = PolynomialRing(QQ,stars)
+    g = matrix(P,m)
+    counter=0
+    for a in range(m-1):
+        for b in range(a+1,m):
+            for k in range(aggregate[b]):
+                g[a,b] -= stars[counter]*t**k
+                counter+=1
[…]

### 2021-01-03 examples.tex
stuck on ex6

@@
 \begin{example}
-$\lambda_1 = (1,0,0)$, $\lambda_2 = (1,1,0)$, $\mu_1 = (0,1,0)$, $\mu_2 = (1,0,1)$.
-\jcom{$\mu = \mu_1 + \mu_2$ determines the blocks we have on the RHS of the BD MVy isomorphism of Equation~\ref{eq:topmvy2}.}
+$\lambda_1 = (1,0,0)$, $\lambda_2 = (1,1,0)$, $\mu_1 = (0,1,0)$, $\mu_2 = (1,0,1)$. \jcom{$\mu = \mu_1 + \mu_2$ determines the blocks we have on the RHS of the BD MVy isomorphism.} 
+\[
+\left[\begin{BMAT}(e){c;c;c}{c;c;c} 
+    s & A_0 & A_1\\
+    0 & 0 & A_2\\
+    0 & 0 & s
+\end{BMAT}\right]    
+\]
+% 
+% In the non-BD case, MVy establish
+% $$
+% \overline{\Gr^\lambda}\cap \cW^\mu \to 
+% \left\{ X = 
+% \left[\begin{BMAT}{cc|cc|c}{cc|cc|c}
+% 0 & 1 & 0 & 0 & 0 \\
+% * & * & * & * & * \\
+% 0 & 0 & 0 & 1 & 0 \\
+% * & * & * & * & * \\
+% * & 0 & * & 0 & * 
+% \end{BMAT}\right] \big| X \in \overline{\OO}_\lambda
+% \right\}
+% $$
 
-In the non-BD case, MVy establish
-$$
-\overline{\Gr^\lambda}\cap \cW^\mu \to 
-\left\{ X = 
-\left[\begin{BMAT}{cc|cc|c}{cc|cc|c}
-0 & 1 & 0 & 0 & 0 \\
-* & * & * & * & * \\
-0 & 0 & 0 & 1 & 0 \\
-* & * & * & * & * \\
-* & 0 & * & 0 & * 
-\end{BMAT}\right] \big| X \in \overline{\OO}_\lambda
-\right\}
-$$
-
-In the BD case the RHS will consist of the same block like matrices $X$ but now having eigenvalues $s, 0$ such that $X - s\big|_{E_s}\in \OO_{\lambda_2}$ 
+% In the BD case the RHS will consist of the same block like matrices $X$ but now having eigenvalues $s, 0$ such that $X - s\big|_{E_s}\in \OO_{\lambda_2}$ 
 \end{example}
@@
 I think that the simplest example would be the fusion product of the MV cycles for $\SL_3$ of weights $2\alpha_1$ and $2\alpha_2$.
-Following the notation from the mvbasis paper, this would correspond to the following multiplication:
-$$x^2 y^2 = (xy-z)^2 + 2(xy - z) z + z^2\,.$$
+    Following the notation from the mvbasis paper, this would correspond to the following multiplication: $$x^2 y^2 = (xy-z)^2 + 2(xy - z) z + z^2\,.$$
 
-For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$.
+For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. Then 
+\[
+\left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc} 
+    0 & 1 & 0 & 0 & 0 & 0\\
+    -s^2 & 2s & A_0 & A_1 & A_2 & A_3\\
+    0 & 0 & 0 & 1 & 0 & 0\\
+    0 & 0 & 0 & 0 & A_4 & A_5\\
+    0 & 0 & 0 & 0 & 0 & 1\\
+    0 & 0 & 0 & 0 & -s^2 & 2s
+    \end{BMAT}\right]
+\]
 
@@
 \end{aligned}    
+\]
+Then 
+\[
+\left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc} 
+    0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+    0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+    0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+    0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
+    0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0\\
+    0 & 0 & 0 & 0 & -s^2 & 2s & A_0 & A_1 & A_2 & A_3 & A_4 & A_5\\
+    0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0\\
+    0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
+    0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0\\
+    0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -s^2 & 2s & A_6 & A_7\\
+    0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
+    0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+    \end{BMAT}\right]    
 \]
@@
     \]
+    % \[
+    %     \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c} 
+    %         0 & 1 & 0 & 0 & 0 & 0 & 0\\
+    %         0 & 0 & 1 & 0 & 0 & 0 & 0\\
+    %         0 & 0 & 0 & A_0 & A_1 & A_2 & A_3\\
+    %         0 & 0 & 0 & 0 & 1 & 0 & 0\\
+    %         0 & 0 & 0 & 0 & 0 & 1 & 0\\
+    %         0 & 0 & 0 & 0 & -s^2 & 2*s & A_4\\
+    %         0 & 0 & 0 & 0 & 0 & 0 & 0
+    %     \end{BMAT}    
+    % \]
 \end{example}
@@
     Let $G = \SL_3$ and $\uvi = 121$.
-    Take $n_\bullet^1 = (1,0,0)$, and $n_\bullet^2 = (1,0,1)$ or $(0,1,0)$.
-So $\mu_1, = (2,2,1)$, $\lambda_1 = (3,1,1)$ and $\mu_2 = (1,1,1)$, $\lambda_2 = (2,1,0)$.
-\acom{We should show that order does not matter.}
-    Then $\TT_{\mu_1,\mu_2}^+\cap\OO_{\lambda_1,\lambda_2}$ is made up of elements 
+
+    Take $n_\bullet^1 = (1,0,0)$, and $n_\bullet^2 = (1,0,1)$ or $(0,1,0)$. So 
     \[
-    \begin{bmatrix}
-        0 & 1 & 0 \\
-        0 & 0 & 1 \\
-        0 & 0 & s & 0 & a_2 & a_3 & b_1 & b_2 \\
-          &   &   & 0 & 1 & 0 \\
-          &   &   & 0 & 0 & 1 \\
-          &   &   & 0 & 0 & s & c_1 & 0 \\
-          &   &   &   &   &   & 0 & 1 \\
-          &   &   &   &   &   & 0 & s 
-    \end{bmatrix}    
+        \begin{aligned}
+            \mu_1 &= (2,2,1) & \mu_2 &= (1,1,1) & \mu &= (3,3,2)\\
+            \lambda_1 &= (3,1,1) & \lambda_2 &= (2,1,0) & \lambda &= (5,2,1)
+        \end{aligned}
     \]
-    and zero eigenspace conforming to the shape 
+    Note
     \[
-    \lambda_1 = \yng(3,1,1)    
+    \tau(1,0,0) = \young(112,2,3) \qquad \tau(1,0,1) = \young(12,3) \qquad \tau(0,1,0) = \young(13,2)    
     \]
-    is made of three cycles
-    \begin{align*}
-        a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
-        e_4 & \\
-        e_7 & 
-    \end{align*}
-    while the $s$-eigenspace confirming to the shape 
+
+    \acom{We should show that order does not matter; i.e.\ swapping indices on $\lambda$'s and $\mu$'s produces the same result.}
+
+    $\TT_{\mu_1,\mu_2}^+\cap\OO_{\lambda_1,\lambda_2}$ is made up of elements of the form
     \[
-    \lambda_2 = \yng(2,1)    
+        A = \left[\begin{BMAT}(e){ccc;ccc;cc}{ccc;ccc;cc} 
+            0 & 1 & 0 & 0 & 0 & 0 & 0 & 0\\
+            0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
+            0 & 0 & s & A_0 & A_1 & A_2 & A_3 & A_4\\
+            0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
+            0 & 0 & 0 & 0 & 0 & 1 & 0 & 0\\
+            0 & 0 & 0 & 0 & 0 & s & A_5 & A_6\\
+            0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
+            0 & 0 & 0 & 0 & 0 & 0 & 0 & s
+            \end{BMAT}\right]
+    % \begin{bmatrix}
+    %     0 & 1 & 0 \\
+    %     0 & 0 & 1 \\
+    %     0 & 0 & s & 0 & a_2 & a_3 & b_1 & b_2 \\
+    %       &   &   & 0 & 1 & 0 \\
+    %       &   &   & 0 & 0 & 1 \\
+    %       &   &   & 0 & 0 & s & c_1 & 0 \\
+    %       &   &   &   &   &   & 0 & 1 \\
+    %       &   &   &   &   &   & 0 & s 
+    % \end{bmatrix}    
     \]
-    is made of the two cycles 
-    \begin{align*}
-        e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
-        e_4 + s e_5 + s^2 e_6 & 
-    \end{align*}
-    assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
+As usual, denote by $E_e$ the generalized $e$-eigenspace of $A$.
+$A\big|_{\CC^3\cap E_0}$ should have Jordan type $(2)$.
+The obvious 2-cycle is generated by $e_2$: $\{e_2, A e_2\}$.
+$A\big|_{\CC^3\cap E_s}$ should have Jordan type $(1)$.
+We take $e_1 + se_2 + s^2 e_3 \in\Ker(A-s)$.
+Next $A\big|_{\CC^6\cap E_0}$ should have Jordan type $(3,1)$ while $A\big|_{\CC^6\cap E_s}$ will have Jordan type $(2)$ or $(1,1)$.
+% This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$.
+The new 1-cycle must be $\{e_4\}$.
+\acom{Why?} Hence our first equation: $A_0 = 0$.
+As to the 3-cycle, it can only be generated by $e_5$, i.e.\ the original 2-cycle is modified: $\{e_5 \mapsto A_1 e_3 + e_4 \mapsto \}$
+% TODO: Make a table 
+% 
+% The zero eigenspace of $A$ conforms to the shape 
+%     \[
+%     \lambda_1 = \yng(3,1,1)    
+%     \] 
+%     is made of three cycles
+%     \begin{align*}
+%         a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
+%         e_4 & \\
+%         e_7 & 
+%     \end{align*}
+%     while the $s$-eigenspace confirming to the shape 
+%     \[
+%     \lambda_2 = \yng(2,1)    
+%     \]
+%     is made of the two cycles 
+%     \begin{align*}
+%         e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
+%         e_4 + s e_5 + s^2 e_6 & 
+%     \end{align*}
+%     assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
 \end{example}

### 2021-01-03 sage/slicy.py

@@ -87,8 +87,31 @@ def sagefy(rows):
 
 def ezbmatify(rows,blocktype):
     N = len(rows)
-    bmat = ""
-
+    m = len(blocktype)
+    bmat = "\\left[\\begin{BMAT}(e){"
+    for i in range(m):
+        for j in range(blocktype[i]):
+            bmat += "c"
+        if i != m - 1:
+            bmat += ";"
+    bmat += "}{"
+    for i in range(m):
+        for j in range(blocktype[i]):
+            bmat += "c"
+        if i != m - 1:
+            bmat += ";"
+    bmat += "} \n"
+    for i in range(N):
+        # m2 += "{"
+        for j in range(N):
+            bmat += str(rows[i][j]) 
+            if j != N-1:
+                bmat += " & "
+        # bmat += "\\\\ \n"
+        if i != N - 1:
+            bmat += "\\\\\n"
+    bmat += "\n\\end{BMAT}\\right]"
+    return print(bmat)
 # Generates output like: 
 # \begin{BMAT}(e){ccc;ccc;c}{ccc;ccc;c}
 #             0 & 1 & 0 & 0 & 0 & 0 & 0 \\

### 2021-01-03 examples.tex
styling and module side

@@
 % I think the answer is basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain} 
-
+\newpage
 \section*{Non simple root weights}
@@
 Next $A\big|_{\CC^6\cap E_0}$ should have Jordan type $(3,1)$ while $A\big|_{\CC^6\cap E_s}$ will have Jordan type $(2)$ or $(1,1)$.
+\acom{This example breaks.
+Why?
+How should we choose weights?}
+
+Take 2: Let's try different weights.
+\[
+\begin{aligned}
+    \mu_1 &= (1,1,0) & \lambda_1 &= (2,0,0) \\
+    \mu_2 &= (1,1,1) & \lambda_2 &= (2,1,0) \\
+    \mu &= (2,2,1) & \lambda &= (4,1,0)
+\end{aligned}    
+\]
+and 
+\[
+\tau(1,0,0) = \young(12) \qquad \tau(1,0,1) = \young(12,3) \quad \tau(0,1,0) = \young(13,2)    
+\]
+Then 
+\[
+A = \left[\begin{BMAT}(e){cc;cc;c}{cc;cc;c} 
+    0 & 1 & 0 & 0 & 0\\
+    0 & s & A_0 & A_1 & A_2\\
+    0 & 0 & 0 & 1 & 0\\
+    0 & 0 & 0 & s & A_3\\
+    0 & 0 & 0 & 0 & s
+    \end{BMAT}\right]
+\]
+We have $E_0 \cap \CC^2 = \Sp(e_1)$, $E_s \cap \CC^2 = \Sp(e_1 + se_2)$.
+Next $E_0 \cap \CC^4$ is spanned by a 2-cycle generated by $-\frac{A_0} s e_2 + e_3$ and $E_s \cap \CC^4$ is spanned by a 2-cycle generated by
+$$
+\frac{s}{A_1 + \frac{A_0}{s}}e_4 + \frac{1}{A_1 + \frac{A_0}{s}} e_3 - \frac 1 s e_1 
+$$ 
+or the additional 1-cycle $e_4 - \frac{A_1}{A_0} e_3$ assuming $A_0 + sA_1 = 0$. 
+Finally $E_s$ is spanned by an additional 1-cycle 
+$$
+e_5 - \frac{A_2}{A_1 + \frac{A_0}{s}} e_4 + \frac 1 s \frac{A_2}{A_1 + \frac{A_0}{s}}e_3 
+$$
+assuming $A_3 = 0$. Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $e_1 + \frac s {A_2} e_5$ and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$. 
+This gives us 
+\[
+    \young(12) \ast \young(12,3) = (A_3) \qquad \young(12) \ast \young(13,2) = (A_0 + sA_1 , A_3) \to (A_0 , A_3)
+\]  
+Does it agree with what is expected on the module/cluster side? 
+\[
+S_1 \ast (1\to 2) = \qquad S_1 \ast (1\leftarrow 2) =
+\]
 % This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$.
@@
 \end{example}
-
+\newpage
 \begin{example}[Roger]

### 2021-01-03 examples.tex
Roger's add what happens on the module side
fixed first non simple root weight ex

@@
 $$
-assuming $A_3 = 0$. Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $e_1 + \frac s {A_2} e_5$ and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$. 
+assuming $A_3 = 0$ and $A_2 = 0$.
+Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $-\frac{1}{s} e_1 + \frac s {A_2} e_5$ and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$.
 This gives us 
 \[
-    \young(12) \ast \young(12,3) = (A_3) \qquad \young(12) \ast \young(13,2) = (A_0 + sA_1 , A_3) \to (A_0 , A_3)
+    \young(12) \ast \young(12,3) = (A_2,A_3) \qquad \young(12) \ast \young(13,2) = (A_0 + sA_1 , A_3) \to (A_0 , A_3)
 \]  
@@
 \[
-S_1 \ast (1\to 2) = \qquad S_1 \ast (1\leftarrow 2) =
+S_1 \ast (1\to 2) = S_1 \oplus (1 \to 2) \qquad S_1 \ast (1\leftarrow 2) = S_1 \oplus (1 \leftarrow 2)
 \]
+The MV cycle of $\young(12)$ is a $\PP^1$: via MVy it has an open subset comprised of matrices 
+\[
+    \left[\begin{BMAT}(e){c;c}{c;c} 
+        0 & A_0\\
+        0 & 0
+        \end{BMAT}\right] : A_0\ne 0
+\]
+The MV cycles of the other two tableaux are made up of matrices of the form 
+\[
+    \left[\begin{BMAT}(e){c;c;c}{c;c;c} 
+        0 & A_0 & A_1\\
+        0 & 0 & A_2\\
+        0 & 0 & 0
+        \end{BMAT}\right] : 
+        \begin{cases}
+            A_0 \ne 0 \text{ and } A_2 = 0 & \tau = \young(12,3) \\
+            A_0 = 0 \text{ and } A_2 \ne 0 & \tau = \young(13,2)
+        \end{cases} 
+\] both $\CC^2$'s. \acom{How do the coordinates relate?}
 % This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$.

### 2021-01-10 examples.tex
spewed cycles
Rogers adds

@@
 $$
-assuming $A_3 = 0$ and $A_2 = 0$.
-Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $-\frac{1}{s} e_1 + \frac s {A_2} e_5$ and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$.
+assuming $A_3 = 0$.
+% and $A_2 = 0$?? 
+Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $-\frac{1}{s} e_1 + \frac s {A_2} e_5$.
+% and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$??
 This gives us 
 \[
-    \young(12) \ast \young(12,3) = (A_2,A_3) \qquad \young(12) \ast \young(13,2) = (A_0 + sA_1 , A_3) \to (A_0 , A_3)
+    \young(12) \ast \young(12,3) = (A_3) \qquad % A_2, 
+    \young(12) \ast \young(13,2) = (A_0 + sA_1) \to (A_0) %  , A_3
 \]  
@@
 Now consider the case that the young diagram we are working with is $\tau_2$.
-Then we have $e_4 + se_5$ part of a 2-cycle that can be found by looking at the upper-left $6 \times 6$-submatrix.
+Then we have $e_4 + se_5 + x(e_1 + se_2 + s^2e_3)$ part of a 2-cycle that can be found by looking at the upper-left $6 \times 6$-submatrix.
 We find that the 2-cycle is
 \[
-\left\{e_4 + se_5, -\frac{1}{s}e_4 + \frac{s}{e}e_6 \right\}
+\left\{e_4 + se_5 + x(e_1 + se_2 + s^2e_3), -\frac{2x}{s}e_1 -xe_2 -\frac{1}{s}e_4 + \frac{s}{e}e_6 \right\}
 \]
@@
 
-For the remaining 2-cycle, we note that $e_4 + se_5 \notin \col(X-sI)$ but $e_6 \in \col(X-sI)$ so our 2-cycle is
+For the remaining 2-cycle, we want it to end with $x(e_1 + se_2 + s^2e_3) + (e_4 + se_5) + ye_6$ so our 2-cycle is
 \[
-\left\{ e_6, \frac{1}{g} e_7 \right\}
+\left\{ x(e_1 + se_2 + s^2e_3) + (e_4 + se_5) + ye_6, -\frac{2x}{s}e_1 -xe_2 -\frac{1}{s}e_4 +\frac{s}{f} e_7\right\}
 \]
-which requires $d = 0$ and $f = 0$.
+which requires $af-ds^2=0$ and $fy-sg = 0$. As $y$ is free, the last equation is not really a restriction on $f$ and $g$.
 
@@
     g = 0 & c = 0 \\
-    eb = 0 & d = 0 \\
-    bf = 0 & e = 0 \\
-    ed-cf = 0 & f = 0
+    eb = 0 & e = 0 \\
+    bf = 0 & bf = 0 \\
+    ed-cf = 0 & 
 \end{array}
@@
 \[
-\frac {\CC[a,b,c,d,e,f,g]}{\langle a,c,d,e,f \rangle}
-\cong \CC[b,g]
+\frac {\CC[a,b,c,d,e,f,g]}{\langle a,c,e,df \rangle}
+\cong \frac{\CC[b,d,f,g]}{\langle df \rangle}
 \]
-which corresponds to $\AA^2$.
+which corresponds to $\AA^3 \cup \AA^3$.
 Since $\tau'_2$ corresponds to the module $2\leftarrow 3$, we expect two irreducible components corresponding to the modules $P_3 = 1 \leftarrow 2 \leftarrow 3$ and $1 \rightarrow 2 \leftarrow 3$.
@@
 \end{example}
+
+\begin{example}[Above example redone]
+    In $\CC[A_0..A_6]$ where 
+    \[
+        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c} 
+            0 & 1 & 0 & 0 & 0 & 0 & 0\\
+            0 & 0 & 1 & 0 & 0 & 0 & 0\\
+            0 & -s^2 & 2s & A_0 & A_1 & A_2 & A_3\\
+            0 & 0 & 0 & 0 & 1 & 0 & 0\\
+            0 & 0 & 0 & 0 & s & A_4 & A_5\\
+            0 & 0 & 0 & 0 & 0 & s & A_6\\
+            0 & 0 & 0 & 0 & 0 & 0 & s
+            \end{BMAT}\right]    
+    \]
+    we have 
+    $$
+    \begin{aligned}
+        \young(12)*\young(11,23,4) &= ({\color{blue}A_6,A_2A_5-A_3A_4},A_1A_4 + A_2s,A_1s + A_0) \\
+        &= (A_6,A_2A_5 - A_3A_4, A_1A_4,A_0) \text{ at } s = 0 \\
+        &= (A_0,A_4,A_5,A_6) \sqcup (A_0,A_1,A_6,A_2A_5 - A_3 A_4) \sqcup (A_0,A_2,A_4,A_6)
+    \end{aligned}
+    $$ 
+    while 
+    $$
+    \begin{aligned}
+        \young(12)*\young(11,24,3) &= ({\color{blue}sA_0A_5 + (1 + s^2)A_1A_5+sA_3},A_2,A_4,A_1s + A_0) \\
+        &= (A_1A_5,A_2,A_4,A_0) \text{ at } s = 0 \\
+        &= (A_0,A_2,A_4,A_5) \sqcup (A_0,A_1,A_2,A_4) 
+    \end{aligned} 
+    $$
+    Cycles are 
+    \[
+    \frac{A_0}{s^2}e_2 + e_4 \xrightarrow{A} e_1    
+    \]
+    and, in the $\young(11,23)$ case, 
+    \[
+    \begin{aligned}
+        e_2 + 2s e_3 \xrightarrow{A-s} e_1 + se_2 + s^2 e_3 \\
+        (sA_4 e_4 + (1 + s^2)A_4 e_5 + se_6)/(sA_4) \xrightarrow{A-s} (e_4 + se_5)/s 
+    \end{aligned}    
+    \]
+    while in the $\young(11,2,3)$ case,
+    \[
+        \begin{aligned}
+      e_6 \xrightarrow{A-s} 0 \\
+      e_4 + (1/s + s) e_5 + (1/A_5) e_7 \xrightarrow{A-s} (1/s)e_4 + e_5 + \ast e_6   
+        \end{aligned}
+    \]
+\end{example}
 \end{document}

### 2021-01-11 examples.tex
added tablaux equations to examples

@@
 \maketitle
+\tableofcontents
 
 % \section{Examples}
-\section*{Disjoint, non-dominant $\mu$}
+\section{\today}
+Let $Z$ be the MV cycle of weight $\alpha_3$ with Lusztig datum $(000,00,1)$ and $Z'$ the MV cycle of weight $\alpha_{1,2}$ with Lusztig datum $(010,00,0)$.
+
+In terms of tableax the fusion $Z\ast Z'$ can be encoded as 
+\begin{align}
+    \young(1,2,4) \ast \young(3) &= \young(13,2,4) + \young(14,2,3) \\
+    S_3 \ast (1\leftarrow 2) &= (1\leftarrow 2 \to 3) + P_3 \\ 
+    (000,00,1)\ast (010,00,0) &= (010,00,1) + (001,00,0) \\
+    &= (A_0 , A_5, A_1A_4 - A_2A_3) \sqcup (A_0 , A_1, A_3) 
+\end{align}
+where the ideals in line 3 are given in coordinates on matrices of the form
+\[
+    \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c} 
+        0 & A_0 & A_1 & A_2\\
+        0 & 0 & A_3 & A_4\\
+        0 & 0 & s & A_5\\
+        0 & 0 & 0 & 0
+        \end{BMAT}\right]
+\]
+
+Next let $Z$ be the MV cycle of weight $\alpha_{1,3}$ having Lusztig datum $(100,01,0)$ and $Z'$ the MV cycle of weight $\alpha_2$ having Lusztig datum $(000,10,0)$.
+
+Again, in terms of tableaux, $Z\ast Z'$ is given by 
+\begin{align}
+    \young(2,4) \ast \young(1,3) &= \young(13,24) + \young(12,34) \\
+    (1\to 2\leftarrow 3) \ast S_2 &= P_2 + (2\leftarrow 3) \oplus (1 \to 2) \\
+    (100,01,0) \ast (000,10,0) &= (010,01,0) + (100,11,0) 
+\end{align}
+
+TODO: fill in the ideals.
+
+Now take $Z$ to be the MV cycle of weight $\alpha_{1,3}$ with Lusztig datum $(010,00,1)$ and leave $Z'$ as above. Then 
+\begin{align}
+    \young(13,2,4) \ast \young(11,23) &= \young(1113,223,4) + \young(1113,224,3) \\
+    (1 \leftarrow 2 \to 3) \ast S_2 &= (2\to 3) \oplus (1\leftarrow 2) + P_2 \\
+    (010,00,1) \ast (000,10,0) &= (010,10,1) + (010,01,0)
+\end{align}
+TODO: fill in the ideals.
+
+Also computed: 
+\begin{align}
+    \young(1,2,4) \ast \young(12,3) &= \young(112,24,3) + \young(112,23,4) \\
+    (000,00,1) \ast (100,10,0) &= (100,01,0) + (100,10,1) \\
+    S_3 \ast (1\to 2) &= (1 \to 2 \leftarrow 3) + (1 \to 2 \to 3) \\
+    &= (A_0,A_5,A_4,A_2) \sqcup (A_0,A_5,A_4,A_6) 
+\end{align}
+in 
+\[
+    \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c} 
+        0 & 1 & 0 & 0 & 0 & 0\\
+        0 & s & A_0 & A_1 & A_2 & A_3\\
+        0 & 0 & 0 & 1 & 0 & 0\\
+        0 & 0 & 0 & s & A_4 & A_5\\
+        0 & 0 & 0 & 0 & s & A_6\\
+        0 & 0 & 0 & 0 & 0 & 0
+        \end{BMAT}\right]    
+\]
+TODO: add explanation, double check the ideals.
+
+Finally, we guess that the fusion $2\alpha_1 \ast 2\alpha_2$ is encoded by the tableau equation 
+\[
+\young(22) \ast \young(11,33) = \young(1122,33) + \young(1123,23) + \young(1133,22)     
+\]
+Remains to check this and make sense of the middle term.
+
+% 1
+% 2 0 
+% 2 1 0 
+% 2 1 0 0
+
+% 2
+% 3 1 
+% 3 1 1 
+% 3 2 1 0
+
+% 2 
+% 3 1 
+% 3 2 0 
+% 3 2 1 0
+
+\section{Disjoint, non-dominant weight}
 
@@
 
-\section*{Some multiplicity}
+\section{Some multiplicity}
 
@@
 
-For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. Then 
+For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. 
 \[
-\left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc} 
+\yng(2) = \{\young(22)\} \qquad \yng(2,2) = \{\young(11,33)\} 
+\]
+Then 
+\[
+A = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc} 
     0 & 1 & 0 & 0 & 0 & 0\\
@@
 \]
+needs $A-s\big|_{\CC^2\cap E_s}$ has Jordan type $(2)$, $A\big|_{\CC^4\cap E_0}$ has Jordan type $(2)$, and $A-s\big|_{E_s}$ has Jordan type $(2,2)$. 
+So 
+\[
+E_0 = \{A_0 \e_1 + s^2\e_3\leftarrow A_0 \e_2 + s^2 \e_4 + (A_0 + A_1 + \frac {2A_0}  s  ) \e_1 + s^2 \e_3 \}   
+\]
+while 
+\begin{gather}
+E_s^1 = \{\e_1 + s \e_2\leftarrow \e_1 + (1 + s) \e_2 \}  \\
+E_s^2 = \{ -\frac{A_2 + sA_3}{A_0 + sA_1}\e_3 - \frac{sA_2 + s^2 A_3}{A_0 + sA_1} \e_4 + \e_5 + s \e_6  \leftarrow\}
+\end{gather}
+if 
+\begin{gather}
+    0 = A_4 + sA_5 \\
+    \to A_0 A_4 \text{ as } s \to 0 
+\end{gather}
+and
 
@@
 \begin{comment}
-\section*{Getting a feel for things}
+\section{Getting a feel for things}
 \begin{example}
@@
 
-\section*{Simple root weights, things working}
+\section{Simple root weights, things working}
 \begin{example}
@@
 \newpage
-\section*{Non simple root weights}
+\section{Non simple root weights}
 \begin{example}[Anne]

### 2021-01-12 examples.tex
added explanation to first two examples

@@
 \]
+Check that 
+\[
+\begin{gathered}
+    E_0 = \{\e_1 , \e_2 , \e_4 - \frac 1 s A_5 \e_3 \} \to \{\e_1 , \e_2 , - A_5 \e_3 \} \\
+    E_s = \{\e_3 + \frac 1 s A_3 \e_2 + \frac 1 s A_1 \e_1 \} \to \{A_3 \e_2 + A_1 \e_1 \}
+\end{gathered}    
+\]
+The equations imposed by the factor tableaux also degenerate.
+\[
+(A_0, sA_2 - A_1 A_5, sA_4 - A_3 A_5) \to (A_0, A_1A_5, A_3A_5) = (A_0,A_5) \sqcup (A_0, A_1, A_3)
+\]
+Need to supplement $A_5 = 0$ case with $\col_3 \wedge \col_4 = 0$ or $A_1 A_4 - A_2 A_3 = 0$ in order that $\dim \ker A = 3$.
+
+\begin{remark}
+    If we take $s\to\infty$ in $E_0$, $E_s$ we get the spanning set $\{\e_1,\e_2,\e_4\}\sqcup\{\e_3\}$. Does this have any significance? 
+\end{remark}
 
@@
     (1\to 2\leftarrow 3) \ast S_2 &= P_2 + (2\leftarrow 3) \oplus (1 \to 2) \\
-    (100,01,0) \ast (000,10,0) &= (010,01,0) + (100,11,0) 
+    (100,01,0) \ast (000,10,0) &= (010,01,0) + (100,11,0) \\
+    & = (A_5, A_0) \sqcup (A_3, A_0 A_4 + A_1 A_5)
 \end{align} 
-
-TODO: fill in the ideals.
+% 
+% TODO: fill in the ideals. 
+Let's verify with MVy. Consider
+\[
+    A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c} 
+        s & A_0 & A_1 & A_2\\
+        0 & 0 & A_3 & A_4\\
+        0 & 0 & s & A_5\\
+        0 & 0 & 0 & 0
+        \end{BMAT}\right] \qquad A-s = 
+        \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c} 
+            0 & A_0 & A_1 & A_2\\
+            0 & -s & A_3 & A_4\\
+            0 & 0 & 0 & A_5\\
+            0 & 0 & 0 & -s
+            \end{BMAT}\right]
+\]
+Then 
+\begin{align}
+    E_0 &= \{s \e_2 - A_0 \e_1, \\
+     & sA_0 \e_4 - A_0 A_5 \e_3 + A_1 A_5 \e_2 - A_0 A_1 \e_1 \text{ if } sA_4 - A_3 A_5 = 0 \}\\
+     &\to \{ \e_1, -A_0A_5 \e_3 + A_1 A_5 \e_2 - A_0 A_1 \e_1 \text{ if } A_3 A_5 = 0 \} \\
+    E_s &= \{\e_1, \\
+        & s\e_3 + A_3 \e_2 \text{ if } sA_1 + A_0 A_3 = 0 \} \\
+        &\to \{ \e_1 , \e_2 \text{ if } A_0 A_3 = 0  \}
+\end{align}
+From this we see that $Z\ast Z'$ is contained in
+\[
+(A_3 A_5 , A_0 A_3) = (A_3) \sqcup (A_5, A_0) 
+\]
+Expected dimension is $4 + 3 - 2 - 1 = 4$ hence the first ideal is not big enough.
+Indeed the case $A_3 = 0$ and $A_5 \ne 0$ has to be supplemented with $A\big|_{s=0}^2 = 0$ since the total Jordan type is $(1,1) + (1,1) = (2,2)$.
+This adds the condition $A_0 A_4 + A_1 A_5 = 0$.
 

### 2021-01-13 examples.tex
multiplicity example

@@
 \end{align}
-TODO: fill in the ideals.
+% TODO: fill in the ideals. 
+Verifying. Consider 
+\[
+    A = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c} 
+        0 & 1 & 0 & 0 & 0 & 0 & 0 & 0\\
+        0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
+        0 & -s^2 & 2s & A_0 & A_1 & A_2 & A_3 & A_4\\
+        0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
+        0 & 0 & 0 & 0 & s & A_5 & A_6 & A_7\\
+        0 & 0 & 0 & 0 & 0 & 0 & 1 & 0\\
+        0 & 0 & 0 & 0 & 0 & 0 & s & A_8\\
+        0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+        \end{BMAT}\right]    
+\]
+and 
+\[
+A - s = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c} 
+    -s & 1 & 0 & 0 & 0 & 0 & 0 & 0\\
+    0 & -s & 1 & 0 & 0 & 0 & 0 & 0\\
+    0 & -s^2 & s & A_0 & A_1 & A_2 & A_3 & A_4\\
+    0 & 0 & 0 & -s & 1 & 0 & 0 & 0\\
+    0 & 0 & 0 & 0 & 0 & A_5 & A_6 & A_7\\
+    0 & 0 & 0 & 0 & 0 & -s & 1 & 0\\
+    0 & 0 & 0 & 0 & 0 & 0 & 0 & A_8\\
+    0 & 0 & 0 & 0 & 0 & 0 & 0 & -s
+    \end{BMAT}\right]
+\]
+Then 
+\begin{align}
+    E_0 &= \{\e_1, \\
+        & \e_4 \text{ if } A_0 = 0, \\
+        &  s\e_6 - A_5 \e_5 + c\e_2  \text{ if } A_2 = 0 , \\
+        & A_5 \e_8 - A_7 \e_6 \text{ if } A_4, A_8 = 0  \} \\ 
+        &\to \{ \e_1 , \e_4, -A_5 \e_5 + c\e_2 , A_5 \e_8 - A_7 \e_6 \\
+        &\text{if } A_0, A_2, A_4, A_8 = 0 \} \\
+    E_s &= \{s^2 \e_3 + s \e_2 + \e_1, s\e_3 - \frac 1 s \e_1, \\
+        & s\e_5 + \e_4 \text{ if } A_1 = 0, \\
+        & s\e_7 + \e_6 + \e_5 \text{ if } A_5 + (A_6 - 1)s = 0 \} \label{ln:a3} \\
+        &\to \{\e_1, \e_4, \e_6 + \e_5 \text{ if } A_1, A_5 = 0 \}
+\end{align}
+In line~\ref{ln:a3} I don't think $A_3 =0$ because we can probably add some combination $a\e_1 + b\e_2 + c\e_3$ so that $\e_7$ maps to both 1-cycles (the 2-d kernel) determined so far.
+
+Thus $Z \ast Z'$ is contained in $(A_0,A_2,A_4,A_8, A_1, A_5)$
 
@@
 
-For this example, I think we need $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. 
+% For this example, I think we need
+Take $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, $\mu_2 = (2,0,2)$. Note that there is only one tableau of weight $\mu_i$ and type $\lambda_i$ for each $i$. 
 \[
@@
 \]
-Then 
+Consider
 \[
@@
 \]
-needs $A-s\big|_{\CC^2\cap E_s}$ has Jordan type $(2)$, $A\big|_{\CC^4\cap E_0}$ has Jordan type $(2)$, and $A-s\big|_{E_s}$ has Jordan type $(2,2)$. 
-So 
-\[
-E_0 = \{A_0 \e_1 + s^2\e_3\leftarrow A_0 \e_2 + s^2 \e_4 + (A_0 + A_1 + \frac {2A_0}  s  ) \e_1 + s^2 \e_3 \}   
-\]
-while 
-\begin{gather}
-E_s^1 = \{\e_1 + s \e_2\leftarrow \e_1 + (1 + s) \e_2 \}  \\
-E_s^2 = \{ -\frac{A_2 + sA_3}{A_0 + sA_1}\e_3 - \frac{sA_2 + s^2 A_3}{A_0 + sA_1} \e_4 + \e_5 + s \e_6  \leftarrow\}
-\end{gather}
-if 
-\begin{gather}
-    0 = A_4 + sA_5 \\
-    \to A_0 A_4 \text{ as } s \to 0 
-\end{gather}
-and
+Then 
+\begin{align}
+E_s &= \{ \e_1 + s\e_2, \e_1 + (s+1) \e_2 \\
+    & \e_5 + s\e_6 + \frac 1 s (A_4 + A_5 s) \e_4 + \frac 1 {s^2} (A_4 + A_5 s) \e_3 \\
+    & \text{if } (A_0 + A_1 s) (A_4 + A_5s) + (A_2 + A_3 s) s^2 = 0 , \\
+    & \e_1 + (s+a) \e_2 + \e_6 + \frac 1 s \e_5 + \frac 1 s A_5 \e_4 - \frac 1 {s^3} A_4 \e_3 \}  \\
+    & \text{if } -2\,{A}_{3}s^{3}-{A}_{2}s^{2}+{A}_{0}{A}_{4}-{A}_{5}s = 0  \\
+E_0 &= \{A_0 \e_1 + s^2 \e_3 , A_0 \e_2 + s^2 \e_4 + \frac{A_1}{A_0}\e_1 - 2s \e_3 \}
+\end{align}
+Taking $s\to 0$ we get 
+\begin{align}
+    E_{s=0} &= \{
+        \e_1 , \e_1 + \e_2, \e_3 \text{ if } A_0A_4 = 0\} \\
+    E_0 &= \{\e_1 , A_0^2 \e_2 + A_1 \e_1 \}
+\end{align}
+So $Z\ast Z'$ is contained in $(A_0A_4)$. If we look at $(A\big|_{s=0})^4$, which must be zero since $\lambda = (4,2)$, we pick up the additional equation ${A}_{1}{A}_{4}+{A}_{0}{A}_{5}$. 
+Therefore the ideal of $Z\ast Z'$ is 
+\begin{equation}
+    (A_0A_4 , A_1A_4 + A_0 A_5 ) \subset \CC[A_0..A_5] 
+\end{equation}
+which decomposes as 
+\((A_4, A_5) \sqcup (A_0, A_1) \sqcup (A_0,A_4) \).
+Since $$\CC[x,y]/(xy,x+y)\cong \CC[z]/(z^2)$$ the component $(A_0,A_4)$ occurs with multiplicity 2 as expected!
+Localize at, or colon out $(A_1,A_5)$.
+
+Note that these ideals correspond to expected tableaux as follows.
+\begin{align}
+\young(22) \ast \young(11,33) &= \young(1122,33) + {\color{red}2?}\young(1123,23) + \young(1133,22)  \\
+  &= (A_4, A_5) + {\color{red}2?}(A_0,A_4) + (A_0, A_1) \\
+  &= (20,2) + {\color{red}2?}(11,1) + (02,0) \\
+  &= (11\to 22) + {\color{red}2?}((1\to (1\leftarrow 2))\to 2) + (11\leftarrow 22) \\ 
+  &= (xy-z)^2 + 2(xy-z)z + z^2
+\end{align} 
+\begin{question}
+    How do we tell from the tableaux that an ideal is occuring with multiplicity? 
+\end{question}
 
 % Adding 2020-12-30 14:03:05: 
+% Removing 2021-01-12 18:59:05
+\begin{comment}
 Let's also try  
@@
 \]
+\end{comment}
 \end{example}

### 2021-02-13 exchange relations examples.tex
Rogers exchange rels and examples

\documentclass{article}
\usepackage{basic}

\title{Exchange Relations Examples}
\author{Roger Bai, Anne Dranowski}
% \date{October 2020}
% , Joel Kamnitzer
\date{Last edit: approx.\ \today}

\begin{document}

\maketitle
\tableofcontents

\section{Preliminaries}
Let $G = SL_4$. Each example will have a fusion product of MV cycles where each cycle is represented by its corresponding generic module. Two tableau are equivalent if we can pad one to get the other. In determining how many restrictions we have at each step, we have the formula:
$$ \#\text{ of free variables in the column} = \#\text{ of box} - \#\text{ of boxes in the column}.$$
We first list out the tableau of each MV cycle:

\[\begin{array}{cccccc} \vspace{1mm}
    S_1 &\leadsto \young(12) & S_2 &\leadsto \young(11,23) & S_3 &\leadsto \young(11,22,34) \\ \vspace{1mm}
    1 \rightarrow 2 &\leadsto \young(12,3) & 1 \leftarrow 2 &\leadsto \young(13,2) & 1 \rightarrow 2 \leftarrow 3 &\leadsto \young(112,24,3) \\ \vspace{1mm}
    2 \rightarrow 3 &\leadsto \young(11,23,4) & 2 \leftarrow 3 &\leadsto \young(11,24,3) & 1 \leftarrow 2 \rightarrow 3 &\leadsto \young(13,2,4) \\
    P_1 &\leadsto \young(12,3,4) & P_2 &\leadsto \young(113,24) & P_3 &\leadsto \young(114,22,3)
\end{array}\]

\section{Example 1: $S_1 * S_2 = 1 \leftarrow 2 + 1 \rightarrow 2$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
    \lambda_2 &= (2,2,0,0) & \mu_2 &= (2,1,1,0) \\
    \lambda &= (4,2,0,0) & \mu &= (3,2,1,0)
\end{aligned}
\]
and the tableaux are
\[
\young(12) \text{ and } \young(11,23).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c}
    0 & 1 & & & & \\
     & 0 & 1 & & & \\
     & -s^2 & 2s & a_1 & a_2 & b_1 \\
     & & & 0 & 1 & \\
     & & & & s & b_2 \\
     & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we do have $e_1 \in \ker X$ and $e_1 +se_2 + s^2 e_3 \in \ker(X-s)$.
    \item There are no restrictions from $X$, but we do expect 1 restriction from $X-s$. Indeed, we require ${\color{red} a_1+sa_2 = 0}$ so that $e_4 + se_5 \in \ker(X-s)$.
    \item We expect 1 restriction from $X-s$. Indeed, we have ${\color{red} a_2b_2 + sb_1 = 0}$ so that $\ker(X-s) \subset \col(X-s)$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2]}{\langle a_1, a_2b_2 \rangle} \cong \frac{\CC[a_2,b_1,b_2]}{\langle a_2 \rangle \cap \langle b_2 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle a_2 \rangle &\leadsto \young(1113,22) &\leadsto 1 \leftarrow 2 \\ 
    \langle b_2 \rangle &\leadsto \young(1112,23) &\leadsto 1 \rightarrow 2
\end{array}
\]

\section{Example 2: $S_3 * S_2 = 2 \rightarrow 3 + 2 \leftarrow 3$}
$S_2 * S_3 = 2 \rightarrow 3 + 2 \leftarrow 3$

Take 
\[\begin{aligned}
    \lambda_1 &= (2,2,2,0) & \mu_1 &= (2,2,1,1) \\
    \lambda_2 &= (2,2,0,0) & \mu_2 &= (2,1,1,0) \\
    \lambda &= (4,4,2,0) & \mu &= (4,3,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(11,22,34) \text{ and } \young(11,23).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){cccc;ccc;cc;c}{cccc;ccc;cc;c}
    0 & 1 & & & & & & & & \\
     & 0 & 1 & & & & & & & \\
     & & 0 & 1 & & & & & & \\
     & & -s^2 & 2s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 \\
     & & & & 0 & 1 & & & & \\
     & & & & & 0 & 1 & & & \\
     & & & & & & s & b_3 & b_4 & c_2 \\
     & & & & & & & 0 & 1 & \\
     & & & & & & & & s & c_3 \\
     & & & & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we do have $e_1 \in \ker X$ and $e_1 +se_2 + s^2 e_3 + s^3 e_4 \in \ker(X-s)$.
    \item We expect 2 restrictions from $X$ and 1 restriction from $X-s$. Indeed, we require ${\color{red} a_1 = 0}$ so that $e_5 \in \ker X$ and ${\color{red} a_2 = 0}$ for $\Sp\{e_1, e_5\} \subset \col X$. Furthermore, we need $\color{red} a_3 = 0$ for $e_5 + se_6 + s^2 e_7 \in \ker(X-s)$.
    \item We expect 2 restrictions from $X$ and 1 restriction from $X-s$. Indeed, we have ${\color{red} b_1 = b_3 = 0}$ so that $e_8 \in \ker X$ and ${\color{red} b_2 = 0}$ for $\ker(X-s) \subset \col (X-s)$.
    \item We expect 2 restrictions from $X$. We require ${\color{red} c_1 = 0}$ and ${\color{red} b_4c_3 -sc_2 = 0}$ so that $\ker X \subset \col X$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,a_3,b_1,b_2,b_3,c_1,b_4c_3 \rangle} \cong \frac{\CC[b_4,c_2,c_3]}{\langle b_4 \rangle \cap \langle c_3 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_4 \rangle &\leadsto \young(1111,2224,33) &\leadsto 2 \leftarrow 3 \\ 
    \langle c_3 \rangle &\leadsto \young(1111,2223,34) &\leadsto 2 \rightarrow 3
\end{array}
\]

\section{Example 3: $S_1 * 2 \rightarrow 3 = P_1 + 1\leftarrow 2 \rightarrow 3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
    \lambda_2 &= (2,2,1,0) & \mu_2 &= (2,1,1,1) \\
    \lambda &= (4,2,1,0) & \mu &= (3,2,1,1)
\end{aligned}
\]
and the tableaux are
\[
\young(12) \text{ and } \young(11,23,4).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
    0 & 1 & & & & & \\
     & 0 & 1 & & & & \\
     & -s^2 & 2s & a_1 & a_2 & b_1 & c_1 \\
     & & & 0 & 1 & & \\
     & & & & s & b_2 & c_2 \\
     & & & & & s & c_3 \\
     & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There are no restrictions coming from $X$, but we expect 1 coming from $X-s$. Indeed, we require ${\color{red} a_1 + sa_2}$ for $e_4 + se_5 \in \ker(X-s)$.
    \item There is 1 restriction from $X-s$. We need ${\color{red} a_1b_2 - s^2b_1 = a_2b_2 + sb_1 = 0}$ so that $\Sp\{e_1 + se_2 + s^2e_3, e_4 + se_5\} \subset \col(X-s)$.
    \item There are 2 restrictions from $X-s$. We need ${\color{red} c_3 = b_1c_2 - b_2c_1 = 0}$ for $\dim \ker (X-s) = 3$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ gives an additional equation of ${\color{red} a_2c_2 + b_1c_3 = 0}$ so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,c_1,c_2,c_3]}{\langle a_1,c_3,a_2b_2,a_2c_2,b_1c_2-b_2c_1 \rangle} \cong \frac{\CC[a_2,b_1,b_2,c_1,c_2]}{\langle b_2,c_2 \rangle \cap \langle a_2,b_1c_2-b_2c_1 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_2,c_2 \rangle &\leadsto \young(1112,23,4) &\leadsto P_1 \\ 
    \langle a_2,b_1c_2-b_2c_1 \rangle &\leadsto \young(1113,22,4) &\leadsto 1 \leftarrow 2 \rightarrow 3
\end{array}
\]

\section{Example 4: $S_1 * 2 \leftarrow 3 = P_3 + 1 \rightarrow 2 \leftarrow 3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
    \lambda_2 &= (2,2,1,0) & \mu_2 &= (2,1,1,1) \\
    \lambda &= (4,2,1,0) & \mu &= (3,2,1,1)
\end{aligned}
\]
and the tableaux are
\[
\young(12) \text{ and } \young(11,24,3).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
    0 & 1 & & & & & \\
     & 0 & 1 & & & & \\
     & -s^2 & 2s & a_1 & a_2 & b_1 & c_1 \\
     & & & 0 & 1 & & \\
     & & & & s & b_2 & c_2 \\
     & & & & & s & c_3 \\
     & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There are no restrictions coming from $X$, but we expect 1 coming from $X-s$. Indeed, we require ${\color{red} a_1 + sa_2}$ for $e_4 + se_5 \in \ker(X-s)$.
    \item There are 2 restrictionsfrom $X-s$. We need ${\color{red} b_1 = b_2 = 0}$ so that $e_6 \in \ker(X-s)$.
    \item There is 1 restriction from $X-s$. We need ${\color{red} a_2c_2 + sc_1 = 0}$ so that $\ker(X-s) \subset \col(X-s)$.
\end{enumerate}
The equations from the minimal polynomial $X^2(X-s)^2$ all go away so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,c_1,c_2,c_3]}{\langle a_1,b_1, b_2,a_2c_2 \rangle} \cong \frac{\CC[a_2,c_1,c_2,c_3]}{\langle a_2 \rangle \cap \langle c_2 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle a_2 \rangle &\leadsto \young(1114,22,3) &\leadsto P_3 \\ 
    \langle c_2 \rangle &\leadsto \young(1112,24,3) &\leadsto 1 \rightarrow 2 \leftarrow 3
\end{array}
\]

\section{Example 5: $S_3 * 1 \rightarrow 2 = 1 \rightarrow 2 \leftarrow 3 + P_1$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,2,2,0) & \mu_1 &= (2,2,1,1) \\
    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
    \lambda &= (4,3,2,0) & \mu &= (3,3,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(11,22,34) \text{ and } \young(12,3).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;c}{ccc;ccc;cc;c}
    0 & 1 & & & & & & & \\
     & 0 & 1 & & & & & & \\
     & & s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 \\
     & & & 0 & 1 & & & & \\
     & & & & 0 & 1 & & & \\
     & & & & & s & b_3 & b_4 & c_2 \\
     & & & & & & 0 & 1 & \\
     & & & & & & & s & c_3 \\
     & & & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There are 2 restrictions coming from $X$ and no restrictions from $X-s$. Indeed, we require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 = 0}$ for $\Sp\{e_1,e_4\} \subset \col X$.
    \item There are 2 restrictions from $X$ and 1 restriction from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_7 \in \ker X$. Furthermore, we need ${\color{red}b_4 = 0}$ so that $\dim \ker (X-s) = 2$.
    \item There are 2 restrictions from $X$. We need ${\color{red} c_2 = b_2c_3 - sc_1 = 0}$ for $\ker X \subset \col X$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,b_1,b_3,b_4,c_2,b_2c_3 \rangle} \cong \frac{\CC[a_3,b_2,c_1,c_3]}{\langle b_2 \rangle \cap \langle c_3 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_2 \rangle &\leadsto \young(1112,224,33) &\leadsto 1 \rightarrow 2 \leftarrow 3 \\ 
    \langle c_3 \rangle &\leadsto \young(1112,223,34) &\leadsto P_1
\end{array}
\]

\section{Example 6: $S_3 * 1 \leftarrow 2 = P_3 + 1 \leftarrow 2 \rightarrow 3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,2,2,0) & \mu_1 &= (2,2,1,1) \\
    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
    \lambda &= (4,3,2,0) & \mu &= (3,3,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(11,22,34) \text{ and } \young(13,2).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;c}{ccc;ccc;cc;c}
    0 & 1 & & & & & & & \\
     & 0 & 1 & & & & & & \\
     & & s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 \\
     & & & 0 & 1 & & & & \\
     & & & & 0 & 1 & & & \\
     & & & & & s & b_3 & b_4 & c_2 \\
     & & & & & & 0 & 1 & \\
     & & & & & & & s & c_3 \\
     & & & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There are 2 restrictions coming from $X$ and 1 restriction from $X-s$. Indeed, we require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 = 0}$ for $\Sp\{e_1,e_4\} \subset \col X$. Furthermore, we require ${\color{red} a_3 = 0}$ for $e_4 + se_5 + s^2e_6 \in \ker(X-s)$.
    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_7 \in \ker X$.
    \item There are 2 restrictions from $X$. We need ${\color{red} b_4c_3 - sc_2 = b_2c_3 - sc_1 = 0}$ for $\ker X \subset \col X$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,a_3,b_1,b_3,b_2c_3,b_4c_3 \rangle} \cong \frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2,b_4 \rangle \cap \langle c_3 \rangle}$$
However, for the ideal $\langle c_3 \rangle$, we require $\dim \ker (X|_{s = 0}) = 3$ so we also need to include the equation ${\color{red} b_2c_2 - b_4c_1 = 0}$. Then the coordinate ring is really
$$\frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2,b_4 \rangle \cap \langle c_3,b_2c_2-b_4c_1 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_2,b_4 \rangle &\leadsto \young(1114,222,33) &\leadsto P_3 \\ 
    \langle c_3,b_2c_2-b_4c_1 \rangle &\leadsto \young(1113,222,34) &\leadsto 1 \leftarrow 2 \rightarrow 3
\end{array}
\]

\section{Example 7: $1 \leftarrow 2 * 2 \leftarrow 3 = P_2 + S_2 \oplus P_3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,1,0,0) & \mu_1 &= (1,1,1,0) \\
    \lambda_2 &= (2,2,1,0) & \mu_2 &= (2,1,1,1) \\
    \lambda &= (4,3,1,0) & \mu &= (3,2,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(13,2) \text{ and } \young(11,24,3).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
    0 & 1 & & & & & & \\
     & 0 & 1 & & & & & \\
     & -s^2 & 2s & a_1 & a_2 & b_1 & b_2 & c_1 \\
     & & & 0 & 1 & & & \\
     & & & & s & b_3 & b_4 & c_2 \\
     & & & & & 0 & 1 & \\
     & & & & & & s & c_3 \\
     & & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 = 0}$ for $e_4 + se_5 \in \ker (X-s)$.
    \item There are no restrictions from $X$ but 2 restrictions from $X-s$. We need ${\color{red} b_1 + sb_2 = b_3 + sb_4 = 0}$ so that $e_6 + se_7 \in \ker (X-s)$.
    \item There is 1 restriction from $X-s$. We need ${\color{red} b_2c_3 - sc_1 = 0}$ for $\ker (X-s) \subset \col (X-s)$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,b_1,b_3,b_2c_3 \rangle} \cong \frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2 \rangle \cap \langle c_3 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_2 \rangle &\leadsto \young(1114,223,3) &\leadsto S_2 \oplus P_3 \\ 
    \langle c_3 \rangle &\leadsto \young(1113,224,3) &\leadsto P_2
\end{array}
\]

\section{Example 8: $1 \rightarrow 2 * 2 \rightarrow 3 = P_2 + S_2 \oplus P_1$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,1,0,0) & \mu_1 &= (1,1,1,0) \\
    \lambda_2 &= (2,2,1,0) & \mu_2 &= (2,1,1,1) \\
    \lambda &= (4,3,1,0) & \mu &= (3,2,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(12,3) \text{ and } \young(11,23,4).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
    0 & 1 & & & & & & \\
     & 0 & 1 & & & & & \\
     & -s^2 & 2s & a_1 & a_2 & b_1 & b_2 & c_1 \\
     & & & 0 & 1 & & & \\
     & & & & s & b_3 & b_4 & c_2 \\
     & & & & & 0 & 1 & \\
     & & & & & & s & c_3 \\
     & & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There is no restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 + sa_2 = 0}$ for $e_4 + se_5 \in \ker (X-s)$.
    \item There is 1 restriction from $X$ and 1 restriction from $X-s$. We need ${\color{red} b_3 = 0}$ so that $\dim \ker X = 2$. Furthermore, we have ${\color{red} b_1 + a_2b_4 +sb_2 = 0}$ so that $\Sp\{e_1 + se_2 + s^2e_3, e_4 + se_5\} \subset \col (X-s)$.
    \item There are 2 restrictions from $X-s$. We need ${\color{red} c_3 = b_1c_2 + s(b_2c_2 - b_4c_1) = 0}$ for $\dim \ker (X-s) = 3$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ gives the additional equation ${\color{red} a_2c_2 + sc_1 = 0}$ so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,b_3,c_3,b_1 + a_2b_4,b_1c_2,a_2c_2 \rangle} \cong \frac{\CC[a_2,b_1,b_2,b_4,c_1,c_2]}{\langle a_2,b_1 \rangle \cap \langle b_1+a_2b_4,c_2 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle a_2,b_1 \rangle &\leadsto \young(1113,224,3) &\leadsto P_2 \\ 
    \langle b_1+a_2b_4,c_2 \rangle &\leadsto \young(1112,233,4) &\leadsto S_2 \oplus P_1
\end{array}
\]

\section{Example 9: $S_2 * 1 \leftarrow 2 \rightarrow 3 = P_2 + 1 \leftarrow 2 \oplus 2 \rightarrow 3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,2,0,0) & \mu_1 &= (2,1,1,0) \\
    \lambda_2 &= (2,1,1,0) & \mu_2 &= (1,1,1,1) \\
    \lambda &= (4,3,1,0) & \mu &= (3,2,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(11,23) \text{ and } \young(13,2,4).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
    0 & 1 & & & & & & \\
     & 0 & 1 & & & & & \\
     & & s & a_1 & a_2 & b_1 & b_2 & c_1 \\
     & & & 0 & 1 & & & \\
     & & & & s & b_3 & b_4 & c_2 \\
     & & & & & 0 & 1 & \\
     & & & & & & s & c_3 \\
     & & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 = 0}$ for $e_4 + se_5 \in \ker (X-s)$.
    \item There is 1 restriction from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = 0}$ so that $\ker X \subset \col X$.
    \item There are 2 restrictions from $X-s$. We need ${\color{red} c_3 = b_3c_1 + s(b_2c_2 - b_4c_1) = 0}$ for $\dim \ker (X-s) = 3$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,b_1,c_3, b_3c_1 \rangle} \cong \frac{\CC[b_2,b_3,b_4,c_1,c_2]}{\langle b_3 \rangle \cap \langle c_1 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_3 \rangle &\leadsto \young(1113,224,3) &\leadsto P_2 \\ 
    \langle c_1 \rangle &\leadsto \young(1113,223,4) &\leadsto 1 \leftarrow 2 \oplus 2 \rightarrow 3 
\end{array}
\]

\section{Example 10: $S_2 * 1 \rightarrow 2 \leftarrow 3 = P_2 + 1 \rightarrow 2 \oplus 2 \leftarrow 3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,2,0,0) & \mu_1 &= (2,1,1,0) \\
    \lambda_2 &= (3,2,1,0) & \mu_2 &= (2,2,1,1) \\
    \lambda &= (5,4,1,0) & \mu &= (4,3,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(11,23) \text{ and } \young(112,24,3).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){cccc;ccc;cc;c}{cccc;ccc;cc;c}
    0 & 1 & & & & & & & & \\
     & 0 & 1 & & & & & & & \\
     & & 0 & 1 & & & & & & \\
     & & -s^2 & 2s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 \\
     & & & & 0 & 1 & & & & \\
     & & & & & 0 & 1 & & & \\
     & & & & & s^2 & 2s & b_3 & b_4 & c_2 \\
     & & & & & & & 0 & 1 & \\
     & & & & & & & & s & c_3 \\
     & & & & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_5 \in \ker X$ and ${\color{red} a_2 + sa_3 = 0}$ for $e_5 + se_6 + s^2 e_7 \in \ker (X-s)$.
    \item There is 1 restriction from $X$ and 2 restrictions from $X-s$. We need ${\color{red} a_2b_3 + s^2b_1 = a_3b_3 - sb_1 = 0}$ so that $\ker X \subset \col X$. Furthermore, we require ${\color{red} b_1 + sb_2 = b_3 + sb_4 = 0}$ so that $e_8 + se_9 \in \ker (X-s)$.
    \item There is 1 restriction from $X-s$. We need ${\color{red} b_3c_3 - s^2c_2 = b_4c_3 + sc_2 = 0}$ for $\ker (X-s) \subset \col (X-s)$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^3$ gives the additional equations ${\color{red} a_3b_4 + b_1 = a_3c_2 + b_2c_3 = 0}$ so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,b_1,b_3,a_3b_4,b_4c_3,a_3c_2+b_2c_3 \rangle} \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3]}{\langle b_4,a_3c_2+b_2c_3 \rangle \cap \langle a_3,c_3 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_4,a_3c_2+b_2c_3 \rangle &\leadsto \young(11112,2234,3) &\leadsto 1 \rightarrow 2 \oplus 2 \leftarrow 3 \\ 
    \langle a_3,c_3 \rangle &\leadsto \young(11113,2224,3) &\leadsto P_2
\end{array}
\]

\section{Example 11: $1 \leftarrow 2 \rightarrow 3 * 1 \rightarrow 2 = 1 \leftarrow 2 \oplus P_1  + S_1 \oplus P_2$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,1,1,0) & \mu_1 &= (1,1,1,1) \\
    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
    \lambda &= (4,2,1,0) & \mu &= (2,2,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(13,2,4) \text{ and } \young(12,3).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
    0 & 1 & & & & & \\
     & s & a_1 & a_2 & b_1 & b_2 & c_1 \\
     & & 0 & 1 & & & \\
     & & & s & b_3 & b_4 & c_2 \\
     & & & & 0 & 1 & \\
     & & & & & s & c_3 \\
     & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ but no restrictions from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_3 \in \ker X$.
    \item There are no restrictions from $X$ and 1 restriction from $X-s$. We need ${\color{red} b_3 + sb_4 = 0}$ so that $e_5 + se_6 \in \ker (X-s)$.
    \item There are 2 restrictions from $X-s$. We need ${\color{red} c_3 = b_1c_2-b_3c_1 = 0}$ for $\ker (X-s) \subset \col (X-s)$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^3$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,b_3,c_3,b_1c_2 \rangle} \cong \frac{\CC[a_2,b_1,b_2,b_4,c_1,c_2]}{\langle b_1 \rangle \cap \langle c_2 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_1 \rangle &\leadsto \young(1123,24,3) &\leadsto S_1 \oplus P_2 \\ 
    \langle c_2 \rangle &\leadsto \young(1123,23,4) &\leadsto 1 \leftarrow 2 \oplus P_1 
\end{array}
\]
\end{document}

### 2021-02-14 exchange relations examples.tex
Finished examples.

@@
 
-\section{Preliminaries}
+\section*{Preliminaries}
 Let $G = SL_4$.
@@
 \end{enumerate}
-The minimal polynomial $X^2(X-s)^3$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
+The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
 $$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,b_3,c_3,b_1c_2 \rangle} \cong \frac{\CC[a_2,b_1,b_2,b_4,c_1,c_2]}{\langle b_1 \rangle \cap \langle c_2 \rangle}$$
@@
 \]
+
+\section{Example 12: $1 \rightarrow 2 \leftarrow 3 * 1 \leftarrow 2 = 1 \rightarrow 2 \oplus P_3  + S_1 \oplus P_2$}
+Take 
+\[\begin{aligned}
+    \lambda_1 &= (3,2,1,0) & \mu_1 &= (2,2,1,1) \\
+    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
+    \lambda &= (5,3,1,0) & \mu &= (3,3,2,1)
+\end{aligned}
+\]
+and the tableaux are
+\[
+\young(112,24,3) \text{ and } \young(13,2).
+\]
+The matrix in consideration is:
+\[
+X = \left[\begin{BMAT}(e){ccc;ccc;cc;c}{ccc;ccc;cc;c}
+    0 & 1 & & & & & & & \\
+     & 0 & 1 & & & & & & \\
+     & & s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 \\
+     & & & 0 & 1 & & & & \\
+     & & & & 0 & 1 & & & \\
+     & & & & & s & b_3 & b_4 & c_2 \\
+     & & & & & & 0 & 1 & \\
+     & & & & & & & s & c_3 \\
+     & & & & & & & & 0
+\end{BMAT}
+\right]
+\]
+\begin{enumerate}[label=\boxed{\arabic*}:]
+    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 +s^2e_3 \in \ker (X-s)$.
+    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$.
+We require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 + sa_3 = 0}$ for $e_4 + se_5 + s^2e_6 \in \ker (X-s)$.
+    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_7 \in \ker X$.
+    \item There is 1 restriction from $X-s$. We need ${\color{red} b_4c_3 - sc_2 = 0}$ for $\ker (X-s) \subset \col (X-s)$.
+\end{enumerate}
+The minimal polynomial $X^3(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
+$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,b_1,b_3,b_4c_3 \rangle} \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3]}{\langle b_4 \rangle \cap \langle c_3 \rangle}$$
+The corresponding tableau for each ideal is:
+\[\begin{array}{ccc}\vspace{1mm}
+    \langle b_4 \rangle &\leadsto \young(11124,223,3) &\leadsto 1 \rightarrow 2 \oplus P_3 \\ 
+    \langle c_3 \rangle &\leadsto \young(11123,224,3) &\leadsto S_1 \oplus P_2
+\end{array}
+\]
+
+\section{Example 13: $1 \leftarrow 2 \rightarrow 3 * 2 \leftarrow 3 = 2 \rightarrow 3 \oplus P_3  + S_3 \oplus P_2$}
+Take 
+\[\begin{aligned}
+    \lambda_1 &= (2,2,1,0) & \mu_1 &= (2,1,1,1) \\
+    \lambda_2 &= (2,1,1,0) & \mu_2 &= (1,1,1,1) \\
+    \lambda &= (4,3,2,0) & \mu &= (3,2,2,2)
+\end{aligned}
+\]
+and the tableaux are
+\[
+\young(11,24,3) \text{ and } \young(13,2,4).
+\]
+The matrix in consideration is:
+\[
+X = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
+    0 & 1 & & & & & & & \\
+     & 0 & 1 & & & & & & \\
+     & & s & a_1 & a_2 & b_1 & b_2 & c_1 & c_2 \\
+     & & & 0 & 1 & & & & \\
+     & & & & s & b_3 & b_4 & c_3 & c_4 \\
+     & & & & & 0 & 1 & & \\
+     & & & & & & s & c_5 & c_6 \\
+     & & & & & & & 0 & 1 \\
+     & & & & & & & & s
+\end{BMAT}
+\right]
+\]
+\begin{enumerate}[label=\boxed{\arabic*}:]
+    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 +s^2e_3 \in \ker (X-s)$.
+    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 = 0}$ for $e_4 + se_5 \in \ker (X-s)$.
+    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_6 \in \ker X$.
+    \item There is 1 restriction from $X$ and 2 restrictions from $X-s$.
+We need ${\color{red} b_2c_5 - sc_1 = b_2c_6 - c_1 = 0}$ for $\ker X \subset \col X$.
+Furthermore, we need ${\color{red} c_5 + sc_6 = 0}$ and ${\color{red} b_2c_3 - b_4c_1 + s(b_2c_4 - b_4c_2) = 0}$ so that $\dim \ker (X-s) = 3$.
+\end{enumerate}
+The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
+$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3,c_4,c_5,c_6]}{\langle a_1,a_2,b_1,b_3,c_5, c_1-b_2c_6,b_2c_3-b_4c_1 \rangle} \cong \frac{\CC[b_2,b_4,c_1,c_2,c_3,c_4,c_6]}{\langle b_2,c_1 \rangle \cap \langle c_1-b_2c_6, c_3-b_4c_6, b_2c_3-b_4c_1 \rangle}$$
+The corresponding tableau for each ideal is:
+\[\begin{array}{ccc}\vspace{1mm}
+    \langle b_2,c_1 \rangle &\leadsto \young(1114,223,34) &\leadsto 2 \rightarrow 3 \oplus P_3 \\ 
+    \langle c_1-b_2c_6,c_3-b_4c_6,b_2c_3-b_4c_1 \rangle &\leadsto \young(1113,224,34) &\leadsto S_3 \oplus P_2
+\end{array}
+\]
+
+\section{Example 14: $1 \rightarrow 2 \leftarrow 3 * 2 \rightarrow 3 = 2 \leftarrow 3 \oplus P_1  + S_3 \oplus P_2$}
+Take 
+\[\begin{aligned}
+    \lambda_1 &= (3,2,1,0) & \mu_1 &= (2,2,1,1) \\
+    \lambda_2 &= (2,2,1,0) & \mu_2 &= (2,1,1,1) \\
+    \lambda &= (5,4,2,0) & \mu &= (4,3,2,2)
+\end{aligned}
+\]
+and the tableaux are
+\[
+\young(112,24,3) \text{ and } \young(11,23,4).
+\]
+The matrix in consideration is:
+\[
+X = \left[\begin{BMAT}(e){cccc;ccc;cc;cc}{cccc;ccc;cc;cc}
+    0 & 1 & & & & & & & & & \\
+     & 0 & 1 & & & & & & & & \\
+     & & 0 & 1 & & & & & & & \\
+     & & -s^2 & 2s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 & c_2 \\
+     & & & & 0 & 1 & & & & & \\
+     & & & & & 0 & 1 & & & & \\
+     & & & & & & s & b_3 & b_4 & c_3 & c_4 \\
+     & & & & & & & 0 & 1 & & \\
+     & & & & & & & & s & c_5 & c_6 \\
+     & & & & & & & & & 0 & 1 \\
+     & & & & & & & & & & s
+\end{BMAT}
+\right]
+\]
+\begin{enumerate}[label=\boxed{\arabic*}:]
+    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 +s^2e_3 + s^3e_4 \in \ker (X-s)$.
+    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$.
+We require ${\color{red} a_1 = 0}$ for $e_5 \in \ker X$ and ${\color{red} a_2 + sa_3 = 0}$ for $e_5 + se_6 + s^2e_7 \in \ker (X-s)$.
+    \item There are 2 restrictions from $X$ and 1 restriction from $X-s$.
+We need ${\color{red} b_1 = b_3 = 0}$ so that $e_8 \in \ker X$.
+Furthermore, we need ${\color{red} a_2b_4 - s^2b_2 = a_3b_4 + sb_2 = 0}$ for $\Sp\{e_1 + se_2 +s^2e_3 + s^3e_4, e_5 + se_6 + s^2e_7\} \subset \col (X-s)$.
+    \item There is 1 restriction from $X$ and 2 restrictions from $X-s$.
+We need ${\color{red} b_4c_5 - sc_3 = 0}$ for $\ker X \subset \col X$.
+In addition, we need ${\color{red} c_5 + sc_6 = 0}$ and ${\color{red} b_2c_3 - b_4c_1 + s(b_2c_4 - b_4c_2) = 0}$ so that $\dim \ker (X-s) = 3$.
+\end{enumerate}
+The minimal polynomial $X^3(X-s)^2$ gives the additional equations ${\color{red} a_3c_3 = 0}$ and ${\color{red} c_1 + a_3c_4 + b_2c_6 = 0}$ so our coordinate ring after taking $s \rightarrow 0$ is
+$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3,c_4,c_5,c_6]}{\langle a_1,a_2,b_1,b_3,c_5,a_3b_4,a_3c_3,b_2c_3-b_4c_1,c_1+a_3c_4+b_2c_6 \rangle}$$
+$$ \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3,c_4,c_6]}{\langle a_3,b_2c_3-b_4c_1,c_1+b_2c_6 \rangle \cap \langle b_4,c_3,c_1+a_3c_4+b_2c_6 \rangle}$$
+The corresponding tableau for each ideal is:
+\[\begin{array}{ccc}\vspace{1mm}
+    \langle a_3,b_2c_3-b_4c_1,c_1+b_2c_6 \rangle &\leadsto \young(11113,2224,34) &\leadsto S_3 \oplus P_2 \\ 
+    \langle b_4,c_3,c_1+a_3c_4+b_2c_6 \rangle &\leadsto \young(11112,2234,34) &\leadsto 2 \leftarrow 3 \oplus P_1
+\end{array}
+\]
+
+\section{Example 15: $1 \rightarrow 2 \leftarrow 3 * 1 \leftarrow 2 \rightarrow 3 = S_1 \oplus S_3 \oplus P_2 + P_1 \oplus P_3$}
+Take 
+\[\begin{aligned}
+    \lambda_1 &= (3,2,1,0) & \mu_1 &= (2,2,1,1) \\
+    \lambda_2 &= (2,1,1,0) & \mu_2 &= (1,1,1,1) \\
+    \lambda &= (5,3,2,0) & \mu &= (3,3,2,2)
+\end{aligned}
+\]
+and the tableaux are
+\[
+\young(112,24,3) \text{ and } \young(13,2,4).
+\]
+The matrix in consideration is:
+\[
+X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
+    0 & 1 & & & & & & & & \\
+     & 0 & 1 & & & & & & & \\
+     & & s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 & c_2 \\
+     & & & 0 & 1 & & & & & \\
+     & & & & 0 & 1 & & & & \\
+     & & & & & s & b_3 & b_4 & c_3 & c_4 \\
+     & & & & & & 0 & 1 & & \\
+     & & & & & & & s & c_5 & c_6 \\
+     & & & & & & & & 0 & 1 \\
+     & & & & & & & & & s
+\end{BMAT}
+\right]
+\]
+\begin{enumerate}[label=\boxed{\arabic*}:]
+    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 +s^2e_3 \in \ker (X-s)$.
+    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$.
+We require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 + sa_3 = 0}$ for $e_4 + se_5 + s^2e_6 \in \ker (X-s)$.
+    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_7 \in \ker X$.
+    \item There is 1 restriction from $X$ and 2 restrictions from $X-s$.
+We need ${\color{red} b_4c_5 - sc_3 = 0}$ for $\ker X \subset \col X$.
+In addition, we need ${\color{red} c_5 + sc_6 = 0}$ and ${\color{red} b_2c_3 - b_4c_1 + s(b_2c_4 - b_4c_2) = 0}$ so that $\dim \ker (X-s) = 3$.
+\end{enumerate}
+The minimal polynomial $X^3(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
+$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3,c_4,c_5,c_6]}{\langle a_1,a_2,b_1,b_3,c_5,c_3+b_4c_6,b_2c_3-b_4c_1 \rangle}$$
+$$ \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3,c_4,c_6]}{\langle b_4,c_3 \rangle \cap \langle b_2c_6-c_1,c_3+b_4c_6 \rangle}$$
+The corresponding tableau for each ideal is:
+\[\begin{array}{ccc}\vspace{1mm}
+    \langle b_4,c_3 \rangle &\leadsto \young(11124,223,34) &\leadsto P_1 \oplus P_3 \\
+    \langle b_2c_6-c_1,c_3+b_4c_6 \rangle &\leadsto \young(11123,224,34) &\leadsto S_1 \oplus S_3 \oplus P_2
+\end{array}
+\]
 \end{document}

### 2021-02-14 draft.tex
just stylin
added tablaux equations to examples
long butt todo list
stashing conflicting local changes
moved some stuff around and added to todo
some abstracts some notes following sat mtg some other

@@
 \title{How to compute the fusion product of MV cycles in type A}
-% & , Joel Kamnitzer?
-\author{Roger Bai, Anne Dranowski} 
+\author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
 \date{October 2020}
@@
         L\otimes_{\CC[t]} \CC\xt &\in \Gr^{\lambda_1} \text{ and } \\ 
-        L \otimes_{\C[t]} \CC\xt[t-a] = L_0 \text{ for all $ a \ne 0, s$} \}\,.
+        L \otimes_{\CC[t]} \CC\xt[t-a] = L_0 \text{ for all $ a \ne 0, s$} \}\,.
     \end{split}
@@
 \section{Exposition}
+
+In Anderson and Kogan conjectured in \cite{anderson2005algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
+and they conjecture a formula for many of them.
+
+It's not clear how this work helps/relates to AK/their conjectures.
+
+The generalized MVy is interesting in its own right.
+
+Computing fusion still hard but at least boiled down to linear algebra. Cf.\ fusion product as it appears in BD, FL, MV, AK, BFM.
+
+\begin{quotation}
+However, we make crucial use of an idea of Drinfeld, going back to around 1990.
+He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
+\end{quotation}
+
+Exchange relations only work on cluster modules where one is a mutation of the other (i.e.\ those corresponding to cluster monomials which are related by mutation).
+Of course this gives me everything.
+Up to $A_4$ as in type $A_5$ there exist indecomposable modules which are not cluster, so exchange relations do not apply.
+The hope (conjecture) is that this paper gives a way to compute on such modules.
+Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is (possibly) cluster, and suggesting that $c_Y = b_Z + 2b$.
 
@@
      & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
-     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
      & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
@@
 
+\begin{conjecture}
+    Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
+\end{conjecture}
+
+\bibliographystyle{alpha}
+\bibliography{mvybd}
+
 \end{document}

### 2021-02-14 examples.tex
typo ish
Updates from Overleaf
fixed comment example environment intersection error
long butt todo list
some abstracts some notes following sat mtg some other

@@
 \]
-Remains to check this and make sense of the middle term.
+This is checked below.
 
@@
 \end{question}
+\end{example}
 
@@
 \end{comment}
-\end{example}
 
@@
         \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
-        \lambda_2 &= (2,2,1,0) & \mu_2 &= (3,2,1,1)
+        \lambda_2 &= (2,2,1,0) & \mu_2 &= (2,1,1,1)
     \end{aligned}
@@
 \end{example}
+\begin{example}
+% weight a_1 + a_2 + a_3 = 1 0 0 -1
+% can translate 
+% 1->2<-3 * 1<-2->3 = S_1 \oplus P_2 \oplus S_3 + P_1 \oplus P_3
+% 100,01,0 * 010,00,1 = 110,01,1 will correspond to S_1 \oplus P_2 \oplus S_3 module?
+% 
+% M_1 * M_2 = \sum M_\alpha 
+% Pol(M_1) + Pol(M_2) = \cup Pol(M_\alpha) and all \alpha's are needed.. in all the A_3 exchange relations, not in this example
+
+Try the following tableaux:
+\[
+1\to 2 \leftarrow 3 = \young(2,4) \qquad 1\leftarrow 2 \to 3 = \young(13,2,4)
+\]
+which won't work because $\mu_1 + \mu_2$ is not dominant. Can try anyway to see what fails.
+
+Next best guess:
+\[
+1\to 2\leftarrow 3 = \young(12,24,3) 
+\]
+
+Question: can we do better? 
+\end{example}
+
+\section{\today}
+
+\begin{example}
+    Let $G = \SL_3(\CC)$ with the standard choices of $B$, $T$, and $N$. Then $\CC[N] = \CC[x,y,z]$ where 
+    \begin{equation}
+        \begin{bmatrix}
+            1 & x & z \\
+              & 1 & y \\
+              &   & 1 
+        \end{bmatrix}
+    \end{equation}
+    and the unique biperfect basis (also cluster basis in that it's generated by cluster monomials) is 
+    \begin{equation}
+        \{x^a z^b (xy-z)^c \}\cup \{y^a z^b (xy-z)^c \}
+    \end{equation}
+    where $a,b,c$ are non-negative integers.
+\end{example}
+
 \end{document}

### 2021-02-15 draft.tex
added to denouement

@@
 Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is (possibly) cluster, and suggesting that $c_Y = b_Z + 2b$.
+Can still consider $ext(M_Z)$.
+Say $b_Z^2 = b_{Z_1} + b_{Z_2}$.
+
+$x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
+
+Representation theory?
 
@@
 
-    For the reverse containment, we choose $ [g] \in G\overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}$.
+    For the reverse containment, we choose $ [g] \in \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}$.
 By the lemma below, $[g] \in \cW_\mu$ and thus it lies in the image of our map and we are done.
@@
 \begin{proposition}
-    Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
+    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
+    Let $Z_{i} = Z_{\tau_i}$  be an MV cycle of type $\lambda_i\in P_+$ and weight $\mu_i\in P$ ($i = 1,2$). Then 
     \begin{equation}
-        Z_\tau\ast Z_\sigma 
+        % Z_\tau\ast Z_\sigma 
+        m_{\lambda_1\lambda_2} ([Z_1]\otimes[Z_2]) = \sum_{Z\in\cZ(\lambda)_\mu} i\left(
+            Z,\pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
+        \right) [Z]
     \end{equation}
-    is found by??? 
+    is found by\dots 
+    In particular, the multiplicity of $Z_\tau$ in the product of the zero fiber 
+    % (divisor class) 
+    and the 
+    % (Zariski) 
+    closure of the family $Z_1 \times Z_2 \times U$ is equal to the multiplicity of $X_\tau$ among 
+    \begin{equation}\label{eq:tabmult}
+        \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu_1,\mu_2}^{+,s}
+    \end{equation}
+    and since stable MV cycles can be represented by ordinary ones the multiplicities in 
+    $$
+    b_{Z_1}b_{Z_2} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
+        Z, \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
+    \right) b_Z 
+    $$
+    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda_i$ and $\mu_i$ ($i = 1,2$).
 \end{proposition}
+\acom{or Corollary?}
 
 \begin{conjecture}
-    Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
+    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
+    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau_1$ and $\tau_2$. 
+    % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
+    Then 
+    \begin{equation}
+        i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}) = 1 \,. 
+    \end{equation}
 \end{conjecture}

### 2021-02-16 draft.tex
updated bib

@@
 
-In Anderson and Kogan conjectured in \cite{anderson2005algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
+In Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
 and they conjecture a formula for many of them.
@@
 
-$x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
+% No; $x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
 

### 2021-02-16 draft.tex
some notation and intro

@@
 
+\section{Introduction}
+% 
+The Mirkovic--Vybornov isomorphism \cite{mirkovic2007quiver} relates slices in the affine Grassmannian to slices in conjugacy classes of nilpotent matrices and Nakajima quiver varieties.
+As an application it provides a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities.
+%
+
+The Beilinson--Drinfeld Grassmannian, essential to \cite{mirkovic2007geometric}, is a space which is used to define a fusion (aka convolution) product on sheaves (representations) and MV cycles (bases).
+% 
+This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2020bases}).
+% conjectured by JEA and proved by BKK
+%
+
+The purpose of this paper is to give an elementary way to compute this product in type $A$.
+We do not know how fruitful this work might be in the large landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is as yet computationally expensive.
+
 \section{Players}
 
-$G = \GL_m$.
+Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
+% are there other possibilities?? :S 
+Write $P$ for the character lattice of $T$.
+Identify $P\cong \ZZ^m$ so that the set of dominant weights $P_+$ is described/given by the set of partitions having at most $m$ nonzero parts.
+Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
+We will also need the notation $\cO_x$ for the completion of the local ring $\CC[t]$ at $x\in\spec\CC[t]$ and $\cK_x$ for its fraction field $\CC\xT[t-x]$.
+% 
+Note that (by choosing the local coordinate $t-x$ on $\spec\CC[t]$) we can identify $\cO_x \cong \cO$ and $\cK_x\cong\cK$.
+
+% Set $\AA = \AA^1_x$ (the subscript denoting the chosen local coordinate) and fix $s\in \AA - \{0\}$.
 
 \begin{itemize}
-    \item The ordinary affine Grassmannian $\Gr$
-    \item The Beilinson--Drinfeld Grassmannian $\Grbd\to C$
+    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$ % switched out ordinary Gr notation for curly Gr 
+    \item The Beauville--Laszlo Grassmannian $\Grbd[x] = G(\cK_x)/G(\cO_x)$ % TODO: in terms of bundles it is $\{(P,\sigma) : P is a PGB over A and \sigma is a trivialization of P on A - x\}$
+    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0) % switched out general curve $C$ for affine line $\AA$; TODO: in terms of bundles it is $\{(P,\sigma,x):agaiin P is a PGB on A, x \in A, and now \sigma is a trivialization away from 0 _and_ x \}
     \item Partitions $\mu_i\le\lambda_i$ of $N_i$ ($i=1,2$) and $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of $N = \sum N_i$

### 2021-02-16 draft.tex
more minor edits

@@
 % 
+\begin{quotation}
+    However, we make crucial use of an idea of Drinfeld, going back to around 1990.
+He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
+\end{quotation}
 
@@
 Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_x$ for the completion of the local ring $\CC[t]$ at $x\in\spec\CC[t]$ and $\cK_x$ for its fraction field $\CC\xT[t-x]$.
+We will also need the notation $\cO_s$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC[t]$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$.
 % 
-Note that (by choosing the local coordinate $t-x$ on $\spec\CC[t]$) we can identify $\cO_x \cong \cO$ and $\cK_x\cong\cK$.
+Note that (by choosing the local coordinate $t-s$ on $\spec\CC[t]$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.
 
@@
     \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$ % switched out ordinary Gr notation for curly Gr 
-    \item The Beauville--Laszlo Grassmannian $\Grbd[x] = G(\cK_x)/G(\cO_x)$ % TODO: in terms of bundles it is $\{(P,\sigma) : P is a PGB over A and \sigma is a trivialization of P on A - x\}$
-    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0) % switched out general curve $C$ for affine line $\AA$; TODO: in terms of bundles it is $\{(P,\sigma,x):agaiin P is a PGB on A, x \in A, and now \sigma is a trivialization away from 0 _and_ x \}
-    \item Partitions $\mu_i\le\lambda_i$ of $N_i$ ($i=1,2$) and $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of $N = \sum N_i$
-    \item The slices $\Gr_\mu$ and $\cW_{\mu_1,\mu_2}$ to the orbits $\Gr^\lambda$ and $(\Grbd[2])^{\lambda_1,\lambda_2}$
-    \item The nilpotent and semi-nilpotent cones $\cN$ and $\cN_s$ (of matrices with eigenvalues 0 and 0 or $s\ne 0$)
-    \item The slices $\TT_\mu$ and $\TT_{\mu_1,\mu_2}$ to the orbits $\OO_\lambda$ and $\OO_{\lambda_1,\lambda_2}$ 
+    \item The Beauville--Laszlo Grassmannian $\Grbd[s] = G(\cK_s)/G(\cO_s)$ % TODO: in terms of bundles it is $\{(P,\sigma) : P is a PGB over A and \sigma is a trivialization of P on A - x\}$
+    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0; and the second point $s$ varying away from $s = 0$) % switched out general curve $C$ for affine line $\AA$; TODO: in terms of bundles it is $\{(P,\sigma,x):agaiin P is a PGB on A, x \in A, and now \sigma is a trivialization away from 0 _and_ x \}
+    \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
+    \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
+    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ \acom{and its closure?}
+    \item The orbit $\Gr_\AA^{\lambda_1,\lambda_2}\to\AA$ whose generic fibre is $\Gr^{\lambda_1} \times \Gr^{\lambda_2}$ and whose zero fibre is $\Gr^{\lambda}$ \acom{and closures?}
+    \item The slice $\Gr_\mu = G_1[t^{-1}]L_\mu$ to the orbit $\Gr^\lambda$
+    \item The slice $\cW_\mu = G_1\xT[t^{-1}] L_\mu$ to the orbit $\Gr_\AA^{\lambda_1,\lambda_2}$ \acom{is not presented as a family; why need define it in thick Gr?}% $(\Grbd[2])^{\lambda_1,\lambda_2}$; replaced \cW_{\mu_1,\mu_2} = by Joel's not'n & def, seemingly independent of the decomposition of \mu; modified Joel's double bracket --- still confused over where W_\mu ought to live
+    \item The nilpotent and semi-nilpotent cones $\cN$ and $\cN_\AA$ (of matrices with eigenvalues in $\{0\}$ and $\{0,s\} \in \AA\times\AA$ resp.) 
+    \item The slice $\TT_\mu$ to the orbits $\OO_\lambda$ 
+    \item The family of slices $\TT_{\mu_1,\mu_2}^{\AA}$ to the family of orbits $\OO^{\AA}_{\lambda_1,\lambda_2}$ 
 \end{itemize}
 
-New (?) definitions among these are as follows.
+% New (?) definitions among these are as follows.
 % 
-
 %The [family of] slices [with $s$-fibre?]
@@
 
-We define
-$$L_\mu = t^\mu, L_{\mu_1, \mu_2} = t^{\mu_1} (t-s)^{\mu_2} \in G((t^{-1}))/G[t]$$
+Recall (from \cite{kamnitzer2014yangians}) that there is an embedding of the usual ``thin'' affine Grassmannian $\Gr $ as we have defined it into the ``thick'' affine Grassmannian.
+\acom{In \cite{kamnitzer2014yangians} the thick Gr is said to be necessary for the noncommutative algebras considered.
+What is our reason for preferring it to the thin Gr?
+Can we replace thick by thin?}
+\[
+\Gr \cong G[t,t^{-1}]/G[t]\hookrightarrow G\xT[t^{-1}]/G[t]\,.
+\]
+Let $L_\mu = t^\mu G(\cO)$ and $L_{\mu_1, \mu_2} = t^{\mu_1} (t-s)^{\mu_2} G(\cO)$. \acom{or $ t^{\mu_1} (t-s)^{\mu_2} G[t]$ in thick?} % \in G((t^{-1}))/G[t]
 
-\begin{equation}
-    \cW_\mu = G_1[[t^{-1}]]L_\mu \subset G((t^{-1}))/G[t]
-\end{equation}
-a subscheme of the thick affine Grassmannian
+% \begin{equation}
+%     \cW_\mu = G_1[[t^{-1}]]L_\mu \subset G((t^{-1}))/G[t]
+% \end{equation}
+% a subscheme of the thick affine Grassmannian
 
-Note that $ L_{\mu_1, \mu_2} = (t-s)^{\mu_2} t^{-\mu_2} L_{\mu} \in \cW_\mu$
-and that  $L_{\mu_1,\mu_2}\in\Grbd[2]$ is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$; i.e.\
+Note that $ L_{\mu_1, \mu_2} = (t-s)^{\mu_2} t^{-\mu_2} L_{\mu} \in \cW_\mu$ \acom{thick or thin}
+and that  $L_{\mu_1,\mu_2}\in\Grbd$ \acom{should say $\Grbd[s]$ as it's really a lattice in a given fibre being characterized?} is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ \acom{thick only} i.e.\
 \begin{equation}
     \label{eq:defWBD}
-    \begin{split}
+    % \begin{split}
         %L_{\mu_1,\mu_2}\otimes \CC[(t-s)^{-1}] =
-        L_{\mu_1,\mu_2}\otimes \CC\xt &= L_{\mu_2} \otimes \CC\xt \text{ and } \\
-        %L_{\mu_1,\mu_2}\otimes\CC[t^{-1}] =
-        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] &= L_{\mu_1} \otimes \CC\xt[t-s]
-    \end{split}
+        L_{\mu_1,\mu_2}\otimes \CC\xt = L_{\mu_2} \otimes \CC\xt \qquad
+        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] = L_{\mu_1} \otimes \CC\xt[t-s]
+    % \end{split}
 \end{equation}
-where $L_{\mu_i}$ denotes the point $t^{\mu_i}G(\cO)\in\Gr$. 
+where 
+% $L_{\mu_i}$ denotes the point $t^{\mu_i}G(\cO)\in\Gr$ and 
+the tensor product is taken over $\CC[t]$. 
 %
@@
 \begin{equation}
-    S_{\mu_1,\mu_2} = N_-(\CC((t^{-1}))) L_{\mu_1,\mu_2}\,. 
+    S_{\mu_1,\mu_2} = N_-(\CC\xT[t^{-1}]) L_{\mu_1,\mu_2}\,. 
 \end{equation}
+\acom{1.
+Introduce $N_\pm$.
+2.
+In \cite{kamnitzer2014yangians} the global version of $S^\mu_-$ is the subvariety $S^\mu_{-,\AA}\subset\Grbd$ whose generic fibre is $\bigcup_{\mu_1 + \mu_2 = \mu} S^{\mu_1}_-\times S^{\mu_2}_-$ and whose zero fibre is $S^\mu_-$ which don't look to be the same thing.}
 
-The orbit of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as follows
+The family \acom{orbit?
+orbits?
+family of orbits?} of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as described more explicitly as follows
 \begin{equation}
@@
     \begin{split}
-        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : 
+        % (\Grbd[2])^{\lambda_1,\lambda_2} = 
+        \Gr_{\AA}^{\lambda_1,\lambda_2} = 
+        \{L \in\Grbd : 
         %L\otimes\CC[t^{-1}] 
@@
         L\otimes_{\CC[t]} \CC\xt &\in \Gr^{\lambda_1} \text{ and } \\ 
-        L \otimes_{\CC[t]} \CC\xt[t-a] = L_0 \text{ for all $ a \ne 0, s$} \}\,.
+        L \otimes_{\CC[t]} \CC\xt[t-a] &= L_0 \text{ for all $ a \ne 0, s$} \}\,.
     \end{split}
@@
 
-\jcom{It is important to add the condition that the lattices are trivial at $ a $.}
+\jcom{It is important to add the condition that the lattices are trivial at $ a $.} \acom{$a\ne 0,s$}
 % 
-\acom{These defining conditions are again just telling us that in the fibre over the fixed point $(0,s)\in C^{(2)}$ this set is pairs of lattices; note that we invert the indeterminates $t$ and $(t-s)$ \textit{after} specializing $(0,s)$.
+% \acom{These defining conditions are again just telling us that in the fibre over the fixed point $(0,s)\in C^{(2)}$ this set is pairs of lattices; note that we invert the indeterminates $t$ and $(t-s)$ \textit{after} specializing $(0,s)$.
 Could we give a more explicit characterization like $t^{N_1}(t-s)^{N_2} L_0 \subseteq L\subseteq t^{-N_1}(t-s)^{-N_2}$?}
@@
 In Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
-and they conjecture a formula for many of them.
+% and they conjectured a formula for many of them.
 
-It's not clear how this work helps/relates to AK/their conjectures.
+It's not clear how this work helps with/relates to AK/their conjectures.
 
-The generalized MVy is interesting in its own right.
+The generalized MVy is interesting in its own right. \acom{is it?}
 
@@
 
-\begin{quotation}
-However, we make crucial use of an idea of Drinfeld, going back to around 1990.
-He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
-\end{quotation}
+Interesting combinatorics? Witnessing a product on SSYT.
 
@@
     \begin{equation}
-        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2} \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap \cW_{\mu_1,\mu_2}
+        \overline{\OO}_{\lambda_1,\lambda_2}\cap\TT_{\mu_1,\mu_2} \to \overline\Gr_\AA^{\lambda_1,\lambda_2}\cap \cW_{\mu_1,\mu_2}
     \end{equation}

### 2021-02-17 draft.tex
changes by Joel

@@
 Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_s$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC[t]$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$.
+We will also need the notation $\cO_s$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$.
 % 
@@
 
+\subsection{Lattices}
+We will use the lattice model, so it is useful to recall the following definition.
+Let $ R \subset K$ be two rings (usually, but not always, $K $ will be a field).
+Let $ n \in \mathbb N$ and consider $ K^n $ as a $K$-module.
+By restriction $ K^n$ can be viewed as an $R$-module.
+An $R$-lattice in $ M$ is an $R$-submodule $ L \subset K^n$ such that $ L $ is a free rank $ n $ $R$-module and $ L \otimes_R K = K^n $.
+Equivalently $ L = span_R(v_1, \dots, v_n)$ where $ v_1, \dots, v_n$ are free generators of $K^n$.
+
+The trivial lattice is $L_0 = R^n \subset K^n $.
+The group $GL_n(K) $ as simply transitively on the set of $ R$-lattices in $K^n$ and we obtain a bijection between the set of such lattices and $ GL_n(K)/GL_n(R)$.
+
+We will be particularly interested in $\CC[t]$-lattices in $ \CC[t,t^{-1}]^n$.  Given such a lattice $ L $ and a point $ a \in \C$, the specialization of $ L $ at $ a $ is defined as
+$$
+L(a) := L \otimes_{\CC[t]} \CC[[t-a]] \subset \CC((t-a))
+$$
+In particular we say that $ L $ is trivial at $ a $ if $ L(a) = \CC[[t-a]]^n.$
+
+\jcom{I wasn't sure of the notation to use here, but I wanted something which didn't conflict with $ L_0$.}
+
+\subsection{Affine Grassmannian actors}
+
 \begin{itemize}
-    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$ % switched out ordinary Gr notation for curly Gr 
-    \item The Beauville--Laszlo Grassmannian $\Grbd[s] = G(\cK_s)/G(\cO_s)$ % TODO: in terms of bundles it is $\{(P,\sigma) : P is a PGB over A and \sigma is a trivialization of P on A - x\}$
-    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0; and the second point $s$ varying away from $s = 0$) % switched out general curve $C$ for affine line $\AA$; TODO: in terms of bundles it is $\{(P,\sigma,x):agaiin P is a PGB on A, x \in A, and now \sigma is a trivialization away from 0 _and_ x \}
+    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by
+    $$\Gr = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{0\} $} \} $$
+    We also have a lattice description 
+    $$ \Gr = \{ L \subset \CC^n \otimes \cK : \text{ $L$ is a $\cO$-lattice} \}
+$$
+    \item For any $ s \in \CC $ , the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
+    $$\Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{s\} $} \} $$
+    We also have a lattice description 
+    $$ \Gr_s = \{ L \subset \CC^n \otimes \cK_s : \text{ $L$ is a $\cO_s$-lattice} \}
+$$   
+    \item The thick affine Grassmannian $\Gr^{th} = G(\CC((t^{-1})))/G(\CC[t])$. It is described in modular terms by
+    $$\Gr = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ (a disk centered at $ \infty$)} \} $$
+    We also have a lattice description 
+    $$ \Gr^{th} = \{ L \subset \C^n \otimes \CC((t^{-1})) : \text{ $L$ is a $\CC[t]$-lattice} \}
+$$   
+\jcom{Maybe write $\cK_\infty$ for $ \CC((t^{-1})) $?  Also maybe change the ``thick'' notation''.}
+
+    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0; and the second point $s$ varying away from $s = 0$)
+     It is described in modular terms by
+    $$\Grbd = \{ (P, s, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{0, s\} $} \} $$
+    We also have a lattice description 
+    $$ \Grbd = \{ L \subset \CC^n \otimes \CC[t,t^{-1}], s \in \CC : \text{ $L$ is a $\CC[t]$-lattice, $L$ is trivial for any $ a \ne 0, s$} \}
+    $$
+
+\end{itemize}
+
+\begin{itemize}
     \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 

### 2021-02-17 draft.tex
some typo fixes up to section 3

--- 2021-02-16 draft.tex
@@
+%!TEX program = lualatex
+
 \documentclass{article}
 \usepackage{basic}
+\usepackage{emoji}
+% \setemojifont{Apple Color Emoji}
 % Working title: 
@@
 % 
-The Mirkovic--Vybornov isomorphism \cite{mirkovic2007quiver} relates slices in the affine Grassmannian to slices in conjugacy classes of nilpotent matrices and Nakajima quiver varieties.
-As an application it provides a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities.
+The Mirkovic--Vybornov isomorphism (\cite{mirkovic2007quiver,mirkovic2019comparison}) relates slices in the affine Grassmannian to slices in conjugacy classes of nilpotent matrices and Nakajima quiver varieties.
+In so doing it provides a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities.
 %
 
-The Beilinson--Drinfeld Grassmannian, essential to \cite{mirkovic2007geometric}, is a space which is used to define a fusion (aka convolution) product on sheaves (representations) and MV cycles (bases).
+[Liaison]
+
+The Beilinson--Drinfeld Grassmannian, essential to \cite{mirkovic2007geometric}, is a space which is used to define a fusion (aka convolution) product on sheaves (representations) as well as MV cycles (bases).
 % 
-This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2020bases}).
+This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019mirkovic}).
 % conjectured by JEA and proved by BKK
 % 
+To quote from Mirkovic and Vilonen:
 \begin{quotation}
@@
 \end{quotation}
+% 
+[Liaison]
 
 The purpose of this paper is to give an elementary way to compute this product in type $A$.
-We do not know how fruitful this work might be in the large landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is as yet computationally expensive.
+We do not know how fruitful this work might be in the larger landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is as yet computationally expensive.
+% 
+Moreover, it is not clear why one should care about the fusion product on bases. \emoji{smile} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull}
 
@@
 Write $P$ for the character lattice of $T$.
-Identify $P\cong \ZZ^m$ so that the set of dominant weights $P_+$ is described/given by the set of partitions having at most $m$ nonzero parts.
+Identify $P\cong \ZZ^m$ so that the set of dominant weights $P_+$ is given by the set of partitions having at most $m$ nonzero parts.
 Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_s$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC[t]$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$.
+We will also need the notation $\cO_s$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$.
+% TODO: given by or described by?
 % 
-Note that (by choosing the local coordinate $t-s$ on $\spec\CC[t]$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.
+Note that (by changing the local coordinate on $\spec\CC[t]$ to $t-s$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.
 
@@
 
+\subsection{Lattices}
+\label{ss:lat}
+We will use the lattice model, so it is useful to recall the following definition.
+Let $ R \subset K$ be two rings (usually, but not always, $K $ will be a field).
+Let $ n \in \mathbb N$ and consider $ K^n $ as a $K$-module.
+By restriction $ K^n$ can be viewed as an $R$-module.
+An $R$-lattice in $ M$ is an $R$-submodule $ L \subset K^n$ such that $ L $ is a free rank $ n $ $R$-module and $ L \otimes_R K = K^n $.
+Equivalently $ L = \Sp_R(v_1, \dots, v_n)$ where $ v_1, \dots, v_n$ are free generators of $K^n$.
+
+The trivial lattice is $L_0 = R^n \subset K^n $.
+The group $\GL_n(K) $ acts simply transitively on the set of $ R$-lattices in $K^n$ and we obtain a bijection between the set of such lattices and $\GL_n(K)/\GL_n(R)$.
+
+We will be particularly interested in $\CC[t]$-lattices in $ \CC[t,t^{-1}]^n$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
+$$
+L(a) := L \otimes_{\CC[t]} \CC[[t-a]] \subset \CC((t-a))\,.
+$$
+In particular we say that $ L $ is trivial at $ a $ if $ L(a) = \CC[[t-a]]^n.$
+
+\jcom{I wasn't sure of the notation to use here, but I wanted something which didn't conflict with $ L_0$.}
+
+\acom{I think that MVy use this notation also:
+
+\includegraphics[width=\textwidth]{img/Capture d’écran, le 2021-02-17 à 13.03.10.png}}
+
+\subsection{Affine Grassmannians} %  actors
+
+Set $\AA = \AA^1$ and $\PP = \PP^1$.
+
 \begin{itemize}
-    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$ % switched out ordinary Gr notation for curly Gr 
-    \item The Beauville--Laszlo Grassmannian $\Grbd[s] = G(\cK_s)/G(\cO_s)$ % TODO: in terms of bundles it is $\{(P,\sigma) : P is a PGB over A and \sigma is a trivialization of P on A - x\}$
-    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0; and the second point $s$ varying away from $s = 0$) % switched out general curve $C$ for affine line $\AA$; TODO: in terms of bundles it is $\{(P,\sigma,x):agaiin P is a PGB on A, x \in A, and now \sigma is a trivialization away from 0 _and_ x \}
-    \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
-    \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
+    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by \acom{Where $V_0$ is the trivial rank $n$ vector bundle on $\PP$?}
+    $$
+    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{0\} $} \} 
+    $$
+    We also have a lattice description 
+    $$ 
+    \Gr = \{ L \subset \CC^n \otimes_\cO \cK : \text{ $L$ is a $\cO$-lattice} \}
+    $$
+    % 
+    \item For any $ s \in \CC $, the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
+    $$
+    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{s\} $} \} 
+    $$
+    We also have a lattice description 
+    $$ \Gr_s = \{ L \subset \CC^n \otimes_{\cO_s} \cK_s : \text{ $L$ is a $\cO_s$-lattice} \}
+$$   
+    \item The thick affine Grassmannian $\Gr^{\sf th} = G(\CC\xT[t^{-1}])/G(\CC[t])$. It is described in modular terms by
+    $$
+        \Gr^{\sf th} = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
+    $$
+    where $D_\infty$ denotes a disk centered at $ \infty$.
+    We also have a lattice description 
+$$ 
+\Gr^{\sf th} = \{ L \subset \CC^n \otimes_{\CC[t]} \CC((t^{-1})) : \text{ $L$ is a $\CC[t]$-lattice} \}
+$$   
+\jcom{Maybe write $\cK_\infty$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.}
+
+    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s$ varying away from $s = 0$).
+    It is described in modular terms by
+    {\small
+    $$
+    \Grbd = 
+    % \begin{aligned}
+        \left\{ 
+            (P,\varphi,s) : V\text{ is a rank $n$ vector bundle on }\PP, \varphi : V \rightarrow V_0 \text{ on } \PP \setminus \{0, s\}  
+        \right\} 
+    % \end{aligned}
+    $$}
+    We also have a lattice description 
+    {\small
+    $$ 
+    \Grbd = 
+    \{ L \subset \CC^n \otimes_{\CC[t]} \CC[t,t^{-1}], s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
+    % , $L$ is 
+    trivial at any $ a \ne 0, s$} \}
+    $$}
+    % 
+\end{itemize}
+
+Now fix $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) in $P$ and their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$. 
+% 
+\begin{itemize}
+    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
+    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
+    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$ and the point ?? $t^\lambda G(\CC[t])$ in $\Gr^{\sf th}$ \acom{abandon lattice of coweight notation?}
     \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ \acom{and its closure?}
-    \item The orbit $\Gr_\AA^{\lambda_1,\lambda_2}\to\AA$ whose generic fibre is $\Gr^{\lambda_1} \times \Gr^{\lambda_2}$ and whose zero fibre is $\Gr^{\lambda}$ \acom{and closures?}
+    \item The family $\Gr_\AA^{\lambda_1,\lambda_2}\to\AA$ whose generic fibre is $\Gr^{\lambda_1} \times \Gr^{\lambda_2}$ and whose zero fibre is $\Gr^{\lambda}$ \acom{1.
+and closures?
+2.
+can probably be described as an orbit of some group scheme}
     \item The slice $\Gr_\mu = G_1[t^{-1}]L_\mu$ to the orbit $\Gr^\lambda$
-    \item The slice $\cW_\mu = G_1\xT[t^{-1}] L_\mu$ to the orbit $\Gr_\AA^{\lambda_1,\lambda_2}$ \acom{is not presented as a family; why need define it in thick Gr?}% $(\Grbd[2])^{\lambda_1,\lambda_2}$; replaced \cW_{\mu_1,\mu_2} = by Joel's not'n & def, seemingly independent of the decomposition of \mu; modified Joel's double bracket --- still confused over where W_\mu ought to live
+    \item The ``slice'' $\cW_\mu = G_1\xT[t^{-1}] t^\mu G(\CC[t])$ to the ``orbit'' $\Gr_\AA^{\lambda_1,\lambda_2}$ \acom{is not presented as a family}% $(\Grbd[2])^{\lambda_1,\lambda_2}$; replaced \cW_{\mu_1,\mu_2} = by Joel's not'n & def, seemingly independent of the decomposition of \mu; modified Joel's double bracket --- still confused over where W_\mu ought to live
+\end{itemize}
+The following notation leaves the realm of affine Grassmannians and probably deserves its own subsection. E.g.\ ``nilpotent cones?''
+\begin{itemize}
     \item The nilpotent and semi-nilpotent cones $\cN$ and $\cN_\AA$ (of matrices with eigenvalues in $\{0\}$ and $\{0,s\} \in \AA\times\AA$ resp.) 
-    \item The slice $\TT_\mu$ to the orbits $\OO_\lambda$ 
-    \item The family of slices $\TT_{\mu_1,\mu_2}^{\AA}$ to the family of orbits $\OO^{\AA}_{\lambda_1,\lambda_2}$ 
+    \item The slice $\TT_\mu$ to the orbit $\OO_\lambda$ 
+    \item The ``family of slices'' $\TT_{\mu_1,\mu_2}^{\AA}$ to the ``family of orbits'' $\OO^{\AA}_{\lambda_1,\lambda_2}$ \acom{ok to describe as such?}
 \end{itemize}
@@
 
-Recall (from \cite{kamnitzer2014yangians}) that there is an embedding of the usual ``thin'' affine Grassmannian $\Gr $ as we have defined it into the ``thick'' affine Grassmannian.
+Recall (citation?) that there is an embedding of the usual (``thin'') affine Grassmannian $\Gr $ as we have defined it into the ``thick'' affine Grassmannian. 
+%
+
 \acom{In \cite{kamnitzer2014yangians} the thick Gr is said to be necessary for the noncommutative algebras considered.
 What is our reason for preferring it to the thin Gr?
-Can we replace thick by thin?}
+Can we replace thick by thin?
+Joel said that rather it is needed/used because unlike the thin $\Gr$ which is an ind-scheme, the thick $\Gr^{\sf th}$ is a scheme, so taking Spec of global functions (on $\cW_\mu$?) will recover $\cW_\mu$?}
 \[
-\Gr \cong G[t,t^{-1}]/G[t]\hookrightarrow G\xT[t^{-1}]/G[t]\,.
+\Gr \cong G(\CC[t,t^{-1}])/G(\CC[t])\hookrightarrow \Gr^{\sf th} := G(\CC\xT[t^{-1}])/G(\CC[t]) \quad g\cO \mapsto gG(\CC[t])  \,.
 \]
-Let $L_\mu = t^\mu G(\cO)$ and $L_{\mu_1, \mu_2} = t^{\mu_1} (t-s)^{\mu_2} G(\cO)$. \acom{or $ t^{\mu_1} (t-s)^{\mu_2} G[t]$ in thick?} % \in G((t^{-1}))/G[t]
-
+Let 
+% $L_\mu = t^\mu G(\cO)$ and 
+$L_{\mu_1, \mu_2} = t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])$. 
+% \acom{or $ t^{\mu_1} (t-s)^{\mu_2} G[t]$ in thick?} % \in G((t^{-1}))/G[t]
+% 
 % \begin{equation}
@@
 % a subscheme of the thick affine Grassmannian
-
-Note that $ L_{\mu_1, \mu_2} = (t-s)^{\mu_2} t^{-\mu_2} L_{\mu} \in \cW_\mu$ \acom{thick or thin}
-and that  $L_{\mu_1,\mu_2}\in\Grbd$ \acom{should say $\Grbd[s]$ as it's really a lattice in a given fibre being characterized?} is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ \acom{thick only} i.e.\
+% 
+Note that $ L_{\mu_1, \mu_2} = (t-s)^{\mu_2} t^{-\mu_2} L_{\mu} \in \cW_\mu$ 
+% \acom{thick or thin}
+and that  $L_{\mu_1,\mu_2}\in\Grbd$ \acom{should say $\Grbd[s]$ as it's really a lattice in a given fibre being characterized?} is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$, i.e.\
+% \acom{thick only} 
 \begin{equation}
@@
 orbits?
-family of orbits?} of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as described more explicitly as follows
+family of orbits?} of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ (i.e.\ which are trivial at $a \ne 0$ or $s$, to use the terminology introduced in the \cref{ss:lat}) is described more explicitly as follows
 \begin{equation}
@@
 
-\jcom{It is important to add the condition that the lattices are trivial at $ a $.} \acom{$a\ne 0,s$}
+% \jcom{It is important to add the condition that the lattices are trivial at $ a $.} \acom{$a\ne 0,s$}
 % 
@@
 
+\begin{comment}
     The [family of] slice[s $\TT_{\mu_1,\mu_2}$ fibred over $C=\AA^1$ with $s$-fibre]
@@
 where $\n\subset\mat(N)$ is the unipotent subalgebra of uppertriangular matrices.
+\end{comment}
 
-\acom{or---as Joel pointed out, may be ok with:
-The slice $\TT_\mu$ as defined in MVy, no change, \text{and} the family of slices $$\TT_{\mu_1,\mu_2}^{+,s} = \TT_\mu \cap \n + C_{\mu_1,\mu_2}^s$$ where 
+\acom{
+    % or---as Joel pointed out, may be ok with:
+The slice $\TT_\mu$ as defined in \cite{mirkovic2007quiver}, no change, \text{and} the family of slices $$\TT_{\mu_1,\mu_2}^{+,s} = \TT_\mu \cap \n + C_{\mu_1,\mu_2}^s$$ where $C_{\mu_1,\mu_2}^s$ is the block diagonal matrix of companion matrices of
 % 
 \begin{equation}
-    C_s \text{ is the block diagonal matrix of companion matrices of } t^{\mu_{1,k}}(t-s)^{\mu_{2,k}}
+    % C_s \text{ is the block diagonal matrix of companion matrices of } 
+    t^{\mu_{1,k}}(t-s)^{\mu_{2,k}} \quad (1\le k\le m).
 \end{equation}
 % not sure about notation
-
+Watch out for mixing up of $m$ and $n$.
 }
 
-The [family of] orbit[s $\OO_{\lambda_1,\lambda_2}$ fibred over $C = \AA^1$ with $s$-fibre]  
+The [family of] orbit[s $\OO_{\lambda_1,\lambda_2}$ fibred over $C = \AA$ with $s$-fibre]  
 \begin{equation}
@@
 
-In Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
+Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
 % and they conjectured a formula for many of them.

### 2021-02-18 draft.tex
joel made more changes

@@
 \usepackage{emoji}
+
+\newcommand{\Grth}{\Gr^{\sf th}}
+
 % \setemojifont{Apple Color Emoji}
@@
 \begin{itemize}
-    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by \acom{Where $V_0$ is the trivial rank $n$ vector bundle on $\PP$?}
+    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
     $$
@@
     $$
+    where $V_0$ is the trivial rank $n$ vector bundle on $\PP$.
+
     We also have a lattice description 
@@
     $$
-        \Gr^{\sf th} = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
+        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
     $$
@@
 $$   
-\jcom{Maybe write $\cK_\infty$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.}
+\jcom{Maybe write $\cK_\infty$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''. I made a $\Grth$ macro, but I had no idea where to put it.}
 
@@
     $$}
+    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by
+    $$ \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1})/G(\CC[t])$$
+
     We also have a lattice description 
@@
 
-Now fix $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) in $P$ and their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$. 
+These different versions of the affine Grassmannian are related as follows.  First there is an isomorphism $ \Gr \cong \Gr_s $ coming from the isomorphism $ \Ks \cong \K$.
+
+Second, we have a map $$ \Grbd \rightarrow \Grth $$ which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
+$$
+G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\CC((t^{-1}))/G(\C[t])
+$$
+Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^n \rightarrow \CC((t^{-1}))^n$ on the ambient spaces.
+
+The fibres $ Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ are given as follows
+$$
+\Gr_{0,s} \cong \begin{cases} \Gr \times \Gr_s, \  s \ne 0 \\
+\Gr, \ s = 0.
+\end{cases}
+$$
+This isomorphism is given in the lattice realization as
+$$
+L \mapsto (L(0), L(s))
+$$
+in the $ s \ne 0 $ case.
+
+The following construction will be very important in this paper.
+Let $ X_1, X_2 \subset \Gr$ be two subschemes.
+Then using the isomorphism $ \Gr \cong \Gr_s $ for each $ s$, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.
+Via this isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
+We define $ X_1 * X_2 $ to be the scheme theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.
+We have the projection $ \pi: \Grbd \rightarrow \A $ and we form $ X_1 \cdot X_2 = X_1 * X_2 \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.
+We regard $ X_1 \cdot X_2$ as a subscheme of $ \Gr $ using the isomorphism $\Gr_{0,0} \cong \Gr $.
+
+\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper. I don't know what notation we should use.}
+
+Now fix dominant weights $ \lambda_i \in P_+$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2$ of size $ N = N_1 + N_2$.
+
 % 
@@
     % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
-    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$ and the point ?? $t^\lambda G(\CC[t])$ in $\Gr^{\sf th}$ \acom{abandon lattice of coweight notation?}
-    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ \acom{and its closure?}
-    \item The family $\Gr_\AA^{\lambda_1,\lambda_2}\to\AA$ whose generic fibre is $\Gr^{\lambda_1} \times \Gr^{\lambda_2}$ and whose zero fibre is $\Gr^{\lambda}$ \acom{1.
+    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$ 
+    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure $ \overline{\Gr}^\lambda = \cup_{\lambda' \le \lambda} \Gr^{\lambda'}$.
+    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \A$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.
+By construction the fibre of $ \overline{\Gr}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.
+By Zhu's theorem (\jcom{need ref}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
+\end{itemize}
+\begin{itemize}
+    %The family $\overline{\Gr}_\AA^{\lambda_1,\lambda_2}\to\AA$ whose generic fibre is $\overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$ and whose zero fibre is $\Gr^{\lambda}$ \acom{1.
 and closures?

### 2021-02-18 draft.tex
fixed some typos and added joels macros to style file

@@
 \usepackage{emoji}
-
-\newcommand{\Grth}{\Gr^{\sf th}}
 
@@
 
-These different versions of the affine Grassmannian are related as follows.  First there is an isomorphism $ \Gr \cong \Gr_s $ coming from the isomorphism $ \Ks \cong \K$.
+These different versions of the affine Grassmannian are related as follows.  First there is an isomorphism $ \Gr \cong \Gr_s $ coming from the isomorphism $ \Ks \cong \cK$.
 
@@
 $$
-G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\CC((t^{-1}))/G(\C[t])
+G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\CC((t^{-1}))/G(\CC[t])
 $$
@@
 We define $ X_1 * X_2 $ to be the scheme theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.
-We have the projection $ \pi: \Grbd \rightarrow \A $ and we form $ X_1 \cdot X_2 = X_1 * X_2 \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.
+We have the projection $ \pi: \Grbd \rightarrow \AA $ and we form $ X_1 \cdot X_2 = X_1 * X_2 \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.
 We regard $ X_1 \cdot X_2$ as a subscheme of $ \Gr $ using the isomorphism $\Gr_{0,0} \cong \Gr $.
@@
     \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure $ \overline{\Gr}^\lambda = \cup_{\lambda' \le \lambda} \Gr^{\lambda'}$.
-    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \A$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.
+    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.
 By construction the fibre of $ \overline{\Gr}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.

### 2021-02-18 draft.tex

@@
 
-Now fix dominant weights $ \lambda_i \in P_+$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2$ of size $ N = N_1 + N_2$.
+Now fix dominant weights $ \lambda_i, \mu_i \in P_+$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2 = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.
 
@@
 By Zhu's theorem (\jcom{need ref}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
-\end{itemize}
-\begin{itemize}
-    %The family $\overline{\Gr}_\AA^{\lambda_1,\lambda_2}\to\AA$ whose generic fibre is $\overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$ and whose zero fibre is $\Gr^{\lambda}$ \acom{1.
-and closures?
-2.
-can probably be described as an orbit of some group scheme}
+
     \item The slice $\Gr_\mu = G_1[t^{-1}]L_\mu$ to the orbit $\Gr^\lambda$

### 2021-02-18 draft.tex
joels changes

@@
 % are there other possibilities?? :S 
-Write $P$ for the character lattice of $T$.
-Identify $P\cong \ZZ^m$ so that the set of dominant weights $P_+$ is given by the set of partitions having at most $m$ nonzero parts.
+Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.
+The dominant weights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
+We also need the notion of effective dominant coweight, which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
+So an effective dominant coweight $ \lambda $ is a partition of $ \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
+
 Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_s$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$.
+We will also need the notation $\cO_s = \CC[[t-s]]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$.
 % TODO: given by or described by?
@@
 Note that (by changing the local coordinate on $\spec\CC[t]$ to $t-s$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.
+
+Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
 
@@
 Let $ R \subset K$ be two rings (usually, but not always, $K $ will be a field).
-Let $ n \in \mathbb N$ and consider $ K^n $ as a $K$-module.
-By restriction $ K^n$ can be viewed as an $R$-module.
-An $R$-lattice in $ M$ is an $R$-submodule $ L \subset K^n$ such that $ L $ is a free rank $ n $ $R$-module and $ L \otimes_R K = K^n $.
-Equivalently $ L = \Sp_R(v_1, \dots, v_n)$ where $ v_1, \dots, v_n$ are free generators of $K^n$.
+Let $ m \in \mathbb N$ and consider $ K^n $ as a $K$-module.
+By restriction $ K^m$ can be viewed as an $R$-module.
+An $R$-lattice in $ M$ is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.
+Equivalently $ L = \Sp_R(v_1, \dots, v_m)$ where $ v_1, \dots, v_n$ are free generators of $K^m$.
 
-The trivial lattice is $L_0 = R^n \subset K^n $.
-The group $\GL_n(K) $ acts simply transitively on the set of $ R$-lattices in $K^n$ and we obtain a bijection between the set of such lattices and $\GL_n(K)/\GL_n(R)$.
+The trivial lattice is $L_0 = R^m \subset K^m $.
+The group $\GL_m(K) $ acts transitively on the set of $ R$-lattices in $K^m$, thus giving a bijection between the set of such lattices and $\GL_m(K)/\GL_m(R)$.
 
-We will be particularly interested in $\CC[t]$-lattices in $ \CC[t,t^{-1}]^n$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
+We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
 $$
@@
 $$
-In particular we say that $ L $ is trivial at $ a $ if $ L(a) = \CC[[t-a]]^n.$
+We say that $ L $ is trivial at $ a $ if $ L(a) = \CC[[t-a]]^m.$
 
@@
 
-\acom{I think that MVy use this notation also:
+\acom{I think that MVy use this notation also: }
 
-\includegraphics[width=\textwidth]{img/Capture d’écran, le 2021-02-17 à 13.03.10.png}}
+%\includegraphics[width=\textwidth]{img/Capture d’écran, le 2021-02-17 à 13.03.10.png}}
 
@@
     $$
-    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{0\} $} \} 
+    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \rightarrow V_0 $ on $ D_0 \setminus \{0\} $} \} 
     $$
-    where $V_0$ is the trivial rank $n$ vector bundle on $\PP$.
+    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disk centered at $ 0 \in \PP$.
 
@@
     $$ 
-    \Gr = \{ L \subset \CC^n \otimes_\cO \cK : \text{ $L$ is a $\cO$-lattice} \}
+    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}
     $$
@@
     $$
-    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{s\} $} \} 
+    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \rightarrow V_0 $ on $ D_s \setminus \{s\} $} \} 
     $$
     We also have a lattice description 
-    $$ \Gr_s = \{ L \subset \CC^n \otimes_{\cO_s} \cK_s : \text{ $L$ is a $\cO_s$-lattice} \}
+    $$ \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \}
 $$   
@@
     $$
-        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
+        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
     $$
@@
 $$ 
-\Gr^{\sf th} = \{ L \subset \CC^n \otimes_{\CC[t]} \CC((t^{-1})) : \text{ $L$ is a $\CC[t]$-lattice} \}
+\Gr^{\sf th} = \{ L \subset  \CC((t^{-1}))^m : \text{ $L$ is a $\CC[t]$-lattice} \}
 $$   
-\jcom{Maybe write $\cK_\infty$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''. I made a $\Grth$ macro, but I had no idea where to put it.}
+\jcom{Maybe write $\cK_\infty$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.}
 
-    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s$ varying away from $s = 0$).
+    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s$).
     It is described in modular terms by
@@
         \left\{ 
-            (P,\varphi,s) : V\text{ is a rank $n$ vector bundle on }\PP, \varphi : V \rightarrow V_0 \text{ on } \PP \setminus \{0, s\}  
+            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \rightarrow V_0 \text{ on } \PP \setminus \{0, s\}  
         \right\} 
@@
     The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by
-    $$ \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1})/G(\CC[t])$$
+    $$ \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])$$
 
-    We also have a lattice description 
+    We also have a lattice descriptions 
     {\small
+    \begin{gather*}
+    \Grbd = 
+    \{ L \subset  \CC(t)^m, s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
+    % , $L$ is 
+    trivial at any $ a \ne 0, s$} \} \\
+     \Gr_{0,s} = 
+    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
+    \end{gather*} }
+    % 
+    \item The positive part $ \Gr^+$ of the affine Grassmannian and of the thick affine Grassmannian ${\Grth}^+$ is defined as
     $$
-    \Grbd = 
-    \{ L \subset \CC^n \otimes_{\CC[t]} \CC[t,t^{-1}], s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
-    % , $L$ is 
-    trivial at any $ a \ne 0, s$} \}
-    $$}
-    % 
+    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\CC((t^{-1}))) / G(\CC[t]) $$
+    In modular terms, $\Gr^+$ (resp.
+${\Grth}^+$) is the set of those $ (V, \varphi)$, where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.
+over $ \PP$).
+In lattice terms, $ \Gr^+$ (resp.
+${\Grth}^+$) contains those lattices $L$ which are contained in the standard lattice $ L_0$, i.e.
+$ L \subseteq L_0$.
 \end{itemize}
 
-These different versions of the affine Grassmannian are related as follows.  First there is an isomorphism $ \Gr \cong \Gr_s $ coming from the isomorphism $ \Ks \cong \cK$.
+These different versions of the affine Grassmannian are related as follows.
+
+First there is an isomorphism $ \Gr \cong \Gr_s $ coming from the isomorphism $ \cK \cong \Ks$.
 
@@
 $$
-Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^n \rightarrow \CC((t^{-1}))^n$ on the ambient spaces.
+Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \CC((t^{-1}))^m$ on the ambient spaces.
 
@@
 in the $ s \ne 0 $ case.
+\jcom{Maybe we should introduce some notation for this isomorphism.}
 
@@
 
-\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper. I don't know what notation we should use.}
+\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper and it is the most convenient way to define $Gr^{\lambda_1, \lambda_2}$.
+I don't know what notation we should use.}
 
-Now fix dominant weights $ \lambda_i, \mu_i \in P_+$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2 = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.
+Now fix effective dominant weights $ \lambda_i, \mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2 = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.
 
@@
     % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
-    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$ 
+    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$.  In the lattice model, we have
+    $$ L_\lambda = span_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m) $$.
     \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure $ \overline{\Gr}^\lambda = \cup_{\lambda' \le \lambda} \Gr^{\lambda'}$.
+This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
     \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.
-By construction the fibre of $ \overline{\Gr}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.
+By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.
 By Zhu's theorem (\jcom{need ref}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
 
-    \item The slice $\Gr_\mu = G_1[t^{-1}]L_\mu$ to the orbit $\Gr^\lambda$
-    \item The ``slice'' $\cW_\mu = G_1\xT[t^{-1}] t^\mu G(\CC[t])$ to the ``orbit'' $\Gr_\AA^{\lambda_1,\lambda_2}$ \acom{is not presented as a family}% $(\Grbd[2])^{\lambda_1,\lambda_2}$; replaced \cW_{\mu_1,\mu_2} = by Joel's not'n & def, seemingly independent of the decomposition of \mu; modified Joel's double bracket --- still confused over where W_\mu ought to live
+    Suppose that $ s \ne 0$.
+In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Grbd_{0,s} \cong \Gr \times \Gr_s $.
+This open locus is a $ G(\CC[t])$ orbit.
+The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ is given in Lemma \ref{le:Grl1l2} below.
+
+    \item The locus $\cW_\mu = G_1[[t^{-1}]]L_\mu \subset \Grth $.
+In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the Harder-Narasimhan filtration at $ \infty$.
+The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.
+
+    \item The semiinfinite orbit $ S^\mu = N(\cK)L_\mu \subset \Gr $.  
+    \item The family of semiinfinite orbits $ S^{\mu_1, \mu_2}_\AA := S^{\mu_1} * S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
+    $$
+    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2}
+    $$
+    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^\mu$.
+
+    \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.}
+
 \end{itemize}
-The following notation leaves the realm of affine Grassmannians and probably deserves its own subsection. E.g.\ ``nilpotent cones?''
+
+\subsection{Matrices}
+We now consider some subvarieties of the space of $ N$x$N$ matrices.
+
+%Recall that $ \lambda$ is a partition of $N$ and $ \lambda_1, \lambda_2 $ are partitions of $ N_1, N_2$ with $N_1 + N_2 = N$.
+
 \begin{itemize}
-    \item The nilpotent and semi-nilpotent cones $\cN$ and $\cN_\AA$ (of matrices with eigenvalues in $\{0\}$ and $\{0,s\} \in \AA\times\AA$ resp.) 
-    \item The slice $\TT_\mu$ to the orbit $\OO_\lambda$ 
-    \item The ``family of slices'' $\TT_{\mu_1,\mu_2}^{\AA}$ to the ``family of orbits'' $\OO^{\AA}_{\lambda_1,\lambda_2}$ \acom{ok to describe as such?}
+    \item For $ s \in \CC$, we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
+    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \cup_{\lambda' \le \lambda} \OO^{\lambda'}$
+    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda_1, \lambda_2}_{0,s}$ of matrices conjugate to $ J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.
+Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \cup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$
+
+    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space is said to have Jordan type $(0,\lambda_1), (s,\lambda_2)$ if its matrix representatives lies in $ \OO^{\lambda_1, \lambda_2}_{0,s}$
+    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.
+\jcom{We should justify why the 0 fibre is correct scheme-theoretically.}
+
+    \item The Mirkovic-Vybnornov slice $\TT_\mu$.  \jcom{Anne, can you add this definition?}
+
+    To each $ A \in \TT_\mu$, we will associate an $m$\times$m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
+       \begin{equation}
+            g(A)_{ij} = \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i = j$} \\
+             - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i \ne j$ }
+        \end{cases}
+    \end{equation}
+    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
+\jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
+
+    \item The ``upper-triangular'' MVy slice $\TT^{\mu_1, \mu_2,+}_\AA \rightarrow \AA $, defined by
+    $$
+    \TT^{\mu_1, \mu_2,+}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
+    $$
+    So a matrix in $\TT^{\mu_1, \mu_2,+}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.
+
+    Note that the fibre $  \TT^{\mu_1, \mu_2,+}_{0,0}$ is the same as the intersection of $ T^\mu $ with the strictly upper triangular matrices.
+
+    \jcom{Instead of $\TT^+$ maybe a different letter would be best?
+I'm moved all $\lambda, \mu$ to upper indices for consistency (except for $ \cW_\mu, T_\mu$) and also to let us put $ s $ or $ \AA$ in the lower index.
+I haven't been very consistent about $ \AA $ vs $ \CC$.
+Which do you prefer?}
 \end{itemize}
+
+\subsection{Old stuff}
+\jcom{I'm going to delete everything below here in this section, if that is ok with you.}
 
@@
 
+\begin{lemma} \label{le:Grl1l2}
+    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
+    \begin{enumerate}
+        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_s \rightarrow \Grth^+$
+        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$
+        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
+    \end{enumerate}
+\end{lemma}
+
+\begin{lemma} \label{le:Wmu}
+    Let $ L \in \Grth^+$.  The following are equivalent:
+    \begin{enumerate}
+        \item $ L \in \cW_\mu$.
+        \item $ \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
+    \end{enumerate}
+\end{lemma}
+
+Since the above basis will occur often, we will denote it  $ \beta_\mu$.
+
+\begin{lemma}
+    Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu_1, \mu_2}_\AA$ lands in $ \cW_\mu$.
+\end{lemma}
+
 \section{Climax}
+
+\begin{theorem} 
+The map $ T_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
+$$ L \mapsto [t|_{L_0/L} ]_{\beta_\mu}$$
+\end{theorem}
+
+\jcom{Do we have a reference?}
+
+For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda_1, \lambda_2}_\AA $ with $\cW_\mu$.
+As $  \overline{\Gr}^{\lambda_1, \lambda_2}_\AA $ is not a subscheme of $ \Grth$ by this intersection, we really mean the preimage of $ \cW_\mu$ under the map $$ \overline{\Gr}^{\lambda_1, \lambda_2}_\AA  \hookrightarrow \Grbd \rightarrow \Grth$$
+This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective.
+
+In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T^\mu$, using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
+
+\begin{theorem} \label{th:OGrl}
+    There is an isomorphism
+    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \cong \overline{Gr}^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+    given by $ (A,s) \mapsto (g(A), s)$.
+\end{theorem}
+
+\begin{theorem}
+    The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
+    $$ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T^{\mu_1, \mu_2, +}_\AA \cong \overline{Gr}^{\lambda_1, \lambda_2}_\AA \cap S^{\mu_1, \mu_2}_\AA$$
+\end{theorem}
 

### 2021-02-18 draft.tex
comments up to p5

@@
 
-\documentclass{article}
+\documentclass[draft]{article}
 \usepackage{basic}
@@
 % 
-Moreover, it is not clear why one should care about the fusion product on bases. \emoji{smile} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull}
+Moreover, it is not clear why one should care about the fusion product on bases. \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull}
 
@@
 Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.
-The dominant weights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
-We also need the notion of effective dominant coweight, which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
+The dominant \ul{weights} of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
+We also need the notion of effective dominant \ul{coweight},
+\acom{can we conflate or should we be precise and say coweight?}
+which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
 So an effective dominant coweight $ \lambda $ is a partition of $ \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
+Write $P_+$ for dominant and $P_{++}$ for effective dominant.
 
@@
 
-Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
+Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
+% with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
+% \[
+%     \begin{pNiceMatrix}[nullify-dots,xdots/line-style=loosely dotted]
+%         (t-s)^{\mu_1} & 0             & \Cdots & 0 \\
+%         0             & (t-s)^{\mu_2} & \Ddots & \Vdots \\
+%         % 0 & b & a & \Ddots & & \\
+%         \Vdots              & \Ddots        & \Ddots & 0 \\
+%         % \Vdots & & & & \\
+%         0             & \Cdots        &   0    & (t-s)^{\mu_m}
+%     \end{pNiceMatrix}
+% \]
+\[
+\begin{bmatrix}
+    (t-s)^{\mu_1} \\
+    & (t-s)^{\mu_2} \\ 
+    & & \ddots \\
+    & & & (t-s)^{\mu_m}
+\end{bmatrix} \in \GL_m(\cK).
+\]
+% nicematrix test
+% $\begin{bNiceArray}{ccc|c}[margin]
+%     \Block{3-3}<\Large>{A} & & & 0 \\
+%     & \hspace*{1cm} & & \Vdots \\
+%     & & & 0 \\
+%     \hline
+%     0 & \Cdots& 0 & 0
+%     \end{bNiceArray}$
+% 
+% $\begin{pNiceMatrix}
+%     \frac12 & -\frac12 \\
+%     \frac13 & \frac14 \\
+%     \end{pNiceMatrix}$
 
@@
 We will use the lattice model, so it is useful to recall the following definition.
-Let $ R \subset K$ be two rings (usually, but not always, $K $ will be a field).
-Let $ m \in \mathbb N$ and consider $ K^n $ as a $K$-module.
+Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field).
+Let $ m \in \mathbb N$ and consider $ K^m $ as a $K$-module.
 By restriction $ K^m$ can be viewed as an $R$-module.
-An $R$-lattice in $ M$ is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.
-Equivalently $ L = \Sp_R(v_1, \dots, v_m)$ where $ v_1, \dots, v_n$ are free generators of $K^m$.
+An $R$-lattice in $M$ is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.
+Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.
 
-The trivial lattice is $L_0 = R^m \subset K^m $.
-The group $\GL_m(K) $ acts transitively on the set of $ R$-lattices in $K^m$, thus giving a bijection between the set of such lattices and $\GL_m(K)/\GL_m(R)$.
+% The trivial lattice is 
+$L_0(R) = R^m \subset K^m $ is called the trivial lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
+% the set of such lattices 
+this set and $\GL_m(K)/\GL_m(R)$.
 
@@
 $$
-L(a) := L \otimes_{\CC[t]} \CC[[t-a]] \subset \CC((t-a))\,.
+L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]\,.
 $$
-We say that $ L $ is trivial at $ a $ if $ L(a) = \CC[[t-a]]^m.$
+We say that $ L $ is trivial at $ a $ if $ L(a) = \CC\xt[t-a]^m$. For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.
 
-\jcom{I wasn't sure of the notation to use here, but I wanted something which didn't conflict with $ L_0$.}
+\acom{Should we also mention our interest in $\cO$-lattices in $\cK^m$?}
 
-\acom{I think that MVy use this notation also: }
+% \jcom{I wasn't sure of the notation to use here, but I wanted something which didn't conflict with $ L_0$.}
+
+% \acom{I think that MVy use this notation also: }
 
@@
     $$ 
-    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}
+    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}\,.
     $$
     % 
-    \item For any $ s \in \CC $, the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
+    \item For any $ s \in \CC $, \acom{should it be $\AA$ instead of $\CC$} the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
     $$
@@
     $$
+    where $D_s$ is the formal disk centered at $s\in\PP$.
+
     We also have a lattice description 
-    $$ \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \}
-$$   
+$$ \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} $$   
     \item The thick affine Grassmannian $\Gr^{\sf th} = G(\CC\xT[t^{-1}])/G(\CC[t])$. It is described in modular terms by
@@
     $$
-    where $D_\infty$ denotes a disk centered at $ \infty$.
+    where $D_\infty$ denotes a disk centered at $ \infty$. \acom{What is the difference between ``a disk'' and ``the formal disk''}
+
     We also have a lattice description 
@@
     $$
-\jcom{Maybe write $\cK_\infty$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.}
 
-    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s$).
+    \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?}
+
+    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
     It is described in modular terms by
-    {\small
+    % {\small
     $$
@@
     % \end{aligned}
-    $$}
+    $$%}
+
     The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by
-    $$ \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])$$
+    % 
+    $$ 
+    \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,.
+    $$
+    \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
 
     We also have a lattice descriptions 
-    {\small
+    % {\small
     \begin{gather*}
@@
     \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
-    \end{gather*} }
+    \end{gather*}%}
+    \acom{$s\in\CC$ should be $s\in\AA$?}
     % 
-    \item The positive part $ \Gr^+$ of the affine Grassmannian and of the thick affine Grassmannian ${\Grth}^+$ is defined as
+    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp. are defined as 
+    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
     $$
-    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\CC((t^{-1}))) / G(\CC[t]) $$
+    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\CC\xT[t^{-1}]) / G(\CC[t]) 
+    $$
+    \acom{What is $M_m$?}
+
     In modular terms, $\Gr^+$ (resp.
-${\Grth}^+$) is the set of those $ (V, \varphi)$, where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.
+${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.
 over $ \PP$).
+
     In lattice terms, $ \Gr^+$ (resp.
-${\Grth}^+$) contains those lattices $L$ which are contained in the standard lattice $ L_0$, i.e.
+${\Grth}^+$) contains those lattices $L$ which are contained in the standard \acom{previously called ``trivial''} lattice $ L_0(\cO)$ (resp.
+$L_0(\CC[t])$.
+% , i.e.
 $ L \subseteq L_0$.
@@
 
-These different versions of the affine Grassmannian are related as follows.
+These \acom{which?} different versions of the affine Grassmannian are related as follows.
 
-First there is an isomorphism $ \Gr \cong \Gr_s $ coming from the isomorphism $ \cK \cong \Ks$.
+First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \cK \cong \Ks$.
 
@@
 $$
-G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\CC((t^{-1}))/G(\CC[t])
+G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\CC\xT[t^{-1}])/G(\CC[t])
 $$
-Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \CC((t^{-1}))^m$ on the ambient spaces.
+\acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
 
-The fibres $ Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ are given as follows
+Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \CC\xT[t^{-1}]^m$ on the ambient spaces.
+
+The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
 $$
-\Gr_{0,s} \cong \begin{cases} \Gr \times \Gr_s, \  s \ne 0 \\
-\Gr, \ s = 0.
+\Gr_{0,s} \cong 
+\begin{cases} 
+    \Gr \times \Gr_s & s \ne 0 \\
+    \Gr              & s = 0\,.
 \end{cases}
 $$
-This isomorphism is given in the lattice realization as
+In the $s\ne 0$ case this isomorphism is given in the lattice realization \acom{vs ``model''?} by taking trivializations; 
 $$
-L \mapsto (L(0), L(s))
+L \mapsto (L(0), L(s))\,.
 $$
-in the $ s \ne 0 $ case.
+% in the $ s \ne 0 $ case.
 \jcom{Maybe we should introduce some notation for this isomorphism.}
+\acom{Ok. Question: how is the isomorphism given at $s=0$?}
 
+\subsubsection{Maybe subsection? ``The convolution construction?''}
 The following construction will be very important in this paper.
 Let $ X_1, X_2 \subset \Gr$ be two subschemes.
-Then using the isomorphism $ \Gr \cong \Gr_s $ for each $ s$, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.
-Via this isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
-We define $ X_1 * X_2 $ to be the scheme theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.
+Then using the isomorphism $ \Gr \cong \Gr_s $ for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.
+Via \ul{this} \acom{rather, the above?} isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
+
+We define $ X_1 * X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.
 We have the projection $ \pi: \Grbd \rightarrow \AA $ and we form $ X_1 \cdot X_2 = X_1 * X_2 \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.
-We regard $ X_1 \cdot X_2$ as a subscheme of $ \Gr $ using the isomorphism $\Gr_{0,0} \cong \Gr $.
+We regard $ X_1 \cdot X_2$ as a subscheme of $ \Gr $ using \ul{the isomorphism} $\Gr_{0,0} \cong \Gr $.
+\acom{Repeat question: what is this iso?
+Roger says maybe it's in MV?}
 
-\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper and it is the most convenient way to define $Gr^{\lambda_1, \lambda_2}$.
+\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper and it is the most convenient way to define $\Gr^{\lambda_1, \lambda_2}$.
 I don't know what notation we should use.}
 
-Now fix effective dominant weights $ \lambda_i, \mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2 = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.
+\acom{Roger and I have been using $\ast$ to denote fusion.
+Do we need a notation for the scheme-theoretic closure of $X_1\times X_2\times\AA^\times$?
+If not then I like $X_1\ast X_2 = \overline{X_1 \times X_2 \times \AA^\times}\cap \pi^{-1}(0)$.}
+
+Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.
 
@@
     \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$. In the lattice model, we have
-    $$ L_\lambda = span_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m) $$.
-    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure $ \overline{\Gr}^\lambda = \cup_{\lambda' \le \lambda} \Gr^{\lambda'}$.
+    $$ 
+    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
+    $$
+    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
+    $ \overline{\Gr^\lambda} = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
+    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??}
     This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
@@
 By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.
-By Zhu's theorem (\jcom{need ref}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
+By Zhu's theorem (\jcom{need ref} \acom{\cite[Proposition 3.1.14]{zhu2016introduction}}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
 

### 2021-02-19 draft.tex
added stuff on MVy slice

@@
 Then using the isomorphism $ \Gr \cong \Gr_s $ for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.
-Via \ul{this} \acom{rather, the above?} isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
+Via \ul{this} \acom{rather, the above?
+$L\mapsto (L(0),L(s))$} isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
 
@@
     This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
-    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.
+    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{\Gr}^{\lambda_1} * \overline{\Gr}^{\lambda_2}$.
+\acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
+
     By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.
@@
     Suppose that $ s \ne 0$.
-In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Grbd_{0,s} \cong \Gr \times \Gr_s $.
-This open locus is a $ G(\CC[t])$ orbit.
-The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ is given in Lemma \ref{le:Grl1l2} below.
+In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.
+This open locus is a $ G(\CC[t])$-orbit
+    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
+    whose lattice description is given in \Cref{le:Grl1l2} below.
 
-    \item The locus $\cW_\mu = G_1[[t^{-1}]]L_\mu \subset \Grth $.
-In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the Harder-Narasimhan filtration at $ \infty$.
+    \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
+    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here?}
+    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the \ul{Harder--Narasimhan filtration of $V$ at $ \infty$}.
 The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.
+\acom{que est-ce?}
 
-    \item The semiinfinite orbit $ S^\mu = N(\cK)L_\mu \subset \Gr $.  
-    \item The family of semiinfinite orbits $ S^{\mu_1, \mu_2}_\AA := S^{\mu_1} * S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
+    \item The semi-infinite orbit $ S^\mu = N(\cK)L_\mu \subset \Gr $.  
+    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_\AA := S^{\mu_1} * S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
     $$
-    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2}
+    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} \,. % \G(\CC[t])
     $$
+    \acom{should be $G(\cO)$-coset or $G(\CC[t])$-coset?}
     On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^\mu$.
@@
     \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.}
+    % TODO!
 
@@
 \subsection{Matrices}
-We now consider some subvarieties of the space of $ N$x$N$ matrices.
+We now consider some subvarieties of the space of $ N\times N$ matrices.
 
@@
 \begin{itemize}
-    \item For $ s \in \CC$, we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
-    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \cup_{\lambda' \le \lambda} \OO^{\lambda'}$
+    \item For $ s \in \CC$, we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. \acom{$s\in\AA$?}
+    % 
+    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\lambda' \le \lambda} \OO^{\lambda'}$.
+    % 
     \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda_1, \lambda_2}_{0,s}$ of matrices conjugate to $ J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.
-Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \cup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$
-
-    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space is said to have Jordan type $(0,\lambda_1), (s,\lambda_2)$ if its matrix representatives lies in $ \OO^{\lambda_1, \lambda_2}_{0,s}$
+Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \bigcup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$.
+\acom{$s\in\AA$?}
+    % 
+    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda_1), (s,\lambda_2))$ if its matrix representatives lie in $ \OO^{\lambda_1, \lambda_2}_{0,s}$.
+    % 
     \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.
@@
 
-    \item The Mirkovic-Vybnornov slice $\TT_\mu$.  \jcom{Anne, can you add this definition?}
+    \item Fix the ``\mu-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$.
+The Mirkovic--Vybnornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that
+    \[
+        \begin{aligned}
+            &\text{for all } 1 \le a,s\le m\,,
+            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
+            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
+            &\text{then } (e^t_s)' (A-J_\mu) e^b_a = 0 \,.
+        \end{aligned}    
+    \]
+    In words, $A$ is a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
+    Mirkovic and Vybornov describe $\TT_\mu$ as the slice in which $f$ acts as close to regular nilpotent as possible.
+    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
+    \acom{this ok?} % \jcom{Anne, can you add this definition?}
 
-    To each $ A \in \TT_\mu$, we will associate an $m$\times$m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
+    \item To each $ A \in \TT_\mu$, we will associate an $m$\times$m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
        \begin{equation}

### 2021-02-19 draft.tex
joel made some responses

--- 2021-02-18 draft.tex
@@
 Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.
-The dominant \ul{weights} of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
-We also need the notion of effective dominant \ul{coweight},
-\acom{can we conflate or should we be precise and say coweight?}
+The dominant coweights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
+We also need the notion of effective dominant coweight,
+\acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
 which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
@@
 Write $P_+$ for dominant and $P_{++}$ for effective dominant.
+
+We will also study the affine space of $m$x$m$ matrices which we denote $ M_m$.
 
@@
     & & & (t-s)^{\mu_m}
-\end{bmatrix} \in \GL_m(\cK).
+\end{bmatrix} 
 \]
+which we will view in $ GL_m(R) $ for any ring $ R $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ R = \Ks, \CC(t)$).
 % nicematrix test
@@
 % The trivial lattice is 
-$L_0(R) = R^m \subset K^m $ is called the trivial lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
+$L_0(R) = R^m \subset K^m $ is called the standard lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
 % the set of such lattices 
@@
 \acom{Should we also mention our interest in $\cO$-lattices in $\cK^m$?}
+\jcom{I don't think that it is necessary.  I just put the part about $ \CC(t)$ to set up the notation for this specialization.}
 
@@
     $$
-    where $D_\infty$ denotes a disk centered at $ \infty$. \acom{What is the difference between ``a disk'' and ``the formal disk''}
+    where $D_\infty$ denotes a disk centered at $ \infty$. \acom{What is the difference between ``a disk'' and ``the formal disk''} \jcom{No difference.}
 
@@
 
-    \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?}
+    \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?
+Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?} \jcom{That's a good point!
+Maybe we could use some kind of bold  Gr (``thick'' letters) or maybe that would be too confusing.}
 
@@
     \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
+    \jcom{Yes, that is one reason.
+But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).
+For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
 
@@
     $$
-    \acom{What is $M_m$?}
+    \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}
 
@@
     In lattice terms, $ \Gr^+$ (resp.
-${\Grth}^+$) contains those lattices $L$ which are contained in the standard \acom{previously called ``trivial''} lattice $ L_0(\cO)$ (resp.
+${\Grth}^+$) contains those lattices $L$ which are contained in the standard \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
+But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.} lattice $ L_0(\cO)$ (resp.
 $L_0(\CC[t])$.
@@
 \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
+\jcom{Permission granted!}
 
@@
 $$
-In the $s\ne 0$ case this isomorphism is given in the lattice realization \acom{vs ``model''?} by taking trivializations; 
+In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivialization to the appropriate disks.
+In the lattice realization, it is given by forming tensor products
 $$
@@
 
-\subsubsection{Maybe subsection? ``The convolution construction?''}
+In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
+
+\jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
+
+\subsection{The fusion construction}
 The following construction will be very important in this paper.
@@
 Then using the isomorphism $ \Gr \cong \Gr_s $ for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.
-Via \ul{this} \acom{rather, the above?} isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
+Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
 
@@
 Roger says maybe it's in MV?}
+\jcom{Now answered above.}
 
@@
 If not then I like $X_1\ast X_2 = \overline{X_1 \times X_2 \times \AA^\times}\cap \pi^{-1}(0)$.}
+\jcom{I think that we will need notations for both things, but I'm happy to use $ \ast$ for the central fibre and use something else for the whole family.}
 
+\subsection{Some subvarieties of affine Grassmannians}
 Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.
@@
     $ \overline{\Gr^\lambda} = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
-    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??}
+    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
     This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.

### 2021-02-19 draft.tex

--- 2021-02-19 draft.tex
@@
 Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.
-The dominant \ul{weights} of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
-We also need the notion of effective dominant \ul{coweight},
-\acom{can we conflate or should we be precise and say coweight?}
+The dominant coweights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
+We also need the notion of effective dominant coweight,
+% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
 which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
@@
 Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_s = \CC[[t-s]]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$.
+We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$ \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?}
 % TODO: given by or described by?
@@
     & & & (t-s)^{\mu_m}
-\end{bmatrix} \in \GL_m(\cK).
+\end{bmatrix} 
 \]
+which we will view in $\GL_m(R) $ for any ring $ R $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ R = \Ks, \CC(t)$).
+
+We will also study the affine space of $m\times m$ matrices which we denote $ M_m$.
 % nicematrix test
@@
 
-\acom{Should we also mention our interest in $\cO$-lattices in $\cK^m$?}
+% \acom{Should we also mention our interest in $\cO$-lattices in $\cK^m$?}
+% \jcom{I don't think that it is necessary.  I just put the part about $ \CC(t)$ to set up the notation for this specialization.}
 
@@
     We also have a lattice description 
-$$ \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} $$   
-    \item The thick affine Grassmannian $\Gr^{\sf th} = G(\CC\xT[t^{-1}])/G(\CC[t])$. It is described in modular terms by
+    $$ 
+    \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} \,. 
+    $$   
+    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
+    It is described in modular terms by
     $$
@@
     $$
-    where $D_\infty$ denotes a disk centered at $ \infty$. \acom{What is the difference between ``a disk'' and ``the formal disk''}
+    where $D_\infty$ denotes a disk centered at $ \infty$. 
+    % \acom{What is the difference between ``a disk'' and ``the formal disk''} \jcom{No difference.}
 
@@
     $$ 
-    \Gr^{\sf th} = \{ L \subset  \CC((t^{-1}))^m : \text{ $L$ is a $\CC[t]$-lattice} \}
-    $$
+    \Grth = \{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \}\,.
+    $$ % \CC((t^{-1}))^m
 
-    \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?}
+    \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?
+Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?} \jcom{That's a good point!
+Maybe we could use some kind of bold  Gr (``thick'' letters) or maybe that would be too confusing.} \acom{Ok, it's tentative.}
 
@@
     $$
-    \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
+    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
+    % \jcom{Yes, that is one reason.
+But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).
+For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
+    % \acom{lol}
 
@@
     % 
-    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp. are defined as 
+    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp.\ are defined as 
     % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
@@
     $$
-    \acom{What is $M_m$?}
+    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}
 
@@
 
-    In lattice terms, $ \Gr^+$ (resp.
-${\Grth}^+$) contains those lattices $L$ which are contained in the standard \acom{previously called ``trivial''} lattice $ L_0(\cO)$ (resp.
-$L_0(\CC[t])$.
-% , i.e.
-$ L \subseteq L_0$.
+    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the standard 
+    % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
+But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.}
+    % \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
+    lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$. % , i.e. $ L \subseteq L_0$.
 \end{itemize}
@@
 
-Second, we have a map $$ \Grbd \rightarrow \Grth $$ which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
+Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
+% $$ \Grbd \rightarrow \Grth $$ 
+which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
 $$
-G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\CC\xT[t^{-1}])/G(\CC[t])
+G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])
 $$
-\acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
+% \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
+% \jcom{Permission granted!}
+% \acom{replaced}
 
-Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \CC\xT[t^{-1}]^m$ on the ambient spaces.
+Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
 
@@
 $$
-In the $s\ne 0$ case this isomorphism is given in the lattice realization \acom{vs ``model''?} by taking trivializations; 
+In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializating to the appropriate disks.  
+In the lattice realization, it is given by forming tensor products 
 $$
@@
 \jcom{Maybe we should introduce some notation for this isomorphism.}
-\acom{Ok. Question: how is the isomorphism given at $s=0$?}
+% \acom{Ok. Question: how is the isomorphism given at $s=0$?}
+\acom{Ok. TODO.}
 
-\subsubsection{Maybe subsection? ``The convolution construction?''}
+In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
+
+\jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
+
+\subsection{The fusion construction}
 The following construction will be very important in this paper.
 Let $ X_1, X_2 \subset \Gr$ be two subschemes.
-Then using the isomorphism $ \Gr \cong \Gr_s $ for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.
-Via \ul{this} \acom{rather, the above?
-$L\mapsto (L(0),L(s))$} isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
+Then using the isomorphism $ \Gr \cong \Gr_s $, for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.
+% <<<<<<< HEAD
+% Via \ul{this} \acom{rather, the above? $L\mapsto (L(0),L(s))$} 
+Next, using the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
+% =======
+% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
+% >>>>>>> 5a15ce15b14109bab482282aa5657c9596f7892d
 
-We define $ X_1 * X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.
-We have the projection $ \pi: \Grbd \rightarrow \AA $ and we form $ X_1 \cdot X_2 = X_1 * X_2 \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.
-We regard $ X_1 \cdot X_2$ as a subscheme of $ \Gr $ using \ul{the isomorphism} $\Gr_{0,0} \cong \Gr $.
-\acom{Repeat question: what is this iso?
-Roger says maybe it's in MV?}
+We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
+We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = X_1 \ast_\AA X_2 \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
+We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
+% \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
+% \jcom{Now answered above.}
 
@@
 If not then I like $X_1\ast X_2 = \overline{X_1 \times X_2 \times \AA^\times}\cap \pi^{-1}(0)$.}
+\jcom{I think that we will need notations for both things, but I'm happy to use $ \ast$ for the central fibre and use something else for the whole family.} \acom{Ok, I have changed it to notation from Roger's thesis/AK.
+Only now I am confused as to what is being called fusion---why do we not take the top dimensional subscheme?}
 
+\subsection{Some subvarieties of affine Grassmannians}
 Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.
@@
     \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
-    $ \overline{\Gr^\lambda} = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
-    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??}
+    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
+    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
     This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
-    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{\Gr}^{\lambda_1} * \overline{\Gr}^{\lambda_2}$.
-\acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
+    % 
+    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
+    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
+    \acom{should we also subsript this family with $0,\AA$?}
 
     By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.
-By Zhu's theorem (\jcom{need ref} \acom{\cite[Proposition 3.1.14]{zhu2016introduction}}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
+By Zhu's theorem (\jcom{need ref} \acom{pretty sure it's \cite[Proposition 3.1.14]{zhu2016introduction}}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
 
@@
     \item The semi-infinite orbit $ S^\mu = N(\cK)L_\mu \subset \Gr $.  
-    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_\AA := S^{\mu_1} * S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
+    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
     $$
@@
     % 
-    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.
+    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.
 \jcom{We should justify why the 0 fibre is correct scheme-theoretically.}
+    \acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
+    in $\AA_s\times \AA_{\det}$? 
+    so the set of $A$ which are conjugate to
+    $J_{0,\lambda_1} \oplus J_{s,\lambda_2}$
+    by a matrix whose determinant is divisible by $s$ is also closed?}
 
@@
 Which do you prefer?}
+
+    \acom{Different letter fine by me.
+Maybe $\UU$?
+And, I guess we do not need $\AA$ but it is a nice letter to have.
+It is also good to distinguish the $\CC$ over which $R,K$ is defined and the $\AA$ over which $\Grbd$ is defined?}
 \end{itemize}

### 2021-02-19 draft.tex
delete old stuff

@@
 
-    \acom{Different letter fine by me.
-Maybe $\UU$?
-And, I guess we do not need $\AA$ but it is a nice letter to have.
-It is also good to distinguish the $\CC$ over which $R,K$ is defined and the $\AA$ over which $\Grbd$ is defined?}
+    \acom{Maybe $\UU$ for a different letter?
+And, I guess we do not need $\AA$ but it is a nice letter to have around.
+It also serves to distinguish the $\CC$ over which $R,K$ are defined from the $\AA$ over which $\Grbd$ is defined?}
 \end{itemize}
@@
 \jcom{I'm going to delete everything below here in this section, if that is ok with you.}
-
+\acom{Yup!}
 % New (?) definitions among these are as follows.

### 2021-02-19 draft.tex
double yup

--- 2021-02-19 draft.tex
@@
     \jcom{Instead of $\TT^+$ maybe a different letter would be best?
-I'm moved all $\lambda, \mu$ to upper indices for consistency (except for $ \cW_\mu, T_\mu$) and also to let us put $ s $ or $ \AA$ in the lower index.
+I'm moved all $\lambda, \mu$ to upper indices for consistency (except for $ \cW_\mu, \TT_\mu$) and also to let us put $ s $ or $ \AA$ in the lower index.
 I haven't been very consistent about $ \AA $ vs $ \CC$.
@@
 \jcom{I'm going to delete everything below here in this section, if that is ok with you.}
+\acom{Yup!}
 

### 2021-02-21 draft.tex
more changes from joel

--- 2021-02-19 draft.tex
@@
 Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$ \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?}
+We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$ \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?} \jcom{That wouldn't quite make sense.
+Maybe this would be the place to define these disks $D_\infty$ and then we could say the function field of the disk.}
 % TODO: given by or described by?
@@
     \acom{$s\in\CC$ should be $s\in\AA$?}
+    \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
     % 
@@
 Only now I am confused as to what is being called fusion---why do we not take the top dimensional subscheme?}
+\jcom{I guess that there are two things that one could mean by fusion of MV cycles.
+This scheme $ X_1 \circ X_2$ or the expression which appear in Theorem 7.11 of mvbasis, which is a linear combination of the top-dimensional components of this scheme with multiplicites.
+In the general context of this section ($X_1, X_2$ are not necessarily MV cycles), then I guess it is best to talk about the subscheme.
+Maybe we can call the expression appearing Theorem 7.11 the ``numerical fusion'' of MV cycles.
+By the way, somewhere in this paper we should explain Theorem 7.11 and say that this gives us motivation to study fusion of MV cycles.}
 
@@
     % 
-    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
+    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast \overline{\Gr}^{\lambda_2}$.
     % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
-    \acom{should we also subsript this family with $0,\AA$?}
+    %\acom{should we also subsript this family with $0,\AA$?}
 
@@
     $$
-    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} \,. % \G(\CC[t])
+    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
     $$
-    \acom{should be $G(\cO)$-coset or $G(\CC[t])$-coset?}
+%    \acom{should be $G(\cO)$-coset or $G(\CC[t])$-coset?}
+\jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
     On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^\mu$.
@@
     by a matrix whose determinant is divisible by $s$ is also closed?}
+    \jcom{I didn't follow your argument.
+One approach would be to write down the generators for the ideal of $overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.
+For example, take $ \lambda_1 = (1) = \lambda_2 $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.
+I am hoping that we can find a reference for this result somewhere.}
 
@@
     \acom{this ok?} % \jcom{Anne, can you add this definition?}
+    \jcom{When you wrote ``In words,'', it is not quite correct because of the diagonal blocks have those 1s.  Also it would be good to have an example.  And what is $f$ in the last sentence? }
 
@@
 It also serves to distinguish the $\CC$ over which $R,K$ are defined from the $\AA$ over which $\Grbd$ is defined?}
+    \jcom{Sure $\UU$ is good.}
 \end{itemize}
 
-\subsection{Old stuff}
-\jcom{I'm going to delete everything below here in this section, if that is ok with you.}
-\acom{Yup!}
-% New (?) definitions among these are as follows.
-% 
-%The [family of] slices [with $s$-fibre?]
-%\begin{equation}
-%    \cW_{\mu_1,\mu_2} = G_1 [t^{-1},(t-s)^{-1}]L_{\mu_1,\mu_2}
-%\end{equation}
-
-Recall (citation?) that there is an embedding of the usual (``thin'') affine Grassmannian $\Gr $ as we have defined it into the ``thick'' affine Grassmannian. 
-%
-
-\acom{In \cite{kamnitzer2014yangians} the thick Gr is said to be necessary for the noncommutative algebras considered.
-What is our reason for preferring it to the thin Gr?
-Can we replace thick by thin?
-Joel said that rather it is needed/used because unlike the thin $\Gr$ which is an ind-scheme, the thick $\Gr^{\sf th}$ is a scheme, so taking Spec of global functions (on $\cW_\mu$?) will recover $\cW_\mu$?}
-\[
-\Gr \cong G(\CC[t,t^{-1}])/G(\CC[t])\hookrightarrow \Gr^{\sf th} := G(\CC\xT[t^{-1}])/G(\CC[t]) \quad g\cO \mapsto gG(\CC[t])  \,.
-\]
-Let 
-% $L_\mu = t^\mu G(\cO)$ and 
-$L_{\mu_1, \mu_2} = t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])$. 
-% \acom{or $ t^{\mu_1} (t-s)^{\mu_2} G[t]$ in thick?} % \in G((t^{-1}))/G[t]
-% 
-% \begin{equation}
-%     \cW_\mu = G_1[[t^{-1}]]L_\mu \subset G((t^{-1}))/G[t]
-% \end{equation}
-% a subscheme of the thick affine Grassmannian
-% 
-Note that $ L_{\mu_1, \mu_2} = (t-s)^{\mu_2} t^{-\mu_2} L_{\mu} \in \cW_\mu$ 
-% \acom{thick or thin}
-and that  $L_{\mu_1,\mu_2}\in\Grbd$ \acom{should say $\Grbd[s]$ as it's really a lattice in a given fibre being characterized?} is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$, i.e.\
-% \acom{thick only} 
-\begin{equation}
-    \label{eq:defWBD}
-    % \begin{split}
-        %L_{\mu_1,\mu_2}\otimes \CC[(t-s)^{-1}] =
-        L_{\mu_1,\mu_2}\otimes \CC\xt = L_{\mu_2} \otimes \CC\xt \qquad
-        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] = L_{\mu_1} \otimes \CC\xt[t-s]
-    % \end{split}
-\end{equation}
-where 
-% $L_{\mu_i}$ denotes the point $t^{\mu_i}G(\cO)\in\Gr$ and 
-the tensor product is taken over $\CC[t]$. 
-%
-
-The family of semi-infinite orbits 
-\begin{equation}
-    S_{\mu_1,\mu_2} = N_-(\CC\xT[t^{-1}]) L_{\mu_1,\mu_2}\,. 
-\end{equation}
-\acom{1.
-Introduce $N_\pm$.
-2.
-In \cite{kamnitzer2014yangians} the global version of $S^\mu_-$ is the subvariety $S^\mu_{-,\AA}\subset\Grbd$ whose generic fibre is $\bigcup_{\mu_1 + \mu_2 = \mu} S^{\mu_1}_-\times S^{\mu_2}_-$ and whose zero fibre is $S^\mu_-$ which don't look to be the same thing.}
-
-The family \acom{orbit?
-orbits?
-family of orbits?} of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ (i.e.\ which are trivial at $a \ne 0$ or $s$, to use the terminology introduced in the \cref{ss:lat}) is described more explicitly as follows
-\begin{equation}
-    \label{eq:defGrBDlambda}
-    \begin{split}
-        % (\Grbd[2])^{\lambda_1,\lambda_2} = 
-        \Gr_{\AA}^{\lambda_1,\lambda_2} = 
-        \{L \in\Grbd : 
-        %L\otimes\CC[t^{-1}] 
-        L \otimes_{\CC[t]} \CC\xt[t-s] 
-        &\in \Gr^{\lambda_2} \text{ and } \\
-        % L\otimes\CC[(s-t)^{-1}] 
-        L\otimes_{\CC[t]} \CC\xt &\in \Gr^{\lambda_1} \text{ and } \\ 
-        L \otimes_{\CC[t]} \CC\xt[t-a] &= L_0 \text{ for all $ a \ne 0, s$} \}\,.
-    \end{split}
-\end{equation}
-
-% \jcom{It is important to add the condition that the lattices are trivial at $ a $.} \acom{$a\ne 0,s$}
-% 
-% \acom{These defining conditions are again just telling us that in the fibre over the fixed point $(0,s)\in C^{(2)}$ this set is pairs of lattices; note that we invert the indeterminates $t$ and $(t-s)$ \textit{after} specializing $(0,s)$.
-Could we give a more explicit characterization like $t^{N_1}(t-s)^{N_2} L_0 \subseteq L\subseteq t^{-N_1}(t-s)^{-N_2}$?}
-
-The [family ``$\cN\otimes\CC[s]$? $\cN\times\CC$?'' of] semi-nilpotent cone[s fibred over $C = \AA^1$ with $s$-fibre] 
-\begin{equation}
-    \cN_s = \{A \in \mat(N) : \text{eigenvalues of } A \text{ are } 0 \text{ or }s\}\,.
-\end{equation}
-
-\begin{comment}
-    The [family of] slice[s $\TT_{\mu_1,\mu_2}$ fibred over $C=\AA^1$ with $s$-fibre]
-\begin{equation}
-    \begin{split}
-        \TT_{\mu_1,\mu_2}^s = \{ B + C_s: B &\text{ is a }\mu\times\mu \text{ block matrix of zeros} \\
-        &\text{except possibly in the last }\min(\mu_i,\mu_j) \\ 
-        &\text{columns of the last row of each }\mu_i\times\mu_j \text{ block} \\
-        &\text{and } C_s \text{ is the block diagonal matrix of}\\
-        &\text{companion matrices of } t^{\mu_{1,k}}(t-s)^{\mu_{2,k}}\}\,.
-    \end{split}
-\end{equation}
-
-The uppertriangular subfamily $\TT_{\mu_1,\mu_2}^{+}$ with $s$-fibre
-\begin{equation}
-    \TT_{\mu_1,\mu_2}^{+,s} = \{B + C_s \in \TT_{\mu_1,\mu_2} : B \in\n\}
-\end{equation}
-where $\n\subset\mat(N)$ is the unipotent subalgebra of uppertriangular matrices.
-\end{comment}
-
-\acom{
-    % or---as Joel pointed out, may be ok with:
-The slice $\TT_\mu$ as defined in \cite{mirkovic2007quiver}, no change, \text{and} the family of slices $$\TT_{\mu_1,\mu_2}^{+,s} = \TT_\mu \cap \n + C_{\mu_1,\mu_2}^s$$ where $C_{\mu_1,\mu_2}^s$ is the block diagonal matrix of companion matrices of
-% 
-\begin{equation}
-    % C_s \text{ is the block diagonal matrix of companion matrices of } 
-    t^{\mu_{1,k}}(t-s)^{\mu_{2,k}} \quad (1\le k\le m).
-\end{equation}
-% not sure about notation
-Watch out for mixing up of $m$ and $n$.
-}
-
-The [family of] orbit[s $\OO_{\lambda_1,\lambda_2}$ fibred over $C = \AA$ with $s$-fibre]  
-\begin{equation}
-    \OO_{\lambda_1,\lambda_2}^s = \{A \in \cN_s : A \text{ is conjugate to } J_{\lambda_1}\oplus (sI_{N_2} + J_{\lambda_2})\}
-\end{equation}
-where $J_{\lambda_i}$ is the Jordan normal form of block type $\lambda_i$ and $I_{N_2}$ is the identity matrix in $\mat(N_2)$.
-% 
 \section{Exposition}
@@
 \end{theorem}
+
+\jcom{I was thinking about the proof of this result.
+It is enough to prove that for $ A \in \OO^{\lambda_1, \lambda_2}_s \cap \TT_\mu $, $g(A) \in S^{\mu_1, \mu_2}_s $ if and only if $ A \in T^+$.
+It is easy to show that if $ A \in T^+$, then $ g(A) \in S^{\mu_1, \mu_2}_s $.
+But the converse is not so obvious.
+(I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu_1, \mu_2}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu_1, \mu_2}$ and $ T^+ $ as attracting sets for a $\CC^\times$ action.
+Which do you prefer?}
 

### 2021-02-21 draft.tex
added picture of T plus defense of argument

@@
 By the way, somewhere in this paper we should explain Theorem 7.11 and say that this gives us motivation to study fusion of MV cycles.}
+\acom{Sure! It is quoted at the end, in \Cref{s:denouement} as an application.}
 
@@
     \jcom{I didn't follow your argument.
-One approach would be to write down the generators for the ideal of $overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.
+One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.
 For example, take $ \lambda_1 = (1) = \lambda_2 $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.
 I am hoping that we can find a reference for this result somewhere.}
+    \acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda_1}\oplus J_{s,\lambda_2}$ limit to matrices which are conjugate to $J_\lambda$.
+In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}
 
@@
     \]
-    In words, $A$ is a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
+    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
     Mirkovic and Vybornov describe $\TT_\mu$ as the slice in which $f$ acts as close to regular nilpotent as possible.
     % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
+    In pictures, the elements $A$ look like 
+    \[
+        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
+             & 1 & & & & & \\
+             &  & 1 & & & & \\
+            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
+              &  & &  & 1 & & \\
+              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
+             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
+             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
+        \end{BMAT}
+        \right]
+    \]
+    % 
     \acom{this ok?} % \jcom{Anne, can you add this definition?}
     \jcom{When you wrote ``In words,'', it is not quite correct because of the diagonal blocks have those 1s.  Also it would be good to have an example.  And what is $f$ in the last sentence? }
+    \acom{fixed? As for $f$ I think it is an $\sl_2$ triplet. Hopeful you could explain what MVy meant bc I never quite understood!}
 
@@
     \jcom{Sure $\UU$ is good.}
+    \acom{And, sorry, ignore my other comment; it's the same $\CC$ (or $\AA$) nothing to distinguish.}
 \end{itemize}
@@
 \jcom{Do we have a reference?}
+\acom{Your paper with Sabin??}
 
@@
 \section{Denouement}
+\label{s:denouement}
 

### 2021-02-21 draft.tex
joels replies

@@
 The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.
-\acom{que est-ce?}
+\acom{que est-ce?} \jcom{It's not very relevant for this paper.
+Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN-filtration; it is a partial flag of subbundles of type determined by $ \mu$.
+We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.
+Maybe ``preserves'' is not the best word above.}
 

### 2021-02-21 draft.tex
typos in lattice sec

@@
 We will use the lattice model, so it is useful to recall the following definition.
-Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field).
-Let $ m \in \mathbb N$ and consider $ K^m $ as a $K$-module.
+Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field \acom{When is $K$ not a field?}).
+Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and consider $ K^m $ as a $K$-module.
 By restriction $ K^m$ can be viewed as an $R$-module.
-An $R$-lattice in $M$ is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.
+An $R$-lattice in $M$ \acom{what is $M$?
+should be $K^m$?} is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.
 Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.
@@
 $$
-L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]\,.
+L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
 $$
-We say that $ L $ is trivial at $ a $ if $ L(a) = \CC\xt[t-a]^m$. For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.
+We say that $ L $ is trivial at $ a $ if $ L(a) = \CC\xt[t-a]^m$. \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
+For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.
 
@@
 
-    \item To each $ A \in \TT_\mu$, we will associate an $m$\times$m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
+    \item To each $ A \in \TT_\mu$, we will associate an $m\times m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
        \begin{equation}

### 2021-02-21 draft.tex
graff typo missed a Kinf
should have brackets around star product in circ construction right

@@
     $$
-    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\CC\xT[t^{-1}]) / G(\CC[t]) 
+    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\Kinf) / G(\CC[t]) % \CC\xT[t^{-1}] missed a spot  
     $$
@@
 We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
-We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = X_1 \ast_\AA X_2 \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
+We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
 We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 

### 2021-02-21 draft.tex
circ contained in not equal to central fibre of bdgr typo

@@
 We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
-We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
+We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
 We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 

### 2021-02-22 draft.tex
about nondom mu_i
so long as sum is dom
typo in coweight as point of GL(K) descr

@@
 \]
-which we will view in $\GL_m(R) $ for any ring $ R $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ R = \Ks, \CC(t)$).
+which we will view in $\GL_m(K) $ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it
 
@@
 Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.
+\acom{At some point at least mention that we expect this to go through for permutations of $\mu_i\in P_{++}$ i.e.\ skew partitions?
+or non-dominant, but also non-negative weights, so long as $\mu_1 + \mu_2$ is in $P_{++}$}
 

### 2021-02-22 draft.tex
some missing cosets

@@
     whose lattice description is given in \Cref{le:Grl1l2} below.
+    \acom{Why $G(\CC[t])$}
 
@@
 \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
-    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^\mu$.
+    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$.
+\acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}
 
@@
         \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_s \rightarrow \Grth^+$
-        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$
+        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$ \acom{why no $G(\CC[t])$-coset?}
         \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.

### 2021-02-22 draft.tex
notn for numerical fusion

@@
 By the way, somewhere in this paper we should explain Theorem 7.11 and say that this gives us motivation to study fusion of MV cycles.}
-\acom{Sure! It is quoted at the end, in \Cref{s:denouement} as an application.}
+\acom{Sure! It is quoted at the end, in \Cref{s:denouement} as an application. Addendum: for the numerical fusion I suggest simply $[Z_1][Z_2]$. This is what I will use in my talk. }
 
@@
     $$
-    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
+    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
     $$
@@
 \begin{itemize}
-    \item For $ s \in \CC$, we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. \acom{$s\in\AA$?}
+    \item For $ s \in \CC$ and $\lambda\in P_{++}$ we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. \acom{$s\in\AA$?}
     % 

### 2021-02-23 draft.tex
misc changes

@@
     % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
-    In pictures, the elements $A$ look like 
+    In pictures, aka by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
     \[
@@
     \]
+    Smaller: 
+    \[
+        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
+            0 & 1 & 0 & 0 & 0\\
+            0 & 0 & 1 & 0 & 0\\
+            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
+            0 & 0 & 0 & 0 & 1\\
+            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
+            \end{BMAT}\right]    
+            \mapsto 
+            \left[\begin{array}{rr}
+                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
+                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
+            \end{array}\right]
+    \]
     % 
@@
        \begin{equation}
-            g(A)_{ij} = \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i = j$} \\
-             - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i \ne j$ }
+            g(A)_{ij} = 
+            \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
+                % \text{ if $ i = j$} \\
+             - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
+            %  \text{ if $ i \ne j$ }
         \end{cases}
@@
     where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
+    For example, the $A$ above will define 
+    % \acom{the transpose of! TODO. Had script?}
+    % \[
+    % \begin{bmatrix}
+    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
+    %     & t^2 \\
+    %     & & t \\
+    %     & & & t 
+    % \end{bmatrix}    
+    % \]
 \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
@@
     Note that the fibre $  \TT^{\mu_1, \mu_2,+}_{0,0}$ is the same as the intersection of $ T^\mu $ with the strictly upper triangular matrices.
+
+    $\UU_{0,0}$ entries look like 
+    \[
+        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
+            0 & 1 & 0 & 0 & 0\\
+            0 & 0 & 1 & 0 & 0\\
+            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
+            0 & 0 & 0 & 0 & 1\\
+            0 & 0 & 0 & 0 & 0
+            \end{BMAT}\right]    \mapsto 
+            \left[\begin{array}{rr}
+                t^{3} & 0 \\
+                -A_{12}^2 t - A_{12}^1 & t^{2}
+            \end{array}\right]
+    \]
+    $\UU$ entries look like 
+    \[
+        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
+            0 & 1 & 0 & 0 & 0 & 0\\
+            0 & 0 & 1 & 0 & 0 & 0\\
+            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
+            0 & 0 & 0 & 0 & 1 & 0\\
+            0 & 0 & 0 & 0 & s & A_{23}^1\\
+            0 & 0 & 0 & 0 & 0 & s
+            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
+    \]
 

### 2021-02-23 sage/slicy.py

@@ -11,6 +11,7 @@ def mvy(blocktype):
     # N = sum(blocktype[i] for i in range(numblocks))
     indices = [(a,b,k) for a in range(numblocks-1) for b in range(a+1,numblocks) for k in range(blocktype[b])]
     stars = list(var('A_%d' % (i)) for i in range(len(indices)))
+    # stars = list(var('A_%s' % (str(indices[i]))) for i in range(len(indices)))
     D = [jordan_block(0,blocktype[i]) for i in range(numblocks)]
     # T = block_diagonal_matrix(D)
     P = PolynomialRing(QQ,stars)

### 2021-02-23 sage/roger.py
changed some ^ to ** in rogers code

@@ -1,0 +1,269 @@
+# !/opt/sage/sage -python
+
+# Given a sequence $\mu = (\mu_0,\ldots,\mu_m-1)\vdash N$ we wish to output an N by N matrix which takes the form that is predicted by the 
+from sage.all import *
+
+# x = var('x')
+
+n = max(len(t1.weight()),len(t2.weight()))
+
+def get_lambda(n,t1,t2):
+	lambda_1 = [0]*n
+	lambda_2 = [0]*n
+	for i in range(0,len(t1)):
+		lambda_1[i] = len(t1[i])
+	for i in range(0,len(t2)):
+		lambda_2[i] = len(t2[i])
+	return lambda_1, lambda_2
+
+def get_mu(n,t1,t2):
+	mu_1 = [0]*n
+	mu_2 = [0]*n
+	for i in t1:
+		for j in i:
+			mu_1[j-1] += 1
+	for i in t2:
+		for j in i:
+			mu_2[j-1] += 1
+	mu = [a+b for a,b in zip(mu_1,mu_2)] # zip creates tuples out of inputs
+	return mu_1, mu_2, mu
+
+def create_ring(n,t1,t2,mu):
+	vari = []
+	for k in range(1, len(mu)):
+		for i in range(k+1, len(mu)+1):
+			for j in range(0, mu[i-1]):
+				vari.append('x_{}_{}_{}'.format(k,i,j+1))
+	vari.append('s')
+	R = PolynomialRing(QQ, vari)
+    # TODO: try with ZZ/big prime
+	R.inject_variables() # this creates the variables 
+	return R, vari
+
+# insert select rows to a zero matrix 
+def insert_r(M,k,row):
+	return matrix(M.rows()[:k]+[row]+M.rows()[k:])
+
+# create select nonzero rows 
+def create_upper_row_matrix(mu,row,R,vari):
+	mat = []
+	for j in range(row, len(mu)):
+		m = matrix(R,mu[row-1]-1,mu[j])
+		v = [var(v) for v in vari if v.startswith('x_{}_{}'.format(row,j+1))]
+		d = insert_r(m,m.nrows(),v)
+		mat.append(d)
+	return mat
+
+# create weakly upper triangular mu slice block matrix
+def create_matrix(mu_1,mu_2,mu,R,vari):
+	mat = []
+	for i in range(0, len(mu)):
+		row = [] + [0]*i
+		p = x**(mu_1[i])*(x-s)**(mu_2[i])
[…]

### 2021-02-24 draft.tex

@@
     \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here?}
-    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the \ul{Harder--Narasimhan filtration of $V$ at $ \infty$}.
+    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
 The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.
+
     \acom{que est-ce?} \jcom{It's not very relevant for this paper.
@@
 Maybe ``preserves'' is not the best word above.}
+    % A: Ok thanks!
 
@@
 
-    \item Fix the ``\mu-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$.
+    \item Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$.
 The Mirkovic--Vybnornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that
@@
         \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_s \rightarrow \Grth^+$
+        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
         \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$ \acom{why no $G(\CC[t])$-coset?}
-        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
     \end{enumerate}
 \end{lemma}
+
+\begin{proof}
+First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\CC[[t]])t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$.
+
+    Now assume that $ L $ lies in the image of the map from $ \Gr^{\lambda_1, \lambda_2}_s$.
+We know that $ L(0) \in \Gr^{\lambda_1}, L(s) \in \Gr^{\lambda_2} $.
+This means that $t $ acting on $ \CC[[t]]^m / L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on $ \CC[[t-s]]^m / L(s) $ has Jordan type $ \lambda_2$.
+Now, the map $ L_0 / L \rightarrow \CC[[t]]^m / L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \CC[[t]]^m / L(0)$.
+This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).
+
+    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} $ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1} $ since $ (t-s)^{\lambda_2} \in G(\CC[[t]])$.
+In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
+\end{proof}
 
@@
         \item $ L \in \cW_\mu$.
-        \item $ \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
+                \item $ L = Span_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1} p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
+        \item $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
+
     \end{enumerate}
@@
 
-Since the above basis will occur often, we will denote it  $ \beta_\mu$.
+\begin{proof}
+    Let $ L \in \cW_\mu$.
+Then $ L = Span_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \CC[[t^{-1}]]$.
+Since $ L \in \Grth $, we see that $ v_i \in L_0$ which mean that $ p_{ij} := q_{ij}t^{\mu_i} \in \CC[t]$.
+If $ \mu_j < \mu_i$, then we can alter this basis to $ v'_i = v_i - r v_j$ for some polynomial $r \in \CC[t]$ and thus ensure that $ p_{ij} $  has degree less than $ \min(\mu_i, \mu_j)$.
+Thus (i) implies (ii).
+
+    Suppose that $ L = Span_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in Span_\CC(\beta_\mu) $
+in $ L_0/L$.  For this, we can deduce that $ \beta_\mu$ forms a basis for $ L_0/L$.  Hence (ii) implies (iii).  
+    Finally, if we know that $ \beta_\mu $ forms a basis, then $ v_i := t^{\mu_i} e_i - \sum_{j=1} p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \mu_j $.
+It is easy to see that $ L = Span_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.
+    \end{proof}
 
@@
 \end{lemma}
+
+\begin{proof}
+    Let $ L $ lie in this image.
+Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ from some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.
+Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.
+Note that $ h \in T_1\CC([[t^{-1}]])$.
+Then,
+    $$ L = h (h^{-1} g h) t^{\mu}$$
+    Note that $ h^{-1} g h \in N(\CC((t^{-1})))$ and from KWWY \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.
+    \end{proof}
 
@@
 \acom{Your paper with Sabin??}
+\jcom{I took at a look at Mirkovic-Vybornov (both versions) and at my paper with Sabin.
+In Mirkovic-Vybornov, there is nothing about the image of the map.
+In the paper with Sabin, we describe the image as $ L \subset L_0$, $[e_1], \dots $ forms a basis and $ z^{\mu_i} e_i \in W_{\mu_i} + L$.
+I don't know why I put that third condition.
+It seems automatic to me, since from the ``basis'' condition we know that $ W_{\mu_i} + L = L_0$.
+Anyway, I think that I will try to write out the proof again for this paper.}
 

### 2021-02-24 draft.tex
Updates from Overleaf

@@
     % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
-    In pictures, aka by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
+    In pictures, the elements $A$ look like 
     \[
@@
     \]
-    Smaller: 
-    \[
-        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
-            0 & 1 & 0 & 0 & 0\\
-            0 & 0 & 1 & 0 & 0\\
-            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
-            0 & 0 & 0 & 0 & 1\\
-            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
-            \end{BMAT}\right]    
-            \mapsto 
-            \left[\begin{array}{rr}
-                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
-                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
-            \end{array}\right]
-    \]
     % 
@@
        \begin{equation}
-            g(A)_{ij} = 
-            \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
-                % \text{ if $ i = j$} \\
-             - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
-            %  \text{ if $ i \ne j$ }
+            g(A)_{ij} = \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i = j$} \\
+             - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i \ne j$ }
         \end{cases}
@@
     where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
-    For example, the $A$ above will define 
-    % \acom{the transpose of! TODO. Had script?}
-    % \[
-    % \begin{bmatrix}
-    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
-    %     & t^2 \\
-    %     & & t \\
-    %     & & & t 
-    % \end{bmatrix}    
-    % \]
 \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
@@
     Note that the fibre $  \TT^{\mu_1, \mu_2,+}_{0,0}$ is the same as the intersection of $ T^\mu $ with the strictly upper triangular matrices.
-
-    $\UU_{0,0}$ entries look like 
-    \[
-        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
-            0 & 1 & 0 & 0 & 0\\
-            0 & 0 & 1 & 0 & 0\\
-            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
-            0 & 0 & 0 & 0 & 1\\
-            0 & 0 & 0 & 0 & 0
-            \end{BMAT}\right]    \mapsto 
-            \left[\begin{array}{rr}
-                t^{3} & 0 \\
-                -A_{12}^2 t - A_{12}^1 & t^{2}
-            \end{array}\right]
-    \]
-    $\UU$ entries look like 
-    \[
-        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
-            0 & 1 & 0 & 0 & 0 & 0\\
-            0 & 0 & 1 & 0 & 0 & 0\\
-            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
-            0 & 0 & 0 & 0 & 1 & 0\\
-            0 & 0 & 0 & 0 & s & A_{23}^1\\
-            0 & 0 & 0 & 0 & 0 & s
-            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
-    \]
 

### 2021-02-24 draft.tex
mtg chgs begun to lunch break

--- 2021-02-24 draft.tex
@@
 
-Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
-% are there other possibilities?? :S 
-Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.
-The dominant coweights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
-We also need the notion of effective dominant coweight,
-% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
-which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
-So an effective dominant coweight $ \lambda $ is a partition of $ \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
-Write $P_+$ for dominant and $P_{++}$ for effective dominant.
+\subsection{Rings and discs}
 
 Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$ \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?} \jcom{That wouldn't quite make sense.
-Maybe this would be the place to define these disks $D_\infty$ and then we could say the function field of the disk.}
+We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$ \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?}
+\jcom{That wouldn't quite make sense.  Maybe this would be the place to define these disks $D_\infty$ and then we could say the function field of the disk.} 
 % TODO: given by or described by?
@@
 
+Set $\PP = \PP^1$. We will study formal spectra of $R$ and $K$ as formal disks in $\PP$. \acom{TODO: talk about discs.}
+
+\subsection{Groups}
+
 We will also study the affine space of $m\times m$ matrices which we denote $ M_m$.
+
+Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
+% are there other possibilities?? :S 
+Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.
+The dominant coweights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
+We also need the notion of effective dominant coweight,
+% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
+which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
+So an effective dominant coweight $ \lambda $ is a partition of $ \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
+Write $P_+$ for dominant and $P_{++}$ for effective dominant.
+
 % nicematrix test
@@
 \label{ss:lat}
-We will use the lattice model, so it is useful to recall the following definition.
-Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field \acom{When is $K$ not a field?}).
-Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and consider $ K^m $ as a $K$-module.
-By restriction $ K^m$ can be viewed as an $R$-module.
-An $R$-lattice in $M$ \acom{what is $M$?
-should be $K^m$?} is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.
+We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field 
+% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
+Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
+% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
+is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.
 Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.
+\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} \acom{Roger proved it.}
+% is this true?
 
 % The trivial lattice is 
-$L_0(R) = R^m \subset K^m $ is called the standard lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
+$L_0 = L_0(R) = R^m \subset K^m $ is called the standard lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
 % the set of such lattices 
-this set and $\GL_m(K)/\GL_m(R)$.
+this set and $\GL_m(K)/\GL_m(R)$. \acom{Maybe abuse notation and warn the reader.}
 
@@
 $$
-L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
+% L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
+L(a) := L \otimes_{\CC[t]} \cO_a \subset \cK_a^m\,.
 $$
-We say that $ L $ is trivial at $ a $ if $ L(a) = \CC\xt[t-a]^m$. \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
+We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
+% \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
 For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.
@@
 \subsection{Affine Grassmannians} %  actors
-
-Set $\AA = \AA^1$ and $\PP = \PP^1$.
+% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
+% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
+Set $\AA = \AA^1$.
 
@@
     $$
-    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \rightarrow V_0 $ on $ D_0 \setminus \{0\} $} \} 
+    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \} 
     $$
@@
     % 
-    \item For any $ s \in \CC $, \acom{should it be $\AA$ instead of $\CC$} the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
+    \item For any $ s \in \CC $, 
+    % \acom{should it be $\AA$ instead of $\CC$} 
+    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
     $$
-    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \rightarrow V_0 $ on $ D_s \setminus \{s\} $} \} 
+    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \} 
     $$
-    where $D_s$ is the formal disk centered at $s\in\PP$.
+    where $D_s$ is the formal disk centered at $s$ viewed as an element of $\PP$.
 
@@
     $$
-        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
+        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
     $$
@@
 
-    \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?
+    % \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?
 Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?} \jcom{That's a good point!
@@
         \left\{ 
-            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \rightarrow V_0 \text{ on } \PP \setminus \{0, s\}  
+            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} V_0 \text{ on } \PP \setminus \{0, s\}  
         \right\} 
@@
 
-    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by
+    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{why do we have the $s\ne 0$ restriction here}
     % 
     $$ 
-    \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,.
+    \Gr_{0,s} = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
     $$
@@
     \Grbd = 
-    \{ L \subset  \CC(t)^m, s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
+    \{ (L,s) :
+    % s\in\AA,\,
+    % L \subset  \CC(t)^m, s \in \AA 
+    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
     % , $L$ is 
-    trivial at any $ a \ne 0, s$} \} \\
      \Gr_{0,s} = 
@@
     \end{gather*}%}
-    \acom{$s\in\CC$ should be $s\in\AA$?}
-    \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
+    \acom{We do not consistently specify where $s$ is in these definitions}
+    % \acom{$s\in\CC$ should be $s\in\AA$?}
+    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
     % 
@@
 
-    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the standard 
+    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the (relevant?) standard lattice. 
     % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
@@
     % \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
-    lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$. % , i.e. $ L \subseteq L_0$.
+    % lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.
 \end{itemize}
+% \acom{enumerate the points for now}
+These different versions of the affine Grassmannian are related as follows.
 
-These \acom{which?} different versions of the affine Grassmannian are related as follows.
-
-First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \cK \cong \Ks$.
-
-Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
+\begin{enumerate}
+    \item First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \cK \cong \Ks$.
+    \item Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
     % $$ \Grbd \rightarrow \Grth $$ 
@@
     Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
-
-The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
+    \item The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
     $$
@@
     $$
-In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializating to the appropriate disks.  
+    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializing to the appropriate disks.  
     In the lattice realization, it is given by forming tensor products 
@@
     % \acom{Ok. Question: how is the isomorphism given at $s=0$?}
-\acom{Ok. TODO.}
+    \acom{Ok.
+TODO.
+Also write this in group theoretic terms.
+Probably $[g] \mapsto ([g],[g])$ is ok.
+Since $g\CC[t]\otimes_{\CC[t]}\cO_s \cong g\cO_s $ for some reason, where $g\in\CC[t,t^{-1},(t-s)^{-1}]$ can be viewed as $g\in\cK_s$.}
 
@@
     \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
+\end{enumerate}
 
@@
 % Via \ul{this} \acom{rather, the above? $L\mapsto (L(0),L(s))$} 
-Next, using the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
+Next, using the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $, 
+for each $ s \ne 0$,  
+\rcom{usually written $\Gr_{0,\AA^\times} \cong \Gr \times \Gr_s \times \AA^\times$, cite MVi} 
+we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
 % =======
@@
 
+\acom{We will write only coset representatives for (orbits of) elements of the various Grassmannians; right cosets will be clear from context.}
+
 % 
@@
     % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
-    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$. In the lattice model, we have
+    \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
+    % In the lattice model, we have %  G(\cO); understood from context 
     $$ 
@@
     % 
-    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast \overline{\Gr}^{\lambda_2}$.
+    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$.
     % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
@@
     whose lattice description is given in \Cref{le:Grl1l2} below.
-    \acom{Why $G(\CC[t])$}
+    \acom{Why $G(\CC[t])$. Because we are on the left side!}
 
     \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
-    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here?}
+    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $t^\mu L_0(R)$. Or just use $t^\mu$.}
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.

### 2021-03-01 draft.tex
some comments from anne and roger

@@
 Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$ \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?}
-\jcom{That wouldn't quite make sense.  Maybe this would be the place to define these disks $D_\infty$ and then we could say the function field of the disk.} 
+We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$.
+
+% \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?} 
+\jcom{That wouldn't quite make sense.  Maybe this would be the place to define these discs $D_\infty$ and then we could say the function field of the disc.} 
 % TODO: given by or described by?
 %
+
 Note that (by changing the local coordinate on $\spec\CC[t]$ to $t-s$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.
@@
 
-Set $\PP = \PP^1$. We will study formal spectra of $R$ and $K$ as formal disks in $\PP$. \acom{TODO: talk about discs.}
+\acom{Set $\PP = \PP^1$. We will study formal spectra of $R$ and $K$ as formal discs in $\PP$.}
+% \acom{TODO: talk about discs.}
 
@@
 Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  
-The dominant coweights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
+\acom{This assumes $G$ is defined over $\CC$ right?} 
+Under this isomorphism the dominant coweights of $ G $ 
+% is
+are identified with the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
 We also need the notion of effective dominant coweight, 
@@
 which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
-So an effective dominant coweight $ \lambda $ is a partition of $ \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
+So an effective dominant coweight $ \lambda $ is a partition of $|\lambda| = \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
 Write $P_+$ for dominant and $P_{++}$ for effective dominant.
@@
 \label{ss:lat}
-We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field 
+We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field). 
 % \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
@@
 Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.
-\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} \acom{Roger proved it.}
+
+\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
+\acom{Roger has proved that what is written is ok.}
 % is this true?
@@
 % The trivial lattice is 
-$L_0 = L_0(R) = R^m \subset K^m $ is called the standard lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
+$ L_0(R) = R^m \subset K^m $ is called the standard lattice. 
+We will abuse notation and dentoe $L(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
+The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
 % the set of such lattices 
-this set and $\GL_m(K)/\GL_m(R)$. \acom{Maybe abuse notation and warn the reader.}
+this set and $\GL_m(K)/\GL_m(R)$. 
+% \acom{Maybe abuse notation and warn the reader.}
+\acom{is it clear that $\GL(R^m) \le \GL(K^m)$ is normal?}
 
@@
 For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$. 
+\acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}
 
@@
     $$
-    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disk centered at $ 0 \in \PP$.
+    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disc centered at $ 0 \in \PP$.
 
@@
     $$
-    where $D_s$ is the formal disk centered at $s$ viewed as an element of $\PP$.
+    where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
 
@@
     $$
-        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
+        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \} % (a disc centered at $ \infty$)
     $$
-    where $D_\infty$ denotes a disk centered at $ \infty$. 
-    % \acom{What is the difference between ``a disk'' and ``the formal disk''} \jcom{No difference.}
+    where $D_\infty$ denotes a disc centered at $ \infty$. 
+    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}
 
@@
     \Grth = \{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \}\,.
-    $$ % \CC((t^{-1}))^m
+    $$ % \CC\xT[t^{-1}]^m
 
@@
     $$
-    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializing to the appropriate disks.  
+    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializing to the appropriate discs.  
     In the lattice realization, it is given by forming tensor products 
@@
     \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
-    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $t^\mu L_0(R)$. Or just use $t^\mu$.}
+    \acom{want $\TT_\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $\TT_\mu L_0(R)$. Or just use $\TT_\mu$.}
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
@@
 
-    \item The ``upper-triangular'' MVy slice $\TT^{\mu_1, \mu_2,+}_\AA \rightarrow \AA $, defined by
+    \item The ``upper-triangular'' MVy slice $\UU^{\mu_1, \mu_2}_\AA \rightarrow \AA $, defined by
     $$
-    \TT^{\mu_1, \mu_2,+}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
+    \UU^{\mu_1, \mu_2}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
     $$
-    So a matrix in $\TT^{\mu_1, \mu_2,+}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.
+    So a matrix in $\UU^{\mu_1, \mu_2}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.
 
-    Note that the fibre $  \TT^{\mu_1, \mu_2,+}_{0,0}$ is the same as the intersection of $ T^\mu $ with the strictly upper triangular matrices.
+    Note that the fibre $  \UU^{\mu_1, \mu_2}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the strictly upper triangular matrices.
 
@@
         \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
-        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$ \acom{why no $G(\CC[t])$-coset?}
+        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$ 
+        % \acom{why no $G(\CC[t])$-coset?}
     \end{enumerate}
@@
 \begin{proof}
-First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\CC[[t]])t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$.
+First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\CC\xt)t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$.
 
@@
 We know that $ L(0) \in \Gr^{\lambda_1}, L(s) \in \Gr^{\lambda_2} $.
-This means that $t $ acting on $ \CC[[t]]^m / L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on $ \CC[[t-s]]^m / L(s) $ has Jordan type $ \lambda_2$.
-Now, the map $ L_0 / L \rightarrow \CC[[t]]^m / L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \CC[[t]]^m / L(0)$.
+This means that $t $ acting on $ \CC\xt^m / L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on $ \CC\xt[t-s]^m / L(s) $ has Jordan type $ \lambda_2$.
+Now, the map $ L_0 / L \rightarrow \CC\xt^m / L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \CC\xt^m / L(0)$.
 This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).
 
-    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} $ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1} $ since $ (t-s)^{\lambda_2} \in G(\CC[[t]])$.
+    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} $ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1} $ since $ (t-s)^{\lambda_2} \in G(\CC\xt)$.
 In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
@@
         \item $ L \in \cW_\mu$.
-                \item $ L = Span_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1} p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
+                \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1} p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
         \item $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
@@
     Let $ L \in \cW_\mu$.
-Then $ L = Span_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \CC[[t^{-1}]]$.
+Then $ L = \Sp_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \CC\xt[t^{-1}]$.
 Since $ L \in \Grth $, we see that $ v_i \in L_0$ which mean that $ p_{ij} := q_{ij}t^{\mu_i} \in \CC[t]$.
@@
 
-    Suppose that $ L = Span_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in Span_\CC(\beta_\mu) $
+    Suppose that $ L = \Sp_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in \Sp_\CC(\beta_\mu) $
 in $ L_0/L$.  For this, we can deduce that $ \beta_\mu$ forms a basis for $ L_0/L$.  Hence (ii) implies (iii).  
     Finally, if we know that $ \beta_\mu $ forms a basis, then $ v_i := t^{\mu_i} e_i - \sum_{j=1} p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \mu_j $.
-It is easy to see that $ L = Span_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.
+It is easy to see that $ L = \Sp_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.
     \end{proof}
@@
 Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.
-Note that $ h \in T_1\CC([[t^{-1}]])$.
+Note that $ h \in T_1\CC(\xt[t^{-1}])$.
 Then,
     $$ L = h (h^{-1} g h) t^{\mu}$$
-    Note that $ h^{-1} g h \in N(\CC((t^{-1})))$ and from KWWY \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.
+    Note that $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ and from KWWY \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.
     \end{proof}
@@
 \begin{theorem} 
-The map $ T_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
+The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
 $$ L \mapsto [t|_{L_0/L} ]_{\beta_\mu}$$
@@
 I don't know why I put that third condition.
-It seems automatic to me, since from the ``basis'' condition we know that $ W_{\mu_i} + L = L_0$.
+It seems automatic to me, since from the ``basis'' condition we know that $W_{\mu_i} + L = L_0$.
 Anyway, I think that I will try to write out the proof again for this paper.}
+\acom{Rather $(\sum W_{\mu_i} )+ L = L_0$? But yes we agree that the basis assumption is enough. Can try to prove by induction?}
 
@@
 
-In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T^\mu$, using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
+In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu$, using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
 
@@
     There is an isomorphism
-    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \cong \overline{Gr}^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \cong \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
     given by $ (A,s) \mapsto (g(A), s)$.
@@
     The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
-    $$ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T^{\mu_1, \mu_2, +}_\AA \cong \overline{Gr}^{\lambda_1, \lambda_2}_\AA \cap S^{\mu_1, \mu_2}_\AA$$
+    $$ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \UU^{\mu_1, \mu_2}_\AA \cong \overline{\Gr}^{\lambda_1, \lambda_2}_\AA \cap S^{\mu_1, \mu_2}_\AA$$
 \end{theorem}
@@
 It is enough to prove that for $ A \in \OO^{\lambda_1, \lambda_2}_s \cap \TT_\mu $, $g(A) \in S^{\mu_1, \mu_2}_s $ if and only if $ A \in T^+$.
-It is easy to show that if $ A \in T^+$, then $ g(A) \in S^{\mu_1, \mu_2}_s $.
+It is easy to show that if $ A \in \UU$, then $ g(A) \in S^{\mu_1, \mu_2}_s $.
 But the converse is not so obvious.
-(I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu_1, \mu_2}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu_1, \mu_2}$ and $ T^+ $ as attracting sets for a $\CC^\times$ action.
+(I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu_1, \mu_2}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu_1, \mu_2}$ and $\UU$ as attracting sets for a $\CC^\times$ action.
 Which do you prefer?}
-
+% 
+\acom{Assuming Theorem 2 we think this follows by application of Roger's lemma. Also, I think my thesis is complete on this point.}
+% 
 \section{Falling Action} % Resolution
@@
     To see this, note that there is a natural isomorphism
-    $$\CC[[t]]^m/(L \otimes_{\CC[t]} \CC[[t]]) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
+    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
     carrying the action of $t $ to the action of $t$.
@@
     The left hand side is the same thing as
-    $$ \CC[[t]]^m / (L \otimes_{\CC[t]} \CC[[t]]) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC[[t]] $$
+    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
 
@@
 $$
-\cW_\mu^s = G_1[[t^{-1}]]t^\mu \cap G[t,t^{-1}, (t-s)^{-1}] / G[t]
+\cW_\mu^s = G_1\xt[t^{-1}]\TT_\mu \cap G[t,t^{-1}, (t-s)^{-1}] / G[t]
 $$
-where we regard $G[t,t^{-1}, (t-s)^{-1}] / G[t] \subset G((t^{-1}))/G[t] $
+where we regard $G[t,t^{-1}, (t-s)^{-1}] / G[t] \subset G\xT[t^{-1}]/G[t] $
 
@@
 \begin{split}
-    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
-     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
-     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
-     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
-     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
-     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
+    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
+     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
+     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
+     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
+     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
      & = W_{\mu_1 + \mu_2}
@@
 \]
-where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
+where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
 \[
@@
 1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
-\in B_1[[t^{-1}]].
+\in B_1\xt[t^{-1}].
 \]

### 2021-03-01 draft.tex
Updates from Overleaf

--- 2021-02-24 draft.tex
@@
 \jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} \acom{Roger proved it.}
+\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$.
+Since $L\otimes K = K^m$, these also generate $K^m$ over $K$.
+Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$.
+Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis.
+I think the only thing that is needed is that the rings are commutative.}
 % is this true?
@@
 
-    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{why do we have the $s\ne 0$ restriction here}
+    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{Why do we have the $s\ne 0$ restriction here? We use $\Gr_{0,0}$ later.}
     % 
@@
 
-\acom{We will write only coset representatives for (orbits of) elements of the various Grassmannians; right cosets will be clear from context.}
+We will write only coset representatives for (orbits of) elements of the various Grassmannians; right cosets will be clear from context.
 
@@
     $$ 
-    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
+    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure % L_\lambda
     $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
-    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
+    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
     This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
@@
     whose lattice description is given in \Cref{le:Grl1l2} below.
-    \acom{Why $G(\CC[t])$. Because we are on the left side!}
+    % \acom{Why $G(\CC[t])$. Because we are on the left side!}
 
-    \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
-    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $t^\mu L_0(R)$. Or just use $t^\mu$.}
+    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $. % L_\mu
+    % \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $t^\mu L_0(R)$. Or just use $t^\mu$.}
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
@@
     % A: Ok thanks!
+    \acom{c.f.\ the lattice description for the ordinary $\Gr$. 
+    $$G_1[t^{-1}] t^\mu = \{L\in \Gr : L = \Sp_{\cO}(v_1,\dots,v_m) \text{ such that }  v_j = t^{\mu_j} e_j + \sum p_{ij} e_i \text{ with  } \deg p_{ij} < \mu_j \}$$}
 
-    \item The semi-infinite orbit $ S^\mu = N(\cK)L_\mu \subset \Gr $.  
-    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
+    \item The semi-infinite orbit $ S^\mu = N(\cK) t^\mu \subset \Gr $. % L_\mu  
+    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  
+    If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
     $$
-    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
+    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
     $$
 %    \acom{should be $G(\cO)$-coset or $G(\CC[t])$-coset?}
-\jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
+\jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.} \acom{Unless we need to describe the corresponding lattice?}
     On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$.
@@
 \acom{$s\in\AA$?}
+    \end{itemize}
     % 
-    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda_1), (s,\lambda_2))$ if its matrix representatives lie in $ \OO^{\lambda_1, \lambda_2}_{0,s}$.
+    A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda_1), (s,\lambda_2))$ if its matrix representatives lie in $ \OO^{\lambda_1, \lambda_2}_{0,s}$.
     % 
+    \begin{itemize}
     \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.
@@
 In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}
+
+    \acom{\ul{see what} \cite{weyman1989equations} does.}
 
@@
 
-    \item The ``upper-triangular'' MVy slice $\TT^{\mu_1, \mu_2,+}_\AA \rightarrow \AA $, defined by
+    \item The ``upper-triangular'' MVy slice $\UU^{\mu_1, \mu_2}_\AA \rightarrow \AA $, defined by \acom{maybe can do without 0 subscript on $\UU$, adding in for analogy}
     $$
-    \TT^{\mu_1, \mu_2,+}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
+    \UU^{\mu_1, \mu_2}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
     $$
-    So a matrix in $\TT^{\mu_1, \mu_2,+}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.
+    So a matrix in $\UU^{\mu_1, \mu_2}_{0,\AA}  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.
+The fibre over $s$ is denoted by $\UU^{\mu_1, \mu_2}_{0,s}$.
 
-    Note that the fibre $  \TT^{\mu_1, \mu_2,+}_{0,0}$ is the same as the intersection of $ T^\mu $ with the strictly upper triangular matrices.
+    Note that the fibre $  \UU^{\mu_1, \mu_2}_{0,0}$ is the same as the intersection of 
+    % $ T^\mu $ % TODO: we mean TT_\mu right?
+    $\TT_\mu$ with the strictly upper triangular matrices.
 
-    $\UU_{0,0}$ entries look like 
+    $\UU^{\mu_1,\mu_2}_{0,0}$ entries look like 
     \[
@@
             0 & 0 & 0 & 0 & 0
-            \end{BMAT}\right]    \mapsto 
-            \left[\begin{array}{rr}
-                t^{3} & 0 \\
-                -A_{12}^2 t - A_{12}^1 & t^{2}
-            \end{array}\right]
+            \end{BMAT}\right]    \in \UU^{(3,2)}_{0,0}
+            % \mapsto 
+            % \left[\begin{array}{rr}
+            %     t^{3} & 0 \\
+            %     -A_{12}^2 t - A_{12}^1 & t^{2}
+            % \end{array}\right]
     \]
-    $\UU$ entries look like 
+    $\UU^{\mu_1,\mu_2}_{0,s}$ entries look like 
     \[

### 2021-03-03 draft.tex
Pseudocode and updated examples.

--- 2021-03-01 draft.tex
@@
 \author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
-\date{October 2020}
+% \date{October 2020}
+\date{\today}
 
@@
 \acom{Roger has proved that what is written is ok.}
+\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear we that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$.
+Since $L\otimes K = K^m$, these also generate $K^m$ over $K$.
+Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$.
+Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis.
+I think the only thing that is needed is that the rings are commutative.}
 % is this true?
@@
 % \acom{Maybe abuse notation and warn the reader.}
-\acom{is it clear that $\GL(R^m) \le \GL(K^m)$ is normal?}
+% \acom{is it clear that $\GL(R^m) \le \GL(K^m)$ is normal?} \jcom{It isn't normal and the quotient is not a group.}
 
@@
 \begin{proof}
-First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\CC\xt)t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$.
+First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\cO)t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$.
 
-    Now assume that $ L $ lies in the image of the map from $ \Gr^{\lambda_1, \lambda_2}_s$.
+    Now assume that $ (L, s) \in \Gr^{\lambda_1, \lambda_2}_s$.
 We know that $ L(0) \in \Gr^{\lambda_1}, L(s) \in \Gr^{\lambda_2} $.
 This means that $t $ acting on $ \CC\xt^m / L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on $ \CC\xt[t-s]^m / L(s) $ has Jordan type $ \lambda_2$.
-Now, the map $ L_0 / L \rightarrow \CC\xt^m / L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \CC\xt^m / L(0)$.
+Now, the map $ L_0 / L \rightarrow \CC\xt^m / L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.
+The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$.
 This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).
@@
                 \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1} p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
-        \item $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
-
+        \item $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$ and for all $ i $, 
+        $$ t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \min(\mu_i, \mu_j), 1 \le j \le m \}) + L $$.
     \end{enumerate}
 \end{lemma}
+
+\jcom{I realized the meaning of the ``extra'' condition from the paper with Sabin and I added it into point 3.}
 
@@
 Then $ L = \Sp_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \CC\xt[t^{-1}]$.
-Since $ L \in \Grth $, we see that $ v_i \in L_0$ which mean that $ p_{ij} := q_{ij}t^{\mu_i} \in \CC[t]$.
-If $ \mu_j < \mu_i$, then we can alter this basis to $ v'_i = v_i - r v_j$ for some polynomial $r \in \CC[t]$ and thus ensure that $ p_{ij} $  has degree less than $ \min(\mu_i, \mu_j)$.
+Since $ L \in \Grth^+ $, we see that $ v_i \in L_0$ which means that $ p_{ij} := q_{ij}t^{\mu_i} $ lies in $ \CC[t]$.
+By construction, the polynomial $ p_{ij}$ has degree less than $ \mu_i$.
+
+    Fix $ i$ and suppose that for some $ j$, $ \mu_j < \mu_i$.
+In this case, we can alter our basis to $ v'_i = v_i - r v_j$ for some polynomial $r \in \CC[t]$.
+This gives us new polynomials $ p'_{ij} = p_{ij} - r (t^{\mu_j} + p_{jj}) $.
+In this way, we can ensure that $ p_{ij} $ has degree less than $ \min(\mu_i, \mu_j)$.
 Thus (i) implies (ii).
@@
     Suppose that $ L = \Sp_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in \Sp_\CC(\beta_\mu) $
-in $ L_0/L$.  For this, we can deduce that $ \beta_\mu$ forms a basis for $ L_0/L$.  Hence (ii) implies (iii).  
-    Finally, if we know that $ \beta_\mu $ forms a basis, then $ v_i := t^{\mu_i} e_i - \sum_{j=1} p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \mu_j $.
+in $ L_0/L$ and we see that 
+$$t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \mu_i \}) + L $$.
+From this, we can deduce that $ \beta_\mu$ forms a basis for $ L_0/L$.  Hence (ii) implies (iii).  
+    Finally, given (iii), then we can see $ v_i := t^{\mu_i} e_i - \sum_{j=1} p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \min(\mu_i,\mu_j) $.
 It is easy to see that $ L = \Sp_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.
@@
 Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.
-Note that $ h \in T_1\CC(\xt[t^{-1}])$.
+Note that $ h \in T_1(\CC(\xt[t^{-1}]))$.
 Then,
@@
 \section{Climax}
+Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in section ??.
+As $ g(A) \in M_n(\CC[t]) \cap G_1(\CC\xt[t^{-1}])$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
 
-\begin{theorem} 
+The following result in \cite[Theorem 3.2]{cautis2018categorical}.
+
+\begin{theorem} \label{th:TmuWmu}
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
@@
 \end{theorem}
-
-\jcom{Do we have a reference?}
-\acom{Your paper with Sabin??}
-\jcom{I took at a look at Mirkovic-Vybornov (both versions) and at my paper with Sabin.
-In Mirkovic-Vybornov, there is nothing about the image of the map.
-In the paper with Sabin, we describe the image as $ L \subset L_0$, $[e_1], \dots $ forms a basis and $ z^{\mu_i} e_i \in W_{\mu_i} + L$.
-I don't know why I put that third condition.
-It seems automatic to me, since from the ``basis'' condition we know that $W_{\mu_i} + L = L_0$.
-Anyway, I think that I will try to write out the proof again for this paper.}
-\acom{Rather $(\sum W_{\mu_i} )+ L = L_0$? But yes we agree that the basis assumption is enough. Can try to prove by induction?}
 
@@
     There is an isomorphism
-    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \cong \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \cong \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
     given by $ (A,s) \mapsto (g(A), s)$.
 \end{theorem}
+
+\begin{proof}
+Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \text{ if and only if } (g(A), s) \in \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+This follows immediately from Lemma \ref{le:Grl1l2}.
+\end{proof}
 

### 2021-03-09 draft.tex
deleted some discs

@@
 
-Set $\cO = \CC\xt$ and $\cK = \CC\xT$.
-We will also need the notation $\cO_s = \CC\xt[t-s]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$, as well as $\Kinf = \CC\xT[t^{-1}]$.
+Set $\cO = \cO_0 = \CC\xt$ and $\cK = \cK_0 = \CC\xT$.
+% TODO: I rearranged this sentence, because starting it with 'for any other' presupposes we have introduced s 
+%  For any other 
+We will also consider $\cO_s = \CC\xt[t-s]$ and its fraction field $\cK_s=\CC\xT[t-s]$, for any 
+$ s \in \CC\setminus\{0\} $, as well as $ \Oinf = \CC\xt[t^{-1}] $ and $\Kinf = \CC\xT[t^{-1}]$. For any $ s \in \PP = \PP^1$, 
+% TODO: Identifying $s\in\CC$ and the line $s\in\PP$ containing it right?
+$ \cO_s$ is the completion of the local ring $ \mathcal O_{\PP, s} $ and thus the formal spectrum of $ \cO_s$ is the formal neighbourhood $ D_s$ of $ s $ (also called the formal disc centered at $ s$).
+Similarly the formal spectrum of the field $\cK_s$ is the deleted formal neighbourhood (or punctured disc), denoted $ D_s \setminus \{s\} $.
 
-% \acom{for the fraction field of the completion of $\CC[t]$ at $\infty$?} 
-\jcom{That wouldn't quite make sense.  Maybe this would be the place to define these discs $D_\infty$ and then we could say the function field of the disc.} 
-% TODO: given by or described by?
+Note that for $ s \in \CC $, we have an obvious isomorphisms  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$.
+
+\subsection{Groups}
+
+We will also study the affine space of $m\times m$ matrices which we denote $ M_m$.
+
+Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
+% are there other possibilities?? :S 
+Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  
+\acom{This identification assumes we are taking $\CC$ points of $G$ right?
+i.e.\ it's really $P(T(\CC)) = \Hom(\CC^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?}
+Under this isomorphism the dominant coweights of $ G $ 
+% is
+are identified with the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
+We also need the notion of effective dominant coweight, 
+% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
+which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
+So an effective dominant coweight $ \lambda $ is a partition of $|\lambda| = \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
+We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights.
+
+% nicematrix test
+% $\begin{bNiceArray}{ccc|c}[margin]
+%     \Block{3-3}<\Large>{A} & & & 0 \\
+%     & \hspace*{1cm} & & \Vdots \\
+%     & & & 0 \\
+%     \hline
+%     0 & \Cdots& 0 & 0
+%     \end{bNiceArray}$
 % 
+% $\begin{pNiceMatrix}
+%     \frac12 & -\frac12 \\
+%     \frac13 & \frac14 \\
+%     \end{pNiceMatrix}$
 
-Note that (by changing the local coordinate on $\spec\CC[t]$ to $t-s$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.
+% Set $\AA = \AA^1_x$ (the subscript denoting the chosen local coordinate) and fix $s\in \AA - \{0\}$.
 
@@
 
-\acom{Set $\PP = \PP^1$. We will study formal spectra of $R$ and $K$ as formal discs in $\PP$.}
-% \acom{TODO: talk about discs.}
-
-\subsection{Groups}
-
-We will also study the affine space of $m\times m$ matrices which we denote $ M_m$.
-
-Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
-% are there other possibilities?? :S 
-Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  
-\acom{This assumes $G$ is defined over $\CC$ right?} 
-Under this isomorphism the dominant coweights of $ G $ 
-% is
-are identified with the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
-We also need the notion of effective dominant coweight, 
-% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
-which means those $ \lambda $ as above with $ \lambda_m \ge 0$.
-So an effective dominant coweight $ \lambda $ is a partition of $|\lambda| = \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
-Write $P_+$ for dominant and $P_{++}$ for effective dominant.
-
-% nicematrix test
-% $\begin{bNiceArray}{ccc|c}[margin]
-%     \Block{3-3}<\Large>{A} & & & 0 \\
-%     & \hspace*{1cm} & & \Vdots \\
-%     & & & 0 \\
-%     \hline
-%     0 & \Cdots& 0 & 0
-%     \end{bNiceArray}$
-% 
-% $\begin{pNiceMatrix}
-%     \frac12 & -\frac12 \\
-%     \frac13 & \frac14 \\
-%     \end{pNiceMatrix}$
-
-% Set $\AA = \AA^1_x$ (the subscript denoting the chosen local coordinate) and fix $s\in \AA - \{0\}$.
-
 \subsection{Lattices}
@@
 I think the only thing that is needed is that the rings are commutative.}
+\jcom{Great.}
 % is this true?
@@
 $ L_0(R) = R^m \subset K^m $ is called the standard lattice. 
-We will abuse notation and dentoe $L(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
+We will abuse notation and denote $L(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
 The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
@@
 
+\jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
+\acom{Ok.}
+
 \begin{itemize}
@@
     $$
-    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disc centered at $ 0 \in \PP$.
+    where $V_0$ is the trivial rank $m$ vector bundle.
+    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.
 
@@
     $$
-    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \} 
+    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \}\,.
     $$
-    where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
+    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
+    \acom{What about fixing the notation $V_0$ somewhere?}
 
@@
 
+    \begin{remark}
+        Base case $m = 1$: by a slight abuse of notation let $\lambda_1, \lambda_2 \in \NN$. Claim: $J=J_{0,\lambda_1} \oplus J_{s,\lambda_2}$ is conjugate to
+
+% $\begin{pNiceArray}{CC|CC}[first-row,last-row=5,first-col,last-col,nullify-dots]
+% & C_1 & \Cdots & & C_4 & \\
+% L_1 & a_{11} & a_{12} & a_{13} & a_{14} & L_1 \\
+% \Vdots & a_{21} & a_{22} & a_{23} & a_{24} & \Vdots \\
+% \hline
+% & a_{31} & a_{32} & a_{33} & a_{34} & \\
+% L_4 & a_{41} & a_{42} & a_{43} & a_{44} & L_4 \\
+% & C_1 & \Cdots & & C_4 &
+% \end{pNiceArray}$
+\[
+        A = \begin{bNiceArray}{ccc|ccc}[columns-width = auto,first-row,last-col,code-for-first-row = \color{blue}\scriptstyle\rotate,code-for-last-col = \color{blue}\scriptstyle,nullify-dots,xdots/line-style=loosely dotted]
+        1 & \Cdots & \lambda_1 & \lambda_1 + 1 & \Cdots & \lambda_1 + \lambda_2 \\
+        0 & 1 & 0 & 0 & 0 & 0 & 1\\
+        0 & \Ddots & 1 & 0 & 0 & 0 & \Vdots \\
+        0 & 0 & 0 & 1 & 0 & 0 & \lambda_1 \\
+        \hline
+         & & & s & 1 & 0 & \lambda_1 + 1 \\
+         & & & 0 & \Ddots & 1 & \Vdots \\
+         & & & 0 & 0 & s & \lambda_1 + \lambda_2 
+        \end{bNiceArray} 
+\]
+% Denote by $R_i$ the $i$th row of $J$ 
+Let $g = E_{\lambda_2}\cdots E_1$ be the product of elementary matrices $E_i$ which correspond to the elementary row operations 
+$$R_{\lambda_1 + i - 1} \leftarrow R_{\lambda_1 + i-1} + \frac 1s R_{\lambda_1 + i}$$ 
+for $i = 1,\dots,\lambda_2$. Then $gJg^{-1} = A$. For the next part we introduce the notation $A_{\lambda_1+\lambda_2}$ for this matrix $A$.
+
+Now let $\lambda_1,\lambda_2$ be arbitrary. Clearly $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to 
+$$\bigoplus_{i=1}^m (J_{\lambda_{1,i}}\oplus J_{\lambda_{2,i}})\,.$$ 
+Moreover each block $J_{\lambda_{1,i}}\oplus J_{\lambda_{2,i}}$ is conjugate to $A_{\lambda_{1,i}+\lambda_{2,i}}$.
+Altogether $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to $\bigoplus_{i = 1}^m A_{\lambda_{1,i}+\lambda_{2,i}}$ and this latter matrix specializes to the Jordan normal form $J_{0,\lambda_1 + \lambda_2}$ at $s=0$.
+
+% By Tanisaki $A\in \OO^\lambda$ iff the coefficients of $z^m$ in $k\times k$ minors of $zI - A$ for any $m\le p_\lambda(k) - 1$ and for any $k = 1\dots |\lambda|$ vanish.
+Here $p_\lambda(k) = \lambda_{n-k+1} + \cdots + b_n$ and $k = 1,\dots,n$.
+So $p_\lambda(k) = \#$ boxes in the last $k$ rows of $\lambda$.
+
+% In particular this result describes the ideal $I_i$ of $N_i\times N_i$ matrices $A_i$ such that $A_i - \delta_{i,2}s$ is conjugate to $J_{\delta_{i,2} s, \lambda_i}$ for $i = 1,2$.
+Let $A_1,A_2$ be such a pair of matrices.
+Clearly $A_1 \oplus A_2$ is conjugate to $J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.
+Let $g$ be such that $g(J_{0,\lambda_1} \oplus J_{s,\lambda_2})g^{-1} = \bigoplus_{i = 1}^m A_{\lambda_{1,i}+\lambda_{2,i}}$.
+
+% If we apply the change of basis $g$ to the ideal $I=I_1 + I_2$ and set $s = 0$ (if possible) do we recover the ideal of $\OO^{\lambda_1 + \lambda_2}$? Let $A^g = g(A_1 \oplus A_2) g^{-1}$...
+    \end{remark}
+
     \item Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$.
@@
                 \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1} p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
-        \item $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$ and for all $ i $, 
-        $$ t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \min(\mu_i, \mu_j), 1 \le j \le m \}) + L $$.
+        \item  For all $ i $, 
+        $$ t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \min(\mu_i, \mu_j), 1 \le j \le m \}) + L. $$
     \end{enumerate}
+    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$
 \end{lemma}
@@
 in $ L_0/L$ and we see that 
-$$t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \mu_i \}) + L $$.
-From this, we can deduce that $ \beta_\mu$ forms a basis for $ L_0/L$.  Hence (ii) implies (iii).  
+$$t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \mu_i \}) + L $$
+ Hence (ii) implies (iii).  
     Finally, given (iii), then we can see $ v_i := t^{\mu_i} e_i - \sum_{j=1} p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \min(\mu_i,\mu_j) $.
 It is easy to see that $ L = \Sp_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.
+
+    Finally to show that $ \beta_\mu$ forms a basis for $ L_0/L$, it suffices to show that for each $ i$, $ t^\mu_i e_i  \in \Sp_\CC(\beta_\mu) + L$.  This follows immediately from (iii).
+
     \end{proof}
@@
 \begin{proof}
-Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \text{ if and only if } (g(A), s) \in \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \text{ if and only if } (g(A), s) \in \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
 This follows immediately from Lemma \ref{le:Grl1l2}.
@@
 % 
+\jcom{I thought about this and I agree with you now.  I will write this up soon.}
+
+\begin{proof}
+ Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA $ if and only if $ (g(A),s) \in S^{\mu_1, \mu_2}_\AA $.
+
+ On the one hand, if $ (A,s) \UU^{\mu_1, \mu_2}_\AA $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu_1} (t-s)^{\mu_2}$, and so $ g(A) \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+
+ On the other hand, if $ (g(A), s) \in S^{\mu_1, \mu_2}_\AA$, then we can write 
+ $$
+ g t^\mu r= n t^{\mu_1} (t-s)^{\mu_2}
+$$
+for some $ r \in G(\CC[t]), n \in N[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.
+Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1 \CC[[t]]$.
+Note that $ h^{-1}n h \in N((t^{-1}))$, so we can factor it as $ n = n_1 n_2 $, where $ n_1 \in N_1(\CC[[t^{-1}]]), n_2 \in N(\CC[t])$.
+So then after doing a bit of algebra, we reach
+$$
+t^\mu r (t^{-\mu} n_2 t^\mu) t^{-\mu} = g^{-1} h n_1
+$$
+The right hand side $ g^{-1} g n_1 $ lies in$ G_1(\CC[[t^{-1}]]) $.
+Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.
+Moreover since $ \mu $ is dominant, we know that $$t^\mu G(\CC[[t]]) t^{-\mu} \cap G_1(\CC[[t^{-1}]]) = N_1(\CC[[t^{-1}]])$$
+ Thus, we deduce that $ g^{-1} h n_1 \in N_1(\CC[[t^{-1}]])$ and hence $ g(A) \in N_1(\CC[[t^{-1}]]) t^{\mu_1} (t-s)^{\mu_2} $.
+Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \UU^{\mu_1, \mu_2}_\AA$ as desired.
+\end{proof}
+
+\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
+To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.
+In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
+
 \section{Falling Action} % Resolution
@@
 
+\appendix
+\section{Examples}
+\rcom{I have 3 examples in mind right now: fusion product producing 1 term (maybe $1 \leftarrow 2 * 1 \rightarrow 2$), fusion product producing more than 1 term $(S_1 * S_2)$, and fusion product with multiplicities $((S_1 * S_2)^2)$}
+
+We view MV cycles as semi-standard young tableaux.
+Suppose we have two tableaux $\tau_1$ and $\tau_2$ with respective weights $\lambda_i$ and $\mu_i$ and we wished to taked their fusion product.
+We consider a generic matrix $X \in \UU^{\lambda_1,\lambda_2}_{0,s}$.
+
+The subtableaux of $\tau_1$ and $\tau_2$ where we take the first $j$ entries of each $\mu_i$ correspond to the submatrix $X_j$ of $X$ that consists of the first $j$ blocks.
+These subtableaux impose rank conditions, equivalently vanishing minors, on $X_j$ which allows us to deduce relations on the variables in $X$.
+The relations must also include the new variables in the latest block and cannot have $s$ as a factor.
+
+To find the MV cycles, equivalently tableaux, in the $0$-fibre of the fusion, we consider the ring generated by all the variables of $X$ and quotient out the ideal generated by the relations from the vanishing minors as well as the minimal polynomial of $X$.
+We then add $s$ into the ideal.
+Each piece in the primary decomposition of this ideal will correspond to a tableaux, and subsequently a MV cycle.
+
+\begin{example}
+Let $G = SL_3$ and consider the tableaux
+$$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$
+The weights are $\lambda_1 = \lambda_2 = (2,1,0)$ and $\mu_1 = \mu_2 = (1,1,1)$. Hence the matrix in consideration is 
+\[
+X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
+    0 & 1 & & & & \\
+     & s & a_1 & a_2 & b_1 & b_2 \\
+     & & 0 & 1 & & \\
+     & & & s & b_3 & b_4 \\
+     & & & & 0 & 1 \\
+     & & & & & s
+\end{BMAT}
+\right].
+\]
+
+For the first entry of each $\mu_i$, we have the following subtableaux to consider:
+$$\young(1) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1).$$
+Let $X_1$ be the top-left $2 \times 2$ submatrix of $X$. The subtableaux imposes the conditions $\dim \ker X_1 = 1$ and $\dim \ker (X_1-s) = 1$. We see that we do not obtain any relations from this.
+
+For the first two entries of each $\mu_i$, we have the following subtableaux:
+$$\young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1,2).$$
+Let $X_2$ be the top-left $4 \times 4$ submatrix of $X$.
+The left subtableau imposes the conditions $\dim \ker X_2 = 1$ and $\dim \ker X_2^2 = 2$ while the right subtableau imposes the condition that $\dim \ker (X_2 -s) = 2$.
+These conditions force the relation $$a_1 + sa_2 = 0.$$
+
+The original tableaux for $X$ imposes the conditions that $\dim \ker X = 2$, $\dim \ker X^2 = 3$, $\dim \ker (X-s) = 2$, and $\dim \ker (X-s)^2 = 3$. These force the relation $$b_3 = 0.$$
+
+Hence we consider the quotient
+$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,s]}{\langle a_1+sa_2,b_3,s \rangle} \cong
+\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4]}{\langle a_1,b_3 \rangle}.$$
+We see already that the $0$-fibre is irreducible. The tableau corresponding to the ideal $\langle a_1, b_3 \rangle$ is 
+$$\young(1123,23)$$
+which corresponds to the MV cycle that is the cross product of the MV cycles corresponding to $\tau_1$ and $\tau_2$.
+\end{example}
+
 \bibliographystyle{alpha}

### 2021-03-09 draft.tex
minor edits plus commented out nicematrix

@@
 which we will view in $\GL_m(K) $ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it 
+\acom{Add: Warning: We will also view $(t-s)^\mu$ in $\GL_m(K)/\GL_m(R)$. We hope it will be expedient and evident.}
 
@@
 % G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
-Set $\AA = \AA^1$.
+Set $\AA = \AA^1$ \acom{and let $V_0$ denote the trivial vector bundle}.
 
 \jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
-\acom{Ok.}
+\acom{Ok. We could omit the repetitive $X=$ bits from the display styled alternate descriptions. That way they will fit within the margins.}
 
@@
     $$
-    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \} 
-    $$
-    where $V_0$ is the trivial rank $m$ vector bundle.
+    \Gr = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \right\} \,. 
+    $$
+    % where $V_0$ is the trivial rank $m$ vector bundle.
     % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.
@@
     $$ 
-    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}\,.
+    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
     $$
@@
     $$
-    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \}\,.
+    \Gr_s = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \right\}\,.
     $$
     % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
-    \acom{What about fixing the notation $V_0$ somewhere?}
+    % \acom{What about fixing the notation $V_0$ somewhere?}
 
@@
     $$ 
-    \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} \,. 
+    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
     $$   
@@
     $$
-        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \} % (a disc centered at $ \infty$)
-    $$
-    where $D_\infty$ denotes a disc centered at $ \infty$. 
+        \Grth = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
+    $$
+    % where $D_\infty$ denotes a disc centered at $ \infty$. 
     % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}
@@
     $$ 
-    \Grth = \{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \}\,.
+    \Grth = \left\{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \right\}\,.
     $$ % \CC\xT[t^{-1}]^m
@@
     $$%}
-
+    % 
     The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{why do we have the $s\ne 0$ restriction here}
@@
     % 
-    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp.\ are defined as 
+    \item The positive parts, $ \Gr^+$ and ${\Grth}^+$, of the affine Grassmannian and the thick affine Grassmannian, respectively, are defined as 
     % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
     $$
-    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\Kinf) / G(\CC[t]) % \CC\xT[t^{-1}] missed a spot  
+    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. % \CC\xT[t^{-1}] missed a spot  
     $$
     % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}
-
+    % 
     In modular terms, $\Gr^+$ (resp.
@@
 
-    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the (relevant?) standard lattice. 
+    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the \acom{add (relevant)?} standard lattice. 
     % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
@@
     % $$ \Grbd \rightarrow \Grth $$ 
-    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
-    $$
-    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])
+    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by \acom{...inclusion?}
+    $$
+    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,. 
     $$
@@
 Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$. 
+% Coweights define elements in the various affine Grassmannians which we consider.
+Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent.
+% the right cosets which they represent are clear from the context.
+
 \acom{At some point at least mention that we expect this to go through for permutations of $\mu_i\in P_{++}$ i.e.\ skew partitions?
 or non-dominant, but also non-negative weights, so long as $\mu_1 + \mu_2$ is in $P_{++}$}
-
-\acom{We will write only coset representatives for (orbits of) elements of the various Grassmannians; right cosets will be clear from context.}
-
 % 
@@
     $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
-    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
+    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
     This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
@@
 % \end{pNiceArray}$
+\begin{comment}
 \[
@@
 \]
+\end{comment}
 % Denote by $R_i$ the $i$th row of $J$ 

### 2021-03-09 draft.tex
minor updates to draft and sty

@@
 which we will view in $\GL_m(K) $ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it 
-\acom{Add: Warning: We will also view $(t-s)^\mu$ in $\GL_m(K)/\GL_m(R)$. We hope it will be expedient and evident.}
+\acom{Add warning that we will also write $(t-s)^\mu$ for its image in $\GL_m(K)/\GL_m(R)$. We hope it will be evident?}
 
@@
 Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.
-
+% 
+\begin{comment}
 \jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
@@
 \jcom{Great.}
-% is this true?
+\end{comment}
 
@@
 this set and $\GL_m(K)/\GL_m(R)$. 
+\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$.
+If $e_1,\dots,e_m$ denote the standard basis elements of $L_0(\cO)$ then
+$$ 
+L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
+$$}
 % \acom{Maybe abuse notation and warn the reader.}
@@
 % L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
-L(a) := L \otimes_{\CC[t]} \cO_a \subset \cK_a^m\,.
-$$
-We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
+L(a) := L \otimes_{\CC[t]} \cO_a %\,. % The containment is not part of the definition so I comment it out \subset \cK_a^m\,.
+$$
+and if $ L(a) = \cO_a^m$ then $L$ is said to be trivial at $a$. 
+% We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
 % \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
@@
 \jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
-\acom{Ok. We could omit the repetitive $X=$ bits from the display styled alternate descriptions. That way they will fit within the margins.}
+\acom{Ok. We could omit the repetitive ``$X=$'' bits from the display styled alternate descriptions. That way they will fit within the margins.}
 
@@
 
-    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the \acom{add (relevant)?} standard lattice. 
+    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the relevant standard lattice. 
     % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
@@
     % $$ \Grbd \rightarrow \Grth $$ 
-    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by \acom{...inclusion?}
+    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by the inclusion
     $$
@@
 \subsection{Some subvarieties of affine Grassmannians}
-Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$. 
+Now fix effective dominant coweights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$. 
 % Coweights define elements in the various affine Grassmannians which we consider.
@@
 \acom{At some point at least mention that we expect this to go through for permutations of $\mu_i\in P_{++}$ i.e.\ skew partitions?
-or non-dominant, but also non-negative weights, so long as $\mu_1 + \mu_2$ is in $P_{++}$}
+or non-dominant and non-negative coweights; so long as their sum $\mu_1 + \mu_2$ is effective dominant.}
+
+The following subsets are indexed by coweights. 
 % 
@@
     \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
-    % In the lattice model, we have %  G(\cO); understood from context 
     $$ 
@@
     $$ 
-    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
+    \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
+    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
     $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
@@
     By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.
-By Zhu's theorem (\jcom{need ref} \acom{pretty sure it's \cite[Proposition 3.1.14]{zhu2016introduction}}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
+By \cite[Proposition 3.1.14]{zhu2016introduction},
+    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
+    the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
 
@@
     whose lattice description is given in \Cref{le:Grl1l2} below.
-    \acom{Why $G(\CC[t])$. Because we are on the left side!}
-
-    \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
-    \acom{want $\TT_\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $\TT_\mu L_0(R)$. Or just use $\TT_\mu$.}
+    % \acom{Why $G(\CC[t])$. Because we are on the left side!}
+
+    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
+    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?}
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
 The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.
-
-    \acom{que est-ce?} \jcom{It's not very relevant for this paper.
-Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN-filtration; it is a partial flag of subbundles of type determined by $ \mu$.
+    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.
+Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.
 We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.
@@
     % A: Ok thanks!
-
-    \item The semi-infinite orbit $ S^\mu = N(\cK)L_\mu \subset \Gr $.  
+    % 
+    \item The semi-infinite orbit $ S^\mu = N(\cK)t^\mu \subset \Gr $.  
     \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
@@
     $$
-%    \acom{should be $G(\cO)$-coset or $G(\CC[t])$-coset?}
-\jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
+    % TODO: resolve
+    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
     On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
-\acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}
+    % TODO: resolve
+    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}
 
@@
 \subsection{Matrices}
-We now consider some subvarieties of the space of $ N\times N$ matrices.
-
-%Recall that $ \lambda$ is a partition of $N$ and $ \lambda_1, \lambda_2 $ are partitions of $ N_1, N_2$ with $N_1 + N_2 = N$.
+\acom{Keep fixed $\lambda_i,\mu_i,\lambda, \mu$ arbitrary effective dominant coweights and their sums of size $N$ as in the previous section.} We now consider some subvarieties of the space of $ N\times N$ matrices.
 
 \begin{itemize}
-    \item For $ s \in \CC$ and $\lambda\in P_{++}$ we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. \acom{$s\in\AA$?}
+    \item For $ s \in \CC$ 
+    % and $\lambda\in P_{++}$
+    we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. 
+    % \acom{$s\in\AA$?}
     % 
@@
 Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \bigcup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$.
-\acom{$s\in\AA$?}
+    % \acom{$s\in\AA$?}
     % 
@@
     \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.
+
     \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
@@
 
-    \item To each $ A \in \TT_\mu$, we will associate an $m\times m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
-       \begin{equation}
+    \item To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
+    of polynomials 
+    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
+    \begin{equation}
+        \label{eq:mvyofa}
         g(A)_{ij} = 
@@
     % \]
+
     \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
-
-    \item The ``upper-triangular'' MVy slice $\UU^{\mu_1, \mu_2}_\AA \rightarrow \AA $, defined by
+    \acom{Ok.}
+
+    \item The ``upper-triangular'' \mvy slice $\UU^{\mu_1, \mu_2}_\AA \rightarrow \AA $, defined by
     $$
@@
     $$
-    So a matrix in $\UU^{\mu_1, \mu_2}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.
-
-    Note that the fibre $  \UU^{\mu_1, \mu_2}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the strictly upper triangular matrices.
+    So a matrix in $\UU^{\mu_1, \mu_2}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).
+
+    Note that the fibre $  \UU^{\mu_1, \mu_2}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.
 
@@
             0 & 0 & 0 & 0 & 0
-            \end{BMAT}\right]    \mapsto 
-            \left[\begin{array}{rr}
-                t^{3} & 0 \\
-                -A_{12}^2 t - A_{12}^1 & t^{2}
-            \end{array}\right]
+            \end{BMAT}\right]    
+            % \mapsto 
+            % \left[\begin{array}{rr}
+            %     t^{3} & 0 \\
+            %     -A_{12}^2 t - A_{12}^1 & t^{2}
+            % \end{array}\right]
     \]
-    $\UU$ entries look like 
+    $\UU^{\mu_1, \mu_2}_\AA$ entries look like 
     \[
@@
 
-    \jcom{Instead of $\TT^+$ maybe a different letter would be best?
+    % \jcom{Instead of $\TT^+$ maybe a different letter would be best?
 I'm moved all $\lambda, \mu$ to upper indices for consistency (except for $ \cW_\mu, \TT_\mu$) and also to let us put $ s $ or $ \AA$ in the lower index.
@@
 Which do you prefer?}
-
-    \acom{Maybe $\UU$ for a different letter?
+    % 
+    % \acom{Maybe $\UU$ for a different letter?
 And, I guess we do not need $\AA$ but it is a nice letter to have around.
 It also serves to distinguish the $\CC$ over which $R,K$ are defined from the $\AA$ over which $\Grbd$ is defined?}
-    \jcom{Sure $\UU$ is good.}
-    \acom{And, sorry, ignore my other comment; it's the same $\CC$ (or $\AA$) nothing to distinguish.}
+    % \jcom{Sure $\UU$ is good.}
+    % \acom{And, sorry, ignore my other comment; it's the same $\CC$ (or $\AA$) nothing to distinguish.}
 \end{itemize}
@@
 
-The generalized MVy is interesting in its own right. \acom{is it?}
+The generalized \mvy is interesting in its own right. \acom{is it?}
 
@@
 Up to $A_4$ as in type $A_5$ there exist indecomposable modules which are not cluster, so exchange relations do not apply.
+
 The hope (conjecture) is that this paper gives a way to compute on such modules.
-Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is (possibly) cluster, and suggesting that $c_Y = b_Z + 2b$.
-Can still consider $ext(M_Z)$.
-Say $b_Z^2 = b_{Z_1} + b_{Z_2}$.
+Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is a cluster monomial belonging to both bases and $c_Y$ is the square of a cluster monomial ($b'$ say) belonging to both bases.
+The $\barD$ equation suggests that $(b')^2 = b_Z + 2b$.
+We can try to check this using Roger's script.
+Such calculations bring us closer to answering two questions.
+First, how forgetful is $\barD$.
+Second, on the level of modules, are the terms appearing in the fusion product determined by $\Ext^1$ of the factors.
+By Roger's thesis this is true if the factors are cluster modules related by a mutation.
 
@@
     \begin{enumerate}
-        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_s \rightarrow \Grth^+$
+        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$
         \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.

### 2021-03-09 draft.tex
added check to lemma 3

@@
     \begin{enumerate}
-        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$
+        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$.
         \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
-        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$ 
+        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$.
         % \acom{why no $G(\CC[t])$-coset?}
@@
 
-    Now assume that $ (L, s) \in \Gr^{\lambda_1, \lambda_2}_s$.
-We know that $ L(0) \in \Gr^{\lambda_1}, L(s) \in \Gr^{\lambda_2} $.
-This means that $t $ acting on $ \CC\xt^m / L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on $ \CC\xt[t-s]^m / L(s) $ has Jordan type $ \lambda_2$.
-Now, the map $ L_0 / L \rightarrow \CC\xt^m / L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.
+    Now assume that $ (L, s) \in \Gr^{\lambda_1, \lambda_2}_{0,s}$. We know that \acom{by definition?} $ L(0) \in \Gr^{\lambda_1}$ and $L(s) \in \Gr^{\lambda_2} $.  This means that $t $ acting on 
+    % $ \CC\xt^m / L(0)$ 
+    $\cO^m/L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on 
+    % $ \CC\xt[t-s]^m / L(s) $ 
+    $\cO_s^m/L(s)$ has Jordan type $ \lambda_2$.  Now, the map 
+    % $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
+    $L_0/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.
 The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$.
@@
 
-    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} $ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1} $ since $ (t-s)^{\lambda_2} \in G(\CC\xt)$.
-In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
+    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} $ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1} $ since 
+    % $ (t-s)^{\lambda_2} \in G(\CC\xt)$. 
+    $ (t-s)^{\lambda_2} \in G(\cO)$. In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
 \end{proof}
@@
         \item $ L \in \cW_\mu$.
-                \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1} p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
+                \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1}^m p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
+\acom{Do we want to sum over $j \ne i$ here?
+Maybe nvm because in $\TT_\mu$ the diagonal blocks can have $*$'s in the last row.
+Also $\cO$ sb $\CC[t]$.}
         \item  For all $ i $, 
@@
     \end{enumerate}
-    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$
+    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
 \end{lemma}
@@
 \jcom{I realized the meaning of the ``extra'' condition from the paper with Sabin and I added it into point 3.}
+\acom{Technically though the extra condition in that paper is weaker? $W_{\mu_i}$ being the span of $e_j,te_j,\dots,t^{\mu_i-1}e_j$ or the complement of $t^{\mu_i}\cO^m$ in $\cO^m$.}
 
@@
 
-    Suppose that $ L = \Sp_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in \Sp_\CC(\beta_\mu) $
-in $ L_0/L$ and we see that 
-$$t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \mu_i \}) + L $$
+    Suppose that $ L = \Sp_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in \Sp_\CC(\beta_\mu) $ in $ L_0/L$ and we see that 
+    $$t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \mu_i \}) + L\,. $$
     Hence (ii) implies (iii).
-    Finally, given (iii), then we can see $ v_i := t^{\mu_i} e_i - \sum_{j=1} p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \min(\mu_i,\mu_j) $.
+
+    Finally, given (iii), then we can see $ v_i := t^{\mu_i} e_i - \sum_{j=1}^m p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \min(\mu_i,\mu_j) $.
 It is easy to see that $ L = \Sp_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.
 
-    Finally to show that $ \beta_\mu$ forms a basis for $ L_0/L$, it suffices to show that for each $ i$, $ t^\mu_i e_i  \in \Sp_\CC(\beta_\mu) + L$.  This follows immediately from (iii).
-
+    Finally to show that $ \beta_\mu$ forms a basis for $ L_0/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.  This follows immediately from (iii).
+    % 
     \end{proof}
@@
 \begin{lemma}
-    Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu_1, \mu_2}_\AA$ lands in $ \cW_\mu$.
+    Let $\mu_1,\mu_2 \in P$ and $\mu = \mu_1 + \mu_2$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu_1, \mu_2}_{0,\AA}$ lands in $ \cW_\mu$.
 \end{lemma}
@@
     Let $ L $ lie in this image.
-Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ from some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.
+Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ fom some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.
 Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.
-Note that $ h \in T_1(\CC(\xt[t^{-1}]))$.
-Then,
-    $$ L = h (h^{-1} g h) t^{\mu}$$
-    Note that $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ and from KWWY \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.
+Note that $ h \in T_1(\CC\xt[t^{-1}])$.
+    Moreover,
+    $$ L = h (h^{-1} g h) t^{\mu}\,. $$
+    Note that 
+    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
+    $h^{-1} g h \in N(\cK_\infty)$ and from \cite{kamnitzer2014yangians} 
+    \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.
+
+    \acom{
+        % The argument from my thesis does not go through since $\cW_\mu$ is defined mod $\CC[t]$.
+More precisely, we still have $N(\Kinf) = N_1(\CC[t]) N(\CC\xt[t^{-1}])$ and so $h^{-1}g h=g_1g_2$ for some $g_1 \in N_1(\CC[t])$ for some $g_2\in N\xt[t^{-1}]$.
+But now we would like to write $g_2 t^\mu = t^\mu g_3$ for some $g_3\in\CC[t]$.
+Oh, but I guess we can also
+        To check this write $N(\Kinf) = N_1(\CC\xt[t^{-1}])N(\CC[t])$.
+Does it hold?
+If $\mu$ is dominant and $g\in N(\CC[t])$ then $gt^\mu = t^\mu g'$ for some $g'\in N(\CC[t])$.} % What is a textbook reference for these factorization claims?
+are they obvious; they seem obvi
     \end{proof}

### 2021-03-09 draft.tex
fixed some typos up to falling action

@@
 \section{Climax}
-Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in section ??.
+Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.
+% section ??.  
 As $ g(A) \in M_n(\CC[t]) \cap G_1(\CC\xt[t^{-1}])$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
 
-The following result in \cite[Theorem 3.2]{cautis2018categorical}.
+The following result is \cite[Theorem 3.2]{cautis2018categorical}.
 
@@
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
-$$ L \mapsto [t|_{L_0/L} ]_{\beta_\mu}$$
+$$ L \mapsto [t|_{L_0/L} ]_{\beta_\mu} \,. $$
+\acom{Up to transpose?}
 \end{theorem}
 
-For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda_1, \lambda_2}_\AA $ with $\cW_\mu$.
-As $  \overline{\Gr}^{\lambda_1, \lambda_2}_\AA $ is not a subscheme of $ \Grth$ by this intersection, we really mean the preimage of $ \cW_\mu$ under the map $$ \overline{\Gr}^{\lambda_1, \lambda_2}_\AA  \hookrightarrow \Grbd \rightarrow \Grth$$
-This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective.
-
-In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu$, using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
+For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA} $ with $\cW_\mu$.  
+As $  \overline{\Gr}^{\lambda_1, \lambda_2}_\AA $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the map 
+$$ 
+\overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA}  \hookrightarrow \Grbd \rightarrow \Grth\,.
+$$
+This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective. \acom{Jiuzu was asking about this.}
+
+In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
+\acom{Grammar of `write using the map' is iffy.
+Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}
 
@@
     There is an isomorphism
-    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \cong \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \cong \overline\Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
     given by $ (A,s) \mapsto (g(A), s)$.
 \end{theorem}
+\acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
 
 \begin{proof}
-Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \text{ if and only if } (g(A), s) \in \Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \text{ if and only if } (g(A), s) \in \overline\Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
 This follows immediately from Lemma \ref{le:Grl1l2}.
@@
 \jcom{I thought about this and I agree with you now.  I will write this up soon.} 
+% 
+\acom{But I am also curious about the attracting set approach.}
 
@@
 
- On the one hand, if $ (A,s) \UU^{\mu_1, \mu_2}_\AA $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu_1} (t-s)^{\mu_2}$, and so $ g(A) \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+ On the one hand, if $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu_1} (t-s)^{\mu_2}$, and so $ g(A) \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
 
@@
 $$
-for some $ r \in G(\CC[t]), n \in N[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.
-Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1 \CC[[t]]$.
-Note that $ h^{-1}n h \in N((t^{-1}))$, so we can factor it as $ n = n_1 n_2 $, where $ n_1 \in N_1(\CC[[t^{-1}]]), n_2 \in N(\CC[t])$.
-So then after doing a bit of algebra, we reach
-$$
-t^\mu r (t^{-\mu} n_2 t^\mu) t^{-\mu} = g^{-1} h n_1
-$$
-The right hand side $ g^{-1} g n_1 $ lies in$ G_1(\CC[[t^{-1}]]) $.
-Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.
-Moreover since $ \mu $ is dominant, we know that $$t^\mu G(\CC[[t]]) t^{-\mu} \cap G_1(\CC[[t^{-1}]]) = N_1(\CC[[t^{-1}]])$$
- Thus, we deduce that $ g^{-1} h n_1 \in N_1(\CC[[t^{-1}]])$ and hence $ g(A) \in N_1(\CC[[t^{-1}]]) t^{\mu_1} (t-s)^{\mu_2} $.
-Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \UU^{\mu_1, \mu_2}_\AA$ as desired.
+for some $ r \in G(\CC[t]), n \in N[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1 \CC[[t]]$.
+\acom{sb $T_1\xt[t^{-1}]$ as above?}
+Note that $ h^{-1}n h \in N(\Kinf)$, 
+% ((t^{-1}))
+so we can factor it as $ n = n_1 n_2 $, where $ n_1 \in N_1(\CC\xt[t^{-1}]), n_2 \in N(\CC[t])$.  So then after doing a bit of algebra, we reach
+$$
+t^\mu r (t^{-\mu} n_2 t^\mu) t^{-\mu} = g^{-1} h n_1.
+$$
+The right hand side $ g^{-1} g n_1 $ \acom{sb $g^{-1}hn_1$} lies in $ G_1(\CC\xt[t^{-1}]) $.  Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.  
+Moreover since $ \mu $ is dominant, we know that 
+$$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
+Thus, we deduce that $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ and hence $ g(A) \in N_1(\CC\xt[t^{-1}]) t^{\mu_1} (t-s)^{\mu_2} $.
+Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA$ as desired.
 \end{proof}

### 2021-03-10 draft.tex
minor changes from mtg

@@
 $ \cO_s$ is the completion of the local ring $ \mathcal O_{\PP, s} $ and thus the formal spectrum of $ \cO_s$ is the formal neighbourhood $ D_s$ of $ s $ (also called the formal disc centered at $ s$).
-Similarly the formal spectrum of the field $\cK_s$ is the deleted formal neighbourhood (or punctured disc), denoted $ D_s \setminus \{s\} $.
+Similarly the formal spectrum of the field $\cK_s$ is the deleted formal neighbourhood (or punctured disc), denoted $ D_s^\times$.
 
@@
 i.e.\ it's really $P(T(\CC)) = \Hom(\CC^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?}
+\jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}
+
 Under this isomorphism the dominant coweights of $ G $ 
@@
 
+\acom{Add $G_1$}
+
 \subsection{Lattices}
@@
 $ L_0(R) = R^m \subset K^m $ is called the standard lattice. 
-We will abuse notation and denote $L(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
+We will abuse notation and denote $L_0(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
 The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
@@
 % L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
-L(a) := L \otimes_{\CC[t]} \cO_a %\,. % The containment is not part of the definition so I comment it out \subset \cK_a^m\,.
-$$
-and if $ L(a) = \cO_a^m$ then $L$ is said to be trivial at $a$. 
+L(a) := L \otimes_{\CC[t]} \cO_a, \text{ a lattice in } \cK_a.  %\,. % The containment is not part of the definition so I comment it out \subset \cK_a^m\,.
+$$
+If $ L(a) = L_0(\cO_a)$ then $L$ is said to be trivial at $a$. 
 % We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
@@
 For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$. 
-\acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}
+% \acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}
 
@@
 % G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
-Set $\AA = \AA^1$ \acom{and let $V_0$ denote the trivial vector bundle}.
+Set $\AA = \AA^1$ and let $V_0$ denote the trivial rank $ m $ vector bundle.
 
@@
     $$
-    \Gr = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \right\} \,. 
+    \Gr = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0^\times $} \right\} \,. 
     $$
@@
     $$
+    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, V_0)$ using $ \varphi$.
     % 
@@
     $$
-    \Gr_s = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \right\}\,.
+    \Gr_s = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D^\times_s $} \right\}\,.
     $$
@@
     $$
-        \Grth = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
+        \Grth = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
     $$
@@
     % 
-    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{why do we have the $s\ne 0$ restriction here}
+    The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
+    % \rcom{why do we have the $s\ne 0$ restriction here} \jcom{it would work when $ s = 0$, but it looks a bit strange there.}
     % 
@@
 \begin{enumerate}
-    \item First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \cK \cong \Ks$.
+    \item First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
     \item Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
@@
 for each $ s \ne 0$,  
-\rcom{usually written $\Gr_{0,\AA^\times} \cong \Gr \times \Gr_s \times \AA^\times$, cite MVi} 
+\rcom{Joel: usually written $\Gr_{0,\AA^\times} \cong \Gr \times \Gr_s \times \AA^\times$, cite MVi} 
 we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
@@
 
-\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper and it is the most convenient way to define $\Gr^{\lambda_1, \lambda_2}$.
+%\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper and it is the most convenient way to define $\Gr^{\lambda_1, \lambda_2}$.
 I don't know what notation we should use.}
 
-\acom{Roger and I have been using $\ast$ to denote fusion.
+%\acom{Roger and I have been using $\ast$ to denote fusion.
 Do we need a notation for the scheme-theoretic closure of $X_1\times X_2\times\AA^\times$?
 If not then I like $X_1\ast X_2 = \overline{X_1 \times X_2 \times \AA^\times}\cap \pi^{-1}(0)$.}
-\jcom{I think that we will need notations for both things, but I'm happy to use $ \ast$ for the central fibre and use something else for the whole family.} \acom{Ok, I have changed it to notation from Roger's thesis/AK.
+%\jcom{I think that we will need notations for both things, but I'm happy to use $ \ast$ for the central fibre and use something else for the whole family.} \acom{Ok, I have changed it to notation from Roger's thesis/AK.
 Only now I am confused as to what is being called fusion---why do we not take the top dimensional subscheme?}
-\jcom{I guess that there are two things that one could mean by fusion of MV cycles.
+%\jcom{I guess that there are two things that one could mean by fusion of MV cycles.
 This scheme $ X_1 \circ X_2$ or the expression which appear in Theorem 7.11 of mvbasis, which is a linear combination of the top-dimensional components of this scheme with multiplicites.
@@
 By the way, somewhere in this paper we should explain Theorem 7.11 and say that this gives us motivation to study fusion of MV cycles.}
-\acom{Sure! It is quoted at the end, in \Cref{s:denouement} as an application. Addendum: for the numerical fusion I suggest simply $[Z_1][Z_2]$. This is what I will use in my talk. }
+%\acom{Sure! It is quoted at the end, in \Cref{s:denouement} as an application. Addendum: for the numerical fusion I suggest simply $[Z_1][Z_2]$. This is what I will use in my talk. }
 
@@
     \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
-    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?}
+    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.  And unless $ A $ is nilpotent, then $g(A)$ won't live there.}
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
@@
 
-    \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
-    \acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
-    in $\AA_s\times \AA_{\det}$? 
-    so the set of $A$ which are conjugate to
-    $J_{0,\lambda_1} \oplus J_{s,\lambda_2}$
-    by a matrix whose determinant is divisible by $s$ is also closed?}
-    \jcom{I didn't follow your argument.
+   % \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
+    %\acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
+    %in $\AA_s\times \AA_{\det}$? 
+    %so the set of $A$ which are conjugate to
+    %$J_{0,\lambda_1} \oplus J_{s,\lambda_2}$
+    %by a matrix whose determinant is divisible by $s$ is also closed?}
+    %\jcom{I didn't follow your argument.
 One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.
@@
 I am hoping that we can find a reference for this result somewhere.}
-    \acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda_1}\oplus J_{s,\lambda_2}$ limit to matrices which are conjugate to $J_\lambda$.
+    %\acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda_1}\oplus J_{s,\lambda_2}$ limit to matrices which are conjugate to $J_\lambda$.
 In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}
@@
     % 
-    \acom{this ok?} % \jcom{Anne, can you add this definition?}
-    \jcom{When you wrote ``In words,'', it is not quite correct because of the diagonal blocks have those 1s.  Also it would be good to have an example.  And what is $f$ in the last sentence? }
-    \acom{fixed? As for $f$ I think it is an $\sl_2$ triplet. Hopeful you could explain what MVy meant bc I never quite understood!}
+    %\acom{this ok?} % \jcom{Anne, can you add this definition?}
+    %\jcom{When you wrote ``In words,'', it is not quite correct because of the diagonal blocks have those 1s.  Also it would be good to have an example.  And what is $f$ in the last sentence? }
+    %\acom{fixed? As for $f$ I think it is an $\sl_2$ triplet. Hopeful you could explain what MVy meant bc I never quite understood!}
 
@@
 are they obvious; they seem obvi
+        \jcom{Yes, that is correct.  I think that I once had Alex write out a careful proof of this fact.  It holds for any unipotent group.  The proof is by induction.}
     \end{proof}
@@
 \acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
-
+\jcom{Oops, no I think that we should stick with $ X_{0, \AA}$.}
 \begin{proof}
@@
 $$
-for some $ r \in G(\CC[t]), n \in N[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1 \CC[[t]]$.
-\acom{sb $T_1\xt[t^{-1}]$ as above?}
+for some $ r \in G(\CC[t]), n \in N[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1\xt[t^{-1}] $.
 Note that $ h^{-1}n h \in N(\Kinf)$, 
@@
 $$
-The right hand side $ g^{-1} g n_1 $ \acom{sb $g^{-1}hn_1$} lies in $ G_1(\CC\xt[t^{-1}]) $.  Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.  
+The right hand side $ g^{-1} h n_1 $ lies in $ G_1(\CC\xt[t^{-1}]) $.  Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.  
 Moreover since $ \mu $ is dominant, we know that 
@@
 We view MV cycles as semi-standard young tableaux.
-Suppose we have two tableaux $\tau_1$ and $\tau_2$ with respective weights $\lambda_i$ and $\mu_i$ and we wished to taked their fusion product.
+Suppose we have two tableaux $\tau_1$ and $\tau_2$ with respective weights $\lambda_i$ and $\mu_i$ and we wished to take their fusion product.
 We consider a generic matrix $X \in \UU^{\lambda_1,\lambda_2}_{0,s}$.
 
-The subtableaux of $\tau_1$ and $\tau_2$ where we take the first $j$ entries of each $\mu_i$ correspond to the submatrix $X_j$ of $X$ that consists of the first $j$ blocks.
-These subtableaux impose rank conditions, equivalently vanishing minors, on $X_j$ which allows us to deduce relations on the variables in $X$.
+Consider the subtableaux $\tau_{1,i}$ of $\tau_1$ and $\tau_{2,i}$ of $\tau_2$ where we take the boxes of $\tau_1$ and $\tau_2$ containing the numbers $1,\dots,i$.
+Let $\lambda_{1,j}$ and $\lambda_{2,j}$ be the corresponding dominant weights.
+For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\lambda_{1,i}, \lambda_{2,i}}_{0,s}$ of $X$.
+These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ which allows us to deduce relations on the variables in $X$.
 The relations must also include the new variables in the latest block and cannot have $s$ as a factor.
@@
 $$\young(1123,23)$$
-which corresponds to the MV cycle that is the cross product of the MV cycles corresponding to $\tau_1$ and $\tau_2$.
+which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau_1$ and $\tau_2$.
 \end{example}

### 2021-03-10 draft.tex
goodbye original falling action
some explanation of how to apply ES

@@
     \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
-    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.  And unless $ A $ is nilpotent, then $g(A)$ won't live there.}
+    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.
+And unless $ A $ is nilpotent, then $g(A)$ won't live there.} \acom{Another notational thing is $G_1\xt[t^{-1}] = G_1(\CC\xt[t^{-1}])$ and in our paper this short hand is only used for these kernel subgroups.}
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
@@
 Altogether $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to $\bigoplus_{i = 1}^m A_{\lambda_{1,i}+\lambda_{2,i}}$ and this latter matrix specializes to the Jordan normal form $J_{0,\lambda_1 + \lambda_2}$ at $s=0$.
+
+\acom{The following is a rough note.}
+
+The relevant result from Eisenbud--Saltman seems to be that 
+$$X_r = X_{r,0} = \{A:\rk A^i \le r(i) \}$$ 
+is the flat limit of 
+$$X_{r,\lambda} = \{A : \rk (A-\lambda_i)^j\le r(i,j)\}$$
+with $r(i,j)$ determined by $r(i)$.
+
+The case that we are interested in is the case of two eigenvalues. Let me change notation so that $\lambda_i$ are shapes and let me only look at the open loci where the rank conditions are strict.
+
+Let $m_i = \lambda_{i,1}$ ($i = 1,2$), $m = m_1 + m_2$, and define
+$$r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda_1 + \lambda_2 = \lambda\vdash N$$
+on $j = 1,\dots,m$. Note that $r(j-1) - r(j)$ is the length of the $j$th column of $\lambda$. As in \cite{eisenbud1989rank} we will denote this quantity $a_j$. 
+%
+
+Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(m_1)}$ are the (lengths of) columns of $\lambda_1$ and $a_{p(m_1 + 1)},\dots, a_{p(m_1 + m_2)}$ are the (lengths of) columns of $\lambda_2$.
+Then the functions 
+$$
+r(1,j) = N - a_{p(1)} - \cdots - a_{p(j)} \text{ and } r(2,j) = N - a_{p(m_1 + 1)} - \cdots - a_{p(m_1 + j)}
+$$
+are such that 
+\begin{align*}
+    \OO^{\lambda_1,\lambda_2} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots,\lambda_{1,1} \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = \lambda_{1,1} + 1 ,\dots, \lambda_{2,1} \}
+\end{align*}
+and according to \cite[Theorem 2.1(iii)]{eisenbud1989rank} the family $X_{r,\AA^m}$ is flat over $\AA^m$ with zero fibre $X_{r,0} = \OO^\lambda$ as desired.
+
+% On the one hand, we know that $r(i,j)$ should be equal to $N$ minus the number of boxes in the first $j$ columns of $\lambda_i$.
+On the other hand, ES define $r(i,j)$ to be $N$ minus the $i$th chunk of $j$ columns determined by the rank function $r(i)$.
+Also, we would like for $r(i)$ to determine the shape $\lambda = \lambda_1 + \lambda_2$.
+Take for example $\lambda_1 = \lambda_2 = (2,1)$.
+Then $\lambda = (4,2)$ and so $r\{0,1,2,3,4\}=\{6,4,2,1,0\}$ and
+% $$\{a_1,a_2,a_3,a_4\} = \{6-4,4-2,2-1,1-0\}=\{2,2,1,1\}\,.$$
+
+% For another example take $\lambda_1 = (1)$ and $\lambda_2 = (1,1)$. Then $\lambda = (2,1)$ and $r\{0,1,2\} = \{3,1,0\}$ so $\{a_1,a_2\} = \{2,1\}$.
+
+% Again too small.
+The problem is I don't think that it is in general true that some permutation of the list $r(i-1) - r(i)$ will be the list of lengths of columns of $\lambda_1$ followed by the list of lengths of columns of $\lambda_2$ which is what we are looking for.
+For one thing there's in general more than one way to write a partition as a sum of two partitions.
+Ok, concretely, a third example.
+Take $\lambda_1 = (a,b)$ and $\lambda_2 = (c,d)$ then $\lambda = (a + c, b + d)$ and
+% $$r\{0,1,\dots,a + c\} = \{N, N-2, \dots, N-2(b+d), N-2(b+d) - 1,\dots, 0\}$$
+% so 
+% $$\{a_1,a_2,\dots\} = \{2,2,\dots,2,1,1,\dots,1\}$$
+% with $b+d$ 2s and $a+c - b - d$ 1s.
+Wait a minute, nevermind, of course this is true.
+We have two partitions $\lambda_1$ and $\lambda_2$ and one way to form the partition $\lambda = \lambda_1 + \lambda_2$ is to break $\lambda_i$ down into columns, order the columns by length, and recombine.
+Cool.
+I think it's fine.
+\acom{That's it for the note.}
 
@@
 Maybe nvm because in $\TT_\mu$ the diagonal blocks can have $*$'s in the last row.
-Also $\cO$ sb $\CC[t]$.}
+Also $\cO$ should be $\CC[t]$.}
         \item  For all $ i $, 
@@
     Let $ L \in \cW_\mu$.
-Then $ L = \Sp_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \CC\xt[t^{-1}]$.
+Then $ L = \Sp_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \Oinf$.
 Since $ L \in \Grth^+ $, we see that $ v_i \in L_0$ which means that $ p_{ij} := q_{ij}t^{\mu_i} $ lies in $ \CC[t]$.
@@
 \begin{proof}
-    Let $ L $ lie in this image.
-Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ fom some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.
-Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.
-Note that $ h \in T_1(\CC\xt[t^{-1}])$.
+    Let $ L $ lie in this image.  Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ fom some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.  Note that $ h \in T_1(\Oinf)$. 
     Moreover,
@@
 Oh, but I guess we can also
-        To check this write $N(\Kinf) = N_1(\CC\xt[t^{-1}])N(\CC[t])$.
+        To check this write $N(\Kinf) = N_1(\Oinf)N(\CC[t])$.
 Does it hold?
@@
 % section ??.  
-As $ g(A) \in M_n(\CC[t]) \cap G_1(\CC\xt[t^{-1}])$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
+As $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
 
@@
 % ((t^{-1}))
-so we can factor it as $ n = n_1 n_2 $, where $ n_1 \in N_1(\CC\xt[t^{-1}]), n_2 \in N(\CC[t])$.  So then after doing a bit of algebra, we reach
+so we can factor it as $ n = n_1 n_2 $, where $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t])$.  So then after doing a bit of algebra, we reach
 $$
@@
 $$
-The right hand side $ g^{-1} h n_1 $ lies in $ G_1(\CC\xt[t^{-1}]) $.  Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.  
+The right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.  
 Moreover since $ \mu $ is dominant, we know that 
-$$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
-Thus, we deduce that $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ and hence $ g(A) \in N_1(\CC\xt[t^{-1}]) t^{\mu_1} (t-s)^{\mu_2} $.
-Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA$ as desired.
+$$t^\mu G(\cO) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.$$
+% $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
+Thus, we deduce that $ g^{-1} h n_1 \in N_1(\Oinf)$ 
+% $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
+and hence $ g(A) \in N_1(\Oinf) t^{\mu_1} (t-s)^{\mu_2} $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA$ as desired.
 \end{proof}
@@
 \section{Falling Action} % Resolution
-
+\begin{comment}
 \begin{theorem}
@@
 \end{proof}
+\end{comment}
 
@@
 \rcom{I have 3 examples in mind right now: fusion product producing 1 term (maybe $1 \leftarrow 2 * 1 \rightarrow 2$), fusion product producing more than 1 term $(S_1 * S_2)$, and fusion product with multiplicities $((S_1 * S_2)^2)$}
+
+\acom{Plus fusion product of fake MV cycles for a fourth!}
 

### 2021-03-16 draft.tex
joel changed some notation and finished the proof of theorem 3

@@
     We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, V_0)$ using $ \varphi$.
+On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.
     % 
@@
 Since $g\CC[t]\otimes_{\CC[t]}\cO_s \cong g\cO_s $ for some reason, where $g\in\CC[t,t^{-1},(t-s)^{-1}]$ can be viewed as $g\in\cK_s$.}
+
+    In group-theoretic terms, this isomorphism is given using the diagonal map
+    $$G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) \rightarrow G(\cK)/G(\cO) \times G(\cK_s)/G(\cO_s)
+    $$
+    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) $, we have
+    $$
+    g \CC[t]^m \otimes_{\CC[t]} \cO = g \cO^m
+    $$
+    and similarly for $ L(s)$.
 
@@
 $$
-r(1,j) = N - a_{p(1)} - \cdots - a_{p(j)} \text{ and } r(2,j) = N - a_{p(m_1 + 1)} - \cdots - a_{p(m_1 + j)}
+\begin{aligned}
+r(1,j) &= N - a_{p(1)} - \cdots - a_{p(j)} \\
+% \text{ and } 
+r(2,j) &= N - a_{p(m_1 + 1)} - \cdots - a_{p(m_1 + j)}
+\end{aligned}
 $$
@@
 \begin{align*}
-    \OO^{\lambda_1,\lambda_2} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots,\lambda_{1,1} \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = \lambda_{1,1} + 1 ,\dots, \lambda_{2,1} \}
+    \OO^{\lambda_1,\lambda_2}_{0,s} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots, m_1 \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = m_1 + 1 ,\dots, m \}
 \end{align*}
 and according to \cite[Theorem 2.1(iii)]{eisenbud1989rank} the family $X_{r,\AA^m}$ is flat over $\AA^m$ with zero fibre $X_{r,0} = \OO^\lambda$ as desired.
+I guess we need to carefully choose the $W \subset \AA^m$ defining our family, which is smaller than the family $X_{r,\AA^m}$.
+Well, $W$ is just cut out by $0 = x_1 = x_2 = \cdots = x_{m_1}$ and $ x_{m_1 + 1} = \cdots = x_m$.
+Or some permutation thereof to match the permutation $p$ above.
 
@@
     % $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
-    $L_0/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.
+    $\CC[t]^m/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.
 The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$.
@@
 
-    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} $ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1} $ since 
+    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} \CC[t]^m$ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1}\cO^m $ since 
     % $ (t-s)^{\lambda_2} \in G(\CC\xt)$. 
@@
         \item $ L \in \cW_\mu$.
-                \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1}^m p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
+                \item $ L = \Sp_{\CC[t]}(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1}^m p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
 \acom{Do we want to sum over $j \ne i$ here?
@@
     Let $ L \in \cW_\mu$.
-Then $ L = \Sp_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \Oinf$.
+Then $ L = \Sp_{\CC[t]}(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \Oinf$.
 Since $ L \in \Grth^+ $, we see that $ v_i \in L_0$ which means that $ p_{ij} := q_{ij}t^{\mu_i} $ lies in $ \CC[t]$.
@@
 
-    Suppose that $ L = \Sp_\cO(v_1, \dots, v_m)$ as in (ii).  Then $[t^{\mu_i} e_i] \in \Sp_\CC(\beta_\mu) $ in $ L_0/L$ and we see that 
-    $$t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \mu_i \}) + L\,. $$
+    Suppose that $ L = \Sp_{\CC[t]}(v_1, \dots, v_m)$ as in (ii).  Then
+    $$t^{\mu_i} e_i - v_i \in \Sp_\CC(\{t^k e_j :  k < \min(\mu_i, \mu_j), 1 \le j \le m \})  \,. $$
     Hence (ii) implies (iii).
@@
 
-    Finally to show that $ \beta_\mu$ forms a basis for $ L_0/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.  This follows immediately from (iii).
+    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.  This follows immediately from (iii).
     % 
@@
 \begin{proof}
-    Let $ L $ lie in this image.  Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ fom some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.  Note that $ h \in T_1(\Oinf)$. 
+    Let $ L $ lie in this image.
+Then $ L = g t^{\mu_1} (t-s)^{\mu_2}\CC[t]^m$ for some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.
+Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.
+Note that $ h \in T_1(\Oinf)$.
     Moreover,
-    $$ L = h (h^{-1} g h) t^{\mu}\,. $$
+    $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
     Note that 
     % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
-    $h^{-1} g h \in N(\cK_\infty)$ and from \cite{kamnitzer2014yangians} 
-    \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.
-
-    \acom{
-        % The argument from my thesis does not go through since $\cW_\mu$ is defined mod $\CC[t]$.
-More precisely, we still have $N(\Kinf) = N_1(\CC[t]) N(\CC\xt[t^{-1}])$ and so $h^{-1}g h=g_1g_2$ for some $g_1 \in N_1(\CC[t])$ for some $g_2\in N\xt[t^{-1}]$.
-But now we would like to write $g_2 t^\mu = t^\mu g_3$ for some $g_3\in\CC[t]$.
-Oh, but I guess we can also
-        To check this write $N(\Kinf) = N_1(\Oinf)N(\CC[t])$.
-Does it hold?
-If $\mu$ is dominant and $g\in N(\CC[t])$ then $gt^\mu = t^\mu g'$ for some $g'\in N(\CC[t])$.} % What is a textbook reference for these factorization claims?
-are they obvious; they seem obvi
-        \jcom{Yes, that is correct.  I think that I once had Alex write out a careful proof of this fact.  It holds for any unipotent group.  The proof is by induction.}
+    $h^{-1} g h \in N(\cK_\infty)$ and so we can factor $ h^{-1} g h = n_1 n_2$ for $ n_1 \in N_1(\CC\xt[t^{-1}]), n_2 \in N(\CC[t]) $.
+Since $ \mu $ is dominant, we see that $ t^{-\mu} n t^\mu \in N(\CC[t]) $.
+Thus, $ L = h n_1 t^\mu \CC[t]^m$.
+Since $ hn_1 \in G_1(\CC\xt[t^{-1}])$, the result follows.
     \end{proof}
@@
 \begin{theorem} \label{th:TmuWmu}
-The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
-$$ L \mapsto [t|_{L_0/L} ]_{\beta_\mu} \,. $$
+The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
+$$ L \mapsto [t|_{\CC[t]^m/L} ]_{\beta_\mu} \,. $$
 \acom{Up to transpose?}
@@
     $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \cong \overline\Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
-    given by $ (A,s) \mapsto (g(A), s)$.
+    given by $ (A,s) \mapsto (g(A)\CC[t]^m, s)$.
 \end{theorem}
@@
 \begin{proof}
-Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \text{ if and only if } (g(A), s) \in \overline\Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
 This follows immediately from Lemma \ref{le:Grl1l2}.

### 2021-03-16 draft.tex
minor fixes and bib adds

@@
 
-We will also study the affine space of $m\times m$ matrices which we denote $ M_m$.
+% \acom{Add $G_1$}
+\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$.
+The affine space of $m\times m$ matrices which we denote $ M_m$.
+The first congruence subgroup $G_1$ and why we take $\Oinf$ points instead of $\CC[t]$ points as some of the lit does.}
 
@@
 Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  
-\acom{This identification assumes we are taking $\CC$ points of $G$ right?
+% TODO: Thank you - resolved!
+% \acom{This identification assumes we are taking $\CC$ points of $G$ right?
 i.e.\ it's really $P(T(\CC)) = \Hom(\CC^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?}
-\jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}
+% \jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}
 
@@
 
-\acom{Add $G_1$}
-
 \subsection{Lattices}
@@
 
-\jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
-\acom{Ok. We could omit the repetitive ``$X=$'' bits from the display styled alternate descriptions. That way they will fit within the margins.}
+% \jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
+% \acom{Ok. We could omit the repetitive ``$X=$'' bits from the display styled alternate descriptions. That way they will fit within the margins.}
+% TODO: Just trying it out
 
@@
     $$
-    \Gr = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0^\times $} \right\} \,. 
+    % \Gr = 
+    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0^\times $} \right\} \,. 
     $$
@@
     We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, V_0)$ using $ \varphi$.
-On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.
+On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap}
     % 
@@
     $$
-    \Gr_s = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D^\times_s $} \right\}\,.
+    % \Gr_s = 
+    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D^\times_s $} \right\}\,.
     $$
@@
     $$
-        \Grth = \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
+        % \Grth = 
+        % \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
     $$
@@
     $$
-    \Grbd = 
+    % \Grbd = 
     % \begin{aligned}
@@
     $$ 
-    \Gr_{0,s} = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
+    % \Gr_{0,s} = 
+    G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
     $$
@@
     % 
-    \item The positive parts, $ \Gr^+$ and ${\Grth}^+$, of the affine Grassmannian and the thick affine Grassmannian, respectively, are defined as 
+    \item The positive parts, 
+    \[
+        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO)
+    \]
+    and
+    \[
+        {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
+    \]
+    % $ \Gr^+$ and ${\Grth}^+$, 
+    of the affine Grassmannian and the thick affine Grassmannian, respectively. %, are defined as 
     % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
-    $$
-    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. % \CC\xT[t^{-1}] missed a spot  
-    $$
-    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}
+    % $$
+    % \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. % \CC\xT[t^{-1}] missed a spot  
+    % $$
     % 
@@
     % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
-    \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
-    $$ 
-    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
-    $$ 
-    \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
+    % \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
+    % $$ 
+    % L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
+    % $$ 
+    % \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
     \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
@@
     % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
-    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
+    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{Do we need to justify this.}
     % 
@@
     By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  
-By \cite[Proposition 3.1.14]{zhu2016introduction},
+    % By \cite[Proposition 3.1.14]{zhu2016introduction},
     % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
-    the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
+    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
+    Over $s=0$ the fibre is shown to be $ \overline{\Gr}^{\lambda_1 + \lambda_2}$ in the proof of \cite[Proposition 3.1.14]{zhu2016introduction}.
 
@@
     \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
+    % 
     \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.
-And unless $ A $ is nilpotent, then $g(A)$ won't live there.} \acom{Another notational thing is $G_1\xt[t^{-1}] = G_1(\CC\xt[t^{-1}])$ and in our paper this short hand is only used for these kernel subgroups.}
+And unless $ A $ is nilpotent, then $g(A)$ won't live there.} \acom{But our $A$ is always nilpotent?
+Another notational thing is $G_1\xt[t^{-1}] = G_1(\CC\xt[t^{-1}])$ and in our paper this short hand is only used for these kernel subgroups.}
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
@@
     $$
-    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
+    % S^{\mu_1, \mu_2}_{0,s} = 
+    N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
     $$
@@
     where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
-    For example, the $A$ above will define 
+    % For example, the $A$ above will define 
     % \acom{the transpose of! TODO. Had script?}
@@
 
-    \item The ``upper-triangular'' \mvy slice $\UU^{\mu_1, \mu_2}_\AA \rightarrow \AA $, defined by
-    $$
-    \UU^{\mu_1, \mu_2}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
-    $$
-    So a matrix in $\UU^{\mu_1, \mu_2}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).
+    \item The ``upper-triangular'' \mvy slice $\UU^{\mu_1, \mu_2}_{0,\AA}\rightarrow \AA $, defined by
+    $$
+    \UU^{\mu_1, \mu_2}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
+    $$
+    So a matrix in $\UU^{\mu_1, \mu_2}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).
 
@@
     \]
-    $\UU^{\mu_1, \mu_2}_\AA$ entries look like 
+    $\UU^{\mu_1, \mu_2}_{0,\AA}$ entries look like 
     \[
@@
 
-Computing fusion still hard but at least boiled down to linear algebra. Cf.\ fusion product as it appears in BD, FL, MV, AK, BFM.
-
-Interesting combinatorics? Witnessing a product on SSYT.
+Computing fusion still hard but at least boiled down to linear algebra.
+Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
+
+Interesting combinatorics?
+Presumably it is related to Feigin and Loktev's generalized Kostka polynomials?
+Though Joel says that the product on SSYT that we are witnessing is unlikely to have a combinatorial description.
 
@@
     \begin{enumerate}
-        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$.
-        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
+        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$. \acom{Should we describe this map somewhere? Earlier?}
+        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$. \acom{vestigial $L_0$}
         \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$.
@@
 
-    Now assume that $ (L, s) \in \Gr^{\lambda_1, \lambda_2}_{0,s}$. We know that \acom{by definition?} $ L(0) \in \Gr^{\lambda_1}$ and $L(s) \in \Gr^{\lambda_2} $.  This means that $t $ acting on 
+    Now assume that $ (L, s) \in \Gr^{\lambda_1, \lambda_2}_{0,s}$.
+We know that \acom{Rather than we know, it is by definition?} $ L(0) \in \Gr^{\lambda_1}$ and $L(s) \in \Gr^{\lambda_2} $.
+This means that $t $ acting on
     % $ \CC\xt^m / L(0)$ 
@@
 This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).
+\acom{is this map $v + L \mapsto v + L(0)$?}
 
@@
     \end{proof}
+\acom{note-to-self, skipped this; return to it.}
 
@@
 \end{lemma}
+\acom{the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too..
+Anyway I think that you address this below Joel.
+Probably it is worth writing out the map just before this first occurence?
+\textit{is it $(L,s)\mapsto L$?}}
 
@@
 % section ??.  
-As $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
+Since $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
 
@@
 $$ L \mapsto [t|_{\CC[t]^m/L} ]_{\beta_\mu} \,. $$
-\acom{Up to transpose?}
+\acom{Up to transpose?!}
 \end{theorem}
@@
 For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA} $ with $\cW_\mu$.  
-As $  \overline{\Gr}^{\lambda_1, \lambda_2}_\AA $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the map 
+As $  \overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA} $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the map 
 $$ 
@@
 $$
-This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective. \acom{Jiuzu was asking about this.}
+This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective.
 
@@
     There is an isomorphism
-    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \cong \overline\Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+    $$\overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda_1, \lambda_2}_{0,\AA} \cap \cW_\mu $$
     given by $ (A,s) \mapsto (g(A)\CC[t]^m, s)$.
 \end{theorem}
-\acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
-\jcom{Oops, no I think that we should stick with $ X_{0, \AA}$.}
+% \acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
+% \jcom{Oops, no I think that we should stick with $ X_{0, \AA}$.}
+% TODO: comb the doc at the end for this notation 
 \begin{proof}
-Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
+Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda_1, \lambda_2}_{0,\AA} \cap \cW_\mu $$
 This follows immediately from Lemma \ref{le:Grl1l2}.
@@
     The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
-    $$ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap \UU^{\mu_1, \mu_2}_\AA \cong \overline{\Gr}^{\lambda_1, \lambda_2}_\AA \cap S^{\mu_1, \mu_2}_\AA$$
+    $$ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \cap \UU^{\mu_1, \mu_2}_{0,\AA} \cong \overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA} \cap S^{\mu_1, \mu_2}_{0,\AA}$$
 \end{theorem}
@@
 \begin{proof}
- Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA $ if and only if $ (g(A),s) \in S^{\mu_1, \mu_2}_\AA $.
-
- On the one hand, if $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu_1} (t-s)^{\mu_2}$, and so $ g(A) \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
-
- On the other hand, if $ (g(A), s) \in S^{\mu_1, \mu_2}_\AA$, then we can write 
+ Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu_1, \mu_2}_{0,\AA} $.
+
+ On the one hand, if $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA} $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu_1} (t-s)^{\mu_2}$, and so $ g(A) \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+
+ On the other hand, if $ (g(A), s) \in S^{\mu_1, \mu_2}_{0,\AA}$, then we can write 
  $$
@@
 % $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
-and hence $ g(A) \in N_1(\Oinf) t^{\mu_1} (t-s)^{\mu_2} $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA$ as desired.
+and hence $ g(A) \in N_1(\Oinf) t^{\mu_1} (t-s)^{\mu_2} $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA}$ as desired.
 \end{proof}
@@
 
-\begin{proposition}
+\begin{proposition}(\cite{baumann2019mirkovic})
     % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
-    Let $Z_{i} = Z_{\tau_i}$  be an MV cycle of type $\lambda_i\in P_+$ and weight $\mu_i\in P$ ($i = 1,2$). Then 
+    Let $Z_{i} = Z_{\tau_i}$  be an MV cycle of type $\lambda_i\in P_{++}$ and weight $\mu_i\in P$ ($i = 1,2$). Then 
     \begin{equation}
         % Z_\tau\ast Z_\sigma 
-        m_{\lambda_1\lambda_2} ([Z_1]\otimes[Z_2]) = \sum_{Z\in\cZ(\lambda)_\mu} i\left(
-            Z,\pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
-        \right) [Z]
-    \end{equation}
-    is found by\dots 
-    In particular, the multiplicity of $Z_\tau$ in the product of the zero fiber 
+        m_{\lambda_1\lambda_2} ([Z_1]\otimes[Z_2]) 
+        = 
+        % \sum_{Z\in\cZ(\lambda)_\mu} 
+        \sum_{\tau\in S(\lambda)_\mu}
+        i\left(
+            Z_\tau, Z_1\circ Z_2 
+            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
+        \right) [Z_\tau]
+    \end{equation}
+    and the intersection multiplicities on the right are found by the algorithm described in APX.
+    In particular, 
+    the multiplicity of $Z_\tau$
+    % in the product of the zero fiber 
     % (divisor class) 
-    and the 
+    % and the 
     % (Zariski) 
-    closure of the family $Z_1 \times Z_2 \times U$ is equal to the multiplicity of $X_\tau$ among 
+    % closure of the family $Z_1 \times Z_2 \times U$ 
+    is equal to the multiplicity of its generalized orbital variety $X_\tau$ among the set 
     \begin{equation}\label{eq:tabmult}
-        \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu_1,\mu_2}^{+,s}
-    \end{equation}
-    and since stable MV cycles can be represented by ordinary ones the multiplicities in 
+        \irr\lim_{s\to 0} \overline{\OO}^{\lambda_1,\lambda_2}_{0,s}\cap\UU^{\mu_1,\mu_2}_{0,s} \,. 
+        % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu_1,\mu_2}^{+,s}
+    \end{equation}
+    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
     $$
     b_{Z_1}b_{Z_2} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
-        Z, \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
+        Z, Z_1 \circ Z_2 
+        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
     \right) b_Z 
@@
     \begin{equation}
-        i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}) = 1 \,. 
+        i(\tau, 
+        % \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}
+        % Z_1 \circ Z_2 
+        \tau_1 \circ \tau_2 
+        ) = 1 \,. 
     \end{equation}
@@
 \appendix
+\section{Generalized orbital varieties?}
+TODO: recall $\tau\mapsto X_\tau \mapsto Z_\tau$
+\section{Tableaux and families}
+TODO: $Z_1\ast_\AA Z_2$ is described by $\tau_1\ast\tau_2$ or $\tau_1\sqcup\tau_2$
 \section{Examples}

### 2021-03-20 draft.tex
misc minor changes since last mtg

@@
     % in the $ s \ne 0 $ case.
-    \jcom{Maybe we should introduce some notation for this isomorphism.}
+    % \jcom{Maybe we should introduce some notation for this isomorphism.}
     % \acom{Ok. Question: how is the isomorphism given at $s=0$?}
-    \acom{Ok.
+    % \acom{Ok.
 TODO.
@@
 % ((t^{-1}))
-so we can factor it as $ n = n_1 n_2 $, where $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t])$.  So then after doing a bit of algebra, we reach
+so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t])$.  So then after doing a bit of algebra, we reach
 $$
@@
 $$
-The right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.  
+The right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.
+
 Moreover since $ \mu $ is dominant, we know that 
-$$t^\mu G(\cO) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.$$
+$$t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.$$
 % $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
@@
 % $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
-and hence $ g(A) \in N_1(\Oinf) t^{\mu_1} (t-s)^{\mu_2} $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA}$ as desired.
+and hence $ g(A) \in t^{\mu_1} (t-s)^{\mu_2} N_1(\Oinf) $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA}$ as desired.
 \end{proof}
@@
 $$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$
+The MV cycles corresponding to $\tau_1$ and $\tau_2$ are both isomorphic to $\PP^2$.
 The weights are $\lambda_1 = \lambda_2 = (2,1,0)$ and $\mu_1 = \mu_2 = (1,1,1)$. Hence the matrix in consideration is 
@@
 
+\begin{example}
+Let $G = SL_3$ and consider the tableaux
+$$\tau_1 = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(11,23).$$
+The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.
+We have the weights to be $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (1,1,0)$, and $\mu_2 = (2,1,1)$. The matrix under consideration is therefore
+\[
+X = \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c}
+    0 & 1 & & & & \\
+     & 0 & 1 & & & \\
+     & -s^2 & 2s & a_1 & a_2 & b_1 \\
+     & & & 0 & 1 & \\
+     & & & & s & b_2 \\
+     & & & & & s
+\end{BMAT}
+\right].
+\]
+There are no relations from looking at the submatrix $X_1$. From the submatrix $X_2$, we require $$a_1 + sa_2 = 0.$$
+From $X$, we further obtain the relations $$a_2b_2 + sb_1 = 0, a_1b_2 + s^2b_1 = 0.$$
+Then the quotient ring we find is
+$$\frac{\CC[a_1,a_2,b_1,b_2,s]}{\langle a_1+sa_2, a_2b_2+sb_1, a_1b_2+s^2b_1, s\rangle} \cong \frac{\CC[a_1,a_2,b_1,b_3,s]}{\langle a_1, a_2\rangle \cap \langle a_1, b_2 \rangle}.$$
+We see that the 0-fibre is reducible with two components. The tableau corresponding to each ideal is
+$$\begin{array}{cc} \vspace{1mm}
+    \young(1113,22) & \text{for } \langle a_1, a_2 \rangle \\ 
+    \young(1112,23) & \text{for } \langle a_1, b_2 \rangle.
+\end{array}$$
+Each of these tableaux corresponds to a MV cycle isomorphic to $\PP^2$ so the generic fibre $\PP^1 \times \PP^1$ degenerates to two copies of $\PP^2$.
+\end{example}
+
+\begin{example}
+Let $G = SL_3$ and consider the following tableaux:
+$$\tau_1 = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(1111,2233).$$
+The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
+The weights are then $\lambda_1 = (4,0,0)$, $\lambda_2 = (4,4,0)$, $\mu_1 = (2,2,0)$, and $\mu_2 = (4,2,2)$.
+Then we are considering the following matrix:
+\[
+X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
+    0 & 1 & & & & & & & & & & \\
+     & 0 & 1 & & & & & & & & & \\
+     & & 0 & 1 & & & & & & & & \\
+     & & & 0 & 1 & & & & & & & \\
+     & & & & 0 & 1 & & & & & & \\
+     & & -s^4 & 3s^3 & -6s^2 & 4s & a_1 & a_2 & a_3 & a_4 & b_1 & b_2 \\
+     & & & & & & 0 & 1 & & & & \\
+     & & & & & & & 0 & 1 & & & \\
+     & & & & & & & & 0 & 1 & & \\
+     & & & & & & & & -s^2 & 2s & b_3 & b_4 \\
+     & & & & & & & & & & 0 & 1 \\
+     & & & & & & & & & & -s^2 & 2s
+\end{BMAT}
+\right].
+\]
+By computer, it can be checked that we obtain the following 3 ideals:
+$$
+\begin{array}{cl}
+    I_1 = & \langle a_1, a_2, a_3, a_4, s \rangle \\
+    I_2 = & \langle a_1, a_2, b_3, b_4, s \rangle \\
+    I_3 = & \langle a_1, a_2, b_3^2, a_4b_3 + a_3b_4, a_3b_3, a_3^2, s \rangle.
+\end{array}
+$$
+It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same.
+The tableau corresponding to each ideal is
+$$
+\begin{array}{cc}\vspace{1mm}
+    \young(11111133,2222) & \text{for } I_1 \\ \vspace{1mm}
+    \young(11111122,2233) & \text{for } I_2 \\ \vspace{1mm}
+    \young(11111123,2223) & \text{for } I_3.
+\end{array}
+$$
+The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
+\end{example}
+
+\begin{example}
+Let us redo example 3 but with non-dominant weights $\mu_i$ such that $\mu_1 + \mu_2$ is still dominant. Then consider the tableaux
+$$\tau_1 = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(11,33).$$
+Then the weights are $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, and $\mu_2 = (2,0,2)$. Our matrix $X$ is now
+\[
+X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
+    0 & 1 & & & & \\
+    -s^2 & 2s & a_1 & a_2 & b_1 & b_2 \\
+     & & 0 & 1 & & \\
+     & & & 0 & b_3 & b_4 \\
+     & & & & 0 & 1 \\
+     & & & & -s^2 & 2s
+\end{BMAT}
+\right].
+\]
+Using a computer, the ideals we now get are
+$$
+\begin{array}{cl}
+    I_1 = & \langle a_1, a_2 \rangle \\
+    I_2 = & \langle b_3, b_4 \rangle \\
+    I_3 = & \langle b_3^2, a_2b_3 + a_1b_4, a_1b_3, a_1^2 \rangle. 
+\end{array}
+$$
+The tableaux corresponding to each ideal is
+$$
+\begin{array}{cc}\vspace{1mm}
+    \young(1133,22) & \text{for } I_1 \\ \vspace{1mm}
+    \young(1122,33) & \text{for } I_2 \\ \vspace{1mm}
+    \young(1123,23) & \text{for } I_3
+\end{array}
+$$
+and the MV cycles corresponding to each are the same as before.
+\end{example}
+
 \bibliographystyle{alpha}

### 2021-03-21 sage/mvy.py
rogers code redone

@@ -1,0 +1,195 @@
+# !/opt/sage/sage -python
+
+# test inputs
+
+t1 = Tableau([[1,1,3],[2]])
+t2 = Tableau([[1,2]])
+n = 3
+
+# main 
+
+def get_lambda(n,t1,t2):
+    lambda1 = [0]*n
+    lambda2 = [0]*n
+    for i in range(0,len(t1)):
+        lambda1[i] = len(t1[i])
+    for i in range(0,len(t2)):
+        lambda2[i] = len(t2[i])
+    return lambda1, lambda2
+
+lambda_1,lambda_2 = get_lambda(n,t1,t2)
+
+def get_mus(n,t1,t2):
+    mu1 = [0]*n
+    mu2 = [0]*n
+    for i in t1:
+        for j in i:
+            mu1[j-1] += 1
+    for i in t2:
+        for j in i:
+            mu2[j-1] += 1
+    mu = [a+b for a,b in zip(mu1,mu2)]
+    return mu1,mu2,mu
+
+mu1,mu2,mu = get_mus(n,t1,t2)
+m = len(mu)
+
+def mu_vars(t1,t2):
+    svs = [] # symbolic? vars
+    for i in range(1,m):
+        for j in range(i+1,m+1):
+            for k in range(0,mu[j-1]):
+                svs.append('x_{}_{}_{}'.format(i,j,k+1))
+    return svs
+
+svs = mu_vars(t1,t2)
+R = PolynomialRing(GF(101),svs) # no s!
+R.inject_variables()
+
+var('x,s')
+
+def insert_row(mat,row):
+    return matrix(mat.rows()[:mat.nrows()]+[row]+mat.rows()[mat.nrows():])
+
+def upper_row_matrix(row):
+    symbMat = []
+    for i in range(row,m):
+        mat = matrix(mu[row-1]-1,mu[i])
+        v = [var(v) for v in svs if v.startswith('x_{}_{}'.format(row,i+1))]
+        d = insert_row(mat,v)
+        symbMat.append(d)
+    return symbMat
+
+def mu_matrix(t1,t2):
+    symbMat = []
+    for i in range(0,m):
+        row = [] + [0]*i
+        p = x**(mu1[i])*(x-s)**(mu2[i])
+        row.append(companion_matrix(p.coefficients(x,sparse=False),format='bottom'))
+        row += upper_row_matrix(i+1)
+        symbMat.append(row)
+    return block_matrix(symbMat)
+
[…]

### 2021-03-21 sage/anne.py
various changes to sage files

@@ -1,7 +1,7 @@
 # !/opt/sage/sage -python
 
 # Given a sequence $\mu = (\mu_0,\ldots,\mu_m-1)\vdash N$ we wish to output an N by N matrix which takes the form that is predicted by the 
-from sage.all import *
+# from sage.all import *
 
 # returns matrix in
 # Mirkovic-Vybornov slice
@@ -21,7 +21,7 @@ def mvy(blocktype):
         for b in range(a+1,numblocks):
             for k in range(blocktype[b]):
                 # print (a,b,k)
-                # print(sum(blocktype[i] for  i in range(a+1))-1,sum(blocktype[i] for  i in range(b))+k)
+                # print(sum(blocktype[i] for  i in range(a+1))-1,sum(blocktype[i] for  i in range(b))+k
                 T[sum(blocktype[i] for  i in range(a+1))-1,sum(blocktype[i] for  i in range(b))+k] = stars[counter]
                 counter+=1
     return T

### 2021-03-21 sage/mvy.py

@@ -1,5 +1,7 @@
 # !/opt/sage/sage -python
 
+from sage.symbolic.expression_conversions import polynomial 
+
 # test inputs
 
 t1 = Tableau([[1,1,3],[2]])
@@ -8,7 +10,7 @@ n = 3
 
 # main 
 
-def get_lambda(n,t1,t2):
+def get_lambdas(n,t1,t2):
     lambda1 = [0]*n
     lambda2 = [0]*n
     for i in range(0,len(t1)):
@@ -17,7 +19,7 @@ def get_lambda(n,t1,t2):
         lambda2[i] = len(t2[i])
     return lambda1, lambda2
 
-lambda_1,lambda_2 = get_lambda(n,t1,t2)
+lambda_1,lambda_2 = get_lambdas(n,t1,t2)
 
 def get_mus(n,t1,t2):
     mu1 = [0]*n
@@ -46,7 +48,7 @@ svs = mu_vars(t1,t2)
 R = PolynomialRing(GF(101),svs) # no s!
 R.inject_variables()
 
-var('x,s')
+
 
 def insert_row(mat,row):
     return matrix(mat.rows()[:mat.nrows()]+[row]+mat.rows()[mat.nrows():])
@@ -60,6 +62,8 @@ def upper_row_matrix(row):
         symbMat.append(d)
     return symbMat
 
+var('x,s')
+
 def mu_matrix(t1,t2):
     symbMat = []
     for i in range(0,m):
@@ -68,24 +72,43 @@ def mu_matrix(t1,t2):
         row.append(companion_matrix(p.coefficients(x,sparse=False),format='bottom'))
         row += upper_row_matrix(i+1)
         symbMat.append(row)
-    return block_matrix(symbMat)
+    return block_matrix(R['s'],symbMat)
 
-tmp = mu_matrix(t1,t2) 
-T = tmp.change_ring(PolynomialRing(GF(7),tmp.variables()))  
+# tmp = mu_matrix(t1,t2) 
+# T = tmp.change_ring(PolynomialRing(GF(7),tmp.variables()))  
 
-from sage.symbolic.expression_conversions import polynomial 
+# from sage.symbolic.expression_conversions import polynomial 
 
-Ts = T - polynomial(s,base_ring=GF(7))
+# Ts = T - polynomial(s,base_ring=GF(7))
+
+def mu_matrices_over_gf(t1,t2):
+    T = mu_matrix(t1,t2) 
[…]

### 2021-03-21 draft.tex
notes on last mtg added so we remember whats left to do

@@
 which we will view in $\GL_m(K) $ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it 
-\acom{Add warning that we will also write $(t-s)^\mu$ for its image in $\GL_m(K)/\GL_m(R)$. We hope it will be evident?}
+\acom{1.
+Add warning that we will also write $(t-s)^\mu$ for its image in $\GL_m(K)/\GL_m(R)$.
+We hope it will be evident?
+2.
+Change notation $\mu = (\mu_1,\dots,\mu_m)$ since we also have $\mu = \mu_1 + \mu_2$.
+We could do $\mu = \mu' + \mu''$ or $\mu = a + b$?
+The notation $\mu^{(i)}$ is alreayd taken to mean sth.
+Ofc all can be changed.
+Can also do $\mu = {}_{1}\mu + {}_{2}\mu$}
 
@@
 % The trivial lattice is 
-$ L_0(R) = R^m \subset K^m $ is called the standard lattice. 
-We will abuse notation and denote $L_0(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
+% No more: L_0(R) = 
+$ R^m \subset K^m $ is called the standard lattice. 
+% We will abuse notation and denote $L_0(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
 The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
@@
 this set and $\GL_m(K)/\GL_m(R)$. 
-\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$.
-If $e_1,\dots,e_m$ denote the standard basis elements of $L_0(\cO)$ then
+\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
+% $L_0(\cO)$ then 
+$\cO^m$ then 
 $$ 
@@
 $$
-If $ L(a) = L_0(\cO_a)$ then $L$ is said to be trivial at $a$. 
+If 
+% $ L(a) = L_0(\cO_a)$ 
+$L(a) = \cO_a^m$ then $L$ is said to be trivial at $a$. 
 % We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
@@
 % G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
-Set $\AA = \AA^1$ and let $V_0$ denote the trivial rank $ m $ vector bundle.
+Set $\AA = \AA^1$ and let $V_0$ denote the trivial rank $ m $ vector bundle. \acom{Change $V_0$}
 
@@
 \begin{itemize}
-    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
+    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by \acom{Change $V_0$}
     $$
@@
     We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, V_0)$ using $ \varphi$.
-On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap}
+On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap} \acom{Change $V_0$}
     % 
@@
     % \acom{should it be $\AA$ instead of $\CC$} 
-    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
+    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by \acom{Change $V_0$}
     $$
@@
     \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
-    It is described in modular terms by
+    It is described in modular terms by \acom{Change $V_0$}
     % {\small
@@
 over $ \PP$).
+\acom{Change $V_0$}
 
@@
         \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$. \acom{Should we describe this map somewhere? Earlier?}
-        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$. \acom{vestigial $L_0$}
+        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$. \acom{vestigial $L_0$ change to $\CC[t]^m$}
         \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$.
@@
 \begin{proof}
-First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\cO)t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$.
+First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\cO)t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$. \acom{Change $L_0$}
 
@@
     \end{enumerate}
-    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
+    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$. \acom{Change $L_0$}
 \end{lemma}
@@
 By construction, the polynomial $ p_{ij}$ has degree less than $ \mu_i$.
+\acom{Change $L_0$}
 
@@
 \end{lemma}
-\acom{the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too..
+\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?}}
+% Resolved?
+the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too..
 Anyway I think that you address this below Joel.
-Probably it is worth writing out the map just before this first occurence?
-\textit{is it $(L,s)\mapsto L$?}}
 
@@
 
+% TODO: un-appendicize 
 \appendix
+
 \section{Generalized orbital varieties?}
 TODO: recall $\tau\mapsto X_\tau \mapsto Z_\tau$
+
+\begin{question}
+    Smallest $\mu_1, \mu_2$ such that\dots?
+\end{question}
+
 \section{Tableaux and families}
+
 TODO: $Z_1\ast_\AA Z_2$ is described by $\tau_1\ast\tau_2$ or $\tau_1\sqcup\tau_2$
+
+\begin{question}
+    How do we know that our algorithm produces MV cycles? 
+\end{question}
+
+\begin{proposition}
+    Let $\tau_1,\tau_2$\dots 
+    \[
+    \{A\in\UU_{0,s}^{\mu_1,\mu_2} : A \big|_{\mu^1 + \cdots + \mu^i} \in \OO_{0,s}^{\lambda_{1}^{(i)},\lambda_2^{(i)}} \text{ all } i\} = Z_{\tau_1}\times Z_{\tau_2}
+    \]
+\end{proposition}
+
+\begin{proof}
+    Want $L(0) \in Z(\tau_1)$ and $L(s) = Z(\tau_2)$. \acom{Another notational possibility is $\mu = \mu^0 + \mu^s$ etc., or $\mu(0) + \mu(s)$ or some variant with the eigenvalues being the indices.}
+
+    Fix $i \in \{1,\dots,m\}$ and let $p = \mu^1 + \cdots + \mu^i$. 
+    % Define $\lambda^{(i)}(\tau_1 \circ \tau_2)$ so that the 
+    Jordan type of $t\big|_{\CC[t]^p/L(0)\cap\CC[t]^p}$ is $\lambda_1^{(i)}$ and Jordan type of $t\big|_{\CC[t]^p/L(s)\cap \CC[t]^p}$ is $\lambda_2^{(i)}$.
+
+    Need that the operations of taking quotients and taking generalized eigenspaces (i.e.\ $-\otimes\CC\xt[t-a]$) commute.
+\end{proof}
+
+\begin{question}[Related question]
+    If $\mu_1,\mu_2$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
+    \[
+    \begin{tikzcd}
+        \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu_1,\mu_2}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
+        \overline\OO^{\lambda_1,\lambda_2} \cap \UU^{\mu_1,\mu_2} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
+    \end{tikzcd}    
+    \]
+\end{question}
+
 \section{Examples}

### 2021-03-23 sage/mvy.py
function now works. but not correct.

@@ -4,9 +4,9 @@ from sage.symbolic.expression_conversions import polynomial
 
 # test inputs
 
-t1 = Tableau([[1,1,3],[2]])
-t2 = Tableau([[1,2]])
-n = 3
+t1 = Tableau([[1,3]])
+t2 = Tableau([[1,3],[2],[4]])
+n = 4
 
 # main 
 
@@ -48,7 +48,10 @@ svs = mu_vars(t1,t2)
 R = PolynomialRing(GF(101),svs) # no s!
 R.inject_variables()
 
-
+gen_str = ''
+for g in R.gens():
+    gen_str += str(g) + ', '
+S = PolynomialRing(GF(101), gen_str + 's')
 
 def insert_row(mat,row):
     return matrix(mat.rows()[:mat.nrows()]+[row]+mat.rows()[mat.nrows():])
@@ -72,12 +75,12 @@ def mu_matrix(t1,t2):
         row.append(companion_matrix(p.coefficients(x,sparse=False),format='bottom'))
         row += upper_row_matrix(i+1)
         symbMat.append(row)
-    return block_matrix(R['s'],symbMat)
+    return block_matrix(S,symbMat)
 
-# tmp = mu_matrix(t1,t2) 
-# T = tmp.change_ring(PolynomialRing(GF(7),tmp.variables()))  
+# tmp = mu_matrix(t1,t2)
+# T = tmp.change_ring(PolynomialRing(GF(7),tmp.variables()))
 
-# from sage.symbolic.expression_conversions import polynomial 
+# from sage.symbolic.expression_conversions import polynomial
 
 # Ts = T - polynomial(s,base_ring=GF(7))
 
@@ -86,7 +89,7 @@ def mu_matrices_over_gf(t1,t2):
     # T = tmp.change_ring(PolynomialRing(GF(7),tmp.variables()))
     return T,  T - polynomial(s,base_ring=GF(101))  
 
-# create submatrices 
+# create submatrices
 
 # size = mu[0]
 
@@ -131,7 +134,7 @@ def create_ideal(t1,t2):
     Tsubs,Tssubs = mu_submatrices_over_gf(mat,mats)
     rel = []
     # J_0 = ideal(0)
-    J_0 = R['s'].ideal([])
+    J_0 = S.ideal([]).primary_decomposition()
     size = mu[0]
     for i in range(1,m):
         size_0 = size
@@ -150,38 +153,37 @@ def create_ideal(t1,t2):
[…]

### 2021-03-23 sage/mvy.py
added local declaration

@@ -48,8 +48,6 @@ svs = mu_vars(t1,t2)
 R = PolynomialRing(GF(101),svs) # no s!
 R.inject_variables()
 
-
-
 def insert_row(mat,row):
     return matrix(mat.rows()[:mat.nrows()]+[row]+mat.rows()[mat.nrows():])
 
@@ -153,11 +151,13 @@ def create_ideal(t1,t2):
             good_ideals = [] # not sure where best to init this 
             print(rel)
             print(ideal(rel).base_ring())
+            print(type(ideal(rel)))
+            print(type(R['s'].ideal(rel)))
             # print(ideal(rel).groebner_basis())
             if rel != []:
-                # J = ideal(ideal(rel).groebner_basis()).primary_decomposition()
+                J = R['s'].ideal(R['s'].ideal(rel).groebner_basis()).primary_decomposition()
                 # J = ideal(rel).primary_decomposition()
-                J = R['s'].ideal(rel)
+                # J = R['s'].ideal(rel)
                 for K in J:
                     rk_old = rk_old_start
                     t1_sub_old = t1_sub_old_start
@@ -207,7 +207,7 @@ def create_ideal(t1,t2):
                         t2_sub_old = [l[1:] for l in t2_sub_old if l != []]
                         kerTs_old += len([l for l in t2_sub_old if l != []])
                         rk_old = size_0 - kerTs_old
-                    if res == True and K.gens() != [0] and True in (polynomial(s,base_ring=GF(7)).divides(ele) for ele in K.gens()):
+                    if res == True and K.gens() != [0] and True in (polynomial(s,base_ring=GF(101)).divides(ele) for ele in K.gens()):
                         res = False
                     if res == True and J != J_0 and not True in [True in (str(v).startswith('x_{}_{}'.format(n,i+1)) for v in K.gens().variables()) for n in range(1,i+1)]:
                         res = False

### 2021-03-29 draft.tex
joels latest changes some notational

@@
 \subsection{Groups}
-
+Let $H $ be an algebraic group over $ \CC $.
+We will be interested $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.
+Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.
+We denote the kernel of this map by $ H_1(\cO_s)$.
+We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$ which is often called the first congruence subgroup.
 % \acom{Add $G_1$}
-\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$.
+%\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$.
 The affine space of $m\times m$ matrices which we denote $ M_m$.
@@
 
+We will also be interested in the affine space $ M_m$ of $m$x$m$ matrices.
+Note that for any $ \CC$-algebra $ R $,  $GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
+Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.
+
 \subsection{Lattices}
 \label{ss:lat}
-We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field). 
+We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
 % \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
@@
 % the set of such lattices 
-this set and $\GL_m(K)/\GL_m(R)$. 
+this set and $\GL_m(K)/\GL_m(R)$, since $ GL_m(R) $ is the stabilizer of the standard lattice. 
 \acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
@@
 % G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
-Set $\AA = \AA^1$ and let $V_0$ denote the trivial rank $ m $ vector bundle. \acom{Change $V_0$}
+Set $\AA = \AA^1$ and let $\Vtriv$ denote the trivial rank $ m $ vector bundle.
 
@@
 \begin{itemize}
-    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by \acom{Change $V_0$}
+    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by %\acom{Change $V_0$}
     $$
     % \Gr = 
-    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0^\times $} \right\} \,. 
+    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_0^\times $} \right\} \,. 
     $$
@@
     $$
-    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, V_0)$ using $ \varphi$.
+    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.
 On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap} \acom{Change $V_0$}
@@
     % \acom{should it be $\AA$ instead of $\CC$} 
-    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by \acom{Change $V_0$}
-    $$
+    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by     $$
     % \Gr_s = 
-    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D^\times_s $} \right\}\,.
+    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,.
     $$
@@
     $$
-        % \Grth = 
-        % \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
+         \Grth = 
+         \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
     $$
@@
         \left\{ 
-            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} V_0 \text{ on } \PP \setminus \{0, s\}  
+            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} \Vtriv \text{ on } \PP \setminus \{0, s\}  
         \right\} 
@@
 \begin{enumerate}
-    \item First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
-    \item Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
+    \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
+    \item We have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
     % $$ \Grbd \rightarrow \Grth $$ 
@@
 The following construction will be very important in this paper.
+First, we recall that we have an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $, 
+for each $ s \ne 0$.  In turn, we have the isomorphism $ \Gr_s \cong \Gr$.
+
+Gluing these together, we obtain
+$$
+\tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr_{\CC^\times} \rightarrow \Gr \times \Gr
+$$
+where the first morphism is an isomorphism and the second map uses $ \Gr_s \cong \Gr $ on each fibre.
+(This $\tau$ matches the map $ \tau $ of \cite{mirkovicvilonen}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
+
 Let $ X_1, X_2 \subset \Gr$ be two subschemes.
-Then using the isomorphism $ \Gr \cong \Gr_s $, for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.
-% <<<<<<< HEAD
-% Via \ul{this} \acom{rather, the above? $L\mapsto (L(0),L(s))$} 
-Next, using the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $, 
-for each $ s \ne 0$,  
-\rcom{Joel: usually written $\Gr_{0,\AA^\times} \cong \Gr \times \Gr_s \times \AA^\times$, cite MVi} 
-we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
+We define the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
+
+\jcom{I changed this a bit in order to match Mirkovic-Vilonen better.}
 % =======
@@
 
-We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
-We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
+We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  
+Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $ and define $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
 We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
+
+By this construction, $X_1 \ast_{\AA} X_2 $ is a flat family over $\CC$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
+
 % \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
@@
 \subsection{Some subvarieties of affine Grassmannians}
-Now fix effective dominant coweights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$. 
+Now fix effective dominant coweights $\lambda_1, \lambda_2 \in P_{++}$ of sizes $N_1, N_2$  and their sums $ \lambda = \lambda_1 + \lambda_2 $ of size $ N = N_1 + N_2$. 
 % Coweights define elements in the various affine Grassmannians which we consider.
@@
 % the right cosets which they represent are clear from the context.
-
-\acom{At some point at least mention that we expect this to go through for permutations of $\mu_i\in P_{++}$ i.e.\ skew partitions?
-or non-dominant and non-negative coweights; so long as their sum $\mu_1 + \mu_2$ is effective dominant.}
-
-The following subsets are indexed by coweights. 
+We consider the following subschemes of the affine Grassmannians.
 % 
@@
     % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
-    Over $s=0$ the fibre is shown to be $ \overline{\Gr}^{\lambda_1 + \lambda_2}$ in the proof of \cite[Proposition 3.1.14]{zhu2016introduction}.
+    Over $s=0$ the fibre is shown to be $ \overline{\Gr}^{\lambda_1 + \lambda_2}$ by a theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}.
 
@@
     % \acom{Why $G(\CC[t])$. Because we are on the left side!}
-
-    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
-    % 
-    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.
-And unless $ A $ is nilpotent, then $g(A)$ won't live there.} \acom{But our $A$ is always nilpotent?
-Another notational thing is $G_1\xt[t^{-1}] = G_1(\CC\xt[t^{-1}])$ and in our paper this short hand is only used for these kernel subgroups.}
+\end{itemize}
+Now fix two effective coweights $ \mu_1, \mu_2 \in \mathbb N^m$ such that $ \mu_i$ has size $ N_i$ and such that $ \mu_1 + \mu_2 $ is dominant.
+Using $ \mu_1, \mu_2$, we define the following subschemes.
+
+\begin{itemize}
+    \item The locus $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
+    % 
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
@@
     % 
-    \item The semi-infinite orbit $ S^\mu = N(\cK)t^\mu \subset \Gr $.  
+    \item The semi-infinite orbit $ S^\mu = N_-(\cK)t^\mu \subset \Gr $.  
     \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
@@
     % S^{\mu_1, \mu_2}_{0,s} = 
-    N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
+    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
     $$
@@
 
-    \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.}
+    \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.  I changed $ N$ to $ N_-$.}
     % TODO!
@@
 % Denote by $R_i$ the $i$th row of $J$ 
-Let $g = E_{\lambda_2}\cdots E_1$ be the product of elementary matrices $E_i$ which correspond to the elementary row operations 
-$$R_{\lambda_1 + i - 1} \leftarrow R_{\lambda_1 + i-1} + \frac 1s R_{\lambda_1 + i}$$ 
-for $i = 1,\dots,\lambda_2$. Then $gJg^{-1} = A$. For the next part we introduce the notation $A_{\lambda_1+\lambda_2}$ for this matrix $A$.
-
-Now let $\lambda_1,\lambda_2$ be arbitrary. Clearly $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to 
-$$\bigoplus_{i=1}^m (J_{\lambda_{1,i}}\oplus J_{\lambda_{2,i}})\,.$$ 
-Moreover each block $J_{\lambda_{1,i}}\oplus J_{\lambda_{2,i}}$ is conjugate to $A_{\lambda_{1,i}+\lambda_{2,i}}$.
+%Let $g = E_{\lambda_2}\cdots E_1$ be the product of elementary matrices $E_i$ which correspond to the elementary row operations 
+%$$R_{\lambda_1 + i - 1} \leftarrow R_{\lambda_1 + i-1} + \frac 1s R_{\lambda_1 + i}$$ 
+%for $i = 1,\dots,\lambda_2$. Then $gJg^{-1} = A$. For the next part we introduce the notation $A_{\lambda_1+\lambda_2}$ for this matrix $A$.
+
+%Now let $\lambda_1,\lambda_2$ be arbitrary. Clearly $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to 
+%$$\bigoplus_{i=1}^m (J_{\lambda_{1,i}}\oplus J_{\lambda_{2,i}})\,.$$ 
+%Moreover each block $J_{\lambda_{1,i}}\oplus J_{\lambda_{2,i}}$ is conjugate to $A_{\lambda_{1,i}+\lambda_{2,i}}$.
 Altogether $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to $\bigoplus_{i = 1}^m A_{\lambda_{1,i}+\lambda_{2,i}}$ and this latter matrix specializes to the Jordan normal form $J_{0,\lambda_1 + \lambda_2}$ at $s=0$.
@@
     \item Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$.
-The Mirkovic--Vybnornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that
+The Mirkovic--Vybornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that
     \[
@@
     In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
-    Mirkovic and Vybornov describe $\TT_\mu$ as the slice in which $f$ acts as close to regular nilpotent as possible.
     % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
@@
     \]
-    % 
-    %\acom{this ok?} % \jcom{Anne, can you add this definition?}
-    %\jcom{When you wrote ``In words,'', it is not quite correct because of the diagonal blocks have those 1s.  Also it would be good to have an example.  And what is $f$ in the last sentence? }
-    %\acom{fixed? As for $f$ I think it is an $\sl_2$ triplet. Hopeful you could explain what MVy meant bc I never quite understood!}
 
@@
         \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$. \acom{Should we describe this map somewhere? Earlier?}
-        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$. \acom{vestigial $L_0$ change to $\CC[t]^m$}
+        \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
         \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$.
@@
                 \item $ L = \Sp_{\CC[t]}(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1}^m p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
-\acom{Do we want to sum over $j \ne i$ here?
-Maybe nvm because in $\TT_\mu$ the diagonal blocks can have $*$'s in the last row.
-Also $\cO$ should be $\CC[t]$.}
         \item  For all $ i $, 
@@
 Then $ L = \Sp_{\CC[t]}(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \Oinf$.
-Since $ L \in \Grth^+ $, we see that $ v_i \in L_0$ which means that $ p_{ij} := q_{ij}t^{\mu_i} $ lies in $ \CC[t]$.
+Since $ L \in \Grth^+ $, we see that $ v_i \in \CC[t]^m$ which means that $ p_{ij} := q_{ij}t^{\mu_i} $ lies in $ \CC[t]$.
 By construction, the polynomial $ p_{ij}$ has degree less than $ \mu_i$.
-\acom{Change $L_0$}
 
@@
 
-\jcom{I was thinking about the proof of this result.
+%\jcom{I was thinking about the proof of this result.
 It is enough to prove that for $ A \in \OO^{\lambda_1, \lambda_2}_s \cap \TT_\mu $, $g(A) \in S^{\mu_1, \mu_2}_s $ if and only if $ A \in T^+$.
@@
 % 
-\acom{Assuming Theorem 2 we think this follows by application of Roger's lemma. Also, I think my thesis is complete on this point.}
-% 
-\jcom{I thought about this and I agree with you now.  I will write this up soon.} 
-% 
-\acom{But I am also curious about the attracting set approach.}
+%\acom{Assuming Theorem 2 we think this follows by application of Roger's lemma. Also, I think my thesis is complete on this point.}
+% 
+%\jcom{I thought about this and I agree with you now.  I will write this up soon.} 
+% 
+%\acom{But I am also curious about the attracting set approach.}
 
 \begin{proof}
+We could prove this by observing the both sides are the attracting locus of an appropriate $ \CC^\times$ action. However, we will give the following more algebraic proof.
+
  Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu_1, \mu_2}_{0,\AA} $.
 
- On the one hand, if $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA} $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu_1} (t-s)^{\mu_2}$, and so $ g(A) \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+ On the one hand, if $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA} $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu_1} (t-s)^{\mu_2}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
 
@@
 $$
-for some $ r \in G(\CC[t]), n \in N[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1\xt[t^{-1}] $.
+for some $ r \in G(\CC[t]), n \in N_-[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1\xt[t^{-1}] $.
 Note that $ h^{-1}n h \in N(\Kinf)$, 
 % ((t^{-1}))
-so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t])$.  So then after doing a bit of algebra, we reach
+so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_{-,1}(\Oinf), n_2 \in N_-(\CC[t])$.  So then after doing a bit of algebra, we reach
 $$
@@
 
-\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
+%\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
 To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.

### 2021-03-29 rogers_exchange_relations_examples.tex
major overhaul in the sage folder

--- 2021-02-14 exchange relations examples.tex
@@
 $$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,a_3,b_1,b_3,b_2c_3,b_4c_3 \rangle} \cong \frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2,b_4 \rangle \cap \langle c_3 \rangle}$$
-However, for the ideal $\langle c_3 \rangle$, we require $\dim \ker (X|_{s = 0}) = 3$ so we also need to include the equation ${\color{red} b_2c_2 - b_4c_1 = 0}$. Then the coordinate ring is really
+However, for the ideal $\langle c_3 \rangle$, we require $\dim \ker (X|_{s = 0}) = 3$ so we also need to include the equation ${\color{red} b_2c_2 - b_4c_1 = 0}$ \rcom{this equation shows up in the script, so it's one of the minors}.
+Then the coordinate ring is really
 $$\frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2,b_4 \rangle \cap \langle c_3,b_2c_2-b_4c_1 \rangle}$$
@@
 $$ \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3,c_4,c_6]}{\langle a_3,b_2c_3-b_4c_1,c_1+b_2c_6 \rangle \cap \langle b_4,c_3,c_1+a_3c_4+b_2c_6 \rangle}$$
+\rcom{The script also has the equations $b_4c_6 + c_3$ and $b_2c_3c_6 + c_1c_3$ in the ideal.
+With this, the decomposition is the same except the first ideal also has $b_4c_6 + c_3$.
+The tableaux we get remain the same.}
 The corresponding tableau for each ideal is:
@@
 $$ \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3,c_4,c_6]}{\langle b_4,c_3 \rangle \cap \langle b_2c_6-c_1,c_3+b_4c_6 \rangle}$$
+\rcom{The script also has the equation $b_2c_3c_6 + c_1c_3$ in the ideal. In the decomposition, the second ideal also has $b_2c_3 - c_1b_4$. The corresponding tableaux are unchanged.}
 The corresponding tableau for each ideal is:

### 2021-03-29 sage/mvy.py

@@ -1,362 +1,0 @@
-# !/opt/sage/sage -python
-
-from sage.symbolic.expression_conversions import polynomial 
-
-# test inputs
-
-# t1 = Tableau([[1,3]])
-# t2 = Tableau([[1,3],[2],[4]])
-# n = 4
-
-# t1 = Tableau([[1,2]])
-# t2 = Tableau([[1,1],[2,3]])
-# n = 3
-
-# ok
-# t1 = Tableau([[1,1],[2,2],[3,4]])
-# t2 = Tableau([[1,1],[2,3]])
-# n = 4 
-
-# t1 = Tableau([[1,2]])
-# t2 = Tableau([[1,1],[2,3],[4]])
-# n = 4
-
-# t1 = Tableau([[1,2]])
-# t2 = Tableau([[1,1],[2,4],[3]])
-# n = 4
-
-# t1 = Tableau([[1,1],[2,2],[3,4]])
-# t2 = Tableau([[1,2],[3]])
-# n = 4
-
-# t1 = Tableau([[1,1],[2,2],[3,4]])
-# t2 = Tableau([[1,3],[2]])
-# n = 4
-
-# t1 = Tableau([[1,1],[2,4],[3]])
-# t2 = Tableau([[1,3],[2]])
-# n = 4
-
-# t1 = Tableau([[1,1],[2,3],[4]])
-# t2 = Tableau([[1,2],[3]])
-# n = 4
-
-# t1 = Tableau([[1,1],[2,3]])
-# t2 = Tableau([[1,3],[2],[4]])
-# n = 4
-
-# t1 = Tableau([[1,1],[2,3]])
-# t2 = Tableau([[1,1,2],[2,4],[3]])
-# n = 4
-
-# t1 = Tableau([[1,3],[2],[4]])
-# t2 = Tableau([[1,2],[3]])
-# n = 4 
-
-# t1 = Tableau([[1,1,2],[2,4],[3]])
-# t2 = Tableau([[1,3],[2]])
-# n = 4
-
-# t1 = Tableau([[1,1],[2,4],[3]])
-# t2 = Tableau([[1,3],[2],[4]])
-# n = 4
-
-# t1 = Tableau([[1,1,2],[2,4],[3]])
-# t2 = Tableau([[1,1],[2,3],[4]])
-# n = 4
-
-# t1 = Tableau([[1,1,2],[2,4],[3]])
[…]

### 2021-03-29 sage/mvy_ideal_maker.py

@@ -2,6 +2,9 @@
 
 from sage.symbolic.expression_conversions import polynomial 
 
+# file = open('test.txt','w')
+# file2 = open('test2.txt','w')
+
 # test inputs
 
 # t1 = Tableau([[1,3]])
@@ -70,13 +73,20 @@ from sage.symbolic.expression_conversions import polynomial
 # n = 4
 
 # rly bad
-t1 = Tableau([[1,3],[2,5],[4]])
-t2 = t1
-n = 5
+# t1 = Tableau([[1,3],[2,5],[4]])
+# t2 = t1
+# n = 5
 
-# main 
+# rly rly bad
+t = Tableau([[1,3],[2,5],[4],[6]])
 
-def get_lambdas(n,t1,t2):
+# main
+
+def get_n(t1,t2):
+    return max(len(t1.weight()),len(t2.weight()))
+
+def get_lambdas(t1,t2):
+    n = get_n(t1,t2)
     lambda1 = [0]*n
     lambda2 = [0]*n
     for i in range(0,len(t1)):
@@ -85,9 +95,8 @@ def get_lambdas(n,t1,t2):
         lambda2[i] = len(t2[i])
     return lambda1, lambda2
 
-lambda_1,lambda_2 = get_lambdas(n,t1,t2)
-
-def get_mus(n,t1,t2):
+def get_mus(t1,t2):
+    n = max(len(t1.weight()),len(t2.weight()))
     mu1 = [0]*n
     mu2 = [0]*n
     for i in t1:
@@ -96,83 +105,99 @@ def get_mus(n,t1,t2):
     for i in t2:
         for j in i:
             mu2[j-1] += 1
-    mu = [a+b for a,b in zip(mu1,mu2)]
-    return mu1,mu2,mu
+    # mu = [a+b for a,b in zip(mu1,mu2)]
+    return mu1,mu2
+    # ,mu
 
-mu1,mu2,mu = get_mus(n,t1,t2)
-m = len(mu)
+def get_mu(t1,t2):
+    mu1,mu2 = get_mus(t1,t2)
+    return [a+b for a,b in zip(mu1,mu2)]
 
-def mu_vars(t1,t2):
-    svs = [] # symbolic? vars
+def get_lambda(t1,t2):
+    lambda1,lambda2 = get_lambdas(t1,t2)
+    return [a+b for a,b in zip(lambda1,lambda2)]
+
+def mu_vars(mu):
+    m = len(mu)
+    svs = []
[…]

### 2021-03-29 draft.tex
major overhaul in the sage folder
unappedicized appendix

@@
 
-\jcom{I changed this a bit in order to match Mirkovic-Vilonen better.}
+\jcom{I changed this a bit in order to match Mirkovic--Vilonen better.}
 % =======
@@
 % TODO: un-appendicize 
-\appendix
-
-\section{Generalized orbital varieties?}
+% \appendix
+
+\subsection{Generalized orbital varieties?}
 TODO: recall $\tau\mapsto X_\tau \mapsto Z_\tau$
@@
 
-\section{Tableaux and families}
+\subsection{Tableaux and families}
 
@@
 
-    Need that the operations of taking quotients and taking generalized eigenspaces (i.e.\ $-\otimes\CC\xt[t-a]$) commute.
+    Need: operations of taking quotients and taking generalized eigenspaces (i.e.\ $-\otimes\CC\xt[t-a]$) commute.
+
+    \acom{Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}
 \end{proof}
@@
         \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu_1,\mu_2}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
-        \overline\OO^{\lambda_1,\lambda_2} \cap \UU^{\mu_1,\mu_2} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
+        \overline\OO^{\lambda_1,\lambda_2}_{0,s} \cap \UU^{\mu_1,\mu_2}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
     \end{tikzcd}    
@@
 
-\section{Examples}
+\subsection{Examples}
 \rcom{I have 3 examples in mind right now: fusion product producing 1 term (maybe $1 \leftarrow 2 * 1 \rightarrow 2$), fusion product producing more than 1 term $(S_1 * S_2)$, and fusion product with multiplicities $((S_1 * S_2)^2)$}

### 2021-03-31 draft.tex
minor moves

@@
 
-    \begin{remark}
+% TODO: delete commented out remark and subcomment!
+% \begin{remark}
+\begin{comment}
         Base case $m = 1$: by a slight abuse of notation let $\lambda_1, \lambda_2 \in \NN$. Claim: $J=J_{0,\lambda_1} \oplus J_{s,\lambda_2}$ is conjugate to
@@
 % \end{pNiceArray}$
-\begin{comment}
 \[
@@
 
-\acom{The following is a rough note.}
-
-The relevant result from Eisenbud--Saltman seems to be that 
-$$X_r = X_{r,0} = \{A:\rk A^i \le r(i) \}$$ 
-is the flat limit of 
-$$X_{r,\lambda} = \{A : \rk (A-\lambda_i)^j\le r(i,j)\}$$
-with $r(i,j)$ determined by $r(i)$.
-
-The case that we are interested in is the case of two eigenvalues. Let me change notation so that $\lambda_i$ are shapes and let me only look at the open loci where the rank conditions are strict.
-
-Let $m_i = \lambda_{i,1}$ ($i = 1,2$), $m = m_1 + m_2$, and define
-$$r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda_1 + \lambda_2 = \lambda\vdash N$$
-on $j = 1,\dots,m$. Note that $r(j-1) - r(j)$ is the length of the $j$th column of $\lambda$. As in \cite{eisenbud1989rank} we will denote this quantity $a_j$. 
-%
-
-Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(m_1)}$ are the (lengths of) columns of $\lambda_1$ and $a_{p(m_1 + 1)},\dots, a_{p(m_1 + m_2)}$ are the (lengths of) columns of $\lambda_2$.
-Then the functions 
-$$
-\begin{aligned}
-r(1,j) &= N - a_{p(1)} - \cdots - a_{p(j)} \\
-% \text{ and } 
-r(2,j) &= N - a_{p(m_1 + 1)} - \cdots - a_{p(m_1 + j)}
-\end{aligned}
-$$
-are such that 
-\begin{align*}
-    \OO^{\lambda_1,\lambda_2}_{0,s} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots, m_1 \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = m_1 + 1 ,\dots, m \}
-\end{align*}
-and according to \cite[Theorem 2.1(iii)]{eisenbud1989rank} the family $X_{r,\AA^m}$ is flat over $\AA^m$ with zero fibre $X_{r,0} = \OO^\lambda$ as desired.
-I guess we need to carefully choose the $W \subset \AA^m$ defining our family, which is smaller than the family $X_{r,\AA^m}$.
-Well, $W$ is just cut out by $0 = x_1 = x_2 = \cdots = x_{m_1}$ and $ x_{m_1 + 1} = \cdots = x_m$.
-Or some permutation thereof to match the permutation $p$ above.
-
-% On the one hand, we know that $r(i,j)$ should be equal to $N$ minus the number of boxes in the first $j$ columns of $\lambda_i$.
-On the other hand, ES define $r(i,j)$ to be $N$ minus the $i$th chunk of $j$ columns determined by the rank function $r(i)$.
-Also, we would like for $r(i)$ to determine the shape $\lambda = \lambda_1 + \lambda_2$.
-Take for example $\lambda_1 = \lambda_2 = (2,1)$.
-Then $\lambda = (4,2)$ and so $r\{0,1,2,3,4\}=\{6,4,2,1,0\}$ and
-% $$\{a_1,a_2,a_3,a_4\} = \{6-4,4-2,2-1,1-0\}=\{2,2,1,1\}\,.$$
-
-% For another example take $\lambda_1 = (1)$ and $\lambda_2 = (1,1)$. Then $\lambda = (2,1)$ and $r\{0,1,2\} = \{3,1,0\}$ so $\{a_1,a_2\} = \{2,1\}$.
-
-% Again too small.
-The problem is I don't think that it is in general true that some permutation of the list $r(i-1) - r(i)$ will be the list of lengths of columns of $\lambda_1$ followed by the list of lengths of columns of $\lambda_2$ which is what we are looking for.
-For one thing there's in general more than one way to write a partition as a sum of two partitions.
-Ok, concretely, a third example.
-Take $\lambda_1 = (a,b)$ and $\lambda_2 = (c,d)$ then $\lambda = (a + c, b + d)$ and
-% $$r\{0,1,\dots,a + c\} = \{N, N-2, \dots, N-2(b+d), N-2(b+d) - 1,\dots, 0\}$$
-% so 
-% $$\{a_1,a_2,\dots\} = \{2,2,\dots,2,1,1,\dots,1\}$$
-% with $b+d$ 2s and $a+c - b - d$ 1s.
-Wait a minute, nevermind, of course this is true.
-We have two partitions $\lambda_1$ and $\lambda_2$ and one way to form the partition $\lambda = \lambda_1 + \lambda_2$ is to break $\lambda_i$ down into columns, order the columns by length, and recombine.
-Cool.
-I think it's fine.
-\acom{That's it for the note.}
-
 % By Tanisaki $A\in \OO^\lambda$ iff the coefficients of $z^m$ in $k\times k$ minors of $zI - A$ for any $m\le p_\lambda(k) - 1$ and for any $k = 1\dots |\lambda|$ vanish.
@@
 % If we apply the change of basis $g$ to the ideal $I=I_1 + I_2$ and set $s = 0$ (if possible) do we recover the ideal of $\OO^{\lambda_1 + \lambda_2}$? Let $A^g = g(A_1 \oplus A_2) g^{-1}$...
-    \end{remark}
+% \end{remark}
 
@@
 
+% TODO: place this better? 
+% \acom{The following is a rough note.}
+
+\begin{proposition}
+    The family $\OO^{\lambda_1,\lambda_2}_{0,\AA}$ defined by \Cref{above} has zero fibre $\OO^\lambda$. 
+\end{proposition}
+
+We will show that this is a corollary of the following result on ``rank varieties''.
+
+\begin{theorem}(\cite{eisenbud1989rank})
+Let $r$ be a decreasing concave non-negative integral function with $r(0) = N$ (the dimension of the ambient vector space).
+Such a function is called a rank function.
+Then, in the space of $N\times N$ matrices,
+% The relevant result from Eisenbud--Saltman seems to be that 
+$$X_r = X_{r,0} = \{A:\rk A^i \le r(i) \}$$ 
+is the flat limit of 
+% $$X_{r,\lambda} = \{A : \rk (A-\lambda_i)^j\le r(i,j)\}$$
+$$X_{r,z} = \{A : \rk (A-z_i)^j\le r(i,j)\}$$
+with $r(i,j)$ determined by $r(i)$.  
+\end{theorem}
+
+The case that we are interested in is the case of two eigenvalues: $(z_1,z_2) = (0,s)$. \acom{Does order matter?} 
+% Let me change notation so that $\lambda_i$ are shapes and 
+We begin by considering the open loci where the rank conditions are strict.
+
+Recall that $\lambda_1 + \lambda_2 = \lambda$ is a partition of $N$. 
+Let $m_i = \lambda_{i,1}$ ($i = 1,2$), $m = m_1 + m_2$, and define
+$$r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$$
+on $j = 1,\dots,m$. Note that $r(j-1) - r(j)$ is the length of the $j$th column of $\lambda$. As in \cite{eisenbud1989rank} we will denote this quantity $a_j$. 
+%
+
+Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(m_1)}$ are the (lengths of) columns of $\lambda_1$ and $a_{p(m_1 + 1)},\dots, a_{p(m_1 + m_2)}$ are the (lengths of) columns of $\lambda_2$.
+Then the functions 
+$$
+\begin{aligned}
+r(1,j) &= N - a_{p(1)} - \cdots - a_{p(j)} \\
+% \text{ and } 
+r(2,j) &= N - a_{p(m_1 + 1)} - \cdots - a_{p(m_1 + j)}
+\end{aligned}
+$$
+are such that 
+\begin{align*}
+    \OO^{\lambda_1,\lambda_2}_{0,s} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots, m_1 \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = m_1 + 1 ,\dots, m \}
+\end{align*}
+and according to \cite[Theorem 2.1(iii)]{eisenbud1989rank} the family $X_{r,\AA^m}$ is flat over $\AA^m$ with zero fibre $X_{r,0} = \OO^\lambda$ as desired.
+I guess we need to carefully choose the $W \subset \AA^m$ defining our family, which is smaller than the family $X_{r,\AA^m}$.
+Well, $W$ is just cut out by $0 = x_1 = x_2 = \cdots = x_{m_1}$ and $ x_{m_1 + 1} = \cdots = x_m$.
+Or some permutation thereof to match the permutation $p$ above.
+
+% On the one hand, we know that $r(i,j)$ should be equal to $N$ minus the number of boxes in the first $j$ columns of $\lambda_i$.
+On the other hand, ES define $r(i,j)$ to be $N$ minus the $i$th chunk of $j$ columns determined by the rank function $r(i)$.
+Also, we would like for $r(i)$ to determine the shape $\lambda = \lambda_1 + \lambda_2$.
+Take for example $\lambda_1 = \lambda_2 = (2,1)$.
+Then $\lambda = (4,2)$ and so $r\{0,1,2,3,4\}=\{6,4,2,1,0\}$ and
+% $$\{a_1,a_2,a_3,a_4\} = \{6-4,4-2,2-1,1-0\}=\{2,2,1,1\}\,.$$
+
+% For another example take $\lambda_1 = (1)$ and $\lambda_2 = (1,1)$. Then $\lambda = (2,1)$ and $r\{0,1,2\} = \{3,1,0\}$ so $\{a_1,a_2\} = \{2,1\}$.
+
+% Again too small.
+The problem is I don't think that it is in general true that some permutation of the list $r(i-1) - r(i)$ will be the list of lengths of columns of $\lambda_1$ followed by the list of lengths of columns of $\lambda_2$ which is what we are looking for.
+For one thing there's in general more than one way to write a partition as a sum of two partitions.
+Ok, concretely, a third example.
+Take $\lambda_1 = (a,b)$ and $\lambda_2 = (c,d)$ then $\lambda = (a + c, b + d)$ and
+% $$r\{0,1,\dots,a + c\} = \{N, N-2, \dots, N-2(b+d), N-2(b+d) - 1,\dots, 0\}$$
+% so 
+% $$\{a_1,a_2,\dots\} = \{2,2,\dots,2,1,1,\dots,1\}$$
+% with $b+d$ 2s and $a+c - b - d$ 1s.
+Wait a minute, nevermind, of course this is true.
+We have two partitions $\lambda_1$ and $\lambda_2$ and one way to form the partition $\lambda = \lambda_1 + \lambda_2$ is to break $\lambda_i$ down into columns, order the columns by length, and recombine.
+Cool.
+I think it's fine.
+% \acom{That's it for the note.}
+
 \section{Exposition}
@@
 This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).
-\acom{is this map $v + L \mapsto v + L(0)$?}
+\acom{is this map $v + L \mapsto v + L(0)$?} \marginpar[]{*}
+    % todo
 
@@
     % $L_i = L\otimes \CC[(t-p_i)^{-1}]$ 
-    and $p_1 = s$ while $p_2 = 0$. \acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue? Basic linear algebra? Joel?}
+    and $p_1 = s$ while $p_2 = 0$.
+
+    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
+    carrying the action of $t $ to the action of $t$.
+
+    The left hand side is the same thing as
+    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
+    \acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue? Basic linear algebra? Joel?}
 \end{enumerate}
@@
     Need: operations of taking quotients and taking generalized eigenspaces (i.e.\ $-\otimes\CC\xt[t-a]$) commute.
-
-    \acom{Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}
+    See $(*)$ above. Also 
+    % 
+    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
+    carrying the action of $t $ to the action of $t$.
+
+    The left hand side is the same thing as
+    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
+    \acom{Restricting to an eigenspace is like inverting (forgetting) the action of $t$ by any other generalized eigenvalue.
+Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}
+
+    Exercise 2.20 from \cite{atiyah2018introduction}: If $f : A \to B$ is a ring homomorphism and $M$ is a flat $A$-module, then $M_B = B\otimes_A M$ is a flat $B$-module.
+Take $A=\CC[t]$ and $B=\CC\xt$.
+\marginpar[]{*}
 \end{proof}

### 2021-03-31 draft.tex
maybe nothing

@@
 where the first morphism is an isomorphism and the second map uses $ \Gr_s \cong \Gr $ on each fibre.
-(This $\tau$ matches the map $ \tau $ of \cite{mirkovicvilonen}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
+(This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
 

### 2021-04-01 draft.tex
added more detail to ES fact

@@
     % 
-    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.
+    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$ a consequence of Eisenbud and Salten's description/characterization(?) of ``rank varieties'' as proved in \Cref{cor:es}.
 
@@
 
-\begin{proposition}
-    The family $\OO^{\lambda_1,\lambda_2}_{0,\AA}$ defined by \Cref{above} has zero fibre $\OO^\lambda$. 
-\end{proposition}
-
-We will show that this is a corollary of the following result on ``rank varieties''.
-
 \begin{theorem}(\cite{eisenbud1989rank})
+    \label{thm:es}
 Let $r$ be a decreasing concave non-negative integral function with $r(0) = N$ (the dimension of the ambient vector space).
@@
 
-The case that we are interested in is the case of two eigenvalues: $(z_1,z_2) = (0,s)$. \acom{Does order matter?} 
+\acom{Don't know how much of this setup to recall but here are the parts that will appear in the quoted theorem.}
+% 
+ES show that 
+\begin{enumerate}
+    \item $X_r$ is a normal variety
+    \item $X_r$ is Gorenstein with rational singularities
+    \item $X_r$ fits into a flat family over $\AA^m$ of normal varieties whose fibre over a point $(z_1,\dots,z_m)$ such that the $z_i$ are all distinct is 
+\end{enumerate}
+\[
+    X_{r;z_1,\dots,z_m} = \left\{
+        A \in \End(V) : \cork(A - z_i) \ge r(i-1) - r(i) , i = 1,\dots,m 
+        \right\}
+\]
+They construct a simultaneous resolution of singularities and use the resolution of $X_r$ to describe the tangent space to $X_r$ at a point corresponding to an endomorphism $A$ such that $\rk A^i = r_i$ for all $i$.
+As an application of the tangent space computation they show that the general fiber of this family can be written as the scheme-theoretic intersection of varieties like $X_r$.
+
+To construct the resolution, they take $m$ to be the largest number such that $r(m) \ne r(m+1)$.
+% Fact: rank functions stabilize
+Let $(x_1,\dots, x_m)$ be coordinates on $\AA^m$ and let $W\subset \AA^m$ be a linear subvariety (translate of subvectorspace). 
+They introduce the flag variety $F = \{(V = V_0 \supset V_1 \supset \cdots \supset V_m \supset 0 ) : \dim V_i = r(i)\}$ and define $\mathcal X_{r,W}\subset\End(V) \times W \times F$ to be the subvariety of triples $(A,\vec z,\{V_i\})$ such that $(A-z_i) V_{i-1} \subset V_i$ for $z_i = x_i(\vec z)$ and $i = 1,\dots,m$.
+The (reduced image of) projection of $\mathcal X_{r,W}$ down to $\End(V) \times W$ is denoted $X_{r,W}$ a closed affine subvariety.
+
+\begin{theorem}
+    (\cite[Theorem~2.1 iii)]{eisenbud1989rank})
+    $X_{r,W}$ is the restriction of $X_{r,\AA^m}$ to $W$ and it is flat over $W$. 
+\end{theorem}
+
+They apply this result to study the fibers of the family $X_{r,\AA^m}$ over points $\vec z \in \AA^m$ for $z_i$ not necessarily distinct.
+They partition the coordinates $z_i$ of $\vec z$ by equality with the help of a permutation $p$ of $\{1,\dots,m\}$ such that
+\begin{align*}
+    z_{p(1)} &= \cdots = z_{p(m_1)} , \\
+    z_{p(m_1 + 1)} &= \cdots = z_{p(m_2)} , \\ 
+    \dots \\
+    z_{p(m_s + 1)} &= \cdots = z_{p(m_s + 1)}
+\end{align*}
+and $p$ preserves the order within each interval $m_i + 1,\dots,m_{i+1}$. \acom{Not sure what this means. Order of coordinates?} With this notation in place they define 
+\begin{gather*}
+    r(i,j):= \dim V - a_{p(m_i + 1)} - \cdots - a_{p(m_i + j )} \\
+    \qquad \qquad \qquad \qquad \qquad \text{ for } i = 1,\dots,s \text{ and } j = 1,\dots , m_{i + 1 } - m_i 
+\end{gather*}
+where $a_i = r(i-1) - r(i)$ which characterizes the Jordan types of the generalized eigenspaces associated to the eigenvalues $z_i$. Finally they state the following corollary. 
+\begin{corollary}
+    (\cite[Corollary~2.2]{eisenbud1989rank})
+    The scheme-theoretic fibre of $X_{r,W}$ over $\vec z\in W$ is 
+    \[
+        X_{r,\vec z} = \{A \in \End(V) : \rk (A-z_i)^j\le r(i,j) \text{ for all } i , j \}
+    \]
+\end{corollary}
+
+\begin{corollary}
+    \label{cor:es}
+    The family $\OO^{\lambda',\lambda''}_{0,\AA}$ defined by \Cref{above} has zero fibre $\OO^\lambda$. 
+\end{corollary}
+
+\begin{lemma}
+    \label{lem:es}
+    Let $\lambda = \lambda' + \lambda''$ be permutations.
+There exists a permutation of the columns of $\lambda$ such that the first $\lambda'_1$ columns are precisely the columns of $\lambda'$ and the next $\lambda''_1$ columns are precisely the columns of $\lambda''$.
+\end{lemma}
+
+\begin{lemma}
+   $r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$ is a rank function. 
+\end{lemma}
+
+The case that we are interested in is the case of two generalized/repeated eigenvalues, i.e.\ $\vec z = (z_1,z_2) = (0,s)$. \acom{Does order matter?} 
 % Let me change notation so that $\lambda_i$ are shapes and 
@@
 I guess we need to carefully choose the $W \subset \AA^m$ defining our family, which is smaller than the family $X_{r,\AA^m}$.
-Well, $W$ is just cut out by $0 = x_1 = x_2 = \cdots = x_{m_1}$ and $ x_{m_1 + 1} = \cdots = x_m$.
-Or some permutation thereof to match the permutation $p$ above.
+Well, $W$ is just cut out by $0 = x_1 = x_2 = \cdots = x_{m_1}$ and $ x_{m_1 + 1} = \cdots = x_m$, or some permutation thereof to match the permutation $p$ above.
 
@@
     % Define $\lambda^{(i)}(\tau_1 \circ \tau_2)$ so that the 
-    Jordan type of $t\big|_{\CC[t]^p/L(0)\cap\CC[t]^p}$ is $\lambda_1^{(i)}$ and Jordan type of $t\big|_{\CC[t]^p/L(s)\cap \CC[t]^p}$ is $\lambda_2^{(i)}$.
+    Jordan type of $t\big|_{\CC[t]^p/L(0)\cap\CC[t]^p}$ is $\lambda_1^{(i)}$ and Jordan type of $t-s\big|_{\CC[t]^p/L(s)\cap \CC[t]^p}$ is $\lambda_2^{(i)}$.
 

### 2021-04-02 draft.tex
relevant fact from AM

@@
 \marginpar[]{*}
+
+    This exercise is irrelevant. We want to say something about two different modules over the same base ring. As Roger reminded the relevant fact is \cite[Proposition~10.14]{atiyah2018introduction}: 
+    % 
+    \begin{quotation}
+        If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
+    \end{quotation}
+    applied to $A = \CC[t]$ and $\fa = (t)$. 
 \end{proof}

### 2021-04-08 draft.tex
Updates from Overleaf

--- 2021-04-01 draft.tex
@@
 Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.
-We denote the kernel of this map by $ H_1(\cO_s)$.
-We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$ which is often called the first congruence subgroup.
+We denote the kernel of this map by $ H_1(\cO_s)$, often called the first congruence subgroup.
+We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$.
 % \acom{Add $G_1$}
@@
 
-We will also be interested in the affine space $ M_m$ of $m$x$m$ matrices.
+We will also be interested in the affine space $ M_m$ of $m \times m$ matrices.
 Note that for any $ \CC$-algebra $ R $,  $GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
@@
 this set and $\GL_m(K)/\GL_m(R)$, since $ GL_m(R) $ is the stabilizer of the standard lattice. 
-\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
+%\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
 % $L_0(\cO)$ then 
-$\cO^m$ then 
-$$ 
-L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
-$$}
-% \acom{Maybe abuse notation and warn the reader.}
-% \acom{is it clear that $\GL(R^m) \le \GL(K^m)$ is normal?} \jcom{It isn't normal and the quotient is not a group.}
+%$\cO^m$ then 
+%$$ 
+%L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
+%$$}
 
@@
 
-% \jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
-% \acom{Ok. We could omit the repetitive ``$X=$'' bits from the display styled alternate descriptions. That way they will fit within the margins.}
-% TODO: Just trying it out
-
-\begin{itemize}
-    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by %\acom{Change $V_0$}
-    $$
-    % \Gr = 
+We now define various version of the affine Grassmannian which will play an important role in this paper.
+
+\begin{definition}
+     The \textbf{ordinary affine Grassmannian} $\Gr = G(\cK)/G(\cO)$.
+\end{definition}    
+    It is described in modular terms by 
+    $$
+     \Gr = 
     \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_0^\times $} \right\} \,. 
     $$
-    % where $V_0$ is the trivial rank $m$ vector bundle.
-    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.
 
@@
     We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.
-On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap} \acom{Change $V_0$}
-    % 
-    \item For any $ s \in \CC $, 
+On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap}
+    % 
+\begin{definition}
+ For any $ s \in \CC $, 
     % \acom{should it be $\AA$ instead of $\CC$} 
-    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by     $$
-    % \Gr_s = 
-    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,.
-    $$
-    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
-    % \acom{What about fixing the notation $V_0$ somewhere?}
-
-    We also have a lattice description 
-    $$ 
+    the \textbf{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. 
+\end{definition}    
+As above, we have modular and lattice descriptions
+\begin{gather*}
+    \Gr_s = 
+    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,. \\
     \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
-    $$   
-    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
-    It is described in modular terms by
-    $$
+\end{gather*}
+
+\begin{definition}
+The \textbf{thick affine Grassmannian} $\Grth = G(\Kinf)/G(\CC[t])$.
+\end{definition}
+    Again, we have the following modular and lattice descriptions
+    \begin{gather*}
          \Grth = 
-         \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
-    $$
-    % where $D_\infty$ denotes a disc centered at $ \infty$. 
-    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}
-
-    We also have a lattice description 
-    $$ 
+         \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,. \\
     \Grth = \left\{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \right\}\,.
-    $$ % \CC\xT[t^{-1}]^m
-
+     % \CC\xT[t^{-1}]^m 
+    \end{gather*}
     % \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?
@@
 
-    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
-    It is described in modular terms by \acom{Change $V_0$}
+    \begin{definition} The (two point) \textbf{Beilinson--Drinfeld Grassmannian} $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
+      \end{definition}
+    It is described in modular terms by 
     % {\small
     $$
-    % \Grbd = 
+     \Grbd = 
     % \begin{aligned}
@@
     % 
-    \item The positive parts, 
-    \[
-        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO)
-    \]
-    and
-    \[
-        {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
-    \]
-    % $ \Gr^+$ and ${\Grth}^+$, 
-    of the affine Grassmannian and the thick affine Grassmannian, respectively. %, are defined as 
-    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
-    % $$
-    % \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. % \CC\xT[t^{-1}] missed a spot  
-    % $$
-    % 
+    \begin{definition} The \textbf{positive parts} of $\Gr $ and $\Grth$ are defined by 
+    $$
+        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \quad        {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
+    $$
+    \end{definition}
     In modular terms, $\Gr^+$ (resp.
-${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.
+${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow \Vtriv $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.
 over $ \PP$).
-\acom{Change $V_0$}
 
@@
     % lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.
-\end{itemize}
+
 % \acom{enumerate the points for now}
+\subsection{Relations between different affine Grassmannians}
 These different versions of the affine Grassmannian are related as follows.
@@
     $$
-    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) $, we have
-    $$
-    g \CC[t]^m \otimes_{\CC[t]} \cO = g \cO^m
+    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}]) $, we have
+    $$
+    \left( g \CC[t]^m \right) \otimes_{\CC[t]} \cO = g \cO^m
     $$
@@
 
-    \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
+%    \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
 \end{enumerate}
@@
 \subsection{Some subvarieties of affine Grassmannians}
-Now fix effective dominant coweights $\lambda_1, \lambda_2 \in P_{++}$ of sizes $N_1, N_2$  and their sums $ \lambda = \lambda_1 + \lambda_2 $ of size $ N = N_1 + N_2$. 
+Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N_1, N_2$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N_1 + N_2$. 
 % Coweights define elements in the various affine Grassmannians which we consider.
@@
 % 
-\begin{itemize}
-    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
-    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
-    % \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
-    % $$ 
-    % L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
-    % $$ 
-    % \acom{This definition makes sense for any $\lambda\in P$? Also, we don't really need it here---I have moved it up to the lattices section.}
-    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
+\begin{definition}
+The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
     $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
+\end{definition}
     % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
-    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{Do we need to justify this.}
-    % 
-    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$.
-    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
+    Since $ \lambda $ effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
+    % 
+\begin{definition} The \textbf{fusion of two spherical Schubert varieties} $$ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA $$
+\end{definition}
+    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
     %\acom{should we also subsript this family with $0,\AA$?}
-
-    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  
+    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
     % By \cite[Proposition 3.1.14]{zhu2016introduction},
     % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
-    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
-    Over $s=0$ the fibre is shown to be $ \overline{\Gr}^{\lambda_1 + \lambda_2}$ by a theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}.
+    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
+    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by a theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}.
 
     Suppose that $ s \ne 0$.
-In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.
+In the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.
 This open locus is a $ G(\CC[t])$-orbit
-    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
+    % .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
     whose lattice description is given in \Cref{le:Grl1l2} below.
     % \acom{Why $G(\CC[t])$. Because we are on the left side!}
-\end{itemize}
-Now fix two effective coweights $ \mu_1, \mu_2 \in \mathbb N^m$ such that $ \mu_i$ has size $ N_i$ and such that $ \mu_1 + \mu_2 $ is dominant.
-Using $ \mu_1, \mu_2$, we define the following subschemes.
-
-\begin{itemize}
-    \item The locus $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
-    % 
+
+As above, since $ \lambda', \lambda'' $ are effective, the map $ \Gr_{0, \AA} \rightarrow \Grth$ restricts to a map $ \Gr^{\lambda', \lambda''}_{0, \AA} \rightarrow \Grth^+$.
+
+Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ such that $ \mu_i$ has size $ N_i$ and such that $ \mu = \mu' + \mu'' $ is dominant.
+(We do not require $ \mu', \mu'' $ to be effective.) Using $ \mu, \mu', \mu''$, we define the following subschemes.
+
+\begin{definition}
+    The \textbf{Kazhdan-Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
+\end{definition}
+Since $\mu $ is effective, we see that $ \cW_\mu $ lies inside the positive thick Grassmannian $ \Grth^+$.
+    %
+
     In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
-The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.
+The lattice description of $ \cW_\mu $ is given in Lemma \ref{le:Wmu} below.
     % \acom{que est-ce?} \jcom{It's not very relevant for this paper.
@@
     % 
-    \item The semi-infinite orbit $ S^\mu = N_-(\cK)t^\mu \subset \Gr $.  
-    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
-    $$
-    % S^{\mu_1, \mu_2}_{0,s} = 
-    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
+\begin{definition} The \textbf{semi-infinite orbit} 
+$$ S^\mu = N_-(\cK)t^\mu \subset \Gr $$ 
+and the \textbf{fusion of  semi-infinite orbits} 
+$$ S^{\mu', \mu''}_{0,\AA} := S^{\mu'} \ast_\AA S^{\mu''} \,.$$  
+\end{definition}
+If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
+    $$
+    % S^{\mu', \mu''}_{0,s} = 
+    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
     $$
     % TODO: resolve
-    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
-    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
+    % \jcom{Maybe we should introduce the $ L_{\mu', \mu''} $ notation, but I'm not sure it is necessary.}
+    On the other hand, if $ s = 0$, then the fibre $S^{\mu', \mu''}_{0,0} $ equals $ S^{\mu' + \mu''}$. 
     % TODO: resolve
-    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}
-
-    \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.  I changed $ N$ to $ N_-$.}
-    % TODO!
-
-\end{itemize}
+    % \acom{changed $\mu$ to $\mu' + \mu''$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda', \lambda''} $}
+
+    \jcom{Still need a reference for why this central fibre is reduced.}
 
 \subsection{Matrices}
-\acom{Keep fixed $\lambda_i,\mu_i,\lambda, \mu$ arbitrary effective dominant coweights and their sums of size $N$ as in the previous section.} We now consider some subvarieties of the space of $ N\times N$ matrices.
+ We now consider some subvarieties of the space of $ N\times N$ matrices, again using the $ \lambda, \lambda', \lambda'', \mu, \mu', \mu''$ defined in the previous section.
+Recall that $\lambda, \mu $ are partitions of $ N$.
 
@@
     % 
-    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\lambda' \le \lambda} \OO^{\lambda'}$.
-    % 
-    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda_1, \lambda_2}_{0,s}$ of matrices conjugate to $ J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.
-Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \bigcup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$.
+    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
+    % 
+    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
+Its closure is $ \overline{\OO}^{\lambda', \lambda''}_{0,s} = \bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.
     % \acom{$s\in\AA$?}
     % 
-    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda_1), (s,\lambda_2))$ if its matrix representatives lie in $ \OO^{\lambda_1, \lambda_2}_{0,s}$.
-    % 
-    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$ a consequence of Eisenbud and Salten's description/characterization(?) of ``rank varieties'' as proved in \Cref{cor:es}.
+    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
+    % 
+    \item The family of adjoint orbits $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$ a consequence of Eisenbud and Salten's description/characterization(?) of ``rank varieties'' as proved in \Cref{cor:es}.
 
@@
     %so the set of $A$ which are conjugate to
-    %$J_{0,\lambda_1} \oplus J_{s,\lambda_2}$
+    %$J_{0,\lambda'} \oplus J_{s,\lambda''}$
     %by a matrix whose determinant is divisible by $s$ is also closed?}
     %\jcom{I didn't follow your argument.
-One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.
-For example, take $ \lambda_1 = (1) = \lambda_2 $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.
+One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda', \lambda''}_{0,s} $ and then set $ s =0$.
+For example, take $ \lambda' = (1) = \lambda'' $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.
 I am hoping that we can find a reference for this result somewhere.}
-    %\acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda_1}\oplus J_{s,\lambda_2}$ limit to matrices which are conjugate to $J_\lambda$.
+    %\acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda'}\oplus J_{s,\lambda''}$ limit to matrices which are conjugate to $J_\lambda$.
 In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}
@@
 \begin{comment}
-        Base case $m = 1$: by a slight abuse of notation let $\lambda_1, \lambda_2 \in \NN$. Claim: $J=J_{0,\lambda_1} \oplus J_{s,\lambda_2}$ is conjugate to
+        Base case $m = 1$: by a slight abuse of notation let $\lambda', \lambda_2 \in \NN$. Claim: $J=J_{0,\lambda'} \oplus J_{s,\lambda_2}$ is conjugate to
 
@@
 
-    \item The ``upper-triangular'' \mvy slice $\UU^{\mu_1, \mu_2}_{0,\AA}\rightarrow \AA $, defined by
-    $$
-    \UU^{\mu_1, \mu_2}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
-    $$
-    So a matrix in $\UU^{\mu_1, \mu_2}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).
-
-    Note that the fibre $  \UU^{\mu_1, \mu_2}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.
+    \item The ``upper-triangular'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
+    $$
+    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
+    $$
+    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).
+
+    Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.
 
@@
     \]
-    $\UU^{\mu_1, \mu_2}_{0,\AA}$ entries look like 
+    $\UU^{\mu', \mu''}_{0,\AA}$ entries look like 
     \[
@@
 
-Recall that $\lambda_1 + \lambda_2 = \lambda$ is a partition of $N$. 
+Recall that $\lambda' + \lambda'' = \lambda$ is a partition of $N$. 
 Let $m_i = \lambda_{i,1}$ ($i = 1,2$), $m = m_1 + m_2$, and define
@@
 
-Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(m_1)}$ are the (lengths of) columns of $\lambda_1$ and $a_{p(m_1 + 1)},\dots, a_{p(m_1 + m_2)}$ are the (lengths of) columns of $\lambda_2$.
+Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(m_1)}$ are the (lengths of) columns of $\lambda'$ and $a_{p(m_1 + 1)},\dots, a_{p(m_1 + m_2)}$ are the (lengths of) columns of $\lambda''$.
 Then the functions 
@@
 \begin{align*}
-    \OO^{\lambda_1,\lambda_2}_{0,s} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots, m_1 \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = m_1 + 1 ,\dots, m \}
+    \OO^{\lambda',\lambda''}_{0,s} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots, m_1 \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = m_1 + 1 ,\dots, m \}
 \end{align*}
@@
 On the other hand, ES define $r(i,j)$ to be $N$ minus the $i$th chunk of $j$ columns determined by the rank function $r(i)$.
-Also, we would like for $r(i)$ to determine the shape $\lambda = \lambda_1 + \lambda_2$.
-Take for example $\lambda_1 = \lambda_2 = (2,1)$.
+Also, we would like for $r(i)$ to determine the shape $\lambda = \lambda' + \lambda''$.
+Take for example $\lambda' = \lambda'' = (2,1)$.
 Then $\lambda = (4,2)$ and so $r\{0,1,2,3,4\}=\{6,4,2,1,0\}$ and
@@
 
-% For another example take $\lambda_1 = (1)$ and $\lambda_2 = (1,1)$. Then $\lambda = (2,1)$ and $r\{0,1,2\} = \{3,1,0\}$ so $\{a_1,a_2\} = \{2,1\}$.
+% For another example take $\lambda' = (1)$ and $\lambda'' = (1,1)$. Then $\lambda = (2,1)$ and $r\{0,1,2\} = \{3,1,0\}$ so $\{a_1,a_2\} = \{2,1\}$.
 
 % Again too small.
-The problem is I don't think that it is in general true that some permutation of the list $r(i-1) - r(i)$ will be the list of lengths of columns of $\lambda_1$ followed by the list of lengths of columns of $\lambda_2$ which is what we are looking for.
+The problem is I don't think that it is in general true that some permutation of the list $r(i-1) - r(i)$ will be the list of lengths of columns of $\lambda'$ followed by the list of lengths of columns of $\lambda''$ which is what we are looking for.
 For one thing there's in general more than one way to write a partition as a sum of two partitions.
 Ok, concretely, a third example.
-Take $\lambda_1 = (a,b)$ and $\lambda_2 = (c,d)$ then $\lambda = (a + c, b + d)$ and
+Take $\lambda' = (a,b)$ and $\lambda'' = (c,d)$ then $\lambda = (a + c, b + d)$ and
 % $$r\{0,1,\dots,a + c\} = \{N, N-2, \dots, N-2(b+d), N-2(b+d) - 1,\dots, 0\}$$
@@
 Wait a minute, nevermind, of course this is true.
-We have two partitions $\lambda_1$ and $\lambda_2$ and one way to form the partition $\lambda = \lambda_1 + \lambda_2$ is to break $\lambda_i$ down into columns, order the columns by length, and recombine.
+We have two partitions $\lambda'$ and $\lambda''$ and one way to form the partition $\lambda = \lambda' + \lambda''$ is to break $\lambda_i$ down into columns, order the columns by length, and recombine.
 Cool.
@@
     \begin{enumerate}
-        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_{0,s} \rightarrow \Grth^+$. \acom{Should we describe this map somewhere? Earlier?}
-        \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
-        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$.
+        \item $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. \acom{Should we describe this map somewhere? Earlier?}
+        \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $(0,\lambda'), (s,\lambda'')$.
+        \item $ L \in G(\CC[t]) t^{\lambda'} (t-s)^{\lambda''}$.
         % \acom{why no $G(\CC[t])$-coset?}
@@
 
-    Now assume that $ (L, s) \in \Gr^{\lambda_1, \lambda_2}_{0,s}$.
-We know that \acom{Rather than we know, it is by definition?} $ L(0) \in \Gr^{\lambda_1}$ and $L(s) \in \Gr^{\lambda_2} $.
+    Now assume that $ (L, s) \in \Gr^{\lambda', \lambda''}_{0,s}$.
+We know that \acom{Rather than we know, it is by definition?} $ L(0) \in \Gr^{\lambda'}$ and $L(s) \in \Gr^{\lambda''} $.
 This means that $t $ acting on
     % $ \CC\xt^m / L(0)$ 
-    $\cO^m/L(0)$ has Jordan type $ \lambda_1$ and $ t$ acting on 
+    $\cO^m/L(0)$ has Jordan type $ \lambda'$ and $ t$ acting on 
     % $ \CC\xt[t-s]^m / L(s) $ 
-    $\cO_s^m/L(s)$ has Jordan type $ \lambda_2$.  Now, the map 
+    $\cO_s^m/L(s)$ has Jordan type $ \lambda''$.  Now, the map 
     % $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
@@
 
-    On the other hand, if $ L = g t^{\lambda_1} (t-s)^{\lambda_2} \CC[t]^m$ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda_1}\cO^m $ since 
-    % $ (t-s)^{\lambda_2} \in G(\CC\xt)$. 
-    $ (t-s)^{\lambda_2} \in G(\cO)$. In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
+    On the other hand, if $ L = g t^{\lambda'} (t-s)^{\lambda''} \CC[t]^m$ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda'}\cO^m $ since 
+    % $ (t-s)^{\lambda''} \in G(\CC\xt)$. 
+    $ (t-s)^{\lambda''} \in G(\cO)$. In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
 \end{proof}
@@
 
-    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.  This follows immediately from (iii).
+    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.
+\rcom{Preimage of $\beta_\mu$}  This follows immediately from (iii).
     % 
@@
 \begin{lemma}
-    Let $\mu_1,\mu_2 \in P$ and $\mu = \mu_1 + \mu_2$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu_1, \mu_2}_{0,\AA}$ lands in $ \cW_\mu$.
+    Let $\mu',\mu'' \in P$ and $\mu = \mu' + \mu''$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
 \end{lemma}
@@
 \begin{proof}
-    Let $ L $ lie in this image.
-Then $ L = g t^{\mu_1} (t-s)^{\mu_2}\CC[t]^m$ for some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.
-Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.
-Note that $ h \in T_1(\Oinf)$.
+    Let $ L $ lie in this image.  Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.  Note that $ h \in T_1(\Oinf)$. 
     Moreover,
@@
     $h^{-1} g h \in N(\cK_\infty)$ and so we can factor $ h^{-1} g h = n_1 n_2$ for $ n_1 \in N_1(\CC\xt[t^{-1}]), n_2 \in N(\CC[t]) $.
-Since $ \mu $ is dominant, we see that $ t^{-\mu} n t^\mu \in N(\CC[t]) $.
+Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N(\CC[t]) $ \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?}.
 Thus, $ L = h n_1 t^\mu \CC[t]^m$.
@@
 
-For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA} $ with $\cW_\mu$.  
-As $  \overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA} $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the map 
-$$ 
-\overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA}  \hookrightarrow \Grbd \rightarrow \Grth\,.
+For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ with $\cW_\mu$.  
+As $  \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the map 
+$$ 
+\overline{\Gr}^{\lambda', \lambda''}_{0,\AA}  \hookrightarrow \Grbd \rightarrow \Grth\,.
 $$
@@
 
-In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
+In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
 \acom{Grammar of `write using the map' is iffy.
@@
     There is an isomorphism
-    $$\overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda_1, \lambda_2}_{0,\AA} \cap \cW_\mu $$
+    $$\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu $$
     given by $ (A,s) \mapsto (g(A)\CC[t]^m, s)$.
@@
 \begin{proof}
-Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda_1, \lambda_2}_{0,\AA} \cap \cW_\mu $$
+Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu $$
 This follows immediately from Lemma \ref{le:Grl1l2}.
@@
     The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
-    $$ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \cap \UU^{\mu_1, \mu_2}_{0,\AA} \cong \overline{\Gr}^{\lambda_1, \lambda_2}_{0,\AA} \cap S^{\mu_1, \mu_2}_{0,\AA}$$
+    $$ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \UU^{\mu', \mu''}_{0,\AA} \cong \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} \cap S^{\mu', \mu''}_{0,\AA}$$
 \end{theorem}
@@
 %\jcom{I was thinking about the proof of this result.
-It is enough to prove that for $ A \in \OO^{\lambda_1, \lambda_2}_s \cap \TT_\mu $, $g(A) \in S^{\mu_1, \mu_2}_s $ if and only if $ A \in T^+$.
-It is easy to show that if $ A \in \UU$, then $ g(A) \in S^{\mu_1, \mu_2}_s $.
+It is enough to prove that for $ A \in \OO^{\lambda', \lambda''}_s \cap \TT_\mu $, $g(A) \in S^{\mu', \mu''}_s $ if and only if $ A \in T^+$.
+It is easy to show that if $ A \in \UU$, then $ g(A) \in S^{\mu', \mu''}_s $.
 But the converse is not so obvious.
-(I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu_1, \mu_2}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu_1, \mu_2}$ and $\UU$ as attracting sets for a $\CC^\times$ action.
+(I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu', \mu''}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu', \mu''}$ and $\UU$ as attracting sets for a $\CC^\times$ action.
 Which do you prefer?}
@@
 
- Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu_1, \mu_2}_{0,\AA} $.
-
- On the one hand, if $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA} $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu_1} (t-s)^{\mu_2}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
-
- On the other hand, if $ (g(A), s) \in S^{\mu_1, \mu_2}_{0,\AA}$, then we can write 
- $$
- g t^\mu r= n t^{\mu_1} (t-s)^{\mu_2}
-$$
-for some $ r \in G(\CC[t]), n \in N_-[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1\xt[t^{-1}] $.
+ Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu', \mu''}_{0,\AA} $.
+
+ On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.
+
+ On the other hand, if $ (g(A), s) \in S^{\mu', \mu''}_{0,\AA}$, then we can write 
+ $$
+ g t^\mu r= n t^{\mu'} (t-s)^{\mu''}
+$$
+for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\CC\xt[t^{-1}]) $.
 Note that $ h^{-1}n h \in N(\Kinf)$, 
@@
 $$
-t^\mu r (t^{-\mu} n_2 t^\mu) t^{-\mu} = g^{-1} h n_1.
+t^\mu r (t^{-\mu} n_2^{-1} t^\mu) t^{-\mu} = g^{-1} h n_1.
 $$
@@
 % $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
-and hence $ g(A) \in t^{\mu_1} (t-s)^{\mu_2} N_1(\Oinf) $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_{0,\AA}$ as desired.
+and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''} N_1(\Oinf) $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA}$ as desired.
 \end{proof}
@@
 \begin{theorem}
-    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu_1 +\mu_2$, and $\lambda =\lambda_1+\lambda_2$. 
+    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
     % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
@@
     \begin{equation}
-        \overline{\OO}_{\lambda_1,\lambda_2}\cap\TT_{\mu_1,\mu_2} \to \overline\Gr_\AA^{\lambda_1,\lambda_2}\cap \cW_{\mu_1,\mu_2}
+        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
     \end{equation}
-    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda_1,\lambda_2}^s}\cap\TT_{\mu_1,\mu_2}^s$ on the left to the representative of the $s$-fibre on the right defined by
+    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by
     \begin{equation}
         \begin{split}
-            g &= t^{\mu_1} (t-s)^{\mu_2} + a(t) \\
+            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
             a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
@@
     with $\deg p_{ij}(t) < \mu_i = \mu_{1,i} + \mu_{2,i}$ ($1\le i\le m$).
-    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu_1,\mu_2}$ in this way?}
-    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda_1$ while its generalized $s$-eigenspace will have block type $\le \lambda_2$.
+    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu',\mu''}$ in this way?}
+    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda'$ while its generalized $s$-eigenspace will have block type $\le \lambda''$.
     To see this, note that there is a natural isomorphism
@@
         \begin{split}
-            t\big|_{\CC\xt^m/L_1}\text{ has Jordan type} \le \lambda_1 \\
-            t\big|_{\CC\xt^m/L_2}\text{ has Jordan type} \le \lambda_2 
+            t\big|_{\CC\xt^m/L_1}\text{ has Jordan type} \le \lambda' \\
+            t\big|_{\CC\xt^m/L_2}\text{ has Jordan type} \le \lambda'' 
         \end{split}
@@
     \begin{equation}
-        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+ \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}\,. 
+        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+ \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu''}\,. 
     \end{equation}

### 2021-04-08 draft.tex
beginning of edits to beginning

--- 2021-04-02 draft.tex
@@
 % 
-The Mirkovic--Vybornov isomorphism (\cite{mirkovic2007quiver,mirkovic2019comparison}) relates slices in the affine Grassmannian to slices in conjugacy classes of nilpotent matrices and Nakajima quiver varieties.
-In so doing it provides a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities.
-%
-
-[Liaison]
-
-The Beilinson--Drinfeld Grassmannian, essential to \cite{mirkovic2007geometric}, is a space which is used to define a fusion (aka convolution) product on sheaves (representations) as well as MV cycles (bases).
+% The Mirkovi\'c--Vybornov isomorphism
+In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ on the one hand to slices in $n\times n$ nilpotent orbits
+% conjugacy classes of nilpotent matrices 
+and on the other hand to Nakajima quiver varieties. 
+This article generalizes the first of these relations (an isomorphism) to families by way of the Beilinson--Drinfeld Grassmannian.
+Essential to \cite{mirkovic2007geometric}, this space is used to define a fusion (aka convolution) product on sheaves (representations) but can also be used to define a fusion product of MV cycles (bases).
 % 
@@
 
-The purpose of this paper is to give an elementary way to compute this product in type $A$.
+The purpose of this paper is to give a conceptually elementary way to compute this product in type $A$.
 We do not know how fruitful this work might be in the larger landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is as yet computationally expensive.
@@
 \subsection{Groups}
-Let $H $ be an algebraic group over $ \CC $.
-We will be interested $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.
+Let $H $ be an algebraic group over $ \CC $.  We will be interested in $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  
+\acom{random question, I know $H(R)$ is supposed to mean functor of points of the scheme $H$ but can it also be viewed as a base change from $\CC$ to $\RR$?}
 Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.
@@
 
-Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
+Given a coweight $\mu \in P$ and a point $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
 % with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
@@
 We could do $\mu = \mu' + \mu''$ or $\mu = a + b$?
-The notation $\mu^{(i)}$ is alreayd taken to mean sth.
+The notation $\mu^{(i)}$ is already taken to mean sth.
 Ofc all can be changed.
-Can also do $\mu = {}_{1}\mu + {}_{2}\mu$}
-
-We will also be interested in the affine space $ M_m$ of $m$x$m$ matrices.
-Note that for any $ \CC$-algebra $ R $,  $GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
-Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.
+Can also do $\mu = {}_{1}\mu + {}_{2}\mu$.
+\emoji{sweat-smile}}
+
+We will also be interested in the affine space $ M_m$ of $m\times m$ matrices.
+Note that for any $ \CC$-algebra $ R $, $\GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
+Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in \GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.
 
@@
 \label{ss:lat}
-We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
+We will use the lattice model \acom{for...?}, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
 % \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
@@
 % the set of such lattices 
-this set and $\GL_m(K)/\GL_m(R)$, since $ GL_m(R) $ is the stabilizer of the standard lattice. 
-\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
+this set and $\GL_m(K)/\GL_m(R)$, since $ \GL_m(R) $ is the stabilizer of the standard lattice. 
+\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ --- not yet introduced --- given $\lambda\in P$.
+If $e_1,\dots,e_m$ denote the standard basis elements of
 % $L_0(\cO)$ then 
@@
     We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.
-On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap} \acom{Change $V_0$}
+On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.
+    % \emoji{clap} 
+    % \acom{Change $V_0$}
     % 
@@
     \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
-    It is described in modular terms by \acom{Change $V_0$}
+    It is described in modular terms by 
+    % \acom{Change $V_0$}
     % {\small
     $$
-    % \Grbd = 
+    \Grbd = 
     % \begin{aligned}
@@
     % \acom{lol}
-
-    We also have a lattice descriptions 
+    We also have the lattice descriptions 
     % {\small
@@
     % L \subset  \CC(t)^m, s \in \AA 
-    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
+    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \}\,, \\
     % , $L$ is 
      \Gr_{0,s} = 
-    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
+    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}\,.
     \end{gather*}%}
-    \acom{We do not consistently specify where $s$ is in these definitions}
+    % \acom{We do not consistently specify where $s$ is in these definitions}
     % \acom{$s\in\CC$ should be $s\in\AA$?}
@@
     In modular terms, $\Gr^+$ (resp.
-${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.
+${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow \Vtriv $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.
 over $ \PP$).
-\acom{Change $V_0$}
+    % \acom{Change $V_0$}
 
@@
     \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
-    \item We have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
+    \item We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
     % $$ \Grbd \rightarrow \Grth $$ 
@@
 Since $g\CC[t]\otimes_{\CC[t]}\cO_s \cong g\cO_s $ for some reason, where $g\in\CC[t,t^{-1},(t-s)^{-1}]$ can be viewed as $g\in\cK_s$.}
-
-    In group-theoretic terms, this isomorphism is given using the diagonal map
-    $$G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) \rightarrow G(\cK)/G(\cO) \times G(\cK_s)/G(\cO_s)
-    $$
-    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) $, we have
+    % 
+    Lastly, in group-theoretic terms, this isomorphism is given using the diagonal map
+    $$
+    G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) \rightarrow G(\cK)/G(\cO) \times G(\cK_s)/G(\cO_s)\,,
+    $$
+    % This
+    which is compatible with the lattice description, since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) $, we have
     $$
@@
 \jcom{I changed this a bit in order to match Mirkovic--Vilonen better.}
-% =======
+\acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
 % Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
-% >>>>>>> 5a15ce15b14109bab482282aa5657c9596f7892d
 
 We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  
-Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $ and define $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
-We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
-
-By this construction, $X_1 \ast_{\AA} X_2 $ is a flat family over $\CC$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
+Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
+% $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
+\begin{equation}
+    \label{deservesdisplay}
+    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
+\end{equation}
+which we call the fusion of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
+
+By this construction, \acom{technically, there were two given above, so *these* constructions?} $X_1 \ast_{\AA} X_2 $ is a flat family over $\CC$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
 
@@
 \subsection{Some subvarieties of affine Grassmannians}
-Now fix effective dominant coweights $\lambda_1, \lambda_2 \in P_{++}$ of sizes $N_1, N_2$  and their sums $ \lambda = \lambda_1 + \lambda_2 $ of size $ N = N_1 + N_2$. 
+Now fix effective dominant coweights 
+% $\lambda_1, \lambda_2 \in P_{++}$ 
+$\lambda',\lambda''\in P_{++}$ of sizes 
+% $N_1, N_2$  
+$N',N''$ respectively, and let $ \lambda = \lambda' + \lambda''$ whose size $N' + N''$ is denoted $N$. \acom{This $N$ conflicts with $N\subset G$ the unipotent subgroup.}
+% $ N = N_1 + N_2$. 
 % Coweights define elements in the various affine Grassmannians which we consider.
@@
     \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
-    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
+    $ \overline\Gr^\lambda = \bigcup_{\nu \le \lambda} \Gr^{\nu} $.  
     % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
@@
     % 
-    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$.
+    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda',\lambda''} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''}$.
+    \item \acom{NOTE TO SELF CONTINUE HERE}
     % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
@@
 and the MV cycles corresponding to each are the same as before.
+\[
+{\lambda'}^{(i)}    
+\]  
 \end{example}

### 2021-04-08 sage/mvy_ideal_maker.py

@@ -79,6 +79,7 @@ from sage.symbolic.expression_conversions import polynomial
 
 # rly rly bad
 t = Tableau([[1,3],[2,5],[4],[6]])
+tt = Tableau([[1,1,3,3],[2,2,5,5],[4,4],[6,6]])
 
 # main
 

### 2021-04-08 draft.tex

--- 2021-04-08 draft.tex
@@
 \subsection{Groups}
-Let $H $ be an algebraic group over $ \CC $.
-We will be interested $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.
+Let $H $ be an algebraic group over $ \CC $.  We will be interested in $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  
+\acom{random question, I know $H(R)$ is supposed to mean functor of points of the scheme $H$ but can it also be viewed as a base change from $\CC$ to $\RR$?}
 Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.
-We denote the kernel of this map by $ H_1(\cO_s)$, often called the first congruence subgroup.
-We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$.
+We denote the kernel of this map by $ H_1(\cO_s)$.
+We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$ which is often called the first congruence subgroup.
 % \acom{Add $G_1$}
@@
 We could do $\mu = \mu' + \mu''$ or $\mu = a + b$?
-The notation $\mu^{(i)}$ is alreayd taken to mean sth.
+The notation $\mu^{(i)}$ is already taken to mean sth.
 Ofc all can be changed.
-Can also do $\mu = {}_{1}\mu + {}_{2}\mu$}
-
-We will also be interested in the affine space $ M_m$ of $m \times m$ matrices.
-Note that for any $ \CC$-algebra $ R $,  $GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
-Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.
+Can also do $\mu = {}_{1}\mu + {}_{2}\mu$.
+\emoji{sweat-smile}}
+
+We will also be interested in the affine space $ M_m$ of $m\times m$ matrices.
+Note that for any $ \CC$-algebra $ R $, $\GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
+Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in \GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.
 
@@
     We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.
-On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.\emoji{clap}
+On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.
+    % \emoji{clap} 
+    % \acom{Change $V_0$}
     % 
@@
 
-    \begin{definition} The (two point) \textbf{Beilinson--Drinfeld Grassmannian} $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
+    \begin{definition} 
+        The (two point) \textbf{Beilinson--Drinfeld Grassmannian} $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
     \end{definition}
@@
     % 
-    \begin{definition} The \textbf{positive parts} of $\Gr $ and $\Grth$ are defined by 
-    $$
-        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \quad        {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
+    \begin{definition} 
+    The \textbf{positive parts} of $\Gr $ and $\Grth$ are defined by 
+    $$
+        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \quad        
+        {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
     $$
@@
 Since $g\CC[t]\otimes_{\CC[t]}\cO_s \cong g\cO_s $ for some reason, where $g\in\CC[t,t^{-1},(t-s)^{-1}]$ can be viewed as $g\in\cK_s$.}
-
-    In group-theoretic terms, this isomorphism is given using the diagonal map
-    $$G(\CC[t, t^{-1}, (t-s)^{-1}])/G(\CC[t]) \rightarrow G(\cK)/G(\cO) \times G(\cK_s)/G(\cO_s)
-    $$
+    % 
     This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}]) $, we have
@@
 \subsection{Some subvarieties of affine Grassmannians}
-Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N_1, N_2$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N_1 + N_2$. 
+Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N',N''$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
 % Coweights define elements in the various affine Grassmannians which we consider.
@@
     % 
-\begin{definition} The \textbf{fusion of two spherical Schubert varieties} $$ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA $$
+\begin{definition} 
+    The \textbf{fusion of two spherical Schubert varieties} $$ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA $$
 \end{definition}
@@
     % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
-    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by a theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}.
+    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by 
+    % a theorem of Zhu 
+    \cite[Proposition 3.1.14]{zhu2016introduction}.
 
@@
 \begin{definition}
-    The \textbf{Kazhdan-Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
+    The \textbf{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
 \end{definition}
@@
 
-    \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
-    \acom{Ok.}
+    % \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
+    % \acom{Ok.}
 

### 2021-04-08 draft.tex
zzzzz...

@@
     The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
-    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
+    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $ a \textbf{spherical Schubert variety}.  
 \end{definition}
     % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
-    Since $ \lambda $ effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
+    Note, since $ \lambda $ is effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
+\acom{why and so?
+cuz orbits are connected?}
     % 
 \begin{definition} 
-    The \textbf{fusion of two spherical Schubert varieties} $$ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA $$
+    The \textbf{fusion of two spherical Schubert varieties} 
+    $$ 
+    \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.
+    $$
 \end{definition}
@@
     %\acom{should we also subsript this family with $0,\AA$?}
-    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
+    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
     % By \cite[Proposition 3.1.14]{zhu2016introduction},
@@
 
-Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ such that $ \mu_i$ has size $ N_i$ and such that $ \mu = \mu' + \mu'' $ is dominant.
-(We do not require $ \mu', \mu'' $ to be effective.) Using $ \mu, \mu', \mu''$, we define the following subschemes.
+Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ of size $N',N''$ resp. such that $ \mu = \mu' + \mu'' $ is dominant. (We do not require $ \mu', \mu'' $ to be effective.) 
+Using $ \mu, \mu', \mu''$, we define the following subschemes.
 
@@
             &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
-            &\text{then } (e^t_s)' (A-J_\mu) e^b_a = 0 \,.
+            &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
         \end{aligned}    
@@
     $$
-    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
-    $$
-    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).
+    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
+    $$
+    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
 
@@
 
-    $\UU_{0,0}$ entries look like 
+    $\UU_{0,0}^{(?),(?)}$ entries look like 
     \[
@@
 \begin{proof}
-    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.
+    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.
 Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
@@
 
-    For the reverse containment, we choose $ [g] \in \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}$.
+    For the reverse containment, we choose $ [g] \in \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu',\mu''}$.
 By the lemma below, $[g] \in \cW_\mu$ and thus it lies in the image of our map and we are done.
@@
 
-% Define $S_{\mu_1,\mu_2}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
-
-\acom{is it a fibre of $S_{\mu_1,\mu_2}$ defined above?}
+% Define $S_{\mu',\mu''}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
+
+\acom{is it a fibre of $S_{\mu',\mu''}$ defined above?}
 
@@
 \begin{lemma}%[Roger's lemma]
-    Let $\mu_1,\mu_2$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
+    Let $\mu',\mu''$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
     \begin{equation}
-        S_{\mu_1,\mu_2}^s \subset \cW_\mu 
+        S_{\mu',\mu''}^s \subset \cW_\mu 
     \end{equation}
@@
     \begin{equation}\label{eq:tabmult}
-        \irr\lim_{s\to 0} \overline{\OO}^{\lambda_1,\lambda_2}_{0,s}\cap\UU^{\mu_1,\mu_2}_{0,s} \,. 
-        % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu_1,\mu_2}^{+,s}
+        \irr\lim_{s\to 0} \overline{\OO}^{\lambda_1,\lambda_2}_{0,s}\cap\UU^{\mu',\mu''}_{0,s} \,. 
+        % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu',\mu''}^{+,s}
     \end{equation}
@@
     \[
-    \{A\in\UU_{0,s}^{\mu_1,\mu_2} : A \big|_{\mu^1 + \cdots + \mu^i} \in \OO_{0,s}^{\lambda_{1}^{(i)},\lambda_2^{(i)}} \text{ all } i\} = Z_{\tau_1}\times Z_{\tau_2}
+    \{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\mu^1 + \cdots + \mu^i} \in \OO_{0,s}^{\lambda_{1}^{(i)},\lambda_2^{(i)}} \text{ all } i\} = Z_{\tau_1}\times Z_{\tau_2}
     \]
@@
     $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
-    \acom{Restricting to an eigenspace is like inverting (forgetting) the action of $t$ by any other generalized eigenvalue.
-Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}
+    \acom{Unrelated comments.
+1) Restricting to an eigenspace is like inverting (forgetting) the action of $t$ by any other generalized eigenvalue.
+2) Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}
 
@@
 \begin{question}[Related question]
-    If $\mu_1,\mu_2$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
+    If $\mu',\mu''$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
     \[
     \begin{tikzcd}
-        \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu_1,\mu_2}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
-        \overline\OO^{\lambda_1,\lambda_2}_{0,s} \cap \UU^{\mu_1,\mu_2}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
+        \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu',\mu''}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
+        \overline\OO^{\lambda_1,\lambda_2}_{0,s} \cap \UU^{\mu',\mu''}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
     \end{tikzcd}    
@@
 \begin{example}
-Let $G = SL_3$ and consider the tableaux
+Let $G = \GL_3$ and consider the tableaux
 $$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$

### 2021-04-08 draft.tex
rogers adds

@@
 \begin{example}
-Let $G = SL_3$ and consider the tableaux
+Let $G = \GL_3$ and consider the tableaux
 $$\tau_1 = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(11,23).$$
@@
 \begin{example}
-Let $G = SL_3$ and consider the following tableaux:
+Let $G = \GL_3$ and consider the following tableaux:
 $$\tau_1 = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(1111,2233).$$

### 2021-04-08 draft.tex
miostly apostraphes

--- 2021-04-08 draft.tex
@@
 
-As an application we can compute fusion of stable MV cycles of type $\alpha_i$ for any $i \in I$. What about more general weights? Having $\kpf > 1$.
+As an application we can compute fusion of stable MV cycles of type $\alpha_i$ for any $i \in I$. What about more general weights? Having $\kpf > 1$. Well yeah.
 
@@
     % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
-    Let $Z_{i} = Z_{\tau_i}$  be an MV cycle of type $\lambda_i\in P_{++}$ and weight $\mu_i\in P$ ($i = 1,2$). Then 
+    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''\in P_{++}$ and weight $\mu',\mu''\in P$ resp.\ such that $\mu = \mu' + \mu'' \in P_{++}$. Then 
     \begin{equation}
         % Z_\tau\ast Z_\sigma 
-        m_{\lambda_1\lambda_2} ([Z_1]\otimes[Z_2]) 
+        m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
         = 
@@
         i\left(
-            Z_\tau, Z_1\circ Z_2 
+            Z_\tau, Z'\circ Z''
             % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
@@
     \begin{equation}\label{eq:tabmult}
-        \irr\lim_{s\to 0} \overline{\OO}^{\lambda_1,\lambda_2}_{0,s}\cap\UU^{\mu',\mu''}_{0,s} \,. 
+        \irr\lim_{s\to 0} \overline{\OO}^{\lambda',\lambda''}_{0,s}\cap\UU^{\mu',\mu''}_{0,s} \,. 
         % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu',\mu''}^{+,s}
@@
     $$
-    b_{Z_1}b_{Z_2} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
-        Z, Z_1 \circ Z_2 
+    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
+        Z, Z' \circ Z''
         % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
@@
     $$
-    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda_i$ and $\mu_i$ ($i = 1,2$).
+    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$.
 \end{proposition}
@@
     % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
-    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau_1$ and $\tau_2$. 
+    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
     % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
@@
         % Z_1 \circ Z_2 
-        \tau_1 \circ \tau_2 
+        \tau' \circ \tau''
         ) = 1 \,. 
@@
 \end{conjecture}
+
+\begin{proposition}
+    Given Lusztig data $n_\bullet',n_\bullet''\in\NN^\ell$ the smallest choice of $\mu',\mu''\in P$ and $\lambda',\lambda''\in P_{++}$ such that $\mu = \mu' + \mu''\in P_{++}$ and $\tau'\in S(\lambda')_{\mu'}$, $\tau''\in S(\lambda'')_{\mu''}$ are SSYT with the prescribed Lusztig data, are\dots
+\end{proposition}
+\begin{proof}
+    [Sketch.]
+    The last row of the GT pattern of $\tau'$ (resp.\ $\tau''$) is $\lambda'$ (resp.\ $\lambda''$). 
+    Guess: the smallest choices will be the appropriate pieces of the smallest choices for $\lambda$, $\mu$, and $n_\bullet = n_\bullet' + n_\bullet''$.
+E.g.\ take $n_\bullet' = (2,0,0), n_\bullet'' = (0,0,2)$ so $n_\bullet = (2,0,2)$.
+Then $\lambda - \mu = 2\alpha_1 + 2\alpha_2$ %or $(\lambda_1 - \mu_1,\lambda_2 - \mu_2, \lambda_3 - \mu_3) = (2,0,2)$
+    \begin{gather}
+        (\lambda_1 - \mu_1,\lambda_2 - \mu_2, \lambda_3 - \mu_3) = (2,0,-2)
+        \\
+        % (\lambda_1(2) - \mu_1(2),\lambda_2(2) - \mu_2(2), \lambda_3(2) - \mu_3(2)) &= (2,0,2) \\
+        % (\lambda_1(1) - \mu_1(1),\lambda_2(1) - \mu_2(1), \lambda_3(1) - \mu_3(1)) &= (2,0,2)
+        \begin{matrix}
+            & & \lambda_1(1) \\
+            & \lambda_1 (2) = \lambda_1(1) + 2 & & \lambda_2(2) \\
+            \lambda_1 = \lambda_1(2) + 0  & & \lambda_2 = \lambda_2(2) + 2 & & \lambda_3 
+        \end{matrix}\\
+        \Rightarrow \mu_3 \ge 2, \mu_2 \ge 2, \mu_1 \ge 2 \\
+        \Rightarrow \lambda_3 \ge 0, \lambda_2 \ge 2, \lambda_1 \ge 4 \\
+        \Rightarrow \lambda_2(2) = \lambda_2 - 2 \ge 0 , \lambda_1(2) = \lambda_1 \ge 4 \\ 
+        \Rightarrow \lambda_1(1) = \lambda_1(2) - 2 \ge 2 \\ 
+        \young(1122,33)
+        % \Leftrightarrow 
+        % \begin{matrix}
+        %     & & \lambda_1(1) \\
+        %     & \lambda_1 (2) = \lambda_1(1) + 2 & & \lambda_2(2) \\
+        %     \lambda_1 = \lambda_1(2) + 0  & & \lambda_2 = \lambda_2(2) + 2 & & 0 
+        % \end{matrix}
+    \end{gather} 
+    Since the tableau formed by taking the smallest possible choices for each of the inequalities is semi-standard we're good.
+
+    In general we have $\mu_i\ge\sum_k n_{i,k}$ where $n_{i,k} = \lambda_k(i) - \lambda_{k}(i-1)$ and then $\lambda_i \ge \nu_i + \mu_i$ where $\nu = \wt(n_\bullet)$.
+The rest of the lower bounds are determined recursively by the relation $\lambda_k(i-1) =  \lambda_k(i) - n_{i,k}$.
+Choose the minimum values satisfying the bounds until $\lambda_k(i) < \lambda_{k+1}(i)$ for some $k,i$.
+If this should happen go back to the start and increment all/some of the initial $\lambda_k$ by an appropriate amount.
+\end{proof}
 

### 2021-04-08 sage/mvy_ideal_maker.py

@@ -207,8 +207,14 @@ def mu_submatrices_over_gf(t1,t2):
 
 # Roger's stuff
 
-# return kxk minors of matrix mat using last col columns
-def minors_with_last_col(mat,col,k):
+# return kxk minors of matrix mat = mat0**pow using last col columns
+def minors_with_last_col(mat0,pow,col,k):
+    mat = mat0**pow
+    all_rows0 = []
+    for i in range(mat0.column(mat0.ncols()-1).length()):
+        if not mat0.column(mat0.ncols()-1)[i].is_constant():
+            # all_rows0.append(i)
+            all_rows0.append(mat0.column(mat0.ncols()-1)[i])
     all_rows = range(mat.nrows())
     first_cols = range(mat.ncols()-col) 
     last_cols = range(mat.ncols()-col,mat.ncols())
@@ -218,7 +224,8 @@ def minors_with_last_col(mat,col,k):
             for lcols in Combinations(last_cols,i) :
                 for fcols in Combinations(first_cols,k-i):
                     mnr = mat.matrix_from_rows_and_columns(rows,lcols+fcols).determinant()
-                    if mnr != 0:
+                    # if mnr != 0:
+                    if not Set(mnr.variables()).intersection(Set(all_rows0)).is_empty():
                         mnrs.append(mnr)
     return mnrs
 

### 2021-04-09 draft.tex
whered we leaf off yest
minor edits

--- 2021-04-08 draft.tex
@@
 % The Mirkovi\'c--Vybornov isomorphism
-In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ on the one hand to slices in $n\times n$ nilpotent orbits
+In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $n\times n$ nilpotent orbits on the one hand
 % conjugacy classes of nilpotent matrices 
-and on the other hand to Nakajima quiver varieties. 
-This article generalizes the first of these relations (an isomorphism) to families by way of the Beilinson--Drinfeld Grassmannian.
+and to Nakajima quiver varieties on the other hand. 
+This paper generalizes the first of these relations (an isomorphism) to families of slices by way of the Beilinson--Drinfeld Grassmannian. 
 Essential to \cite{mirkovic2007geometric}, this space is used to define a fusion (aka convolution) product on sheaves (representations) but can also be used to define a fusion product of MV cycles (bases).
@@
     Note, since $ \lambda $ is effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
-\acom{why and so?
-cuz orbits are connected?}
+\acom{why ``and so''?
+bc orbits are connected?}
     % 
@@
 
+\subsection{Pseudocode}
+
 \begin{question}

### 2021-04-09 draft.tex
Updates from Overleaf

--- 2021-04-08 draft.tex
@@
 
-As an application we can compute fusion of stable MV cycles of type $\alpha_i$ for any $i \in I$. What about more general weights? Having $\kpf > 1$. Well yeah.
+As an application we can compute fusion of stable MV cycles of type $\alpha_i$ for any $i \in I$. What about more general weights? Having $\kpf > 1$.
 
@@
     % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
-    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''\in P_{++}$ and weight $\mu',\mu''\in P$ resp.\ such that $\mu = \mu' + \mu'' \in P_{++}$. Then 
+    Let $Z_{i} = Z_{\tau_i}$  be an MV cycle of type $\lambda_i\in P_{++}$ and weight $\mu_i\in P$ ($i = 1,2$). Then 
     \begin{equation}
         % Z_\tau\ast Z_\sigma 
-        m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
+        m_{\lambda_1\lambda_2} ([Z_1]\otimes[Z_2]) 
         = 
@@
         i\left(
-            Z_\tau, Z'\circ Z''
+            Z_\tau, Z_1\circ Z_2 
             % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
@@
     \begin{equation}\label{eq:tabmult}
-        \irr\lim_{s\to 0} \overline{\OO}^{\lambda',\lambda''}_{0,s}\cap\UU^{\mu',\mu''}_{0,s} \,. 
+        \irr\lim_{s\to 0} \overline{\OO}^{\lambda_1,\lambda_2}_{0,s}\cap\UU^{\mu',\mu''}_{0,s} \,. 
         % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu',\mu''}^{+,s}
@@
     $$
-    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
-        Z, Z' \circ Z''
+    b_{Z_1}b_{Z_2} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
+        Z, Z_1 \circ Z_2 
         % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
@@
     $$
-    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$.
+    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda_i$ and $\mu_i$ ($i = 1,2$).
 \end{proposition}
@@
     % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
-    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
+    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau_1$ and $\tau_2$. 
     % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
@@
         % Z_1 \circ Z_2 
-        \tau' \circ \tau''
+        \tau_1 \circ \tau_2 
         ) = 1 \,. 
@@
 \end{conjecture}
-
-\begin{proposition}
-    Given Lusztig data $n_\bullet',n_\bullet''\in\NN^\ell$ the smallest choice of $\mu',\mu''\in P$ and $\lambda',\lambda''\in P_{++}$ such that $\mu = \mu' + \mu''\in P_{++}$ and $\tau'\in S(\lambda')_{\mu'}$, $\tau''\in S(\lambda'')_{\mu''}$ are SSYT with the prescribed Lusztig data, are\dots
-\end{proposition}
-\begin{proof}
-    [Sketch.]
-    The last row of the GT pattern of $\tau'$ (resp.\ $\tau''$) is $\lambda'$ (resp.\ $\lambda''$). 
-    Guess: the smallest choices will be the appropriate pieces of the smallest choices for $\lambda$, $\mu$, and $n_\bullet = n_\bullet' + n_\bullet''$.
-E.g.\ take $n_\bullet' = (2,0,0), n_\bullet'' = (0,0,2)$ so $n_\bullet = (2,0,2)$.
-Then $\lambda - \mu = 2\alpha_1 + 2\alpha_2$ %or $(\lambda_1 - \mu_1,\lambda_2 - \mu_2, \lambda_3 - \mu_3) = (2,0,2)$
-    \begin{gather}
-        (\lambda_1 - \mu_1,\lambda_2 - \mu_2, \lambda_3 - \mu_3) = (2,0,-2)
-        \\
-        % (\lambda_1(2) - \mu_1(2),\lambda_2(2) - \mu_2(2), \lambda_3(2) - \mu_3(2)) &= (2,0,2) \\
-        % (\lambda_1(1) - \mu_1(1),\lambda_2(1) - \mu_2(1), \lambda_3(1) - \mu_3(1)) &= (2,0,2)
-        \begin{matrix}
-            & & \lambda_1(1) \\
-            & \lambda_1 (2) = \lambda_1(1) + 2 & & \lambda_2(2) \\
-            \lambda_1 = \lambda_1(2) + 0  & & \lambda_2 = \lambda_2(2) + 2 & & \lambda_3 
-        \end{matrix}\\
-        \Rightarrow \mu_3 \ge 2, \mu_2 \ge 2, \mu_1 \ge 2 \\
-        \Rightarrow \lambda_3 \ge 0, \lambda_2 \ge 2, \lambda_1 \ge 4 \\
-        \Rightarrow \lambda_2(2) = \lambda_2 - 2 \ge 0 , \lambda_1(2) = \lambda_1 \ge 4 \\ 
-        \Rightarrow \lambda_1(1) = \lambda_1(2) - 2 \ge 2 \\ 
-        \young(1122,33)
-        % \Leftrightarrow 
-        % \begin{matrix}
-        %     & & \lambda_1(1) \\
-        %     & \lambda_1 (2) = \lambda_1(1) + 2 & & \lambda_2(2) \\
-        %     \lambda_1 = \lambda_1(2) + 0  & & \lambda_2 = \lambda_2(2) + 2 & & 0 
-        % \end{matrix}
-    \end{gather} 
-    Since the tableau formed by taking the smallest possible choices for each of the inequalities is semi-standard we're good.
-
-    In general we have $\mu_i\ge\sum_k n_{i,k}$ where $n_{i,k} = \lambda_k(i) - \lambda_{k}(i-1)$ and then $\lambda_i \ge \nu_i + \mu_i$ where $\nu = \wt(n_\bullet)$.
-The rest of the lower bounds are determined recursively by the relation $\lambda_k(i-1) =  \lambda_k(i) - n_{i,k}$.
-Choose the minimum values satisfying the bounds until $\lambda_k(i) < \lambda_{k+1}(i)$ for some $k,i$.
-If this should happen go back to the start and increment all/some of the initial $\lambda_k$ by an appropriate amount.
-\end{proof}
 
@@
 Suppose we have two tableaux $\tau_1$ and $\tau_2$ with respective weights $\lambda_i$ and $\mu_i$ and we wished to take their fusion product.
-We consider a generic matrix $X \in \UU^{\lambda_1,\lambda_2}_{0,s}$.
+We consider a generic matrix $X \in \UU^{\mu_1,\mu_2}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda_1,\lambda_2}_{0,s}$.
 
 Consider the subtableaux $\tau_{1,i}$ of $\tau_1$ and $\tau_{2,i}$ of $\tau_2$ where we take the boxes of $\tau_1$ and $\tau_2$ containing the numbers $1,\dots,i$.
-Let $\lambda_{1,j}$ and $\lambda_{2,j}$ be the corresponding dominant weights.
-For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\lambda_{1,i}, \lambda_{2,i}}_{0,s}$ of $X$.
-These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ which allows us to deduce relations on the variables in $X$.
+Let $\lambda_{1,j}$ and $\lambda_{2,j}$ be the corresponding sizes and $\mu_{1,j}$ and $\mu_{2,j}$ be the corresponding weights of the subtableaux.
+For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu_{1,i}, \mu_{2,i}}_{0,s}$ of $X$.
+These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda_{1,i}, \lambda_{2,i}}_{0,s}$, which allows us to deduce relations on the variables in $X$.
 The relations must also include the new variables in the latest block and cannot have $s$ as a factor.
@@
 $$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$
+
+Lusztig data: $(010000)$ for $\tau_1$, $(100100)$ for $\tau_2$
+
+Dimensions: $\alpha_1 + \alpha_2$ for both.
+
 The MV cycles corresponding to $\tau_1$ and $\tau_2$ are both isomorphic to $\PP^2$.
@@
 which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau_1$ and $\tau_2$.
+
+Lusztig datum: $(110100)$
+
+Dimension: $2\alpha_1 + 2\alpha_2$
 \end{example}
@@
 $$\tau_1 = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(11,23).$$
+
+Lustig data: $(100000)$ for $\tau_1$, 
 The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.

### 2021-04-09 draft.tex
Added lusztig data and dim for examples.

@@
 
-Lusztig data: $(010000)$ for $\tau_1$, $(100100)$ for $\tau_2$
-
-Dimensions: $\alpha_1 + \alpha_2$ for both.
+Lusztig data: $(010)$ for $\tau_1$, $(101)$ for $\tau_2$
+
+Dimensions: $(1,0,-1)$ for both.
 
@@
 
-Lusztig datum: $(110100)$
-
-Dimension: $2\alpha_1 + 2\alpha_2$
+Lusztig datum: $(111)$
+
+Dimension: $(2,0,-2)$
 \end{example}
@@
 
-Lustig data: $(100000)$ for $\tau_1$, 
+Lustig data: $(100)$ for $\tau_1$, $(001)$ for $\tau_2$.
+
+Dimensions: $(1,-1,0)$ for $\tau_1$, $(0,1,-1)$ for $\tau_2$.
+
 The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.
@@
 We see that the 0-fibre is reducible with two components. The tableau corresponding to each ideal is
-$$\begin{array}{cc} \vspace{1mm}
-    \young(1113,22) & \text{for } \langle a_1, a_2 \rangle \\ 
-    \young(1112,23) & \text{for } \langle a_1, b_2 \rangle.
+$$\begin{array}{cccc} \vspace{1mm}
+    \young(1113,22) & \text{for } \langle a_1, a_2 \rangle & \text{Lusztig: }(101) & \dim = (1,0,-1)\\ 
+    \young(1112,23) & \text{for } \langle a_1, b_2 \rangle & \text{Lusztig: }(010) & \dim = (1,0,-1).
 \end{array}$$
@@
 $$\tau_1 = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(1111,2233).$$
+
+Lusztig data: $(200)$ for $\tau_1$, $(002)$ for $\tau_2$.
+
+Dimensions: $(2,-2,0)$ for $\tau_1$, $(0,2,-2)$ for $\tau_2$.
+
 The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
@@
 $$
-\begin{array}{cc}\vspace{1mm}
-    \young(11111133,2222) & \text{for } I_1 \\ \vspace{1mm}
-    \young(11111122,2233) & \text{for } I_2 \\ \vspace{1mm}
-    \young(11111123,2223) & \text{for } I_3.
+\begin{array}{cccc}\vspace{1mm}
+    \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
+    \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
+    \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
 \end{array}
@@
 and the MV cycles corresponding to each are the same as before.
-\[
-{\lambda'}^{(i)}    
-\]  
 \end{example}

### 2021-04-10 draft.tex
exhuast and slow

--- 2021-04-09 draft.tex
@@
 % 
-This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019mirkovic}).
+This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019Mirkovi\'c}).
 % conjectured by JEA and proved by BKK
 % 
-To quote from Mirkovic and Vilonen:
+To quote from Mirkovi\'c and Vilonen:
 \begin{quotation}
@@
 Let $H $ be an algebraic group over $ \CC $.  We will be interested in $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  
+% 
 \acom{random question, I know $H(R)$ is supposed to mean functor of points of the scheme $H$ but can it also be viewed as a base change from $\CC$ to $\RR$?}
+% 
 Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.
@@
 % are there other possibilities?? :S 
-Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  
+Write $P$ for the coweight lattice $\Hom(\CC^\times,T)$ of $T$, so we have $P\cong \ZZ^m$.  
 % TODO: Thank you - resolved!
@@
 which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  
-So an effective dominant coweight $ \lambda $ is a partition of $|\lambda| = \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.
+\acom{1.
+No boldface on this new term.
+Proceed with selective boldfacing?
+2.
+Since we sometimes need $\Peff$ which contains $P_{++} = \Peff\cap\Pdom$, how about just using the notation $\Peff,\Pdom$ instead of $P_+, P_{++}$ for a change?}
+% 
+So an effective dominant coweight $ \lambda $ is a partition of $|\lambda| = \lambda_1 + \cdots + \lambda_m\in\NN$, which we call the size of $ \lambda$.
 We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights.
@@
 \]
-which we will view in $\GL_m(K) $ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it 
-\acom{1.
-Add warning that we will also write $(t-s)^\mu$ for its image in $\GL_m(K)/\GL_m(R)$.
-We hope it will be evident?
-2.
+which we will view in 
+% $\GL_m(K) $ 
+$G(K)$ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it 
+\acom{Add warning that we will also write $(t-s)^\mu$ for its image in 
+% $\GL_m(K)/\GL_m(R)$ 
+$G(K)/G(R)$ and we hope it will be clear? Only we haven't introduced this space yet.}
+% Resolved
+% 2.
 Change notation $\mu = (\mu_1,\dots,\mu_m)$ since we also have $\mu = \mu_1 + \mu_2$.
@@
 
-We will also be interested in the affine space $ M_m$ of $m\times m$ matrices.
-Note that for any $ \CC$-algebra $ R $, $\GL_m(R) $ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
-Thus $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but $ t^\lambda \in \GL_m(\CC[t]) $ if and only if $ \lambda = 0 $.
+We will also be interested in the affine space $ M_m$ of $m\times m$ matrices.  Note that for any $ \CC$-algebra $ R $, 
+% $\GL_m(R) $ 
+$G(R)$ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$. Thus for example $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but 
+% $ t^\lambda \in \GL_m(\CC[t]) $ 
+$t^\lambda\in G(\CC[t])$ if and only if $ \lambda = 0 $. \acom{maybe add that it's the same for $G(\cO)$.}
 
@@
 \label{ss:lat}
-We will use the lattice model \acom{for...?}, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
+We will use the lattice model \acom{for each of the affine Grassmannians which we consider---again, this is putting the cart in front of the horse, as we haven't introduced any affine Grassmannians yet}, so it is useful to recall the following definition.
+Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field).
 % \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
-Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
+Consider $ K^m $ as a $K$-module.
+\acom{left or right, doesn't matter?
+I think we are in a situation where they are the same, but I need a reminder.} By restriction $ K^m$ can be viewed as an $R$-module.
+An $R$-lattice in $K^m$ \acom{definiton, no boldface}
 % \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
-is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.
-Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.
+is an $R$-submodule $ L \subset K^m$ 
+% such that $ L $ 
+which is a free $R$-module of rank $ m $ and satisfies $ L \otimes_R K = K^m $. Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. 
 % 
@@
 % the set of such lattices 
-this set and $\GL_m(K)/\GL_m(R)$, since $ GL_m(R) $ is the stabilizer of the standard lattice. 
+this set and $\GL_m(K)/\GL_m(R)$, since $ \GL_m(R) $ is the stabilizer of the standard lattice. 
 %\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
@@
 
-We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
+We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$. 
+% TODO: 
+% \acom{Wait, I thought $\CC(t)$ is used in the Ran space version of the BD Gr.}
+Given such a lattice $ L $ and a point $ a \in \CC$, the specialization \acom{definition, no boldface} of $ L $ at $ a $ is defined as
 $$
 % L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
-L(a) := L \otimes_{\CC[t]} \cO_a, \text{ a lattice in } \cK_a.  %\,. % The containment is not part of the definition so I comment it out \subset \cK_a^m\,.
-$$
+L(a) := L \otimes_{\CC[t]} \cO_a, 
+% \text{ a lattice in } \cK_a^m.  
+$$
+a lattice in $\cK_a^m$. 
 If 
@@
 % \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
-For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$. 
+For example, since $(t-s)^{-1} = \frac 1 {a-s}\sum(\frac{t-a}{s-a})^k$ if $a\ne s$, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$. 
 % \acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}
@@
 % G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
-Set $\AA = \AA^1$ and let $\Vtriv$ denote the trivial rank $ m $ vector bundle.
-
-We now define various version of the affine Grassmannian which will play an important role in this paper.
+Set $\AA = \AA^1$ viewed as the subset $\PP\setminus \{\infty\}$ of $\PP$. Let $\Vtriv$ denote the trivial rank $ m $ vector bundle. 
+% 
+We now define various versions of ``the'' affine Grassmannian which will play an important r\^ole in this paper.
 
@@
     $$
-    We obtain the lattice from $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.
-On the other hand, we obtain the lattice from the group-theoretic description $ G(\cK) / G(\cO) $ by setting $ L = g \cO^m$ for $ g \in G(\cK)$.
-    % \emoji{clap} 
-    % \acom{Change $V_0$}
+    We obtain a lattice from a pair $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.  
+    On the other hand, to get a lattice from the group-theoretic description $ G(\cK) / G(\cO) $ we set $ L = g \cO^m$ for $ g \in G(\cK)$.
     % 
@@
  For any $ s \in \CC $, 
-    % \acom{should it be $\AA$ instead of $\CC$} 
-    the \textbf{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. 
+    the \textbf{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ \textbf{at} $ s $. 
 \end{definition}    
-As above, we have modular and lattice descriptions
+As above, we have modular and lattice descriptions:
 \begin{gather*}
     \Gr_s = 
-    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,. \\
+    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,, \\
     \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
 \end{gather*}
-
+% 
+% TODO:
+% consider decorating lattice, modular, group-theoretic descriptions? 
+% paper too short for it, ok. 
+% but it's a little weird how we do 
+% $$ X = A \\ X = Y $$ 
+% Hmm.. maybe it's alright
+% I was going to suggest we do $$ X = A \\ = B $$ instead 
+% 
 \begin{definition}
@@
 \end{definition}
-    Again, we have the following modular and lattice descriptions
+Again, we have the following modular and lattice descriptions:
 \begin{gather*}
         \Grth = 
-         \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,. \\
-    \Grth = \left\{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \right\}\,.
+        \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,, \\
+\Grth = \left\{ L : L \subset  \Kinf^m \text{ is a $\CC[t]$-lattice} \right\}\,.
     % \CC\xT[t^{-1}]^m 
@@
 Maybe we could use some kind of bold  Gr (``thick'' letters) or maybe that would be too confusing.} \acom{Ok, it's tentative.}
-
+% 
 \begin{definition} 
-        The (two point) \textbf{Beilinson--Drinfeld Grassmannian} $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
+    The two point \textbf{Beilinson--Drinfeld Grassmannian} 
+    $$\pi : \Grbd\to \AA$$ 
+    with one point fixed at 0, and the second point $s\in\AA$ varying.
 \end{definition}
 It is described in modular terms by 
-    % {\small
 $$
     \Grbd = 
-    % \begin{aligned}
     \left\{ 
         (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} \Vtriv \text{ on } \PP \setminus \{0, s\}  
-        \right\} 
-    % \end{aligned}
-    $$%}
-    % 
+    \right\}\,. 
+$$
 The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
@@
 $$ 
-    % \Gr_{0,s} = 
 G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
 $$
+\acom{What is the modular description of the fibre?}
 % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
@@
 % \acom{lol}
-    We also have the lattice descriptions 
-    % {\small
+We also have the lattice descriptions:
+% 
 \begin{gather*}
@@
 \{ (L,s) :
-    % s\in\AA,\,
-    % L \subset  \CC(t)^m, s \in \AA 
-    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \}\,, \\
+L \subset  \CC(t)^m\text{ is a $\CC[t]$-lattice trivial at any }a \ne 0, s \}\,, \\
 % , $L$ is 
     \Gr_{0,s} = 
-    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}\,.
-    \end{gather*}%}
-    % \acom{We do not consistently specify where $s$ is in these definitions}
-    % \acom{$s\in\CC$ should be $s\in\AA$?}
-    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
+\{ L : L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m \text{ is a $\CC[t]$-lattice} \}\,.
+\end{gather*}
 % 
 \begin{definition} 
-    The \textbf{positive parts} of $\Gr $ and $\Grth$ are defined by 
-    $$
-        \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \quad        
+The \textbf{positive parts} of $\Gr $ and $\Grth$, resp., are defined by 
+$$
+    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and }      
     {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
@@
 \end{definition}
-    In modular terms, $\Gr^+$ (resp.
-${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow \Vtriv $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.
-over $ \PP$).
-
-    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the relevant standard lattice. 
+In modular terms, $\Gr^+$ (resp.\ ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow \Vtriv $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.\ over $ \PP$).
+
+In lattice terms, $ \Gr^+$ (resp.\ ${\Grth}^+$) contains those lattices $L$ which are contained in the appropriate standard lattice. 
 % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
@@
 
-% \acom{enumerate the points for now}
 \subsection{Relations between different affine Grassmannians}
@@
 \begin{enumerate}
-    \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
-    \item We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
+    % TODO: I think it makes more sense to put the first point at the end; it just relates (fibres of) the BD Gr to the ordinary Gr
+    % \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
+    \item We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $.
     % $$ \Grbd \rightarrow \Grth $$ 
-    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by the inclusion
+    It is given in modular terms by restricting the trivialization to $ D_\infty$. \acom{Does it mean $(V,\varphi,s)\mapsto (V\big|_{D_\infty},\varphi\big|_{D_\infty})$}
+    It is given in group-theoretic terms on the fibre over $ s $ by the inclusion
     $$
@@
     % \acom{replaced}
-
-    Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
+    % 
+    Finally, it is given in lattice terms on the fibre over $s$ as the identity on the lattice $(L,s)\mapsto L$ and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
     \item The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
-    $$
+    \begin{equation*}
+    % \label{eq:grbdgrs}
     \Gr_{0,s} \cong 
@@
     \end{cases}
-    $$
-    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializing to the appropriate discs.  
+    \end{equation*}
+    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle to the appropriate discs and trivializing.    
     In the lattice realization, it is given by forming tensor products 
@@
     % 
+    Finally, in group-theoretic terms, it is given (on representatives) by $g\mapsto (g,g)$.
+\acom{Reinstated the map.
+Choosing to supress the coset in our notation makes it potentially ambiguous.
+Maybe we can say inclusion $\times$ inclusion?
+In any case we should say something.
+Else, what are we referring to when we say ``This is compatible'' in the next line?}
     This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}]) $, we have
     $$
-    \left( g \CC[t]^m \right) \otimes_{\CC[t]} \cO = g \cO^m
+    \left( g \CC[t]^m \right) \otimes_{\CC[t]} \cO \cong g \cO^m
     $$
@@
     In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
-
+    \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$. 
+    % 
     %    \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
@@
 First, we recall that we have an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $, 
-for each $ s \ne 0$.  In turn, we have the isomorphism $ \Gr_s \cong \Gr$.
+for each $ s \ne 0$.  In turn, we have the isomorphism $ \Gr_s \cong \Gr$. \acom{We only just stated these. Too early to recall.}
 
 Gluing these together, we obtain
+\acom{Gluing together the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above,) we obtain}
 $$
@@
 $$
+\acom{What's $\Gr_{\CC^\times}$, $\Gr_{0,\CC^\times}$?}
 where the first morphism is an isomorphism and the second map uses $ \Gr_s \cong \Gr $ on each fibre.
@@
 
-Let $ X_1, X_2 \subset \Gr$ be two subschemes.
-We define the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
-
-\jcom{I changed this a bit in order to match Mirkovic--Vilonen better.}
-\acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
+Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
+% 
+% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
+% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
 % Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
-
+% 
 We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  
@@
 % $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
-\begin{equation}
-    \label{deservesdisplay}
+\begin{equation*}
+    % \label{deservesdisplay}
     X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
-\end{equation}
-which we call the fusion of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
-
-By this construction, \acom{technically, there were two given above, so *these* constructions?} $X_1 \ast_{\AA} X_2 $ is a flat family over $\CC$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
+\end{equation*}
+which we call the fusion of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. \acom{definition, no boldface}
+% 
+By construction, 
+% \acom{technically, there were two given above, so *these* constructions?} 
+$X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
+\acom{Question abt general fact: why is scheme-theoretic closure of product flat?}
 
@@
 \subsection{Some subvarieties of affine Grassmannians}
-Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N',N''$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
+Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N',N''$  and their sum $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
 % Coweights define elements in the various affine Grassmannians which we consider.
@@
     The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
-    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $ a \textbf{spherical Schubert variety}.  
+    $ \overline\Gr^\lambda = \bigcup_{\gamma \le \lambda} \Gr^{\gamma} $ a \textbf{spherical Schubert variety}.  
 \end{definition}
@@
 %\acom{should we also subsript this family with $0,\AA$?}
-    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
+By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ of $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA}$ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.
 % By \cite[Proposition 3.1.14]{zhu2016introduction},
@@
 % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
-    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by 
+Over $s=0$ the fibre is reduced and equal to $ \overline{\Gr}^{\lambda' + \lambda''}$ by 
 % a theorem of Zhu 
@@
 
-    Suppose that $ s \ne 0$.
-In the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.
+% Suppose that $ s \ne 0$.  
+Moreover, if $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.
 This open locus is a $ G(\CC[t])$-orbit
@@
 As above, since $ \lambda', \lambda'' $ are effective, the map $ \Gr_{0, \AA} \rightarrow \Grth$ restricts to a map $ \Gr^{\lambda', \lambda''}_{0, \AA} \rightarrow \Grth^+$.
+\acom{What is ``as above''?
+Also, we have only described the open loci in fibres over $s\ne0$.}
 
@@
 \end{definition}
-Since $\mu $ is effective, we see that $ \cW_\mu $ lies inside the positive thick Grassmannian $ \Grth^+$.
-    %
-
-    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
+Again, since $\mu $ is effective, we see that $ \cW_\mu $ lies inside the positive thick Grassmannian $ \Grth^+$.
+%
+
+In modular terms, $\cW_\mu$ corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
 The lattice description of $ \cW_\mu $ is given in Lemma \ref{le:Wmu} below.
@@
 and the \textbf{fusion of  semi-infinite orbits} 
-$$ S^{\mu', \mu''}_{0,\AA} := S^{\mu'} \ast_\AA S^{\mu''} \,.$$  
+$$ S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''} \to \AA \,.$$  
 \end{definition}
@@
 % \acom{changed $\mu$ to $\mu' + \mu''$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda', \lambda''} $}
-
+% 
 \jcom{Still need a reference for why this central fibre is reduced.}
+\acom{Two definitions in one. Why does fusion of spherical schubs get preferential treatment \emoji{astonished}}
 
@@
     % 
-    \item The family of adjoint orbits $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$ a consequence of Eisenbud and Salten's description/characterization(?) of ``rank varieties'' as proved in \Cref{cor:es}.
+    \item The family of adjoint orbits $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose \acom{Claim:} fibre over 0 is $\overline{\OO}^\lambda$ (a consequence of Eisenbud and Salten's characterization of ``rank varieties'' as proved in \Cref{cor:es}).
+\acom{TODO: make into definition to be x-referenced in proof of description of fibres}
 
@@
     \item Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$.
-The Mirkovic--Vybornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that
+The Mirkovi\'c--Vybornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that
     \[
@@
     % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
-    In pictures, aka by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
+    In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
     \[
@@
     \]
-    Smaller: 
-    \[
-        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
-            0 & 1 & 0 & 0 & 0\\
-            0 & 0 & 1 & 0 & 0\\
-            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
-            0 & 0 & 0 & 0 & 1\\
-            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
-            \end{BMAT}\right]    
-            \mapsto 
-            \left[\begin{array}{rr}
-                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
-                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
-            \end{array}\right]
-    \]
-
+    % 
     \item To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
@@
     where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
+    For example,
+    \[
+        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
+            0 & 1 & 0 & 0 & 0\\
+            0 & 0 & 1 & 0 & 0\\
+            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
+            0 & 0 & 0 & 0 & 1\\
+            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
+            \end{BMAT}\right]    
+            \mapsto 
+            \left[\begin{array}{rr}
+                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
+                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
+            \end{array}\right]\,. 
+    \]
     % For example, the $A$ above will define 
@@
     % \]
-
+    % 
     % \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
     % \acom{Ok.}
-
+    % 
     \item The ``upper-triangular'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
@@
     Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.
-
-    $\UU_{0,0}^{(?),(?)}$ entries look like 
-    \[
-        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
-            0 & 1 & 0 & 0 & 0\\
-            0 & 0 & 1 & 0 & 0\\
-            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
-            0 & 0 & 0 & 0 & 1\\
-            0 & 0 & 0 & 0 & 0
-            \end{BMAT}\right]    
-            % \mapsto 
-            % \left[\begin{array}{rr}
-            %     t^{3} & 0 \\
-            %     -A_{12}^2 t - A_{12}^1 & t^{2}
-            % \end{array}\right]
-    \]
-    $\UU^{\mu', \mu''}_{0,\AA}$ entries look like 
+For example, elements of $ \UU_{0,s}^{(1,1,0),(2,1,1)}$ look like
+% 
+% $\UU_{0,0}^{(?),(?)}$ entries look like 
+% \[
+%     \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
+%         0 & 1 & 0 & 0 & 0\\
+%         0 & 0 & 1 & 0 & 0\\
+%         0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
+%         0 & 0 & 0 & 0 & 1\\
+%         0 & 0 & 0 & 0 & 0
+%         \end{BMAT}\right]    
+%         % \mapsto 
+%         % \left[\begin{array}{rr}
+%         %     t^{3} & 0 \\
+%         %     -A_{12}^2 t - A_{12}^1 & t^{2}
+%         % \end{array}\right]
+% \]
     \[
@@
             0 & 0 & 0 & 0 & 0 & s
-            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
+            \end{BMAT}\right] \,.    % \in \UU_{0,s}^{(1,1,0),(2,1,1)}
     \]
@@
 % \acom{The following is a rough note.} 
-
-\begin{theorem}(\cite{eisenbud1989rank})
-    \label{thm:es}
-Let $r$ be a decreasing concave non-negative integral function with $r(0) = N$ (the dimension of the ambient vector space).
+\subsubsection{Detour of rank varieties}
+% \begin{theorem}(\cite{eisenbud1989rank})
+    % \label{thm:es}
+Let $r$ be a decreasing concave non-negative integral function with $r(0) = N$.
 Such a function is called a rank function.
-Then, in the space of $N\times N$ matrices,
+Eisenbud and Saltment associate to a rank function the vareity of $N\times N$ matrices
 % The relevant result from Eisenbud--Saltman seems to be that 
 $$X_r = X_{r,0} = \{A:\rk A^i \le r(i) \}$$ 
-is the flat limit of 
+and show that it is the flat limit of a certain family 
 % $$X_{r,\lambda} = \{A : \rk (A-\lambda_i)^j\le r(i,j)\}$$
@@
 with $r(i,j)$ determined by $r(i)$.  
-\end{theorem}
+% \end{theorem}
 
@@
 % 
-ES show that 
+More precisely, they show that 
 \begin{enumerate}
@@
         A \in \End(V) : \cork(A - z_i) \ge r(i-1) - r(i) , i = 1,\dots,m 
-        \right\}
+        \right\}\,. 
 \]
@@
 
-To construct the resolution, they take $m$ to be the largest number such that $r(m) \ne r(m+1)$.
-% Fact: rank functions stabilize
-Let $(x_1,\dots, x_m)$ be coordinates on $\AA^m$ and let $W\subset \AA^m$ be a linear subvariety (translate of subvectorspace). 
-They introduce the flag variety $F = \{(V = V_0 \supset V_1 \supset \cdots \supset V_m \supset 0 ) : \dim V_i = r(i)\}$ and define $\mathcal X_{r,W}\subset\End(V) \times W \times F$ to be the subvariety of triples $(A,\vec z,\{V_i\})$ such that $(A-z_i) V_{i-1} \subset V_i$ for $z_i = x_i(\vec z)$ and $i = 1,\dots,m$.
-The (reduced image of) projection of $\mathcal X_{r,W}$ down to $\End(V) \times W$ is denoted $X_{r,W}$ a closed affine subvariety.
-
+To construct the resolution, they take $m$ to be the largest number such that $r(m) \ne r(m+1)$
+and consider the affine space $\AA^m$ with coordinates $(x_1,\dots, x_m)$. Given $W\subset \AA^m$ a linear subvariety, 
+% TODO: clarify that linear subvariety means to them a (translate of subvectorspace)
+they introduce $\mathcal X_{r,W}\subset\End(V) \times W \times F_r$ where $F_r$ is the (paritial) flag variety $F_r = \{(V = V_0 \supset V_1 \supset \cdots \supset V_m \supset 0 ) : \dim V_i = r(i)\}$.
+% 
+$\mathcal X_{r,W}\subset\End(V) \times W \times F$ is defined to be the subvariety of triples $(A,\vec z,\{V_i\})$ such that $(A-z_i) V_{i-1} \subset V_i$ for $z_i = x_i(\vec z)$ and $i = 1,\dots,m$. 
+The (reduced image of) projection of $\mathcal X_{r,W}$ down to $\End(V) \times W$ is denoted $X_{r,W}$ and it is a closed affine subvariety. 
+% 
 \begin{theorem}
     (\cite[Theorem~2.1 iii)]{eisenbud1989rank})
-    $X_{r,W}$ is the restriction of $X_{r,\AA^m}$ to $W$ and it is flat over $W$. 
+    $X_{r,W}$ is the restriction of $X_{r,\AA^m}$ to $W$ and as such it is flat over $W$. 
 \end{theorem}
 
-They apply this result to study the fibers of the family $X_{r,\AA^m}$ over points $\vec z \in \AA^m$ for $z_i$ not necessarily distinct.
-They partition the coordinates $z_i$ of $\vec z$ by equality with the help of a permutation $p$ of $\{1,\dots,m\}$ such that
+This result is applied to study the fibers of the family $X_{r,\AA^m}$ over points $\vec z \in \AA^m$ for $z_i$ not necessarily distinct.
+The coordinates $z_i$ of $\vec z$ are partitioned by equality with the help of a permutation $p$ of $\{1,\dots,m\}$ such that
 \begin{align*}
@@
 \end{align*}
-and $p$ preserves the order within each interval $m_i + 1,\dots,m_{i+1}$. \acom{Not sure what this means. Order of coordinates?} With this notation in place they define 
+and $p$ preserves the order within each interval $m_i + 1,\dots,m_{i+1}$. \acom{Not sure what this means. Order of coordinates?} With this notation in place Eisenbud and Saltman define the numbers
 \begin{gather*}
@@
 \end{gather*}
-where $a_i = r(i-1) - r(i)$ which characterizes the Jordan types of the generalized eigenspaces associated to the eigenvalues $z_i$. Finally they state the following corollary. 
-\begin{corollary}
+where $a_i = r(i-1) - r(i)$.
+It is through the $r(i,j)$ that the rank function $r$ determines the Jordan types of the generalized eigenspaces of the vector of (generalized) eigenvalues $\vec z$. 
+\begin{proposition}
     (\cite[Corollary~2.2]{eisenbud1989rank})
+    \label{prop:es}
     The scheme-theoretic fibre of $X_{r,W}$ over $\vec z\in W$ is 
     \[
-        X_{r,\vec z} = \{A \in \End(V) : \rk (A-z_i)^j\le r(i,j) \text{ for all } i , j \}
-    \]
-\end{corollary}
-
+        X_{r,\vec z} = \{A \in \End(V) : \rk (A-z_i)^j\le r(i,j) \text{ for all } i , j \}\,. 
+    \]
+\end{proposition}
+% 
 \begin{corollary}
     \label{cor:es}
-    The family $\OO^{\lambda',\lambda''}_{0,\AA}$ defined by \Cref{above} has zero fibre $\OO^\lambda$. 
+    The family $\OO^{\lambda',\lambda''}_{0,\AA}$ defined above has zero fibre $\OO^\lambda$. 
 \end{corollary}
-
+% 
+The only work we have to do to apply \Cref{prop:es} is to determine the rank function that will allow us to realize $\OO^\lambda$ as a rank variety, and the family $\OO^{\lambda',\lambda''}_{0,\AA}$ as a deformation of it.
+%  
 \begin{lemma}
     \label{lem:es}
-    Let $\lambda = \lambda' + \lambda''$ be permutations.
-There exists a permutation of the columns of $\lambda$ such that the first $\lambda'_1$ columns are precisely the columns of $\lambda'$ and the next $\lambda''_1$ columns are precisely the columns of $\lambda''$.
+    Let $\lambda = \lambda' + \lambda''$ be partitions.
+There exists a permutation of the columns of $\lambda$ such that the first $\lambda'_1$ columns are precisely the columns of $\lambda'$ and the last $\lambda''_1$ columns are precisely the columns of $\lambda''$.
 \end{lemma}
-
+Recall that $\lambda' + \lambda'' = \lambda$ is a partition of $N$. 
+% Let $m_i = \lambda_{i,1}$ ($i = 1,2$), $m = m_1 + m_2$, and define
+Let $m = \lambda_1' + \lambda_2'$ and define 
+$$r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$$
+on $j = 1,\dots,m$. 
 \begin{lemma}
-   $r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$ is a rank function. 
+   The function $r$
+%    defined by $r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$ 
+is a rank function. 
 \end{lemma}
 
-The case that we are interested in is the case of two generalized/repeated eigenvalues, i.e.\ $\vec z = (z_1,z_2) = (0,s)$. \acom{Does order matter?} 
+The case that we are interested in is the case of two generalized eigenvalues, i.e.\ $\vec z = (z_1,z_2) = (0,s)$. 
+\acom{Does order matter?} 
 % Let me change notation so that $\lambda_i$ are shapes and 
@@
 
-Recall that $\lambda' + \lambda'' = \lambda$ is a partition of $N$. 
-Let $m_i = \lambda_{i,1}$ ($i = 1,2$), $m = m_1 + m_2$, and define
-$$r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$$
-on $j = 1,\dots,m$. Note that $r(j-1) - r(j)$ is the length of the $j$th column of $\lambda$. As in \cite{eisenbud1989rank} we will denote this quantity $a_j$. 
-%
-
-Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(m_1)}$ are the (lengths of) columns of $\lambda'$ and $a_{p(m_1 + 1)},\dots, a_{p(m_1 + m_2)}$ are the (lengths of) columns of $\lambda''$.
+Note that $r(j-1) - r(j) = : a_j$ is the length of the $j$th column of $\lambda$. 
+% As in \cite{eisenbud1989rank} we will denote this quantity $a_j$. 
+% 
+% 
+Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(\lambda_1')}$ are the (lengths of) columns of $\lambda'$ and $a_{p(\lambda_1' + 1)},\dots, a_{p(m)}$ are the (lengths of) columns of $\lambda''$.
 Then the functions 
@@
 % \text{ and } 
-r(2,j) &= N - a_{p(m_1 + 1)} - \cdots - a_{p(m_1 + j)}
+r(2,j) &= N - a_{p(\lambda_1' + 1)} - \cdots - a_{p(\lambda_1' + j)}
 \end{aligned}
@@
 \begin{align*}
-    \OO^{\lambda',\lambda''}_{0,s} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots, m_1 \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = m_1 + 1 ,\dots, m \}
+    \OO^{\lambda',\lambda''}_{0,s} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots, \lambda_1' \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = \lambda_1' + 1 ,\dots, m \}
 \end{align*}
-and according to \cite[Theorem 2.1(iii)]{eisenbud1989rank} the family $X_{r,\AA^m}$ is flat over $\AA^m$ with zero fibre $X_{r,0} = \OO^\lambda$ as desired.
+and according to \cite[Theorem 2.1(iii)]{eisenbud1989rank} the family $X_{r,(0,s)}$ is flat over $W = \{x_1 = \cdots = x_{\lambda_1'} = 0 , x_{\lambda_1'} = \cdots = x_m\}$ (a linear subvariety of $\AA^m$) with zero fibre $X_{r,(0,0)} = \OO^\lambda$ as desired.
+\acom{Do you need to permute the indices defining $W$?}
+% $X_{r,\AA^m}$ is flat over $\AA^m$ with zero fibre $X_{r,0} = \OO^\lambda$ as desired.
 I guess we need to carefully choose the $W \subset \AA^m$ defining our family, which is smaller than the family $X_{r,\AA^m}$.
@@
 Computing fusion still hard but at least boiled down to linear algebra.
-Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
+Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,Mirkovi\'c2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
 
@@
 \begin{proof}
-First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\cO)t^\lambda $ if and only if $ t |_{L_0/L} $ has Jordan type $ \lambda$. \acom{Change $L_0$}
+First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\cO)t^\lambda $ if and only if $ t |_{\cO^m/L} $ has Jordan type $ \lambda$. 
+% \acom{Change $L_0$}
 
@@
     \end{enumerate}
-    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$. \acom{Change $L_0$}
+    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ \CC[t]^m/L$. 
+    % \acom{Change $L_0$}
 \end{lemma}
-
-\jcom{I realized the meaning of the ``extra'' condition from the paper with Sabin and I added it into point 3.}
-\acom{Technically though the extra condition in that paper is weaker? $W_{\mu_i}$ being the span of $e_j,te_j,\dots,t^{\mu_i-1}e_j$ or the complement of $t^{\mu_i}\cO^m$ in $\cO^m$.}
-
+% 
+% \jcom{I realized the meaning of the ``extra'' condition from the paper with Sabin and I added it into point 3.}
+% \acom{Technically though the extra condition in that paper is weaker? $W_{\mu_i}$ being the span of $e_j,te_j,\dots,t^{\mu_i-1}e_j$ or the complement of $t^{\mu_i}\cO^m$ in $\cO^m$.}
+% 
 \begin{proof}
@@
 \end{proof}
-\acom{note-to-self, skipped this; return to it.}
-
+% \acom{note-to-self, skipped this; return to it.}
+% 
 \begin{lemma}
@@
 \end{lemma}
-\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?}}
+\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?} Update: added this above.}
 % Resolved?
@@
 
-The following result is \cite[Theorem 3.2]{cautis2018categorical}.
-
+The following result is \cite[Theorem 3.2]{cautis2018categorical} up to transpose.
+% 
 \begin{theorem} \label{th:TmuWmu}
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
-$$ L \mapsto [t|_{\CC[t]^m/L} ]_{\beta_\mu} \,. $$
-\acom{Up to transpose?!}
+$$ L \mapsto [t|_{\CC[t]^m/L} ]_{\beta_\mu}' \,. $$
+% \acom{Up to transpose?!}
 \end{theorem}
+%
 
 For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ with $\cW_\mu$.  
-As $  \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the map 
+As $  \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ is not a subscheme of $ \Grth$, by this intersection, we really mean the preimage of $ \cW_\mu$ under the composition
 $$ 
@@
 \begin{proof}
-    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.
+    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovi\'c-Vybornov isomorphism.
 Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
@@
 
-\begin{proposition}(\cite{baumann2019mirkovic})
+\begin{proposition}(\cite{baumann2019Mirkovi\'c})
     % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
@@
 Suppose we have two tableaux $\tau_1$ and $\tau_2$ with respective weights $\lambda_i$ and $\mu_i$ and we wished to take their fusion product.
-We consider a generic matrix $X \in \UU^{\mu_1,\mu_2}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda_1,\lambda_2}_{0,s}$.
+We consider a generic matrix $X \in \UU^{\lambda_1,\lambda_2}_{0,s}$.
 
 Consider the subtableaux $\tau_{1,i}$ of $\tau_1$ and $\tau_{2,i}$ of $\tau_2$ where we take the boxes of $\tau_1$ and $\tau_2$ containing the numbers $1,\dots,i$.
-Let $\lambda_{1,j}$ and $\lambda_{2,j}$ be the corresponding sizes and $\mu_{1,j}$ and $\mu_{2,j}$ be the corresponding weights of the subtableaux.
-For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu_{1,i}, \mu_{2,i}}_{0,s}$ of $X$.
-These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda_{1,i}, \lambda_{2,i}}_{0,s}$, which allows us to deduce relations on the variables in $X$.
+Let $\lambda_{1,j}$ and $\lambda_{2,j}$ be the corresponding dominant weights.
+For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\lambda_{1,i}, \lambda_{2,i}}_{0,s}$ of $X$.
+These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ which allows us to deduce relations on the variables in $X$.
 The relations must also include the new variables in the latest block and cannot have $s$ as a factor.
@@
 $$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$
-
-Lusztig data: $(010000)$ for $\tau_1$, $(100100)$ for $\tau_2$
-
-Dimensions: $\alpha_1 + \alpha_2$ for both.
-
 The MV cycles corresponding to $\tau_1$ and $\tau_2$ are both isomorphic to $\PP^2$.
@@
 which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau_1$ and $\tau_2$.
-
-Lusztig datum: $(110100)$
-
-Dimension: $2\alpha_1 + 2\alpha_2$
 \end{example}
@@
 $$\tau_1 = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(11,23).$$
-
-Lustig data: $(100000)$ for $\tau_1$, 
 The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.

### 2021-04-10 draft.tex

@@
 $$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$
+
+Lusztig data: $(010)$ for $\tau_1$, $(101)$ for $\tau_2$
+
+Dimensions: $(1,0,-1)$ for both.
+
 The MV cycles corresponding to $\tau_1$ and $\tau_2$ are both isomorphic to $\PP^2$.
@@
 which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau_1$ and $\tau_2$.
+
+Lusztig datum: $(111)$
+
+Dimension: $(2,0,-2)$
 \end{example}
@@
 $$\tau_1 = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(11,23).$$
+
+Lustig data: $(100)$ for $\tau_1$, $(001)$ for $\tau_2$.
+
+Dimensions: $(1,-1,0)$ for $\tau_1$, $(0,1,-1)$ for $\tau_2$.
+
 The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.

### 2021-04-10 draft.tex
Updates from Overleaf

--- 2021-04-09 draft.tex
@@
     \begin{enumerate}
-        \item $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. \acom{Should we describe this map somewhere? Earlier?}
+        \item $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. %\acom{Should we describe this map somewhere? Earlier?}
         \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $(0,\lambda'), (s,\lambda'')$.
@@
 
-    Now assume that $ (L, s) \in \Gr^{\lambda', \lambda''}_{0,s}$.
-We know that \acom{Rather than we know, it is by definition?} $ L(0) \in \Gr^{\lambda'}$ and $L(s) \in \Gr^{\lambda''} $.
-This means that $t $ acting on
+    Now assume that $ (L, s) \in \Gr^{\lambda', \lambda''}_{0,s}$.  By definition, $ L(0) \in \Gr^{\lambda'}$ and $L(s) \in \Gr^{\lambda''} $.  This means that $t $ acting on 
     % $ \CC\xt^m / L(0)$ 
@@
     % $ \CC\xt[t-s]^m / L(s) $ 
-    $\cO_s^m/L(s)$ has Jordan type $ \lambda''$.  Now, the map 
+    $\cO_s^m/L(s)$ has Jordan type $ \lambda''$.  For $ a = 0, s$,  $\CC[t]^m/L \otimes_{\CC[t]} \cO_a \cong \cO_a^m / L(a) $.
+    Thus, Lemma \ref{le:linalg} shows that the map
     % $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
@@
     $ (t-s)^{\lambda''} \in G(\cO)$. In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
+\end{proof}
+
+\begin{lemma}
+    Let $ T : V \rightarrow V$ be a linear operator on a finite-dimensional complex vector space.
+Define a $ \CC[t]$-module structure on $ V $ where $ t $ acts by $ T$.
+For any  $ a \in \CC$, the map
+    $$ V  \rightarrow V \otimes_{\CC[t]} \cO_a$$
+    restricts to an isomorphism between the generalized $ a $ eigenspace of $ T $ and $ V \otimes_{\CC[t]} \cO_a$
+
+    \end{lemma}
+
+\begin{proof}
+    Let $ E_b $ denote the generalized $b$-eigenspace of $T$.
+Then $ V = \oplus_{b \in \CC} E_b$.
+Since $ t - b$ is invertible in $ \cO_a$ and $ T -b $ acts nilpotently on $ E_b$, we see that $ E_b \otimes_{\CC[t]} \cO_a = 0 $.
+
+    So it suffices to show that $ E_a \rightarrow E_a \otimes_{\CC[t]} \cO_a$ is an isomorphism.
+By the classification of modules over $ \CC[t]$, it suffices to check this when  $ E_a = \CC[t]/(t-a)^k$, where it is clearly true.
 \end{proof}
@@
     \end{enumerate}
-    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$. \acom{Change $L_0$}
+    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ \CC[t]^m/L$. 
 \end{lemma}
@@
 \section{Climax}
-Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.
+Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.  Note that $g(A)t^{-\mu} \in G_1(\Oinf)$.
 % section ??.  
-Since $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
+Since $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)t^\mu$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
+(Alternatively, we can see that $ g(A) \CC[t]^m$ satisfies the condition (ii) from Lemma \ref{le:Wmu}.)
 
@@
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
-$$ L \mapsto [t|_{\CC[t]^m/L} ]_{\beta_\mu} \,. $$
-\acom{Up to transpose?!}
+$$ L \mapsto [t|_{\CC[t]^m/L} ]^{tr}_{\beta_\mu} \,. $$
+%\acom{Up to transpose?!}
 \end{theorem}
@@
 $$
-The right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.
+Since $ g, h, n_1 \in G_(\Oinf)$, the right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.
+Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.
 

### 2021-04-10 draft.tex

--- 2021-04-10 draft.tex
@@
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
-$$ L \mapsto [t|_{\CC[t]^m/L} ]_{\beta_\mu}' \,. $$
-% \acom{Up to transpose?!}
+$$ L \mapsto [t|_{\CC[t]^m/L} ]^{tr}_{\beta_\mu} \,. $$
+%\acom{Up to transpose?!}
 \end{theorem}

### 2021-04-11 draft.tex
joels edits

@@
 \acom{random question, I know $H(R)$ is supposed to mean functor of points of the scheme $H$ but can it also be viewed as a base change from $\CC$ to $\RR$?}
+\jcom{Usually $ H_R$ is the notation used for the base change, so using $ H(R)$ here is a bit of an abuse, but it is common and harmless.}
 % 
 Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.
-We denote the kernel of this map by $ H_1(\cO_s)$.
-We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$ which is often called the first congruence subgroup.
+We denote the kernel of this map by $ H_1(\cO_s)$, often called the  first congruence subgroup.
+We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$.
 % \acom{Add $G_1$}
@@
 % are there other possibilities?? :S 
-Write $P$ for the coweight lattice $\Hom(\CC^\times,T)$ of $T$, so we have $P\cong \ZZ^m$.  
+The coweight lattice of $ G $ is $ \ZZ^m = \Hom(\CC^\times,T)$.
 % TODO: Thank you - resolved!
@@
 
-Under this isomorphism the dominant coweights of $ G $ 
+The \textbf{dominant coweights} of $ G $ 
 % is
-are identified with the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
-We also need the notion of effective dominant coweight, 
+are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.
+
+A coweight $ \mu = (\mu_1, \dots, \mu_m)$ is called \textbf{effective}, if $ \mu_j \ge 0 $ for all $ j$.
+%We also need the notion of effective dominant coweight, 
 % \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
-which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  
+%which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  
 \acom{1.
@@
 Since we sometimes need $\Peff$ which contains $P_{++} = \Peff\cap\Pdom$, how about just using the notation $\Peff,\Pdom$ instead of $P_+, P_{++}$ for a change?}
+\jcom{I added the definition of effective coweight.
+I actually don't think that we need any special notation $ P, P_+, P_{dom}$ etc !
+Later we can just write ``$ \lambda \in \ZZ^m$ a dominant or effective coweight'' etc}
 % 
 So an effective dominant coweight $ \lambda $ is a partition of $|\lambda| = \lambda_1 + \cdots + \lambda_m\in\NN$, which we call the size of $ \lambda$.
-We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights.
+%We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights.
 
@@
 
-Given a coweight $\mu \in P$ and a point $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
+Given a coweight $\mu \in \ZZ^m$ and a point $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
 % with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
@@
 % $\GL_m(R) $ 
-$G(R)$ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$. Thus for example $ t^\lambda \in M_m(\CC[t])$ for all $ \lambda \in P_{++}$ but 
+$G(R)$ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$. Thus for example $ (t-s)^\mu\in M_m(\CC[t])$ for all effective $ \mu \in \ZZ^m$ but 
 % $ t^\lambda \in \GL_m(\CC[t]) $ 
-$t^\lambda\in G(\CC[t])$ if and only if $ \lambda = 0 $. \acom{maybe add that it's the same for $G(\cO)$.}
+$(t-s)^\mu\in G(\CC[t])$ if and only if $ \mu = 0 $.
+
+\acom{maybe add that it's the same for $G(\cO)$.}
 
@@
 \label{ss:lat}
-We will use the lattice model \acom{for each of the affine Grassmannians which we consider---again, this is putting the cart in front of the horse, as we haven't introduced any affine Grassmannians yet}, so it is useful to recall the following definition.
-Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field).
+We will use the lattice model for the affine Grassmannian, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
 % \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
@@
 % \acom{Wait, I thought $\CC(t)$ is used in the Ran space version of the BD Gr.}
-Given such a lattice $ L $ and a point $ a \in \CC$, the specialization \acom{definition, no boldface} of $ L $ at $ a $ is defined as
+Given such a lattice $ L $ and a point $ a \in \CC$, the \textbf{specialization} of $ L $ at $ a $ is defined as
 $$
@@
 % $ L(a) = L_0(\cO_a)$ 
-$L(a) = \cO_a^m$ then $L$ is said to be trivial at $a$. 
+$L(a) = \cO_a^m$ then $L$ is said to be \textbf{trivial at $a$}. 
 % We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
 % \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
-For example, since $(t-s)^{-1} = \frac 1 {a-s}\sum(\frac{t-a}{s-a})^k$ if $a\ne s$, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$. 
+For example, since $t-s $ is invertible in $ \cO_a $ if $ a \ne s $, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$. 
 % \acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}
@@
 $$
-\acom{What is the modular description of the fibre?}
+\acom{What is the modular description of the fibre?} \jcom{That is written above (just fix $ s$).}
 % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
@@
     % \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
-    \item We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $.
+    \item 
+    %We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $.
     % $$ \Grbd \rightarrow \Grth $$ 
-    It is given in modular terms by restricting the trivialization to $ D_\infty$. \acom{Does it mean $(V,\varphi,s)\mapsto (V\big|_{D_\infty},\varphi\big|_{D_\infty})$}
-    It is given in group-theoretic terms on the fibre over $ s $ by the inclusion
+    We define a map $ \Grbd \rightarrow \Grth $ by 
+    $$(V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty})$$
+
+%    It is given in modular terms by restricting the trivialization to $ D_\infty$. \acom{Does it mean $(V,\varphi,s)\mapsto (V\big|_{D_\infty},\varphi\big|_{D_\infty})$}
+    In group-theoretic terms, on the fibre over $ s $, this is the inclusion
     $$
@@
     \end{equation*}
-    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle to the appropriate discs and trivializing.    
-    In the lattice realization, it is given by forming tensor products 
+    This isomorphism is given in the modular realization by restricting the vector bundle and trivialization.
+
+    Suppose that $ s \ne 0 $.  In the lattice realization, this is given by forming the specializations 
     $$
@@
     $$
+    Note that if $ L = g \CC[t]^m$ for $ g \in G([t,t^{-1}, (t-s)^{-1}])$, then 
+    $$(L(0), L(s)) = (g \cO^m, g\cO^m_s)$$
+
+    \jcom{I restated this again.  I think that it is simpler and more clear like this.  And I think that this is the fact that we end up using later.}
+
     % in the $ s \ne 0 $ case.
@@
     % 
-    Finally, in group-theoretic terms, it is given (on representatives) by $g\mapsto (g,g)$.
+%    Finally, in group-theoretic terms, it is given (on representatives) by $g\mapsto (g,g)$.
 \acom{Reinstated the map.
@@
 Else, what are we referring to when we say ``This is compatible'' in the next line?}
-    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}]) $, we have
-    $$
-    \left( g \CC[t]^m \right) \otimes_{\CC[t]} \cO \cong g \cO^m
-    $$
-    and similarly for $ L(s)$.
+%    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}]) $, we have
+%    $$
+%    \left( g \CC[t]^m \right) \otimes_{\CC[t]} \cO \cong g \cO^m
+%    $$
+%    and similarly for $ L(s)$.
 
@@
 The following construction will be very important in this paper.
-First, we recall that we have an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $, 
-for each $ s \ne 0$.  In turn, we have the isomorphism $ \Gr_s \cong \Gr$. \acom{We only just stated these. Too early to recall.}
-
-Gluing these together, we obtain
-\acom{Gluing together the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above,) we obtain}
+
+Let $ \Gr_{0, \CC^\times} $ denote the preimage of $ \Gr_{0, \AA} $ under the map $\Gr_{0,\AA} \rightarrow \AA $.
+Gluing together the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above) we obtain
 $$
@@
 $$
-\acom{What's $\Gr_{\CC^\times}$, $\Gr_{0,\CC^\times}$?}
 where the first morphism is an isomorphism and the second map uses $ \Gr_s \cong \Gr $ on each fibre.
 (This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
+\jcom{I added the def of $ \Gr_{0, \CC^\times}$ but not $ \Gr_{\CC^\times}$.  We could drop it and condense the definition of $ \tau$ to one map.}
 
@@
 \end{equation*}
-which we call the fusion of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. \acom{definition, no boldface}
+which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
 % 
@@
 $X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
-\acom{Question abt general fact: why is scheme-theoretic closure of product flat?}
+\acom{Question abt general fact: why is scheme-theoretic closure of product flat?} \jcom{See Hartshorne Proposition III.9.8.
+I just taught this on the last day of my algebraic geometry class!}
 
@@
 \subsection{Some subvarieties of affine Grassmannians}
-Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N',N''$  and their sum $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
+Now fix effective dominant coweights $\lambda', \lambda'' $ of sizes $N',N''$  and their sum $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
 % Coweights define elements in the various affine Grassmannians which we consider.
@@
     % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
-    Note, since $ \lambda $ is effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
-\acom{why ``and so''?
-bc orbits are connected?}
+
     % 
@@
 
-As above, since $ \lambda', \lambda'' $ are effective, the map $ \Gr_{0, \AA} \rightarrow \Grth$ restricts to a map $ \Gr^{\lambda', \lambda''}_{0, \AA} \rightarrow \Grth^+$.
-\acom{What is ``as above''?
-Also, we have only described the open loci in fibres over $s\ne0$.}
-
-Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ of size $N',N''$ resp. such that $ \mu = \mu' + \mu'' $ is dominant. (We do not require $ \mu', \mu'' $ to be effective.) 
+Because we consider effective dominant weight, the spherical Schubert varieties and their fusions lie in the positive part of the (thick) affine Grassmannian.
+
+\begin{lemma}
+    The map $ \Gr_{0, \AA} \rightarrow \Grth$ restricts to a map $ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} \rightarrow \Grth^+$.
+\end{lemma}
+\begin{proof}
+    Let $ s \ne 0 $.
+Since $ \lambda', \lambda'' $ are effective, $ t^{\lambda'}, (t-s)^{\lambda''} \in \Grth^+ $.
+Since $\Grth^+$ is closed and invariant under the action of $ G(\CC[t])$,  $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} \subset \Grth^+$.
+
+    For the $ s = 0$ fibre, a similar reasoning applies (or we can simply conclude by taking closure).
+\end{proof}
+    \acom{why ``and so''? bc orbits are connected?}
+    \jcom{I turned this into a Lemma.}
+
+%As above, since $ \lambda', \lambda'' $ are effective, the map $ \acom{What is ``as above''? Also, we have only described the open loci in fibres over $s\ne0$.}
+
+Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ of size $N',N''$ resp. such that $ \mu = \mu' + \mu'' $ is dominant. (We do not require $ \mu', \mu'' $ to be dominant.) 
 Using $ \mu, \mu', \mu''$, we define the following subschemes.
@@
     % $ \CC\xt[t-s]^m / L(s) $ 
-    $\cO_s^m/L(s)$ has Jordan type $ \lambda''$.  For $ a = 0, s$,  $\CC[t]^m/L \otimes_{\CC[t]} \cO_a \cong \cO_a^m / L(a) $.
+    $\cO_s^m/L(s)$ has Jordan type $ \lambda''$.  For $ a = 0, s$,  we see that $$\CC[t]^m/L \otimes_{\CC[t]} \cO_a \cong \cO_a^m / L(a). $$
     Thus, Lemma \ref{le:linalg} shows that the map
@@
 This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).
-\acom{is this map $v + L \mapsto v + L(0)$?} \marginpar[]{*}
+\acom{is this map $v + L \mapsto v + L(0)$?} \jcom{yes} \marginpar[]{*}
     % todo
@@
 
-\begin{lemma}
-    Let $ T : V \rightarrow V$ be a linear operator on a finite-dimensional complex vector space.
-Define a $ \CC[t]$-module structure on $ V $ where $ t $ acts by $ T$.
-For any  $ a \in \CC$, the map
+\begin{lemma} \label{le:linalg}
+    Let $ V $ be a $ \CC[t]$-module which is finite-dimensional as a $ \CC$ vector space.  For any  $ a \in \CC$, the map
     $$ V  \rightarrow V \otimes_{\CC[t]} \cO_a$$
-    restricts to an isomorphism between the generalized $ a $ eigenspace of $ T $ and $ V \otimes_{\CC[t]} \cO_a$
+    restricts to an isomorphism between the generalized $ a $-eigenspace of $ t $ and $ V \otimes_{\CC[t]} \cO_a$
 
@@
 \begin{proof}
-    Let $ E_b $ denote the generalized $b$-eigenspace of $T$.
+    For any $ b \in \CC$, let $ E_b $ denote the generalized $b$-eigenspace of $t$.
 Then $ V = \oplus_{b \in \CC} E_b$.
-Since $ t - b$ is invertible in $ \cO_a$ and $ T -b $ acts nilpotently on $ E_b$, we see that $ E_b \otimes_{\CC[t]} \cO_a = 0 $.
+Since $ t - b$ is invertible in $ \cO_a$ and $ t -b $ acts nilpotently on $ E_b$, we see that $ E_b \otimes_{\CC[t]} \cO_a = 0 $.
 
@@
 \end{lemma}
-\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?} Update: added this above.}
+%\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?} Update: added this above.}
 % Resolved?
@@
 $$
-Since $ g, h, n_1 \in G_(\Oinf)$, the right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.
+Since $ g, h, n_1 \in G_1(\Oinf)$, the right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.
 Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.

### 2021-04-12 draft.tex
Joel cleaned up ES

@@
 
-\subsection{Matrices}
+\section{Matrices}
+
+\subsection{Adjoint orbits and their deformations}
  We now consider some subvarieties of the space of $ N\times N$ matrices, again using the $ \lambda, \lambda', \lambda'', \mu, \mu', \mu''$ defined in the previous section.
@@
 
-\begin{itemize}
-    \item For $ s \in \CC$ 
+ For $ s \in \CC$ 
     % and $\lambda\in P_{++}$
-    we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. 
+    we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. 
     % \acom{$s\in\AA$?}
     %
-    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
-    % 
-    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
+
+\begin{definition}
+The nilpotent orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.
+\end{definition}  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
+    % 
+\begin{definition}
+ For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
+\end{definition}  
+    % \acom{$s\in\AA$?}
+    % 
+     A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
+    %
+
      Its closure is $ \overline{\OO}^{\lambda', \lambda''}_{0,s} = \bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.
-    % \acom{$s\in\AA$?}
-    % 
-    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
-    % 
-    \item The family of adjoint orbits $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose \acom{Claim:} fibre over 0 is $\overline{\OO}^\lambda$ (a consequence of Eisenbud and Salten's characterization of ``rank varieties'' as proved in \Cref{cor:es}).
+
+     We recall that these adjoint orbit closures are given by rank conditions.  More precisely we have
+     $$
+     \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^i \le N - \#\text{~boxes in first $i$ columns of }\lambda \}
+     $$
+     and
+     \begin{equation} \label{eq:ranks}
+     \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i \le N - 
+     \#\text{~boxes in first $i$ columns of }\lambda' \quad
+     \rk (A-s)^i \le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
+     \end{equation}
+
+\begin{proposition} \label{prop:adjoint}
+    There exists a flat family  $\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $s \in \AA$ is reduced and given by
+       $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ if $s \ne 0 $ and
+$        \overline{\OO}^\lambda $ if $ s = 0$.
+\end{proposition}
+
+In order to prove this result, we will need to recall some results from Eisenbud-Saltman \cite{eisenbud1989rank}.
+
+Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
+\jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.}
+
+Let $ W$ be a subspace of $ \AA^k$.  Eisenbud-Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions.  We will now describe these fibres.
+
+Let $ z \in \AA^k$.
+Some of the coordinates of $z$ are equal; we introduce some data to describe these equalities.
+There exist unique $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a minimal length permutation  $ p $ of $ \{1, \dots, k\}$ such that $$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)} $$
+
+\jcom{Eisenbud-Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
+
+Next for $ j = 1, \dots r $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
+$$
+    r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
+$$
+\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
+By \cite[Corollary 2.2]{eisenbud1989rank}, the fibre of the flat family $ X_{r,W} $ over $ z$ is given by
+\begin{equation} \label{eq:ESfibre}
+X_{r,z} = \{ A \in M_N(\CC) :\rk (A-s_j)^i\le r_{z,j}(i) \text{ for all } i , j \text{ as above}\}.
+\end{equation}
+
+We will now apply these ideas to prove our Proposition \ref{prop:adjoint}.
+
+\begin{proof}
+
+%\begin{lemma}
+%    \label{lem:es}
+%    Let $\lambda = \lambda' + \lambda''$ be partitions.
+There exists a permutation of the columns of $\lambda$ such that the first $\lambda'_1$ columns are precisely the columns of $\lambda'$ and the last $\lambda''_1$ columns are precisely the columns of $\lambda''$.
+%\end{lemma}
+%Recall that $\lambda' + \lambda'' = \lambda$ is a partition of $N$.
+
+Define 
+$$r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda$$
+It is easy to see that this is a rank function, with $ k = \lambda_1$, the number of columns of $ \lambda$.
+%\begin{lemma}
+%   The function $r$
+%    defined by $r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$ 
+%is a rank function. 
+%\end{lemma}
+
+Since $\lambda = \lambda' + \lambda''$, there exists a permutation $ p $ of $ \{1, \dots, k\}$ (the columns of $ \lambda$) such that $ p(1), \dots, p(k_1) $ are the columns of $ \lambda'$ and $ p(k_1+1), \dots, p(k)$ are the columns of $ \lambda''$.
+Here $ k_1 = \lambda'_1$ the number of columns of $ \lambda'$.
+
+For $ s \in \CC$, we define $ z(s) \in \CC^k$, with $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1 \dots + k$.
+
+For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduces the permutation $ p$, that $ r = 2 $, and that
+\begin{equation} \label{eq:rcols}
+r_{z(s), 1}(i) =  N - 
+     \#\text{~boxes in first $i$ columns of }\lambda'
+     \quad
+     r_{z(s), 2}(i) =  N - \#\text{~boxes in first $i$ columns of }\lambda'' 
+     \end{equation}
+On the other hand, for $z(0)$, we get $ r = 1$ and that 
+\begin{equation} \label{eq:rcol2}
+r_{z(0),1}(i) = r(i) = n -  N - 
+     \#\text{~boxes in first $i$ columns of }\lambda
+\end{equation}
+\jcom{Someone should check that I chose the notation correctly to make this work out.}
+
+Let $ W = \{ z(s) : s \in \CC \}$.
+Combining (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) we see that the Eisenbud-Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
+\end{proof}
+
+%     The family of adjoint orbits $  whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose \acom{Claim:} fibre over 0 is $\overline{\OO}^\lambda$ (a consequence of Eisenbud and Salten's characterization of ``rank varieties'' as proved in \Cref{cor:es}).
 \acom{TODO: make into definition to be x-referenced in proof of description of fibres}
@@
 
-    \item Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$.
-The Mirkovi\'c--Vybornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that
+\subsection{The Mirkovic-Vybornov slice} Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
+\begin{definition}The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
     \[
@@
     \]
+\end{definition}
+\jcom{I'm not a huge fan of this description, but I don't know how to write it better.}
+
     In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
@@
     % 
-    \item To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
+     To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
     of polynomials 
@@
     % 
-    \item The ``upper-triangular'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
+    \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
     $$
@@
     $$
+    \end{definition}
     So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
@@
     % \acom{And, sorry, ignore my other comment; it's the same $\CC$ (or $\AA$) nothing to distinguish.}
-\end{itemize}
 
@@
 % \acom{The following is a rough note.} 
+\begin{comment}
 \subsubsection{Detour of rank varieties}
@@
 \[
-    X_{r;z_1,\dots,z_m} = \left\{
-        A \in \End(V) : \cork(A - z_i) \ge r(i-1) - r(i) , i = 1,\dots,m 
-        \right\}\,. 
+. 
 \]
@@
 and $p$ preserves the order within each interval $m_i + 1,\dots,m_{i+1}$. \acom{Not sure what this means. Order of coordinates?} With this notation in place Eisenbud and Saltman define the numbers
-\begin{gather*}
+
+% 
+\begin{corollary}
+    \label{cor:es}
+    The family $\OO^{\lambda',\lambda''}_{0,\AA}$ defined above has zero fibre $\OO^\lambda$. 
+\end{corollary}\begin{gather*}
     r(i,j):= \dim V - a_{p(m_i + 1)} - \cdots - a_{p(m_i + j )} \\
@@
 \end{proposition}
-% 
-\begin{corollary}
-    \label{cor:es}
-    The family $\OO^{\lambda',\lambda''}_{0,\AA}$ defined above has zero fibre $\OO^\lambda$. 
-\end{corollary}
 % 
@@
 % \acom{That's it for the note.}
+\end{comment}
 

### 2021-04-12 __latexindent_temp.tex
fixed some typos

--- 2021-04-12 draft.tex
@@
 % 
-\acom{random question, I know $H(R)$ is supposed to mean functor of points of the scheme $H$ but can it also be viewed as a base change from $\CC$ to $\RR$?}
-\jcom{Usually $ H_R$ is the notation used for the base change, so using $ H(R)$ here is a bit of an abuse, but it is common and harmless.}
+% \acom{random question, I know $H(R)$ is supposed to mean functor of points of the scheme $H$ but can it also be viewed as a base change from $\CC$ to $\RR$?}
+% \jcom{Usually $ H_R$ is the notation used for the base change, so using $ H(R)$ here is a bit of an abuse, but it is common and harmless.}
 % 
@@
 % \jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}
-
+% 
 The \textbf{dominant coweights} of $ G $ 
@@
 are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
-
+% 
 A coweight $ \mu = (\mu_1, \dots, \mu_m)$ is called \textbf{effective}, if $ \mu_j \ge 0 $ for all $ j$.
-%We also need the notion of effective dominant coweight, 
+% We also need the notion of effective dominant coweight, 
 % \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
 %which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  
-\acom{1.
+% \acom{1.
 No boldface on this new term.
@@
 Since we sometimes need $\Peff$ which contains $P_{++} = \Peff\cap\Pdom$, how about just using the notation $\Peff,\Pdom$ instead of $P_+, P_{++}$ for a change?}
-\jcom{I added the definition of effective coweight.
+% \jcom{I added the definition of effective coweight.
 I actually don't think that we need any special notation $ P, P_+, P_{dom}$ etc !
 Later we can just write ``$ \lambda \in \ZZ^m$ a dominant or effective coweight'' etc}
+% TODO: it's settled then, no special notation fro coweights!
 % 
@@
 %We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights. 
-
+% 
 % nicematrix test
@@
 %     \end{pNiceMatrix}$
-
+% 
 % Set $\AA = \AA^1_x$ (the subscript denoting the chosen local coordinate) and fix $s\in \AA - \{0\}$. 
+%
 
@@
 $(t-s)^\mu\in G(\CC[t])$ if and only if $ \mu = 0 $.
-
+% 
 \acom{maybe add that it's the same for $G(\cO)$.}
@@
 \acom{left or right, doesn't matter?
-I think we are in a situation where they are the same, but I need a reminder.} By restriction $ K^m$ can be viewed as an $R$-module.
+I think we are in a situation where they are the same, i.e.\ our rings are commutative.} By restriction $ K^m$ can be viewed as an $R$-module.
 An $R$-lattice in $K^m$ \acom{definiton, no boldface}
@@
 $$
-\acom{What is the modular description of the fibre?} \jcom{That is written above (just fix $ s$).}
+% \acom{What is the modular description of the fibre?} \jcom{That is written above (just fix $ s$).}
+% 
 % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
@@
     % $$ \Grbd \rightarrow \Grth $$ 
-    We define a map $ \Grbd \rightarrow \Grth $ by 
-    $$(V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty})$$
-
+    We define a map $ \Grbd \rightarrow \Grth $ by \acom{Don't we also want to restrict $V$}
+    $$
+    (V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty})\,.
+    $$
+    % 
     % It is given in modular terms by restricting the trivialization to $ D_\infty$. \acom{Does it mean $(V,\varphi,s)\mapsto (V\big|_{D_\infty},\varphi\big|_{D_\infty})$}
@@
     Note that if $ L = g \CC[t]^m$ for $ g \in G([t,t^{-1}, (t-s)^{-1}])$, then 
-    $$(L(0), L(s)) = (g \cO^m, g\cO^m_s)$$
-
+    $$
+        (L(0), L(s)) = (g \cO^m, g\cO^m_s)\,. 
+    $$
+    % 
     \jcom{I restated this again.  I think that it is simpler and more clear like this.  And I think that this is the fact that we end up using later.}
-
+    % 
+% 
 % in the $ s \ne 0 $ case.
@@
 %    and similarly for $ L(s)$.
-
+    % 
     In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
@@
 \end{proof}
-    \acom{why ``and so''? bc orbits are connected?}
-    \jcom{I turned this into a Lemma.}
+    % \acom{why ``and so''? bc orbits are connected?}
+    % \jcom{I turned this into a Lemma.}
 
@@
 \end{definition}  
-    % \acom{$s\in\AA$?}
-    % 
 A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
@@
 
-     Its closure is $ \overline{\OO}^{\lambda', \lambda''}_{0,s} = \bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.
+The closure $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ is $\bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.
 
@@
      and
-     \begin{equation} \label{eq:ranks}
-     \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i \le N - 
-     \#\text{~boxes in first $i$ columns of }\lambda' \quad
-     \rk (A-s)^i \le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
+     \begin{equation} 
+        \label{eq:ranks}
+        \begin{split}
+            % 
+         \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : &\rk A^i \le N - 
+         \#\text{~boxes in first $i$ columns of }\lambda' \\
+         &\rk (A-s)^i \le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
+        \end{split}
      \end{equation}
-
+%  
 \begin{proposition} \label{prop:adjoint}
@@
 \end{proposition}
-
-In order to prove this result, we will need to recall some results from Eisenbud-Saltman \cite{eisenbud1989rank}.
+% 
+In order to prove this result, we will need to recall some results from Eisenbud--Saltman \cite{eisenbud1989rank}.
+%
 
@@
 
-Let $ W$ be a subspace of $ \AA^k$.  Eisenbud-Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions.  We will now describe these fibres.
+Let $ W$ be a subspace of $ \AA^k$. Eisenbud \& Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions.  We will now describe these fibres.
 
@@
 
-\jcom{Eisenbud-Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
+\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
 
@@
 
-\subsection{The Mirkovic-Vybornov slice} Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
+\subsection{The Mirkovic--Vybornov slice} 
+% 
+Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
 \begin{definition}The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
@@
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
-$$ L \mapsto [t|_{\CC[t]^m/L} ]^{tr}_{\beta_\mu} \,. $$
+$$ L \mapsto [t|_{\CC[t]^m/L} ]^{\tr}_{\beta_\mu} \,. $$
 %\acom{Up to transpose?!}
@@
 In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
-\acom{Grammar of `write using the map' is iffy.
-Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}
+% \acom{Grammar of `write using the map' is iffy. Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}
 
@@
 $$
-for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\CC\xt[t^{-1}]) $.
+for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\Oinf) $. % was CC\xt[]
 Note that $ h^{-1}n h \in N(\Kinf)$, 

### 2021-04-12 draft.tex
minor issue with ES rewrite

@@
 and
-     \begin{equation} \label{eq:ranks}
-     \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i \le N - 
-     \#\text{~boxes in first $i$ columns of }\lambda' \quad
-     \rk (A-s)^i \le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
+\begin{equation} 
+\label{eq:ranks}
+\begin{split}
+    % 
+    \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : &\rk A^i \le N - 
+    \#\text{~boxes in first $i$ columns of }\lambda' \\
+    &\rk (A-s)^i \le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
+\end{split}
 \end{equation}
-
+%  
 \begin{proposition} \label{prop:adjoint}
@@
 \end{proposition}
-
-In order to prove this result, we will need to recall some results from Eisenbud-Saltman \cite{eisenbud1989rank}.
+% 
+In order to prove this result, we will need to recall some results from Eisenbud--Saltman \cite{eisenbud1989rank}.
+%
 
 Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
-\jcom{I don't know if it is really necessary to introduce this $ k$.  Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.}
-
-Let $ W$ be a subspace of $ \AA^k$.  Eisenbud-Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions.  We will now describe these fibres.
+\jcom{I don't know if it is really necessary to introduce this $ k$.
+Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$?
+Was $k = m$ replaced because $m$ is already used?}
+
+Let $ W$ be a subspace of $ \AA^k$. Eisenbud \& Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions. We will now describe these fibres.
 
 Let $ z \in \AA^k$.
-Some of the coordinates of $z$ are equal; we introduce some data to describe these equalities.
-There exist unique $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a minimal length permutation  $ p $ of $ \{1, \dots, k\}$ such that $$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)} $$
-
-\jcom{Eisenbud-Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
+Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities.
+There exist unique $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a minimal length permutation  $ p $ of $ \{1, \dots, k\}$ such that
+$$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,. $$
+
+\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
+
+\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
 
@@
 $$
-    r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
+    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
+    r_{z,j}(i):= N - r(p(k_j)) + r(p(k_j + i)) \, . 
 $$
 \jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
+
+% 
 By \cite[Corollary 2.2]{eisenbud1989rank}, the fibre of the flat family $ X_{r,W} $ over $ z$ is given by
@@
 Define 
-$$r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda$$
+$$r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,.$$
 It is easy to see that this is a rank function, with $ k = \lambda_1$, the number of columns of $ \lambda$.
@@
 
-For $ s \in \CC$, we define $ z(s) \in \CC^k$, with $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1 \dots + k$.
-
-For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduces the permutation $ p$, that $ r = 2 $, and that
-\begin{equation} \label{eq:rcols}
-r_{z(s), 1}(i) =  N - 
-     \#\text{~boxes in first $i$ columns of }\lambda'
-     \quad
-     r_{z(s), 2}(i) =  N - \#\text{~boxes in first $i$ columns of }\lambda'' 
+For $ s \in \CC$, we define $ z(s) \in \CC^k$, with $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1, \dots, k$.
+
+For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduce the permutation $ p$, that $ r = 2 $, and that
+\begin{equation} 
+    \label{eq:rcols}
+\begin{split}
+        r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
+        r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
+\end{split}
 \end{equation}
-On the other hand, for $z(0)$, we get $ r = 1$ and that 
+On the other hand, for $z(0)$, we get that $ r = 1$ and that 
 \begin{equation} \label{eq:rcol2}
 r_{z(0),1}(i) = r(i) = n -  N - 
-     \#\text{~boxes in first $i$ columns of }\lambda
+     \#\text{~boxes in first $i$ columns of }\lambda\,. 
 \end{equation}
@@
 
-Let $ W = \{ z(s) : s \in \CC \}$.
-Combining (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) we see that the Eisenbud-Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
+\acom{What do we mean by equalities in $z(s)$ reproduce $p$?
+I thought $z(s)$ was defined by $p$.
+Also, $r_{z(s),1}(i) = N- r(p(k_1)) + r(p(k_1 + i)) = N - (N-\#\text{boxes in first }p(k_1)\text{ cols} + \cdots)\ne $~\Cref{eq:rcols}.
+We want to apply $p$ to $\{1,\dots,i\}$ and not just $i$.
+I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$.}
+
+% 
+Let $ W = \{ z(s) : s \in \CC \}$.  Combining \Cref{eq:ranks,eq:ESfibre,eq:rcols,eq:rcol2} 
+% (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) 
+we see that the Eisenbud--Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
 \end{proof}
@@
 \jcom{I'm not a huge fan of this description, but I don't know how to write it better.}
+
+\acom{Agree. Happy to just have the in-words description.}
 
@@
         \end{BMAT}
-        \right]
+        \right]\,. 
     \]
@@
     $$
-    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
+    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
     $$
@@
 This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).
-\acom{is this map $v + L \mapsto v + L(0)$?} \jcom{yes} \marginpar[]{*}
+    % \acom{is this map $v + L \mapsto v + L(0)$?} \jcom{yes} \marginpar[]{*}
     % todo
@@
     Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.
-\rcom{Preimage of $\beta_\mu$}  This follows immediately from (iii).
+
+    \rcom{Preimage of $\beta_\mu$}
+
+    This follows immediately from (iii).
     % 
@@
     % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
-    $h^{-1} g h \in N(\cK_\infty)$ and so we can factor $ h^{-1} g h = n_1 n_2$ for $ n_1 \in N_1(\CC\xt[t^{-1}]), n_2 \in N(\CC[t]) $.
-Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N(\CC[t]) $ \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?}.
-Thus, $ L = h n_1 t^\mu \CC[t]^m$.
-Since $ hn_1 \in G_1(\CC\xt[t^{-1}])$, the result follows.
+    $h^{-1} g h \in N(\cK_\infty)$ and so we can factor $ h^{-1} g h = n_1 n_2$ for $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t]) $.
+Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N(\CC[t]) $.
+% \CC\xt[t^{-1}]s
+
+    \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?}
+
+    \acom{Si}
+
+    Thus, $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
     \end{proof}
@@
 This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective. 
-
+% Joel: The only non-injectivity comes from the fact that we forget the data
+% of s.  So the map is non-injective over the locus where s is not
+% actually an eigenvalue (in lattice terms where L(s) is the standard
+% lattice).
 In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
-\acom{Grammar of `write using the map' is iffy.
-Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}
+% \acom{Grammar of `write using the map' is iffy. Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}
 
@@
 \begin{proof}
-Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, $$ (A,s) \in \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu $$
+Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, 
+$$ 
+(A,s) \in \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \text{ if and only if } (g(A)\CC[t]^m, s) \in \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu \,. 
+$$
 This follows immediately from Lemma \ref{le:Grl1l2}.
 \end{proof}
-
+% 
 \begin{theorem}
     The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
-    $$ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \UU^{\mu', \mu''}_{0,\AA} \cong \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} \cap S^{\mu', \mu''}_{0,\AA}$$
+    $$ 
+    \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \UU^{\mu', \mu''}_{0,\AA} \cong \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} \cap S^{\mu', \mu''}_{0,\AA}\,.
+    $$
 \end{theorem}
@@
 
+\acom{$g(A)$ is lower-triangular}
+
 On the other hand, if $ (g(A), s) \in S^{\mu', \mu''}_{0,\AA}$, then we can write 
@@
 
-Moreover since $ \mu $ is dominant, we know that 
+Moreover, since $ \mu $ is dominant, we know that 
 $$t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.$$
@@
 % $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
-and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''} N_1(\Oinf) $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA}$ as desired.
+and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''} N_1(\Oinf) $.  
+% Given that we know that 
+Since $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA}$ as desired.
 \end{proof}
 
-%\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
+\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
 To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.
 In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
+
+\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
 

### 2021-04-12 draft.tex
Updates from Overleaf

@@
 
+\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$.
+When we multiply by $t^{-\mu}$, we scale the $i$th column by $t^{-\mu_i}$.
+So the diagonal entries are $1 + p$ where $p \in t^{-1}\CC[t^{-1}]$ while the off-diagonal entries in column $i$ have highest (in $t$) degree $\min(\mu_i-1, \mu_j-1) - \mu_i < 0$.
+Hence $g \in G_1(\cO_\infty)$.}
+
 \section{Falling Action} % Resolution

### 2021-04-12 draft.tex
Corrected typo in g(A) example.
fixed typo and completed check of eqs 3

@@
 \begin{equation} \label{eq:rcol2}
-r_{z(0),1}(i) = r(i) = n -  N - 
+r_{z(0),1}(i) = r(i) = 
+ N - 
      \#\text{~boxes in first $i$ columns of }\lambda\,. 
@@
 We want to apply $p$ to $\{1,\dots,i\}$ and not just $i$.
-I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$.}
+I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$.
+For a minute I thought it was actually fine, but what we have is: $r_{z(s),j}(i) = N - (\#\text{boxes in cols }1,\dots,p(k_j + i) - \#\text{boxes in cols }1,\dots,p(k_j))$ and what we want is $\dots (\#\text{boxes in cols }p(1),\dots,p(k_j + i) - \#\text{boxes in cols }p(1),\dots,p(k_j + i))$ right?}
 
@@
             \left[\begin{array}{rr}
-                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
+                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
                 -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1

### 2021-04-12 draft.tex
added min weights and tableaux

@@
     So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
-
-    Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.
     For example, elements of $ \UU_{0,s}^{(1,1,0),(2,1,1)}$ look like 
@@
     \]
+    % 
+    Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.
+
+    \acom{Mention that any other decomposition $\nu' + \nu''$ of $\mu' + \mu''$ will give a slice $\UU^{\nu',\nu''}_{0,\AA}$ with the same zero fibre.}
 
@@
 Computing fusion still hard but at least boiled down to linear algebra.
-Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,Mirkovi\'c2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
+Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
 
@@
 \label{s:denouement}
-
-As an application we can compute fusion of stable MV cycles of type $\alpha_i$ for any $i \in I$. What about more general weights? Having $\kpf > 1$. Well yeah.
-
-\begin{proposition}(\cite{baumann2019Mirkovi\'c})
+% 
+In this section we demonstrate how to put the main results of this paper into practice.
+% 
+Given $\lambda$ dominant effective and $\mu\le\lambda$ effective, let $YT(\lambda)_\mu$ denote the set of semistandard Young tableaux of shape $\lambda$ and weight $\mu$. 
+%
+
+We need the following result from \cite{dthesis}.
+\begin{proposition}
+    Generalized orbital varieties are indexed by semistandard Young tableaux. Composing with the ordinary Mirkovi\'c--Vybornov isomorphism gives bijections 
+    \[
+        YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \irr \overline\Gr^\lambda\cap S^\mu_-\,. 
+    \]
+    % $$
+    % \begin{tikzcd}
+    %     YT(\lambda)_\mu \ar[r] \ar[d] & \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \ar[d] \\
+    %     GT(\lambda)_\mu \ar[r] & \irr \overline\Gr^\lambda\cap S^\mu_-
+    % \end{tikzcd}
+    % $$
+\end{proposition}
+% 
+Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. 
+% 
+\begin{proposition}(\cite{baumann2019mirkovic})
     % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
-    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''\in P_{++}$ and weight $\mu',\mu''\in P$ resp.\ such that $\mu = \mu' + \mu'' \in P_{++}$. Then 
+    Let $Z',Z''$  be MV cycles of coweight $(\lambda',\mu'),(\lambda'',\mu'')$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
+    Then 
     \begin{equation}
+        \label{eq:tabmult}
         % Z_\tau\ast Z_\sigma 
@@
         i\left(
-            Z_\tau, Z'\circ Z''
+            Z(\tau), Z'\circ Z''
             % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
-        \right) [Z_\tau]
+        \right) [Z(\tau)]
     \end{equation}
-    and the intersection multiplicities on the right are found by the algorithm described in APX.
-    In particular, 
-    the multiplicity of $Z_\tau$
+    and the intersection multiplicities on the right are found by the algorithm described in \Cref{ss:algo}.
+
+    \acom{Add pseudocode}
+
+    In particular, the multiplicity of $Z(\tau)$
     % in the product of the zero fiber 
@@
     % closure of the family $Z_1 \times Z_2 \times U$ 
-    is equal to the multiplicity of its generalized orbital variety $X_\tau$ among the set 
-    \begin{equation}\label{eq:tabmult}
-        \irr\lim_{s\to 0} \overline{\OO}^{\lambda',\lambda''}_{0,s}\cap\UU^{\mu',\mu''}_{0,s} \,. 
+    is equal to the multiplicity of its generalized orbital variety $X(\tau)$ 
+    in $ \overline{\OO}^{\lambda',\lambda''}_{0,0}\cap\UU^{\mu',\mu''}_{0,0} $. 
+    % among the set 
+    % \begin{equation}\label{eq:tabmult}
+        % \irr\lim_{s\to 0} 
+        % \overline{\OO}^{\lambda',\lambda''}_{0,0}\cap\UU^{\mu',\mu''}_{0,0} \,. 
         % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu',\mu''}^{+,s}
-    \end{equation}
+    % \end{equation}
+
     Since stable MV cycles can be represented by ordinary ones the multiplicities in 
@@
     $$
-    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$.
+    can also be deduced from \Cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$. These are described in \Cref{lem:mintab,prop:minwts} below.
 \end{proposition}
-\acom{or Corollary?}
-
+% 
 \begin{conjecture}
@@
 \end{conjecture}
+%
+
+\begin{lemma}
+    \label{lem:mintab}
+    Let $n_\bullet$ be a Lusztig datum of coweight $\nu$.
+There exist $\lambda,\mu$ smallest such that $n_\bullet$ is the Lusztig datum of a tableau $\tau\in YT(\lambda)_\mu$.
+They are determined by the following minimization problem.
+Regard $n_\bullet$ as a strictly lower triangular matrix with $(r,c)$th entry $n_{r,c}$ is equal to the number of boxes of weight $r$ in row $c$ of $\tau$.
+Note that since $r > c$ this data does not account for the number of boxes of weight $r$ in row $r$.
+Let $\mu^0$ be the diagonal matrix whose $(r,r)$th entry $\mu^0_r$ is equal to the number of boxes of weight $r$ in row $r$ of $\tau$.
+Note that the sum of the rows of $n_\bullet + \mu^0$ is the shape $\lambda$ of $\tau$, and the sum of the columns of $n_\bullet + \mu^0$ is the weight $\mu$ of $\tau$.
+The solution to the minimization problem
+    \[
+        \begin{gathered}
+        % 
+        \text{minimize }\mu^0\text{ such that} \\
+        % \text{the sum of the rows of }n_\bullet + \mu^0\text{ is non-increasing},
+        % \text{the sum of the columns of }n_\bullet + \mu^0\text{ is non-increasing}
+        \text{both }\lambda,\mu\text{ are non-increasing}
+        \end{gathered} 
+    \]
+    is got recursively from % setting $\mu^0_m = 0$, 
+    \[
+        \begin{gathered}
+            \mu^0_{m} = 0 \\ 
+            \mu^0_{m-1} = \max\{0 , \sum n_{m,c} - \sum n_{m-1,c}\} \\ 
+            \mu^0_i = \max\{0, \mu^0_{i+1} + \sum n_{i+1,c} - \sum n_{i,c} , \mu_{i+1}^0 + \sum n_{r,i+1} - \sum n_{r,i}\}
+        \end{gathered}
+    \]
+    for $i = 1,\dots,m-2$. 
+    In words, given a Luszig datum $n_\bullet$, if we wish to produce a minimal SSYT for it, 
+    \begin{itemize}
+        \item we can always take the number of $m$'s in row $m$ to be zero; 
+        \item we can take the number of $m-1$'s in row $m-1$ to be zero, unless $n_\bullet$ tells us that there are more $m$'s the first $m-1$ rows than there are $m-1$'s in the first $m-2$ rows, and in that case we take $\mu^0_{m-1}$ so that it exactly offsets the difference;
+        \item we can take the number of $m-2$'s in row $m-2$ to be zero, unless $n_\bullet$ tells us there are more $m-1$'s in the first $m-1$ rows (building off the last step) than there are $m-2$'s in the first $m-3$ rows, or, that there are more boxes in row $m-1$ than there are in row $m-2$, and then we take $\mu^0_{m-2}$ to offset the minimum of the two differences;
+        \item induct up to $\mu^0_1$. 
+    \end{itemize}
+\end{lemma}
 
 \begin{proposition}
-    Given Lusztig data $n_\bullet',n_\bullet''\in\NN^\ell$ the smallest choice of $\mu',\mu''\in P$ and $\lambda',\lambda''\in P_{++}$ such that $\mu = \mu' + \mu''\in P_{++}$ and $\tau'\in S(\lambda')_{\mu'}$, $\tau''\in S(\lambda'')_{\mu''}$ are SSYT with the prescribed Lusztig data, are\dots
+    \label{prop:minwts}
+    Given two Lusztig data $n_\bullet',n_\bullet''$ there is a smallest choice of effective coweights $\mu',\mu''$ and effective dominant coweights $\lambda',\lambda''$ such that $\mu = \mu' + \mu''$ is effective dominant and $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ are semistandard Young tableaux with the prescribed Lusztig data.
+They are got by choosing the minimum $\lambda,\mu$ for $n_\bullet = n_\bullet ' + n_\bullet ''$ afforded by \Cref{lem:mintab}, and then breaking off $n_{r,c}'$ boxes of weight $r$ from each row $c<r$ of $\tau$ to form a $\tau'_0$ an intermediate tableau.
+If $\tau'_0$ is of an acceptable shape then we keep it.
+If it is not, then we correct it by padding it using some boxes of weight $r$ in row $r$ of what remains of $\tau$.
+
+    \acom{To be completed.}
 \end{proposition}
-\begin{proof}
-    [Sketch.]
-    The last row of the GT pattern of $\tau'$ (resp.\ $\tau''$) is $\lambda'$ (resp.\ $\lambda''$). 
-    Guess: the smallest choices will be the appropriate pieces of the smallest choices for $\lambda$, $\mu$, and $n_\bullet = n_\bullet' + n_\bullet''$.
-E.g.\ take $n_\bullet' = (2,0,0), n_\bullet'' = (0,0,2)$ so $n_\bullet = (2,0,2)$.
-Then $\lambda - \mu = 2\alpha_1 + 2\alpha_2$ %or $(\lambda_1 - \mu_1,\lambda_2 - \mu_2, \lambda_3 - \mu_3) = (2,0,2)$
-    \begin{gather}
-        (\lambda_1 - \mu_1,\lambda_2 - \mu_2, \lambda_3 - \mu_3) = (2,0,-2)
-        \\
-        % (\lambda_1(2) - \mu_1(2),\lambda_2(2) - \mu_2(2), \lambda_3(2) - \mu_3(2)) &= (2,0,2) \\
-        % (\lambda_1(1) - \mu_1(1),\lambda_2(1) - \mu_2(1), \lambda_3(1) - \mu_3(1)) &= (2,0,2)
-        \begin{matrix}
-            & & \lambda_1(1) \\
-            & \lambda_1 (2) = \lambda_1(1) + 2 & & \lambda_2(2) \\
-            \lambda_1 = \lambda_1(2) + 0  & & \lambda_2 = \lambda_2(2) + 2 & & \lambda_3 
-        \end{matrix}\\
-        \Rightarrow \mu_3 \ge 2, \mu_2 \ge 2, \mu_1 \ge 2 \\
-        \Rightarrow \lambda_3 \ge 0, \lambda_2 \ge 2, \lambda_1 \ge 4 \\
-        \Rightarrow \lambda_2(2) = \lambda_2 - 2 \ge 0 , \lambda_1(2) = \lambda_1 \ge 4 \\ 
-        \Rightarrow \lambda_1(1) = \lambda_1(2) - 2 \ge 2 \\ 
-        \young(1122,33)
-        % \Leftrightarrow 
-        % \begin{matrix}
-        %     & & \lambda_1(1) \\
-        %     & \lambda_1 (2) = \lambda_1(1) + 2 & & \lambda_2(2) \\
-        %     \lambda_1 = \lambda_1(2) + 0  & & \lambda_2 = \lambda_2(2) + 2 & & 0 
-        % \end{matrix}
-    \end{gather} 
-    Since the tableau formed by taking the smallest possible choices for each of the inequalities is semi-standard we're good.
-
-    In general we have $\mu_i\ge\sum_k n_{i,k}$ where $n_{i,k} = \lambda_k(i) - \lambda_{k}(i-1)$ and then $\lambda_i \ge \nu_i + \mu_i$ where $\nu = \wt(n_\bullet)$.
-The rest of the lower bounds are determined recursively by the relation $\lambda_k(i-1) =  \lambda_k(i) - n_{i,k}$.
-Choose the minimum values satisfying the bounds until $\lambda_k(i) < \lambda_{k+1}(i)$ for some $k,i$.
-If this should happen go back to the start and increment all/some of the initial $\lambda_k$ by an appropriate amount.
-\end{proof}
-
-% TODO: un-appendicize 
-% \appendix
-
-\subsection{Generalized orbital varieties?}
-TODO: recall $\tau\mapsto X_\tau \mapsto Z_\tau$
 
 \subsection{Pseudocode}
-
-\begin{question}
-    Smallest $\mu_1, \mu_2$ such that\dots?
-\end{question}
+%
 
 \subsection{Tableaux and families}
-
-TODO: $Z_1\ast_\AA Z_2$ is described by $\tau_1\ast\tau_2$ or $\tau_1\sqcup\tau_2$
+% 
+TODO: resume here
+
+$Z'\ast_\AA Z''$ is described by $\tau'\ast\tau''$
 

### 2021-04-12 draft.tex
joel fixed es section

--- 2021-04-12 draft.tex
@@
 Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$?
-Was $k = m$ replaced because $m$ is already used?}
+Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes}
 
@@
 Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities.
-There exist unique $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a minimal length permutation  $ p $ of $ \{1, \dots, k\}$ such that
-$$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,. $$
+There exist $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
+$$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,.
+$$ We require that $ p $ is of minimal length, given the choice of $ s_1, \dots, s_r$.
+The data $s_\bullet, p, k_\bullet$ is unique up to a permutation of $ \{1, \dots, k\}$.
 
@@
 \acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
+\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}
 
@@
     % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
-    r_{z,j}(i):= N - r(p(k_j)) + r(p(k_j + i)) \, . 
+    r_{z,j}(i):= N + \sum_{a = 1}^i r(p(k_j + a)) - r(p(k_j +a) - 1)  \, . 
 $$
 \jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
+\jcom{I fixed it now.  I didn't want to use ES's $a_i$.}
 
@@
 
-For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduce the permutation $ p$, that $ r = 2 $, and that
+For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of $ r = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.  We also see that
 \begin{equation} 
@@
 For a minute I thought it was actually fine, but what we have is: $r_{z(s),j}(i) = N - (\#\text{boxes in cols }1,\dots,p(k_j + i) - \#\text{boxes in cols }1,\dots,p(k_j))$ and what we want is $\dots (\#\text{boxes in cols }p(1),\dots,p(k_j + i) - \#\text{boxes in cols }p(1),\dots,p(k_j + i))$ right?}
+
+\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.
+I changed the wording of ``reproduce''.
+I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}
 

### 2021-04-13 draft.tex
Notation for examples.

@@
 We view MV cycles as semi-standard young tableaux.
-Suppose we have two tableaux $\tau_1$ and $\tau_2$ with respective weights $\lambda_i$ and $\mu_i$ and we wished to take their fusion product.
-We consider a generic matrix $X \in \UU^{\mu_1,\mu_2}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda_1,\lambda_2}_{0,s}$.
-
-Consider the subtableaux $\tau_{1,i}$ of $\tau_1$ and $\tau_{2,i}$ of $\tau_2$ where we take the boxes of $\tau_1$ and $\tau_2$ containing the numbers $1,\dots,i$.
-Let $\lambda_{1,j}$ and $\lambda_{2,j}$ be the corresponding sizes and $\mu_{1,j}$ and $\mu_{2,j}$ be the corresponding weights of the subtableaux.
-For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu_{1,i}, \mu_{2,i}}_{0,s}$ of $X$.
-These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda_{1,i}, \lambda_{2,i}}_{0,s}$, which allows us to deduce relations on the variables in $X$.
+Suppose we have two tableaux $\tau'$ and $\tau''$, with respective weights $\lambda'$, $\mu'$ and $\lambda''$, $\mu''$, and we wished to take their fusion product.
+We consider a generic matrix $X \in \UU^{\mu',\mu''}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda',\lambda''}_{0,s}$.
+
+Consider the subtableaux $\tau'_{i}$ of $\tau'$ and $\tau''_{i}$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$.
+Let $\lambda'_{j}$ and $\lambda''_{j}$ be the corresponding sizes and $\mu'_{j}$ and $\mu'_{j}$ be the corresponding weights of the subtableaux.
+For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu'_{i}, \mu''_{i}}_{0,s}$ of $X$.
+These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda'_{i}, \lambda''_{i}}_{0,s}$, which allows us to deduce relations on the variables in $X$.
 The relations must also include the new variables in the latest block and cannot have $s$ as a factor.
@@
 Let $G = \GL_3$ and consider the tableaux
-$$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$
-
-Lusztig data: $(010)$ for $\tau_1$, $(101)$ for $\tau_2$
+$$\tau' = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau''=\young(13,2).$$
+
+Lusztig data: $(010)$ for $\tau'$, $(101)$ for $\tau''$
 
@@
 
-The MV cycles corresponding to $\tau_1$ and $\tau_2$ are both isomorphic to $\PP^2$.
-The weights are $\lambda_1 = \lambda_2 = (2,1,0)$ and $\mu_1 = \mu_2 = (1,1,1)$. Hence the matrix in consideration is 
+The MV cycles corresponding to $\tau'$ and $\tau''$ are both isomorphic to $\PP^2$.
+The weights are $\lambda' = \lambda'' = (2,1,0)$ and $\mu' = \mu'' = (1,1,1)$. Hence the matrix in consideration is 
 \[
@@
     0 & 1 & & & & \\
-     & s & a_1 & a_2 & b_1 & b_2 \\
+     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
      & & 0 & 1 & & \\
-     & & & s & b_3 & b_4 \\
+     & & & s & A_{23}^1 & A_{23}^2 \\
      & & & & 0 & 1 \\
@@
 
-For the first entry of each $\mu_i$, we have the following subtableaux to consider:
+For the first entry of $\mu'$ and $\mu''$, we have the following subtableaux to consider:
 $$\young(1) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1).$$
@@
 
-For the first two entries of each $\mu_i$, we have the following subtableaux:
+For the first two entries of $\mu'$ and $\mu''$, we have the following subtableaux:
 $$\young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1,2).$$
@@
 The left subtableau imposes the conditions $\dim \ker X_2 = 1$ and $\dim \ker X_2^2 = 2$ while the right subtableau imposes the condition that $\dim \ker (X_2 -s) = 2$.
-These conditions force the relation $$a_1 + sa_2 = 0.$$
-
-The original tableaux for $X$ imposes the conditions that $\dim \ker X = 2$, $\dim \ker X^2 = 3$, $\dim \ker (X-s) = 2$, and $\dim \ker (X-s)^2 = 3$. These force the relation $$b_3 = 0.$$
+These conditions force the relation $$A_{12}^1 + sA_{12}^2 = 0.$$
+
+The original tableaux for $X$ imposes the conditions that $\dim \ker X = 2$, $\dim \ker X^2 = 3$, $\dim \ker (X-s) = 2$, and $\dim \ker (X-s)^2 = 3$. These force the relation $$A_{23}^1 = 0.$$
 
 Hence we consider the quotient
-$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,s]}{\langle a_1+sa_2,b_3,s \rangle} \cong
-\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4]}{\langle a_1,b_3 \rangle}.$$
-We see already that the $0$-fibre is irreducible. The tableau corresponding to the ideal $\langle a_1, b_3 \rangle$ is 
+$$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2,s]}{\langle A_{12}^1+sA_{12}^2,A_{23}^1,s \rangle} \cong
+\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2]}{\langle A_{12}^1,A_{23}^1 \rangle}.$$
+We see already that the $0$-fibre is irreducible. The tableau corresponding to the ideal $\langle A_{12}^1,A_{23}^1 \rangle$ is 
 $$\young(1123,23)$$
-which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau_1$ and $\tau_2$.
+which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau'$ and $\tau''$.
 
@@
 Let $G = SL_3$ and consider the tableaux
-$$\tau_1 = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(11,23).$$
-
-Lustig data: $(100)$ for $\tau_1$, $(001)$ for $\tau_2$.
-
-Dimensions: $(1,-1,0)$ for $\tau_1$, $(0,1,-1)$ for $\tau_2$.
+$$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$
+
+Lustig data: $(100)$ for $\tau'$, $(001)$ for $\tau''$.
+
+Dimensions: $(1,-1,0)$ for $\tau'$, $(0,1,-1)$ for $\tau''$.
 
 The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.
-We have the weights to be $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (1,1,0)$, and $\mu_2 = (2,1,1)$. The matrix under consideration is therefore
+We have the weights to be $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (1,1,0)$, and $\mu'' = (2,1,1)$. The matrix under consideration is therefore
 \[
@@
      & 0 & 1 & & & \\
-     & -s^2 & 2s & a_1 & a_2 & b_1 \\
+     & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
      & & & 0 & 1 & \\
-     & & & & s & b_2 \\
+     & & & & s & A_{23}^1 \\
      & & & & & s
@@
 \]
-There are no relations from looking at the submatrix $X_1$. From the submatrix $X_2$, we require $$a_1 + sa_2 = 0.$$
-From $X$, we further obtain the relations $$a_2b_2 + sb_1 = 0, a_1b_2 + s^2b_1 = 0.$$
+There are no relations from looking at the submatrix $X_1$. From the submatrix $X_2$, we require $$A_{12}^1 + sA_{12}^2 = 0.$$
+From $X$, we further obtain the relations $$A_{12}^2A_{23}^1 + sA_{13}^1 = 0, A_{12}^1A_{23}^1 + s^2A_{13}^1 = 0.$$
 Then the quotient ring we find is
-$$\frac{\CC[a_1,a_2,b_1,b_2,s]}{\langle a_1+sa_2, a_2b_2+sb_1, a_1b_2+s^2b_1, s\rangle} \cong \frac{\CC[a_1,a_2,b_1,b_3,s]}{\langle a_1, a_2\rangle \cap \langle a_1, b_2 \rangle}.$$
+$$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s]}{\langle A_{12}^1+sA_{12}^2, A_{12}^2A_{23}^1+sA_{13}^1, A_{12}^1A_{23}^1+s^2A_{13}^1, s\rangle} \cong \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,b_3,s]}{\langle A_{12}^1, A_{12}^2\rangle \cap \langle A_{12}^1, A_{23}^1 \rangle}.$$
 We see that the 0-fibre is reducible with two components. The tableau corresponding to each ideal is
 $$\begin{array}{cccc} \vspace{1mm}
-    \young(1113,22) & \text{for } \langle a_1, a_2 \rangle & \text{Lusztig: }(101) & \dim = (1,0,-1)\\ 
-    \young(1112,23) & \text{for } \langle a_1, b_2 \rangle & \text{Lusztig: }(010) & \dim = (1,0,-1).
+    \young(1113,22) & \text{for } \langle A_{12}^1, A_{12}^2 \rangle & \text{Lusztig: }(101) & \dim = (1,0,-1)\\ 
+    \young(1112,23) & \text{for } \langle A_{12}^1, A_{23}^1 \rangle & \text{Lusztig: }(010) & \dim = (1,0,-1).
 \end{array}$$
@@
 Let $G = SL_3$ and consider the following tableaux:
-$$\tau_1 = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(1111,2233).$$
-
-Lusztig data: $(200)$ for $\tau_1$, $(002)$ for $\tau_2$.
-
-Dimensions: $(2,-2,0)$ for $\tau_1$, $(0,2,-2)$ for $\tau_2$.
+$$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$
+
+Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.
+
+Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.
 
 The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
-The weights are then $\lambda_1 = (4,0,0)$, $\lambda_2 = (4,4,0)$, $\mu_1 = (2,2,0)$, and $\mu_2 = (4,2,2)$.
+The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
 Then we are considering the following matrix:
@@
      & & & & 0 & 1 & & & & & & \\
-     & & -s^4 & 3s^3 & -6s^2 & 4s & a_1 & a_2 & a_3 & a_4 & b_1 & b_2 \\
+     & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
      & & & & & & 0 & 1 & & & & \\
@@
      & & & & & & & & 0 & 1 & & \\
-     & & & & & & & & -s^2 & 2s & b_3 & b_4 \\
+     & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
      & & & & & & & & & & 0 & 1 \\
@@
 \begin{array}{cl}
-    I_1 = & \langle a_1, a_2, a_3, a_4, s \rangle \\
-    I_2 = & \langle a_1, a_2, b_3, b_4, s \rangle \\
-    I_3 = & \langle a_1, a_2, b_3^2, a_4b_3 + a_3b_4, a_3b_3, a_3^2, s \rangle.
+    I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
+    I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
+    I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
 \end{array}
@@
 \begin{example}
-Let us redo example 3 but with non-dominant weights $\mu_i$ such that $\mu_1 + \mu_2$ is still dominant. Then consider the tableaux
-$$\tau_1 = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2 = \young(11,33).$$
-Then the weights are $\lambda_1 = (2,0,0)$, $\lambda_2 = (2,2,0)$, $\mu_1 = (0,2,0)$, and $\mu_2 = (2,0,2)$. Our matrix $X$ is now
+Let us redo example 3 but with non-dominant weights $\mu'$ and $\mu''$ such that $\mu' + \mu''$ is effective dominant. Consider the tableaux
+$$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
+Then the weights are $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (0,2,0)$, and $\mu'' = (2,0,2)$. Our matrix $X$ is now
 \[
@@
     0 & 1 & & & & \\
-    -s^2 & 2s & a_1 & a_2 & b_1 & b_2 \\
+    -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
      & & 0 & 1 & & \\
-     & & & 0 & b_3 & b_4 \\
+     & & & 0 & A_{23}^1 & A_{23}^2 \\
      & & & & 0 & 1 \\
@@
 \begin{array}{cl}
-    I_1 = & \langle a_1, a_2 \rangle \\
-    I_2 = & \langle b_3, b_4 \rangle \\
-    I_3 = & \langle b_3^2, a_2b_3 + a_1b_4, a_1b_3, a_1^2 \rangle. 
+    I_1 = & \langle A_{12}^1, A_{12}^2 \rangle \\
+    I_2 = & \langle A_{23}^1, A_{23}^2 \rangle \\
+    I_3 = & \langle (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2 \rangle. 
 \end{array}

### 2021-04-14 draft.tex
mtg edits possibly compounded with other earlier edits

@@
 % section ??.  
-Since $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)t^\mu$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
+Since $ g(A) \in M_m(\CC[t]) \cap G_1(\Oinf)t^\mu$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
 (Alternatively, we can see that $ g(A) \CC[t]^m$ satisfies the condition (ii) from Lemma \ref{le:Wmu}.)
@@
 
-On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is upper triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.
-
-\acom{$g(A)$ is lower-triangular}
+On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.
 
@@
 % 
-TODO: resume here
-
-$Z'\ast_\AA Z''$ is described by $\tau'\ast\tau''$
-
-\begin{question}
-    How do we know that our algorithm produces MV cycles? 
-\end{question}
+Recall that there is an order on repeated entries of a semistandard Young tableau. 
+% 
+In this section we explain how to determine the ideal of $Z'\ast_\AA Z''$ from the minimal pair $(\tau',\tau'')$ corresponding to $(n_\bullet(Z'),n_\bullet(Z''))$.
+% 
+In particular, we prove that ``the generalized Spaltenstein map'' produces MV cycles.
+
+Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as above, and recall the $\mu$-numeration of the standard basis of $\CC^N$.
+Given $A \in M_N(\CC)$ we'll denote by $A\big|_{\CC^i}$ the restriction of $A$ to the subspace spanned by the first $i$ standard basis vectors.
+Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ the shape of $\tau'(i),\tau''(i)$ resp.\ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all but its first $i$ boxes.
+
+\acom{May want a more compact notation such as $A_{k}$}
 
 \begin{proposition}
-    Let $\tau_1,\tau_2$\dots 
-    \[
-    \{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\mu^1 + \cdots + \mu^i} \in \OO_{0,s}^{\lambda_{1}^{(i)},\lambda_2^{(i)}} \text{ all } i\} = Z_{\tau_1}\times Z_{\tau_2}
+    Given $Z',Z''$, let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ be such that\dots If $s\ne 0$, then 
+    \[
+    \overline{\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{\mu_1 + \cdots + \mu_i}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,m\}} 
+    \cong Z'\times Z'' \,. 
+    % = Z(\tau')\times Z(\tau'')\,. 
     \]
@@
 \begin{proof}
-    Want $L(0) \in Z(\tau_1)$ and $L(s) = Z(\tau_2)$. \acom{Another notational possibility is $\mu = \mu^0 + \mu^s$ etc., or $\mu(0) + \mu(s)$ or some variant with the eigenvalues being the indices.}
-
-    Fix $i \in \{1,\dots,m\}$ and let $p = \mu^1 + \cdots + \mu^i$. 
-    % Define $\lambda^{(i)}(\tau_1 \circ \tau_2)$ so that the 
-    Jordan type of $t\big|_{\CC[t]^p/L(0)\cap\CC[t]^p}$ is $\lambda_1^{(i)}$ and Jordan type of $t-s\big|_{\CC[t]^p/L(s)\cap \CC[t]^p}$ is $\lambda_2^{(i)}$.
+    % \acom{Another notational possibility is $\mu = \mu^0 + \mu^s$ etc., or $\mu(0) + \mu(s)$ or some variant with the eigenvalues being the indices.}
+    % 
+    First, reformulate as 
+    \[
+    \begin{tikzcd}
+        & (L,s) \in \Grbd \ar[dr,mapsto]\ar[dl,mapsto]\\
+        t\big|_{\CC[t]^m/L} \in A & & (L(0),L(s)) \in B 
+    \end{tikzcd}
+    \]
+    Fix $i \in \{1,\dots,m\}$, let $p = \mu_1 + \cdots + \mu_i$ and consider $(L',L'')\in Z'\times Z''$. 
+    We need to show that the Jordan type of $t\big|_{\CC[t]^p/L(0)\cap\CC[t]^p}$ is $\lambda'{(p)}$ and Jordan type of $(t-s)\big|_{\CC[t]^p/L(s)\cap \CC[t]^p}$ is $\lambda''{(p)}$.
 

### 2021-04-14 draft.tex
minimizing examples

@@
 
+\acom{If we start with $n_\bullet ' = (0,1,0)$ and $n_\bullet'' = (1,0,1)$ then the smallest $\tau$ for $n_\bullet = (1,1,1)$ is $\young(1123,23)$ and hence the smallest $\mu,\lambda$ are $(2,2,2),(4,2,0)$.
+So far so good.
+However, the ``smallest'' ``fission'' of $\tau$ is $\young(112,23) , \young(3)$.
+We could define ``smallest'' to mean minimizing the dimension of the generalized $s$-eigenspace.
+What do you guys think?
+If we agree to do this we should amend this example.
+For Joel: this is an example where our $B(\infty) \to B(\lambda)$ does not match that of Claxton--Tingley (quoted in my thesis).
+They would get $\lambda = (3,1)$.
+I think that their map satisfies $\lambda$ dominant and $\mu$ such that each $\mu_i\ge 1$.}
+
 Dimensions: $(1,0,-1)$ for both.
@@
 \begin{example}
-Let $G = SL_3$ and consider the tableaux
+Let $G = \GL_3$ and consider the tableaux
 $$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$
@@
 Lustig data: $(100)$ for $\tau'$, $(001)$ for $\tau''$.
+
+\acom{This time the smallest $\tau$ is actually $\young(12,3)$ and the smallest fission is $\young(1,3),\young(2)$. For Joel: this time the our $\lambda$ matches \cite{claxton2015young}'s.}
 
@@
 
+\begin{comment}
 \begin{example}
@@
 \end{example}
+\end{comment}
 
 \begin{example}
+
+    \acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{mirkovic2007quiver}.}
+
 Let us redo example 3 but with non-dominant weights $\mu'$ and $\mu''$ such that $\mu' + \mu''$ is effective dominant. Consider the tableaux

### 2021-04-14 draft.tex
Updates from Overleaf

--- 2021-04-14 draft.tex
@@
 \subsection{Examples}
-\rcom{I have 3 examples in mind right now: fusion product producing 1 term (maybe $1 \leftarrow 2 * 1 \rightarrow 2$), fusion product producing more than 1 term $(S_1 * S_2)$, and fusion product with multiplicities $((S_1 * S_2)^2)$}
-
-\acom{Plus fusion product of fake MV cycles for a fourth!}
+
+% \acom{Plus fusion product of fake MV cycles for a fourth!}
 
@@
 
-Consider the subtableaux $\tau'_{i}$ of $\tau'$ and $\tau''_{i}$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$.
-Let $\lambda'_{j}$ and $\lambda''_{j}$ be the corresponding sizes and $\mu'_{j}$ and $\mu'_{j}$ be the corresponding weights of the subtableaux.
-For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu'_{i}, \mu''_{i}}_{0,s}$ of $X$.
-These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda'_{i}, \lambda''_{i}}_{0,s}$, which allows us to deduce relations on the variables in $X$.
+Consider the subtableaux $\tau'(i)$ of $\tau'$ and $\tau''(i)$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$.
+Let $\lambda'(j)$ and $\lambda''(j)$ be the corresponding sizes and $\mu'(j)$ and $\mu'(j)$ be the corresponding weights of the subtableaux.
+For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu'(i), \mu''(i)}_{0,s}$ of $X$.
+These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda'(i), \lambda''(i)}_{0,s}$, which allows us to deduce relations on the variables in $X$.
 The relations must also include the new variables in the latest block and cannot have $s$ as a factor.
@@
 
+% \begin{example}
+% Let $G = \GL_3$ and consider the tableaux
+% $$\tau' = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau''=\young(13,2).$$
+
+% Lusztig data: $(010)$ for $\tau'$, $(101)$ for $\tau''$
+
+% Dimensions: $(1,0,-1)$ for both.
+
+% The MV cycles corresponding to $\tau'$ and $\tau''$ are both isomorphic to $\PP^2$.
+% The weights are $\lambda' = \lambda'' = (2,1,0)$ and $\mu' = \mu'' = (1,1,1)$. Hence the matrix in consideration is 
+% \[
+% X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
+%     0 & 1 & & & & \\
+%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
+%      & & 0 & 1 & & \\
+%      & & & s & A_{23}^1 & A_{23}^2 \\
+%      & & & & 0 & 1 \\
+%      & & & & & s
+% \end{BMAT}
+% \right].
+% \]
+
+% For the first entry of $\mu'$ and $\mu''$, we have the following subtableaux to consider:
+% $$\young(1) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1).$$
+% Let $X_1$ be the top-left $2 \times 2$ submatrix of $X$. The subtableaux imposes the conditions $\dim \ker X_1 = 1$ and $\dim \ker (X_1-s) = 1$. We see that we do not obtain any relations from this.
+
+% For the first two entries of $\mu'$ and $\mu''$, we have the following subtableaux:
+% $$\young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1,2).$$
+% Let $X_2$ be the top-left $4 \times 4$ submatrix of $X$.
+The left subtableau imposes the conditions $\dim \ker X_2 = 1$ and $\dim \ker X_2^2 = 2$ while the right subtableau imposes the condition that $\dim \ker (X_2 -s) = 2$.
+These conditions force the relation $$A_{12}^1 + sA_{12}^2 = 0.$$
+
+% The original tableaux for $X$ imposes the conditions that $\dim \ker X = 2$, $\dim \ker X^2 = 3$, $\dim \ker (X-s) = 2$, and $\dim \ker (X-s)^2 = 3$. These force the relation $$A_{23}^1 = 0.$$
+
+% Hence we consider the quotient
+% $$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2,s]}{\langle A_{12}^1+sA_{12}^2,A_{23}^1,s \rangle} \cong
+% \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2]}{\langle A_{12}^1,A_{23}^1 \rangle}.$$
+% We see already that the $0$-fibre is irreducible. The tableau corresponding to the ideal $\langle A_{12}^1,A_{23}^1 \rangle$ is 
+% $$\young(1123,23)$$
+% which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau'$ and $\tau''$.
+
+% Lusztig datum: $(111)$
+
+% Dimension: $(2,0,-2)$
+% \end{example}
+
 \begin{example}
 Let $G = \GL_3$ and consider the tableaux
-$$\tau' = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau''=\young(13,2).$$
-
-Lusztig data: $(010)$ for $\tau'$, $(101)$ for $\tau''$
-
-Dimensions: $(1,0,-1)$ for both.
-
-The MV cycles corresponding to $\tau'$ and $\tau''$ are both isomorphic to $\PP^2$.
-The weights are $\lambda' = \lambda'' = (2,1,0)$ and $\mu' = \mu'' = (1,1,1)$. Hence the matrix in consideration is 
-\[
-X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
-    0 & 1 & & & & \\
-     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
-     & & 0 & 1 & & \\
-     & & & s & A_{23}^1 & A_{23}^2 \\
-     & & & & 0 & 1 \\
-     & & & & & s
-\end{BMAT}
-\right].
-\]
-
-For the first entry of $\mu'$ and $\mu''$, we have the following subtableaux to consider:
-$$\young(1) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1).$$
-Let $X_1$ be the top-left $2 \times 2$ submatrix of $X$. The subtableaux imposes the conditions $\dim \ker X_1 = 1$ and $\dim \ker (X_1-s) = 1$. We see that we do not obtain any relations from this.
-
-For the first two entries of $\mu'$ and $\mu''$, we have the following subtableaux:
-$$\young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1,2).$$
-Let $X_2$ be the top-left $4 \times 4$ submatrix of $X$.
-The left subtableau imposes the conditions $\dim \ker X_2 = 1$ and $\dim \ker X_2^2 = 2$ while the right subtableau imposes the condition that $\dim \ker (X_2 -s) = 2$.
-These conditions force the relation $$A_{12}^1 + sA_{12}^2 = 0.$$
-
-The original tableaux for $X$ imposes the conditions that $\dim \ker X = 2$, $\dim \ker X^2 = 3$, $\dim \ker (X-s) = 2$, and $\dim \ker (X-s)^2 = 3$. These force the relation $$A_{23}^1 = 0.$$
-
-Hence we consider the quotient
-$$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2,s]}{\langle A_{12}^1+sA_{12}^2,A_{23}^1,s \rangle} \cong
-\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2]}{\langle A_{12}^1,A_{23}^1 \rangle}.$$
-We see already that the $0$-fibre is irreducible. The tableau corresponding to the ideal $\langle A_{12}^1,A_{23}^1 \rangle$ is 
-$$\young(1123,23)$$
-which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau'$ and $\tau''$.
-
-Lusztig datum: $(111)$
-
-Dimension: $(2,0,-2)$
-\end{example}
-
-\begin{example}
-Let $G = SL_3$ and consider the tableaux
 $$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$
@@
 
+% \begin{example}
+% Let $G = SL_3$ and consider the following tableaux:
+% $$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$
+
+% Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.
+
+% Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.
+
+% The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
+% The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
+% Then we are considering the following matrix:
+% \[
+% X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
+%     0 & 1 & & & & & & & & & & \\
+%      & 0 & 1 & & & & & & & & & \\
+%      & & 0 & 1 & & & & & & & & \\
+%      & & & 0 & 1 & & & & & & & \\
+%      & & & & 0 & 1 & & & & & & \\
+%      & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
+%      & & & & & & 0 & 1 & & & & \\
+%      & & & & & & & 0 & 1 & & & \\
+%      & & & & & & & & 0 & 1 & & \\
+%      & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
+%      & & & & & & & & & & 0 & 1 \\
+%      & & & & & & & & & & -s^2 & 2s
+% \end{BMAT}
+% \right].
+% \]
+% By computer, it can be checked that we obtain the following 3 ideals:
+% $$
+% \begin{array}{cl}
+%     I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
+%     I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
+%     I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
+% \end{array}
+% $$
+% It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same.
+The tableau corresponding to each ideal is
+% $$
+% \begin{array}{cccc}\vspace{1mm}
+%     \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
+%     \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
+%     \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
+% \end{array}
+% $$
+% The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
+% \end{example}
+
 \begin{example}
-Let $G = SL_3$ and consider the following tableaux:
-$$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$
-
-Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.
-
-Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.
-
-The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
-The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
-Then we are considering the following matrix:
-\[
-X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
-    0 & 1 & & & & & & & & & & \\
-     & 0 & 1 & & & & & & & & & \\
-     & & 0 & 1 & & & & & & & & \\
-     & & & 0 & 1 & & & & & & & \\
-     & & & & 0 & 1 & & & & & & \\
-     & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
-     & & & & & & 0 & 1 & & & & \\
-     & & & & & & & 0 & 1 & & & \\
-     & & & & & & & & 0 & 1 & & \\
-     & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
-     & & & & & & & & & & 0 & 1 \\
-     & & & & & & & & & & -s^2 & 2s
-\end{BMAT}
-\right].
-\]
-By computer, it can be checked that we obtain the following 3 ideals:
-$$
-\begin{array}{cl}
-    I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
-    I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
-    I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
-\end{array}
-$$
-It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same.
-The tableau corresponding to each ideal is
-$$
-\begin{array}{cccc}\vspace{1mm}
-    \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
-    \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
-    \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
-\end{array}
-$$
-The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
-\end{example}
-
-\begin{example}
-Let us redo example 3 but with non-dominant weights $\mu'$ and $\mu''$ such that $\mu' + \mu''$ is effective dominant. Consider the tableaux
+Let $G = \GL_3$. Consider the tableaux
 $$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
@@
 \]
-Using a computer, the ideals we now get are
+Using a computer, the ideals we get are
 $$
@@
 $$
-and the MV cycles corresponding to each are the same as before.
+and the MV cycles corresponding to each are isomorphic to $\PP^2 \times \PP^2$.
+\end{example}
+
+Let $G = \GL_4$. There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables. We list the corresponding MV cycles and tableaux:
+\[\begin{array}{cccccc} \vspace{1mm}
+    Z_1 &\leadsto \young(2) & Z_2 &\leadsto \young(1,3) & Z_3 &\leadsto \young(1,2,4) \\ \vspace{1mm}
+    Z_{1 \leftarrow 2} &\leadsto \young(3) & Z_{1 \rightarrow 2} &\leadsto \young(2,3) & Z_{2 \leftarrow 3} &\leadsto \young(1,4) \\ \vspace{1mm}
+     Z_{2 \rightarrow 3} &\leadsto \young(1,3,4) & Z_{in} &\leadsto \young(2,4) & Z_{out} &\leadsto \young(13,2,4)  \\
+    Z_{P_1} &\leadsto \young(2,3,4) & Z_{P_2} &\leadsto \young(3,4) & Z_{P_3} &\leadsto \young(4)
+\end{array}\]
+
+We show that the cluster relations in $\CC[N]$ are also true for the fusion product of the corresponding MV cycles.
+
+For each of the 15 exchange relations, we state the associated matrix $X$, the relations acquired from each submatrix $X_i$, the ideal generated by said relations, and the corresponding tableaux from the ideal.
+
+\begin{example}
+Consider the product $Z_1 * Z_2$, so the tableaux are
+\[
+\young(2) \text{ and } \young(1,3).
+\]
+Our matrix is
+\[
+X = \left[\begin{BMAT}(e){c;c;c}{c;c;c}
+    s & A_{12}^1 & A_{13}^1 \\
+     & 0 & A_{23}^1 \\
+     & & s
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_3 & A_{12}^1A_{23}^1+sA_{13}^1
+\end{array}.
+\]
+Hence our ideal is
+$$\langle A_{12}^1A_{23}^1+sA_{13}^1,s \rangle = 
+\langle A_{12}^1,s \rangle \cap \langle A_{23}^1,s \rangle.$$
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,s \rangle &\leadsto \young(13,2) &\equiv \young(3) &\leadsto Z_{Z_{1 \leftarrow 2}} \\ 
+    \langle A_{23}^1,s \rangle &\leadsto \young(12,3) &\equiv \young(2,3) &\leadsto Z_{Z_{1 \rightarrow 2}}
+\end{array}
+\]
+so $Z_1 * Z_2 = Z_{1 \leftarrow 2} + Z_{1 \rightarrow 2}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_2 * Z_3$, so the tableaux are 
+\[
+\young(1,3) \text{ and } \young(1,2,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
+    0 & 1 & & & \\
+     & s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+     & & s & A_{23}^1 & A_{24}^1 \\
+     & & & 0 & A_{34}^1 \\
+     & & & & s
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1 \\
+    X_3 & A_{13}^1 \\
+    X_4 & A_{14}^1, A_{23}^1A_{34}^1 + sA_{24}^1
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle &\leadsto \young(11,24,3) &\equiv \young(1,4) &\leadsto Z_{2 \leftarrow 3} \\ 
+    \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(11,23,4) &\equiv \young(1,3,4) &\leadsto Z_{2 \rightarrow 3}
+\end{array}
+\]
+so $Z_2 * Z_3 = Z_{2 \leftarrow 3} + Z_{2 \rightarrow 3}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_1 * Z_{2 \rightarrow 3}$, so the tableaux are 
+\[
+\young(2) \text{ and } \young(1,3,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+    s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+     & 0 & A_{23}^1 & A_{24}^1 \\
+     & & s & A_{34}^1 \\
+     & & & s
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
+    X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(12,3,4) &\equiv \young(2,3,4) &\leadsto Z_{P_1} \\ 
+    \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
+\end{array}
+\]
+so $Z_1 * Z_{2 \rightarrow 3} = Z_{P_1} + Z_{out}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_1 * Z_{2 \leftarrow 3}$, so the tableaux are 
+\[
+\young(2) \text{ and } \young(1,4).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(2) \text{ and } \young(11,24,3).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+    0 & 1 & & & & \\
+    -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
+     & & 0 & 1 & & \\
+     & & & s & A_{23}^1 & A_{24}^1 \\
+     & & & & s & A_{34}^1 \\
+     & & & & & s
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1 + sA_{12}^2 \\
+    X_3 & A_{13}^1, A_{23}^1 \\
+    X_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(114,22,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
+    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(2,4) &\leadsto Z_{in}
+\end{array}
+\]
+so $Z_1 * Z_{2 \leftarrow 3} = Z_{P_3} + Z_{in}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_3 * Z_{1 \rightarrow 2}$, so the tableaux are 
+\[
+\young(1,2,4) \text{ and } \young(2,3).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(1,2,4) \text{ and } \young(12,3).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+    0 & 1 & & & & \\
+     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
+     & & 0 & 1 & & \\
+     & & & s & A_{23}^1 & A_{24}^1 \\
+     & & & & s & A_{34}^1 \\
+     & & & & & 0
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1 \\
+    X_3 & A_{23}^1 \\
+    X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(1,4) &\leadsto Z_{in} \\ 
+    \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(112,23,4) &\equiv \young(1,3,4) &\leadsto Z_{P_1}
+\end{array}
+\]
+so $Z_3 * Z_{1 \rightarrow 2} = Z_{in} + Z_{P_1}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_3 * Z_{1 \leftarrow 2}$, so the tableaux are 
+\[
+\young(1,2,4) \text{ and } \young(3).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+    0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+     & 0 & A_{23}^1 & A_{24}^1 \\
+     & & s & A_{34}^1 \\
+     & & & 0
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1 \\
+    X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(14,2,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
+    \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
+\end{array}
+\]
+so $Z_3 * Z_{1 \leftarrow 2} = Z_{P_3} + Z_{out}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3}$, so the tableaux are 
+\[
+\young(3) \text{ and } \young(1,4).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(13,2) \text{ and } \young(1,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
+    0 & 1 & & & \\
+     & s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+     & & 0 & A_{23}^1 & A_{24}^1 \\
+     & & & 0 & A_{34}^1 \\
+     & & & & s
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1 \\
+    X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
+\end{array}.
+\]
+Hence our ideal is 
+\[
+\langle A_{12}^1,A_{13}^1A_{34}^1+sA_{14}^1,s \rangle
+= \langle A_{12}^1,A_{13}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{13}^1,s \rangle &\leadsto \young(114,23) &\equiv \young(14,3) &\leadsto Z_2 Z_{P_3} \\ 
+    \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(113,24) &\equiv \young(3,4) &\leadsto Z_{P_2}
+\end{array}
+\]
+so $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3} = Z_2 Z_{P_3} + Z_{P_2}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3}$, so the tableaux are 
+\[
+\young(2,3) \text{ and } \young(1,3,4).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(12,23) \text{ and } \young(1,3,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+    0 & 1 & & & & & \\
+     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
+     & & 0 & 1 & & & \\
+     & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
+     & & & & 0 & 1 & \\
+     & & & & & s & A_{34}^1 \\
+     & & & & & & s
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1 \\
+    X_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
+    X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
+    \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle &\leadsto \young(112,233,4) &\equiv \young(12,33,4) &\leadsto Z_2 Z_{P_1}
+\end{array}
+\]
+so $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3} = Z_{P_2} + Z_2 Z_{P_1}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_2 * Z_{out}$, so the tableaux are 
+\[
+\young(1,3) \text{ and } \young(13,2,4).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(11,23) \text{ and } \young(13,2,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
+    0 & 1 & & & & & & \\
+     & 0 & 1 & & & & & \\
+     & & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
+     & & & 0 & 1 & & & \\
+     & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
+     & & & & & 0 & 1 & \\
+     & & & & & & s & A_{34}^1 \\
+     & & & & & & & s
+\end{BMAT}
+\right]
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1, A_{12}^2 \\
+    X_3 & A_{13}^1 \\
+    X_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(1113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
+    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(1113,223,4) &\equiv \young(1,3,4) &\leadsto Z_{1 \leftarrow 2} Z_{2 \rightarrow 3}
+\end{array}
+\]
+so $Z_2 * Z_{out} = Z_{P_2} + Z_{1 \leftarrow 2} Z_{2 \rightarrow 3}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_2 * Z_{in}$, so the tableaux are 
+\[
+\young(1,3) \text{ and } \young(2,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+    0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+     & s & A_{23}^1 & A_{24}^1 \\
+     & & 0 & A_{34}^1 \\
+     & & & s
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
+    X_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{34}^1,s \rangle \cap \langle A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(13,24) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
+    \langle A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s \rangle &\leadsto \young(12,34) & &\leadsto Z_{1 \rightarrow 2} Z_{2 \leftarrow 3}
+\end{array}
+\]
+so $Z_2 * Z_{in} = Z_{P_2} + Z_{1 \rightarrow 2} Z_{2 \leftarrow 3}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_{out} * Z_{1 \rightarrow 2}$, so the tableaux are 
+\[
+\young(13,2,4) \text{ and } \young(2,3).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(13,2,4) \text{ and } \young(12,3).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+    0 & 1 & & & & & \\
+     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
+     & & 0 & 1 & & & \\
+     & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
+     & & & & 0 & 1 & \\
+     & & & & & s & A_{34}^1 \\
+     & & & & & & 0
+\end{BMAT}
+\right]
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1 \\
+    X_3 & A_{23}^1 +sA_{23}^2 \\
+    X_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(1112,24,3) &\equiv \young(23,4) &\leadsto Z_1 Z_{P_2} \\ 
+    \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(1123,23,4) &\equiv \young(23,3,4) &\leadsto Z_{1 \leftarrow 2} Z_{P_1}
+\end{array}
+\]
+so $Z_{out} * Z_{1 \rightarrow 2} = Z_1 Z_{P_2} + Z_{1 \leftarrow 2} Z_{P_1}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_{in} * Z_{1 \leftarrow 2}$, so the tableaux are
+\[
+\young(2,4) \text{ and } \young(3).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(2,4) \text{ and } \young(13).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+     s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+     & 0 & A_{23}^1 & A_{24}^1 \\
+     & & s & A_{34}^1 \\
+     & & & 0
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_4 & A_{23}^1A_{34}^1 - sA_{24}^1
+\end{array}.
+\]
+Hence our ideal is 
+\[
+\langle A_{23}^1A_{34}^1 - sA_{24}^1,s \rangle
+= \langle A_{23}^1,s \rangle \cap \langle A_{34}^1,s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{23}^1,s \rangle &\leadsto \young(124,3) &\equiv \young(24,3) &\leadsto Z_{1 \rightarrow 2} Z_{P_3} \\ 
+    \langle A_{34}^1,s \rangle &\leadsto \young(123,4) &\equiv \young(23,4) &\leadsto Z_1 Z_{P_2}
+\end{array}
+\]
+so $Z_{in} * Z_{1 \leftarrow 2} = Z_{1 \rightarrow 2} Z_{P_3} + Z_1 Z_{P_2}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_{out} * Z_{2 \leftarrow 3}$, so the tableaux are 
+\[
+\young(1,4) \text{ and } \young(13,2,4).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(11,24,3) \text{ and } \young(13,2,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
+    0 & 1 & & & & & & & \\
+     & 0 & 1 & & & & & & \\
+     & & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
+     & & & 0 & 1 & & & & \\
+     & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
+     & & & & & 0 & 1 & & \\
+     & & & & & & s & A_{34}^1 & A_{34}^2 \\
+     & & & & & & & 0 & 1 \\
+     & & & & & & & & s
+\end{BMAT}
+\right]
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1,A_{12}^2 \\
+    X_3 & A_{13}^1, A_{23}^1 \\
+    X_4 & \begin{array}{c}
+         A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1,  \\
+         A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
+         A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2
+    \end{array}
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[
+\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s \rangle \cap \begin{array}{c}
+     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s \rangle. 
+\end{array}
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(1114,223,34) &\equiv \young(14,3,4) &\leadsto Z_{2 \rightarrow 3} Z_{P_3} \\ 
+    \begin{array}{c}
+     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s \rangle. 
+\end{array}&\leadsto \young(1113,224,34) &\equiv \young(13,24,4) &\leadsto Z_3 Z_{P_2}
+\end{array}
+\]
+so $Z_{out} * Z_{2 \leftarrow 3} = Z_{2 \rightarrow 3} Z_{P_3} + Z_3 Z_{P_2}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_{in} * Z_{2 \rightarrow 3}$, so the tableaux are 
+\[
+\young(2,4) \text{ and } \young(1,3,4).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(12,24,3) \text{ and } \young(1,3,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
+    0 & 1 & & & & & & \\
+     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
+     & & 0 & 1 & & & & \\
+     & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
+     & & & & 0 & 1 & & \\
+     & & & & & s & A_{34}^1 & A_{34}^2 \\
+     & & & & & & 0 & 1 \\
+     & & & & & & & s
+\end{BMAT}
+\right].
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1 \\
+    X_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
+    X_4 & \begin{array}{c}
+         A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+         A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2,  \\
+         A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
+         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1 
+    \end{array} 
+\end{array}.
+\]
+Hence our ideal decomposes into 
+\[\begin{array}{c}
+     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s \rangle  
+\end{array}
+ \cap \begin{array}{c}
+      \langle A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
+      A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s \rangle. 
+ \end{array} 
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \begin{array}{c}
+     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s \rangle  
+\end{array} &\leadsto \young(113,224,34) &\equiv \young(13,24,4) &\leadsto Z_3 Z_{P_2} \\ 
+    \begin{array}{c}
+      \langle A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
+      A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s \rangle. 
+ \end{array} &\leadsto \young(112,234,34) &\equiv \young(12,34,4) &\leadsto Z_{2 \leftarrow 3} Z_{P_1}
+\end{array}
+\]
+so $Z_{in} * Z_{2 \rightarrow 3} = Z_3 Z_{P_2} + Z_{2 \leftarrow 3} Z_{P_1}$.
+\end{example}
+
+\begin{example}
+Consider the product $Z_{in} * Z_{out}$, so the tableaux are 
+\[
+\young(2,4) \text{ and } \young(13,2,4).
+\]
+As the sum of the weights is not dominant, we will instead be using the tableaux
+\[
+\young(112,24,3) \text{ and } \young(13,2,4).
+\]
+Our matrix is 
+\[
+X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
+    0 & 1 & & & & & & & & \\
+     & 0 & 1 & & & & & & & \\
+     & & s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
+     & & & 0 & 1 & & & & & \\
+     & & & & 0 & 1 & & & & \\
+     & & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
+     & & & & & & 0 & 1 & & \\
+     & & & & & & & s & A_{34}^1 & A_{34}^2 \\
+     & & & & & & & & 0 & 1 \\
+     & & & & & & & & & s
+\end{BMAT}
+\right]
+\]
+The relations from the submatrices are:
+\[
+\begin{array}{c|c}
+    \text{Submatrix} & \text{Relations} \\ \hline
+    X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
+    X_3 & A_{13}^1,A_{23}^1 \\
+    X_4 & \begin{array}{c}
+         A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+         A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
+         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
+         A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
+    \end{array} 
+\end{array}.
+\]
+Our ideal decomposes into 
+\[
+\langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
+\cap \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle.
+\]
+The tableau for each ideal is
+\[\begin{array}{cccc}\vspace{1mm}
+    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
+    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
+\end{array}
+\]
+so $Z_{in} * Z_{out} = Z_{P_1} Z_{P_3} + Z_1 Z_3 Z_{P_2}$.
 \end{example}

### 2021-04-14 draft.tex
Updates from Overleaf

@@
          A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
-         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
+         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
+         A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
          A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
@@
 \]
-Our ideal decomposes into 
+Hence our ideal decomposes into 
 \[
 \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
-\cap \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle.
+\cap \begin{array}{c}
+     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
+\end{array} 
 \]
@@
     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
-    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
+    \begin{array}{c}
+     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
+\end{array} &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
 \end{array}

### 2021-04-14 draft.tex

--- 2021-04-14 draft.tex
@@
 
-% Dimensions: $(1,0,-1)$ for both.
+\acom{If we start with $n_\bullet ' = (0,1,0)$ and $n_\bullet'' = (1,0,1)$ then the smallest $\tau$ for $n_\bullet = (1,1,1)$ is $\young(1123,23)$ and hence the smallest $\mu,\lambda$ are $(2,2,2),(4,2,0)$.
+So far so good.
+However, the ``smallest'' ``fission'' of $\tau$ is $\young(112,23) , \young(3)$.
+We could define ``smallest'' to mean minimizing the dimension of the generalized $s$-eigenspace.
+What do you guys think?
+If we agree to do this we should amend this example.
+For Joel: this is an example where our $B(\infty) \to B(\lambda)$ does not match that of Claxton--Tingley (quoted in my thesis).
+They would get $\lambda = (3,1)$.
+I think that their map satisfies $\lambda$ dominant and $\mu$ such that each $\mu_i\ge 1$.}
+
+Dimensions: $(1,0,-1)$ for both.
 
@@
 
+\acom{This time the smallest $\tau$ is actually $\young(12,3)$ and the smallest fission is $\young(1,3),\young(2)$. For Joel: this time the our $\lambda$ matches \cite{claxton2015young}'s.}
+
 Dimensions: $(1,-1,0)$ for $\tau'$, $(0,1,-1)$ for $\tau''$.
@@
 
-% \begin{example}
-% Let $G = SL_3$ and consider the following tableaux:
-% $$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$
-
-% Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.
-
-% Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.
-
-% The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
-% The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
-% Then we are considering the following matrix:
-% \[
-% X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
-%     0 & 1 & & & & & & & & & & \\
-%      & 0 & 1 & & & & & & & & & \\
-%      & & 0 & 1 & & & & & & & & \\
-%      & & & 0 & 1 & & & & & & & \\
-%      & & & & 0 & 1 & & & & & & \\
-%      & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
-%      & & & & & & 0 & 1 & & & & \\
-%      & & & & & & & 0 & 1 & & & \\
-%      & & & & & & & & 0 & 1 & & \\
-%      & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
-%      & & & & & & & & & & 0 & 1 \\
-%      & & & & & & & & & & -s^2 & 2s
-% \end{BMAT}
-% \right].
-% \]
-% By computer, it can be checked that we obtain the following 3 ideals:
-% $$
-% \begin{array}{cl}
-%     I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
-%     I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
-%     I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
-% \end{array}
-% $$
-% It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same.
+\begin{comment}
+\begin{example}
+Let $G = SL_3$ and consider the following tableaux:
+$$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$
+
+Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.
+
+Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.
+
+The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
+The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
+Then we are considering the following matrix:
+\[
+X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
+    0 & 1 & & & & & & & & & & \\
+     & 0 & 1 & & & & & & & & & \\
+     & & 0 & 1 & & & & & & & & \\
+     & & & 0 & 1 & & & & & & & \\
+     & & & & 0 & 1 & & & & & & \\
+     & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
+     & & & & & & 0 & 1 & & & & \\
+     & & & & & & & 0 & 1 & & & \\
+     & & & & & & & & 0 & 1 & & \\
+     & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
+     & & & & & & & & & & 0 & 1 \\
+     & & & & & & & & & & -s^2 & 2s
+\end{BMAT}
+\right].
+\]
+By computer, it can be checked that we obtain the following 3 ideals:
+$$
+\begin{array}{cl}
+    I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
+    I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
+    I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
+\end{array}
+$$
+It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same.
 The tableau corresponding to each ideal is
-% $$
-% \begin{array}{cccc}\vspace{1mm}
-%     \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
-%     \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
-%     \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
-% \end{array}
-% $$
-% The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
-% \end{example}
+$$
+\begin{array}{cccc}\vspace{1mm}
+    \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
+    \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
+    \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
+\end{array}
+$$
+The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
+\end{example}
+\end{comment}
 
 \begin{example}
-Let $G = \GL_3$. Consider the tableaux
+
+    \acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{mirkovic2007quiver}.}
+
+Let us redo example 3 but with non-dominant weights $\mu'$ and $\mu''$ such that $\mu' + \mu''$ is effective dominant. Consider the tableaux
 $$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$

### 2021-04-14 draft.tex
Fixed last example.

@@
 
-Dimensions: $(1,0,-1)$ for both.
+% Dimensions: $(1,0,-1)$ for both.
 

### 2021-04-16 draft.tex
Fixed a typo.

@@
 Consider $ K^m $ as a $K$-module. 
-\acom{left or right, doesn't matter?
-I think we are in a situation where they are the same, i.e.\ our rings are commutative.} By restriction $ K^m$ can be viewed as an $R$-module.
-An $R$-lattice in $K^m$ \acom{definiton, no boldface}
+% \acom{left or right, doesn't matter? I think we are in a situation where they are the same, i.e.\ our rings are commutative.} 
+By restriction $ K^m$ can be viewed as an $R$-module.  An \textbf{$R$-lattice} in $K^m$ 
 % \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
@@
     % $$ \Grbd \rightarrow \Grth $$ 
-    We define a map $ \Grbd \rightarrow \Grth $ by \acom{Don't we also want to restrict $V$}
+    We define a map $ \Grbd \rightarrow \Grth $ by 
+    % \acom{Don't we also want to restrict $V$} 
+    % Joel says nope, restriction of vector bundle corresponds to specialization of lattice; here the map is inclusion  
     $$
@@
 
-Let $ \Gr_{0, \CC^\times} $ denote the preimage of $ \Gr_{0, \AA} $ under the map $\Gr_{0,\AA} \rightarrow \AA $.
+Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.
 Gluing together the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above) we obtain
@@
 \jcom{I added the def of $ \Gr_{0, \CC^\times}$ but not $ \Gr_{\CC^\times}$.  We could drop it and condense the definition of $ \tau$ to one map.}
+\acom{Todo --- We resolved to rewrite $\tau$ as gluing of the composition above restricted to fibres}
 
@@
 \acom{Question abt general fact: why is scheme-theoretic closure of product flat?} \jcom{See Hartshorne Proposition III.9.8.
-I just taught this on the last day of my algebraic geometry class!}
+I just taught this on the last day of my algebraic geometry class!} \acom{Cool!
+That Proposition is a bit more general too..}
 
@@
 Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$?
-Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes}
+Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes} \acom{I like the idea of making it $N$}
 
@@
 \jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}
+\acom{Oh, sorry, I see it. Maybe because it was the start of a new paragraph I didn't connect `data' and `ranks' at first glance.}
 
@@
 \jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
+\acom{\emoji{+1}}
 
@@
 I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}
+\acom{\emoji{+1}}
 
@@
 % 
-Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
-\begin{definition}The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
-    \[
-        \begin{aligned}
-            &\text{for all } 1 \le a,s\le m\,,
-            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
-            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
-            &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
-        \end{aligned}    
-    \]
-\end{definition}
-\jcom{I'm not a huge fan of this description, but I don't know how to write it better.}
-
-\acom{Agree. Happy to just have the in-words description.}
-
-    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
+% Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
+% \acom{I don't suppose we need this basis now that we're just describing $\TT_\mu$ in words.}
+% 
+% \begin{definition}
+An element of the \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ 
+% defined as the set of $A\in M_N(\CC)$ such that 
+    % \[
+    %     \begin{aligned}
+    %         &\text{for all } 1 \le a,s\le m\,,
+    %         \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
+    %         &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
+    %         &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
+    %     \end{aligned}    
+    % \]
+% \end{definition}
+% \jcom{I'm not a huge fan of this description, but I don't know how to write it better.}
+% 
+% \acom{Agree. Happy to just have the in-words description.}
+% 
+    % In words, $A$ 
+    is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
     % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
@@
 \section{Exposition}
+\label{s:exposition}
 
@@
         \item $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. %\acom{Should we describe this map somewhere? Earlier?}
-        \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $(0,\lambda'), (s,\lambda'')$.
+        \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $((0,\lambda'), (s,\lambda''))$.
         \item $ L \in G(\CC[t]) t^{\lambda'} (t-s)^{\lambda''}$.
@@
     \rcom{Preimage of $\beta_\mu$}  
+    % 
+    \acom{I guess that this is the ``$\mu$-numeration'' of the standard basis of $\CC^N$ that I commented out.}
 
@@
 \begin{proof}
-    Let $ L $ lie in this image.  Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.  Note that $ h \in T_1(\Oinf)$. 
+    Let $ L $ 
+    % lie in this image.  
+    be a lattice in the image of $S^{\mu',\mu''}_{0,\AA}$.
+Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $.
+Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.
+Note that $ h \in T_1(\Oinf)$.
     Moreover,
@@
     % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
-    $h^{-1} g h \in N(\cK_\infty)$ and so we can factor $ h^{-1} g h = n_1 n_2$ for $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t]) $.
-Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N(\CC[t]) $.
-% \CC\xt[t^{-1}]s
-
-    \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?}
-
-    \acom{Si}
-
+    $h^{-1} g h \in N_-(\cK_\infty)$ and so we can factor $ h^{-1} g h$ as $n_1 n_2$ for some $ n_1 \in {(N_-)}_1(\Oinf), n_2 \in {N_-}(\CC[t]) $.
+
+    Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t]) $. % \CC\xt[t^{-1}]s
+% 
+% \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?} % 
+% \acom{Si.}
+% 
     Thus, $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
@@
 \section{Falling Action} % Resolution
+\acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis.
+Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with.
+This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
+
 \begin{comment}
@@
 \end{comment}
-
-\section{Denouement}
-\label{s:denouement}
-% 
-In this section we demonstrate how to put the main results of this paper into practice.
+% 
+% In this section we demonstrate how to put the main results of this paper into practice.
+% 
+Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
+% 
+In this part we prove that 
+% the ideal of 
+$Z'\ast_\AA Z''$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$.
 % 
@@
 \begin{proposition}
-    Generalized orbital varieties are indexed by semistandard Young tableaux. Composing with the ordinary Mirkovi\'c--Vybornov isomorphism gives bijections 
+    % Generalized orbital varieties are indexed by semistandard Young tableaux. 
+    There are bijections 
+    % Composing with the ordinary Mirkovi\'c--Vybornov isomorphism gives bijections 
     \[
         YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \irr \overline\Gr^\lambda\cap S^\mu_-\,. 
+    \]
+    Moreover, there is a \acom{partial?} inverse 
+    \[
+    \CC[N]\to \bigcup_{\lambda~\text{dominant}\atop \mu\le\lambda} YT(\lambda)_\mu \,. 
     \]
@@
 % 
-Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. 
+\acom{Refer to Claxton--Tingley multisegments, Hong--Lee marignally large tableaux for comparison.}
+\jcom{I don't think that you should mention this partial inverse here.
+I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
+
+Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. \acom{Out of place?}
+
+% 
+% 
+% TODO: Not yet, that would be the algo stuff that we are holding off on 
+% In this section we explain how to determine the ideal of $Z'\ast_\AA Z''$ from the minimal pair $(\tau',\tau'')$ corresponding to $(n_\bullet(Z'),n_\bullet(Z''))$.
+% 
+% In particular, we prove that ``the generalized Spaltenstein map'' produces MV cycles. 
+% 
+% and recall the $\mu$-numeration of the standard basis of $\CC^N$. 
+% TODO: can't we do without it^^
+Given $A \in M_N(\CC)$ we'll denote by $A\big|_{\CC^i}$ the restriction of $A$ to the subspace spanned by the first $i$ standard basis vectors.
+Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ the shape of $\tau'(i),\tau''(i)$ resp.\ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all but its first $i$ boxes.
+If the tableau contains repeated entries then first means leftmost.
+
+\begin{proposition}
+    Given $Z',Z''$, let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ be such that\dots If $s\ne 0$, then 
+    \[
+    \overline{\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{i}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\}} 
+    \cong Z'\times Z'' \,. %\mu_1 + \cdots + \mu_i
+    % = Z(\tau')\times Z(\tau'')\,. 
+    \]
+\end{proposition}
+% 
+\jcom{Do you want the ``blocky'' or ``boxy'' description here?
+I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$?
+I'm not so sure that ``boxy'' will work, since with those $s$ in the matrix, it doesn't preserves all the $ \CC^i$.}
+
+\begin{proof}
+    Let $(A,s)$ be an element of the set on the left hand side, let $a\in\{0,s\}$ and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
+    Let $i\in \{1,\dots,N\}$ and write $m(i)$ for the maximum weight of a box in $\tau'(i)$ or $\tau''(i)$.
+
+    The the Jordan type of $A-a\big|_{E_a\cap\CC^{m(i)}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
+    Moreover, the lattice $(L,s)$ defined by $g(A)$ is such that $t-a$ has the same Jordan type on 
+    % $\cO_a^{m(i)} / L(a)\cap\cO_a^{m(i)} = \CC[t]^{m(i)}/L\cap\CC[t]^{m(i)}\otimes_{\CC[t]}\cO_a $ 
+    \begin{equation}
+        \label{eq:bcflat}
+        \cO_a^{m(i)} / L(a)\cap\cO_a^{m(i)} = \CC[t]^{m(i)}/L\cap\CC[t]^{m(i)}\otimes_{\CC[t]}\cO_a 
+    \end{equation}
+    as does $(A-a\big|_{E_a\cap\CC^{m(i)}},s)$. 
+    \acom{Not sure where to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
+    % 
+    \Cref{eq:bcflat} follows from e.g.\ \cite[Proposition~10.14]{atiyah2018introduction}:
+    \begin{quotation}
+        If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
+    \end{quotation}
+    applied to $A = \CC[t]$ and $\fa = (t)$.
+
+    \jcom{I think that it is actually a bit simpler.  Again from teaching algebraic geometry, I found the following.  If $ A $ is a principal ideal domain, then $M $ is flat iff it is torsion-free.}
+
+    The second assertion is a consequence of \Cref{lem:} \acom{Cite Joel's lemma}. 
+    By \Cref{adthesis} \acom{Cite my thesis} it follows that $(L(0),L(s)) \in Z'\times Z''$. 
+    Since all maps are isomoprhisms the converse is automatic. 
+\end{proof}
+
+\begin{question}
+%[Related question] 
+    If $\mu',\mu''$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
+    \[
+    \begin{tikzcd}
+        \overline\Gr^{\lambda',\lambda'}_{0,s}\cap S^{\mu',\mu''}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda'} \cap S^{\mu'} \times \overline\Gr^{\lambda'} \cap S^{\mu''} \supset Z' \times Z'' \ar[d]\\
+        \overline\OO^{\lambda',\lambda''}_{0,s} \cap \UU^{\mu',\mu''}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda'}\cap \TT_{\mu'}\cap \n \times \overline\OO^{\lambda''}\cap \TT_{\mu''}\cap \n
+    \end{tikzcd}    
+    \]
+\end{question}
 % 
@@
     \end{equation}
-    and the intersection multiplicities on the right are found by the algorithm described in \Cref{ss:algo}.
-
-    \acom{Add pseudocode}
-
-    In particular, the multiplicity of $Z(\tau)$
+    and the intersection multiplicities on the right are found by\dots\acom{To be completed.}
+
+    % In particular, the multiplicity of $Z(\tau)$
     % in the product of the zero fiber 
@@
     % closure of the family $Z_1 \times Z_2 \times U$ 
-    is equal to the multiplicity of its generalized orbital variety $X(\tau)$ 
-    in $ \overline{\OO}^{\lambda',\lambda''}_{0,0}\cap\UU^{\mu',\mu''}_{0,0} $. 
+    % is equal to the multiplicity of its generalized orbital variety $X(\tau)$ 
+    % in $ \overline{\OO}^{\lambda',\lambda''}_{0,0}\cap\UU^{\mu',\mu''}_{0,0} $. 
     % among the set 
@@
     % \end{equation}
+    \acom{Some of what was written here (commented out above) was incorrect. We can reiterate for emphasis that $i(Z,Z'\circ Z'')$ is computed in terms of rank varieties.}
 
@@
 
-    \acom{To be completed.}
+    \acom{To be completed. We require a notion of ``smallest'' pair of factor tableaux associated to a given tableau --- that is if we care to include our $B(\infty)\to B(\lambda)$ map. 
+    As the examples show, there may be more than one way to break up a ``minimal'' tableau for $n_\bullet = n_\bullet ' + n_\bullet ''$ into two tableaux with data $n_\bullet' $ and $n_\bullet''$ resp.\ The practical notion of min is such that the generalized nonzero eigenspace has the smallest possible dimension.}
 \end{proposition}
 
-\subsection{Pseudocode}
-%
-
-\subsection{Tableaux and families}
-% 
-Recall that there is an order on repeated entries of a semistandard Young tableau. 
-% 
-In this section we explain how to determine the ideal of $Z'\ast_\AA Z''$ from the minimal pair $(\tau',\tau'')$ corresponding to $(n_\bullet(Z'),n_\bullet(Z''))$.
-% 
-In particular, we prove that ``the generalized Spaltenstein map'' produces MV cycles.
-
-Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as above, and recall the $\mu$-numeration of the standard basis of $\CC^N$.
-Given $A \in M_N(\CC)$ we'll denote by $A\big|_{\CC^i}$ the restriction of $A$ to the subspace spanned by the first $i$ standard basis vectors.
-Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ the shape of $\tau'(i),\tau''(i)$ resp.\ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all but its first $i$ boxes.
-
-\acom{May want a more compact notation such as $A_{k}$}
-
-\begin{proposition}
-    Given $Z',Z''$, let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ be such that\dots If $s\ne 0$, then 
-    \[
-    \overline{\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{\mu_1 + \cdots + \mu_i}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,m\}} 
-    \cong Z'\times Z'' \,. 
-    % = Z(\tau')\times Z(\tau'')\,. 
-    \]
-\end{proposition}
-
-\begin{proof}
-    % \acom{Another notational possibility is $\mu = \mu^0 + \mu^s$ etc., or $\mu(0) + \mu(s)$ or some variant with the eigenvalues being the indices.}
-    % 
-    First, reformulate as 
-    \[
-    \begin{tikzcd}
-        & (L,s) \in \Grbd \ar[dr,mapsto]\ar[dl,mapsto]\\
-        t\big|_{\CC[t]^m/L} \in A & & (L(0),L(s)) \in B 
-    \end{tikzcd}
-    \]
-    Fix $i \in \{1,\dots,m\}$, let $p = \mu_1 + \cdots + \mu_i$ and consider $(L',L'')\in Z'\times Z''$. 
-    We need to show that the Jordan type of $t\big|_{\CC[t]^p/L(0)\cap\CC[t]^p}$ is $\lambda'{(p)}$ and Jordan type of $(t-s)\big|_{\CC[t]^p/L(s)\cap \CC[t]^p}$ is $\lambda''{(p)}$.
-
-    Need: operations of taking quotients and taking generalized eigenspaces (i.e.\ $-\otimes\CC\xt[t-a]$) commute.
-    See $(*)$ above. Also 
-    % 
-    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
-    carrying the action of $t $ to the action of $t$.
-
-    The left hand side is the same thing as
-    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
-    \acom{Unrelated comments.
-1) Restricting to an eigenspace is like inverting (forgetting) the action of $t$ by any other generalized eigenvalue.
-2) Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}
-
-    Exercise 2.20 from \cite{atiyah2018introduction}: If $f : A \to B$ is a ring homomorphism and $M$ is a flat $A$-module, then $M_B = B\otimes_A M$ is a flat $B$-module.
-Take $A=\CC[t]$ and $B=\CC\xt$.
-\marginpar[]{*}
-
-    This exercise is irrelevant. We want to say something about two different modules over the same base ring. As Roger reminded the relevant fact is \cite[Proposition~10.14]{atiyah2018introduction}: 
-    % 
-    \begin{quotation}
-        If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
-    \end{quotation}
-    applied to $A = \CC[t]$ and $\fa = (t)$. 
-\end{proof}
-
-\begin{question}[Related question]
-    If $\mu',\mu''$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
-    \[
-    \begin{tikzcd}
-        \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu',\mu''}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
-        \overline\OO^{\lambda_1,\lambda_2}_{0,s} \cap \UU^{\mu',\mu''}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
-    \end{tikzcd}    
-    \]
-\end{question}
-
+% Let's wait for Gerhard before we discuss our computations any further
+% \subsection{Pseudocode}
+%
+
+\section{Denouement}
+\label{s:denouement}
 \subsection{Examples}
@@
 Consider the subtableaux $\tau'(i)$ of $\tau'$ and $\tau''(i)$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$.
-Let $\lambda'(j)$ and $\lambda''(j)$ be the corresponding sizes and $\mu'(j)$ and $\mu'(j)$ be the corresponding weights of the subtableaux.
+Let $\lambda'(i)$ and $\lambda''(i)$ be the corresponding sizes and $\mu'(i)$ and $\mu'(i)$ be the corresponding weights of the subtableaux.
 For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu'(i), \mu''(i)}_{0,s}$ of $X$.
@@
 
-Let us redo example 3 but with non-dominant weights $\mu'$ and $\mu''$ such that $\mu' + \mu''$ is effective dominant. Consider the tableaux
+Let $G = \GL_3$. Consider the tableaux
 $$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$

### 2021-04-19 draft.tex
joels latest changes and then some

@@
 Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.
-Gluing together the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above) we obtain
-$$
-\tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr_{\CC^\times} \rightarrow \Gr \times \Gr
-$$
-where the first morphism is an isomorphism and the second map uses $ \Gr_s \cong \Gr $ on each fibre.
+Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
+
+These isomorphisms glue together to a projection map
+$$
+\tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
+$$ 
 (This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
-\jcom{I added the def of $ \Gr_{0, \CC^\times}$ but not $ \Gr_{\CC^\times}$.  We could drop it and condense the definition of $ \tau$ to one map.}
-\acom{Todo --- We resolved to rewrite $\tau$ as gluing of the composition above restricted to fibres}
 
@@
 $X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
-\acom{Question abt general fact: why is scheme-theoretic closure of product flat?} \jcom{See Hartshorne Proposition III.9.8.
+
+%\acom{Question abt general fact: why is scheme-theoretic closure of product flat?} \jcom{See Hartshorne Proposition III.9.8.
 I just taught this on the last day of my algebraic geometry class!} \acom{Cool!
@@
 \end{equation}
-\jcom{Someone should check that I chose the notation correctly to make this work out.}
-
-\acom{What do we mean by equalities in $z(s)$ reproduce $p$?
+%\jcom{Someone should check that I chose the notation correctly to make this work out.}
+
+%\acom{What do we mean by equalities in $z(s)$ reproduce $p$?
 I thought $z(s)$ was defined by $p$.
@@
 
-\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.
+%\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.
 I changed the wording of ``reproduce''.
 I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}
-\acom{\emoji{+1}}
+%\acom{\emoji{+1}}
 
@@
 
-    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(\beta_\mu) + L$.
-
-    \rcom{Preimage of $\beta_\mu$}  
-    % 
-    \acom{I guess that this is the ``$\mu$-numeration'' of the standard basis of $\CC^N$ that I commented out.}
+    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(  t^k e_i : 0 \le k < \mu_i, 1 \le i \le m) + L$.
+
+%    \rcom{Preimage of $\beta_\mu$}  
+    % 
+ %   \acom{I guess that this is the ``$\mu$-numeration'' of the standard basis of $\CC^N$ that I commented out.}
 
@@
 
-\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
-
-\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$.
+%\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
+
+%\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$.
 When we multiply by $t^{-\mu}$, we scale the $i$th column by $t^{-\mu_i}$.

### 2021-04-19 draft.tex
whatd i forget

--- 2021-04-14 draft.tex
@@
 \begin{conjecture}
-    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
+    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
     Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
@@
 
-% Dimensions: $(1,0,-1)$ for both.
+Dimensions: $(1,0,-1)$ for both.
 
@@
          A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
-         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
-         A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
+         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
          A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
@@
 \]
-Hence our ideal decomposes into 
+Our ideal decomposes into 
 \[
 \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
-\cap \begin{array}{c}
-     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
-\end{array} 
+\cap \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle.
 \]
@@
     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
-    \begin{array}{c}
-     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
-\end{array} &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
+    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
 \end{array}

### 2021-04-20 draft.tex
that wasnt a kilo

--- 2021-04-19 draft.tex
@@
 % 
-This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019Mirkovi\'c}).
+This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019mirkovic}).
 % conjectured by JEA and proved by BKK
@@
     % 
-    \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : &\rk A^i \le N - 
+    \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i &\le N - 
     \#\text{~boxes in first $i$ columns of }\lambda' \\
-    &\rk (A-s)^i \le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
+    \rk (A-s)^i &\le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
 \end{split}
@@
     %
+
     To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
     of polynomials 
-    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
+    % $ g(A) = \left( g(A)_{ij} \right)$ 
+    $g(A)$
+    in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
     \begin{equation}
@@
     % 
+    \acom{Can add sentence before making next definition? To the effect of ``In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.''}
     \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
@@
     as does $(A-a\big|_{E_a\cap\CC^{m(i)}},s)$. 
-    \acom{Not sure where to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
+    \acom{Not sure when to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
     % 
@@
 
+    \acom{Here $A$ is $\CC[t]$ and $M = \cO$ right? Better, agreed. Does the direction: torsion free implies flat, or not flat implies not torsion free, hold even without the PID assumption?}
+
     The second assertion is a consequence of \Cref{lem:} \acom{Cite Joel's lemma}. 
     By \Cref{adthesis} \acom{Cite my thesis} it follows that $(L(0),L(s)) \in Z'\times Z''$. 
-    Since all maps are isomoprhisms the converse is automatic. 
+    Since all maps are isomorphisms the converse is automatic. 
 \end{proof}

### 2021-04-21 draft.tex
its possible joel edited some more

@@
 
-\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
-
-\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
-\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}
-\acom{Oh, sorry, I see it. Maybe because it was the start of a new paragraph I didn't connect `data' and `ranks' at first glance.}
+%\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
+
+%\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
+%\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}
+%\acom{Oh, sorry, I see it. Maybe because it was the start of a new paragraph I didn't connect `data' and `ranks' at first glance.}
 
@@
 Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. \acom{Out of place?} 
+\rcom{What is $\phi$?}
 

### 2021-04-21 draft.tex
still kind of a mess

@@
 % 
+We begin this section with some new notation.
+Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of (arbitrary) shape $\lambda$ and (arbitrary) weight $\mu$.
+Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
+% For the sake of making a definition, we momentarily put some letters of our alphabet in unexpected roles, and ask you to suspend your disbelief.
+Given an arbitrary tableau $t$ having weight $w$ and shape $s$, we denote by $s(i)$ (resp.\ $w(i)$) the shape (resp.\ the weight) of $t(i)$, the tableau got from $t$ by discarding all boxes of weight exceeding $i$.
+
+Given $\tau\in YT(\lambda)_\mu$ we denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$.
+
+Given $A \in M_N(\CC)$ we denote by 
+% $A\big|_{\CC^i}$ 
+$A\big|_{\CC^p}$ 
+the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}$ preserves $\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
+
+The variety $X(\tau)$ defined by
+% from $\tau\in YT(\lambda)_\mu$ by 
+\[
+X(\tau) = \overline{
+    \{
+        A \in  \overline{\OO}^\lambda\cap\TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
+    \}
+}    
+\]
+is called a generalized orbital variety.
+
+% 
+We need the following result from \cite{dthesis}.
+\begin{proposition}
+    \label{prop:dth}
+    (Part of which is a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison})
+    There is an isomorphism 
+    $\phi: \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \overline\Gr^\lambda\cap S^\mu_-$ 
+    and it is compatible with the bijection $YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ 
+    in the sense that the irreducible component $\phi(X(\tau))$ associated to the semistandard Young tableau $\tau$ is an open dense subset of the MV cycle whose Lusztig datum is equal to that of $\tau$.
+\end{proposition}
+
+% Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all
+% % but its first $i$ boxes
+% boxes of weight exceeding $i$. 
+% % If the tableau contains repeated entries then first means leftmost.
+% 
+\jcom{I don't think that you should mention this partial inverse here.
+I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
+\acom{Ok, I moved it.}
+
+% Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. \acom{Out of place?} 
+% \rcom{What is $\phi$?}
+% 
+% 
+% TODO: Not yet, that would be the algo stuff that we are holding off on 
+% In this section we explain how to determine the ideal of $Z'\ast_\AA Z''$ from the minimal pair $(\tau',\tau'')$ corresponding to $(n_\bullet(Z'),n_\bullet(Z''))$.
+% 
+% In particular, we prove that ``the generalized Spaltenstein map'' produces MV cycles. 
+% 
+% and recall the $\mu$-numeration of the standard basis of $\CC^N$. 
+% TODO: can't we do without it^^
+
+% 
 % In this section we demonstrate how to put the main results of this paper into practice.
 % 
-Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
+Now let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
 % 
@@
 $Z'\ast_\AA Z''$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
-% 
-Given $\lambda$ dominant effective and $\mu\le\lambda$ effective, let $YT(\lambda)_\mu$ denote the set of semistandard Young tableaux of shape $\lambda$ and weight $\mu$. 
-%
-
-We need the following result from \cite{dthesis}.
+\acom{Need to introduce LD.}
 \begin{proposition}
-    % Generalized orbital varieties are indexed by semistandard Young tableaux. 
-    There are bijections 
-    % Composing with the ordinary Mirkovi\'c--Vybornov isomorphism gives bijections 
-    \[
-        YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \irr \overline\Gr^\lambda\cap S^\mu_-\,. 
-    \]
-    Moreover, there is a \acom{partial?} inverse 
-    \[
-    \CC[N]\to \bigcup_{\lambda~\text{dominant}\atop \mu\le\lambda} YT(\lambda)_\mu \,. 
-    \]
-    % $$
-    % \begin{tikzcd}
-    %     YT(\lambda)_\mu \ar[r] \ar[d] & \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \ar[d] \\
-    %     GT(\lambda)_\mu \ar[r] & \irr \overline\Gr^\lambda\cap S^\mu_-
-    % \end{tikzcd}
-    % $$
-\end{proposition}
-% 
-\acom{Refer to Claxton--Tingley multisegments, Hong--Lee marignally large tableaux for comparison.}
-\jcom{I don't think that you should mention this partial inverse here.
-I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
-
-Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. \acom{Out of place?} 
-\rcom{What is $\phi$?}
-
-% 
-% 
-% TODO: Not yet, that would be the algo stuff that we are holding off on 
-% In this section we explain how to determine the ideal of $Z'\ast_\AA Z''$ from the minimal pair $(\tau',\tau'')$ corresponding to $(n_\bullet(Z'),n_\bullet(Z''))$.
-% 
-% In particular, we prove that ``the generalized Spaltenstein map'' produces MV cycles. 
-% 
-% and recall the $\mu$-numeration of the standard basis of $\CC^N$. 
-% TODO: can't we do without it^^
-Given $A \in M_N(\CC)$ we'll denote by $A\big|_{\CC^i}$ the restriction of $A$ to the subspace spanned by the first $i$ standard basis vectors.
-Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ the shape of $\tau'(i),\tau''(i)$ resp.\ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all but its first $i$ boxes.
-If the tableau contains repeated entries then first means leftmost.
-
-\begin{proposition}
-    Given $Z',Z''$, let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ be such that\dots If $s\ne 0$, then 
-    \[
-    \overline{\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{i}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\}} 
+    Given $b_{Z'},b_{Z''}\in\CC[N]$, let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$.
+Let $\mu = \mu' + \mu''$.
+If $s\ne 0$, then
+    \[
+    \overline{\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\}} 
     \cong Z'\times Z'' \,. %\mu_1 + \cdots + \mu_i
@@
 
+\acom{Fixed.}
+
 \begin{proof}
     Let $(A,s)$ be an element of the set on the left hand side, let $a\in\{0,s\}$ and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
-    Let $i\in \{1,\dots,N\}$ and write $m(i)$ for the maximum weight of a box in $\tau'(i)$ or $\tau''(i)$.
-
-    The the Jordan type of $A-a\big|_{E_a\cap\CC^{m(i)}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
+    % Let $i\in \{1,\dots,N\}$ and write $m(i)$ for the maximum weight of a box in $\tau'(i)$ or $\tau''(i)$.
+
+    The the Jordan type of $A-a\big|_{E_a\cap\CC^{|\mu(i)|}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
     Moreover, the lattice $(L,s)$ defined by $g(A)$ is such that $t-a$ has the same Jordan type on 
@@
         \label{eq:bcflat}
-        \cO_a^{m(i)} / L(a)\cap\cO_a^{m(i)} = \CC[t]^{m(i)}/L\cap\CC[t]^{m(i)}\otimes_{\CC[t]}\cO_a 
+        \cO_a^{|\mu(i)|} / L(a)\cap\cO_a^{|\mu(i)|} = \CC[t]^{|\mu(i)|}/L\cap\CC[t]^{|\mu(i)|}\otimes_{\CC[t]}\cO_a 
     \end{equation}
-    as does $(A-a\big|_{E_a\cap\CC^{m(i)}},s)$. 
+    as does $(A-a\big|_{E_a\cap\CC^{|\mu(i)|}},s)$. 
     \acom{Not sure when to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
     % 
-    \Cref{eq:bcflat} follows from e.g.\ \cite[Proposition~10.14]{atiyah2018introduction}:
-    \begin{quotation}
-        If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
-    \end{quotation}
-    applied to $A = \CC[t]$ and $\fa = (t)$.
+    % \Cref{eq:bcflat} follows from e.g.\ \cite[Proposition~10.14]{atiyah2018introduction}:
+    % \begin{quotation}
+    %     If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
+    % \end{quotation}
+    % applied to $A = \CC[t]$ and $\fa = (t)$. 
+    \Cref{eq:bcflat} follows from the fact that a module over a PID is flat if and only if it is torsion free, and $\cO_a$ is clearly torsion free.
 
@@
 
-    The second assertion is a consequence of \Cref{lem:} \acom{Cite Joel's lemma}. 
-    By \Cref{adthesis} \acom{Cite my thesis} it follows that $(L(0),L(s)) \in Z'\times Z''$. 
+    The second assertion is a consequence of \Cref{le:linalg}.
+    By \Cref{prop:dth}, it follows that $(L(0),L(s)) \in Z'\times Z''$. 
     Since all maps are isomorphisms the converse is automatic. 
@@
 
+\acom{How's here?}
+It may be helpful to know the map
+\[
+    \CC[N]\to \bigcup_{\lambda~\text{dominant}\atop \mu\le\lambda} YT(\lambda)_\mu 
+\]
+that we use to find our tableaux.
+    % $$
+    % \begin{tikzcd}
+    %     YT(\lambda)_\mu \ar[r] \ar[d] & \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \ar[d] \\
+    %     GT(\lambda)_\mu \ar[r] & \irr \overline\Gr^\lambda\cap S^\mu_-
+    % \end{tikzcd}
+    % $$
+\acom{Refer to Claxton--Tingley multisegments, Hong--Lee marignally large tableaux for comparison.}
 \begin{lemma}

### 2021-04-21 draft.tex
minor mtg edits plus typos from last upload

@@
     \{
-        A \in  \overline{\OO}^\lambda\cap\TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
+        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
     \}
@@
 \begin{proof}
-    Let $(A,s)$ be an element of the set on the left hand side, let $a\in\{0,s\}$ and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
+    Let $A$ be an element of the set on the left hand side, let $a\in\{0,s\}$ and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
     % Let $i\in \{1,\dots,N\}$ and write $m(i)$ for the maximum weight of a box in $\tau'(i)$ or $\tau''(i)$.
 
-    The the Jordan type of $A-a\big|_{E_a\cap\CC^{|\mu(i)|}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
-    Moreover, the lattice $(L,s)$ defined by $g(A)$ is such that $t-a$ has the same Jordan type on 
+    The the Jordan type of $(A-a)\big|_{E_a\cap\CC^{|\mu(i)|}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
+    Moreover, the lattice $L$ defined by $g(A)$ is such that $t-a$ has the same Jordan type on 
     % $\cO_a^{m(i)} / L(a)\cap\cO_a^{m(i)} = \CC[t]^{m(i)}/L\cap\CC[t]^{m(i)}\otimes_{\CC[t]}\cO_a $ 
@@
         \label{eq:bcflat}
-        \cO_a^{|\mu(i)|} / L(a)\cap\cO_a^{|\mu(i)|} = \CC[t]^{|\mu(i)|}/L\cap\CC[t]^{|\mu(i)|}\otimes_{\CC[t]}\cO_a 
+        \cO_a^{|\mu(i)|} / L(a)\cap\cO_a^{|\mu(i)|} = \left(\CC[t]^{|\mu(i)|}/L\cap\CC[t]^{|\mu(i)|}\right)\otimes_{\CC[t]}\cO_a 
     \end{equation}
-    as does $(A-a\big|_{E_a\cap\CC^{|\mu(i)|}},s)$. 
-    \acom{Not sure when to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
+    as does $(A-a)\big|_{E_a\cap\CC^{|\mu(i)|}}$. 
+    % \acom{Not sure when to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
     % 
@@
         i\left(
-            Z(\tau), Z'\circ Z''
+            X(\tau), X(\tau')\circ X(\tau'')
             % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
-        \right) [Z(\tau)]
+        \right) [Z(\tau)]\,. 
     \end{equation}
-    and the intersection multiplicities on the right are found by\dots\acom{To be completed.}
+    % and the intersection multiplicities on the right are found by\dots\acom{To be completed.}
 
@@
 %
+
+\acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
 \begin{conjecture}
@@
 We consider a generic matrix $X \in \UU^{\mu',\mu''}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda',\lambda''}_{0,s}$.
+\acom{Relations dictated by $\tau$.
+Can mostly refer the reader to the previous section for this background, now.}
 

### 2021-04-21 draft.tex
added labels

@@
 \section{Introduction}
+\label{s:intro}
 % 
@@
 \section{Players}
-
+\label{s:players}
 \subsection{Rings and discs}
-
+\label{ss:rings}
 Set $\cO = \cO_0 = \CC\xt$ and $\cK = \cK_0 = \CC\xT$.
@@
 Note that for $ s \in \CC $, we have an obvious isomorphisms  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$. 
-
+% 
 \subsection{Groups}
+\label{ss:groups}
+% 
 Let $H $ be an algebraic group over $ \CC $.  We will be interested in $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  
@@
 $G(K)$ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it 
-\acom{Add warning that we will also write $(t-s)^\mu$ for its image in 
+\acom{Add warning that we will also sometimes write $(t-s)^\mu$ for its image in 
 % $\GL_m(K)/\GL_m(R)$ 
@@
 
-\subsection{Affine Grassmannians} %  actors
+\subsection{Affine Grassmannians} 
+\label{ss:affgrs}
 % To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
@@
 \begin{definition}
+\label{def:gr}
      The \textbf{ordinary affine Grassmannian} $\Gr = G(\cK)/G(\cO)$.
@@
 \Gr = 
-    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_0^\times $} \right\} \,. 
+    \left\{ 
+        (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_0^\times $} 
+    \right\} \,. 
 $$
@@
 $$ 
-    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
-    $$
+\Gr = 
+    \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
+$$
+% 
 We obtain a lattice from a pair $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.  
@@
 \begin{definition}
+\label{def:grs}
  For any $ s \in \CC $, 
@@
 \Gr_s = 
-    \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} \right\}\,, \\
-    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
+    \left\{ (
+        V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} 
+    \right\}\,, \\
+\Gr_s = 
+    \left\{ 
+        L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} 
+    \right\} \,. 
 \end{gather*}
@@
 \begin{definition}
+\label{def:grth}
 The \textbf{thick affine Grassmannian} $\Grth = G(\Kinf)/G(\CC[t])$.
@@
 \Grth = 
-        \left\{ (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } \right\}\,, \\
-\Grth = \left\{ L : L \subset  \Kinf^m \text{ is a $\CC[t]$-lattice} \right\}\,.
+    \left\{ 
+        (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } 
+    \right\}\,, \\
+\Grth = 
+    \left\{ 
+        L : L \subset  \Kinf^m \text{ is a $\CC[t]$-lattice} 
+    \right\}\,.
     % \CC\xT[t^{-1}]^m 
@@
 \begin{definition} 
-    The two point \textbf{Beilinson--Drinfeld Grassmannian} 
-    $$\pi : \Grbd\to \AA$$ 
-    with one point fixed at 0, and the second point $s\in\AA$ varying.
+\label{def:bdgr}
+The two point \textbf{Beilinson--Drinfeld Grassmannian} $$\pi : \Grbd\to \AA$$ with one point fixed at 0, and the second point $s\in\AA$ varying.
 \end{definition}
+% 
 It is described in modular terms by 
@@
 $$
+% 
 The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
@@
 \Grbd = 
-\{ (L,s) :
-L \subset  \CC(t)^m\text{ is a $\CC[t]$-lattice trivial at any }a \ne 0, s \}\,, \\
+    \left\{ 
+        (L,s) : L \subset  \CC(t)^m\text{ is a $\CC[t]$-lattice trivial at any }a \ne 0, s 
+    \right\}\,, \\
 % , $L$ is 
 \Gr_{0,s} = 
-\{ L : L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m \text{ is a $\CC[t]$-lattice} \}\,.
+    \left\{ 
+        L : L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m \text{ is a $\CC[t]$-lattice} 
+    \right\}\,.
 \end{gather*}
@@
 \begin{definition} 
-The \textbf{positive parts} of $\Gr $ and $\Grth$, resp., are defined by 
-$$
-    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and }      
-    {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
-$$
+\label{def:grplus}
+The \textbf{positive parts} of $\Gr $ (resp.\ $\Grth$),  is defined by 
+\begin{gather*}
+    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \\
+    % \text{ and }      
+    (\text{resp.\ }{\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t]))\,. 
+\end{gather*}
 \end{definition}
+% 
 In modular terms, $\Gr^+$ (resp.\ ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow \Vtriv $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.\ over $ \PP$).
@@
 % lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.
-
+% 
 \subsection{Relations between different affine Grassmannians}
+\label{ss:relsbtwgrs}
+% 
 These different versions of the affine Grassmannian are related as follows.  
-
+% 
 \begin{enumerate}
@@
     % \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
-    \item 
+    \item \label{it:bd-th}
     %We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $.
@@
     Finally, it is given in lattice terms on the fibre over $s$ as the identity on the lattice $(L,s)\mapsto L$ and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
-    \item The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
+    \item \label{it:polyno-taylor}
+    The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
     \begin{equation*}
@@
     \jcom{I restated this again.  I think that it is simpler and more clear like this.  And I think that this is the fact that we end up using later.}
-% 
     % 
@@
     In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
-    \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$. 
+    \item \label{it:grs-gr} There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$. 
     % 
@@
 Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.
-Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (items (2) and (3) above), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
+Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (\cref{it:polyno-taylor,it:grs-gr} of \cref{ss:relsbtwgrs} preceding), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
+% TODO: cf https://tex.stackexchange.com/questions/256849/cleveref-change-behaviour-of-cref-to-use-the-abbreviated-form
 
@@
 
+\acom{Ah, sorry --- so do we introduce a even more general notion of $\ast_\AA$ for arbitrary flat families?
+Looking at Eisenbud's geoemtry of schemes (where flat iff tor-free actually shows up as Exercise II-33!) there does not seem to be anything quite like $\ast_\AA$ or $\circ$ defined.}
+% Cf. https://math.stackexchange.com/questions/1681680/flat-family-limit-of-intersection-vs-intersection-of-limits
+% 
+% 
+% Begin OLD
 %\acom{Question abt general fact: why is scheme-theoretic closure of product flat?} \jcom{See Hartshorne Proposition III.9.8.
@@
 That Proposition is a bit more general too..}
-
+% 
 % \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
 % \jcom{Now answered above.}
-
+% 
 %\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper and it is the most convenient way to define $\Gr^{\lambda_1, \lambda_2}$.
 I don't know what notation we should use.}
-
+% 
 %\acom{Roger and I have been using $\ast$ to denote fusion.
@@
 %\acom{Sure! It is quoted at the end, in \Cref{s:denouement} as an application. Addendum: for the numerical fusion I suggest simply $[Z_1][Z_2]$. This is what I will use in my talk. }
-
+% END OLD
+% 
 \subsection{Some subvarieties of affine Grassmannians}
+\label{ss:subgrs}
 Now fix effective dominant coweights $\lambda', \lambda'' $ of sizes $N',N''$  and their sum $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
@@
 \begin{definition}
+\label{def:sphschub}
     The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
-    $ \overline\Gr^\lambda = \bigcup_{\gamma \le \lambda} \Gr^{\gamma} $ a \textbf{spherical Schubert variety}.  
+    $ \overline\Gr^\lambda = \bigcup_{\gamma \le \lambda} \Gr^{\gamma} $ 
+    a \textbf{spherical Schubert variety}.  
 \end{definition}
     % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
-
     % 
 \begin{definition}
+\label{def:sphfus}
     The \textbf{fusion of two spherical Schubert varieties} 
@@
 Moreover, if $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.
-This open locus is a $ G(\CC[t])$-orbit
+\acom{reference \cref{it:grs-gr}?} This open locus is a $ G(\CC[t])$-orbit
 % .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
@@
 
-Because we consider effective dominant weight, the spherical Schubert varieties and their fusions lie in the positive part of the (thick) affine Grassmannian.
-
+Because we consider effective dominant coweights, the spherical Schubert varieties and their fusions lie in the positive part of the (thick) affine Grassmannian.
+% 
 \begin{lemma}
+\label{le:sphfusispos}
     The map $ \Gr_{0, \AA} \rightarrow \Grth$ restricts to a map $ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} \rightarrow \Grth^+$.
@@
 
-Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ of size $N',N''$ resp. such that $ \mu = \mu' + \mu'' $ is dominant. (We do not require $ \mu', \mu'' $ to be dominant.) 
+Now fix two effective (possibly non-dominant) coweights $ \mu', \mu''$ of sizes $N',N''$ such that $ \mu = \mu' + \mu'' $ is dominant. 
+% (We do not require $ \mu', \mu'' $ to be dominant.) 
 Using $ \mu, \mu', \mu''$, we define the following subschemes.
@@
 \begin{definition}
+\label{def:klslice}
     The \textbf{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
@@
 The lattice description of $ \cW_\mu $ is given in Lemma \ref{le:Wmu} below.
+\acom{First lattice description that doesn't come for free?}
+% 
 % \acom{que est-ce?} \jcom{It's not very relevant for this paper.
@@
 % 
-\begin{definition} The \textbf{semi-infinite orbit} 
+\begin{definition} 
+\label{def:inftyorbits}
+    The \textbf{semi-infinite orbit} 
 $$ S^\mu = N_-(\cK)t^\mu \subset \Gr $$ 
 and the \textbf{fusion of  semi-infinite orbits} 
-$$ S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''} \to \AA \,.$$  
+$$ 
+    S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''} \to \AA \,.
+$$  
 \end{definition}
@@
 \jcom{Still need a reference for why this central fibre is reduced.}
-\acom{Two definitions in one. Why does fusion of spherical schubs get preferential treatment \emoji{astonished}}
+\acom{Two definitions in one. Unlike for spherical schubs}
 
 \section{Matrices}
-
+\label{s:mats}
+% 
 \subsection{Adjoint orbits and their deformations}
+\label{ss:familiesofadjointorbits}
+% 
 We now consider some subvarieties of the space of $ N\times N$ matrices, again using the $ \lambda, \lambda', \lambda'', \mu, \mu', \mu''$ defined in the previous section.
@@
 
- For $ s \in \CC$ 
-    % and $\lambda\in P_{++}$
-    we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. 
-    % \acom{$s\in\AA$?}
-    %
+For $ s \in \CC$ we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
 
 \begin{definition}
+\label{def:Olam}
 The nilpotent orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.
-\end{definition}  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
+\end{definition}  
+% 
+Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
 % 
 \begin{definition}
+\label{def:Olamlam}
     For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
 \end{definition}  
+% 
 A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
+\acom{secret definition; add `a matrix is likewise said to have Jordan type...if it lies in'?}
 %
@@
 
-We recall that these adjoint orbit closures are given by rank conditions.  More precisely we have
+We recall that these adjoint orbit closures are given by rank conditions.  
+More precisely we have
 $$
@@
     \#\text{~boxes in first $i$ columns of }\lambda' \\
-    \rk (A-s)^i &\le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}
+    \rk (A-s)^i &\le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}\,. 
 \end{split}
@@
 %  
-\begin{proposition} \label{prop:adjoint}
-    There exists a flat family  $\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $s \in \AA$ is reduced and given by
-       $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ if $s \ne 0 $ and
-$        \overline{\OO}^\lambda $ if $ s = 0$.
+\begin{proposition} 
+    \label{prop:adjoint}
+    There exists a flat family $\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $s \in \AA$ is reduced and given by $\overline{\OO}^{\lambda', \lambda''}_{0,s}$ if $s \ne 0 $ and $\overline{\OO}^\lambda $ if $ s = 0$.
 \end{proposition}
@@
 Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
-\jcom{I don't know if it is really necessary to introduce this $ k$.
+% \jcom{I don't know if it is really necessary to introduce this $ k$.
 Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$?
@@
 The data $s_\bullet, p, k_\bullet$ is unique up to a permutation of $ \{1, \dots, k\}$.
-
+% 
 %\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
-
+% 
 %\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
@@
 By \cite[Corollary 2.2]{eisenbud1989rank}, the fibre of the flat family $ X_{r,W} $ over $ z$ is given by
-\begin{equation} \label{eq:ESfibre}
+\begin{equation} 
+    \label{eq:ESfibre}
     X_{r,z} = \{ A \in M_N(\CC) :\rk (A-s_j)^i\le r_{z,j}(i) \text{ for all } i , j \text{ as above}\}.
 \end{equation}
-
-We will now apply these ideas to prove our Proposition \ref{prop:adjoint}.
-
+% 
+We will now apply these ideas to prove our \Cref{prop:adjoint}.
+% 
 \begin{proof}
-
+% 
 %\begin{lemma}
@@
 %Recall that $\lambda' + \lambda'' = \lambda$ is a partition of $N$. 
-
+% 
 Define 
-$$r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,.$$
+$$
+    r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,.
+$$
 It is easy to see that this is a rank function, with $ k = \lambda_1$, the number of columns of $ \lambda$.
@@
 
-For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of $ r = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.  We also see that
+For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of $ r = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
+We also see that
 \begin{equation} 
@@
 On the other hand, for $z(0)$, we get that $ r = 1$ and that 
-\begin{equation} \label{eq:rcol2}
-r_{z(0),1}(i) = r(i) = 
- N - 
-     \#\text{~boxes in first $i$ columns of }\lambda\,. 
+\begin{equation} 
+\label{eq:rcol2}
+    r_{z(0),1}(i) = 
+    r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,. 
 \end{equation}
 %\jcom{Someone should check that I chose the notation correctly to make this work out.}
-
+% 
 %\acom{What do we mean by equalities in $z(s)$ reproduce $p$?
@@
 For a minute I thought it was actually fine, but what we have is: $r_{z(s),j}(i) = N - (\#\text{boxes in cols }1,\dots,p(k_j + i) - \#\text{boxes in cols }1,\dots,p(k_j))$ and what we want is $\dots (\#\text{boxes in cols }p(1),\dots,p(k_j + i) - \#\text{boxes in cols }p(1),\dots,p(k_j + i))$ right?}
-
+% 
 %\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.
@@
 %\acom{\emoji{+1}}
-
-% 
-Let $ W = \{ z(s) : s \in \CC \}$.  Combining \Cref{eq:ranks,eq:ESfibre,eq:rcols,eq:rcol2} 
+% 
+Let $ W = \{ z(s) : s \in \CC \}$. Combining \Cref{eq:ranks,eq:ESfibre,eq:rcols,eq:rcol2},
 % (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) 
@@
 \end{proof}
-
+% 
+% 
 % The family of adjoint orbits $  whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose \acom{Claim:} fibre over 0 is $\overline{\OO}^\lambda$ (a consequence of Eisenbud and Salten's characterization of ``rank varieties'' as proved in \Cref{cor:es}).
 \acom{TODO: make into definition to be x-referenced in proof of description of fibres}
-
+% 
 % \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
@@
 In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}
-
+% 
 % TODO: delete commented out remark and subcomment!
@@
 %for $i = 1,\dots,\lambda_2$. Then $gJg^{-1} = A$. For the next part we introduce the notation $A_{\lambda_1+\lambda_2}$ for this matrix $A$. 
-
+% 
 %Now let $\lambda_1,\lambda_2$ be arbitrary. Clearly $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to 
@@
 Altogether $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to $\bigoplus_{i = 1}^m A_{\lambda_{1,i}+\lambda_{2,i}}$ and this latter matrix specializes to the Jordan normal form $J_{0,\lambda_1 + \lambda_2}$ at $s=0$.
-
+% 
 % By Tanisaki $A\in \OO^\lambda$ iff the coefficients of $z^m$ in $k\times k$ minors of $zI - A$ for any $m\le p_\lambda(k) - 1$ and for any $k = 1\dots |\lambda|$ vanish.
@@
 So $p_\lambda(k) = \#$ boxes in the last $k$ rows of $\lambda$.
-
+% 
 % In particular this result describes the ideal $I_i$ of $N_i\times N_i$ matrices $A_i$ such that $A_i - \delta_{i,2}s$ is conjugate to $J_{\delta_{i,2} s, \lambda_i}$ for $i = 1,2$.
@@
 Let $g$ be such that $g(J_{0,\lambda_1} \oplus J_{s,\lambda_2})g^{-1} = \bigoplus_{i = 1}^m A_{\lambda_{1,i}+\lambda_{2,i}}$.
-
+% 
 % If we apply the change of basis $g$ to the ideal $I=I_1 + I_2$ and set $s = 0$ (if possible) do we recover the ideal of $\OO^{\lambda_1 + \lambda_2}$? Let $A^g = g(A_1 \oplus A_2) g^{-1}$...
 % \end{remark}
-
+% 
 \subsection{The Mirkovic--Vybornov slice}
+\label{ss:mvyslice} 
 % 
@@
 \[
-        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
+    \left[
+        \begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
@@
 \[
-        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
+    \left[
+        \begin{BMAT}(e){ccc;cc}{ccc;cc} 
         0 & 1 & 0 & 0 & 0\\
@@
             -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
-            \end{array}\right]\,. 
+        \end{array}
+        \right]\,. 
 \]
@@
 \[
-        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
+    \left[
+        \begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
         0 & 1 & 0 & 0 & 0 & 0\\
@@
         0 & 0 & 0 & 0 & 0 & s
-            \end{BMAT}\right] \,.    % \in \UU_{0,s}^{(1,1,0),(2,1,1)}
+        \end{BMAT}
+    \right] \,.   
+    % \in \UU_{0,s}^{(1,1,0),(2,1,1)}
 \]
@@
 % \acom{And, sorry, ignore my other comment; it's the same $\CC$ (or $\AA$) nothing to distinguish.}
-
+% 
 % TODO: place this better? 
@@
 \label{s:exposition}
-
+% 
 Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
@@
 
-\section{Rising Action} % Problem
-
-\begin{lemma} \label{le:Grl1l2}
+\section{Rising Action}
+\label{s:theproblem}
+\begin{lemma} 
+\label{le:Grl1l2}
     Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
@@
 \end{lemma}
-
+% 
 \begin{proof}
@@
 
-\begin{lemma} \label{le:linalg}
+\begin{lemma} 
+\label{le:linalg} % aka solution 
 Let $ V $ be a $ \CC[t]$-module which is finite-dimensional as a $ \CC$ vector space.  For any  $ a \in \CC$, the map
-    $$ V  \rightarrow V \otimes_{\CC[t]} \cO_a$$
+$$ 
+    V  \rightarrow V \otimes_{\CC[t]} \cO_a
+$$
 restricts to an isomorphism between the generalized $ a $-eigenspace of $ t $ and $ V \otimes_{\CC[t]} \cO_a$
-
 \end{lemma}
-
+% 
 \begin{proof}
@@
 \end{proof}
-
-\begin{lemma} \label{le:Wmu}
+% 
+\begin{lemma} 
+\label{le:Wmu}
 Let $ L \in \Grth^+$.  The following are equivalent:
@@
 Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ \CC[t]^m/L$. 
-    % \acom{Change $L_0$}
 \end{lemma}
@@
     Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(  t^k e_i : 0 \le k < \mu_i, 1 \le i \le m) + L$. 
-
+    % 
     % \rcom{Preimage of $\beta_\mu$}  
@@
     % \acom{I guess that this is the ``$\mu$-numeration'' of the standard basis of $\CC^N$ that I commented out.}
-
+    % 
     This follows immediately from (iii).
@@
 \begin{lemma}
+\label{le:inftyfusiskl} % as in lands in KL slice 
     Let $\mu',\mu'' \in P$ and $\mu = \mu' + \mu''$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
@@
 \end{proof}
-
+% 
 \section{Climax}
+\label{s:climax}
 Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.  Note that $g(A)t^{-\mu} \in G_1(\Oinf)$.
@@
 % 
-\begin{theorem} \label{th:TmuWmu}
+\begin{theorem} 
+\label{th:TmuWmu}
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
@@
 
-\begin{theorem} \label{th:OGrl}
+\begin{theorem} 
+\label{th:OGrl}
 There is an isomorphism
-    $$\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu $$
+$$
+    \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu \cong \overline\Gr^{\lambda', \lambda''}_{0,\AA} \cap \cW_\mu 
+$$
 given by $ (A,s) \mapsto (g(A)\CC[t]^m, s)$.
@@
 \begin{proof}
-Since we already have the isomorphism from Theorem \ref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, 
+Since we already have the isomorphism from \Cref{th:TmuWmu}, it suffices to show that for any $ A \in \TT_\mu$, 
 $$ 
@@
 $$
-This follows immediately from Lemma \ref{le:Grl1l2}.
+This follows immediately from \Cref{le:Grl1l2}.
 \end{proof}
@@
 \begin{theorem}
-    The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
+\label{th:OTGrW}
+The isomorphism from \Cref{th:OGrl} restricts to an isomorphism
 $$ 
@@
 \end{theorem}
-
+% 
 %\jcom{I was thinking about the proof of this result.
@@
 %\acom{But I am also curious about the attracting set approach.}
-
+% 
 \begin{proof}
@@
 Moreover, since $ \mu $ is dominant, we know that 
-$$t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.$$
+$$
+    t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.
+$$
 % $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
@@
 \end{proof}
-
+% 
 \jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
@@
 In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
-
+% 
 %\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
-
+% 
 %\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$.
@@
 This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
-
+% 
 \begin{comment}

### 2021-04-24 draft.tex
Short section on cluster algebras.

--- 2021-04-21 draft.tex
@@
 % 
-
+\section{Cluster Algebras}
+One of the main motivations for this paper is computing certain fusion products that are associated to exchange relations in the cluster algebra structure of $\CC[N]$.
+
+A basis of $\CC[N]$, called the dual semicanonical basis, was originally constructed in \cite{lusztig2000semicanonical} while a cluster algebra structure for $\CC[N]$ was shown in \cite{berenstein2005cluster3} and \cite{geiss2007initial}.
+A natural question was whether the cluster monomials were elements of the dual semicanonical basis, proved in the positive in \cite{geiss2006rigid}.
+
+Another basis for $\CC[N]$ was constructed in \cite{mirkovic2007geometric} called the MV basis.
+This basis is indexed by the MV cycles and the product of basis elements corresponds to the fusion product of the associated MV cycles.
+While this basis is different from the dual semicanonical basis, as shown in \cite{baumann2019mirkovic}, they seemed to share a lot of common elements, such as various cluster variables, which led to the following conjecture.
+
+\begin{conjecture}
+    The cluster monomials of $\CC[N]$ are elements of the MV basis.
+\end{conjecture}
+
+It has been shown in \cite{kato2011polytopal} that for certain initial seeds $(x_1, \dots, x_r)$, each $x_i$ is in the MV basis.
+Then to show every cluster variable is in the MV basis, it suffices to show that for a mutable variable $x_i$, its mutation $x_i^*$ is also in the MV basis.
+The exchange relation corresponding to $x_i$ and $x_i^*$ is of the form
+$$x_ix_i^* = x_+ + x_-$$
+where $x_+$ and $x_-$ are monomials in the $x_j,j\neq i$.
+Let $Z_i$, $Z_+$, and $Z_-$ be the corresponding MV cycles for $x_i$, $x_+$, and $x_-$, respectively.
+If we are able to find an MV cycle $Z_i^*$ such that
+$$Z_i \circ Z_i^* = Z_+ \cup Z_-,$$
+then this means $x_i^*$ is in the MV basis with associated MV cycle $Z_i^*$. In Section \ref{s:denouement}, we present examples showcasing this is indeed true for type $A_3$. 
 \section{Denouement}

### 2021-04-26 draft.tex
proof amended

@@
 \usepackage{emoji}
-
+% TODO: The matrix is lower triangular and the lower-triangular matrix is
 % \setemojifont{Apple Color Emoji}
@@
 These isomorphisms glue together to a projection map
-$$
+\begin{equation}
+\label{eq:mvitau}
     \tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
-$$ 
+\end{equation}
 (This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
@@
 \label{th:OTGrW}
-The isomorphism from \Cref{th:OGrl} restricts to an isomorphism
+The isomorphism from \Cref{th:OGrl} \acom{should ``Theorem'' etc.\ be capitalized when it appears in the middle of a sentence?}
+restricts to an isomorphism
 $$ 
@@
 
-Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu', \mu''}_{0,\AA} $.
+Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu', \mu''}_{0,\AA} $. \acom{not $g(A)\CC[t]^m$}
 
 On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.
-
-On the other hand, if $ (g(A), s) \in S^{\mu', \mu''}_{0,\AA}$, then we can write 
+\acom{not $g(A)\CC[t]^m$}
+
+On the other hand, if $ (g(A), s) \in S^{\mu', \mu''}_{0,\AA}$, \acom{not $g(A)\CC[t]^m$} then we can write 
 $$
@@
 Hence $g \in G_1(\cO_\infty)$.}
-
+% 
+Restricting to the zero fibre we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}.
+\acom{Technically the zero fibre is comprised of $\CC[t]$ lattices and we need to `specialize' to end up in the ordinary $\Gr$.}
+% 
+\begin{corollary}
+    \label{cor:mvy}
+    $\OO^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
+\end{corollary}
 \section{Falling Action} % Resolution
@@
 \]
-is called a generalized orbital variety.
-
-% 
-We need the following result from \cite{dthesis}.
+is called a \textbf{generalized orbital variety}. 
+% 
+It inherits a crystal datum called a \textbf{Lusztig datum} from its tableau. 
+\acom{Cite Joel? Hide dependence on reduced expression?}
+The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is got from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
+$$
+n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
+$$
+for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
+% 
+For example, if 
+\[
+    \tau = \young(1112,23) 
+\]
+then
+\begin{gather*}
+%    \text{if } \tau = \young(1112,23) \text{ then } 
+\gt(\tau) = \begin{matrix}
+       3 \\
+       4 & 1 \\ 
+       4 & 2 & 0 
+   \end{matrix} \text{ and }
+   n_\bullet(\tau) = (1,0,1)\,. 
+\end{gather*}
+% 
+% TODO
+% \begin{theorem}(CITE KAM07)
+%     Taking $\vi$-Luszig datum is a bijection $P\to\NN^{\ell}$. 
+% \end{theorem}
+% 
+We need the following two results from \cite{dthesis}.
+\begin{proposition}
+    \label{pr:govsasirrecs}
+    The decomposition
+    \begin{equation*}
+        % \label{eq:govsasirrecs}
+        \overline{\OO}^\lambda\cap\TT_\mu\cap\n = \bigsqcup_{\tau\in YT(\lambda)_\mu} X(\tau)
+    \end{equation*}
+    is\dots
+\end{proposition}
+% 
+Denote by $Z(\tau)\subset\Gr$ the image of $X(\tau)$ under the isomorphism of \Cref{cor:mvy}. 
+\acom{Still need Lusztig data of MV cycles; with it $B(\infty)$, stable vs ordinary, etc?}
+% 
 \begin{proposition}
     \label{prop:dth}
-    (Part of which is a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison})
-    There is an isomorphism 
-    $\phi: \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \overline\Gr^\lambda\cap S^\mu_-$ 
-    and it is compatible with the bijection $YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ 
-    in the sense that the irreducible component $\phi(X(\tau))$ associated to the semistandard Young tableau $\tau$ is an open dense subset of the MV cycle whose Lusztig datum is equal to that of $\tau$.
+    % The isomorphism 
+    % $\phi: \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \overline\Gr^\lambda\cap S^\mu_-$ 
+    % is compatible with the decomposition of \Cref{pr:govsasirrecs}
+    % the bijection $YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ 
+    % in the sense that 
+    $Z(\tau)$ is dense in the MV cycle whose Lusztig datum is $n_\bullet(\tau)$. 
 \end{proposition}
-
 % Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all
@@
 % 
-Now let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
-% 
-In this part we prove that 
+% 
+In this part we prove that the product 
 % the ideal of 
-$Z'\ast_\AA Z''$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
-\acom{Need to introduce LD.}
+% $Z'\ast_\AA Z''$ 
+$b_{Z'}b_{Z''}\in\CC[N]$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
+% 
+To begin, let $\tau',\tau''$ be given and let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
+%
+
+\acom{We may want to introduce $\ast_s$ in general. For now we make a definition.} Given $s\in\CC$, let 
+\begin{equation*}
+    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,,
+\end{equation*}
+% 
+and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
+If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$ \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}.
+Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing.
+May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s..
+which is ok, as in not a loss of generality.
+Still..}
 \begin{proposition}
-    Given $b_{Z'},b_{Z''}\in\CC[N]$, let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$.
-Let $\mu = \mu' + \mu''$.
-If $s\ne 0$, then
-    \[
-    \overline{\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\}} 
-    \cong Z'\times Z'' \,. %\mu_1 + \cdots + \mu_i
-    % = Z(\tau')\times Z(\tau'')\,. 
-    \]
+    % Given $b_{Z'},b_{Z''}\in\CC[N]$, 
+    % Let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ 
+    % be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$. 
+    % and set $\mu = \mu' + \mu''$. If $s\ne 0$, then 
+    The image of $X(\tau')\ast_s X(\tau'')$ under the isomorphism of \Cref{th:OTGrW} is dense in $Z(\tau')\ast_s Z(\tau'')$. 
+    % \[
+    % \overline{\phi(X(\tau',\tau''))} 
+    % = Z'\ast_s Z'' \,. 
+    % \]
 \end{proposition}
 % 
-\jcom{Do you want the ``blocky'' or ``boxy'' description here?
+% \jcom{Do you want the ``blocky'' or ``boxy'' description here?
 I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$?
@@
 
-\acom{Fixed.}
+% \acom{Fixed.}
 
 \begin{proof}
-    Let $A$ be an element of the set on the left hand side, let $a\in\{0,s\}$ and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
-    % Let $i\in \{1,\dots,N\}$ and write $m(i)$ for the maximum weight of a box in $\tau'(i)$ or $\tau''(i)$.
-
-    The the Jordan type of $(A-a)\big|_{E_a\cap\CC^{|\mu(i)|}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
-    Moreover, the lattice $L$ defined by $g(A)$ is such that $t-a$ has the same Jordan type on 
-    % $\cO_a^{m(i)} / L(a)\cap\cO_a^{m(i)} = \CC[t]^{m(i)}/L\cap\CC[t]^{m(i)}\otimes_{\CC[t]}\cO_a $ 
-    \begin{equation}
-        \label{eq:bcflat}
-        \cO_a^{|\mu(i)|} / L(a)\cap\cO_a^{|\mu(i)|} = \left(\CC[t]^{|\mu(i)|}/L\cap\CC[t]^{|\mu(i)|}\right)\otimes_{\CC[t]}\cO_a 
-    \end{equation}
-    as does $(A-a)\big|_{E_a\cap\CC^{|\mu(i)|}}$. 
-    % \acom{Not sure when to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
-    % 
-    % \Cref{eq:bcflat} follows from e.g.\ \cite[Proposition~10.14]{atiyah2018introduction}:
-    % \begin{quotation}
-    %     If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
-    % \end{quotation}
-    % applied to $A = \CC[t]$ and $\fa = (t)$. 
-    \Cref{eq:bcflat} follows from the fact that a module over a PID is flat if and only if it is torsion free, and $\cO_a$ is clearly torsion free.
+    % The diagram 
+    % \[
+    % \begin{tikzcd}
+    %     \TT_{\mu(i)} \ar[r] \ar[d] & B \ar[d] \\ 
+    %     \TT_{\mu(i-1)} \ar[r] & ?? 
+    % \end{tikzcd}
+    % \]
+    % commutes.
+    Let $i = 1,\dots, m$, let $a = 0,s$, and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
+    Then 
+    \begin{enumerate}
+        \item $(g(A)\CC[t]^m\cap\CC[t]^i,s) = g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$
+        \item \label{eq:twoingredients} $g((A-a)\big|_{E_a \cap \CC^{|\mu(i)|}},a) = \left(g(A) \CC[t]^m \otimes_{\CC[t]}\cO_a \right)\cap \cO_a^i$
+        % g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i \otimes_{\CC[t]} \cO_a $
+    \end{enumerate}
+    \Cref{eq:twoingredients} follows requries \Cref{le:linalg} and the fact that a module over a PID is flat if and only if it is torsion free. % and $\cO_a$ is clearly torsion free
 
@@
 
-    The second assertion is a consequence of \Cref{le:linalg}.
-    By \Cref{prop:dth}, it follows that $(L(0),L(s)) \in Z'\times Z''$. 
-    Since all maps are isomorphisms the converse is automatic. 
+    % In particular, we see that 
+    % \[
+    % Z(\tau) = \{L \in \Gr: L\cap\CC[t]^i \in \Gr^{\lambda(i)} \text{ for } i = 1,\dots, m\}\,.     
+    % \]
 \end{proof}

### 2021-04-28 draft.tex
joels changes followed by annes scribbles

@@
 % is
-are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
-% 
-A coweight $ \mu = (\mu_1, \dots, \mu_m)$ is called \textbf{effective}, if $ \mu_j \ge 0 $ for all $ j$.
+are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) \in \ZZ^m $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
+% 
+A coweight $ \mu = (\mu_1, \dots, \mu_m) \in \ZZ^m$ is called \textbf{effective}, if $ \mu_j \ge 0 $ for all $ j$.
 % We also need the notion of effective dominant coweight, 
@@
 % \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
-For example, since $t-s $ is invertible in $ \cO_a $ if $ a \ne s $, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$. 
+For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$, since $ t-s $ is invertible in $ \cO_a$. 
 % \acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}
@@
 \label{def:grplus}
-The \textbf{positive parts} of $\Gr $ (resp.\ $\Grth$),  is defined by 
+The \textbf{positive parts} of $\Gr $ and $\Grth$,  are defined by 
 \begin{gather*}
@@
     % \text{ and }      
-    (\text{resp.\ }{\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t]))\,. 
+    {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
 \end{gather*}
@@
 
-In lattice terms, $ \Gr^+$ (resp.\ ${\Grth}^+$) contains those lattices $L$ which are contained in the appropriate standard lattice. 
+In lattice terms, $ \Gr^+$ (resp.\ ${\Grth}^+$) contains those lattices $L$ which are contained in $\cO^m$ (resp.\ $\CC[t]^m$).
 % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
@@
     In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
+
     \item \label{it:grs-gr} There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
+
+    Combining with the above point, we obtain an isomorphism
+    $$
+    \tau_s : \Gr_{0,s} \rightarrow \Gr \times \Gr 
+    $$
     % 
@@
 
+\jcom{I moved the ``composition'' of 2 and 3 into 3 and named it $ \tau_s$, since we will use it later quite a bit.
+I'm not that happy with the layout of this section, so feel free to reorganize it (maybe into Propositions?)}
+
 \subsection{The fusion construction}
@@
 Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.
-Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (\cref{it:polyno-taylor,it:grs-gr} of \cref{ss:relsbtwgrs} preceding), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
+
+%Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (\cref{it:polyno-taylor,it:grs-gr} of \cref{ss:relsbtwgrs} preceding), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
 % TODO: cf https://tex.stackexchange.com/questions/256849/cleveref-change-behaviour-of-cref-to-use-the-abbreviated-form
 
-These isomorphisms glue together to a projection map
+These isomorphisms $ \tau_s $ defined above glue together to a projection map
 \begin{equation}
@@
 We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.
-Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
+By construction, this is a flat family over $ \AA$.
+We write $X_1 \ast_s X_2 $ scheme-theoretic fibre over a point $ s \in \AA$.
+
+If $ s \ne 0$, then the map $ \tau_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.
+
+On the other hand, the fibre $ X_1 \ast_0 X_2$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
+We call this subscheme the \textbf{fusion} of $ X_1 $ and $ X_2$.
+
+\jcom{I rewrote this to introduce the $ X_1 \ast_s X_2 $ notation that we need for later.
+In doing so, $ X_1 \circ X_2 $ became obsolete, since we now have $ X_1 \ast_0 X_2$, but if you like we could just define $X_1 \circ X_2 = X_1 \ast_0 X_2 $.}
+
+%Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
 % $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
-\begin{equation*}
+%\begin{equation*}
     % \label{deservesdisplay}
-    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
-\end{equation*}
-which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
-% 
-By construction, 
+%    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
+%\end{equation*}
+%which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  
+% 
+%By construction, 
 % \acom{technically, there were two given above, so *these* constructions?} 
-$X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
+%$X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
 
@@
 Looking at Eisenbud's geoemtry of schemes (where flat iff tor-free actually shows up as Exercise II-33!) there does not seem to be anything quite like $\ast_\AA$ or $\circ$ defined.}
+
+\jcom{I'm not sure how a general notion would be defined.  In our case, we are using the special fact that the general fibre is a product.}
+
+\acom{I mean exactly in the case of this special fact, which is not special to the BD Gr.}
+
 % Cf. https://math.stackexchange.com/questions/1681680/flat-family-limit-of-intersection-vs-intersection-of-limits
@@
 %\acom{should we also subsript this family with $0,\AA$?}
-By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ of $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA}$ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.
+%By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ of $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA}$ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.
 % By \cite[Proposition 3.1.14]{zhu2016introduction},
@@
 % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
-Over $s=0$ the fibre is reduced and equal to $ \overline{\Gr}^{\lambda' + \lambda''}$ by 
-% a theorem of Zhu 
-\cite[Proposition 3.1.14]{zhu2016introduction}.
+By a theorem of Zhu 
+\cite[Proposition 3.1.14]{zhu2016introduction}, $ \overline{\Gr}^{\lambda'} \ast_0 \overline{\Gr}^{\lambda''} $ is reduced and equal to  $ \overline{\Gr}^{\lambda' + \lambda''}$.
 
@@
 \end{definition}
-Again, since $\mu $ is effective, we see that $ \cW_\mu $ lies inside the positive thick Grassmannian $ \Grth^+$.
 %
@@
 In modular terms, $\cW_\mu$ corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
-The lattice description of $ \cW_\mu $ is given in Lemma \ref{le:Wmu} below.
+The lattice description of $ \cW_\mu \cap \Grth$ is given in Lemma \ref{le:Wmu} below.
 \acom{First lattice description that doesn't come for free?}
@@
 % 
-\jcom{Still need a reference for why this central fibre is reduced.}
+\jcom{I realized that this is not correct.  We can't just take the fusion here since we don't want to get the closure of these guys.  I will think about this further.}
 \acom{Two definitions in one. Unlike for spherical schubs}
@@
 % 
-A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
+These matrices and the linear operators they represent will be said to have Jordan type $((0,\lambda'), (s,\lambda''))$.
+
+%A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
 \acom{secret definition; add `a matrix is likewise said to have Jordan type...if it lies in'?}
+\jcom{Is that better?}
+\acom{Yay.}
 %
@@
 The closure $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ is $\bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.     
+\jcom{Do we need this?}
+\acom{No I guess we haven't used it yet. Maybe in Proposition 5..}
 
@@
 %
+
+The following fact seems to be well-known but we could not find this exact statement in the literature.
 \begin{proposition} 
@@
 Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities.
-There exist $ 0=k_0< k_1< \dots < k_r = k $, distinct $ s_1, \dots, s_r \in \CC$ and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
+There exist $ 0=k_0< k_1< \dots < k_\ell = k $, distinct $ s_1, \dots, s_\ell \in \CC$ and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
 $$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,.
-$$ We require that $ p $ is of minimal length, given the choice of $ s_1, \dots, s_r$.
-The data $s_\bullet, p, k_\bullet$ is unique up to a permutation of $ \{1, \dots, k\}$.
+$$ We require that $ p $ is of minimal length, given the choice of $ s_1, \dots, s_\ell$.
+The data $s_\bullet, p, k_\bullet$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
 % 
@@
 
-Next for $ j = 1, \dots r $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
+Next for $ j = 1, \dots \ell $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
 $$
@@
 \jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
-\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
-\acom{\emoji{+1}}
+%\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
+%\acom{\emoji{+1}}
 
@@
 
-For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of $ r = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
+For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of $ \ell = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
 We also see that
@@
 \label{th:OTGrW}
-The isomorphism from \Cref{th:OGrl} \acom{should ``Theorem'' etc.\ be capitalized when it appears in the middle of a sentence?}
+The isomorphism from \Cref{th:OGrl} 
+% \acom{should ``Theorem'' etc.\ be capitalized when it appears in the middle of a sentence?} Yup.
 restricts to an isomorphism
@@
 
-Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $ if and only if $ (g(A),s) \in S^{\mu', \mu''}_{0,\AA} $. \acom{not $g(A)\CC[t]^m$}
+Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $ if and only if $ (g(A)\CC[t]^m,s) \in S^{\mu', \mu''}_{0,\AA} $. 
+%\acom{not $g(A)\CC[t]^m$}
 
@@
 \acom{not $g(A)\CC[t]^m$}
-
-On the other hand, if $ (g(A), s) \in S^{\mu', \mu''}_{0,\AA}$, \acom{not $g(A)\CC[t]^m$} then we can write 
+\jcom{This one isn't a point in $ \Gr$, the others I changed.}
+
+On the other hand, if $ (g(A)\CC[t]^m, s) \in S^{\mu', \mu''}_{0,\AA}$, then we can write 
 $$
@@
     \label{cor:mvy}
-    $\OO^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
+    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
 \end{corollary}
+
 \section{Falling Action} % Resolution
@@
 % 
-Denote by $Z(\tau)\subset\Gr$ the image of $X(\tau)$ under the isomorphism of \Cref{cor:mvy}. 
+Denote by $Z(\tau)\subset\Gr$ the closure of the image of $X(\tau)$ under the isomorphism of \Cref{cor:mvy}. 
 \acom{Still need Lusztig data of MV cycles; with it $B(\infty)$, stable vs ordinary, etc?}
+\jcom{Do you want $ Z(\tau)$ to be the closure?}
+\acom{Sure}
+
 % 
@@
 \end{proposition}
+\acom{We would like to use the action of $W$ which gives isomorphisms
+$Gr^\lambda \cap Gr_\mu \cap S^\mu \cong Gr^\lambda \cap Gr_{w\mu} \cap S^{w\mu}$ to generalize to non-dominant $\mu$.
+But the Lusztig datum of $\tau\in YT(\lambda)_\mu$ may not appear as the Lusztig datum of any element of $YT(\lambda)_{w\mu}$..}
+% This gives us the dimension of Gr^\lambda \cap Gr_\mu \cap S^\mu.
+\begin{lemma}
+Alternate description. Works for non-dominant $\mu$. 
+$$
+Z(\tau) = \{
+L\in\Gr : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\cap S^{\mu(i)}\text{ for all }i \}
+$$
+is an MV cycle. 
+\end{lemma}
 % Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all
@@
 
-\acom{We may want to introduce $\ast_s$ in general. For now we make a definition.} Given $s\in\CC$, let 
+% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.} 
+Given $s\in\CC$, let 
 \begin{equation*}
-    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,,
+    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
 \end{equation*}
 % 
-and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
-If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$ \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}.
+% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
+% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
+% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}.
 Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing.
@@
 Still..}
+
+% \jcom{Now that we have $ \ast_s$ defined in the fusion section, we can refer to that here.}
+
 \begin{proposition}
@@
 \begin{proof}
-    % The diagram 
+    % We wish to apply \Cref{prop:dth}. Nope
+    % We will also need \Cref{le:Grl1l2}. Nope 
+    % Consider the following diagram.
     % \[
     % \begin{tikzcd}
-    %     \TT_{\mu(i)} \ar[r] \ar[d] & B \ar[d] \\ 
-    %     \TT_{\mu(i-1)} \ar[r] & ?? 
+    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
+    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
     % \end{tikzcd}
     % \]
-    % commutes.
-    Let $i = 1,\dots, m$, let $a = 0,s$, and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
-    Then 
-    \begin{enumerate}
-        \item $(g(A)\CC[t]^m\cap\CC[t]^i,s) = g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$
-        \item \label{eq:twoingredients} $g((A-a)\big|_{E_a \cap \CC^{|\mu(i)|}},a) = \left(g(A) \CC[t]^m \otimes_{\CC[t]}\cO_a \right)\cap \cO_a^i$
-        % g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i \otimes_{\CC[t]} \cO_a $
-    \end{enumerate}
-    \Cref{eq:twoingredients} follows requries \Cref{le:linalg} and the fact that a module over a PID is flat if and only if it is torsion free. % and $\cO_a$ is clearly torsion free
+    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
+    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
+    % % 
+    Let $A\in X(\tau')\ast_s X(\tau'')$, let $i = 1,\dots, m$.  
+    % Denote by 
+    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
+    Clearly, the lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
+    $$
+    L\cap \CC[t]^i = l. 
+    $$
+    By definition of $X'\ast_s X''$,  $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$ and lies in $\UU^{\mu'(i),\mu''(i)}_{0,s}$.
+So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}\cap S^{\mu'(i),\mu''(i)}_{0,s}$ which fits the alternate description of $Z(\tau)$..
+
+    \acom{..assuming $\tau_s$ identifies these intersections with products of intersections.}
+
+    \jcom{I removed the $, s)$ from 1.  I don't understand the statement of 2.}
+    \acom{Yup, me neither. Getting there..}
 
@@
 
-    \acom{Here $A$ is $\CC[t]$ and $M = \cO$ right? Better, agreed. Does the direction: torsion free implies flat, or not flat implies not torsion free, hold even without the PID assumption?}
+    \acom{Here $A$ is $\CC[t]$ and $M = \cO$ right?
+Better, agreed.
+Does the direction: torsion free implies flat, or not flat implies not torsion free, hold even without the PID assumption?
+This belongs way back in Joel's Lemma}
 
@@
 \end{proof}
+
+\acom{We compute zero fibres of $\ast_s$ by applying the results of \Cref{dthesis}..}
 

### 2021-04-28 draft.tex
Fixed a typo.

@@
 By construction, this is a flat family over $ \AA$.
-We write $X_1 \ast_s X_2 $ scheme-theoretic fibre over a point $ s \in \AA$.
+We write $X_1 \ast_s X_2 $ for the scheme-theoretic fibre over a point $ s \in \AA$.
 
@@
 % 
+\rcom{I don't think we introduced $\CC[N]$ or the elements $b_Z$ yet. Should I talk about cluster algebras/exchange relations before this?}
 To begin, let $\tau',\tau''$ be given and let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.

### 2021-04-29 draft.tex
meeting notes

@@
 
-The variety $X(\tau)$ defined by
+The variety $X(\tau)$ defined by taking the top dimensional component of \acom{todo}
 % from $\tau\in YT(\lambda)_\mu$ by 
 \[
-X(\tau) = \overline{
+% X(\tau) = 
+\overline{
     \{
@@
     \label{pr:govsasirrecs}
-    The decomposition
+    The set of.. is the irrecs of.. 
     \begin{equation*}
@@
 $$
-Z(\tau) = \{
-L\in\Gr : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\cap S^{\mu(i)}\text{ for all }i \}
+Z(\tau) = \overline{\{
+L\in S^\mu : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\text{ for all }i \}}
 $$
@@
     By definition of $X'\ast_s X''$,  $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$ and lies in $\UU^{\mu'(i),\mu''(i)}_{0,s}$.
-So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}\cap S^{\mu'(i),\mu''(i)}_{0,s}$ which fits the alternate description of $Z(\tau)$..
+So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$ which fits the alternate description of $Z(\tau)$.
 

### 2021-04-29 draft.tex
p14 to 16 revamped

--- 2021-04-28 draft.tex
@@
 On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.
-\acom{not $g(A)\CC[t]^m$}
-\jcom{This one isn't a point in $ \Gr$, the others I changed.}
+% \acom{not $g(A)\CC[t]^m$}
+% \jcom{This one isn't a point in $ \Gr$, the others I changed.}
 
@@
 for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\Oinf) $. % was CC\xt[]
-Note that $ h^{-1}n h \in N(\Kinf)$, 
+Note that $ h^{-1}n h \in N_-(\Kinf)$, 
 % ((t^{-1}))
@@
 Since $ g, h, n_1 \in G_1(\Oinf)$, the right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.
-Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.
+Since $ \mu $ is dominant, $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t])$, and so the left hand side lies in $t^\mu G(\CC[t]) t^{-\mu}$.
 
@@
 $$
-    t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.
+    t^\mu G(\CC[t]) t^{-\mu} \cap G_1(\Oinf) = N_{-,1}(\Oinf)\,.
 $$
 % $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
-Thus, we deduce that $ g^{-1} h n_1 \in N_1(\Oinf)$ 
+Thus, we deduce that $ g^{-1} h n_1 \in N_{-,1}(\Oinf)$ 
 % $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
-and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''} N_1(\Oinf) $.  
+and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''}N_{-,1}(\Oinf) $.  
 % Given that we know that 
@@
 % 
-\jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
+% \jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
 To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.
@@
 %
-Restricting to the zero fibre we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}.
-\acom{Technically the zero fibre is comprised of $\CC[t]$ lattices and we need to `specialize' to end up in the ordinary $\Gr$.}
+
+Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}.
 % 
@@
 \end{corollary}
+The irreducible components of the closure of the intersection on the lefthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}.
+By BKK the set of MV cycles of all possible types and weights can be glued together to form a \textbf{perfect basis} of $\CC[N]$.
+
+\acom{We are ready for applications! One of the motivations for this paper is... Abstractly multiplication is $\ast_s$... To compute we now carry this across \Cref{th:OTGrW}.}
 
 \section{Falling Action} % Resolution
-\acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis.
+\subsection{MV cycles}
+\begin{itemize}
+    \item $\overline{A(n_\bullet)}$
+    \item $D_\gamma$ 
+    \item MV basis?
+\end{itemize}
+% \acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis.
 Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with.
@@
 % 
+\subsection{Alternate MV}
 We begin this section with some new notation.
@@
 
-Given $\tau\in YT(\lambda)_\mu$ we denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$.
-
-Given $A \in M_N(\CC)$ we denote by 
-% $A\big|_{\CC^i}$ 
-$A\big|_{\CC^p}$ 
-the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}$ preserves $\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
-
-The variety $X(\tau)$ defined by
-% from $\tau\in YT(\lambda)_\mu$ by 
-\[
-X(\tau) = \overline{
-    \{
-        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
-    \}
-}    
-\]
-is called a \textbf{generalized orbital variety}. 
-% 
-It inherits a crystal datum called a \textbf{Lusztig datum} from its tableau. 
-\acom{Cite Joel? Hide dependence on reduced expression?}
+Given $\tau\in YT(\lambda)_\mu$ denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$. 
+%
+
 The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is got from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
@@
 % 
-% TODO
-% \begin{theorem}(CITE KAM07)
-%     Taking $\vi$-Luszig datum is a bijection $P\to\NN^{\ell}$. 
-% \end{theorem}
-% 
-We need the following two results from \cite{dthesis}.
+This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
+% 
+We can associate to $\tau$ an MV cycle. \acom{which is something we haven't introduced yet.} Let 
+%  
+\begin{equation*}
+    Z(\tau) = 
+    % \overline{
+        \{
+            L\in S^\mu : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\text{ for all }i 
+        \}\,. 
+    % }
+\end{equation*}
+% 
 \begin{proposition}
-    \label{pr:govsasirrecs}
-    The decomposition
-    \begin{equation*}
-        % \label{eq:govsasirrecs}
-        \overline{\OO}^\lambda\cap\TT_\mu\cap\n = \bigsqcup_{\tau\in YT(\lambda)_\mu} X(\tau)
-    \end{equation*}
-    is\dots
+    \label{pr:newmvdes}
+    $\overline{Z(\tau)}$ the MV cycle whose Lusztig datum is $n_\bullet(\tau)$. 
 \end{proposition}
-% 
-Denote by $Z(\tau)\subset\Gr$ the closure of the image of $X(\tau)$ under the isomorphism of \Cref{cor:mvy}. 
-\acom{Still need Lusztig data of MV cycles; with it $B(\infty)$, stable vs ordinary, etc?}
-\jcom{Do you want $ Z(\tau)$ to be the closure?}
-\acom{Sure}
-
-% 
-\begin{proposition}
-    \label{prop:dth}
-    % The isomorphism 
-    % $\phi: \overline{\OO}^\lambda\cap\TT_\mu\cap\n \to \overline\Gr^\lambda\cap S^\mu_-$ 
-    % is compatible with the decomposition of \Cref{pr:govsasirrecs}
-    % the bijection $YT(\lambda)_\mu \to \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ 
-    % in the sense that 
-    $Z(\tau)$ is dense in the MV cycle whose Lusztig datum is $n_\bullet(\tau)$. 
-\end{proposition}
-\acom{We would like to use the action of $W$ which gives isomorphisms
-$Gr^\lambda \cap Gr_\mu \cap S^\mu \cong Gr^\lambda \cap Gr_{w\mu} \cap S^{w\mu}$ to generalize to non-dominant $\mu$.
-But the Lusztig datum of $\tau\in YT(\lambda)_\mu$ may not appear as the Lusztig datum of any element of $YT(\lambda)_{w\mu}$..}
 % This gives us the dimension of Gr^\lambda \cap Gr_\mu \cap S^\mu.
-\begin{lemma}
-Alternate description. Works for non-dominant $\mu$. 
-$$
-Z(\tau) = \{
-L\in\Gr : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\cap S^{\mu(i)}\text{ for all }i \}
-$$
-is an MV cycle. 
-\end{lemma}
 % Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all
@@
 % 
-\jcom{I don't think that you should mention this partial inverse here.
+% \jcom{I don't think that you should mention this partial inverse here.
 I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
-\acom{Ok, I moved it.}
+% \acom{Ok, I moved it.}
 
@@
 % 
-In this part we prove that the product 
-% the ideal of 
-% $Z'\ast_\AA Z''$ 
-$b_{Z'}b_{Z''}\in\CC[N]$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
-% 
-\rcom{I don't think we introduced $\CC[N]$ or the elements $b_Z$ yet. Should I talk about cluster algebras/exchange relations before this?}
-To begin, let $\tau',\tau''$ be given and let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
-%
-
+\subsection{Fusion of MVCs}
+Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before, and take $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$. 
+%
+
+Given $A \in M_N(\CC)$ we denote by 
+% $A\big|_{\CC^i}$ 
+$A\big|_{\CC^p}$ 
+the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}$ preserves $\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. 
 % \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.} 
@@
     By definition of $X'\ast_s X''$,  $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$ and lies in $\UU^{\mu'(i),\mu''(i)}_{0,s}$.
-So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}\cap S^{\mu'(i),\mu''(i)}_{0,s}$ which fits the alternate description of $Z(\tau)$..
-
-    \acom{..assuming $\tau_s$ identifies these intersections with products of intersections.}
-
-    \jcom{I removed the $, s)$ from 1.  I don't understand the statement of 2.}
-    \acom{Yup, me neither. Getting there..}
-
-    \jcom{I think that it is actually a bit simpler.  Again from teaching algebraic geometry, I found the following.  If $ A $ is a principal ideal domain, then $M $ is flat iff it is torsion-free.}
-
-    \acom{Here $A$ is $\CC[t]$ and $M = \cO$ right?
-Better, agreed.
-Does the direction: torsion free implies flat, or not flat implies not torsion free, hold even without the PID assumption?
-This belongs way back in Joel's Lemma}
-
-    % In particular, we see that 
-    % \[
-    % Z(\tau) = \{L \in \Gr: L\cap\CC[t]^i \in \Gr^{\lambda(i)} \text{ for } i = 1,\dots, m\}\,.     
-    % \]
+So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)} \cong \Gr^{\lambda'(i)}\times \Gr^{\lambda''(i)}$ so $(l(0),l(s))\in Z(\tau')\times Z(\tau'')$.
 \end{proof}
-
-\acom{We compute zero fibres of $\ast_s$ by applying the results of \Cref{dthesis}..}
-
-\begin{question}
-%[Related question] 
-    If $\mu',\mu''$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
-    \[
-    \begin{tikzcd}
-        \overline\Gr^{\lambda',\lambda'}_{0,s}\cap S^{\mu',\mu''}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda'} \cap S^{\mu'} \times \overline\Gr^{\lambda'} \cap S^{\mu''} \supset Z' \times Z'' \ar[d]\\
-        \overline\OO^{\lambda',\lambda''}_{0,s} \cap \UU^{\mu',\mu''}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda'}\cap \TT_{\mu'}\cap \n \times \overline\OO^{\lambda''}\cap \TT_{\mu''}\cap \n
-    \end{tikzcd}    
-    \]
-\end{question}
-% 
+Let $X(\tau')\ast_0 X(\tau'')$ be the zero fibre of $\overline{\cup_{s\in\CC-0} X'\ast_s X''}$. 
+\begin{itemize}
+    \item $X'\ast_0 X'' \cong Z'\ast_0 Z''$ 
+    \item $X'\ast_0 X''$ is a union of GOVs
+    \item hence, $Z'\ast_0 Z''$ is a union of associated MVCs
+\end{itemize}
+
+What is a GOV? Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
+% from $\tau\in YT(\lambda)_\mu$ by 
+\[
+% X(\tau) = 
+% \overline{
+    \{
+        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
+    \}\,. 
+% }    
+\]
+$\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
+% 
+% By \cite[?]{dthesis}.
+\begin{proposition}
+    \label{pr:govsasirrecs}
+    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
+\end{proposition}
+
 \begin{proposition}(\cite{baumann2019mirkovic})
     % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
-    Let $Z',Z''$  be MV cycles of coweight $(\lambda',\mu'),(\lambda'',\mu'')$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
+    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''$ and weight $\mu',\mu''$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
     Then 
     \begin{equation}
-        \label{eq:tabmult}
-        % Z_\tau\ast Z_\sigma 
-        m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
-        = 
-        % \sum_{Z\in\cZ(\lambda)_\mu} 
-        \sum_{\tau\in S(\lambda)_\mu}
-        i\left(
-            X(\tau), X(\tau')\circ X(\tau'')
-            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
-        \right) [Z(\tau)]\,. 
+        Z'\ast_0 Z'' = \cup Z(\tau)
+        % \label{eq:tabmult}
+        % % Z_\tau\ast Z_\sigma 
+        % m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
+        % = 
+        % % \sum_{Z\in\cZ(\lambda)_\mu} 
+        % \sum_{\tau\in S(\lambda)_\mu}
+        % i\left(
+        %     X(\tau), X(\tau')\circ X(\tau'')
+        % \right) [Z(\tau)]\,. 
     \end{equation}
-    % and the intersection multiplicities on the right are found by\dots\acom{To be completed.}
-
-    % In particular, the multiplicity of $Z(\tau)$
-    % in the product of the zero fiber 
-    % (divisor class) 
-    % and the 
-    % (Zariski) 
-    % closure of the family $Z_1 \times Z_2 \times U$ 
-    % is equal to the multiplicity of its generalized orbital variety $X(\tau)$ 
-    % in $ \overline{\OO}^{\lambda',\lambda''}_{0,0}\cap\UU^{\mu',\mu''}_{0,0} $. 
-    % among the set 
-    % \begin{equation}\label{eq:tabmult}
-        % \irr\lim_{s\to 0} 
-        % \overline{\OO}^{\lambda',\lambda''}_{0,0}\cap\UU^{\mu',\mu''}_{0,0} \,. 
-        % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu',\mu''}^{+,s}
-    % \end{equation}
-    \acom{Some of what was written here (commented out above) was incorrect. We can reiterate for emphasis that $i(Z,Z'\circ Z'')$ is computed in terms of rank varieties.}
-
-    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
-    $$
-    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
-        Z, Z' \circ Z''
-        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
-    \right) b_Z 
-    $$
-    can also be deduced from \Cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$. These are described in \Cref{lem:mintab,prop:minwts} below.
+    with $i\left(X(\tau), X(\tau')\circ X(\tau'')\right)$ copies of $Z(\tau)$ showing up on the RHS. 
 \end{proposition}
 % 
-
-\acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
+\acom{Closures missing. Here and elsewhere}
+
 \begin{conjecture}
@@
 \end{conjecture}
-%
-
-\acom{How's here?}
-It may be helpful to know the map
-\[
-    \CC[N]\to \bigcup_{\lambda~\text{dominant}\atop \mu\le\lambda} YT(\lambda)_\mu 
-\]
-that we use to find our tableaux.
-    % $$
-    % \begin{tikzcd}
-    %     YT(\lambda)_\mu \ar[r] \ar[d] & \irr \overline{\OO}^\lambda\cap\TT_\mu\cap\n \ar[d] \\
-    %     GT(\lambda)_\mu \ar[r] & \irr \overline\Gr^\lambda\cap S^\mu_-
-    % \end{tikzcd}
-    % $$
-\acom{Refer to Claxton--Tingley multisegments, Hong--Lee marignally large tableaux for comparison.}
+\acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
+% 
+\subsection{Connection to cluster structure on $\CC[N]$}
+% 
+Goal: 
+$$
+b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
+    Z, Z' \ast_0 Z''
+    % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
+\right) b_Z 
+$$
+
 \begin{lemma}
@@
     As the examples show, there may be more than one way to break up a ``minimal'' tableau for $n_\bullet = n_\bullet ' + n_\bullet ''$ into two tableaux with data $n_\bullet' $ and $n_\bullet''$ resp.\ The practical notion of min is such that the generalized nonzero eigenspace has the smallest possible dimension.}
+    \acom{Reference Claxton--Tingley multisegments, Hong--Lee marignally large tableaux for comparison.}
 \end{proposition}

### 2021-05-05 draft.tex
we havent defined G1

@@
 % 
+\acom{we haven't defined $G_1$}
 
@@
 \end{corollary}
-The irreducible components of the closure of the intersection on the lefthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}.
+The irreducible components of the closure of the intersection on the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}.
 By BKK the set of MV cycles of all possible types and weights can be glued together to form a \textbf{perfect basis} of $\CC[N]$.
@@
 \subsection{MV cycles}
-\begin{itemize}
-    \item $\overline{A(n_\bullet)}$
-    \item $D_\gamma$ 
-    \item MV basis?
-\end{itemize}
+\begin{definition}
+An irreducible component of $ \overline{\Gr}^\lambda \cap S^\mu $ is called an \textbf{Mirkovic-Vilonen cycle} in $ \overline{\Gr}^\lambda$ of coweight $\mu$.
+\end{definition}
+
+\jcom{We could put some stuff here about stable MV cycles and multiplication, but maybe we can have this in a later section.}
+
 % \acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis.
@@
 %
-\begin{comment}
-\begin{theorem}
-    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
-    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
-    There is an isomorphism 
-    \begin{equation}
-        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
-    \end{equation}
-    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by
-    \begin{equation}
-        \begin{split}
-            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
-            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
-        \end{split}
-    \end{equation}
-    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
-\end{theorem}
-
-Let's call this the MVyBD isomorphism.
-
-\begin{proof}
-    The proof is fibre by fibre, so fix $s\ne 0$.
-\acom{Emphasize in the intro later (because this always confuses me) that by the $s$-fibre we really mean the $(0,s)$-fibre; i.e.\ its the BD Grassmannian over the second symmetric power of $C = \AA^1$; better just replace $s$-fibre by $(0,s)$-fibre everywhere it occurs.}
-    \begin{enumerate}
-        \item The map is well defined.
-In particular, it defines $\CC[t]$-lattices in $\CC(t)^m$.
-Moreover, these lattices break down to give pairs of lattices upon inverting $t$ or $t-s$ that have the right properties.
-[Copy Roger's proof]
-        \item The inverse map is got by taking the matrix of multiplication by $t$.
-More precisely, let $ L \in Gr^{BD} \cap \cW_\mu$.
-We work with the quotient $\CC[t]^m/L$ just as in the ordinary MVy isomorphism---the only difference being $\CC\xt$ is replaced by $\CC[t]$.
-\begin{enumerate}
-    \item 
-    We claim that 
-    \begin{equation}
-        \{[e_i],[te_i],\dots,[t^{\mu_{i}-1}e_i] : 1\le i \le m\}
-    \end{equation}
-    is a $\CC$-basis of $\CC[t]^m/L$.
-
-    To see this, we use that $ L $ 
- has a $\CC[t]$-basis of the form 
-    \begin{equation}
-        v_i = t^{\mu_i} + \sum_{j>i} p_{ij}(t) e_j 
-    \end{equation}
-    with $\deg p_{ij}(t) < \mu_i = \mu_{1,i} + \mu_{2,i}$ ($1\le i\le m$).
-    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu',\mu''}$ in this way?}
-    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda'$ while its generalized $s$-eigenspace will have block type $\le \lambda''$.
-    To see this, note that there is a natural isomorphism
-    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
-    carrying the action of $t $ to the action of $t$.
-
-    The left hand side is the same thing as
-    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
-
-    the defining fact that lattices satisfying Equation~\ref{eq:defGrBDlambda} equivalently satisfy 
-    \begin{equation}
-        \begin{split}
-            t\big|_{\CC\xt^m/L_1}\text{ has Jordan type} \le \lambda' \\
-            t\big|_{\CC\xt^m/L_2}\text{ has Jordan type} \le \lambda'' 
-        \end{split}
-    \end{equation}
-    where recall 
-    $L_i = L\otimes \CC\xt$ ??? 
-    % $L_i = L\otimes \CC[(t-p_i)^{-1}]$ 
-    and $p_1 = s$ while $p_2 = 0$.
-
-    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
-    carrying the action of $t $ to the action of $t$.
-
-    The left hand side is the same thing as
-    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
-    \acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue? Basic linear algebra? Joel?}
-\end{enumerate}
-    \end{enumerate}
-\end{proof}
-
-\begin{theorem}[Theorem 1 version 2]
-    Let $\lambda_1,\lambda_2$ and $\mu$ 
-    %be dominant
-    be arbitrary, such that $\lambda = \lambda_1 + \lambda_2 \ge \mu$. Then there is an isomorphism 
-    \begin{equation}
-        \overline{\OO_{\lambda_1,\lambda_2}} \cap \TT_\mu \to \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu 
-    \end{equation}
-    defined by the same map as in Theorem 1.
-\end{theorem}
-
-\jcom{This is true as stated with the ``larger'' definition of $ \cW_\mu $.
-In fact, for any $\lambda_1, \lambda_2$, it is true $ \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu $ is contained in a subset that we could call $ \cW_\mu^s$ which we could define as
-$$
-\cW_\mu^s = G_1\xt[t^{-1}]\TT_\mu \cap G[t,t^{-1}, (t-s)^{-1}] / G[t]
-$$
-where we regard $G[t,t^{-1}, (t-s)^{-1}] / G[t] \subset G\xT[t^{-1}]/G[t] $
-
-The way to think about this is as follows: inside the thick affine Grassmannian we can consider the $G$-bundles trivialized away from just 0, $s$, or equivalently those lattices which become the standard lattice after tensoring with $ \CC[[t-a]] $ for any $ a \ne 0, s$.
-}
-\begin{corollary}
-    The MVyBD isomorphism restricts to an isomorphism of subfamilies 
-    \begin{equation}
-        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+ \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu''}\,. 
-    \end{equation}
-\end{corollary}
-
-\begin{proof}
-    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovi\'c-Vybornov isomorphism.
-Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
-    $$ g = (g t^{-\mu_1}(t-s)^{-\mu_2}) t^{\mu_1}(t-s)^{\mu_2} \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$$
-    So we get containment in one direction.
-
-    For the reverse containment, we choose $ [g] \in \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu',\mu''}$.
-By the lemma below, $[g] \in \cW_\mu$ and thus it lies in the image of our map and we are done.
-\end{proof}
-
-% Define $S_{\mu',\mu''}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.
-
-\acom{is it a fibre of $S_{\mu',\mu''}$ defined above?}
-
-We could also make the following claim.
-
-\begin{lemma}[KWWY14]
-    Let $\mu$ be dominant. Then 
-    \begin{equation}
-        N_{-}\xT[t^{-1}] L_\mu = N_1\xt[t^{-1}]L_\mu
-    \end{equation}
-    \acom{where I am not sure about the double brackets.}
-\end{lemma}
-
-\begin{lemma}%[Roger's lemma]
-    Let $\mu',\mu''$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
-    \begin{equation}
-        S_{\mu',\mu''}^s \subset \cW_\mu 
-    \end{equation}
-    where $\mu = \mu_1 + \mu_2$.
-\end{lemma}
-
-\begin{proof}
-    % Copy Roger's proof.
-    We have
-\[
-\begin{split}
-    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
-     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
-     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
-     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
-     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
-     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
-     & = W_{\mu_1 + \mu_2}
-\end{split}
-\]
-where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
-\[
-\frac{t}{t-s} = 
-1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
-\in B_1\xt[t^{-1}].
-\]
-\end{proof}
-\end{comment}
-% 
-\subsection{Alternate MV}
-We begin this section with some new notation.
-Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of (arbitrary) shape $\lambda$ and (arbitrary) weight $\mu$.
-Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
+
+In \cite{mvcycle}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic-Vilonen polytopes, or equivalently Lusztig data.
+For $ GL_m$, this description can be reworded in terms of Young tableaux.
+\jcom{Maybe add something here about Lusztig data and the standard reduced word.}
+
+We begin with some new notation. Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of shape $\lambda$ and weight $\mu$. 
+%Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
 % For the sake of making a definition, we momentarily put some letters of our alphabet in unexpected roles, and ask you to suspend your disbelief.
@@
 
-Given $\tau\in YT(\lambda)_\mu$ denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$. 
-%
-
-The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is got from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
+Given $\tau\in YT(\lambda)_\mu$ and $ i \in \{1, \dots m\} $, denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$.
+(Note that $ \mu(i)$ only depends on $ \mu$, while $ \lambda(i)$ depends on the tableau $ \tau$.)  We will regard $ \lambda(i)$ (resp.
+$\mu(i)$) as an effective dominant coweight (resp.
+effective coweight) for $GL_i$.
+%
+
+The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula
 $$
@@
 for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
-% 
+\jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}
+
 For example, if 
@@
 % 
-This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
+%This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
 % 
@@
     Z(\tau) = 
-    % \overline{
+     \overline{
         \{
-            L\in S^\mu : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\text{ for all }i 
+            L\in S^\mu : L\cap\cO^i\in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
         \}\,. 
-    % }
+     }
 \end{equation*}
 %
+
+The following result is closely related to Theorem 4 from \cite{dranowski2020generalized}.
+It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson-Kogan \cite{andersonkogan1} (see Section 9 in \cite{mvcycle}).
+We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent-Littelmann-Nguyen \cite[Theorem 2]{GLN}.
 \begin{proposition}
     \label{pr:newmvdes}
-    $\overline{Z(\tau)}$ the MV cycle whose Lusztig datum is $n_\bullet(\tau)$. 
+    $Z(\tau)$ the MV cycle whose Lusztig datum with respect to $ \vi $ is $n_\bullet(\tau)$. 
 \end{proposition}
+\begin{proof}
+    The proof of this theorem follows the same strategy as in \cite{dranowski2020generalized}.
+\jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}
+
+Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+
+\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
+
+First, we consider
+\begin{equation*}
+Z(\tau)_1 := \{ L \in S^\mu : L \cap \cO^i \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
+%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
+\end{equation*}
+From Corollary 9.7 of \cite{mvcycle}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{mvcycle}.
+Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
+We also note that $Z(\tau_1) \subset \Gr^\lambda$ is dense in $ Z(\tau_1)$.
+\jcom{Need to justify this last sentence.}
+
+Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu$, then $ L \cap \cO^i \in S^{\mu(i)}$.  Thus, we get a map $$ f_i : Z(\tau)_1 \rightarrow S^{\mu(i)} \cap S_+^{\lambda(i)} $$
+From the definition of $ Z(\tau)_1 $, we see that $ f_i(Z(\tau_1) = Z(\tau(i)_1)$.
+From above $ \Gr^{\lambda(i)} \cap f_i(Z(\tau(i)_1))$ is a dense constructible subset of $Z(\tau(i)_1)$.
+Since $ Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)} \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ is a dense constructible subset of $ Z(\tau_1) $.
+
+Working with all $ i $ at once, we conclude that
+$$ Z(\tau)_2 := \bigcap_{i=1}^m f_i^{-1}(S^{\mu(i)} \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $$
+is a dense constructible subset of $ Z(\tau)_1$.  Thus $\overline{Z(\tau)_2} = \overline{Z(\tau)_1}$.
+
+On the other hand, by definition 
+$$Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}$$
+
+\jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}
+
+    %See computation 5.3.9 and Lemma 5.4.2 (ignore its proof) of \url{http://www.math.toronto.edu/adranows/athesis.pdf}. 
+\end{proof}
 % This gives us the dimension of Gr^\lambda \cap Gr_\mu \cap S^\mu.
@@
 
-\begin{conjecture}
+\begin{conjecture}\label{conj:cluster in MV}
     The cluster monomials of $\CC[N]$ are elements of the MV basis.
@@
 
-It has been shown in \cite{kato2011polytopal} that for certain initial seeds $(x_1, \dots, x_r)$, each $x_i$ is in the MV basis.
-Then to show every cluster variable is in the MV basis, it suffices to show that for a mutable variable $x_i$, its mutation $x_i^*$ is also in the MV basis.
+Conjecture \ref{conj:cluster in MV} is known for type $A_n$, $n \leq 3$, as in this case, there is a unique biperfect basis for $\CC[N]$ \cite{baumann2019mirkovic}, so the dual semicanonical basis and MV basis are the same.
+
+It has been shown in \cite{kato2011polytopal} that for initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word in the Weyl group for $G$, each $x_i$ is in the MV basis as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
+If the reduced expression satisfies a special condition, then the cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
+
+Suppose we have a seed $(x_1, \dots, x_r)$ where each $x_i$ is already in the MV basis.
+To show all the other cluster variables are in the MV basis, it suffices to show that for a mutable variable $x_i$, its mutation $x_i^*$ is also in the MV basis.
 The exchange relation corresponding to $x_i$ and $x_i^*$ is of the form
 $$x_ix_i^* = x_+ + x_-$$
-where $x_+$ and $x_-$ are monomials in the $x_j,j\neq i$.
-Let $Z_i$, $Z_+$, and $Z_-$ be the corresponding MV cycles for $x_i$, $x_+$, and $x_-$, respectively.
-If we are able to find an MV cycle $Z_i^*$ such that
-$$Z_i \circ Z_i^* = Z_+ \cup Z_-,$$
-then this means $x_i^*$ is in the MV basis with associated MV cycle $Z_i^*$. In Section \ref{s:denouement}, we present examples showcasing this is indeed true for type $A_3$. 
+where $x_+$ and $x_-$ are monomials in the $x_j,j\neq i$. Let $Z_i$ be the MV cycle corresponding to $x_i$, so $x_i = b_{Z_i}$. If we are able to find an MV cycle $Z_i^*$ such that
+$$b_{Z_i} b_{Z_i^*} = x_+ + x_-,$$
+then this means $x_i^* = b_{Z_i^*}$ so it is in the MV basis with associated MV cycle $Z_i^*$. In Section \ref{s:denouement}, we present examples showcasing this is indeed true for type $A_3$. 
 \section{Denouement}

### 2021-05-05 draft.tex
Edited Section 8
added some refs and added some stuff to 7.2

@@
 % 
-We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.
+% We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.
 By construction, this is a flat family over $ \AA$.
@@
 
-If $ s \ne 0$, then the map $ \tau_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.
-
-On the other hand, the fibre $ X_1 \ast_0 X_2$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
+% If $ s \ne 0$, then the map $ \tau_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.
+
+% On the other hand, the fibre $ X_1 \ast_0 X_2$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
 We call this subscheme the \textbf{fusion} of $ X_1 $ and $ X_2$.
 
-\jcom{I rewrote this to introduce the $ X_1 \ast_s X_2 $ notation that we need for later.
+% \jcom{I rewrote this to introduce the $ X_1 \ast_s X_2 $ notation that we need for later.
 In doing so, $ X_1 \circ X_2 $ became obsolete, since we now have $ X_1 \ast_0 X_2$, but if you like we could just define $X_1 \circ X_2 = X_1 \ast_0 X_2 $.}
@@
 
-\acom{Ah, sorry --- so do we introduce a even more general notion of $\ast_\AA$ for arbitrary flat families?
+% \acom{Ah, sorry --- so do we introduce a even more general notion of $\ast_\AA$ for arbitrary flat families?
 Looking at Eisenbud's geoemtry of schemes (where flat iff tor-free actually shows up as Exercise II-33!) there does not seem to be anything quite like $\ast_\AA$ or $\circ$ defined.}
 
-\jcom{I'm not sure how a general notion would be defined.  In our case, we are using the special fact that the general fibre is a product.}
-
-\acom{I mean exactly in the case of this special fact, which is not special to the BD Gr.}
+% \jcom{I'm not sure how a general notion would be defined.  In our case, we are using the special fact that the general fibre is a product.}
+
+% \acom{I mean exactly in the case of this special fact, which is not special to the BD Gr.}
 
@@
     \label{cor:mvy}
-    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
+    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$ where $\n\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
 \end{corollary}
-The irreducible components of the closure of the intersection on the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}.
-By BKK the set of MV cycles of all possible types and weights can be glued together to form a \textbf{perfect basis} of $\CC[N]$.
+The closures of the irreducible components of the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}.
+By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \textbf{perfect basis} of $\CC[N]$.
 
@@
 
+\acom{With this definition here what do we do about the sentence after \Cref{cor:mvy} above?}
+
 % \acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis.
@@
 
-In \cite{mvcycle}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic-Vilonen polytopes, or equivalently Lusztig data.
-For $ GL_m$, this description can be reworded in terms of Young tableaux.
-\jcom{Maybe add something here about Lusztig data and the standard reduced word.}
+In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic-Vilonen polytopes, or equivalently Lusztig data.
+For $\GL_m$, this description can be reworded in terms of Young tableaux.
+\jcom{Maybe add something here about Lusztig data and the standard reduced word, $\vi = (1,2,\dots,m-1,\dots,1,2,1)$.}
 
@@
 $\mu(i)$) as an effective dominant coweight (resp.
-effective coweight) for $GL_i$.
-%
-
-The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula
+effective coweight) for $\GL_i$.
+%
+
+The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
 $$
@@
 $$
-for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
+for $(i,j) = (1,1), (2,1), \dots, (m-1,1), (2,2),\dots,(m-1,2),\dots,(m-1,m-1)$. 
+The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence. See \cite[\S 4]{berenstein1988tensor}.
+
 \jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}
+
+\acom{Yes $i = m$ doesn't make sense. Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),..,(m-1,1),(2,2),..,(m-1,2),..,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things. Right?}
 
@@
 The following result is closely related to Theorem 4 from \cite{dranowski2020generalized}.
-It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson-Kogan \cite{andersonkogan1} (see Section 9 in \cite{mvcycle}).
-We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent-Littelmann-Nguyen \cite[Theorem 2]{GLN}.
+It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2006algebra} \acom{is this the right AK?} (see Section 9 in \cite{kamnitzer2010mirkovic}).
+We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}.
 \begin{proposition}
     \label{pr:newmvdes}
-    $Z(\tau)$ the MV cycle whose Lusztig datum with respect to $ \vi $ is $n_\bullet(\tau)$. 
+    $Z(\tau)$ is the MV cycle whose Lusztig datum with respect to $ \vi $ is $n_\bullet(\tau)$. 
 \end{proposition}
@@
 \jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}    
+\acom{I've been meaning to update the paper. It's peppered with ``typos''.}
 
@@
 \jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
+\acom{For it.}
 
@@
 \end{equation*}
-From Corollary 9.7 of \cite{mvcycle}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{mvcycle}.
+From \cite[Corollary 9.7]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.
 Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
 We also note that $Z(\tau_1) \subset \Gr^\lambda$ is dense in $ Z(\tau_1)$.
-\jcom{Need to justify this last sentence.}
+\jcom{Need to justify this last sentence.} \acom{We mean $Z(\tau_1)\cap \Gr^\lambda$ is dense in $Z(\tau_1)$?}
 
@@
 \subsection{Fusion of MVCs}
-Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before, and take $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$. 
-%
-
+Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
+% 
 Given $A \in M_N(\CC)$ we denote by 
@@
 $A\big|_{\CC^p}$ 
-the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}$ preserves $\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. 
+the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. 
 % \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}
-Given $s\in\CC$, let 
+
+Given $s\in\CC\setminus \{0\}$, and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
 \begin{equation*}
@@
     % % 
-    Let $A\in X(\tau')\ast_s X(\tau'')$, let $i = 1,\dots, m$.  
+    Let $A\in X(\tau')\ast_s X(\tau'')$ and $i = 1,\dots, m$.  
     % Denote by 
     % $E_a$ the generalized $a$-eigenspace of $A$, and by 
-    Clearly, the lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
-    $$
-    L\cap \CC[t]^i = l. 
-    $$
-    By definition of $X'\ast_s X''$,  $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$ and lies in $\UU^{\mu'(i),\mu''(i)}_{0,s}$.
-So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)} \cong \Gr^{\lambda'(i)}\times \Gr^{\lambda''(i)}$ so $(l(0),l(s))\in Z(\tau')\times Z(\tau'')$.
+    The lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
+    $$
+    L\cap \CC[t]^i = l
+    $$
+    where $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denotes the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
+    %
+
+By definition of $\UU^{\mu',\mu''}$ we have $A\big|_{\CC^{|\mu(i)|}}\in\UU^{\mu'(i),\mu''(i)}_{0,s}$ and by definition of $X(\tau')\ast_s X(\tau'')$, $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$.
+So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$ and
+% \Gr^{\lambda'(i)}\times \Gr^{\lambda''(i)}$ so 
+$(l(0),l(s))\in Z(\tau')\times Z(\tau'')$.
 \end{proof}
-Let $X(\tau')\ast_0 X(\tau'')$ be the zero fibre of $\overline{\cup_{s\in\CC-0} X'\ast_s X''}$. 
-\begin{itemize}
-    \item $X'\ast_0 X'' \cong Z'\ast_0 Z''$ 
-    \item $X'\ast_0 X''$ is a union of GOVs
-    \item hence, $Z'\ast_0 Z''$ is a union of associated MVCs
-\end{itemize}
-
-What is a GOV? Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
+% 
+% 
+In analogy with the BD construction \acom{add loc cit} we define $X(\tau')\ast_0 X(\tau'')$ to be the zero fibre of the family $\overline{\bigcup_{s\in\CC\setminus\{0\}} X(\tau')\ast_s X(\tau'')}$ in $M_N(\CC)$.
+% 
+\begin{corollary}
+    $X'\ast_0 X'' \cong Z'\ast_0 Z''$ 
+\end{corollary}
+% 
+Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
 % from $\tau\in YT(\lambda)_\mu$ by 
@@
 \]
-$\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
-% 
-% By \cite[?]{dthesis}.
-\begin{proposition}
+Then $\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
+%
+
+\begin{theorem}
     \label{pr:govsasirrecs}
     The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
-\end{proposition}
+\end{theorem}
+\acom{$\overline{X(\tau)}$ vs $Z(\tau) = \overline{al;sdj}$}
+\begin{corollary}
+    $X'\ast_0 X''$ is a union of GOVs.
+\end{corollary}
+\begin{proof}
+    Since $X'\ast_0 X''\subset \overline{\OO}^\lambda\cap\TT_\mu\cap\n$\dots 
+\end{proof}
 
@@
     Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''$ and weight $\mu',\mu''$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
-    Then 
-    \begin{equation}
-        Z'\ast_0 Z'' = \cup Z(\tau)
+    Then $Z'\ast_0 Z''$ is a union of MVCs
+    % \begin{equation}
+        % Z'\ast_0 Z'' = \bigcup Z(\tau)
         % \label{eq:tabmult}
@@
         % \right) [Z(\tau)]\,. 
-    \end{equation}
-    with $i\left(X(\tau), X(\tau')\circ X(\tau'')\right)$ copies of $Z(\tau)$ showing up on the RHS. 
+    % \end{equation}
+    with $i\left(X(\tau), X(\tau')\circ X(\tau'')\right)$ copies of $Z(\tau)$ showing up. 
 \end{proposition}
 % 
-\acom{Closures missing. Here and elsewhere}
+\acom{Closures missing? Here and elsewhere?}
+% 
+\begin{proof}
+    Since $X'\ast_0 X'' \cong Z'\ast_0 Z''$ and GOVs go to MVCs 
+\end{proof}
 

### 2021-05-11 draft.tex
removed comment
rogers changes

@@
     % 
-    \jcom{I restated this again.  I think that it is simpler and more clear like this.  And I think that this is the fact that we end up using later.}
+    % \jcom{I restated this again.  I think that it is simpler and more clear like this.  And I think that this is the fact that we end up using later.}
     % 
@@
 % \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
-% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
-% 
-% We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.
+Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
+
+We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.
 By construction, this is a flat family over $ \AA$.
@@
 
-% If $ s \ne 0$, then the map $ \tau_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.
-
-% On the other hand, the fibre $ X_1 \ast_0 X_2$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
+If $ s \ne 0$, then the map $ \tau_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.
+
+On the other hand, the fibre $ X_1 \ast_0 X_2$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
 We call this subscheme the \textbf{fusion} of $ X_1 $ and $ X_2$.
@@
 Moreover, if $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.
-\acom{reference \cref{it:grs-gr}?} This open locus is a $ G(\CC[t])$-orbit
+% \acom{reference \cref{it:grs-gr}?} 
+This open locus is a $ G(\CC[t])$-orbit
 % .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
@@
 % 
-Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
+% Temporarily commenting out, don't use
+% Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
 % 
@@
 %A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
-\acom{secret definition; add `a matrix is likewise said to have Jordan type...if it lies in'?}
-\jcom{Is that better?}
-\acom{Yay.}
-%
-
-The closure $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ is $\bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.     
-\jcom{Do we need this?}
-\acom{No I guess we haven't used it yet. Maybe in Proposition 5..}
+% \acom{secret definition; add `a matrix is likewise said to have Jordan type...if it lies in'?}
+% \jcom{Is that better?}
+% \acom{Yay.}
+%
+
+% The closure $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ is $\bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.     
+% \jcom{Do we need this?}
 
@@
 \end{corollary}
-The closures of the irreducible components of the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}.
+%The closures of the irreducible components of the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}.
 By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \textbf{perfect basis} of $\CC[N]$.
 
-\acom{We are ready for applications! One of the motivations for this paper is... Abstractly multiplication is $\ast_s$... To compute we now carry this across \Cref{th:OTGrW}.}
+%\acom{We are ready for applications! One of the motivations for this paper is... Abstractly multiplication is $\ast_s$... To compute we now carry this across \Cref{th:OTGrW}.}
 
@@
 \subsection{MV cycles}
+% 
+% We need to decide on the order in section 7. How about:
+% 
+% 1. MV cycles and tableaux (7.1)
+% 2. GOVs and relation to MV cycles, including fusion (7.2)
+% 3. Stable MV cycles and multiplication  in C[N]
+% 
 \begin{definition}
-An irreducible component of $ \overline{\Gr}^\lambda \cap S^\mu $ is called an \textbf{Mirkovic-Vilonen cycle} in $ \overline{\Gr}^\lambda$ of coweight $\mu$.
+An irreducible component of $\overline{\Gr}^\lambda \cap S^\mu$ is called an \textbf{Mirkovic--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$.
 \end{definition}
 
-\jcom{We could put some stuff here about stable MV cycles and multiplication, but maybe we can have this in a later section.}
-
-\acom{With this definition here what do we do about the sentence after \Cref{cor:mvy} above?}
+% \jcom{We could put some stuff here about stable MV cycles and multiplication, but maybe we can have this in a later section.}
+
+% \acom{With this definition here what do we do about the sentence after \Cref{cor:mvy} above?}
+% \jcom{I just cut it.  I think that it was a bit out of place there.}
 
@@
 
-In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic-Vilonen polytopes, or equivalently Lusztig data.
-For $\GL_m$, this description can be reworded in terms of Young tableaux.
-\jcom{Maybe add something here about Lusztig data and the standard reduced word, $\vi = (1,2,\dots,m-1,\dots,1,2,1)$.}
+In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic--Vilonen polytopes, or equivalently Lusztig data, which are sequences in $\NN^{\Delta_+}$ which depend on a choice of reduced expression.
+For $\GL_m$ and the standard reduced word, this description can be reworded in terms of Young tableaux.
+% \jcom{Maybe add something here about Lusztig data and the standard reduced word, $\vi = (1,2,\dots,m-1,\dots,1,2,1)$.}
 
@@
 Given $\tau\in YT(\lambda)_\mu$ and $ i \in \{1, \dots m\} $, denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$.
-(Note that $ \mu(i)$ only depends on $ \mu$, while $ \lambda(i)$ depends on the tableau $ \tau$.)  We will regard $ \lambda(i)$ (resp.
-$\mu(i)$) as an effective dominant coweight (resp.
-effective coweight) for $\GL_i$.
+(Note that $ \mu(i)$ only depends on $ \mu$, while $ \lambda(i)$ depends on the tableau $ \tau$.)  We will regard $ \lambda(i)$ (resp.\ $\mu(i)$) as an effective dominant coweight (resp.\ effective coweight) for $\GL_i$.
 %
@@
 $$
-n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
-$$
-for $(i,j) = (1,1), (2,1), \dots, (m-1,1), (2,2),\dots,(m-1,2),\dots,(m-1,m-1)$. 
-The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence. See \cite[\S 4]{berenstein1988tensor}.
+\begin{aligned}
+n_\bullet(\tau)_{i,j} &= \lambda(i+1)_j - \lambda(i)_j \\
+(i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
+(2,2),\dots,(m-1,2),%\\
+\dots,%\\
+(m-1,m-1)
+\end{aligned}
+% (i,j) = \begin{smallmatrix}
+% \\
+% (1,1) \\
+% (2,1) & (2,2) \\
+% \vdots & & \ddots \\
+% (m-1,1) & (m-1,2) & \dots & (m-1,m-1) 
+% \end{smallmatrix}
+$$
+% for 
+% $(i,j) = (1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2),\dots,(m-1,m-1)$. 
+% 
+The pattern $\gt(\tau)$ is recorded as a lower-triangular matrix (the array of shapes of subtableaux $\tau(i)$) and the datum $n_\bullet(\tau)$ is recorded as a sequence.
+See \cite[\S 4]{berenstein1988tensor}.
 
@@
 
-\acom{Yes $i = m$ doesn't make sense. Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),..,(m-1,1),(2,2),..,(m-1,2),..,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things. Right?}
+\acom{Yes $i = m$ doesn't make sense.
+Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2,\dots,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things.
+Right?}
 
@@
 % 
-We can associate to $\tau$ an MV cycle. \acom{which is something we haven't introduced yet.} Let 
+We can associate to $\tau$ an MV cycle. 
 %  
@@
 The following result is closely related to Theorem 4 from \cite{dranowski2020generalized}.
-It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2006algebra} \acom{is this the right AK?} (see Section 9 in \cite{kamnitzer2010mirkovic}).
+It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2004mirkovic} (see Section 9 in \cite{kamnitzer2010mirkovic}).
 We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}.
@@
 Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
-We also note that $Z(\tau_1) \subset \Gr^\lambda$ is dense in $ Z(\tau_1)$.
-\jcom{Need to justify this last sentence.} \acom{We mean $Z(\tau_1)\cap \Gr^\lambda$ is dense in $Z(\tau_1)$?}
+We also note that $Z(\tau_1) \cap \Gr^\lambda$ is dense in $ Z(\tau_1)$.
+\jcom{Need to justify this last sentence.}
 
@@
 % 
-\subsection{Fusion of MVCs}
+\subsection{Fusion of MVCs via BD MVy}
 Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
@@
 $(l(0),l(s))\in Z(\tau')\times Z(\tau'')$.
+
+So $A\in\dots$ iff $g(A)\in\dots$ 
 \end{proof}
@@
 % 
-In analogy with the BD construction \acom{add loc cit} we define $X(\tau')\ast_0 X(\tau'')$ to be the zero fibre of the family $\overline{\bigcup_{s\in\CC\setminus\{0\}} X(\tau')\ast_s X(\tau'')}$ in $M_N(\CC)$.
+In analogy with the Beilinson--Drinfeld construction \acom{add loc cit} we define $X(\tau')\ast_0 X(\tau'')$ to be the zero fibre of the family $\overline{\bigcup_{s\in\CC\setminus\{0\}} X(\tau')\ast_s X(\tau'')}$ in $M_N(\CC)$.
 % 
@@
 \end{conjecture}
+\jcom{Rather than adding the Lusztig data, how can you produce $\tau$ directly from $\tau', \tau''$?
+I guess you can just add the GT patterns, so for tableaux you just take the union of the rows, is that right?}
+
 \acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
@@
 \[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,s \rangle &\leadsto \young(13,2) &\equiv \young(3) &\leadsto Z_{Z_{1 \leftarrow 2}} \\ 
-    \langle A_{23}^1,s \rangle &\leadsto \young(12,3) &\equiv \young(2,3) &\leadsto Z_{Z_{1 \rightarrow 2}}
+    \langle A_{12}^1,s \rangle &\leadsto \young(13,2) &\equiv \young(3) &\leadsto {Z_{1 \leftarrow 2}} \\ 
+    \langle A_{23}^1,s \rangle &\leadsto \young(12,3) &\equiv \young(2,3) &\leadsto{Z_{1 \rightarrow 2}}
 \end{array}
@@
 \]
-Hence our ideal decomposes into 
+Hence our ideal decomposes into \acom{formatting funny; can just list irrecs?}
 \[

### 2021-05-15 draft.tex
joel's changes

@@
 
-\jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}
-
-\acom{Yes $i = m$ doesn't make sense.
+%\jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}
+
+%\acom{Yes $i = m$ doesn't make sense.
 Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2,\dots,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things.
@@
 %
+
+We will need the following definitions.
+\begin{definition}
+Let $ L \subset \OO^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
+$$
+\rdim(L) := \dim_\CC \OO^m/L
+$$
+
+If $ \gamma \subset \{1, \dots, m\}$, then we define
+\begin{gather*}
+    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
+L^\gamma:= L \cap \OO^\gamma \subset \OO^\gamma \quad L_\gamma := L / L^{\gamma^c} \subset \OO^\gamma
+\end{gather*}
+where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
+\end{definition}
+
+\begin{lemma}
+    For any $ L \in \Grth$ and any $ 
+    \gamma \subset \{1, \dots, m\} $, we have $ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L$.
+\end{lemma}
+We let $ D_\gamma(L) := \rdim L_\gamma$. By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
+
+\jcom{There is a discrepancy regarding $ \gamma$ and $ \gamma^c$.}
+
+Recall that $ S^\mu = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+
+\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
+\acom{For it.}
+
+\begin{lemma} \label{le:Srdim}
+    Let $ L \in \Grth$.  The following are equivalent:
+    \begin{enumerate}
+        \item $ L \in S_+^\mu$
+        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
+        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
+    \end{enumerate}
+    The same statement hold for $ S_-^\mu$ with the $ L^\gamma$ changed to $ L_\gamma$ above.
+\end{lemma}
+
 We can associate to $\tau$ an MV cycle.   
@@
         \{
-            L\in S^\mu : L\cap\cO^i\in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
+            L\in S^\mu : L_{\{1, \dots, i\}} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
         \}\,. 
@@
 % 
+\jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}
 
@@
 
-Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
-
-\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
-\acom{For it.}
-
 First, we consider
 \begin{equation*}
-Z(\tau)_1 := \{ L \in S^\mu : L \cap \cO^i \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
+Z(\tau)_1 := \{ L \in S^\mu : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
 %Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
 \end{equation*}
-From \cite[Corollary 9.7]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.
+
+Using Lemma \ref{le:Srdim}, we see that
+$$
+Z(\tau)_1 = \{ L \in S^\mu : \rdim L_{\{j, \dots, i\}} = \lambda(i)_j + \dots + \lambda(i)_i
+$$
+
+From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.
 Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
@@
 
-Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu$, then $ L \cap \cO^i \in S^{\mu(i)}$.  Thus, we get a map $$ f_i : Z(\tau)_1 \rightarrow S^{\mu(i)} \cap S_+^{\lambda(i)} $$
+Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu$, then $ L_{\{1, \dots, i\}} \in S^{\mu(i)}$.  Thus, we get a map $$ f_i : Z(\tau)_1 \rightarrow S^{\mu(i)} \cap S_+^{\lambda(i)} $$
 From the definition of $ Z(\tau)_1 $, we see that $ f_i(Z(\tau_1) = Z(\tau(i)_1)$.

### 2021-05-15 draft.tex
last changes

--- 2021-05-11 draft.tex
@@
 
-\documentclass[draft]{article}
+\documentclass[draft]{amsart}
 \usepackage{basic}
@@
 % 
-Moreover, it is not clear why one should care about the fusion product on bases. \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull}
+Moreover, it is not clear why one should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} except for positivity!
 
@@
 % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
-In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
-\[
-    \left[
-        \begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
-            & 1 & & & & & \\
-            &  & 1 & & & & \\
-        A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
-            &  & &  & 1 & & \\
-            A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
-            A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
-            A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
-    \end{BMAT}
-    \right]\,. 
-\]
+In pictures, and by example, the elements $A$ for 
+% $\mu=(3,2,2,1)$ 
+$\mu = (1,2,2,3)$ look like 
+\[
+    TODO: REDO 
+    % \left[
+    %     \begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
+    %         & 1 & & & & & \\
+    %         &  & 1 & & & & \\
+    %     A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
+    %         &  & &  & 1 & & \\
+    %         A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
+    %         A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
+    %         A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
+    % \end{BMAT}
+    % \right]\,. 
+\]
+% \[
+%     \left[\begin{BMAT}(e){c;cc;cc;ccc}{c;cc;cc;ccc} 
+%         0 & A_0 & A_1 & A_2 & A_3 & A_4 & A_5 & A_6\\
+%         0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
+%         0 & 0 & 0 & A_7 & A_8 & A_9 & A_{10} & A_{11}\\
+%         0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
+%         0 & 0 & 0 & 0 & 0 & A_{12} & A_{13} & A_{14}\\
+%         0 & 0 & 0 & 0 & 0 & 0 & 1 & 0\\
+%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
+%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
+%         \end{BMAT}\right]
+% \]
 %
@@
     g(A)_{ij} = 
-\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
+\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ij} t^{k-1} & i = j \\
+    % A^k_{ji} t^{k-1} & i = j \\
         % \text{ if $ i = j$} \\
-        - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
+        - \sum_{k=1}^{\mu_i} A^k_{ij} t^{k-1} & i \ne j
     %  \text{ if $ i \ne j$ }
@@
 \end{equation}
-where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
+where 
+% $A^k_{ji}$ 
+$A^k_{ij}$ is the $k$th entry from the left of the last row of the $\mu_i\times\mu_j$ block of $A$. 
 For example,
 \[
-    \left[
-        \begin{BMAT}(e){ccc;cc}{ccc;cc} 
-        0 & 1 & 0 & 0 & 0\\
-        0 & 0 & 1 & 0 & 0\\
-        A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
-        0 & 0 & 0 & 0 & 1\\
-        A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
-        \end{BMAT}\right]    
-        \mapsto 
-        \left[\begin{array}{rr}
-            t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
-            -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
-        \end{array}
-        \right]\,. 
+    % \left[
+    %     \begin{BMAT}(e){ccc;cc}{ccc;cc} 
+    %     0 & 1 & 0 & 0 & 0\\
+    %     0 & 0 & 1 & 0 & 0\\
+    %     A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
+    %     0 & 0 & 0 & 0 & 1\\
+    %     A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
+    %     \end{BMAT}\right]    
+    %     \mapsto 
+    %     \left[\begin{array}{rr}
+    %         t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
+    %         -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
+    %     \end{array}
+    %     \right]\,. 
+    TODO: REDO
 \]
@@
 \[
-    \left[
-        \begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
-        0 & 1 & 0 & 0 & 0 & 0\\
-        0 & 0 & 1 & 0 & 0 & 0\\
-        0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
-        0 & 0 & 0 & 0 & 1 & 0\\
-        0 & 0 & 0 & 0 & s & A_{23}^1\\
-        0 & 0 & 0 & 0 & 0 & s
-        \end{BMAT}
-    \right] \,.   
-    % \in \UU_{0,s}^{(1,1,0),(2,1,1)}
+    % \left[
+    %     \begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
+    %     0 & 1 & 0 & 0 & 0 & 0\\
+    %     0 & 0 & 1 & 0 & 0 & 0\\
+    %     0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
+    %     0 & 0 & 0 & 0 & 1 & 0\\
+    %     0 & 0 & 0 & 0 & s & A_{23}^1\\
+    %     0 & 0 & 0 & 0 & 0 & s
+    %     \end{BMAT}
+    % \right] \,.   
+TODO: REDO
 \]
@@
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
-$$ L \mapsto [t|_{\CC[t]^m/L} ]^{\tr}_{\beta_\mu} \,. $$
+$$ 
+TODO
+% L \mapsto [t|_{\CC[t]^m/L} ]^{\tr}_{\beta_\mu} \,. 
+$$
 %\acom{Up to transpose?!}
@@
     \label{cor:mvy}
-    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$ where $\n\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
+    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n_+ \cong\overline\Gr^\lambda\cap S^\mu_+$ where $\n_+\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
 \end{corollary}
@@
 See \cite[\S 4]{berenstein1988tensor}.
-
-\jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}
-
-\acom{Yes $i = m$ doesn't make sense.
+Below is an example.
+
+% \jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}
+
+% \acom{Yes $i = m$ doesn't make sense.
 Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2,\dots,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things.
@@
 
-For example, if 
-\[
-    \tau = \young(1112,23) 
-\]
-then
-\begin{gather*}
-%    \text{if } \tau = \young(1112,23) \text{ then } 
-\gt(\tau) = \begin{matrix}
+% \begin{example}
+    \[
+        \tau = \young(1112,23) \qquad \gt(\tau) = \begin{matrix}
             3 \\
@@
             4 & 2 & 0 
-   \end{matrix} \text{ and }
-   n_\bullet(\tau) = (1,0,1)\,. 
-\end{gather*}
+        \end{matrix} \qquad n_\bullet(\tau) = (1,0,1) %\,. 
+    \]
+% \end{example}
+% For example, if 
+% \[
+%     \tau = \young(1112,23) 
+% \]
+% then
+% \begin{gather*}
+% %    \text{if } \tau = \young(1112,23) \text{ then } 
+% \gt(\tau) = \begin{matrix}
+%        3 \\
+%        4 & 1 \\ 
+%        4 & 2 & 0 
+%    \end{matrix} \text{ and }
+%    n_\bullet(\tau) = (1,0,1)\,. 
+% \end{gather*}
 % 
@@
 % 
-We can associate to $\tau$ an MV cycle. 
+We can associate to $\tau$ the MV cycle $Z(\tau)=\overline{\mathring Z(\tau)}$ where
 %  
 \begin{equation*}
-    Z(\tau) = 
-     \overline{
+    \mathring Z(\tau) = 
+    %  \overline{
         \{
             L\in S^\mu : L\cap\cO^i\in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
-        \}\,. 
-     }
+        \} \,. 
+    %  }
 \end{equation*}
@@
 
-Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$. \acom{Sort out notation, do we no longer need $S_-, N_-$?}
 
@@
 On the other hand, by definition 
-$$Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}$$
+$$
+Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
+$$
 
@@
 $A\big|_{\CC^p}$ 
-the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. 
+the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$.
+If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
+\acom{We could also use a more compact notation like $A_{(p)}$}
 % \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}
@@
 Given $s\in\CC\setminus \{0\}$, and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
+% 
 \begin{equation*}
     X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
+\end{equation*}
+% 
+and
+% 
+\begin{equation*}
+    X(\tau')\ast_{\CC^\times} X(\tau'') = 
+    \left\{
+        (A,s)\in M_N(\CC) \times \CC^\times: 
+        A \in X(\tau') \ast_s X(\tau'') 
+    \right\}\,.
 \end{equation*}

### 2021-05-15 draft.tex

@@
 %
-We can associate to $\tau$ the MV cycle $Z(\tau)=\overline{\mathring Z(\tau)}$ where
+
+We will need the following definitions.
+\begin{definition}
+Let $ L \subset \OO^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
+$$
+\rdim(L) := \dim_\CC \OO^m/L
+$$
+
+If $ \gamma \subset \{1, \dots, m\}$, then we define
+\begin{gather*}
+    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
+L^\gamma:= L \cap \OO^\gamma \subset \OO^\gamma \quad L_\gamma := L / L^{\gamma^c} \subset \OO^\gamma
+\end{gather*}
+where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
+\end{definition}
+
+\begin{lemma}
+    For any $ L \in \Grth$ and any $ 
+    \gamma \subset \{1, \dots, m\} $, we have $ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L$.
+\end{lemma}
+We let $ D_\gamma(L) := \rdim L_\gamma$. By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
+
+\jcom{There is a discrepancy regarding $ \gamma$ and $ \gamma^c$.}
+
+Recall that $ S^\mu = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+
+\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
+\acom{For it.}
+
+\begin{lemma} \label{le:Srdim}
+    Let $ L \in \Grth$.  The following are equivalent:
+    \begin{enumerate}
+        \item $ L \in S_+^\mu$
+        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
+        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
+    \end{enumerate}
+    The same statement hold for $ S_-^\mu$ with the $ L^\gamma$ changed to $ L_\gamma$ above.
+\end{lemma}
+
+We can associate to $\tau$ an MV cycle.   
 %  
@@
         \{
-            L\in S^\mu : L\cap\cO^i\in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
-        \} \,. 
-    %  }
+            L\in S^\mu : L_{\{1, \dots, i\}} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
+        \}\,. 
+     }
 \end{equation*}
 % 
+\jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}
 
@@
 
-Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$. \acom{Sort out notation, do we no longer need $S_-, N_-$?}
-
-\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
-\acom{For it.}
-
 First, we consider
 \begin{equation*}
-Z(\tau)_1 := \{ L \in S^\mu : L \cap \cO^i \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
+Z(\tau)_1 := \{ L \in S^\mu : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
 %Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
 \end{equation*}
-From \cite[Corollary 9.7]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.
+
+Using Lemma \ref{le:Srdim}, we see that
+$$
+Z(\tau)_1 = \{ L \in S^\mu : \rdim L_{\{j, \dots, i\}} = \lambda(i)_j + \dots + \lambda(i)_i
+$$
+
+From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.
 Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.

### 2021-05-15 draft.tex
typo
revert to article class
changes to intro

@@
 
-\documentclass[draft]{amsart}
+\documentclass[draft]{article}
 \usepackage{basic}
@@
 % The Mirkovi\'c--Vybornov isomorphism
-In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_n)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $n\times n$ nilpotent orbits on the one hand
+In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_N)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $N\times N$ nilpotent orbits on the one hand
 % conjugacy classes of nilpotent matrices 
 and to Nakajima quiver varieties on the other hand. 
-This paper generalizes the first of these relations (an isomorphism) to families of slices by way of the Beilinson--Drinfeld Grassmannian. 
-Essential to \cite{mirkovic2007geometric}, this space is used to define a fusion (aka convolution) product on sheaves (representations) but can also be used to define a fusion product of MV cycles (bases).
-% 
-This product structure makes the vector space spanned by the MV cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019mirkovic}).
+This paper generalizes the first of these relations (an isomorphism) to families of slices in the Beilinson--Drinfeld Grassmannian. 
+Essential to \cite{mirkovic2007geometric}, this space is used to define a fusion (aka convolution) product on sheaves (representations) but can also be used to define a fusion product on certain cycles (bases).
+% 
+This product structure makes the vector space spanned by the Mirkovi\'c--Vilonen cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019mirkovic}).
 % conjectured by JEA and proved by BKK
 % 
-To quote from Mirkovi\'c and Vilonen:
+To quote from \cite{mirkovic2007geometric}:
 \begin{quotation}
@@
 %
-[Liaison]
-
 The purpose of this paper is to give a conceptually elementary way to compute this product in type $A$.
-We do not know how fruitful this work might be in the larger landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is as yet computationally expensive.
-% 
-Moreover, it is not clear why one should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} except for positivity!
+We do not know how fruitful this work might be in the larger landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is computationally expensive.
+%
+
+One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!
 
@@
     \mathring Z(\tau) = 
-    %  \overline{
         \{
@@
         \}\,. 
-     }
 \end{equation*}

### 2021-05-15 draft.tex
comments edits to groups section

@@
 % 
+Throughout this paper (unless indicated otherwise) the base field is $\CC$.
+
 % The Mirkovi\'c--Vybornov isomorphism
@@
 % are there other possibilities?? :S 
-The coweight lattice of $ G $ is $ \ZZ^m = \Hom(\CC^\times,T)$.
+We identify $\ZZ^m$ with the coweight lattice of $G$ and say that a coweight 
+% The coweight lattice of $ G $ is $ \ZZ^m = \Hom(\CC^\times,T)$.
 % TODO: Thank you - resolved!
@@
 % 
-The \textbf{dominant coweights} of $ G $ 
-% is
-are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) \in \ZZ^m $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
-% 
-A coweight $ \mu = (\mu_1, \dots, \mu_m) \in \ZZ^m$ is called \textbf{effective}, if $ \mu_j \ge 0 $ for all $ j$.
+% The \textbf{dominant coweights} of $ G $ are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) \in \ZZ^m $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
+% 
+% A coweight $ \mu = (\mu_1, \dots, \mu_m) \in \ZZ^m$ is called \textbf{effective} if $ \mu_j \ge 0 $ for all $ j$.
+% 
+$\nu = (\nu_1,\dots,\nu_m)$ is \new{dominant} if $\nu_1\ge\cdots\ge\nu_m$ and \new{effective} if $\nu_j\ge 0$ for all $j$.
 % We also need the notion of effective dominant coweight, 
@@
 % 
-So an effective dominant coweight $ \lambda $ is a partition of $|\lambda| = \lambda_1 + \cdots + \lambda_m\in\NN$, which we call the size of $ \lambda$.
+If $\nu\in\ZZ^m$ is both effective and dominant then it is a partition of size $|\nu| = \nu_1 + \cdots + \nu_m\in\NN$.
 %We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights. 
@@
 % 
-
-Given a coweight $\mu \in \ZZ^m$ and a point $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
+% Given a coweight $\mu \in \ZZ^m$ and a point $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
+Given $s\in\CC$ we define $(t-s)^\nu$ to be the diagonal matrix 
 % with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
@@
 \begin{bmatrix}
-    (t-s)^{\mu_1} \\
-    & (t-s)^{\mu_2} \\ 
+    (t-s)^{\nu_1} \\
+    & (t-s)^{\nu_2} \\ 
     & & \ddots \\
-    & & & (t-s)^{\mu_m}
+    & & & (t-s)^{\nu_m}
 \end{bmatrix} 
 \]
-which we will view in 
+which we can view in 
 % $\GL_m(K) $ 
-$G(K)$ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it 
-\acom{Add warning that we will also sometimes write $(t-s)^\mu$ for its image in 
-% $\GL_m(K)/\GL_m(R)$ 
-$G(K)/G(R)$ and we hope it will be clear? Only we haven't introduced this space yet.}
+$G(K)$ for any ring $ K $ containing $(t-s)^{-1}$ and $\CC[t]$. For example, $(t-s)^\nu\in G(K)$ for $ K = \Ks$ or $\CC(t)$. % A: Think R sb K; changed it
+
+\acom{We will also sometimes write $(t-s)^\mu$ for its image in $G(K)/G(R)$ and we hope it will be clear? Only we haven't introduced this space yet.}
 % Resolved
@@
 %
-\acom{maybe add that it's the same for $G(\cO)$.}
+
+\acom{Maybe add that it's the same for $G(\cO)$. Also, we are using the notation $G(R)$ in one paragraph and defining it in the next. Maybe introduced $M_m$ first? }
 

### 2021-05-15 draft.tex
edits to rels btw diff affgrs

@@
 
-\acom{Maybe add that it's the same for $G(\cO)$. Also, we are using the notation $G(R)$ in one paragraph and defining it in the next. Maybe introduced $M_m$ first? }
+\acom{Maybe add that it's the same for $G(\cO)$. Also, we are using the notation $G(R)$ in one paragraph and defining it in the next. Maybe introduced $M_m$ first?}
 
@@
 % \acom{Wait, I thought $\CC(t)$ is used in the Ran space version of the BD Gr.}
-Given such a lattice $ L $ and a point $ a \in \CC$, the \textbf{specialization} of $ L $ at $ a $ is defined as
-$$
-% L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
-L(a) := L \otimes_{\CC[t]} \cO_a, 
-% \text{ a lattice in } \cK_a^m.  
-$$
-a lattice in $\cK_a^m$. 
-If 
-% $ L(a) = L_0(\cO_a)$ 
-$L(a) = \cO_a^m$ then $L$ is said to be \textbf{trivial at $a$}. 
+Given such a lattice $ L $ and a point $ a \in \CC$, the \textbf{specialization} of $ L $ at $ a $ is a lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $. 
+If $L(a) = \cO_a^m$ then $L$ is said to be \textbf{trivial at $a$}. 
 % We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
@@
 
-%\includegraphics[width=\textwidth]{img/Capture d’écran, le 2021-02-17 à 13.03.10.png}}
+\acom{We are using fixed $m$ in the definitions here.}
 
@@
 % 
-We now define various versions of ``the'' affine Grassmannian which will play an important r\^ole in this paper.
+We now define various versions of ``the'' affine Grassmannian which will play an important role in this paper. 
+% 
+Each definition is made group-theoretically and then restated in ``lattice terms'' and in ``modular terms''. 
+% 
+We also sketch how to pass between descriptions.
+
+\acom{Can we review what exactly is meant by ``terms''? I think that we have (1) a coset space, (2) a moduli space, and (3) a torsor? ``Geometrically'', they are all the same?}
 
@@
 It is described in modular terms by 
+\acom{Can we introduce the first of these restatements as ``As a moduli space it is the set of..''}
 $$
@@
 $$
-
 We also have a lattice description 
+\acom{And this one as ``As a $G$-space..''}
 $$ 
@@
 \label{def:grplus}
-The \textbf{positive parts} of $\Gr $ and $\Grth$,  are defined by 
+The \textbf{positive part} of $\Gr $, resp.\ $\Grth$, is defined by 
 \begin{gather*}
-    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \\
+    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO)\,,\,\, % \\
     % \text{ and }      
-    {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
+    \text{resp.\ } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
 \end{gather*}
@@
 In lattice terms, $ \Gr^+$ (resp.\ ${\Grth}^+$) contains those lattices $L$ which are contained in $\cO^m$ (resp.\ $\CC[t]^m$).
+
+\acom{Maybe we can do without parentheses here.}
 % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
@@
 % 
-\begin{enumerate}
+\begin{proposition}
+    \label{pr:bd-th}
+    The map $\Grbd \rightarrow \Grth $ defined by $(V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty})$ is the inclusion $ G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])$ on fibres.
+In terms of lattices, it is given by $(L,s)\mapsto L$ and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on ambient spaces.
+\end{proposition}
+% 
+\begin{proposition}
+    \label{pr:polyno-taylor}
+    The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
+    \begin{equation*}
+    % \label{eq:grbdgrs}
+    \Gr_{0,s} \cong 
+        \begin{cases} 
+            \Gr \times \Gr_s & s \ne 0 \\
+            \Gr              & s = 0\,.
+        \end{cases}
+    \end{equation*}
+\end{proposition}
+\begin{proof}
+    This isomorphism is given in the modular realization by restricting the vector bundle and trivialization.
+
+    Suppose that $ s \ne 0 $. In the lattice realization, this is given by forming the specializations 
+    $$
+        L \mapsto (L(0), L(s))\,.
+    $$
+    Note that if $ L = g \CC[t]^m$ for $ g \in G([t,t^{-1}, (t-s)^{-1}])$, then 
+    $$
+        (L(0), L(s)) = (g \cO^m, g\cO^m_s)\,. 
+    $$
+    In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
+\end{proof}
+
+\begin{proposition}
+    \label{pr:grs-gr} There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
+
+    Combining with the above point, we obtain an isomorphism
+    $$
+    \tau_s : \Gr_{0,s} \rightarrow \Gr \times \Gr 
+    $$
+\end{proposition}
+
+% \begin{enumerate}
     % TODO: I think it makes more sense to put the first point at the end; it just relates (fibres of) the BD Gr to the ordinary Gr
     % \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
+\begin{comment}
     \item \label{it:bd-th}
@@
     Finally, it is given in lattice terms on the fibre over $s$ as the identity on the lattice $(L,s)\mapsto L$ and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
+\end{comment}
+\begin{comment}
     \item \label{it:polyno-taylor}
@@
     In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
-
+\end{comment}
+\begin{comment}
     \item \label{it:grs-gr} There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
@@
     %    \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
-\end{enumerate}
+\end{comment}
+% \end{enumerate}
 
@@
 I'm not that happy with the layout of this section, so feel free to reorganize it (maybe into Propositions?)}
+
+\acom{Begun. Not sure if it is what you had in mind.}
 

### 2021-05-15 draft.tex
questions in fusion section

@@
 % 
-Throughout this paper (unless indicated otherwise) the base field is $\CC$.
+Throughout this paper (unless indicated otherwise) the base field is $\CC$, but it does not have to be?
 
@@
 Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.  
-
+% 
 %Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (\cref{it:polyno-taylor,it:grs-gr} of \cref{ss:relsbtwgrs} preceding), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
 % TODO: cf https://tex.stackexchange.com/questions/256849/cleveref-change-behaviour-of-cref-to-use-the-abbreviated-form
-
-These isomorphisms $ \tau_s $ defined above glue together to a projection map
+% 
+The isomorphisms $ \tau_s $ defined above glue together to a projection map
 \begin{equation}
@@
 
-Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
+\acom{Question for Joel: What is the benefit of working with diagonals? Letting two points vary? What is an example of a structure that you can't see letting just one point vary as we do.}
+
+Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2)$. % \subset \Gr_{0, \CC^\times} $.
 % 
@@
 % \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
-Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.
-
-We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.
+Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $ from \Cref{pr:grs-gr},  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \CC^\times $  of $\Grbd$.
+
+\acom{Well you might not want but I think it would be good to tell the reader why we use the notation $\CC^\times$ for $\AA\setminus 0$ in $\AA$ or why we use the notation $\AA$ at all..
+E.g.\ do we know what happens for $\GL_m(k)$ over some other base field $k$.}
+
+We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ in $ \Grbd $.
 By construction, this is a flat family over $ \AA$.

### 2021-05-16 draft.tex
qfj re semiinfty fusion as attr of single con com

@@
 \label{def:sphfus}
-    The \textbf{fusion of two spherical Schubert varieties} 
-    $$ 
-        \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.
-    $$
+    The \textbf{fusion of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.
+    % $$ 
+    %     \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.
+    % $$
 \end{definition}
@@
 % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
-By a theorem of Zhu 
-\cite[Proposition 3.1.14]{zhu2016introduction}, $ \overline{\Gr}^{\lambda'} \ast_0 \overline{\Gr}^{\lambda''} $ is reduced and equal to  $ \overline{\Gr}^{\lambda' + \lambda''}$.
-
+By \cite[Proposition 3.1.14]{zhu2016introduction}, $ \overline{\Gr}^{\lambda'} \ast_0 \overline{\Gr}^{\lambda''} $ is reduced and equal to  $ \overline{\Gr}^{\lambda' + \lambda''}$.
 % Suppose that $ s \ne 0$.  
@@
 % \acom{Why $G(\CC[t])$. Because we are on the left side!}
+
+\acom{Sorry I keep changing (abbreviating) ``By a theorem of Zhu'', but is the citation not sufficient?}
 
@@
 \end{proof}
+
+\acom{Does $M_m(\CC[t])\cap G\xT[t^{-1}] = \{g\in M(\CC[t]):\det g\in\CC[t]\setminus0\}$?}
     % \acom{why ``and so''? bc orbits are connected?}
@@
 %
-\acom{we haven't defined $G_1$}
 
@@
 The lattice description of $ \cW_\mu \cap \Grth$ is given in Lemma \ref{le:Wmu} below.
-\acom{First lattice description that doesn't come for free?}
+%
+
+% \acom{First lattice description that doesn't come for free?}
 % 
@@
 \label{def:inftyorbits}
-    The \textbf{semi-infinite orbit} 
-$$ S^\mu = N_-(\cK)t^\mu \subset \Gr $$ 
-and the \textbf{fusion of  semi-infinite orbits} 
-$$ 
-    S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''} \to \AA \,.
-$$  
+    The \textbf{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $. 
+% and the \textbf{fusion of  semi-infinite orbits} 
+% $$ 
+% S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''} \to \AA \,.
+% $$  
 \end{definition}
+\acom{Commented out fusion part for now.
+Unsure about defining it as the family whose 0 fibre is $S^{\mu' + \mu''}$ and whose generic fibre is $S^{\mu'}\times S^{\mu''}$ up to $\tau$.
+Baumann--Riche consider the attracting set of $C_\mu = \sqcup_{\mu' + \mu'' = \mu } m(\tilde C_{\mu',\mu''})$ where $\tilde C_{\mu',\mu''}$ is a connected component of fixed points in $\Grbd\tilde\times\Grbd$.
+Maybe we can consider the attracting set of just one of these?}
+
 If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
@@
 %
+
 \jcom{I realized that this is not correct.  We can't just take the fusion here since we don't want to get the closure of these guys.  I will think about this further.}
-\acom{Two definitions in one. Unlike for spherical schubs}
+% \acom{Two definitions in one. Unlike for spherical schubs}
 

### 2021-05-16 draft.tex
reinstated examples plus a question about attr descr of UU

@@
 % 
-In order to prove this result, we will need to recall some results from Eisenbud--Saltman \cite{eisenbud1989rank}.
+In order to prove this result, we will need to recall some results from Eisenbud--Saltman \cite{eisenbud1989rank}. \acom{Too many results in one sentence.}
 %
@@
 % 
-\subsection{The Mirkovic--Vybornov slice}
+\subsection{The Mirkovi\'c--Vybornov slice}
 \label{ss:mvyslice} 
@@
 % In words, $A$ 
-is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
+is of the form 
+% a $\mu$ Jordan form matrix plus 
+$J_{0,\mu} + x$ where $x$ is a $\mu\times\mu$ block matrix with possibly nonzero entries in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
 % $\dim \TT_\mu = N^2 - \dim \OO_\mu$.
-In pictures, and by example, the elements $A$ for 
-% $\mu=(3,2,2,1)$ 
-$\mu = (1,2,2,3)$ look like 
-\[
-    TODO: REDO 
+
+By example, if 
+% $\mu=(3,2,2,1)$, 
+$\mu = (3,2)$ then $A\in\TT_\mu$ looks like 
+\[
+    \left[
+        \begin{BMAT}(e){ccc;cc}{ccc;cc} 
+        0 & 1 & 0 & 0 & 0\\
+        0 & 0 & 1 & 0 & 0\\
+        A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
+        0 & 0 & 0 & 0 & 1\\
+        A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
+        \end{BMAT}\right] 
+    % TODO: REDO 
     % \left[
@@
     % \end{BMAT}
-    % \right]\,. 
-\]
+    % \right] % \,. 
+\]
+for some $A_{ij}^k\in\CC$. 
 % \[
@@
 
-To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
+To $ A \in \TT_\mu$ we will associate the $m\times m$ matrix 
 of polynomials 
 % $ g(A) = \left( g(A)_{ij} \right)$ 
-$g(A)$
-in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
+$g(A)$ in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
 \begin{equation}
@@
     g(A)_{ij} = 
-\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ij} t^{k-1} & i = j \\
+\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j\,, \\
     % A^k_{ji} t^{k-1} & i = j \\
         % \text{ if $ i = j$} \\
-        - \sum_{k=1}^{\mu_i} A^k_{ij} t^{k-1} & i \ne j
+        - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j\,. 
     %  \text{ if $ i \ne j$ }
@@
 \end{equation}
-where 
-% $A^k_{ji}$ 
-$A^k_{ij}$ is the $k$th entry from the left of the last row of the $\mu_i\times\mu_j$ block of $A$. 
-For example,
-\[
-    % \left[
+$A^k_{ji}$ denotes the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
+%
+
+Continuing with the $\mu=(3,2)$ example, 
+\[
+    % A = \left[
     %     \begin{BMAT}(e){ccc;cc}{ccc;cc} 
@@
     %     \end{BMAT}\right]    
-    %     \mapsto 
-    %     \left[\begin{array}{rr}
-    %         t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
-    %         -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
-    %     \end{array}
-    %     \right]\,. 
-    TODO: REDO
+    % \Longrightarrow 
+        g(A) = 
+        \left[\begin{array}{rr}
+            t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
+            -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
+        \end{array}
+        \right]\,. 
+    % TODO: REDO
 \]
@@
 % 
-\acom{Can add sentence before making next definition? To the effect of ``In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.''}
+\acom{Can add sentence before making next definition?
+To the effect of ``In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.'' Should also say what is up with the hidden transpose.}
+
 \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
@@
 So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
+
 For example, elements of $ \UU_{0,s}^{(1,1,0),(2,1,1)}$ look like 
 % 
-% $\UU_{0,0}^{(?),(?)}$ entries look like 
-% \[
-%     \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
-%         0 & 1 & 0 & 0 & 0\\
-%         0 & 0 & 1 & 0 & 0\\
-%         0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
-%         0 & 0 & 0 & 0 & 1\\
-%         0 & 0 & 0 & 0 & 0
-%         \end{BMAT}\right]    
-%         % \mapsto 
-%         % \left[\begin{array}{rr}
-%         %     t^{3} & 0 \\
-%         %     -A_{12}^2 t - A_{12}^1 & t^{2}
-%         % \end{array}\right]
-% \]
-\[
-    % \left[
-    %     \begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
-    %     0 & 1 & 0 & 0 & 0 & 0\\
-    %     0 & 0 & 1 & 0 & 0 & 0\\
-    %     0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
-    %     0 & 0 & 0 & 0 & 1 & 0\\
-    %     0 & 0 & 0 & 0 & s & A_{23}^1\\
-    %     0 & 0 & 0 & 0 & 0 & s
-    %     \end{BMAT}
-    % \right] \,.   
-TODO: REDO
+\[
+    \left[
+        \begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
+        0 & 1 & 0 & 0 & 0 & 0\\
+        0 & 0 & 1 & 0 & 0 & 0\\
+        0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
+        0 & 0 & 0 & 0 & 1 & 0\\
+        0 & 0 & 0 & 0 & s & A_{23}^1\\
+        0 & 0 & 0 & 0 & 0 & s
+        \end{BMAT}
+    \right] \,.   
+% TODO: REDO
 \]
@@
 \acom{Mention that any other decomposition $\nu' + \nu''$ of $\mu' + \mu''$ will give a slice $\UU^{\nu',\nu''}_{0,\AA}$ with the same zero fibre.}
+
+\acom{These $\UU$'s should also have attr descriptions. What are they?}
 

### 2021-05-16 draft.tex
caught sum micro typos

@@
 
+\acom{This whole section is a big question mark.
+The beginning of the rising action section is more expository, developmental, and the climax is in turn more of a rising action.
+The true climax is probably the fusion section, section 7.}
+
 \section{Rising Action}
@@
     Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
-    \begin{enumerate}
-        \item $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. %\acom{Should we describe this map somewhere? Earlier?}
-        \item The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $((0,\lambda'), (s,\lambda''))$.
-        \item $ L \in G(\CC[t]) t^{\lambda'} (t-s)^{\lambda''}$.
+    \begin{enumerate}[label=(\roman*)]
+        \item \label{it:schub-pos} $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. %\acom{Should we describe this map somewhere? Earlier?}
+        \item \label{it:schub-jt} The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $((0,\lambda'), (s,\lambda''))$.
+        \item \label{it:schub-lat} $ L \in G(\CC[t]) t^{\lambda'} (t-s)^{\lambda''}$.
         % \acom{why no $G(\CC[t])$-coset?}
@@
 The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$.
-This shows that (i) implies (ii) and the logic can be reversed to see that (ii) implies (i).
+This shows that \cref{it:schub-pos} implies \cref{it:schub-jt} and the logic can be reversed to see that \cref{it:schub-jt} implies \cref{it:schub-pos}.
 % \acom{is this map $v + L \mapsto v + L(0)$?} \jcom{yes} \marginpar[]{*}
@@
 % $ (t-s)^{\lambda''} \in G(\CC\xt)$. 
-$ (t-s)^{\lambda''} \in G(\cO)$. In this way, we see that (iii) implies (ii) and the logic can be reversed to get the equivalence.
+$ (t-s)^{\lambda''} \in G(\cO)$. In this way, we see that \cref{it:schub-lat} implies \cref{it:schub-jt} and the logic can be reversed to get equivalence.
 \end{proof}
@@
 Let $ L \in \Grth^+$.  The following are equivalent:
-\begin{enumerate}
-    \item $ L \in \cW_\mu$.
-            \item $ L = \Sp_{\CC[t]}(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1}^m p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
-    \item  For all $ i $, 
+\begin{enumerate}[label=(\roman*)]
+    \item \label{it:slice} $ L \in \cW_\mu$.
+    \item \label{it:basis} $ L = \Sp_{\CC[t]}(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1}^m p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$.
+    \item \label{it:t-act} For all $ i $, 
     $$ t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \min(\mu_i, \mu_j), 1 \le j \le m \}) + L. $$
@@
 In this way, we can ensure that $ p_{ij} $ has degree less than $ \min(\mu_i, \mu_j)$.
-Thus (i) implies (ii).
-
-    Suppose that $ L = \Sp_{\CC[t]}(v_1, \dots, v_m)$ as in (ii).  Then
+    Thus \cref{it:slice} implies \cref{it:basis}.
+
+    Suppose that $ L = \Sp_{\CC[t]}(v_1, \dots, v_m)$ as in \cref{it:basis}.  Then
     $$t^{\mu_i} e_i - v_i \in \Sp_\CC(\{t^k e_j :  k < \min(\mu_i, \mu_j), 1 \le j \le m \})  \,. $$
-    Hence (ii) implies (iii).
-
-    Finally, given (iii), then we can see $ v_i := t^{\mu_i} e_i - \sum_{j=1}^m p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \min(\mu_i,\mu_j) $.
+    Hence \cref{it:basis} implies \cref{it:t-act}.
+
+    Finally, given \cref{it:t-act}, then we can see $ v_i := t^{\mu_i} e_i - \sum_{j=1}^m p_{ij} e_j \in L $ for some $ p_{ij} \in \CC[t]$ of degree less than $ \min(\mu_i,\mu_j) $.
 It is easy to see that $ L = \Sp_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.
 
-    Finally to show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(  t^k e_i : 0 \le k < \mu_i, 1 \le i \le m) + L$. 
+    To show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(  t^k e_i : 0 \le k < \mu_i, 1 \le i \le m) + L$. 
     % 
@@
     % 
-    This follows immediately from (iii).
+    This follows immediately from \cref{it:t-act}.
     % 
@@
 % 
+\acom{Don't have $P$ notation, replacing (in lemma below) with $\ZZ^m$ for now..}
 \begin{lemma}
 \label{le:inftyfusiskl} % as in lands in KL slice 
-    Let $\mu',\mu'' \in P$ and $\mu = \mu' + \mu''$. Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
+    Let $\mu',\mu'' \in \ZZ^m$ and $\mu = \mu' + \mu''$. Under the map $ \Grbd \rightarrow \Grth$ the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
 \end{lemma}
@@
 Since $ g(A) \in M_m(\CC[t]) \cap G_1(\Oinf)t^\mu$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
-(Alternatively, we can see that $ g(A) \CC[t]^m$ satisfies the condition (ii) from Lemma \ref{le:Wmu}.)
+(Alternatively, we can see that $ g(A) \CC[t]^m$ satisfies the condition of \cref{it:basis} from \Cref{le:Wmu}.)
 
@@
 $$ 
-TODO
-% L \mapsto [t|_{\CC[t]^m/L} ]^{\tr}_{\beta_\mu} \,. 
-$$
-%\acom{Up to transpose?!}
+L \mapsto [t|_{\CC[t]^m/L} ]^{\tr}_{\beta_\mu} \,. 
+$$
 \end{theorem}
 % 
+\acom{Should we say what $^{tr}$ means?}
 
@@
 % lattice).
-In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).
+In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$. 
+% (for example the fibre of this map over $ 0 $ is $ \CC $). 
 % \acom{Grammar of `write using the map' is iffy. Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}
@@
 \begin{definition}
-Let $ L \subset \OO^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
-$$
-\rdim(L) := \dim_\CC \OO^m/L
-$$
-
-If $ \gamma \subset \{1, \dots, m\}$, then we define
+Let $ L \subset \CC[t]^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
+$$
+\rdim(L) := \dim_\CC \CC[t]^m/L\,. 
+$$
+% 
+If $ \gamma \subset \{1, \dots, m\}$, we define
 \begin{gather*}
@@
 
+\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$?}
+
 \begin{lemma}
@@
 
-Recall that $ S^\mu = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+Recall that $ S^\mu_- = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
 
@@
 
-We can associate to $\tau$ an MV cycle.   
+We can associate to $\tau$ an MV cycle as follows. Let    
 %  
@@
             L\in S^\mu : L_{\{1, \dots, i\}} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
-        \}\,. 
+        \}
 \end{equation*}
+and $Z(\tau) = \overline{\mathring Z(\tau)}$. 
 % 
@@
 \begin{equation*}
-Z(\tau)_1 := \{ L \in S^\mu : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
+Z(\tau)_1 := \{ L \in S^\mu : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
 %Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
@@
 $$
-Z(\tau)_1 = \{ L \in S^\mu : \rdim L_{\{j, \dots, i\}} = \lambda(i)_j + \dots + \lambda(i)_i
+Z(\tau)_1 = \{ L \in S^\mu : \rdim L_{\{j, \dots, i\}} = \lambda(i)_j + \dots + \lambda(i)_i \}
 $$
@@
 $$
-
+\acom{Need $L_{\{1,..,i\}}$}
 \jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}

### 2021-05-16 draft.tex
hit sect 7

@@
 
-\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$?}
+\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$? Also, don't we want $L_\gamma = R^m/L^{\gamma^c}$}
 
@@
 $$
-\acom{Need $L_{\{1,..,i\}}$}
+\acom{Need $L_{\{1,..,i\}}$ here.}
+
 \jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}
@@
 % 
+\begin{theorem}
+    \label{pr:govsasirrecs}
+    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
+\end{theorem}
+% 
 Given $A \in M_N(\CC)$ we denote by 
@@
 
-Given $s\in\CC\setminus \{0\}$, and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
+Given $s\in\CC^\times$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
 % 
 \begin{equation*}
-    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
+    \mathring X(\tau',\tau'')_{0,s} 
+    % X(\tau')\ast_s \mathring X(\tau'') 
+    = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}
 \end{equation*}
@@
 \begin{equation*}
-    X(\tau')\ast_{\CC^\times} X(\tau'') = 
+    % X(\tau')\ast_{\CC^\times} X(\tau'') = 
+    \mathring X(\tau',\tau'')_{0,\CC^\times} = 
     \left\{
@@
     % and set $\mu = \mu' + \mu''$. If $s\ne 0$, then 
-    The image of $X(\tau')\ast_s X(\tau'')$ under the isomorphism of \Cref{th:OTGrW} is dense in $Z(\tau')\ast_s Z(\tau'')$. 
+    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is dense in $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$. 
     % \[
@@
     $$
-    L\cap \CC[t]^i = l
+    % L\cap \CC[t]^i = l
+    l\cong L_{1,..,i}
     $$
@@
 \begin{corollary}
-    $X'\ast_0 X'' \cong Z'\ast_0 Z''$ 
+    The image of $X'\ast_0 X''$ in $\cong Z'\ast_0 Z''$ is dense and $\iota(X(\tau),X(\tau',\tau'')) = \iota(Z(\tau),Z(\tau')\circ Z(\tau''))$. 
 \end{corollary}
@@
 
-\begin{theorem}
-    \label{pr:govsasirrecs}
-    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
-\end{theorem}
-\acom{$\overline{X(\tau)}$ vs $Z(\tau) = \overline{al;sdj}$}
 \begin{corollary}

### 2021-05-17 draft.tex
Updates from Overleaf

--- 2021-05-16 draft.tex
@@
 
-We begin with some new notation. Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of shape $\lambda$ and weight $\mu$. 
+We begin with the following definitions.
+\begin{definition}
+Let $ L \subset \OO^m$ be a point in $ \Gr_+$.  We define the relative dimension of $L $ by
+$$
+\rdim L := \dim_\CC \OO^m/L\,. 
+$$
+% 
+If $ \gamma \subset \{1, \dots, m\}$, we define two lattices $ L^\gamma, L_\gamma $ in $ \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) $ by
+\begin{gather*}
+%    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
+L^\gamma:= L \cap \OO^\gamma  \qquad L_\gamma := L / L^{\gamma^c} \subset \OO^m / \OO^{\gamma^c} = \OO^\gamma
+\end{gather*}
+where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
+\end{definition}
+We will also need the analogous definitions when $ \OO$ is replaced by $ \CC[t]$ and $L \in \Grth_+$.
+
+We record the following easy observations.
+\begin{lemma} \label{le:rdimTrans} Let $ L \in \Gr_+$.
+\begin{enumerate}
+    \item For any $ 
+    \gamma \subset \{1, \dots, m\} $, we have $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
+    \item For any $ \gamma_1 \subset \gamma_2 \subset \{1, \dots, m\}$, we have $$ (L_{\gamma_1})_{\gamma_2} = L_{\gamma_2}
+$$
+\end{enumerate}
+\end{lemma}
+
+For any $ L \in \Gr_+ $ and $\gamma \subset \{1, \dots, m\} $, we let $ D_\gamma(L) := \rdim L^\gamma = \rdim L_{\gamma^c}$.
+By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
+
+Recall that $ S^\mu_- = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+
+\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
+\acom{For it.}
+
+\begin{lemma} \label{le:Srdim}
+    Let $ L \in \Gr_+$.  The following are equivalent:
+    \begin{enumerate}
+        \item $ L \in S_+^\mu$
+        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
+        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
+    \end{enumerate}
+    Similarly, the following are equivalent:
+        \begin{enumerate}
+        \item $ L \in S_-^\mu$
+        \item $ \rdim L^{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for all $ i = 1, \dots, m $.
+        \item $ \rdim L_{\{1, \dots, i\}} = \mu_{1} + \dots + \mu_i$ for $ i  = 1, \dots, m$.
+    \end{enumerate}
+\end{lemma}
+
+We now introduce some notation related to Young tableaux. Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of shape $\lambda$ and weight $\mu$. 
 %Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
@@
 \begin{aligned}
-n_\bullet(\tau)_{i,j} &= \lambda(i+1)_j - \lambda(i)_j \\
+n_\bullet(\tau)_{i,j} &= \lambda(i+1)_j - \lambda(i)_j = \text{ \# of boxes on the $j$th row of $\tau $ filled with $ i+1$}  \\
 (i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
@@
 
-We will need the following definitions.
-\begin{definition}
-Let $ L \subset \CC[t]^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
-$$
-\rdim(L) := \dim_\CC \CC[t]^m/L\,. 
-$$
-% 
-If $ \gamma \subset \{1, \dots, m\}$, we define
-\begin{gather*}
-    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
-L^\gamma:= L \cap \OO^\gamma \subset \OO^\gamma \quad L_\gamma := L / L^{\gamma^c} \subset \OO^\gamma
-\end{gather*}
-where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
-\end{definition}
-
-\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$?}
-
-\begin{lemma}
-    For any $ L \in \Grth$ and any $ 
-    \gamma \subset \{1, \dots, m\} $, we have $ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L$.
-\end{lemma}
-We let $ D_\gamma(L) := \rdim L_\gamma$. By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
-
-\jcom{There is a discrepancy regarding $ \gamma$ and $ \gamma^c$.}
-
-Recall that $ S^\mu_- = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
-
-\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
-\acom{For it.}
-
-\begin{lemma} \label{le:Srdim}
-    Let $ L \in \Grth$.  The following are equivalent:
-    \begin{enumerate}
-        \item $ L \in S_+^\mu$
-        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
-        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
-    \end{enumerate}
-    The same statement hold for $ S_-^\mu$ with the $ L^\gamma$ changed to $ L_\gamma$ above.
-\end{lemma}
-
 We can associate to $\tau$ an MV cycle as follows. Let    
@@
 \begin{equation*}
-Z(\tau)_1 := \{ L \in S^\mu : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
+Z(\tau)_1 := \{ L \in S^\mu \cap \Gr_+ : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
 %Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
@@
 $$
-Z(\tau)_1 = \{ L \in S^\mu : \rdim L_{\{j, \dots, i\}} = \lambda(i)_j + \dots + \lambda(i)_i \}
-$$
+Z(\tau)_1 = \{ L \in \Gr_+ : \rdim L_{\{j, \dots, i\}} = \lambda(i)_j + \dots + \lambda(i)_i \text{ for all $ 1 \le j \le i \le m $} \}
+$$
+
+\jcom{We could write that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ filled with $ 1, \dots, i $.}
 
@@
 Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
+(In \cite{kamnitzer2010mirkovic}, we worked with $  G(\OO) \backslash G(\cK)$, which we identify with $ \Gr $ using $ [g] \mapsto [g^{-1}]$.)
+
 We also note that $Z(\tau_1) \cap \Gr^\lambda$ is dense in $ Z(\tau_1)$.  
-\jcom{Need to justify this last sentence.}
+\jcom{Need to justify this last sentence.
+There are two possibilities.
+Either we can use compute the MV polytope corresponds to $ \tau $ and show that it lies in the Weyl polytope for $ \lambda $ (is this done anywhere in the literature) or we could use the Mirkovic-Vybornov isomorphism.}
 
@@
 $$
-Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
-$$
-\acom{Need $L_{\{1,..,i\}}$}
+Z(\tau)_2 \subset \{ L \in S^\mu : L_{\{1, \dots, i\}} \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
+$$
+
 \jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}
@@
 \subsection{Fusion of MVCs via BD MVy}
+
+\jcom{Anne, can you reorganize this section to start with $ X(\tau) $ and then do the fusion afterwards?}
+
 Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.

### 2021-05-17 draft.tex

@@
 
+We will need the following definitions.
+\begin{definition}
+Let $ L \subset \CC[t]^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
+$$
+\rdim(L) := \dim_\CC \CC[t]^m/L\,. 
+$$
+% 
+If $ \gamma \subset \{1, \dots, m\}$, we define
+\begin{gather*}
+    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
+L^\gamma:= L \cap \OO^\gamma \subset \OO^\gamma \quad L_\gamma := L / L^{\gamma^c} \subset \OO^\gamma
+\end{gather*}
+where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
+\end{definition}
+
+\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$? Also, don't we want $L_\gamma = R^m/L^{\gamma^c}$}
+
+\begin{lemma}
+    For any $ L \in \Grth$ and any $ 
+    \gamma \subset \{1, \dots, m\} $, we have $ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L$.
+\end{lemma}
+We let $ D_\gamma(L) := \rdim L_\gamma$. By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
+
+\jcom{There is a discrepancy regarding $ \gamma$ and $ \gamma^c$.}
+
+Recall that $ S^\mu_- = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+
+\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
+\acom{For it.}
+
+\begin{lemma} \label{le:Srdim}
+    Let $ L \in \Grth$.  The following are equivalent:
+    \begin{enumerate}
+        \item $ L \in S_+^\mu$
+        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
+        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
+    \end{enumerate}
+    The same statement hold for $ S_-^\mu$ with the $ L^\gamma$ changed to $ L_\gamma$ above.
+\end{lemma}
+
 We can associate to $\tau$ an MV cycle as follows. Let    
@@
 $$
+\acom{Need $L_{\{1,..,i\}}$ here.}
 

### 2021-05-17 draft.tex
my last changes reinstated

@@
 
-We will need the following definitions.
-\begin{definition}
-Let $ L \subset \CC[t]^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
-$$
-\rdim(L) := \dim_\CC \CC[t]^m/L\,. 
-$$
-% 
-If $ \gamma \subset \{1, \dots, m\}$, we define
-\begin{gather*}
-    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
-L^\gamma:= L \cap \OO^\gamma \subset \OO^\gamma \quad L_\gamma := L / L^{\gamma^c} \subset \OO^\gamma
-\end{gather*}
-where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
-\end{definition}
-
-\acom{I started changing $\OO$ to $\CC[t]$ but we should rather change it to $R$ as we'll want this notation for $R = \CC[t]$ as well as $\cO$? Also, don't we want $L_\gamma = R^m/L^{\gamma^c}$}
-
-\begin{lemma}
-    For any $ L \in \Grth$ and any $ 
-    \gamma \subset \{1, \dots, m\} $, we have $ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L$.
-\end{lemma}
-We let $ D_\gamma(L) := \rdim L_\gamma$. By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
-
-\jcom{There is a discrepancy regarding $ \gamma$ and $ \gamma^c$.}
-
-Recall that $ S^\mu_- = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
-
-\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
-\acom{For it.}
-
-\begin{lemma} \label{le:Srdim}
-    Let $ L \in \Grth$.  The following are equivalent:
-    \begin{enumerate}
-        \item $ L \in S_+^\mu$
-        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
-        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
-    \end{enumerate}
-    The same statement hold for $ S_-^\mu$ with the $ L^\gamma$ changed to $ L_\gamma$ above.
-\end{lemma}
-
 We can associate to $\tau$ an MV cycle as follows. Let    
@@
 $$
-\acom{Need $L_{\{1,..,i\}}$ here.}
 
@@
 Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
-% 
 \begin{theorem}
@@
 \end{theorem}
+% 
 % 
@@
 \begin{proposition}
-    % Given $b_{Z'},b_{Z''}\in\CC[N]$, 
-    % Let $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ 
-    % be such that $t^{\lambda'}Z' = X(\tau')$ and $t^{\lambda''}Z'' = X(\tau'')$. 
-    % and set $\mu = \mu' + \mu''$. If $s\ne 0$, then 
     The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is dense in $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$. 
@@
     % L\cap \CC[t]^i = l
-    l\cong L_{1,..,i}
+    l = L_{1,..,i}
     $$
@@
 
+\begin{theorem}
+    \label{pr:govsasirrecs}
+    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
+\end{theorem}
+\acom{$\overline{X(\tau)}$ vs $Z(\tau) = \overline{al;sdj}$}
 \begin{corollary}

### 2021-05-17 draft.tex
qualms with L gamma

@@
 where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
+\acom{I suggest replacing $\mathbb O$ by $R$, and $L/L^{\gamma^c}$ by $(L + R^{\gamma^c})/R^{\gamma^c}$ because that's what we're doing.
+In a lower triangular $g(A)$ columns ${i+1..m}$ cannot be used to eliminate entries in rows ${i+1..m}$ in the first $i$ columns over $\CC[t]$ or $\CC\xt$.}
 \end{definition}
@@
 \jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}
+\acom{And $\{1,\dots,i\}$ etc.}
 
@@
 
-First, we consider
+First, we consider \acom{add \texttt{mathring}'s to these $Z$'s?}
 \begin{equation*}
@@
 \jcom{We could write that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ filled with $ 1, \dots, i $.}
+\acom{\emoji{thumbsup}}
 
@@
 Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
-(In \cite{kamnitzer2010mirkovic}, we worked with $  G(\OO) \backslash G(\cK)$, which we identify with $ \Gr $ using $ [g] \mapsto [g^{-1}]$.)
+(In \cite{kamnitzer2010mirkovic}, we worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using $ [g] \mapsto [g^{-1}]$.)
 

### 2021-05-17 draft.tex
nearly done 7

@@
     \label{cor:mvy}
-    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n_+ \cong\overline\Gr^\lambda\cap S^\mu_+$ where $\n_+\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
+    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu_+$ where $\n\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
 \end{corollary}
@@
 
-    %See computation 5.3.9 and Lemma 5.4.2 (ignore its proof) of \url{http://www.math.toronto.edu/adranows/athesis.pdf}. 
+% See computation 5.3.9 and Lemma 5.4.2 (ignore its proof) of \url{http://www.math.toronto.edu/adranows/athesis.pdf}. 
 \end{proof}
@@
 
-Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
+Given $A \in M_N(\CC)$ we denote by $A\big|_{\CC^p}$ the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$.
+If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
+% TODO: address 
+% \acom{We could also use a more compact notation like $A_{(p)}$}
+% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}
+
+Under the isomorphism of \Cref{cor:mvy} the MV cycles correspond to the so-called \new{generalized orbital varieties}. 
+We can also associate a generalized orbital variety $X(\tau)$ directly to a semistandard tableau $\tau$ by taking the closure of the top-dimensional 
+% \acom{speak to this?} 
+irreducible component of
+% from $\tau\in YT(\lambda)_\mu$ by 
+\[
+\mathring X(\tau) = 
+% \overline{
+    \{
+        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
+    \}\,. 
+% }    
+\]
+% 
+We do not know whether $\mathring X(\tau)$ is in general irreducible.
+% reduced or has embedded components.
+
 \begin{theorem}
@@
 % 
-% 
-Given $A \in M_N(\CC)$ we denote by 
-% $A\big|_{\CC^i}$ 
-$A\big|_{\CC^p}$ 
-the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$.
-If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
-\acom{We could also use a more compact notation like $A_{(p)}$}
-% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}
-
+We will use this theorem to describe intersection multiplicities in the fusion of two MV cycles. 
+% 
+Let us begin by introducing a ``fusion of generalized orbital varieties''. 
+% 
+Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as in previous sections.
+% 
 Given $s\in\CC^\times$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
@@
         (A,s)\in M_N(\CC) \times \CC^\times: 
-        A \in X(\tau') \ast_s X(\tau'') 
+        A \in \mathring X(\tau',\tau'')_{0,s} 
     \right\}\,.
@@
 \begin{proof}
-    % We wish to apply \Cref{prop:dth}. Nope
-    % We will also need \Cref{le:Grl1l2}. Nope 
-    % Consider the following diagram.
-    % \[
-    % \begin{tikzcd}
-    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
-    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
-    % \end{tikzcd}
-    % \]
-    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
-    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
-    % % 
-    Let $A\in X(\tau')\ast_s X(\tau'')$ and $i = 1,\dots, m$.  
-    % Denote by 
-    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
-    The lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
-    $$    
-    % L\cap \CC[t]^i = l
-    l = L_{1,..,i}
-    $$
-    where $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denotes the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
-    %
-
-By definition of $\UU^{\mu',\mu''}$ we have $A\big|_{\CC^{|\mu(i)|}}\in\UU^{\mu'(i),\mu''(i)}_{0,s}$ and by definition of $X(\tau')\ast_s X(\tau'')$, $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$.
-So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$ and
-% \Gr^{\lambda'(i)}\times \Gr^{\lambda''(i)}$ so 
-$(l(0),l(s))\in Z(\tau')\times Z(\tau'')$.
-
-So $A\in\dots$ iff $g(A)\in\dots$ 
+% 
+Fix $A\in \mathring X(\tau',\tau'')_{0,s} $ and $i = 1,\dots, m$.
+
+Let $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denote the $\CC[t]$-submodule generated by the first $i$ standard basis vectors. \acom{Probably don't need to repeat this.}
+
+The lattices $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ and $L=g(A)\CC[t]^m$ are related by the equality $ l = L_{[i]}$ where recall $L_{[i]} = L + \CC[t]^{[i+1,m]} / \CC[t]^{[i+1,m]}\subset \CC[t]^m/\CC[t]^{[i+1,m]} = \CC[t]^i$.
+
+By definition of $\UU^{\mu',\mu''}$ we have $A\big|_{\CC^{|\mu(i)|}}\in\UU^{\mu'(i),\mu''(i)}_{0,s}$ and by definition of $X(\tau',\tau'')_{0,s}$, $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$.
+So, by \Cref{th:OTGrW}, $l = L_{[i]}\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$.
+On the other hand, also by definition of $\UU^{\mu',\mu''}$, we have $L\in S^{\mu',\mu''}$ and consequently $l\in S^{\mu'(i),\mu''(i)}$.
+
+Therefore, as $i$ varies, we see that the pair $(L(0),L(s))\in S^{\mu'}\times S^{\mu''}$ is such that $(L_{[i]}(0),L_{[i]}(s)) \in \Gr^{\lambda'(i)}\times\Gr^{\lambda''(i)}$ and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$.
+
+For the converse we use the fact that the map $A\mapsto g(A)$ is an isomorphism of $\overline{\OO}^{\lambda',\lambda''}_{0,\AA}\cap\UU^{\mu',\mu''}_{0,\AA}$ and $\overline{\Gr}^{\lambda',\lambda''}_{0,\AA}\cap S^{\mu',\mu''}_{0,\AA}$ which restricts to an isomorphism of generalized orbital varieties and MV cycles in the zero fibre.
+\acom{Better way to say?}
+Given $L\in\mathring Z(\tau') \ast_{\CC^\times}\mathring Z(\tau'')$ let $A$ be such that $L = g(A)\CC[t]^i$. Is it clear that $A\in\mathring X(\tau',\tau'')_{0,s}$? 
+Do we need that there exists $(A',A'')\in M_{N'}\times M_{N''}$ such that $L(0) = g(A')\cO^m$ and $L(s) = g(A'')\cO^m$, and that we could take $A'\oplus A''=A$ up to some conjugation that puts $A'\oplus A''\in\TT_\mu$ which is possible because $\TT_\mu$ intersects $\OO^{\lambda',\lambda''}_{0,\AA}$ transversely?
 \end{proof}
 %
-% 
-In analogy with the Beilinson--Drinfeld construction \acom{add loc cit} we define $X(\tau')\ast_0 X(\tau'')$ to be the zero fibre of the family $\overline{\bigcup_{s\in\CC\setminus\{0\}} X(\tau')\ast_s X(\tau'')}$ in $M_N(\CC)$.
+
+Now, in analogy with the Beilinson--Drinfeld construction \acom{add loc cit} we define $X(\tau',\tau'')_{0,0}$ to be the zero fibre of the Zariski closure of $X(\tau',\tau'')_{0,\CC^\times}$ in $M_N(\CC)$.
 % 
 \begin{corollary}
-    The image of $X'\ast_0 X''$ in $\cong Z'\ast_0 Z''$ is dense and $\iota(X(\tau),X(\tau',\tau'')) = \iota(Z(\tau),Z(\tau')\circ Z(\tau''))$. 
+    The image of $\mathring X(\tau',\tau'')_{0,0}$ in $\mathring Z(\tau')\ast_0 \mathring Z(\tau'')$ is dense. In particular 
+    $$\iota(X(\tau),X(\tau',\tau'')) = \iota(Z(\tau),Z(\tau')\circ Z(\tau''))\,.$$
 \end{corollary}
 % 
-Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
-% from $\tau\in YT(\lambda)_\mu$ by 
-\[
-% X(\tau) = 
-% \overline{
-    \{
-        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
-    \}\,. 
-% }    
-\]
-Then $\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
-%
-
-\begin{theorem}
-    \label{pr:govsasirrecs}
-    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
-\end{theorem}
-\acom{$\overline{X(\tau)}$ vs $Z(\tau) = \overline{al;sdj}$}
-\begin{corollary}
-    $X'\ast_0 X''$ is a union of GOVs.
-\end{corollary}
-\begin{proof}
-    Since $X'\ast_0 X''\subset \overline{\OO}^\lambda\cap\TT_\mu\cap\n$\dots 
-\end{proof}
-
-\begin{proposition}(\cite{baumann2019mirkovic})
-    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
-    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''$ and weight $\mu',\mu''$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
-    Then $Z'\ast_0 Z''$ is a union of MVCs
-    % \begin{equation}
-        % Z'\ast_0 Z'' = \bigcup Z(\tau)
-        % \label{eq:tabmult}
-        % % Z_\tau\ast Z_\sigma 
-        % m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
-        % = 
-        % % \sum_{Z\in\cZ(\lambda)_\mu} 
-        % \sum_{\tau\in S(\lambda)_\mu}
-        % i\left(
-        %     X(\tau), X(\tau')\circ X(\tau'')
-        % \right) [Z(\tau)]\,. 
-    % \end{equation}
-    with $i\left(X(\tau), X(\tau')\circ X(\tau'')\right)$ copies of $Z(\tau)$ showing up. 
-\end{proposition}
-% 
-\acom{Closures missing? Here and elsewhere?}
-% 
-\begin{proof}
-    Since $X'\ast_0 X'' \cong Z'\ast_0 Z''$ and GOVs go to MVCs 
-\end{proof}
-
 \begin{conjecture}

### 2021-05-18 draft.tex
mtg w joel changes

@@
 In a lower triangular $g(A)$ columns ${i+1..m}$ cannot be used to eliminate entries in rows ${i+1..m}$ in the first $i$ columns over $\CC[t]$ or $\CC\xt$.}
+\jcom{If you think that it sounds better with $ \OO $ replaced by $ R$, then I won't object to the change.
+Note that the first sentence won't quite make sense ``let $ L \subset \OO^m$ be a point in $ \Gr_+$'', we would have to write ``let $ L \subset R^m$ be a lattice''.}
+\jcom{$ L /L^{\gamma^c} $ is the image of $ L $ in $ \OO^m / \OO^{\gamma^c}$ since the kernel of the map $ L \rightarrow \OO^m / \OO^{\gamma^c}$ is precisely $L^{\gamma^c} $, so I don't think that there is any problem here.
+Again, if you think that it is better, I won't object to your suggested change.}
+\jcom{Your question made me wonder about the following: how do we know that $ L_\gamma$ is a lattice?  (or $ L^\gamma$ for that matter)}
 \end{definition}
@@
 
-For any $ L \in \Gr_+ $ and $\gamma \subset \{1, \dots, m\} $, we let $ D_\gamma(L) := \rdim L^\gamma = \rdim L_{\gamma^c}$.
+For any $ L \in \Gr_+ $ and $\gamma \subset \{1, \dots, m\} $, we let $ D_\gamma(L) := \rdim L^\gamma = \rdim L - \rdim L_{\gamma^c}$.
 By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
@@
 
-First, we consider \acom{add \texttt{mathring}'s to these $Z$'s?}
+First, we consider \acom{add \texttt{mathring}'s to these $Z$'s?} \jcom{Sure.}
 \begin{equation*}
@@
 
-Under the isomorphism of \Cref{cor:mvy} the MV cycles correspond to the so-called \new{generalized orbital varieties}. 
-We can also associate a generalized orbital variety $X(\tau)$ directly to a semistandard tableau $\tau$ by taking the closure of the top-dimensional 
+Under the isomorphism of \Cref{cor:mvy} the MV cycle $Z(\tau)$ corresponds to the \new{generalized orbital varieties} $X(\tau)$ which is obtained by taking the closure of the top-dimensional 
 % \acom{speak to this?} 
@@
 % reduced or has embedded components. 
+\jcom{I guess we need to assume that $ \mu $ is dominant here.}
 
@@
 \end{theorem}
-% 
-We will use this theorem to describe intersection multiplicities in the fusion of two MV cycles. 
-% 
-Let us begin by introducing a ``fusion of generalized orbital varieties''. 
+
+\jcom{Please add a reference to your paper here and also a lemma which states that under the Mirkovic-Vybornov isomorphism $ \mathring X(\tau) $ is mapped isomorphically onto $ \mathring Z(\tau) $.}
+% 
+We will use this theorem to describe the fusion of two MV cycles. 
+% 
+Let us begin by introducing a ``fusion of generalized orbital varieties'' to match. 
 % 
@@
 % 
-and
+\jcom{Maybe instead write ``$A \big|_{\CC^{|\mu(i)|}}$ has Jordan type $ (\lambda'(i), 0), (\lambda''(i), s)$}
 % 
@@
 
+\jcom{We never quite defined $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$ so maybe we should write this down somewhere.
+Once we do this, I'm pretty sure that we will not get ``dense'' but an equality.}
+
 \begin{proof}
@@
 
-The lattices $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ and $L=g(A)\CC[t]^m$ are related by the equality $ l = L_{[i]}$ where recall $L_{[i]} = L + \CC[t]^{[i+1,m]} / \CC[t]^{[i+1,m]}\subset \CC[t]^m/\CC[t]^{[i+1,m]} = \CC[t]^i$.
+The lattices $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ and $L=g(A)\CC[t]^m$ are related by the equality $ l = L_{[i]}$ where recall $L_{[i]} = (L + \CC[t]^{[i+1,m]}) / \CC[t]^{[i+1,m]}\subset \CC[t]^m/\CC[t]^{[i+1,m]} = \CC[t]^i$.
 
@@
 
-Therefore, as $i$ varies, we see that the pair $(L(0),L(s))\in S^{\mu'}\times S^{\mu''}$ is such that $(L_{[i]}(0),L_{[i]}(s)) \in \Gr^{\lambda'(i)}\times\Gr^{\lambda''(i)}$ and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$.
-
-For the converse we use the fact that the map $A\mapsto g(A)$ is an isomorphism of $\overline{\OO}^{\lambda',\lambda''}_{0,\AA}\cap\UU^{\mu',\mu''}_{0,\AA}$ and $\overline{\Gr}^{\lambda',\lambda''}_{0,\AA}\cap S^{\mu',\mu''}_{0,\AA}$ which restricts to an isomorphism of generalized orbital varieties and MV cycles in the zero fibre.
-\acom{Better way to say?}
-Given $L\in\mathring Z(\tau') \ast_{\CC^\times}\mathring Z(\tau'')$ let $A$ be such that $L = g(A)\CC[t]^i$. Is it clear that $A\in\mathring X(\tau',\tau'')_{0,s}$? 
+Therefore, as $i$ varies, we see that the pair $(L(0),L(s))\in S^{\mu'}\times S^{\mu''}$ is such that 
+$$(L_{[i]}(0),L_{[i]}(s))  = (L(0)_{[i]},L(s)_{[i]}) \in \Gr^{\lambda'(i)}\times\Gr^{\lambda''(i)}$$ 
+and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$.
+
+For the converse we use the fact that the map $A\mapsto g(A)$ is an isomorphism of $\overline{\OO}^{\lambda',\lambda''}_{0,\AA}\cap\UU^{\mu',\mu''}_{0,\AA}$ and $\overline{\Gr}^{\lambda',\lambda''}_{0,\AA}\cap S^{\mu',\mu''}_{0,\AA}$ which restricts to an isomorphism of generalized orbital varieties and MV cycles in fibres.
+\acom{Better way to say?} \jcom{I think that you can just rewrite this first half as if and only if and drop the second half. }
+Given $L\in\mathring Z(\tau') \ast_{\CC^\times}\mathring Z(\tau'')$ let $A$ be such that $L = g(A)\CC[t]^i$. \acom{But, is it clear that $A\in\mathring X(\tau',\tau'')_{0,s}$?} 
 Do we need that there exists $(A',A'')\in M_{N'}\times M_{N''}$ such that $L(0) = g(A')\cO^m$ and $L(s) = g(A'')\cO^m$, and that we could take $A'\oplus A''=A$ up to some conjugation that puts $A'\oplus A''\in\TT_\mu$ which is possible because $\TT_\mu$ intersects $\OO^{\lambda',\lambda''}_{0,\AA}$ transversely?
@@
     % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
-    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
-    % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
+    Let $\tau$ be the tableau got by taking the union of the rows of $\tau'$ and $\tau''$ and ordering the entries in each row smallest to largest. 
+    % Note that $\tau$ has shape $\lambda$, weight $\mu$, and  Lusztig datum equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
     Then 
     \begin{equation}
-        i(\tau, 
-        % \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}
-        % Z_1 \circ Z_2 
-        \tau' \circ \tau''
-        ) = 1 \,. 
+        i(Z(\tau), Z(\tau') \circ Z(\tau'')) = 1 \,. 
     \end{equation}

### 2021-05-18 draft.tex
almost fixed

@@
 %!TEX program = lualatex
-
-\documentclass[draft]{article}
+% 
+\documentclass{article} % [draft] TODO: use this at the end to check for overfills 
 \usepackage{basic}
@@
 % Working title: 
-\title{How to compute the fusion product of MV cycles in type A}
+\title{How to compute the fusion product of MV cycles in type $A$}
 \author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
@@
 %
+\acom{We need to assume that $\mu' +\mu''$ is dominant in the theorem below. The assumption for \Cref{th:TmuWmu} is also missing.} 
+% 
 \begin{theorem}
@@
 
-Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}.
+Restricting to the zero fibre and applying $\tau_0$ we recover \cite[Corollary~5.2.2]{dthesis}, itself a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}, the ordinary affine Grassmannian version of \Cref{th:OGrl}.
+% 
+% \acom{The ordinary Gr should be called static. Really onomotopoeic. In opposition with moving. }
 % 
@@
 
+Denote by $[a,b]$ the interval $\{a,a+1,\dots,b-1,b\}\subset\NN$. If $a = 1$ just write $[b]$, and if $a = b$ just write $\{a\}$. 
+% If a = b? Just write $\{b\}$ 
 We begin with the following definitions.
 \begin{definition}
-Let $ L \subset \OO^m$ be a point in $ \Gr_+$.  We define the relative dimension of $L $ by
-$$
-\rdim L := \dim_\CC \OO^m/L\,. 
-$$
-% 
-If $ \gamma \subset \{1, \dots, m\}$, we define two lattices $ L^\gamma, L_\gamma $ in $ \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) $ by
+Let $ L \subset \cO^m$ be a point in $ \Gr_+$.  We define the relative dimension of $L $ by
+$$
+\rdim L := \dim_\CC \cO^m/L\,. 
+$$
+% 
+If $ \gamma \subset [m]$, we define two lattices $ L^\gamma, L_\gamma $ in $ \cO^\gamma := \Sp_{\cO}(e_i : i \in \gamma) $ by
 \begin{gather*}
 %    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
-L^\gamma:= L \cap \OO^\gamma  \qquad L_\gamma := L / L^{\gamma^c} \subset \OO^m / \OO^{\gamma^c} = \OO^\gamma
+L^\gamma:= L \cap \cO^\gamma  \qquad L_\gamma := L / L^{\gamma^c} \subset \cO^m / \cO^{\gamma^c} = \cO^\gamma
 \end{gather*}
-where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
-\acom{I suggest replacing $\mathbb O$ by $R$, and $L/L^{\gamma^c}$ by $(L + R^{\gamma^c})/R^{\gamma^c}$ because that's what we're doing.
+where $ \gamma^c := [m] \setminus \gamma$.
+% 
+% \acom{I suggest replacing $\mathbb O$ by $R$, and $L/L^{\gamma^c}$ by $(L + R^{\gamma^c})/R^{\gamma^c}$ because that's what we're doing.
 In a lower triangular $g(A)$ columns ${i+1..m}$ cannot be used to eliminate entries in rows ${i+1..m}$ in the first $i$ columns over $\CC[t]$ or $\CC\xt$.}
-\jcom{If you think that it sounds better with $ \OO $ replaced by $ R$, then I won't object to the change.
+% \jcom{If you think that it sounds better with $ \OO $ replaced by $ R$, then I won't object to the change.
 Note that the first sentence won't quite make sense ``let $ L \subset \OO^m$ be a point in $ \Gr_+$'', we would have to write ``let $ L \subset R^m$ be a lattice''.}
-\jcom{$ L /L^{\gamma^c} $ is the image of $ L $ in $ \OO^m / \OO^{\gamma^c}$ since the kernel of the map $ L \rightarrow \OO^m / \OO^{\gamma^c}$ is precisely $L^{\gamma^c} $, so I don't think that there is any problem here.
+% \jcom{$ L /L^{\gamma^c} $ is the image of $ L $ in $ \OO^m / \OO^{\gamma^c}$ since the kernel of the map $ L \rightarrow \OO^m / \OO^{\gamma^c}$ is precisely $L^{\gamma^c} $, so I don't think that there is any problem here.
 Again, if you think that it is better, I won't object to your suggested change.}
-\jcom{Your question made me wonder about the following: how do we know that $ L_\gamma$ is a lattice?  (or $ L^\gamma$ for that matter)}
+% \jcom{Your question made me wonder about the following: how do we know that $ L_\gamma$ is a lattice?  (or $ L^\gamma$ for that matter)}
 \end{definition}
-We will also need the analogous definitions when $ \OO$ is replaced by $ \CC[t]$ and $L \in \Grth_+$.
+We will also need the analogous definitions when $ \cO$ is replaced by $ \CC[t]$ and $L \in \Grth_+$.
 
@@
     \item For any $ 
-    \gamma \subset \{1, \dots, m\} $, we have $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
-    \item For any $ \gamma_1 \subset \gamma_2 \subset \{1, \dots, m\}$, we have $$ (L_{\gamma_1})_{\gamma_2} = L_{\gamma_2}
+    \gamma \subset [m] $, we have $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
+    \item For any $ \gamma_1 \subset \gamma_2 \subset [m]$, we have $$ (L_{\gamma_1})_{\gamma_2} = L_{\gamma_2}
 $$
@@
 
-For any $ L \in \Gr_+ $ and $\gamma \subset \{1, \dots, m\} $, we let $ D_\gamma(L) := \rdim L^\gamma = \rdim L - \rdim L_{\gamma^c}$.
+For any $ L \in \Gr_+ $ and $\gamma \subset [m]$, we let $ D_\gamma(L) := \rdim L^\gamma = \rdim L - \rdim L_{\gamma^c}$.
 By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
+\acom{We should introduce $D_\gamma$ briefly.}
 
 Recall that $ S^\mu_- = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
-
-\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
-\acom{For it.}
+% 
+% \jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
+% \acom{For it.}
 
@@
         \item $ L \in S_+^\mu$
-        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
-        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
+        \item $ \rdim L^{[i]} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
+        \item $ \rdim L_{[i+1,m]} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
     \end{enumerate}
@@
         \item $ L \in S_-^\mu$
-        \item $ \rdim L^{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for all $ i = 1, \dots, m $.
-        \item $ \rdim L_{\{1, \dots, i\}} = \mu_{1} + \dots + \mu_i$ for $ i  = 1, \dots, m$.
+        \item $ \rdim L^{[i+1,m]} = \mu_{i+1} + \dots + \mu_m$ for all $ i = 1, \dots, m $.
+        \item $ \rdim L_{[i]} = \mu_{1} + \dots + \mu_i$ for $ i  = 1, \dots, m$.
     \end{enumerate}
@@
 
-We now introduce some notation related to Young tableaux. Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of shape $\lambda$ and weight $\mu$. 
+We now introduce some notation related to Young tableaux. Denote by $YT(\lambda)_\mu$ the set of (possibly semistandard) Young tableaux of shape $\lambda$ and weight $\mu$. 
 %Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
@@
 See \cite[\S 4]{berenstein1988tensor}.
-Below is an example.
+Below is an example with $\lambda = (4,2)$ and $\mu = (3,2,1)$.
 
@@
 
-We can associate to $\tau$ an MV cycle as follows. Let    
+We can associate to $\tau$ the MV cycle $Z(\tau)$ by taking the closure of the top-dimensional irreducible component of  
 %  
@@
         \{
-            L\in S^\mu : L_{\{1, \dots, i\}} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
-        \}
+            L\in S^\mu : L_{[i]} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
+        \}\,. 
 \end{equation*}
-and $Z(\tau) = \overline{\mathring Z(\tau)}$. 
-% 
-\jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}
-\acom{And $\{1,\dots,i\}$ etc.}
+% and $Z(\tau) = \overline{\mathring Z(\tau)}$. 
+% 
+% \jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}
+% \acom{And $\{1,\dots,i\}$ etc.}
 
@@
 We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}.
+\acom{Many alsos}
 \begin{proposition}
     \label{pr:newmvdes}
-    $Z(\tau)$ is the MV cycle whose Lusztig datum with respect to $ \vi $ is $n_\bullet(\tau)$. 
+    $Z(\tau)$ is the MV cycle whose Lusztig datum (with respect to the standard reduced word) is $n_\bullet(\tau)$. 
 \end{proposition}
@@
     The proof of this theorem follows the same strategy as in \cite{dranowski2020generalized}.
-\jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}    
-\acom{I've been meaning to update the paper. It's peppered with ``typos''.}
-
-First, we consider \acom{add \texttt{mathring}'s to these $Z$'s?} \jcom{Sure.}
+% \jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}    
+% \acom{I've been meaning to update the paper. It's peppered with ``typos''.}
+
+First, we consider 
+% \acom{add \texttt{mathring}'s to these $Z$'s?} \jcom{Sure.}
 \begin{equation*}
-Z(\tau)_1 := \{ L \in S^\mu \cap \Gr_+ : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
+\mathring Z(\tau)_1 := \{ L \in S^\mu \cap \Gr_+ : L_{[i]} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
 %Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
@@
 $$
-Z(\tau)_1 = \{ L \in \Gr_+ : \rdim L_{\{j, \dots, i\}} = \lambda(i)_j + \dots + \lambda(i)_i \text{ for all $ 1 \le j \le i \le m $} \}
-$$
-
-\jcom{We could write that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ filled with $ 1, \dots, i $.}
-\acom{\emoji{thumbsup}}
-
-From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.
-Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
-(In \cite{kamnitzer2010mirkovic}, we worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using $ [g] \mapsto [g^{-1}]$.)
-
-We also note that $Z(\tau_1) \cap \Gr^\lambda$ is dense in $ Z(\tau_1)$.  
+\mathring Z(\tau)_1 = \{ L \in \Gr_+ : \rdim L_{[j,i]} = \lambda(i)_j + \dots + \lambda(i)_i \text{ for all $ 1 \le j \le i \le m $} \}
+$$
+where note that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ of weight $ 1, \dots, i $.
+% \jcom{We could write that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ filled with $ 1, \dots, i $.}
+% \acom{\emoji{thumbsup}}
+
+From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ \mathring Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.
+In particular it is irreducible.
+Thus, its closure is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
+(In \cite{kamnitzer2010mirkovic}, the third author worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using $ [g] \mapsto [g^{-1}]$.) \acom{Maybe we should avoid using square brackets as we haven't used them yet?}
+
+We also note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$.  
 \jcom{Need to justify this last sentence.
@@
 
-Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu$, then $ L_{\{1, \dots, i\}} \in S^{\mu(i)}$.  Thus, we get a map $$ f_i : Z(\tau)_1 \rightarrow S^{\mu(i)} \cap S_+^{\lambda(i)} $$
-From the definition of $ Z(\tau)_1 $, we see that $ f_i(Z(\tau_1) = Z(\tau(i)_1)$.
-From above $ \Gr^{\lambda(i)} \cap f_i(Z(\tau(i)_1))$ is a dense constructible subset of $Z(\tau(i)_1)$.
-Since $ Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)} \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ is a dense constructible subset of $ Z(\tau_1) $.
+Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu_-$, then $ L_{[i]} \in S^{\mu(i)}_-$ so we get a map 
+$$ 
+f_i : \mathring Z(\tau)_1 \rightarrow S^{\mu(i)}_- \cap S_+^{\lambda(i)} \,. 
+$$
+From the definition of $ \mathring Z(\tau)_1 $, we see that $ f_i(\mathring Z(\tau)_1 )= \mathring Z(\tau(i))_1$.  
+From above/again $ \Gr^{\lambda(i)} \cap f_i(\mathring Z(\tau(i))_1)$ is a dense constructible subset of $\mathring Z(\tau(i))_1$.  
+Since $ \mathring Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)}_- \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ \acom{$\cap \mathring Z(\tau)_1$?} is a dense constructible subset of $ \mathring Z(\tau)_1 $.
 
 Working with all $ i $ at once, we conclude that
-$$ Z(\tau)_2 := \bigcap_{i=1}^m f_i^{-1}(S^{\mu(i)} \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $$
-is a dense constructible subset of $ Z(\tau)_1$.  Thus $\overline{Z(\tau)_2} = \overline{Z(\tau)_1}$.
+$$ 
+\mathring Z(\tau)_2 := \bigcap_{i=1}^m f_i^{-1}(S^{\mu(i)}_- \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) 
+$$
+is a dense constructible subset of $\mathring Z(\tau)_1$. \acom{Again are we maybe missing capping with $Z$ in the above $:=$?} Thus $\overline{\mathring Z(\tau)_2} = \overline{\mathring Z(\tau)_1}$.
 
@@
 $$
-Z(\tau)_2 \subset \{ L \in S^\mu : L_{\{1, \dots, i\}} \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
+\mathring Z(\tau)_2 \subset \mathring Z(\tau). % \{ L \in S^\mu : L_{[i]} \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
 $$
@@
 
-\jcom{Anne, can you reorganize this section to start with $ X(\tau) $ and then do the fusion afterwards?}
+% \jcom{Anne, can you reorganize this section to start with $ X(\tau) $ and then do the fusion afterwards?}
 
@@
 
+Let $\tau\in YT(\lambda)_\mu$ with $\mu$ dominant.
 Under the isomorphism of \Cref{cor:mvy} the MV cycle $Z(\tau)$ corresponds to the \new{generalized orbital varieties} $X(\tau)$ which is obtained by taking the closure of the top-dimensional
@@
 % reduced or has embedded components. 
-\jcom{I guess we need to assume that $ \mu $ is dominant here.}
-
-\begin{theorem}
-    \label{pr:govsasirrecs}
-    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
-\end{theorem}
-
-\jcom{Please add a reference to your paper here and also a lemma which states that under the Mirkovic-Vybornov isomorphism $ \mathring X(\tau) $ is mapped isomorphically onto $ \mathring Z(\tau) $.}
+% \jcom{I guess we need to assume that $ \mu $ is dominant here.}
+\begin{lemma}
+    Under the Mirkovi\'c--Vybornov isomorphism $\mathring X(\tau)$ is mapped isomorphically onto $\mathring Z(\tau)$. 
+\end{lemma}
+
+% \jcom{Please add a reference to your paper here and also a lemma which states that under the Mirkovic-Vybornov isomorphism $ \mathring X(\tau) $ is mapped isomorphically onto $ \mathring Z(\tau) $.}
 % 
@@
 % 
-\jcom{Maybe instead write ``$A \big|_{\CC^{|\mu(i)|}}$ has Jordan type $ (\lambda'(i), 0), (\lambda''(i), s)$}
+\jcom{Maybe instead write ``$A \big|_{\CC^{|\mu(i)|}}$ has Jordan type $ (\lambda'(i), 0), (\lambda''(i), s)$} \acom{Okay. So no need for the first paragraph of this section?}
 % 
@@
 \begin{proposition}
-    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is dense in $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$. 
+    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$. 
     % \[
@@
 and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$.
-
-For the converse we use the fact that the map $A\mapsto g(A)$ is an isomorphism of $\overline{\OO}^{\lambda',\lambda''}_{0,\AA}\cap\UU^{\mu',\mu''}_{0,\AA}$ and $\overline{\Gr}^{\lambda',\lambda''}_{0,\AA}\cap S^{\mu',\mu''}_{0,\AA}$ which restricts to an isomorphism of generalized orbital varieties and MV cycles in fibres.
-\acom{Better way to say?} \jcom{I think that you can just rewrite this first half as if and only if and drop the second half. }
-Given $L\in\mathring Z(\tau') \ast_{\CC^\times}\mathring Z(\tau'')$ let $A$ be such that $L = g(A)\CC[t]^i$. \acom{But, is it clear that $A\in\mathring X(\tau',\tau'')_{0,s}$?} 
-Do we need that there exists $(A',A'')\in M_{N'}\times M_{N''}$ such that $L(0) = g(A')\cO^m$ and $L(s) = g(A'')\cO^m$, and that we could take $A'\oplus A''=A$ up to some conjugation that puts $A'\oplus A''\in\TT_\mu$ which is possible because $\TT_\mu$ intersects $\OO^{\lambda',\lambda''}_{0,\AA}$ transversely?
+% 
+% For the converse we use the fact that the map $A\mapsto g(A)$ is an isomorphism of $\overline{\OO}^{\lambda',\lambda''}_{0,\AA}\cap\UU^{\mu',\mu''}_{0,\AA}$ and $\overline{\Gr}^{\lambda',\lambda''}_{0,\AA}\cap S^{\mu',\mu''}_{0,\AA}$ which restricts to an isomorphism of generalized orbital varieties and MV cycles in fibres.
+% \acom{Better way to say?} \jcom{I think that you can just rewrite this first half as if and only if and drop the second half. }
+% Given $L\in\mathring Z(\tau') \ast_{\CC^\times}\mathring Z(\tau'')$ let $A$ be such that $L = g(A)\CC[t]^i$. \acom{But, is it clear that $A\in\mathring X(\tau',\tau'')_{0,s}$?} 
+% Do we need that there exists $(A',A'')\in M_{N'}\times M_{N''}$ such that $L(0) = g(A')\cO^m$ and $L(s) = g(A'')\cO^m$, and that we could take $A'\oplus A''=A$ up to some conjugation that puts $A'\oplus A''\in\TT_\mu$ which is possible because $\TT_\mu$ intersects $\OO^{\lambda',\lambda''}_{0,\AA}$ transversely?
 \end{proof}
@@
 
-Now, in analogy with the Beilinson--Drinfeld construction \acom{add loc cit} we define $X(\tau',\tau'')_{0,0}$ to be the zero fibre of the Zariski closure of $X(\tau',\tau'')_{0,\CC^\times}$ in $M_N(\CC)$.
+Now, in analogy with the Beilinson--Drinfeld construction \acom{add loc cit} we define $X(\tau',\tau'')_{0,0}$ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ in $M_N(\CC)\times\CC$.
 % 
 \begin{corollary}
-    The image of $\mathring X(\tau',\tau'')_{0,0}$ in $\mathring Z(\tau')\ast_0 \mathring Z(\tau'')$ is dense. In particular 
-    $$\iota(X(\tau),X(\tau',\tau'')) = \iota(Z(\tau),Z(\tau')\circ Z(\tau''))\,.$$
+    % The image of $\mathring X(\tau',\tau'')_{0,0}$ in $\mathring Z(\tau')\ast_0 \mathring Z(\tau'')$ is dense. In particular 
+    $\iota(X(\tau),X(\tau',\tau'')) = \iota(Z(\tau),Z(\tau')\circ Z(\tau''))\,.$
 \end{corollary}
+% 
+To prove this we require the following main result of \cite{dthesis}.
+\begin{theorem}
+    \label{pr:govsasirrecs}
+    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
+\end{theorem}
 % 
@@
     \begin{equation}
-        i(Z(\tau), Z(\tau') \circ Z(\tau'')) = 1 \,. 
+        \iota(Z(\tau), Z(\tau') \circ Z(\tau'')) = 1 \,. 
     \end{equation}
 \end{conjecture}
-\jcom{Rather than adding the Lusztig data, how can you produce $\tau$ directly from $\tau', \tau''$?
+% 
+% RESOLVED COMMENTS
+% \jcom{Rather than adding the Lusztig data, how can you produce $\tau$ directly from $\tau', \tau''$?
 I guess you can just add the GT patterns, so for tableaux you just take the union of the rows, is that right?}
-
-\acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
+% 
+% \acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
 % 
@@
 $$
-b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
+b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} \iota\left(
     Z, Z' \ast_0 Z''

### 2021-05-20 draft.tex
mv cycles table

@@
 
-Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
+Throughout the paper, we fix $ m \in \NN$.  We let $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
 % are there other possibilities?? :S 
@@
 \acom{We will also sometimes write $(t-s)^\mu$ for its image in $G(K)/G(R)$ and we hope it will be clear? Only we haven't introduced this space yet.}
+\jcom{I think that we do this infrequently enough that it is not a problem and there is no need to mention it here.}
 % Resolved
@@
 \acom{Maybe add that it's the same for $G(\cO)$. Also, we are using the notation $G(R)$ in one paragraph and defining it in the next. Maybe introduced $M_m$ first?}
+\jcom{I don't consider that to be the definition of $ G(R)$.  The definition is the invertible $ m \times m$ matrices with coefficients in $ R $.  So I think that everything is fine.}
 
@@
 % \acom{Wait, I thought $\CC(t)$ is used in the Ran space version of the BD Gr.}
-Given such a lattice $ L $ and a point $ a \in \CC$, the \textbf{specialization} of $ L $ at $ a $ is a lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $. 
+Given such a lattice $ L $ and a point $ a \in \CC$, the \textbf{specialization} of $ L $ at $ a $ is the lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $. 
 If $L(a) = \cO_a^m$ then $L$ is said to be \textbf{trivial at $a$}. 
@@
 \acom{We are using fixed $m$ in the definitions here.}
+\jcom{Added sentence fixing $m $ above.}
 
@@
 % G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
-Set $\AA = \AA^1$ viewed as the subset $\PP\setminus \{\infty\}$ of $\PP$. Let $\Vtriv$ denote the trivial rank $ m $ vector bundle. 
-% 
-We now define various versions of ``the'' affine Grassmannian which will play an important role in this paper. 
-% 
-Each definition is made group-theoretically and then restated in ``lattice terms'' and in ``modular terms''. 
+%Set $\AA = \AA^1$ viewed as the subset $\PP\setminus \{\infty\}$ of $\PP$. Let $\Vtriv$ denote the trivial rank $ m $ vector bundle. 
+% 
+We now define various versions of the affine Grassmannian which will play important roles in this paper. 
+% 
+Each definition is made group-theoretically and then restated as a moduli space of vector bundles and as a moduli space of lattices.
 % 
@@
 
-\acom{Can we review what exactly is meant by ``terms''? I think that we have (1) a coset space, (2) a moduli space, and (3) a torsor? ``Geometrically'', they are all the same?}
+In these definitions, $ \Vtriv$ denote the trivial rank $ m $ vector bundle.
+
+%\acom{Can we review what exactly is meant by ``terms''? I think that we have (1) a coset space, (2) a moduli space, and (3) a torsor? ``Geometrically'', they are all the same?}
+
+%\jcom{Yes, that is true.
+But what is the problem?
+It is nice to describe spaces in different ways.
+Technically, none of our definitions are ``precise'', since we only describe the $ \CC$-points.
+We should describe each one a functor, if we wanted to be completely precise.
+And then we would have three isomorphic functors.
+But let's not do this.}
+
+\acom{Oh, I meant could we review for my own benefit.
+But I do think it is also nice, for readability, to use (slightly) different words to describe the different descriptions.
+Hence my suggestions following Def.\ 1.}
+
+\jcom{I made some changes}
 
@@
 \end{definition}    
-It is described in modular terms by 
-\acom{Can we introduce the first of these restatements as ``As a moduli space it is the set of..''}
+It is the moduli space of vector bundles with trivializations,
+%\acom{Can we introduce the first of these restatements as ``As a moduli space it is the set of..''}
 $$
@@
 $$
-We also have a lattice description 
+It is also a moduli space of lattices, 
 \acom{And this one as ``As a $G$-space..''}
@@
 In lattice terms, $ \Gr^+$ (resp.\ ${\Grth}^+$) contains those lattices $L$ which are contained in $\cO^m$ (resp.\ $\CC[t]^m$).
-
-\acom{Maybe we can do without parentheses here.}
+% TODO: can we? 
+% \acom{Maybe we can do without parentheses here.}
 % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
@@
     \label{pr:bd-th}
-    The map $\Grbd \rightarrow \Grth $ defined by $(V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty})$ is the inclusion $ G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])$ on fibres.
-In terms of lattices, it is given by $(L,s)\mapsto L$ and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on ambient spaces.
+    There is a map $\Grbd \rightarrow \Grth $ defined in the following equivalent ways:
+    \begin{enumerate}
+        \item in modular terms as $$(V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty}) \, ;$$
+        \item in the fibres over $ s \in \AA$ as the inclusion $$
+        G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,;$$
+        \item in terms of lattices, it is given by $(L,s)\mapsto L$, using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on ambient spaces. 
+    \end{enumerate}
 \end{proposition}
 %
+
+The following result is the factorization property of the Beilinson-Drinfeld Grassmannian (see \cite[Prop. 3.13]{zhu2016introduction}).
 \begin{proposition}
@@
     \end{equation*}
+    In the modular realization, this isomorphism is given by restricting the vector bundle and trivialization.
+
+    Suppose that $ s \ne 0 $. In the lattice realization, this is given by forming the specializations 
+    $$
+        L \mapsto (L(0), L(s))\,.
+    $$
+    Note that if $ L = g \CC[t]^m$ for $ g \in G([t,t^{-1}, (t-s)^{-1}])$, then 
+    $$
+        (L(0), L(s)) = (g \cO^m, g\cO^m_s)\,. 
+    $$
+    In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
 \end{proposition}
-\begin{proof}
-    This isomorphism is given in the modular realization by restricting the vector bundle and trivialization.
-
-    Suppose that $ s \ne 0 $. In the lattice realization, this is given by forming the specializations 
-    $$
-        L \mapsto (L(0), L(s))\,.
-    $$
-    Note that if $ L = g \CC[t]^m$ for $ g \in G([t,t^{-1}, (t-s)^{-1}])$, then 
-    $$
-        (L(0), L(s)) = (g \cO^m, g\cO^m_s)\,. 
-    $$
-    In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
-\end{proof}
-
-\begin{proposition}
-    \label{pr:grs-gr} There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
-
-    Combining with the above point, we obtain an isomorphism
-    $$
-    \tau_s : \Gr_{0,s} \rightarrow \Gr \times \Gr 
-    $$
-\end{proposition}
+
+%\begin{proposition}
+ %   \label{pr:grs-gr}
+
+    There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$. 
+    % 
+    Combining with the \Cref{pr:polyno-taylor}, we obtain an isomorphism
+    $$
+    \theta_s : \Gr_{0,s} \rightarrow \Gr \times \Gr 
+    $$
+%\end{proposition}
 
@@
 
-\jcom{I moved the ``composition'' of 2 and 3 into 3 and named it $ \tau_s$, since we will use it later quite a bit.
+% \jcom{I moved the ``composition'' of 2 and 3 into 3 and named it $ \tau_s$, since we will use it later quite a bit.
 I'm not that happy with the layout of this section, so feel free to reorganize it (maybe into Propositions?)}
 
-\acom{Begun. Not sure if it is what you had in mind.}
+% \acom{Begun. Not sure if it is what you had in mind.}
+
+\jcom{I reorganized a bit.  This last point is not really much of a result, so removed the ``proposition'' label.}
 
 \subsection{The fusion construction}
+\jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
+
 The following construction will be very important in this paper.
@@
 % 
-The isomorphisms $ \tau_s $ defined above glue together to a projection map
+The isomorphisms $ \theta_s $ defined above glue together to a projection map
 \begin{equation}
 \label{eq:mvitau}
-    \tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
+    \theta : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
 \end{equation}
-(This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
-
-\acom{Question for Joel: What is the benefit of working with diagonals? Letting two points vary? What is an example of a structure that you can't see letting just one point vary as we do.}
-
-Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2)$. % \subset \Gr_{0, \CC^\times} $.
+(This $\theta$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
+%  TODO: outstanding
+% \acom{Question for Joel: What is the benefit of working with diagonals? Letting two points vary? What is an example of a structure that you can't see letting just one point vary as we do.}
+
+Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $$ X_1 \ast_{\Cx} X_2 := \theta^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $$
 % 
@@
 % \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
-Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $ from \Cref{pr:grs-gr},  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \CC^\times $  of $\Grbd$.
-
-\acom{Well you might not want but I think it would be good to tell the reader why we use the notation $\CC^\times$ for $\AA\setminus 0$ in $\AA$ or why we use the notation $\AA$ at all..
+For $ s \in \Cx$, we write $ X_1 \ast_s X_2  $ for the fibres of $ X_1 \ast_{\Cx} X_2 $ over $ s$.
+By construction, the map $ \theta_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$
+
+% TODO: outstanding 
+% \acom{Well you might not want but I think it would be good to tell the reader why we use the notation $\CC^\times$ for $\AA\setminus 0$ in $\AA$ or why we use the notation $\AA$ at all..
 E.g.\ do we know what happens for $\GL_m(k)$ over some other base field $k$.}
 
-We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ in $ \Grbd $.
-By construction, this is a flat family over $ \AA$.
-We write $X_1 \ast_s X_2 $ for the scheme-theoretic fibre over a point $ s \in \AA$.
-
-If $ s \ne 0$, then the map $ \tau_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.
-
-On the other hand, the fibre $ X_1 \ast_0 X_2$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
+We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  X_1 \ast_{\Cx} X_2 $ in $ \Grbd $. By construction, this is a flat family over $ \AA$.
+
+The fibre $ X_1 \ast_0 X_2$ of $ X_1 \ast_{\AA} X_2 $ over $0$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
 We call this subscheme the \textbf{fusion} of $ X_1 $ and $ X_2$.
@@
 In doing so, $ X_1 \circ X_2 $ became obsolete, since we now have $ X_1 \ast_0 X_2$, but if you like we could just define $X_1 \circ X_2 = X_1 \ast_0 X_2 $.}
-
-%Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
+% 
+% Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
 % $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
-%\begin{equation*}
+% \begin{equation*}
     % \label{deservesdisplay}
 %    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
-%\end{equation*}
-%which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  
-% 
-%By construction, 
+% \end{equation*}
+% which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  
+% 
+% By construction, 
 % \acom{technically, there were two given above, so *these* constructions?} 
-%$X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
+% $X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
 
@@
 \label{def:sphfus}
-    The \textbf{fusion of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.
+    The \textbf{BD family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.
     % $$ 
@@
 \end{definition}
+\jcom{It used to say ``fusion'' of two spherical Schubert varieties, but we are using the word fusion just for the central fibre, so we need a different name.}
 % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
@@
 % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
-By \cite[Proposition 3.1.14]{zhu2016introduction}, $ \overline{\Gr}^{\lambda'} \ast_0 \overline{\Gr}^{\lambda''} $ is reduced and equal to  $ \overline{\Gr}^{\lambda' + \lambda''}$.
+By a Theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}, $ \overline{\Gr}^{\lambda'} \ast_0 \overline{\Gr}^{\lambda''} $ is reduced and equal to  $ \overline{\Gr}^{\lambda' + \lambda''}$.
 % Suppose that $ s \ne 0$.  
-Moreover, if $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.
+If $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''} =  \Gr^{\lambda'} \ast_s \Gr^{\lambda''} $
 % \acom{reference \cref{it:grs-gr}?} 
@@
 \acom{Sorry I keep changing (abbreviating) ``By a theorem of Zhu'', but is the citation not sufficient?}
+\jcom{I like to say a person's name when I cite their work!}
 
@@
 \end{proof}
-
-\acom{Does $M_m(\CC[t])\cap G\xT[t^{-1}] = \{g\in M(\CC[t]):\det g\in\CC[t]\setminus0\}$?}
+% TODO: yes the answer is yes, note to self
+% \acom{Does $M_m(\CC[t])\cap G\xT[t^{-1}] = \{g\in M(\CC[t]):\det g\in\CC[t]\setminus0\}$?}
+
 % \acom{why ``and so''? bc orbits are connected?}
@@
 In modular terms, $\cW_\mu$ corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
-The lattice description of $ \cW_\mu \cap \Grth$ is given in Lemma \ref{le:Wmu} below.
+The lattice description of $ \cW_\mu \cap \Grth_+$ is given in Lemma \ref{le:Wmu} below.
 %
@@
     The \textbf{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $. 
-% and the \textbf{fusion of  semi-infinite orbits} 
-% $$ 
-% S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''} \to \AA \,.
-% $$  
+and the \textbf{family semi-infinite orbits} 
+ $$ 
+ S^{\mu', \mu''}_{0,\AA} \subset \Grbd
+ $$  
+ which we define to have fibres $ S^{\mu'} \ast_s S^{\mu''}_s $ for $ s \ne 0$ and fibre $ S^{\mu}$ over $ s = 0 $.
 \end{definition}
-\acom{Commented out fusion part for now.
+(Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.)
+
+%\acom{Commented out fusion part for now.
 Unsure about defining it as the family whose 0 fibre is $S^{\mu' + \mu''}$ and whose generic fibre is $S^{\mu'}\times S^{\mu''}$ up to $\tau$.
@@
 $$
+See section 5.2 of \cite{baumann2020bases} for further details.
+
 % TODO: resolve
 % \jcom{Maybe we should introduce the $ L_{\mu', \mu''} $ notation, but I'm not sure it is necessary.}
-On the other hand, if $ s = 0$, then the fibre $S^{\mu', \mu''}_{0,0} $ equals $ S^{\mu' + \mu''}$. 
+%On the other hand, if $ s = 0$, then the fibre $S^{\mu', \mu''}_{0,0} $ equals $ S^{\mu' + \mu''}$. 
 % TODO: resolve
@@
 %
-
-\jcom{I realized that this is not correct.  We can't just take the fusion here since we don't want to get the closure of these guys.  I will think about this further.}
-% \acom{Two definitions in one. Unlike for spherical schubs}
 
@@
 % 
-In order to prove this result, we will need to recall some results from Eisenbud--Saltman \cite{eisenbud1989rank}. \acom{Too many results in one sentence.}
+In order to prove this proposition, we will need to recall some results from Eisenbud--Saltman \cite{eisenbud1989rank}. 
 %
@@
 % \begin{definition}
-An element of the \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ 
+The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined to be the affine space of matrices of the form
 % defined as the set of $A\in M_N(\CC)$ such that 
@@
 % In words, $A$ 
-is of the form 
 % a $\mu$ Jordan form matrix plus 
@@
 %
-\acom{Can add sentence before making next definition?
-To the effect of ``In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.'' Should also say what is up with the hidden transpose.}
-
+
+In other words, the $ i,j$ block of $ A $ is used to produce a polynomial which is inserted in the $ j,i$ entry of $ g(A)$.
+
+In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.
 \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
@@
 % 
-Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.
-
-\acom{Mention that any other decomposition $\nu' + \nu''$ of $\mu' + \mu''$ will give a slice $\UU^{\nu',\nu''}_{0,\AA}$ with the same zero fibre.}
-
-\acom{These $\UU$'s should also have attr descriptions. What are they?}
+Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection $ \TT_\mu \cap \mathfrak n $, where $ \mathfrak n $ denotes the set of strictly upper-triangular matrices.
+
+%\acom{Mention that any other decomposition $\nu' + \nu''$ of $\mu' + \mu''$ will give a slice $\UU^{\nu',\nu''}_{0,\AA}$ with the same zero fibre.}
+
+% \acom{These $\UU$'s should also have attr descriptions. What are they?}
+% \jcom{I don't think that it is very interesting. Just take a diagonal matrix, constant on each block.  Then $\UU$ will be the attracting set of the block diagonal matrix for this action.}
+% A: Ok
 
@@
 
+\jcom{Yes, I think that this section should be deleted and the content moved into the introduction.}
+
 \section{Rising Action}
 \label{s:theproblem}
+
+Throughout this section, we continue our notation of the previous sections.
+So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights for $ \GL_m$, with $ \lambda' + \lambda'' = \lambda$.
+Also $ \mu, \mu', \mu''$ are effective coweights with $ \mu = \mu' + \mu''$ and we assume that $ \mu$ is dominant.
+
 \begin{lemma} 
@@
 % 
-\acom{Don't have $P$ notation, replacing (in lemma below) with $\ZZ^m$ for now..}
+%\acom{Don't have $P$ notation, replacing (in lemma below) with $\ZZ^m$ for now..}
 \begin{lemma}
 \label{le:inftyfusiskl} % as in lands in KL slice 
-    Let $\mu',\mu'' \in \ZZ^m$ and $\mu = \mu' + \mu''$. Under the map $ \Grbd \rightarrow \Grth$ the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
+    Under the map $ \Grbd \rightarrow \Grth$ the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
 \end{lemma}
@@
 \label{s:climax}
+Throughout this section, we continue our notation of the previous sections.
+So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights for $ \GL_m$, with $ \lambda' + \lambda'' = \lambda$.
+Also $ \mu, \mu', \mu''$ are effective coweights with $ \mu = \mu' + \mu''$ and we assume that $ \mu$ is dominant.
+
 Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.  Note that $g(A)t^{-\mu} \in G_1(\Oinf)$.
@@
 
-The following result is \cite[Theorem 3.2]{cautis2018categorical} up to transpose.
+The following result is called the Mirkovic-Vybornov isomorphism \cite{mirkovic2007quiver}.
+In the following form, it can be found in \cite[Theorem 3.2]{cautis2018categorical}, except that we have tweaked both maps with a matrix transpose $ \tr$.
+
+\jcom{I'm not sure which of the Mirkovic-Vybornov papers to cite.}
 % 
@@
 % 
-\acom{Should we say what $^{tr}$ means?}
+%\acom{Should we say what $^{tr}$ means?}
 
@@
 
+The following refinement of Mirkovic-Vybornov isomorphism is a special case of \cite[Theorem 5.3]{mirkovic2007quiver}.
 \begin{theorem} 
@@
 %
-\acom{We need to assume that $\mu' +\mu''$ is dominant in the theorem below. The assumption for \Cref{th:TmuWmu} is also missing.} 
+% \acom{We need to assume that $\mu' +\mu''$ is dominant in the theorem below. The assumption for \Cref{th:TmuWmu} is also missing.} 
+% 
+% \jcom{I added a reminder at the beginning of the section.}
 % 
@@
 
-Restricting to the zero fibre and applying $\tau_0$ we recover \cite[Corollary~5.2.2]{dthesis}, itself a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}, the ordinary affine Grassmannian version of \Cref{th:OGrl}.
+Restricting to the zero fibre and applying $\theta_0$ we recover \cite[Corollary~5.2.2]{dthesis}. 
+%itself a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}, the ordinary affine Grassmannian version of \Cref{th:OGrl}. 
 % 
@@
     \label{cor:mvy}
-    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu_+$ where $\n\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
+The map $ A \mapsto g(A)\OO^m$ gives an isomorphism    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu_-$.
 \end{corollary}
@@
 \end{definition}
+By \cite{mirkovic2007geometric}, all these irreducible components have dimension $ \rho(\lambda - \mu)$, where $ \rho = (m, m-1, \dots, 1)$.
 
@@
 
-Denote by $[a,b]$ the interval $\{a,a+1,\dots,b-1,b\}\subset\NN$. If $a = 1$ just write $[b]$, and if $a = b$ just write $\{a\}$. 
+Denote by $[a,b]$ the interval $\{a,a+1,\dots,b-1,b\}\subset\NN$. 
+% If $a = 1$ just write $[b]$, and if $a = b$ just write $\{a\}$. 
 % If a = b? Just write $\{b\}$
+% \jcom{Maybe we should write $[1,b] $ instead of $ [b]$.  It looks a little confusing below to have $ [i+1, m]$ and $[i]$.}
+% 10-4
+
 We begin with the following definitions.
@@
 % 
-If $ \gamma \subset [m]$, we define two lattices $ L^\gamma, L_\gamma $ in $ \cO^\gamma := \Sp_{\cO}(e_i : i \in \gamma) $ by
+If $ \gamma \subset [1,m]$, we define two lattices $ L^\gamma, L_\gamma $ in $ \cO^\gamma := \Sp_{\cO}(e_i : i \in \gamma) $ by
 \begin{gather*}
@@
 \end{gather*}
-where $ \gamma^c := [m] \setminus \gamma$.
+where $ \gamma^c := [1,m] \setminus \gamma$.
 % 
@@
 \end{lemma}
+\acom{Doesn't the identification $G(K)/G(O) \to G(O)\ G(K)$ coming from $g\mapsto g^{-1}$ give us a minus sign somewhere, since we are sending $S^\mu_w$ to $S^{-\mu}_w$, so $D_{\omega_i}(L) = -\rdim L_{[1,i]}$.
+Ignoring the minus sign for now, for $j\le i\le m$, and $L_{[1,i]}$ in $S^{\mu(i)}_- \cap S^{\lambda(i)}_+$ we’d like $D_{\omega_j}(L_{[1,i]}) = \rdim (L_{[1,i]})_{[1,j]} = \lambda(i)_j + \cdots + \lambda(i)_i$ whereas the claim $(L_{[1,i]})_{[1,j]} = L_{[1,j]}$ hides that this lattice also depends on $i$?
+I'm sure I'm missing something here so I will look at it again later.
+$n_{(a,b)} (L_{[1,i]}) = -D_{[a+1,b]} - D_{[a , b-1]} + D_{[a + 1, b-1]} + D_{[a,b]} = - \rdim L_{[a+1,b]} - \rdim L_{[a,b-1]} + \rdim L_{[a+1,b-1]} + \rdim L_{[a,b]}$}
+\jcom{I warned you when we talked on Tuesday that there might be some problems, but I think that we shouldn't dig any deeper here.}
 
@@
 
-Recall that $ S^\mu_- = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+For this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (previously we left out the subscript). We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+\acom{Maybe we shouldn't decorate $S^\mu$ with a subscript $-$ after all since we certainly won't want to add to $S^{\mu',\mu''}_{0,\AA}$ in underscores.}
+\jcom{I agree.  Is the above solution ok?}
 % 
@@
 % \acom{For it.}
+% \acom{As was checked in \cite{dranowski2020generalized} $S^\mu_w = \{D_{w\omega_i} = \langle \mu , w w_0 \omega_i\rangle \}$ so $S^\mu_+ = \{D_{\omega_i}(L) = \rdim L^{w_0\omega_i} \}$} 
+% \jcom{But that was for a different identification of the left and right quotients.  I'm certain that the statements in the Lemma below are correct.}
 
@@
     \begin{enumerate}
-        \item $ L \in S_+^\mu$
-        \item $ \rdim L^{[i]} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
-        \item $ \rdim L_{[i+1,m]} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
+        \item $ L \in S_+^\mu$ \label{Srdim1}
+        \item $ \rdim L^{[1,i]} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $. \label{Srdim2} % \acom{$\rdim L^{[m-i+1,m]} = \mu_{m-i+1} + \cdots + \mu_m$}
+        \item $ \rdim L_{[i+1,m]} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$. \label{Srdim3} % \acom{$\rdim L_{[m-i]}=\mu_1 + \cdots + \mu_{m-i}$}
     \end{enumerate}
@@
         \item $ \rdim L^{[i+1,m]} = \mu_{i+1} + \dots + \mu_m$ for all $ i = 1, \dots, m $.
-        \item $ \rdim L_{[i]} = \mu_{1} + \dots + \mu_i$ for $ i  = 1, \dots, m$.
+        \item $ \rdim L_{[11,i]} = \mu_{1} + \dots + \mu_i$ for $ i  = 1, \dots, m$.
     \end{enumerate}
 \end{lemma}
+
+\begin{proof}
+We prove the first statement as the second is similar.
+Let $ L = n t^\mu \CC[t]^m$ for $ n \in N_+(\cK)$ and let $ v_1, \dots, v_m $ denote the columns of the matrix $ nt^\mu$.
+Then $ L = \Sp_{\cO}(v_1, \dots, v_m)$.
+Fix some $ i \le m$.
+Then $ L^{[1,i]} = \Sp_{\cO}(w_1, \dots, w_i) $ where $ w_j $ denotes the first $ i $ entries of $ v_j $ (by upper-triangularity, the rest of the entries are 0, in any case).
+
+Assume that $L \subset \cO^m$.
+Then $ L^{[1,i]} \subset \cO^i$ and $ \rdim L^{[1,i]} $ is the valuation of the determinant of the matrix with columns $ w_1, \dots, w_i$.
+Since this matrix is upper-triangular with diagonal entries $ t^{\mu_1}, \dots, t^{\mu_i}$, this determinant is $ t^{\mu_1 + \dots + \mu_i} $ and hence $ \rdim L^{[1,i]} = \mu_1 + \dots + \mu_i$.
+
+Thus \ref{Srdim1} implies \ref{Srdim2}.  The converse follows from the fact that every $ L$ lies in some $ S_+^\nu$ and by the above reasoning, $ \nu$ is determined by the values of $ \dim L^{[1,i]}$.
+
+The equivalence of \ref{Srdim2} and \ref{Srdim3} follows from Lemma \ref{le:rdimTrans}.
+\end{proof}
+\jcom{I added a proof.  We can get delete and just put a reference to mvcycle if you prefer.}
+
+\acom{No no this is good! Thanks for other additions}
 
@@
 \begin{aligned}
-n_\bullet(\tau)_{i,j} &= \lambda(i+1)_j - \lambda(i)_j = \text{ \# of boxes on the $j$th row of $\tau $ filled with $ i+1$}  \\
-(i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
-(2,2),\dots,(m-1,2),%\\
+% n_\bullet(\tau)_{i,j} &= \lambda(i+1)_j - \lambda(i)_j = \text{ \# of boxes on the $j$th row of $\tau $ filled with $ i+1$}  \\
+% (i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
+% (2,2),\dots,(m-1,2),%\\
+% \dots,%\\
+% (m-1,m-1)
+n_\bullet(\tau)_{(a,b)} &= \lambda(b)_a - \lambda(b-1)_a = \text{ \# of boxes on the $a$th row of $\tau $ filled with/of weight $b$}  \\
+% (i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
+% (2,2),\dots,(m-1,2),%\\
+% \dots,%\\
+% (m-1,m-1)
+(a,b) &=  (1,2),(1,3),\dots,(1,m),%\\
+(2,3),\dots,(2,m),%\\
 \dots,%\\
-(m-1,m-1)
+(m-1,m)\,. 
 \end{aligned}
@@
 $$
+Note that $ \lambda - \mu = \displaystyle{\sum_{1 \le a < b \le m}n(\tau)_{(a,b)} \beta_{a,b}} $ where $ \beta_{a,b} $ denotes the positive root of $ G$ with a $ 1 $ in the $a $ slot and a $-1$ in the $ b $ slot.
 % for 
@@
 The pattern $\gt(\tau)$ is recorded as a lower-triangular matrix (the array of shapes of subtableaux $\tau(i)$) and the datum $n_\bullet(\tau)$ is recorded as a sequence.
-See \cite[\S 4]{berenstein1988tensor}.
-Below is an example with $\lambda = (4,2)$ and $\mu = (3,2,1)$.
+\acom{See \cite[\S 4]{berenstein1988tensor} for the source?} Below is an example with $\lambda = (4,2)$ and $\mu = (3,2,1)$.
 
@@
 % 
-
-We can associate to $\tau$ the MV cycle $Z(\tau)$ by taking the closure of the top-dimensional irreducible component of  
+% \acom{In this case $L = \langle t^3 e_1 - ate_2 - be_3 , t^2 e_2, te_3\rangle$ so $\rdim L^{w_0\omega_i} = \{1,3,6\} = \langle \mu , w_0 \omega_i\rangle = D_{\omega_i}(L)$}
+
+% \jcom{$L \in S_-^{(3,2,1)}$, so $ \rdim L^{[3,3]} = 1 $ in accordance with the lemma above.}
+
+We can associate to $\tau$ the locus 
 %  
@@
         \{
-            L\in S^\mu : L_{[i]} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
+            L\in S^\mu : L_{[1,i]} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
         \}\,. 
@@
 It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2004mirkovic} (see Section 9 in \cite{kamnitzer2010mirkovic}).
-We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}.
-\acom{Many alsos}
+A different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.
+
 \begin{proposition}
     \label{pr:newmvdes}
+    $ \mathring Z(\tau)$ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.  Let $ Z(\tau)$ denote the closure of this component.  Then, 
     $Z(\tau)$ is the MV cycle whose Lusztig datum (with respect to the standard reduced word) is $n_\bullet(\tau)$. 
 \end{proposition}
+\begin{remark}
+We believe that $ \mathring Z(\tau)$ is irreducible so that $ Z(\tau) = \overline{ \mathring Z(\tau)}$.
+\end{remark}
+
 \begin{proof}
@@
 Thus, its closure is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
-(In \cite{kamnitzer2010mirkovic}, the third author worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using $ [g] \mapsto [g^{-1}]$.) \acom{Maybe we should avoid using square brackets as we haven't used them yet?}
+(In \cite{kamnitzer2010mirkovic}, the third author worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using the map $ G(\cO) g \mapsto g^{-1} G(\cO)$.)
+% \acom{Maybe we should avoid using square brackets as we haven't used them yet?}
 
@@
 
-Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu_-$, then $ L_{[i]} \in S^{\mu(i)}_-$ so we get a map 
+\acom{Ask Joel about this}
+
+Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu_-$, then $ L_{[1,i]} \in S^{\mu(i)}_-$ so we get a map 
 $$ 
@@
 From above/again $ \Gr^{\lambda(i)} \cap f_i(\mathring Z(\tau(i))_1)$ is a dense constructible subset of $\mathring Z(\tau(i))_1$.  
-Since $ \mathring Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)}_- \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ \acom{$\cap \mathring Z(\tau)_1$?} is a dense constructible subset of $ \mathring Z(\tau)_1 $.
+Since $ \mathring Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)}_- \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ 
+% \acom{$\cap \mathring Z(\tau)_1$?} \jcom{The domain of $ f_i$ is $ \mathring Z(\tau)_1$, so automatically, these preimages are contained in $ Z(\tau)_1)$.} 
+is a dense constructible subset of $ \mathring Z(\tau)_1 $.
 
@@
 $$
-is a dense constructible subset of $\mathring Z(\tau)_1$. \acom{Again are we maybe missing capping with $Z$ in the above $:=$?} Thus $\overline{\mathring Z(\tau)_2} = \overline{\mathring Z(\tau)_1}$.
+is a dense constructible subset of $\mathring Z(\tau)_1$. 
+% \acom{Again are we maybe missing capping with $Z$ in the above $:=$?} 
+Thus $\overline{\mathring Z(\tau)_2} = \overline{\mathring Z(\tau)_1}$.
 
@@
     % X(\tau')\ast_s \mathring X(\tau'') 
-    = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}
+    = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} 
+    \text{ has Jordan type } ((\lambda'(i), 0), (\lambda''(i), s))
+    % \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} 
+    \text{ for } i=1,\dots,N\right\}
 \end{equation*}
 % 
-\jcom{Maybe instead write ``$A \big|_{\CC^{|\mu(i)|}}$ has Jordan type $ (\lambda'(i), 0), (\lambda''(i), s)$} \acom{Okay. So no need for the first paragraph of this section?}
-% 
+% \jcom{Maybe instead write ``$A \big|_{\CC^{|\mu(i)|}}$ has Jordan type $ (\lambda'(i), 0), (\lambda''(i), s)$} \acom{Okay. So no need for the first paragraph of this section?}
+% 
+and
 \begin{equation*}
@@
 % 
+Note that elements $A\in\mathring X(\tau',\tau'')$ do not in general correspond to pairs $(A',A'')\in\mathring X(\tau')\times X(\tau'')$ because if $\mu'$ (resp.\ $\mu''$) is not dominant then $X(\tau')$ (resp.\ $X(\tau'')$) is not well-defined.
+% The space we have defined may therefore not be a true fusion in the sense that it may not come from two obvious spaces. \acom{Joel?} 
+\jcom{Even if $ \mu', \mu'$ are dominant, it is not obvious how $ A $ corresponds to a pair $(A', A'')$.
+And since I don't think that ``true fusion'' is a well-defined thing, I think that we can delete the last sentence.}
+\acom{Ok. By choosing bases of generalized eigenspaces?}
+
+% 
 % and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
@@
 Still..}
-
+% 
 % \jcom{Now that we have $ \ast_s$ defined in the fusion section, we can refer to that here.}
-
+Recall the map $\theta : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr$ from \Cref{ss:affgrs}. 
 \begin{proposition}
-    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$. 
+    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\theta^{-1}(\mathring Z(\tau')\times\mathring Z(\tau''))$. 
     % \[
@@
 
+\acom{Should we just use $\tau^{-1}(\mathring Z(\tau') \times \mathring Z(\tau''))$ instead?}
+
+\jcom{Yes, maybe that is a good idea.
+We should recall $ \tau $, and I suppose since we have two $ \tau$s, we had better change notation.
+Maybe we can use a different letter for the $\tau$ used to define fusion and keep $ \tau $ for tableau.}
+
+\acom{Changed it to $\theta$ \emoji{worried}}
+
 \begin{proof}
@@
 Fix $A\in \mathring X(\tau',\tau'')_{0,s} $ and $i = 1,\dots, m$. 
-
-Let $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denote the $\CC[t]$-submodule generated by the first $i$ standard basis vectors. \acom{Probably don't need to repeat this.}
-
-The lattices $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ and $L=g(A)\CC[t]^m$ are related by the equality $ l = L_{[i]}$ where recall $L_{[i]} = (L + \CC[t]^{[i+1,m]}) / \CC[t]^{[i+1,m]}\subset \CC[t]^m/\CC[t]^{[i+1,m]} = \CC[t]^i$.
-
-By definition of $\UU^{\mu',\mu''}$ we have $A\big|_{\CC^{|\mu(i)|}}\in\UU^{\mu'(i),\mu''(i)}_{0,s}$ and by definition of $X(\tau',\tau'')_{0,s}$, $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$.
-So, by \Cref{th:OTGrW}, $l = L_{[i]}\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$.
-On the other hand, also by definition of $\UU^{\mu',\mu''}$, we have $L\in S^{\mu',\mu''}$ and consequently $l\in S^{\mu'(i),\mu''(i)}$.
+% 
+Let $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denote the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
+% \acom{Probably don't need to repeat this.}
+
+The lattices $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ and $L=g(A)\CC[t]^m$ are related by the equality $ l = L_{[1,i]}$ where recall $L_{[1,i]} = (L + \CC[t]^{[i+1,m]}) / \CC[t]^{[i+1,m]}\subset \CC[t]^m/\CC[t]^{[i+1,m]} = \CC[t]^i$.
+
+By definition of $\UU^{\mu',\mu''}_{0,\AA}$ we have $A\big|_{\CC^{|\mu(i)|}}\in\UU^{\mu'(i),\mu''(i)}_{0,s}$ and by definition of $X(\tau',\tau'')_{0,s}$, the Jordan type of $A\big|_{\CC^{|\mu(i)|}}$ is $((\lambda'(i),0),(\lambda''(i),s))$.
+So, $l \in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$ by \Cref{th:OTGrW}.
+On the other hand, 
+% also by definition of $\UU^{\mu',\mu''}_{0,\AA}$, we have 
+since $L\in S^{\mu',\mu''}_{0,s}$, $l\in S^{\mu'(i),\mu''(i)}_{0,s}$.
 
 Therefore, as $i$ varies, we see that the pair $(L(0),L(s))\in S^{\mu'}\times S^{\mu''}$ is such that 
-$$(L_{[i]}(0),L_{[i]}(s))  = (L(0)_{[i]},L(s)_{[i]}) \in \Gr^{\lambda'(i)}\times\Gr^{\lambda''(i)}$$ 
-and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$.
+$$(L_{[1,i]}(0),L_{[1,i]}(s))  = (L(0)_{[1,i]},L(s)_{[1,i]}) \in \Gr^{\lambda'(i)}\times\Gr^{\lambda''(i)}$$ 
+and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$. The argument can be reversed for $L\in\theta^{-1}(\mathring Z(\tau')\times Z(\tau''))$.
 % 
@@
 
-Let $G = \GL_4$. There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables. We list the corresponding MV cycles and tableaux:
-\[\begin{array}{cccccc} \vspace{1mm}
-    Z_1 &\leadsto \young(2) & Z_2 &\leadsto \young(1,3) & Z_3 &\leadsto \young(1,2,4) \\ \vspace{1mm}
-    Z_{1 \leftarrow 2} &\leadsto \young(3) & Z_{1 \rightarrow 2} &\leadsto \young(2,3) & Z_{2 \leftarrow 3} &\leadsto \young(1,4) \\ \vspace{1mm}
-     Z_{2 \rightarrow 3} &\leadsto \young(1,3,4) & Z_{in} &\leadsto \young(2,4) & Z_{out} &\leadsto \young(13,2,4)  \\
-    Z_{P_1} &\leadsto \young(2,3,4) & Z_{P_2} &\leadsto \young(3,4) & Z_{P_3} &\leadsto \young(4)
-\end{array}\]
+Let $G = \GL_4$. There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables. We list the corresponding tableaux, coordinate ring of the MV cycle, and Lusztig-datum below:
+
+\[
+\begin{array}{c|c|c} 
+\tau & \text{Coordinate ring of }Z(\tau) & \text{Lusztig-datum} \\ \hline
+\young(2) & \CC[A_{12}^1] & (1,0,0,0,0,0) \rule{0pt}{3ex}\\
+\young(1,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1,A_{13}^1 \rangle} & (0,0,0,1,0,0) \TS\BS\\
+\young(1,2,4) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 \rangle} & (0,0,0,0,0,1) \TS\BS\\
+\young(3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1 \rangle} & (1,0,0,1,0,0) \TS\BS\\
+\young(2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{23}^1 \rangle} & (0,1,0,0,0,0) \TS\BS\\
+\young(1,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 \rangle} & (0,0,0,1,0,1) \TS\BS\\
+\young(1,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 \rangle} & (0,0,0,0,1,0) \TS\BS\\
+\young(2,4) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 \rangle} & (0,1,0,0,0,1) \TS\BS\\
+\young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 \rangle} & (1,0,0,0,1,0) \TS\BS\\
+\young(2,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{23}^1,A_{24}^1,A_{34}^1 \rangle} & (0,0,1,0,0,0) \TS\BS\\
+\young(3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1 \rangle} & (0,1,0,0,1,0) \TS\BS\\
+\young(4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle} & (1,0,0,1,0,1) \TS\BS\\
+\end{array}
+\]
+
+% \begin{table}[]
+% \centering
+% \begin{tabular}{l|c|c}
+% $\tau$ & Coordinate ring of $Z(\tau)$ & Lusztig-datum \\ \hline
+% \young(2) & $\CC[A_{12}^1]$ & (1,0,0,0,0,0) \\
+% \young(1,3) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1,A_{13}^1 \rangle}$ & (0,0,0,1,0,0) \\
+% \young(1,2,4) & $\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 \rangle}$ & (0,0,0,0,0,1) \\
+% \young(3) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1 \rangle}$ & (1,0,0,1,0,0) \\
+% \young(2,3) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{23}^1 \rangle}$ & (0,1,0,0,0,0) \\
+% \young(1,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 \rangle}$ & (0,0,0,1,0,1) \\
+% \young(1,3,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 \rangle}$ & (0,0,0,0,1,0) \\
+% \young(2,4) & $\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 \rangle}$ & (0,1,0,0,0,1) \\
+% \young(13,2,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 \rangle}$ & (1,0,0,0,1,0) \\
+% \young(2,3,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{23}^1,A_{24}^1,A_{34}^1 \rangle}$ & (0,0,1,0,0,0) \\
+% \young(3,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1 \rangle}$ & (0,1,0,0,1,0) \\
+% \young(4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle}$ & (1,0,0,1,0,1) \\
+% \end{tabular}
+% \end{table}
+
+% \[\begin{array}{cccccc} \vspace{1mm}
+%     Z_1 &\leadsto \young(2) & Z_2 &\leadsto \young(1,3) & Z_3 &\leadsto \young(1,2,4) \\ \vspace{1mm}
+%     Z_{1 \leftarrow 2} &\leadsto \young(3) & Z_{1 \rightarrow 2} &\leadsto \young(2,3) & Z_{2 \leftarrow 3} &\leadsto \young(1,4) \\ \vspace{1mm}
+%      Z_{2 \rightarrow 3} &\leadsto \young(1,3,4) & Z_{in} &\leadsto \young(2,4) & Z_{out} &\leadsto \young(13,2,4)  \\
+%     Z_{P_1} &\leadsto \young(2,3,4) & Z_{P_2} &\leadsto \young(3,4) & Z_{P_3} &\leadsto \young(4)
+% \end{array}\]
 

### 2021-05-27 draft.tex
Joel's last changes

@@
 One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!
+
+Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
+% and they conjectured a formula for many of them.
+
+It's not clear how this work helps with/relates to AK/their conjectures.
+
+The generalized \mvy is interesting in its own right. \acom{is it?}
+
+Computing fusion still hard but at least boiled down to linear algebra.
+Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
+
+Interesting combinatorics?
+Presumably it is related to Feigin and Loktev's generalized Kostka polynomials?
+Though Joel says that the product on SSYT that we are witnessing is unlikely to have a combinatorial description.
+
+Exchange relations only work on cluster modules where one is a mutation of the other (i.e.\ those corresponding to cluster monomials which are related by mutation).
+Of course this gives me everything.
+Up to $A_4$ as in type $A_5$ there exist indecomposable modules which are not cluster, so exchange relations do not apply.
+
+The hope (conjecture) is that this paper gives a way to compute on such modules.
+Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is a cluster monomial belonging to both bases and $c_Y$ is the square of a cluster monomial ($b'$ say) belonging to both bases.
+The $\barD$ equation suggests that $(b')^2 = b_Z + 2b$.
+We can try to check this using Roger's script.
+Such calculations bring us closer to answering two questions.
+First, how forgetful is $\barD$.
+Second, on the level of modules, are the terms appearing in the fusion product determined by $\Ext^1$ of the factors.
+By Roger's thesis this is true if the factors are cluster modules related by a mutation.
+
+% No; $x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
+
+Representation theory?
 
@@
 
-\acom{We will also sometimes write $(t-s)^\mu$ for its image in $G(K)/G(R)$ and we hope it will be clear? Only we haven't introduced this space yet.}
-\jcom{I think that we do this infrequently enough that it is not a problem and there is no need to mention it here.}
+% Resolved
+% \acom{We will also sometimes write $(t-s)^\mu$ for its image in $G(K)/G(R)$ and we hope it will be clear? Only we haven't introduced this space yet.}
+% \jcom{I think that we do this infrequently enough that it is not a problem and there is no need to mention it here.}
 % Resolved
@@
 
-\acom{Maybe add that it's the same for $G(\cO)$. Also, we are using the notation $G(R)$ in one paragraph and defining it in the next. Maybe introduced $M_m$ first?}
-\jcom{I don't consider that to be the definition of $ G(R)$.  The definition is the invertible $ m \times m$ matrices with coefficients in $ R $.  So I think that everything is fine.}
+% \acom{Maybe add that it's the same for $G(\cO)$. Also, we are using the notation $G(R)$ in one paragraph and defining it in the next. Maybe introduced $M_m$ first?}
+% \jcom{I don't consider that to be the definition of $ G(R)$.  The definition is the invertible $ m \times m$ matrices with coefficients in $ R $.  So I think that everything is fine.}
 
@@
 
-\acom{We are using fixed $m$ in the definitions here.}
-\jcom{Added sentence fixing $m $ above.}
+% \acom{We are using fixed $m$ in the definitions here.}
+% \jcom{Added sentence fixing $m $ above.}
 
@@
 
-\acom{Oh, I meant could we review for my own benefit.
+% \acom{Oh, I meant could we review for my own benefit.
 But I do think it is also nice, for readability, to use (slightly) different words to describe the different descriptions.
@@
 
-\jcom{I made some changes}
+% \jcom{I made some changes}
 
@@
 It is also a moduli space of lattices, 
-\acom{And this one as ``As a $G$-space..''}
+% \acom{And this one as ``As a $G$-space..''}
 $$ 
@@
 
-The following result is the factorization property of the Beilinson-Drinfeld Grassmannian (see \cite[Prop. 3.13]{zhu2016introduction}).
+The following result is the factorization property of the Beilinson--Drinfeld Grassmannian (see \cite[Prop. 3.13]{zhu2016introduction}).
 \begin{proposition}
@@
 \jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
+\acom{Do you mean that if we go with $\AA$ we should change $\CC^\times$ as well?
+Also, would you agree that the distinction is the topology?
+So $\AA$ is better if we were using ``generic'' to describe $s\ne 0$, which we are not.}
+\jcom{Yes, either we should write $ \AA, \AA^\times $ or $ \CC, \CC^\times$.  There is no distinction.  Always in this paper, we work with the Zariski topology whether we write $ \AA $ or $ \CC$.}
 
@@
 \jcom{It used to say ``fusion'' of two spherical Schubert varieties, but we are using the word fusion just for the central fibre, so we need a different name.} 
+\acom{Family is good. We should put BD on p. 4.}
 % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
@@
 
-\acom{Sorry I keep changing (abbreviating) ``By a theorem of Zhu'', but is the citation not sufficient?}
-\jcom{I like to say a person's name when I cite their work!}
+% \acom{Sorry I keep changing (abbreviating) ``By a theorem of Zhu'', but is the citation not sufficient?}
+% \jcom{I like to say a person's name when I cite their work!}
+% \acom{Ok}
 
@@
 \label{def:inftyorbits}
-    The \textbf{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $. 
-and the \textbf{family semi-infinite orbits} 
- $$ 
- S^{\mu', \mu''}_{0,\AA} \subset \Grbd
- $$  
+    The \textbf{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $ and the \textbf{family of two semi-infinite orbits} 
+ $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
  which we define to have fibres $ S^{\mu'} \ast_s S^{\mu''}_s $ for $ s \ne 0$ and fibre $ S^{\mu}$ over $ s = 0 $.
 \end{definition}
-(Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.)
-
+Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.
+% 
 %\acom{Commented out fusion part for now.
@@
 Maybe we can consider the attracting set of just one of these?}
-
+% 
 If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
@@
 
-\section{Exposition}
-\label{s:exposition}
-% 
-Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
-% and they conjectured a formula for many of them.
-
-It's not clear how this work helps with/relates to AK/their conjectures.
-
-The generalized \mvy is interesting in its own right. \acom{is it?}
-
-Computing fusion still hard but at least boiled down to linear algebra.
-Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
-
-Interesting combinatorics?
-Presumably it is related to Feigin and Loktev's generalized Kostka polynomials?
-Though Joel says that the product on SSYT that we are witnessing is unlikely to have a combinatorial description.
-
-Exchange relations only work on cluster modules where one is a mutation of the other (i.e.\ those corresponding to cluster monomials which are related by mutation).
-Of course this gives me everything.
-Up to $A_4$ as in type $A_5$ there exist indecomposable modules which are not cluster, so exchange relations do not apply.
-
-The hope (conjecture) is that this paper gives a way to compute on such modules.
-Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is a cluster monomial belonging to both bases and $c_Y$ is the square of a cluster monomial ($b'$ say) belonging to both bases.
-The $\barD$ equation suggests that $(b')^2 = b_Z + 2b$.
-We can try to check this using Roger's script.
-Such calculations bring us closer to answering two questions.
-First, how forgetful is $\barD$.
-Second, on the level of modules, are the terms appearing in the fusion product determined by $\Ext^1$ of the factors.
-By Roger's thesis this is true if the factors are cluster modules related by a mutation.
-
-% No; $x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
-
-Representation theory?
-
-\acom{This whole section is a big question mark.
+% \section{Exposition}
+% \label{s:exposition}
+% %
+
+% \acom{This whole section is a big question mark.
 The beginning of the rising action section is more expository, developmental, and the climax is in turn more of a rising action.
@@
 
-\jcom{Yes, I think that this section should be deleted and the content moved into the introduction.}
+% \jcom{Yes, I think that this section should be deleted and the content moved into the introduction.}
 
@@
 
-The following result is called the Mirkovic-Vybornov isomorphism \cite{mirkovic2007quiver}.
+The following result is called the Mirkovic--Vybornov isomorphism \cite{mirkovic2007quiver}.
 In the following form, it can be found in \cite[Theorem 3.2]{cautis2018categorical}, except that we have tweaked both maps with a matrix transpose $ \tr$.
 
-\jcom{I'm not sure which of the Mirkovic-Vybornov papers to cite.}
+\jcom{I'm not sure which of the Mirkovic--Vybornov papers to cite.} \acom{can say 07, rewritten in 19}
 % 
@@
     \gamma \subset [m] $, we have $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
-    \item For any $ \gamma_1 \subset \gamma_2 \subset [m]$, we have $$ (L_{\gamma_1})_{\gamma_2} = L_{\gamma_2}
+    \item For any $ \gamma_1 \subset \gamma_2 \subset [m]$, we have $$ (L_{\gamma_2})_{\gamma_1} = L_{\gamma_1}
 $$
@@
 \jcom{I warned you when we talked on Tuesday that there might be some problems, but I think that we shouldn't dig any deeper here.} 
+\acom{Well, it's not that deep..
+it's just that $(L_{\gamma_1})_{\gamma_2}$ involves taking $\gamma_2^c\subset \gamma_1$ and landing in $\cO^{\gamma_1\cap\gamma_2}$ whereas $L_{\gamma_2}$ involves taking $\gamma_2^c\subset[m]$ and landing in $\cO^{\gamma_2}$ ...so I think the change makes it true.}
+\jcom{But I assumed that $ \gamma_1 \subset \gamma_2$, so I don' think that taking intersection is necessary.}
+\acom{Even so?
+What was written before was $(L_{\gamma_1})_{\gamma_2} = L_{\gamma_2} $ and if $\gamma_1\subset\gamma_2$ then the intersection is $\gamma_1$.
+Anyway I don't think we ever use Lem.
+6(2), so we can do without it?}
+\jcom{Oh, I guess there was a typo.  I fixed it now.  It is used in the proof of Prop 4, I will add a reference.}
 
@@
 For this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (previously we left out the subscript). We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
-\acom{Maybe we shouldn't decorate $S^\mu$ with a subscript $-$ after all since we certainly won't want to add to $S^{\mu',\mu''}_{0,\AA}$ in underscores.}
-\jcom{I agree.  Is the above solution ok?}
+% \acom{Maybe we shouldn't decorate $S^\mu$ with a subscript $-$ after all since we certainly won't want to add to $S^{\mu',\mu''}_{0,\AA}$ in underscores.}
+% \jcom{I agree.  Is the above solution ok?}
+% \acom{Sure.}
 % 
@@
     Similarly, the following are equivalent:
-        \begin{enumerate}
+        \begin{enumerate}[label=\arabic*'.]
         \item $ L \in S_-^\mu$
         \item $ \rdim L^{[i+1,m]} = \mu_{i+1} + \dots + \mu_m$ for all $ i = 1, \dots, m $.
-        \item $ \rdim L_{[11,i]} = \mu_{1} + \dots + \mu_i$ for $ i  = 1, \dots, m$.
+        \item $ \rdim L_{[1,i]} = \mu_{1} + \dots + \mu_i$ for $ i  = 1, \dots, m$.
     \end{enumerate}
@@
         \{
-            L\in S^\mu : L_{[1,i]} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
+            L\in S^\mu_- : L_{[1,i]} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
         \}\,. 
@@
 \begin{remark}
-We believe that $ \mathring Z(\tau)$ is irreducible so that $ Z(\tau) = \overline{ \mathring Z(\tau)}$.
+We believe that $ \mathring Z(\tau)$ is irreducible so that in fact $ Z(\tau) = \overline{ \mathring Z(\tau)}$.
 \end{remark}
@@
 \begin{equation*}
-\mathring Z(\tau)_1 := \{ L \in S^\mu \cap \Gr_+ : L_{[i]} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
+\mathring Z(\tau)_1 := \{ L \in S^\mu_- \cap \Gr_+ : L_{[1,i]} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
 %Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
 \end{equation*}
-
-Using Lemma \ref{le:Srdim}, we see that
-$$
-\mathring Z(\tau)_1 = \{ L \in \Gr_+ : \rdim L_{[j,i]} = \lambda(i)_j + \dots + \lambda(i)_i \text{ for all $ 1 \le j \le i \le m $} \}
-$$
-where note that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ of weight $ 1, \dots, i $.
+% 
+Using Lemma \ref{le:rdimTrans}(2) and Lemma \ref{le:Srdim}, we see that
+$$
+\mathring Z(\tau)_1 = \{ L \in \Gr_+ : \rdim L_{[a,b]} = \lambda(b)_a + \dots + \lambda(b)_b \text{ for all $ 1 \le a \le b \le m $} \}
+$$
+where note that $ \lambda(b)_a + \dots + \lambda(b)_b$ is the number of boxes on rows $ a, \dots, b$ of weight $ 1, \dots, b $.
 % \jcom{We could write that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ filled with $ 1, \dots, i $.}
@@
 
-We also note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$.  
-\jcom{Need to justify this last sentence.
-There are two possibilities.
-Either we can use compute the MV polytope corresponds to $ \tau $ and show that it lies in the Weyl polytope for $ \lambda $ (is this done anywhere in the literature) or we could use the Mirkovic-Vybornov isomorphism.}
-
-\acom{Ask Joel about this}
+Now, by the results of \cite{kamnitzerfibreshives} (see especially the proof of Theorem 1.4), we note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$.
 
@@
 $$
-
-\jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}
+Since $ \dim \mathring Z(\tau)_2 = \rho(\lambda - \mu)$, we see that $ \mathring Z(\tau) $ must have at least one component of the maximal dimension.
+To see that it cannot have any other components of maximal dimension, we note that
+$$ \bigsqcup_{\tau \in YT(\lambda)_\mu} \mathring Z(\tau) \subset \Gr^\lambda \cap S_-^\mu$$
+and the number of irreducible components of the right hand side \acom{of max dim?} \jcom{it is pure dimensional, as mentioned at the beginning of section 6.1} equals $|YT^\lambda_\mu|$, thus on the left hand side, each $ \mathring Z(\tau)$ can only have one irreducible component of dimension $ \rho(\lambda - \mu)$.
+
+%\jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}
 
@@
 % 
-We do not know whether $\mathring X(\tau)$ is in general irreducible. 
+%We do not know whether $\mathring X(\tau)$ is in general irreducible. 
 % reduced or has embedded components. 
@@
 % \jcom{Now that we have $ \ast_s$ defined in the fusion section, we can refer to that here.}
-Recall the map $\theta : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr$ from \Cref{ss:affgrs}. 
+%Recall the map $\theta : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr$ from \Cref{ss:affgrs}. 
 \begin{proposition}
-    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\theta^{-1}(\mathring Z(\tau')\times\mathring Z(\tau''))$. 
+    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_\Cx \mathring Z(\tau''))$. 
     % \[
@@
 
-\jcom{We never quite defined $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$ so maybe we should write this down somewhere.
+%\jcom{We never quite defined $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$ so maybe we should write this down somewhere.
 Once we do this, I'm pretty sure that we will not get ``dense'' but an equality.}
 
-\acom{Should we just use $\tau^{-1}(\mathring Z(\tau') \times \mathring Z(\tau''))$ instead?}
-
-\jcom{Yes, maybe that is a good idea.
+%\acom{Should we just use $\tau^{-1}(\mathring Z(\tau') \times \mathring Z(\tau''))$ instead?}
+
+%\jcom{Yes, maybe that is a good idea.
 We should recall $ \tau $, and I suppose since we have two $ \tau$s, we had better change notation.
@@
 
-\acom{Changed it to $\theta$ \emoji{worried}}
+%\acom{Changed it to $\theta$ \emoji{worried}}
+\jcom{I went ahead and defined $ \ast_\Cx$ in the fusion section so now we can use it.}
 
@@
 $$(L_{[1,i]}(0),L_{[1,i]}(s))  = (L(0)_{[1,i]},L(s)_{[1,i]}) \in \Gr^{\lambda'(i)}\times\Gr^{\lambda''(i)}$$ 
-and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$. The argument can be reversed for $L\in\theta^{-1}(\mathring Z(\tau')\times Z(\tau''))$.
+and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$. The argument can be reversed for
+$L\in\mathring Z(\tau')\ast_\Cx \mathring Z(\tau'')$.
+% \theta^{-1}(\mathring Z(\tau')\times Z(\tau''))$.
 % 
@@
 
-Now, in analogy with the Beilinson--Drinfeld construction \acom{add loc cit} we define $X(\tau',\tau'')_{0,0}$ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ in $M_N(\CC)\times\CC$.
+Now, in analogy with the Beilinson--Drinfeld construction \acom{add loc cit} \jcom{I think just add a reference our fusion section} we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ in $M_N(\CC)\times\CC$.
 % 
 \begin{corollary}
+\label{cor:iota}
     % The image of $\mathring X(\tau',\tau'')_{0,0}$ in $\mathring Z(\tau')\ast_0 \mathring Z(\tau'')$ is dense. In particular 
-    $\iota(X(\tau),X(\tau',\tau'')) = \iota(Z(\tau),Z(\tau')\circ Z(\tau''))\,.$
+    $\iota(X(\tau), X(\tau',\tau'')_{0,0}) = \iota( Z(\tau), Z(\tau')\ast_0 \mathring Z(\tau''))\,.$
 \end{corollary}
-% 
+\acom{Do we need to introduce $X(\tau',\tau'')_{0,0}$ to state the theorem or can we state it on $\mathring X$'s and $\mathring Z$'s again?}
+\jcom{I changed the statement. I will edit the proof later. }
+
+%
+
 To prove this we require the following main result of \cite{dthesis}.
@@
 \end{theorem}
+% 
+\begin{proof}[Proof of~\Cref{cor:iota}]
+Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ (and dimensions are equal: $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?}) irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties.
+The isomorphisms of Prop.\ 5 and Lem.\ 8 then give the desired equality (from left to right).
+\end{proof}
 % 
@@
 $$
+
+\jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
 
@@
 \[
-\begin{array}{c|c|c} 
+\begin{array}{ccc} 
 \tau & \text{Coordinate ring of }Z(\tau) & \text{Lusztig-datum} \\ \hline

### 2021-05-27 draft.tex
C to A

@@
 We identify $\ZZ^m$ with the coweight lattice of $G$ and say that a coweight 
-% The coweight lattice of $ G $ is $ \ZZ^m = \Hom(\CC^\times,T)$.
+% The coweight lattice of $ G $ is $ \ZZ^m = \Hom(\AA^\times,T)$.
 % TODO: Thank you - resolved!
 % \acom{This identification assumes we are taking $\CC$ points of $G$ right?
-i.e.\ it's really $P(T(\CC)) = \Hom(\CC^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?}
+i.e.\ it's really $P(T(\CC)) = \Hom(\AA^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?}
 % \jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}
@@
 \jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
-\acom{Do you mean that if we go with $\AA$ we should change $\CC^\times$ as well?
+\acom{Do you mean that if we go with $\AA$ we should change $\AA^\times$ as well?
 Also, would you agree that the distinction is the topology?
 So $\AA$ is better if we were using ``generic'' to describe $s\ne 0$, which we are not.}
-\jcom{Yes, either we should write $ \AA, \AA^\times $ or $ \CC, \CC^\times$.  There is no distinction.  Always in this paper, we work with the Zariski topology whether we write $ \AA $ or $ \CC$.}
+\jcom{Yes, either we should write $ \AA, \AA^\times $ or $ \CC, \AA^\times$.  There is no distinction.  Always in this paper, we work with the Zariski topology whether we write $ \AA $ or $ \CC$.}
+\acom{Ok, let's be fancy and write $\AA$.
+(So if someone writes $s\to 0$ you don't think of it as $s$ approaches $0$ in the metric topology, but really as the limit of ideals $(s)\supset (s^2)\supset \cdots$ which, I hope, is the zero ideal?)}
 
@@
 
-Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.  
+Let $ \Gr_{0, \AA^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.  
 % 
@@
 \label{eq:mvitau}
-    \theta : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
+    \theta : \Gr_{0, \AA^\times} \rightarrow \Gr \times \Gr \, .
 \end{equation}
-(This $\theta$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
+(This $\theta$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \AA^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
 %  TODO: outstanding
@@
 
-Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $$ X_1 \ast_{\Cx} X_2 := \theta^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $$
+Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $$ X_1 \ast_{\Cx} X_2 := \theta^{-1}(X_1 \times X_2) \subset \Gr_{0, \AA^\times} $$
 % 
@@
 % TODO: outstanding 
-% \acom{Well you might not want but I think it would be good to tell the reader why we use the notation $\CC^\times$ for $\AA\setminus 0$ in $\AA$ or why we use the notation $\AA$ at all..
+% \acom{Well you might not want but I think it would be good to tell the reader why we use the notation $\AA^\times$ for $\AA\setminus 0$ in $\AA$ or why we use the notation $\AA$ at all..
 E.g.\ do we know what happens for $\GL_m(k)$ over some other base field $k$.}
@@
 But the converse is not so obvious.
-(I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu', \mu''}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu', \mu''}$ and $\UU$ as attracting sets for a $\CC^\times$ action.
+(I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu', \mu''}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu', \mu''}$ and $\UU$ as attracting sets for a $\AA^\times$ action.
 Which do you prefer?}
@@
 \begin{proof}
-We could prove this by observing the both sides are the attracting locus of an appropriate $ \CC^\times$ action. However, we will give the following more algebraic proof.
+We could prove this by observing the both sides are the attracting locus of an appropriate $ \AA^\times$ action. However, we will give the following more algebraic proof.
 
@@
 % 
-Given $s\in\CC^\times$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
+Given $s\in\AA^\times$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
 % 
@@
 \begin{equation*}
-        % X(\tau')\ast_{\CC^\times} X(\tau'') = 
-        \mathring X(\tau',\tau'')_{0,\CC^\times} = 
+        % X(\tau')\ast_{\AA^\times} X(\tau'') = 
+        \mathring X(\tau',\tau'')_{0,\AA^\times} = 
     \left\{
-        (A,s)\in M_N(\CC) \times \CC^\times: 
+        (A,s)\in M_N(\CC) \times \AA^\times: 
         A \in \mathring X(\tau',\tau'')_{0,s} 
@@
 % \jcom{Now that we have $ \ast_s$ defined in the fusion section, we can refer to that here.}
-%Recall the map $\theta : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr$ from \Cref{ss:affgrs}. 
+%Recall the map $\theta : \Gr_{0, \AA^\times} \rightarrow \Gr \times \Gr$ from \Cref{ss:affgrs}. 
 \begin{proposition}
-    The image of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_\Cx \mathring Z(\tau''))$. 
+    The image of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_\Cx \mathring Z(\tau''))$. 
     % \[
@@
 
-%\jcom{We never quite defined $\mathring Z(\tau')\ast_{\CC^\times} \mathring Z(\tau'')$ so maybe we should write this down somewhere.
+%\jcom{We never quite defined $\mathring Z(\tau')\ast_{\AA^\times} \mathring Z(\tau'')$ so maybe we should write this down somewhere.
 Once we do this, I'm pretty sure that we will not get ``dense'' but an equality.}
@@
 % \acom{Better way to say?} \jcom{I think that you can just rewrite this first half as if and only if and drop the second half. }
-% Given $L\in\mathring Z(\tau') \ast_{\CC^\times}\mathring Z(\tau'')$ let $A$ be such that $L = g(A)\CC[t]^i$. \acom{But, is it clear that $A\in\mathring X(\tau',\tau'')_{0,s}$?} 
+% Given $L\in\mathring Z(\tau') \ast_{\AA^\times}\mathring Z(\tau'')$ let $A$ be such that $L = g(A)\CC[t]^i$. \acom{But, is it clear that $A\in\mathring X(\tau',\tau'')_{0,s}$?} 
 % Do we need that there exists $(A',A'')\in M_{N'}\times M_{N''}$ such that $L(0) = g(A')\cO^m$ and $L(s) = g(A'')\cO^m$, and that we could take $A'\oplus A''=A$ up to some conjugation that puts $A'\oplus A''\in\TT_\mu$ which is possible because $\TT_\mu$ intersects $\OO^{\lambda',\lambda''}_{0,\AA}$ transversely?
@@
 
-Now, in analogy with the Beilinson--Drinfeld construction \acom{add loc cit} \jcom{I think just add a reference our fusion section} we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\CC^\times}$ in $M_N(\CC)\times\CC$.
+Now, in analogy with the Beilinson--Drinfeld construction \acom{add loc cit} \jcom{I think just add a reference our fusion section} we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ in $M_N(\CC)\times\CC$.
 % 

### 2021-05-27 draft.tex
up to 63

@@
 \subsection{The fusion construction}
+\label{ss:fuscon}
 \jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
@@
 
-For $ s \in \CC$ we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
+Given $ s \in \AA$ we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
 
@@
 \label{def:Olam}
-The nilpotent orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.
+The nilpotent (adjoint) orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.
+These matrices and the linear operators they represent will be said to have Jordan type $\lambda$.
 \end{definition}  
@@
 \label{def:Olamlam}
-    For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
+    For $ s \in \CC, s \ne 0$, the (adjoint) orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
+    These matrices and the linear operators they represent will be said to have Jordan type $((0,\lambda'), (s,\lambda''))$.
 \end{definition}  
 %
-These matrices and the linear operators they represent will be said to have Jordan type $((0,\lambda'), (s,\lambda''))$.
 
@@
 
-We recall that these adjoint orbit closures are given by rank conditions.  
-More precisely we have
+We recall that these orbits have closures which are given by rank conditions.  
+More precisely, we have
 $$
@@
 
-Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ (called a rank function).  Let $k $ be maximal such that $ r(k) \ne 0 $.
+Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ called a \new{rank function}.  Let $k $ be maximal such that $ r(k) \ne 0 $.
 % \jcom{I don't know if it is really necessary to introduce this $ k$.
@@
 Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes} \acom{I like the idea of making it $N$}
-
-Let $ W$ be a subspace of $ \AA^k$. Eisenbud \& Saltman define a flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions. We will now describe these fibres.
+% 
+Let $ W$ be a subspace of $ \AA^k$.
+Eisenbud and Saltman define and study the flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions.
+We will now describe these fibres.
 
@@
 Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities.
-There exist $ 0=k_0< k_1< \dots < k_\ell = k $, distinct $ s_1, \dots, s_\ell \in \CC$ and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
-$$ s_j = z_{p(k_{j-1}+1)} = \cdots = z_{p(k_j)}\,.
-$$ We require that $ p $ is of minimal length, given the choice of $ s_1, \dots, s_\ell$.
-The data $s_\bullet, p, k_\bullet$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
+There exist a sequence of integers $k_\bullet = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, a sequence of points $s_\bullet = (s_1, \dots, s_\ell )\in\AA^\ell$ such that $s_i\ne s_j$ for any $i\ne j$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
+$$ s_j = z_{p(k_{j-1}+1)} = z_{p(k_{j-1} + 2)} =  \cdots = z_{p(k_j)}$$ 
+for each $j = 1,\dots,\ell$. 
+Given the choice of $ s_\bullet$ we require that $ p $ is of minimal length. 
+Given $z$, the data $k_\bullet, s_\bullet, p$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
 % 
@@
 \jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
+\acom{I don't think that there is any need to swap back.
+But maybe we could use $c$ (for column) isntead of $i$, since we use $i$ in the same context quite a bit to denote a letter in the alphabet $\{1,\dots,m\}$.}
 %\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
@@
 
-For $ s \in \CC$, we define $ z(s) \in \CC^k$, with $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1, \dots, k$.
-
-For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of $ \ell = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
+For $ s \in \AA$, we define $ z(s) \in \AA^k$ by 
+\[
+\begin{cases}
+    z(s)_{p(j)} = 0 &  j = 1, \dots, k_1 \\
+    z(s)_{p(j)} = s & j = k_1 + 1, \dots, k\,.
+\end{cases}    
+\]
+% $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1, \dots, k$.
+
+For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of 
+\(\ell =2\), \(k_\bullet = (0,\lambda_1')\), \(s_\bullet = (0,s)\) and the permutation $p$.
+% $ \ell = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
 We also see that
@@
 \end{equation}
-On the other hand, for $z(0)$, we get that $ r = 1$ and that 
+On the other hand, for $z(0)$, we get that $ \ell = 1$ and that \acom{This was $r = 1$ but I think it should be $\ell = 1$.}
 \begin{equation} 
@@
 % \begin{definition}
-The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is defined to be the affine space of matrices of the form
+Recall that $\mu=(\mu_1,\dots,\mu_m)$ is a partition of $N$. The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is the affine space of $N\times N$ matrices of the form
 % defined as the set of $A\in M_N(\CC)$ such that 
@@
 % a $\mu$ Jordan form matrix plus 
-$J_{0,\mu} + x$ where $x$ is a $\mu\times\mu$ block matrix with possibly nonzero entries in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
+$J_{0,\mu} + x$ where $x$ is a $\mu\times\mu$ block matrix with possibly nonzero entries $A_{ij}^1,\dots,A_{ij}^{\min(\mu_i,\mu_j)}$ in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
 % $\dim \TT_\mu = N^2 - \dim \OO_\mu$.
@@
 \]
-for some $A_{ij}^k\in\CC$. 
+for some $A_{ij}^k\in\AA$. 
 % \[
@@
 
-To $ A \in \TT_\mu$ we will associate the $m\times m$ matrix 
-of polynomials 
+To $ A \in \TT_\mu$ we will associate the $m\times m$ matrix of polynomials 
 % $ g(A) = \left( g(A)_{ij} \right)$ 
-$g(A)$ in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
+$g(A)$ in $ M_m(\AA[t]) $ whose $(i,j)$th entry is defined as follows.
 \begin{equation}
@@
 \end{equation}
-$A^k_{ji}$ denotes the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
+% $A^k_{ji}$ denotes the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
 %
@@
 
-In other words, the $ i,j$ block of $ A $ is used to produce a polynomial which is inserted in the $ j,i$ entry of $ g(A)$.
+In other words, the $ \mu_i\times\mu_j$ block of $ A $ is used to produce a polynomial which is inserted in the $(j,i)$ entry of $ g(A)$.
 
@@
 \end{lemma}
-\acom{Doesn't the identification $G(K)/G(O) \to G(O)\ G(K)$ coming from $g\mapsto g^{-1}$ give us a minus sign somewhere, since we are sending $S^\mu_w$ to $S^{-\mu}_w$, so $D_{\omega_i}(L) = -\rdim L_{[1,i]}$.
+% \acom{Doesn't the identification $G(K)/G(O) \to G(O)\ G(K)$ coming from $g\mapsto g^{-1}$ give us a minus sign somewhere, since we are sending $S^\mu_w$ to $S^{-\mu}_w$, so $D_{\omega_i}(L) = -\rdim L_{[1,i]}$.
 Ignoring the minus sign for now, for $j\le i\le m$, and $L_{[1,i]}$ in $S^{\mu(i)}_- \cap S^{\lambda(i)}_+$ we’d like $D_{\omega_j}(L_{[1,i]}) = \rdim (L_{[1,i]})_{[1,j]} = \lambda(i)_j + \cdots + \lambda(i)_i$ whereas the claim $(L_{[1,i]})_{[1,j]} = L_{[1,j]}$ hides that this lattice also depends on $i$?
@@
 $n_{(a,b)} (L_{[1,i]}) = -D_{[a+1,b]} - D_{[a , b-1]} + D_{[a + 1, b-1]} + D_{[a,b]} = - \rdim L_{[a+1,b]} - \rdim L_{[a,b-1]} + \rdim L_{[a+1,b-1]} + \rdim L_{[a,b]}$}
-\jcom{I warned you when we talked on Tuesday that there might be some problems, but I think that we shouldn't dig any deeper here.} 
-\acom{Well, it's not that deep..
+% \jcom{I warned you when we talked on Tuesday that there might be some problems, but I think that we shouldn't dig any deeper here.} 
+% \acom{Well, it's not that deep..
 it's just that $(L_{\gamma_1})_{\gamma_2}$ involves taking $\gamma_2^c\subset \gamma_1$ and landing in $\cO^{\gamma_1\cap\gamma_2}$ whereas $L_{\gamma_2}$ involves taking $\gamma_2^c\subset[m]$ and landing in $\cO^{\gamma_2}$ ...so I think the change makes it true.}
-\jcom{But I assumed that $ \gamma_1 \subset \gamma_2$, so I don' think that taking intersection is necessary.}
-\acom{Even so?
+% \jcom{But I assumed that $ \gamma_1 \subset \gamma_2$, so I don' think that taking intersection is necessary.}
+% \acom{Even so?
 What was written before was $(L_{\gamma_1})_{\gamma_2} = L_{\gamma_2} $ and if $\gamma_1\subset\gamma_2$ then the intersection is $\gamma_1$.
@@
 6(2), so we can do without it?}
-\jcom{Oh, I guess there was a typo.  I fixed it now.  It is used in the proof of Prop 4, I will add a reference.}
+% \jcom{Oh, I guess there was a typo.  I fixed it now.  It is used in the proof of Prop 4, I will add a reference.}
 
@@
 
-For this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (previously we left out the subscript). We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+In this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (previously we left out the subscript).
+We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
+\acom{HB, ``..we will write.., because we will need the opposite cell..''}
 % \acom{Maybe we shouldn't decorate $S^\mu$ with a subscript $-$ after all since we certainly won't want to add to $S^{\mu',\mu''}_{0,\AA}$ in underscores.}
@@
 \end{proof}
-\jcom{I added a proof.  We can get delete and just put a reference to mvcycle if you prefer.}
-
-\acom{No no this is good! Thanks for other additions}
+% \jcom{I added a proof.  We can get delete and just put a reference to mvcycle if you prefer.}
+
+% \acom{No no this is good! Thanks for other additions}
 
@@
 % \acom{I've been meaning to update the paper. It's peppered with ``typos''.}
-
+% 
 First, we consider 
@@
 $$ \bigsqcup_{\tau \in YT(\lambda)_\mu} \mathring Z(\tau) \subset \Gr^\lambda \cap S_-^\mu$$
-and the number of irreducible components of the right hand side \acom{of max dim?} \jcom{it is pure dimensional, as mentioned at the beginning of section 6.1} equals $|YT^\lambda_\mu|$, thus on the left hand side, each $ \mathring Z(\tau)$ can only have one irreducible component of dimension $ \rho(\lambda - \mu)$.
+and the number of irreducible components of the right hand side 
+% \acom{of max dim?} \jcom{it is pure dimensional, as mentioned at the beginning of section 6.1} 
+equals $|YT^\lambda_\mu|$, thus on the left hand side, each $ \mathring Z(\tau)$ can only have one irreducible component of dimension $ \rho(\lambda - \mu)$.
 
@@
 
-Given $A \in M_N(\CC)$ we denote by $A\big|_{\CC^p}$ the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$.
+Given $A \in M_N(\AA)$ we denote by $A\big|_{\CC^p}$ the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$.
 If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
+\acom{Change $\CC$'s to $\AA$'s?}
 % TODO: address 
@@
 % The space we have defined may therefore not be a true fusion in the sense that it may not come from two obvious spaces. \acom{Joel?} 
-\jcom{Even if $ \mu', \mu'$ are dominant, it is not obvious how $ A $ corresponds to a pair $(A', A'')$.
+% \jcom{Even if $ \mu', \mu'$ are dominant, it is not obvious how $ A $ corresponds to a pair $(A', A'')$.
 And since I don't think that ``true fusion'' is a well-defined thing, I think that we can delete the last sentence.}
-\acom{Ok. By choosing bases of generalized eigenspaces?}
+% \acom{Ok. By choosing bases of generalized eigenspaces?}
 
@@
 
-%\acom{Changed it to $\theta$ \emoji{worried}}
-\jcom{I went ahead and defined $ \ast_\Cx$ in the fusion section so now we can use it.}
+% \acom{Changed it to $\theta$ \emoji{worried}}
+% \jcom{I went ahead and defined $ \ast_\Cx$ in the fusion section so now we can use it.}
+% \acom{TYVM}
 
@@
 
-Now, in analogy with the Beilinson--Drinfeld construction \acom{add loc cit} \jcom{I think just add a reference our fusion section} we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ in $M_N(\CC)\times\CC$.
+Now, in analogy with the Beilinson--Drinfeld construction \Cref{ss:fuscon}
+% \acom{add loc cit} \jcom{I think just add a reference our fusion section} \acom{Yeah that's what I meant, taking loc cit literally}
+we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ in $M_N(\CC)\times\CC$. 
 % 
@@
 \jcom{I changed the statement. I will edit the proof later. }
-
-%
-
-To prove this we require the following main result of \cite{dthesis}.
+%
+
+To prove this we require the following resutl from \cite{dthesis}.
 \begin{theorem}
@@
 \begin{proof}[Proof of~\Cref{cor:iota}]
-Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ (and dimensions are equal: $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?}) irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties.
+Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ and $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?} irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties.
 The isomorphisms of Prop.\ 5 and Lem.\ 8 then give the desired equality (from left to right).

### 2021-05-27 draft.tex
63 begun

@@
 % 
-Goal: 
+There is a map from $\irr \overline{\Gr^\lambda\cap S^\mu_-} \to \CC[N]$ that factors through \acom{??} $\overline{S^0_+\cap S^\nu_-}$ for $\nu = \lambda - \mu$.
+The irreducible components of $ \overline{S^0_+\cap S^\nu_-}$ are called \new{stable MV cycles} and there is a bijection given by multiplication by $t^\lambda$ from $\{Z\in \irr \overline{S^0_+\cap S^\nu_-} : t^\lambda Z \subset\overline\Gr^\lambda\}$ to $\irr \overline{\Gr^\lambda\cap S^\mu_-} $.
+Moreover, the induced map on $\cup L(\lambda)\to\CC[N]$ is not injective, while that on the collection of all stable MV cycles ($\oplus L(0)_\nu\to\CC[N]$) is.
+
+In \cite{baumann2019mirkovic}, Baumann, Knutson and the third author show that the stable MV cycles define a perfect basis of $\CC[N]$ whose structure constants are given by intersection multiplicities.
+%
+
+\begin{theorem}
+    (\cite[Theorem~7.11]{baumann2019mirkovic})
 $$
@@
 $$
+\end{theorem}
 
 \jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
+\acom{Begun}
 

### 2021-05-29 draft.tex
joels edits mostly 62

@@
 \acom{Ok, let's be fancy and write $\AA$.
-(So if someone writes $s\to 0$ you don't think of it as $s$ approaches $0$ in the metric topology, but really as the limit of ideals $(s)\supset (s^2)\supset \cdots$ which, I hope, is the zero ideal?)}
+(So if someone writes $s\to 0$ you don't think of it as $s$ approaches $0$ in the metric topology, but really as the limit of ideals $(s)\supset (s^2)\supset \cdots$ which, I hope, is the zero ideal?) Tentatively remapped our command for $\mathbb C$ to give $\AA$.
+It looks really funny to use it as notation for a field/conflate field and scheme---is there really no distinction?
+Surely $\AA = \spec \AA[t]$ is not great practice?}
+\jcom{I think that it would be more typical to use $ \CC $ for the field and use $ \AA$ for the affine line.  I changed $ \CC $ back to $\CC$.}
 
@@
 \end{equation}
-(This $\theta$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \AA^\times$ instead of the complement of the diagonal in $ \CC^2 $.)
+(This $\theta$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \AA^\times$ instead of the complement of the diagonal in $ \AA^2 $.)
 %  TODO: outstanding
@@
 But maybe we could use $c$ (for column) isntead of $i$, since we use $i$ in the same context quite a bit to denote a letter in the alphabet $\{1,\dots,m\}$.}
+\jcom{Sure, that is a good idea.}
 %\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
@@
 \end{equation}
-On the other hand, for $z(0)$, we get that $ \ell = 1$ and that \acom{This was $r = 1$ but I think it should be $\ell = 1$.}
+On the other hand, for $z(0)$, we get that $ \ell = 1$ and that \acom{This was $r = 1$ but I think it should be $\ell = 1$.} \jcom{Yes, you are correct.}
 \begin{equation} 
@@
 
-\section{Falling Action} % Resolution
+\section{\sout{Falling Action}} % Resolution
 \subsection{MV cycles}
@@
 \end{definition}
+
+\jcom{In this section, I think that $ \mu$ is not necessarily dominant.  So I think that we should we recall our previous notation, but say that $ \mu $ might not be dominant here.}
+
 By \cite{mirkovic2007geometric}, all these irreducible components have dimension $ \rho(\lambda - \mu)$, where $ \rho = (m, m-1, \dots, 1)$.
@@
 \acom{We should introduce $D_\gamma$ briefly.}
-
-In this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (previously we left out the subscript).
-We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.
-\acom{HB, ``..we will write.., because we will need the opposite cell..''}
+\jcom{I think that this is sufficient, since it doesn't really play any role in our paper.}
+
+In this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (with a subscript), because we will also need the opposite semi-infinite cell $S^\mu_+ := N(\cK)t^\mu$.
+%\acom{HB, ``..we will write.., because we will need the opposite cell..''}
 % \acom{Maybe we shouldn't decorate $S^\mu$ with a subscript $-$ after all since we certainly won't want to add to $S^{\mu',\mu''}_{0,\AA}$ in underscores.}
@@
 
-Given $A \in M_N(\AA)$ we denote by $A\big|_{\CC^p}$ the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$.
+Given $A \in M_N(\CC)$ we denote by $A\big|_{\CC^p}$ the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$.
 If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
@@
 Let $\tau\in YT(\lambda)_\mu$ with $\mu$ dominant. 
-Under the isomorphism of \Cref{cor:mvy} the MV cycle $Z(\tau)$ corresponds to the \new{generalized orbital varieties} $X(\tau)$ which is obtained by taking the closure of the top-dimensional
-% \acom{speak to this?} 
-irreducible component of
-% from $\tau\in YT(\lambda)_\mu$ by 
+We define
 \[
@@
     \}\,.
-% }    
-\]
-% 
-%We do not know whether $\mathring X(\tau)$ is in general irreducible. 
-% reduced or has embedded components. 
-% \jcom{I guess we need to assume that $ \mu $ is dominant here.}
+\]
+\jcom{Maybe for consistency, we should write $ \n \cap \TT_\mu$ (opposite order).}
+
 \begin{lemma}
@@
 \end{lemma}
+\jcom{We should add a proof here.  It will be very similar to Prop 5 below.}
+
+By \cite{dthesis}, $ \mathring X(\tau) $ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.
+We write $ X(\tau)$ for the closure of this component.
+It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu$ and will be called a \textbf{generalized orbital variety}.
+
+\jcom{We should give a more specific citation to \cite{drthesis} here and below.
+Also, throughout this paper, we should either cite your paper or your thesis, but not both (unless there is a very good reason to do so).
+I reorganized this section a bit.
+Feel free to add a bit more exposition.}
+
+In fact, these are all the generalized orbital varieties by  \cite{dthesis}. 
+\begin{theorem}
+    \label{pr:govsasirrecs}
+    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
+\end{theorem}
+%
 
@@
 % 
-We will use this theorem to describe the fusion of two MV cycles. 
-% 
-Let us begin by introducing a ``fusion of generalized orbital varieties'' to match. 
+Our goal is to describe the fusion of two MV cycles using fusion of generalized orbital varieties, which we will now define. 
 % 
 Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as in previous sections.
+\jcom{I think that this is can move earlier, with the caveat that I mentioned earlier about $ \mu $ being non-dominant in 6.1 and dominant here.}
+
 % 
@@
 \end{corollary}
-\acom{Do we need to introduce $X(\tau',\tau'')_{0,0}$ to state the theorem or can we state it on $\mathring X$'s and $\mathring Z$'s again?}
-\jcom{I changed the statement. I will edit the proof later. }
-%
-
-To prove this we require the following resutl from \cite{dthesis}.
-\begin{theorem}
-    \label{pr:govsasirrecs}
-    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
-\end{theorem}
-% 
-\begin{proof}[Proof of~\Cref{cor:iota}]
-Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ and $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?} irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties.
-The isomorphisms of Prop.\ 5 and Lem.\ 8 then give the desired equality (from left to right).
+%\acom{Do we need to introduce $X(\tau',\tau'')_{0,0}$ to state the theorem or can we state it on $\mathring X$'s and $\mathring Z$'s again?}
+%\jcom{I changed the statement. I will edit the proof later. }
+%
+
+\begin{proof}
+%[Proof of~\Cref{cor:iota}]
+%Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ and $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?} irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties.
+We can compute intersection multiplicities by passing to dense constructible subsets.  By
+the isomorphisms of Prop.\ 5 and Lem.\ 8, $X(\tau) $ is dense constructible subset of $ Z(\tau) $ and $ X(\tau', \tau'')_{0,0} $ is a dense constructible subset of $ Z(\tau') \ast_0 Z(\tau'') $.  
 \end{proof}
@@
 Let $G = \GL_4$. There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables. We list the corresponding tableaux, coordinate ring of the MV cycle, and Lusztig-datum below:
+
+\jcom{This is a nice table.  But these are the coordinate rings of $ X(\tau)$, not of $ Z(\tau) $.}
 
@@
 
+\jcom{I think that you should clarify what you mean by ``our ideal'' below.  I think that it is the ideal of $ X(\tau', \tau'')_{0,0}$, is that correct?}
+
 \begin{example}

### 2021-05-29 draft.tex
changed i to c and some other subscripts in 31

@@
 \label{ss:fuscon}
-\jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
-\acom{Do you mean that if we go with $\AA$ we should change $\AA^\times$ as well?
+% \jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
+% \acom{Do you mean that if we go with $\AA$ we should change $\AA^\times$ as well?
 Also, would you agree that the distinction is the topology?
 So $\AA$ is better if we were using ``generic'' to describe $s\ne 0$, which we are not.}
-\jcom{Yes, either we should write $ \AA, \AA^\times $ or $ \CC, \AA^\times$.  There is no distinction.  Always in this paper, we work with the Zariski topology whether we write $ \AA $ or $ \CC$.}
-\acom{Ok, let's be fancy and write $\AA$.
+% \jcom{Yes, either we should write $ \AA, \AA^\times $ or $ \CC, \AA^\times$.  There is no distinction.  Always in this paper, we work with the Zariski topology whether we write $ \AA $ or $ \CC$.}
+% \acom{Ok, let's be fancy and write $\AA$.
 (So if someone writes $s\to 0$ you don't think of it as $s$ approaches $0$ in the metric topology, but really as the limit of ideals $(s)\supset (s^2)\supset \cdots$ which, I hope, is the zero ideal?) Tentatively remapped our command for $\mathbb C$ to give $\AA$.
@@
 Surely $\AA = \spec \AA[t]$ is not great practice?}
-\jcom{I think that it would be more typical to use $ \CC $ for the field and use $ \AA$ for the affine line.  I changed $ \CC $ back to $\CC$.}
+% \jcom{I think that it would be more typical to use $ \CC $ for the field and use $ \AA$ for the affine line.  I changed $ \CC $ back to $\CC$.}
 
@@
 $$
-    \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^i \le N - \#\text{~boxes in first $i$ columns of }\lambda \}
+    \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^c \le N - \#\text{~boxes in first $c$ columns of }\lambda \}
 $$
@@
     \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i &\le N - 
-    \#\text{~boxes in first $i$ columns of }\lambda' \\
-    \rk (A-s)^i &\le N - \#\text{~boxes in first $i$ columns of }\lambda'' \}\,. 
+    \#\text{~boxes in first $c$ columns of }\lambda' \\
+    \rk (A-s)^c &\le N - \#\text{~boxes in first $c$ columns of }\lambda'' \}\,. 
 \end{split}
@@
 
-Let $ r $ be a decreasing, concave, non-negative function with $r(0) = N$ called a \new{rank function}.  Let $k $ be maximal such that $ r(k) \ne 0 $.
+Let $ r $ be a decreasing, concave, non-negative function of $\NN$ with $r(0) = N$ called a \new{rank function}.  Let $k $ be maximal such that $ r(k) \ne 0 $.
 % \jcom{I don't know if it is really necessary to introduce this $ k$.
@@
 Let $ W$ be a subspace of $ \AA^k$.
-Eisenbud and Saltman define and study the flat family $ X_{r,W} \rightarrow W$, whose fibres are reduced and defined by rank conditions.
+Eisenbud and Saltman define and study the flat family $ X_{r,W} \rightarrow W$ whose fibres are reduced and defined by rank conditions.
 We will now describe these fibres.
-
-Let $ z \in \AA^k$.
-Some of the coordinates of $z$ may be equal; we introduce some data to keep track of these equalities.
-There exist a sequence of integers $k_\bullet = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, a sequence of points $s_\bullet = (s_1, \dots, s_\ell )\in\AA^\ell$ such that $s_i\ne s_j$ for any $i\ne j$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
-$$ s_j = z_{p(k_{j-1}+1)} = z_{p(k_{j-1} + 2)} =  \cdots = z_{p(k_j)}$$ 
-for each $j = 1,\dots,\ell$. 
+\acom{departing slightly from ES's lingo/notations..}
+
+Let $ z \in \AA^k$ be a point.
+Some of the coordinates of $z$ may be equal so we introduce the following data to keep track of these equalities.
+There exist a sequence of integers $k_\bullet = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, a sequence of points $s_\bullet = (s_1, \dots, s_\ell )\in\AA^\ell$ such that $s_a\ne s_b$ for any $a\ne b$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
+$$ 
+    s_a = z_{p(k_{a-1}+1)} = z_{p(k_{a-1} + 2)} =  \cdots = z_{p(k_a)}
+$$ 
+for each $a = 1,\dots,\ell$. 
 Given the choice of $ s_\bullet$ we require that $ p $ is of minimal length. 
-Given $z$, the data $k_\bullet, s_\bullet, p$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
+Then, given $z$, the data $k_\bullet, s_\bullet, p$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
 % 
@@
 
-Next for $ j = 1, \dots \ell $ and $ i = 1, \dots, k_{j+1} - k_j$, we define
+Next for $ a = 1, \dots \ell $ and $ c = 1, \dots, k_{j+1} - k_j$, we define
 $$
     % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
-    r_{z,j}(i):= N + \sum_{a = 1}^i r(p(k_j + a)) - r(p(k_j +a) - 1)  \, . 
+    r_{z,a}(c):= N + \sum_{d = 1}^c r(p(k_a + d)) - r(p(k_a + d) - 1)  \, . 
 $$
@@
 \jcom{Sure, that is a good idea.}
+\acom{Ok, switched some letters. Think $d$ is good as `delta'.}
 %\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
@@
     \label{eq:ESfibre}
-    X_{r,z} = \{ A \in M_N(\CC) :\rk (A-s_j)^i\le r_{z,j}(i) \text{ for all } i , j \text{ as above}\}.
+    X_{r,z} = \{ A \in M_N(\CC) :\rk (A-s_a)^c\le r_{z,a}(c) \text{ for all } c , a \text{ as above}\}.
 \end{equation}
@@
 $$
-    r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,.
+    r(c) = N - \#\text{~boxes in first $c$ columns of }\lambda\,.
 $$
@@
 \begin{cases}
-    z(s)_{p(j)} = 0 &  j = 1, \dots, k_1 \\
-    z(s)_{p(j)} = s & j = k_1 + 1, \dots, k\,.
+    z(s)_{p(c)} = 0 &  c = 1, \dots, k_1 \\
+    z(s)_{p(c)} = s &  c = k_1 + 1, \dots, k\,.
 \end{cases}    
@@
     \begin{split}
-            r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
-            r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
+            r_{z(s), 1}(c) &=  N - \#\text{~boxes in first $c$ columns of }\lambda' \\
+            r_{z(s), 2}(c) &=  N - \#\text{~boxes in first $c$ columns of }\lambda'' \,. 
     \end{split}
 \end{equation}
-On the other hand, for $z(0)$, we get that $ \ell = 1$ and that \acom{This was $r = 1$ but I think it should be $\ell = 1$.} \jcom{Yes, you are correct.}
+On the other hand, for $z(0)$, we get that $ \ell = 1$ and that 
+% \acom{This was $r = 1$ but I think it should be $\ell = 1$.} \jcom{Yes, you are correct.}
 \begin{equation} 
 \label{eq:rcol2}
-    r_{z(0),1}(i) = 
-    r(i) = N - \#\text{~boxes in first $i$ columns of }\lambda\,. 
+    r_{z(0),1}(c) = 
+    r(c) = N - \#\text{~boxes in first $c$ columns of }\lambda\,. 
 \end{equation}

### 2021-05-29 draft.tex
roger please 63 and 70

@@
 
-\jcom{I'm not sure which of the Mirkovic--Vybornov papers to cite.} \acom{can say 07, rewritten in 19}
+\jcom{I'm not sure which of the Mirkovic--Vybornov papers to cite.} \acom{can say 07, rewritten in 19?}
 % 
@@
 \jcom{In this section, I think that $ \mu$ is not necessarily dominant.  So I think that we should we recall our previous notation, but say that $ \mu $ might not be dominant here.}
+\acom{Ok.}
 
@@
 By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
-\acom{We should introduce $D_\gamma$ briefly.}
-\jcom{I think that this is sufficient, since it doesn't really play any role in our paper.}
+% \acom{We should introduce $D_\gamma$ briefly.}
+% \jcom{I think that this is sufficient, since it doesn't really play any role in our paper.}
+% \acom{Ok; I was thinking just another half-sentence, like these are some valuation functions and/or they are used to characterise combinatorially the MV cycles.}
 
@@
 The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
+\acom{For Joel: weight or filling? See below.}
 $$
@@
 $$
-Note that $ \lambda - \mu = \displaystyle{\sum_{1 \le a < b \le m}n(\tau)_{(a,b)} \beta_{a,b}} $ where $ \beta_{a,b} $ denotes the positive root of $ G$ with a $ 1 $ in the $a $ slot and a $-1$ in the $ b $ slot.
+Note that $ \lambda - \mu = \displaystyle{\sum_{1 \le a < b \le m}n_\bullet(\tau)_{(a,b)} \beta_{a,b}} $ where $ \beta_{a,b} $ denotes the positive root of $ G$ with a $ 1 $ in the $a $ slot and a $-1$ in the $ b $ slot.
 % for 
@@
 The pattern $\gt(\tau)$ is recorded as a lower-triangular matrix (the array of shapes of subtableaux $\tau(i)$) and the datum $n_\bullet(\tau)$ is recorded as a sequence.
-\acom{See \cite[\S 4]{berenstein1988tensor} for the source?} Below is an example with $\lambda = (4,2)$ and $\mu = (3,2,1)$.
+Below is an example with $\lambda = (4,2)$ and $\mu = (3,2,1)$.
+\acom{GT patterns were introduced in \cite{berenstein1988tensor} to study branching?
+In particular \S 4 of that paper introduces the map from tableaux to patterns.
+Note that the map is not 1-to-1.}
 
@@
 If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
-\acom{Change $\CC$'s to $\AA$'s?}
+% \acom{Change $\CC$'s to $\AA$'s?} No.
 % TODO: address 
@@
 \begin{lemma}
+    \label{lem:XtZt}
     Under the Mirkovi\'c--Vybornov isomorphism $\mathring X(\tau)$ is mapped isomorphically onto $\mathring Z(\tau)$. 
@@
 \begin{proposition}
+    \label{pr:XttZtt}
     The image of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_\Cx \mathring Z(\tau''))$. 
@@
 
-Now, in analogy with the Beilinson--Drinfeld construction \Cref{ss:fuscon}
+Now, in analogy with the Beilinson--Drinfeld fusion construction of \Cref{ss:fuscon}
 % \acom{add loc cit} \jcom{I think just add a reference our fusion section} \acom{Yeah that's what I meant, taking loc cit literally}
@@
 We can compute intersection multiplicities by passing to dense constructible subsets.  By
-the isomorphisms of Prop.\ 5 and Lem.\ 8, $X(\tau) $ is dense constructible subset of $ Z(\tau) $ and $ X(\tau', \tau'')_{0,0} $ is a dense constructible subset of $ Z(\tau') \ast_0 Z(\tau'') $.  
+the isomorphisms of \Cref{lem:XtZt} and \Cref{pr:XttZtt}, $X(\tau) $ is a dense constructible subset of $ Z(\tau) $ and $ X(\tau', \tau'')_{0,0} $ is a dense constructible subset of $ Z(\tau') \ast_0 Z(\tau'') $.
+%  
+\acom{Hm, I guess you are right, it is easier than what I had, we just need that the arguments on either side match up, and not that the arguments on one side are related.
+Do we really not need that $X(\tau)$ is contained in $X(\tau',\tau'')_{0,0}$ as an irreducible component at any point?}
 \end{proof}
@@
     \begin{equation}
-        \iota(Z(\tau), Z(\tau') \circ Z(\tau'')) = 1 \,. 
+        \iota(Z(\tau), Z(\tau') \arfu Z(\tau'')) = 1 \,. 
     \end{equation}
@@
 % 
-There is a map from $\irr \overline{\Gr^\lambda\cap S^\mu_-} \to \CC[N]$ that factors through \acom{??} $\overline{S^0_+\cap S^\nu_-}$ for $\nu = \lambda - \mu$.
-The irreducible components of $ \overline{S^0_+\cap S^\nu_-}$ are called \new{stable MV cycles} and there is a bijection given by multiplication by $t^\lambda$ from $\{Z\in \irr \overline{S^0_+\cap S^\nu_-} : t^\lambda Z \subset\overline\Gr^\lambda\}$ to $\irr \overline{\Gr^\lambda\cap S^\mu_-} $.
+The coordinate ring of the unipotent subgroup of upper-triangular matrices with 1s on the diagonal has a $\CC$-basis coming from MV cycles.
+It also has a $\CC$-basis of cluster monomials which is conjectured to be contained in the former.
+\acom{is this right?
+Can two bases of an infinite dimensional vector space be related by proper containment?} In his thesis, the first author uses the fusion construction to check that certain MV cycles are cluster.
+
+We begin by recalling how the MV cycles yield a basis of $\CC[N]$.
+First note that with respect to the adjoint action of $T$ on $N$, the ring of functions on $N$ is graded by the set $-Q_+$ of nonpositive integer linear combinations positive roots.
+% In particular, for any $\nu \in Q_+$ and $\mu$ dominant effective, $\nu + \mu$ is effective dominant?
+% 
+Now, there is a map 
+$$
+    \Psi_\lambda: \irr \overline{\Gr^\lambda\cap S^\mu_-} \to \CC[N]_{\mu - \lambda}
+$$ 
+that factors through $\overline{S^0_+\cap S^\nu_-}$ for $\nu = \lambda - \mu$ in the sense that for any $\lambda',\mu'$ such that $\lambda' - \mu' = \lambda - \mu$, the irreducible components of $\Gr^\lambda\cap S^\mu$ are in bijection with those of $\Gr^{\lambda'}\cap S^{\mu'}_-$ according to their Lusztig data, and if $Z,Z'$ are two such matching components, then $\Psi_\lambda(Z) = \Psi_{\lambda'}(Z')$.
+% 
+In other words, the irreducible components of $ \overline{S^0_+\cap S^\nu_-}$ are called \new{stable MV cycles} and there is a bijection given by multiplication by $t^\lambda$ from $\{Z\in \irr \overline{S^0_+\cap S^\nu_-} : t^\lambda Z \subset\overline\Gr^\lambda\}$ to $\irr \overline{\Gr^\lambda\cap S^\mu_-} $.
 Moreover, the induced map on $\cup L(\lambda)\to\CC[N]$ is not injective, while that on the collection of all stable MV cycles ($\oplus L(0)_\nu\to\CC[N]$) is.

### 2021-05-30 draft.tex

@@
 \acom{is this right?
-Can two bases of an infinite dimensional vector space be related by proper containment?} In his thesis, the first author uses the fusion construction to check that certain MV cycles are cluster.
+Can two bases of an infinite dimensional vector space be related by proper containment?} \rcom{I believe the cluster monomials don't always form a basis.} In his thesis, the first author uses the fusion construction to check that certain MV cycles are cluster.
 

### 2021-05-31 draft.tex
Comments on 6.3. New format for examples applied to Example 3.

--- 2021-05-29 draft.tex
@@
 \usepackage{emoji}
+\usepackage{float}
 % TODO: The matrix is lower triangular and the lower-triangular matrix is
@@
 % 
-% The \textbf{dominant coweights} of $ G $ are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) \in \ZZ^m $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
-% 
-% A coweight $ \mu = (\mu_1, \dots, \mu_m) \in \ZZ^m$ is called \textbf{effective} if $ \mu_j \ge 0 $ for all $ j$.
+% The \new{dominant coweights} of $ G $ are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) \in \ZZ^m $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
+% 
+% A coweight $ \mu = (\mu_1, \dots, \mu_m) \in \ZZ^m$ is called \new{effective} if $ \mu_j \ge 0 $ for all $ j$.
 % 
@@
 % \acom{left or right, doesn't matter? I think we are in a situation where they are the same, i.e.\ our rings are commutative.} 
-By restriction $ K^m$ can be viewed as an $R$-module.  An \textbf{$R$-lattice} in $K^m$ 
+By restriction $ K^m$ can be viewed as an $R$-module.  An \new{$R$-lattice} in $K^m$ 
 % \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
@@
 % \acom{Wait, I thought $\CC(t)$ is used in the Ran space version of the BD Gr.}
-Given such a lattice $ L $ and a point $ a \in \CC$, the \textbf{specialization} of $ L $ at $ a $ is the lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $. 
-If $L(a) = \cO_a^m$ then $L$ is said to be \textbf{trivial at $a$}. 
+Given such a lattice $ L $ and a point $ a \in \CC$, the \new{specialization} of $ L $ at $ a $ is the lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $. 
+If $L(a) = \cO_a^m$ then $L$ is said to be \new{trivial at $a$}. 
 % We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
@@
 \label{def:gr}
-     The \textbf{ordinary affine Grassmannian} $\Gr = G(\cK)/G(\cO)$.
+     The \new{ordinary affine Grassmannian} $\Gr = G(\cK)/G(\cO)$.
 \end{definition}    
@@
  For any $ s \in \CC $, 
-    the \textbf{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ \textbf{at} $ s $. 
+    the \new{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ \new{at} $ s $. 
 \end{definition}    
@@
 \label{def:grth}
-The \textbf{thick affine Grassmannian} $\Grth = G(\Kinf)/G(\CC[t])$.
+The \new{thick affine Grassmannian} $\Grth = G(\Kinf)/G(\CC[t])$.
 \end{definition}
@@
 \label{def:bdgr}
-The two point \textbf{Beilinson--Drinfeld Grassmannian} $$\pi : \Grbd\to \AA$$ with one point fixed at 0, and the second point $s\in\AA$ varying.
+The two point \new{Beilinson--Drinfeld Grassmannian} $$\pi : \Grbd\to \AA$$ with one point fixed at 0, and the second point $s\in\AA$ varying.
 \end{definition}
@@
 \label{def:grplus}
-The \textbf{positive part} of $\Gr $, resp.\ $\Grth$, is defined by 
+The \new{positive part} of $\Gr $, resp.\ $\Grth$, is defined by 
 \begin{gather*}
@@
 The fibre $ X_1 \ast_0 X_2$ of $ X_1 \ast_{\AA} X_2 $ over $0$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
-We call this subscheme the \textbf{fusion} of $ X_1 $ and $ X_2$.
+We call this subscheme the \new{fusion} of $ X_1 $ and $ X_2$.
 
@@
 % \end{equation*}
-% which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  
+% which we call the \new{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  
 % 
@@
 \label{def:sphschub}
-    The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
+    The \new{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
     $ \overline\Gr^\lambda = \bigcup_{\gamma \le \lambda} \Gr^{\gamma} $ 
-    a \textbf{spherical Schubert variety}.  
+    a \new{spherical Schubert variety}.  
 \end{definition}
@@
 \label{def:sphfus}
-    The \textbf{BD family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.
+    The \new{BD family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.
     % $$ 
@@
 \label{def:klslice}
-    The \textbf{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
+    The \new{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
 \end{definition}
@@
 \label{def:inftyorbits}
-    The \textbf{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $ and the \textbf{family of two semi-infinite orbits} 
+    The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $ and the \new{family of two semi-infinite orbits} 
  $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
@@
 % \begin{definition}
-Recall that $\mu=(\mu_1,\dots,\mu_m)$ is a partition of $N$. The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is the affine space of $N\times N$ matrices of the form
+Recall that $\mu=(\mu_1,\dots,\mu_m)$ is a partition of $N$. The \new{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is the affine space of $N\times N$ matrices of the form
 % defined as the set of $A\in M_N(\CC)$ such that 
@@
 In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.
-\begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
+\begin{definition} The ``\new{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
 $$
@@
 \end{corollary}
-%The closures of the irreducible components of the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}.
-By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \textbf{perfect basis} of $\CC[N]$.
+%The closures of the irreducible components of the righthand side are \new{MV cycles of type $\lambda$ and weight $\mu$}.
+By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \new{perfect basis} of $\CC[N]$.
 
@@
 \subsection{MV cycles}
+Let $\lambda\ge\mu$ be dominant effective and effective coweights of $\GL_m$ respectively. 
 % 
@@
 \begin{definition}
-An irreducible component of $\overline{\Gr}^\lambda \cap S^\mu$ is called an \textbf{Mirkovic--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$.
+An irreducible component of $\overline{\Gr}^\lambda \cap S^\mu$ is called an \new{Mirkovic--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$.
 \end{definition}
 
-\jcom{In this section, I think that $ \mu$ is not necessarily dominant.  So I think that we should we recall our previous notation, but say that $ \mu $ might not be dominant here.}
-\acom{Ok.}
-
-By \cite{mirkovic2007geometric}, all these irreducible components have dimension $ \rho(\lambda - \mu)$, where $ \rho = (m, m-1, \dots, 1)$.
+% \jcom{In this section, I think that $ \mu$ is not necessarily dominant.  So I think that we should we recall our previous notation, but say that $ \mu $ might not be dominant here.}
+% \acom{Ok.}
+
+By \cite[Theorem~3.2(b)]{mirkovic2007geometric}, each MV cycle has in $\overline\Gr^\lambda$ of coweight $\mu$ has dimension $ \rho(\lambda - \mu)$ where $\rho$ is the half sum of positive roots.
+Normalizing $ \rho = (m, m-1, \dots, 1)$ and identifying $P \cong P^\vee$ the pairing $P\times P^\vee\to\ZZ $ is given by the ordinary dot product.
 
@@
 Denote by $[a,b]$ the interval $\{a,a+1,\dots,b-1,b\}\subset\NN$. 
-% If $a = 1$ just write $[b]$, and if $a = b$ just write $\{a\}$. 
-% If a = b? Just write $\{b\}$
-% \jcom{Maybe we should write $[1,b] $ instead of $ [b]$.  It looks a little confusing below to have $ [i+1, m]$ and $[i]$.}
-% 10-4
-
+% 
 We begin with the following definitions.
@@
 We will also need the analogous definitions when $ \cO$ is replaced by $ \CC[t]$ and $L \in \Grth_+$. 
-
+% 
 We record the following easy observations.
-\begin{lemma} \label{le:rdimTrans} Let $ L \in \Gr_+$.
+\begin{lemma} \label{le:rdimTrans} Let $ L \in \Gr_+$ \acom{(or $\Grth_+$)}.
 \begin{enumerate}
@@
 
-For any $ L \in \Gr_+ $ and $\gamma \subset [m]$, we let $ D_\gamma(L) := \rdim L^\gamma = \rdim L - \rdim L_{\gamma^c}$.
-By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.
+For any $ L \in \Gr_+ $ \acom{(or $\Grth_+$)} and $\gamma \subset [m]$, we define $ D_\gamma(L) := \rdim L^\gamma = \rdim L - \rdim L_{\gamma^c}$.
+(By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.)
 % \acom{We should introduce $D_\gamma$ briefly.}
@@
 
-In this section only, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (with a subscript), because we will also need the opposite semi-infinite cell $S^\mu_+ := N(\cK)t^\mu$.
+In this section only, \acom{possibly also the next} we will write $ S^\mu_- = N_-(\cK) t^\mu$ (with a subscript), because we will also need the opposite semi-infinite cell $S^\mu_+ := N(\cK)t^\mu$.
 %\acom{HB, ``..we will write.., because we will need the opposite cell..''}
@@
 
-The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
-\acom{For Joel: weight or filling? See below.}
+The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \new{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
+\acom{For Joel: weight or filling? See line below.}
 $$
@@
 
-From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ \mathring Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.
-In particular it is irreducible.
+From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ \mathring Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in Sect.\ 4.3 of \cite{kamnitzer2010mirkovic}.
+In particular, it is irreducible.
 Thus, its closure is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
-(In \cite{kamnitzer2010mirkovic}, the third author worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using the map $ G(\cO) g \mapsto g^{-1} G(\cO)$.)
+(The reader is warned that in \cite{kamnitzer2010mirkovic} the third author worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using the map $ G(\cO) g \mapsto g^{-1} G(\cO)$.)
 % \acom{Maybe we should avoid using square brackets as we haven't used them yet?}
-
-Now, by the results of \cite{kamnitzerfibreshives} (see especially the proof of Theorem 1.4), we note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$.
+% 
+Now, by results of \cite{kamnitzer2008hives}, (see especially the proof of Theorem 1.4,) we note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$. 
+% Explanation: 
+% MV polytopes giving tensor product multiplicity of V(\nu) in
+% V(\lambda) \otimes V(\mu)
+% with
+% Hives with bdy \lambda, \mu, \nu.
+% 
+% If we take \mu and \nu to be sufficiently large compared to \lambda,
+% then this becomes a bijection
+% MV polytopes for the weight multiplicity V(\lambda)_{\nu - \mu}
+% with
+% Young tableaux YT(\lambda)_{\nu - \mu}
+% 
+% Even better, in that paper, I worked geometrically, and I gave a
+% bijection from components of the fibre of the convolution morphism to
+% hives.  Again, taking \mu, \nu large compared to \lambda, this fibre
+% of the convolution morphism becomes Gr^\lambda \cap S^{\nu - \mu}.  So
+% that paper actually does give a bijection from components of
+% Gr^\lambda \cap S^{\nu - \mu} to tableaux.
 
@@
 \]
-\jcom{Maybe for consistency, we should write $ \n \cap \TT_\mu$ (opposite order).}
 
@@
 \end{lemma}
-\jcom{We should add a proof here.  It will be very similar to Prop 5 below.}
-
-By \cite{dthesis}, $ \mathring X(\tau) $ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.
+\jcom{We should add a proof here.  It will be very similar to Prop 5 below.} \acom{Ca marche?}
+\jcom{Oui.  J'ai fait des petites revisions.}
+\begin{proof}
+Fix $A\in\mathring X(\tau)$ and $i\in\{1,\dots,m\}$.
+Let $\cO^i\subset\cO^m$ denote the submodule generated by the first $i$ standard basis vectors.
+Let $l = g(A\big|_{\CC^{\lvert\mu(i)\rvert}}) \cO^i$ and $L = g(A) \cO^m$.
+By definition of the map $A \mapsto g(A)$, since $ A $ is upper-triangular we have that $l = L_{[1,i]}$.
+Moreover, since elements of $\TT_\mu\cap\n$ are upper triangular $A\big|_{\CC^{\lvert\mu(i)\rvert}}\in\TT_{\mu(i)}\cap\n_i$ where $\n_i$ denotes the subalgebra of upper-triangular matrices in $M_{\lvert\mu(i)\rvert}(\CC)$.
+By definition of $\mathring X(\tau)$ this principal submatrix has Jordan type $\lambda(i)$.
+It follows that $l = L_{[1,i]} \in \Gr^{\lambda(i)} \cap S^{\mu(i)}$ for each $i=1,\dots,m$ so that $L\in\mathring Z(\tau)$.
+
+Conversely, let $ L \in \mathring Z(\tau) $.  By \Cref{cor:mvy}, $ L = g(A)$ for some $ A \in \TT_\mu \cap \n $.  Running the above argument in reverse, we see that $ A \in \mathring X(\tau)$. 
+\end{proof}
+
+By \cite[Prop.\ 4.5.4]{dthesis}, $ \mathring X(\tau) $ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.
 We write $ X(\tau)$ for the closure of this component.
-It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu$ and will be called a \textbf{generalized orbital variety}.
-
-\jcom{We should give a more specific citation to \cite{drthesis} here and below.
+It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu \cap \n$ and will be called a \new{generalized orbital variety}.
+
+\jcom{We should give a more specific citation to \cite{dthesis} here and below.
 Also, throughout this paper, we should either cite your paper or your thesis, but not both (unless there is a very good reason to do so).
@@
 Feel free to add a bit more exposition.}
-
-In fact, these are all the generalized orbital varieties by  \cite{dthesis}. 
-\begin{theorem}
+\acom{Just posted to arXiv. Will re-ref shortly. Also made citation more specific.}
+
+In fact, these are all the generalized orbital varieties:
+\begin{theorem}(\cite[Theorem~4.8.2]{dthesis})
     \label{pr:govsasirrecs}
@@
 % 
-Our goal is to describe the fusion of two MV cycles using fusion of generalized orbital varieties, which we will now define. 
-% 
-Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as in previous sections.
-\jcom{I think that this is can move earlier, with the caveat that I mentioned earlier about $ \mu $ being non-dominant in 6.1 and dominant here.}
+Our goal is to describe the fusion of two MV cycles using ``fusion'' of generalized orbital varieties, which we will now define. 
+% \acom{So we \textit{are} calling this a fusion?} \jcom{I think that you used this word already here.  I just reorganized your sentence.} \acom{I agree, but I thought that you were opposed, Joel.}
+% 
+Let $\lambda',\lambda''$ be dominant effective and $\mu',\mu''$ effective such that $\lambda = \lambda' + \lambda''$ and $\mu = \mu' + \mu''$ as in previous sections.
+\jcom{I think that this is can move earlier, with the caveat that I mentioned earlier about $ \mu $ being non-dominant in 6.1 and dominant here.} \acom{Yes.} \acom{But we only start to need the primes now.}
 
@@
 % 
-Fix $A\in \mathring X(\tau',\tau'')_{0,s} $ and $i = 1,\dots, m$. 
+Fix $A\in \mathring X(\tau',\tau'')_{0,s} $ and $i \in \{1,\dots, m\}$. 
 % 
@@
 
-The lattices $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ and $L=g(A)\CC[t]^m$ are related by the equality $ l = L_{[1,i]}$ where recall $L_{[1,i]} = (L + \CC[t]^{[i+1,m]}) / \CC[t]^{[i+1,m]}\subset \CC[t]^m/\CC[t]^{[i+1,m]} = \CC[t]^i$.
-
-By definition of $\UU^{\mu',\mu''}_{0,\AA}$ we have $A\big|_{\CC^{|\mu(i)|}}\in\UU^{\mu'(i),\mu''(i)}_{0,s}$ and by definition of $X(\tau',\tau'')_{0,s}$, the Jordan type of $A\big|_{\CC^{|\mu(i)|}}$ is $((\lambda'(i),0),(\lambda''(i),s))$.
+The lattices $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ and $L=g(A)\CC[t]^m$ are related by the equation $ l = L_{[1,i]}$ where recall $L_{[1,i]} = (L + \CC[t]^{[i+1,m]}) / \CC[t]^{[i+1,m]}\subset \CC[t]^m/\CC[t]^{[i+1,m]} = \CC[t]^i$.
+
+By definition of $\UU^{\mu',\mu''}_{0,\AA}$ we have $A\big|_{\CC^{|\mu(i)|}}\in\UU^{\mu'(i),\mu''(i)}_{0,s}$ and by definition of $\mathring X(\tau',\tau'')_{0,s}$, the Jordan type of $A\big|_{\CC^{|\mu(i)|}}$ is $((\lambda'(i),0),(\lambda''(i),s))$.
 So, $l \in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$ by \Cref{th:OTGrW}.
@@
 \acom{Hm, I guess you are right, it is easier than what I had, we just need that the arguments on either side match up, and not that the arguments on one side are related.
-Do we really not need that $X(\tau)$ is contained in $X(\tau',\tau'')_{0,0}$ as an irreducible component at any point?}
+Though do we really not use that $X(\tau)$ may be contained in $X(\tau',\tau'')_{0,0}$ as an irreducible component?}
 \end{proof}
@@
 \subsection{Connection to cluster structure on $\CC[N]$}
-% 
-The coordinate ring of the unipotent subgroup of upper-triangular matrices with 1s on the diagonal has a $\CC$-basis coming from MV cycles.
-It also has a $\CC$-basis of cluster monomials which is conjectured to be contained in the former.
-\acom{is this right?
-Can two bases of an infinite dimensional vector space be related by proper containment?} In his thesis, the first author uses the fusion construction to check that certain MV cycles are cluster.
-
-We begin by recalling how the MV cycles yield a basis of $\CC[N]$.
-First note that with respect to the adjoint action of $T$ on $N$, the ring of functions on $N$ is graded by the set $-Q_+$ of nonpositive integer linear combinations positive roots.
-% In particular, for any $\nu \in Q_+$ and $\mu$ dominant effective, $\nu + \mu$ is effective dominant?
+\jcom{Maybe we need a word about Langlands duality here.
+Since we are working with $ GL_m$, it is not really necessary, but it would be nice to point this out.
+Also a general comment: maybe it would be best to first talk about multiplication in $\CC[N]$ incl.
+Theorem 7.11 from mvbasis, and then talk about cluster algebras.
+Right now, it is a bit confusing, since we go back and forth.
+Also some of the motivation stuff about the semicanonical basis, etc, will be moved to the intro.}
+\acom{To quote from BFZ for a concise definition: Cluster algebras are a class of commutative rings defined axiomatically in terms of a distinguished family of generators called cluster variables.}
+The coordinate ring of the unipotent subgroup of upper-triangular matrices with 1s on the diagonal is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}.
+
+One of the main motivations for this paper is computing fusion products that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
+
+In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
+This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
+Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
+
+In \cite{baumann2019mirkovic} the third author along with Baumann and Knutson show that the MV cycles yield another geometric basis of $\CC[N]$, called the MV basis.
+% 
+First note that with respect to the adjoint action of $T$ on $N$, $\CC[N]$ is graded by the set $-Q_+$ of nonpositive integer linear combinations of positive roots. 
 % 
@@
 that factors through $\overline{S^0_+\cap S^\nu_-}$ for $\nu = \lambda - \mu$ in the sense that for any $\lambda',\mu'$ such that $\lambda' - \mu' = \lambda - \mu$, the irreducible components of $\Gr^\lambda\cap S^\mu$ are in bijection with those of $\Gr^{\lambda'}\cap S^{\mu'}_-$ according to their Lusztig data, and if $Z,Z'$ are two such matching components, then $\Psi_\lambda(Z) = \Psi_{\lambda'}(Z')$.
-% 
-In other words, the irreducible components of $ \overline{S^0_+\cap S^\nu_-}$ are called \new{stable MV cycles} and there is a bijection given by multiplication by $t^\lambda$ from $\{Z\in \irr \overline{S^0_+\cap S^\nu_-} : t^\lambda Z \subset\overline\Gr^\lambda\}$ to $\irr \overline{\Gr^\lambda\cap S^\mu_-} $.
-Moreover, the induced map on $\cup L(\lambda)\to\CC[N]$ is not injective, while that on the collection of all stable MV cycles ($\oplus L(0)_\nu\to\CC[N]$) is.
-
-In \cite{baumann2019mirkovic}, Baumann, Knutson and the third author show that the stable MV cycles define a perfect basis of $\CC[N]$ whose structure constants are given by intersection multiplicities.
+
+\jcom{This paragraph is a bit confusing.
+Maybe it would be best to first define $ V(\lambda) \rightarrow \CC[N]$ and then $ H_{top}(\overline{Gr}^\lambda \cap S^\mu) \rightarrow \CC[N]$, rather than doing them in one step.
+Then we can draw a commutative square with $ S^0_+ \cap S_-^\nu$ as well.
+}
+% 
+In other words, there is a bijection given by multiplication by $t^\lambda$ from $\{Z\in \irr \overline{S^0_+\cap S^\nu_-} : t^\lambda Z \subset\overline\Gr^\lambda\}$ to $\irr \overline{\Gr^\lambda\cap S^\mu_-} $.
+(Note that the induced map on $\cup L(\lambda)\to\CC[N]$ is not injective.)
+% 
+The irreducible components of $ \cup_{\nu\in Q_+}\overline{S^0_+\cap S^{-\nu}_-}$ are called \new{stable MV cycles} and the \new{MV basis} of $\CC[N]$ is $\cup_{\nu\in Q_+}\{b_Z = \Psi_0(Z) \in \CC[N]_{-\nu}: Z \in \irr \overline{S^0_+\cap S^{-\nu}_-} \}$.
+Moreover, the structure constants of the MV basis are given by intersection multiplicities with multiplication in $\CC[N]$ corresponding to fusion in $\Gr$.
 %
@@
 \begin{theorem}
-    (\cite[Theorem~7.11]{baumann2019mirkovic})
+    (\cite[Theorem~7.11]{baumann2019mirkovic}) \acom{We haven't said how to fuse stable MV cycles..}
 $$
@@
 \end{theorem}
-
-\jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
-\acom{Begun}
-
+\jcom{In principle, the notation $ Z' \ast_0 Z''$ has been defined, since we defined the fusion of any two subschemes of $ \Gr$.
+We should just note that the fusion of the stable MV cycles matches the fusion of MV cycles after translation by $ t^\lambda$.
+I don't think that $ \iota$ has been defined anywhere, has it?}
+
+In the appendix to \cite{baumann2019mirkovic} the second and third author along with Morton-Ferguson check that the MV basis differs from the dual semicanonical basis (at the Kashiwara--Saito counterexample).
+Yet, the two bases have enough in common (c.f.\ BKT,...?), that we have the following conjecture.
+
+\begin{conjecture}
+    The dual semicanonical basis and the MV basis overlap on the cluster monomials. In particular, the cluster monomials are contained in the MV basis. 
+\end{conjecture}
+
+\acom{Which cluster monomials? The ones considered by GLS corresp to certain modules? iiuc they are interchangeable, but it is helpful to anchor one. Roger? Joel? Feel free to reword.} 
+\rcom{I don't understand the question. There is only one set of cluster monomials in $\CC[N]$.}
+
+We note that both of these bases are \new{biperfect} bases of $\CC[N]$ and in type $A_n$ with $n\le 3$ there is a unique biperfect basis of $\CC[N]$.
+
+For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor, and hence \acom{by BKK?}\rcom{I reworded it.} is in the MV basis \cite{kato2011polytopal}.
+% as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
+\acom{what's the subscript $r$?
+also what're the last 2 citations for?
+Neither BFZ nor GLS link generalized minors and MV cycles}
+If the reduced expression satisfies a special condition, then cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
+
+Conversely, suppose we have a seed $(x_1,\dots,x_r)$ such that each $x_i$ is in the MV basis, i.e.\ for each $i$ there exists a stable MV cycle $Z_i$ such that $x_i = b_{Z_i}\in\CC[N]$.
+To show that all cluster variables \acom{for this seed?}\rcom{No, all of them.} are also in the MV basis it suffices to show that if $x_i$ is mutable then its mutation $x_i^*$ is also in the MV basis.
+This observation is based on the exchange relation:
+\[
+    x_i x_i^* = x_+ + x_- 
+\]
+where $x_+,x_-$ are monomials in $ (x_1, \dots, x_r)\setminus x_i$ determined by the cluster structure on $\CC[N]$.
+\acom{the structure of interest?
+or are all cluster structures on this ring the same?} \rcom{The structure is derived from an initial seed coming from a reduced word {\bf i}.
+Each of these are equivalent to each other.}
+So if we can find a stable MV cycle $Z_i^*$ such that $b_{Z_i}b_{Z_i^*} = x_+ + x_-$ for each $i$ then we will have checked the conjecture.
+\acom{And we do not need to assume the special condition of BGL?}\rcom{They deal with cluster monomials in certain clusters while this deals with all cluster variables, so neither one completely implies the other.}
+% \acom{Roger says that $x_i x_i^* = \sum{b_{ij} > 0} x_j + \sum{b_{ij} < 0} x_j$ Do we have a recursion? Explicit candidates for $x_\pm$ starting with $Z_1$}
+
+The following examples give evidence that the mutation $x_i^*$ is in the MV basis. \acom{Roger, reword?}\rcom{Something like this?}
+
+% \jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
+% \acom{Begun}
+
+Before we begin we will need some lemmas, notions and notations. 
+\begin{itemize}
+    \item we have only seen how to fuse ordinary MV cycles; to mutliply MV basis vectors which are indexed by stable MV cycles we'll therefore need a way to represent stable by ordinary; hence:
+    \item a notion/choice of fission 
+    \item the fission lemmas 
+    \item with lemmas in hand, a proposition: given $Z',Z''$ stable with LD... there exist $\tau',\tau''$ (min) such that $b_{Z'} b_{Z''} = b(\tau')  b(\tau'')$
+    \item a shorthand: in examples, instead of writing $Z(\tau)$ for the MV cycle corresponding to the tableau $\tau$ we will only the tableau $\tau$! 
+\end{itemize}
 \begin{lemma}
@@
 % 
-\section{Cluster Algebras}
-One of the main motivations for this paper is computing certain fusion products that are associated to exchange relations in the cluster algebra structure of $\CC[N]$.
-
-A basis of $\CC[N]$, called the dual semicanonical basis, was originally constructed in \cite{lusztig2000semicanonical} while a cluster algebra structure for $\CC[N]$ was shown in \cite{berenstein2005cluster3} and \cite{geiss2007initial}.
-A natural question was whether the cluster monomials were elements of the dual semicanonical basis, proved in the positive in \cite{geiss2006rigid}.
-
-Another basis for $\CC[N]$ was constructed in \cite{mirkovic2007geometric} called the MV basis.
+% \section{Cluster Algebras}
+% One of the main motivations for this paper is computing certain fusion products that are associated to exchange relations in the cluster algebra structure of $\CC[N]$. 
+% 
+% A basis of $\CC[N]$, called the dual semicanonical basis, was originally constructed in \cite{lusztig2000semicanonical} while a cluster algebra structure for $\CC[N]$ was shown in \cite{berenstein2005cluster3} and \cite{geiss2007initial}.
+% A natural question was whether the cluster monomials were elements of the dual semicanonical basis, proved in the positive in \cite{geiss2006rigid}.
+
+% Another basis for $\CC[N]$ was constructed in \cite{mirkovic2007geometric} called the MV basis.
 This basis is indexed by the MV cycles and the product of basis elements corresponds to the fusion product of the associated MV cycles.
@@
 
-\begin{conjecture}\label{conj:cluster in MV}
-    The cluster monomials of $\CC[N]$ are elements of the MV basis.
-\end{conjecture}
-
-Conjecture \ref{conj:cluster in MV} is known for type $A_n$, $n \leq 3$, as in this case, there is a unique biperfect basis for $\CC[N]$ \cite{baumann2019mirkovic}, so the dual semicanonical basis and MV basis are the same.
-
-It has been shown in \cite{kato2011polytopal} that for initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word in the Weyl group for $G$, each $x_i$ is in the MV basis as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
+% \begin{conjecture}\label{conj:cluster in MV}
+%     The cluster monomials of $\CC[N]$ are elements of the MV basis.
+% \end{conjecture}
+
+% Conjecture \ref{conj:cluster in MV} is known for type $A_n$, $n \leq 3$, as in this case, there is a unique biperfect basis for $\CC[N]$ \cite{baumann2019mirkovic}, so the dual semicanonical basis and MV basis are the same.
+
+% It has been shown in \cite{kato2011polytopal} that for initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word in the Weyl group for $G$, each $x_i$ is in the MV basis as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
 If the reduced expression satisfies a special condition, then the cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
 
-Suppose we have a seed $(x_1, \dots, x_r)$ where each $x_i$ is already in the MV basis.
+% Suppose we have a seed $(x_1, \dots, x_r)$ where each $x_i$ is already in the MV basis.
 To show all the other cluster variables are in the MV basis, it suffices to show that for a mutable variable $x_i$, its mutation $x_i^*$ is also in the MV basis.
 The exchange relation corresponding to $x_i$ and $x_i^*$ is of the form
-$$x_ix_i^* = x_+ + x_-$$
-where $x_+$ and $x_-$ are monomials in the $x_j,j\neq i$. Let $Z_i$ be the MV cycle corresponding to $x_i$, so $x_i = b_{Z_i}$. If we are able to find an MV cycle $Z_i^*$ such that
-$$b_{Z_i} b_{Z_i^*} = x_+ + x_-,$$
-then this means $x_i^* = b_{Z_i^*}$ so it is in the MV basis with associated MV cycle $Z_i^*$. In Section \ref{s:denouement}, we present examples showcasing this is indeed true for type $A_3$. 
+% $$x_ix_i^* = x_+ + x_-$$
+% where $x_+$ and $x_-$ are monomials in the $x_j,j\neq i$. Let $Z_i$ be the MV cycle corresponding to $x_i$, so $x_i = b_{Z_i}$. If we are able to find an MV cycle $Z_i^*$ such that
+% $$b_{Z_i} b_{Z_i^*} = x_+ + x_-,$$
+% then this means $x_i^* = b_{Z_i^*}$ so it is in the MV basis with associated MV cycle $Z_i^*$. In Section \ref{s:denouement}, we present examples showcasing this is indeed true for type $A_3$.
+
 \section{Denouement}
@@
 % \acom{Plus fusion product of fake MV cycles for a fourth!}
-
+\acom{TODO: review/rewrite now that we have \S 6.2}
 We view MV cycles as semi-standard young tableaux.
@@
 $$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s]}{\langle A_{12}^1+sA_{12}^2, A_{12}^2A_{23}^1+sA_{13}^1, A_{12}^1A_{23}^1+s^2A_{13}^1, s\rangle} \cong \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,b_3,s]}{\langle A_{12}^1, A_{12}^2\rangle \cap \langle A_{12}^1, A_{23}^1 \rangle}.$$
+\acom{TODO: put ideals of $\arfu$ and their tableaux into tables; also divide into 2 sections, $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with `rising action'?}
 We see that the 0-fibre is reducible with two components. The tableau corresponding to each ideal is
@@
 
-    \acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{mirkovic2007quiver}.}
+    \acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{claxton2015young}}
 
@@
 
-Let $G = \GL_4$. There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables. We list the corresponding tableaux, coordinate ring of the MV cycle, and Lusztig-datum below:
-
-\jcom{This is a nice table.  But these are the coordinate rings of $ X(\tau)$, not of $ Z(\tau) $.}
-
-\[
-\begin{array}{ccc} 
-\tau & \text{Coordinate ring of }Z(\tau) & \text{Lusztig-datum} \\ \hline
+Let $G = \GL_4$.
+There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables.
+We list the corresponding tableaux, coordinate ring of the generalized orbital variety $X(\tau)$, and Lusztig-datum below:
+
+% \jcom{This is a nice table.  But these are the coordinate rings of $ X(\tau)$, not of $ Z(\tau) $.}
+% \renewcommand{\arraystretch}{1.5}
+\begin{table}[ht!]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \tau & \text{Coordinate ring of }X(\tau) & \text{Lusztig-datum} \\
+    \midrule 
 \young(2) & \CC[A_{12}^1] & (1,0,0,0,0,0) \rule{0pt}{3ex}\\
@@
 \young(4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle} & (1,0,0,1,0,1) \TS\BS\\
-\end{array}
-\]
+  \end{tabular}
+\end{table}
+
+% \[
+% \begin{array}{ccc} 
+% \tau & \text{Coordinate ring of }X(\tau) & \text{Lusztig-datum} \\ \hline
+% \young(2) & \CC[A_{12}^1] & (1,0,0,0,0,0) \rule{0pt}{3ex}\\
+% \young(1,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1,A_{13}^1 \rangle} & (0,0,0,1,0,0) \TS\BS\\
+% \young(1,2,4) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 \rangle} & (0,0,0,0,0,1) \TS\BS\\
+% \young(3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1 \rangle} & (1,0,0,1,0,0) \TS\BS\\
+% \young(2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{23}^1 \rangle} & (0,1,0,0,0,0) \TS\BS\\
+% \young(1,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 \rangle} & (0,0,0,1,0,1) \TS\BS\\
+% \young(1,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 \rangle} & (0,0,0,0,1,0) \TS\BS\\
+% \young(2,4) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 \rangle} & (0,1,0,0,0,1) \TS\BS\\
+% \young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 \rangle} & (1,0,0,0,1,0) \TS\BS\\
+% \young(2,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{23}^1,A_{24}^1,A_{34}^1 \rangle} & (0,0,1,0,0,0) \TS\BS\\
+% \young(3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1 \rangle} & (0,1,0,0,1,0) \TS\BS\\
+% \young(4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle} & (1,0,0,1,0,1) \TS\BS\\
+% \end{array}
+% \]
 
@@
 \begin{example}
-Consider the product $Z_1 * Z_2$, so the tableaux are
-\[
-\young(2) \text{ and } \young(1,3).
-\]
+% Consider the product $Z_1 * Z_2$, so the tableaux are
+Consider the product % $Z({{\scriptsize\young(2)}})*Z({\scriptsize\young(1,3)})$
+% \[
+% \young(2) \text{ and } \young(1,3).
+% \]
+$\young(2) * \young(1,3)$.
 Our matrix is
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_3 & A_{12}^1A_{23}^1+sA_{13}^1
-\end{array}.
-\]
-Hence our ideal is
-$$\langle A_{12}^1A_{23}^1+sA_{13}^1,s \rangle = 
-\langle A_{12}^1,s \rangle \cap \langle A_{23}^1,s \rangle.$$
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,s \rangle &\leadsto \young(13,2) &\equiv \young(3) &\leadsto {Z_{1 \leftarrow 2}} \\ 
-    \langle A_{23}^1,s \rangle &\leadsto \young(12,3) &\equiv \young(2,3) &\leadsto{Z_{1 \rightarrow 2}}
-\end{array}
-\]
-so $Z_1 * Z_2 = Z_{1 \leftarrow 2} + Z_{1 \rightarrow 2}$.
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_3 & A_{12}^1A_{23}^1+sA_{13}^1
+% \end{array}.
+% \]
+\noindent Hence, our ideals are
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Ideal} & \text{Tableau} \\
+    \midrule 
+    \langle A_{12}^1,s \rangle & \young(13,2) \equiv \young(3) \\
+    \langle A_{23}^1,s \rangle & \young(12,3) \equiv \young(2,3)
+    \end{tabular}
+\end{table}
+% $$\langle A_{12}^1A_{23}^1+sA_{13}^1,s \rangle = 
+% \langle A_{12}^1,s \rangle \cap \langle A_{23}^1,s \rangle.$$
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,s \rangle &\leadsto \young(13,2) &\equiv \young(3) &\leadsto {Z_{1 \leftarrow 2}} \\ 
+%     \langle A_{23}^1,s \rangle &\leadsto \young(12,3) &\equiv \young(2,3) &\leadsto{Z_{1 \rightarrow 2}}
+% \end{array}
+% \]
+% so $Z_1 * Z_2 = Z_{1 \leftarrow 2} + Z_{1 \rightarrow 2}$.
+\noindent so $\young(2) * \young(1,3) = \young(3) + \young(2,3)$.
 \end{example}
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_2 & A_{12}^1 \\
@@
     X_4 & A_{14}^1, A_{23}^1A_{34}^1 + sA_{24}^1
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1 \\
+%     X_3 & A_{13}^1 \\
+%     X_4 & A_{14}^1, A_{23}^1A_{34}^1 + sA_{24}^1
+% \end{array}.
+% \]
+% 
+\noindent Hence, our ideal decomposes into 
 \[
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
     X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
+%     X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
+% \end{array}.
+% \]
+\noindent Hence, our ideal decomposes into 
 \[
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_2 & A_{12}^1 + sA_{12}^2 \\
@@
     X_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1 + sA_{12}^2 \\
+%     X_3 & A_{13}^1, A_{23}^1 \\
+%     X_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
+% \end{array}.
+% \]
+\noindent Hence, our ideal decomposes into 
 \[
@@
     X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1 \\
+%     X_3 & A_{23}^1 \\
+%     X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
+% \end{array}.
+% \]
+\noindent Hence, our ideal decomposes into 
 \[
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_2 & A_{12}^1 \\
     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1 \\
+%     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
+% \end{array}.
+% \]
+\noindent Hence, our ideal decomposes into 
 \[
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_2 & A_{12}^1 \\
     X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
-\end{array}.
-\]
-Hence our ideal is 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1 \\
+%     X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
+% \end{array}.
+% \]
+\noindent Hence, our ideal is 
 \[
@@
 \]
+% 
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_2 & A_{12}^1 \\
@@
     X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1 \\
+%     X_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
+%     X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
+% \end{array}.
+% \]
+% 
+\noindent Hence, our ideal decomposes into 
 \[
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_2 & A_{12}^1, A_{12}^2 \\
@@
     X_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1, A_{12}^2 \\
+%     X_3 & A_{13}^1 \\
+%     X_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
+% \end{array}.
+% \]
+\noindent Hence, our ideal decomposes into 
 \[
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
     X_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
+%     X_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
+% \end{array}.
+% \]
+\noindent Hence, our ideal decomposes into 
 \[
@@
     X_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
-\end{array}.
-\]
-Hence our ideal decomposes into 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1 \\
+%     X_3 & A_{23}^1 +sA_{23}^2 \\
+%     X_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
+% \end{array}.
+% \]
+\noindent Hence, our ideal decomposes into 
 \[
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
      X_4 & A_{23}^1A_{34}^1 - sA_{24}^1
-\end{array}.
-\]
-Hence our ideal is 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1
+% \end{array}.
+% \]
+\noindent Hence, our ideal is 
 \[
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+% 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
     X_2 & A_{12}^1,A_{12}^2 \\
     X_3 & A_{13}^1, A_{23}^1 \\
-    X_4 & \begin{array}{c}
-         A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1,  \\
-         A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
-         A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2
-    \end{array}
-\end{array}.
-\]
+    X_4 & A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
+        & A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2 
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1,A_{12}^2 \\
+%     X_3 & A_{13}^1, A_{23}^1 \\
+%     X_4 & \begin{array}{c}
+%          A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1,  \\
+%          A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
+%          A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2
+%     \end{array}
+% \end{array}.
+% \]
 Hence our ideal decomposes into 
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
    X_2 & A_{12}^1 \\
     X_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
-    X_4 & \begin{array}{c}
+    X_4 & 
          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-         A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2,  \\
-         A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
-         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1 
-    \end{array} 
-\end{array}.
-\]
+        & A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2, A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
+        & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1 \\
+%     X_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
+%     X_4 & \begin{array}{c}
+%          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+%          A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2,  \\
+%          A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
+%          A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1 
+%     \end{array} 
+% \end{array}.
+% \]
 Hence our ideal decomposes into 
@@
 The relations from the submatrices are:
-\[
-\begin{array}{c|c}
-    \text{Submatrix} & \text{Relations} \\ \hline
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
    X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
     X_3 & A_{13}^1,A_{23}^1 \\
-    X_4 & \begin{array}{c}
-         A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-         A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
-         A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
-         A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
-         A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
-    \end{array} 
-\end{array}.
-\]
+    X_4 & A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+        & A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
+        & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
+        & A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
+        & A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
+    \end{tabular}
+\end{table}
+% \[
+% \begin{array}{c|c}
+%     \text{Submatrix} & \text{Relations} \\ \hline
+%     X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
+%     X_3 & A_{13}^1,A_{23}^1 \\
+%     X_4 & \begin{array}{c}
+%          A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+%          A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
+%          A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
+%          A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
+%          A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
+%     \end{array} 
+% \end{array}.
+% \]
 Hence our ideal decomposes into \acom{formatting funny; can just list irrecs?}

### 2021-06-02 draft.tex
GL_4 examples

@@
 Also some of the motivation stuff about the semicanonical basis, etc, will be moved to the intro.}
-\acom{To quote from BFZ for a concise definition: Cluster algebras are a class of commutative rings defined axiomatically in terms of a distinguished family of generators called cluster variables.}
-The coordinate ring of the unipotent subgroup of upper-triangular matrices with 1s on the diagonal is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}.
-
-One of the main motivations for this paper is computing fusion products that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
-
-In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
-This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
-Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
-
-In \cite{baumann2019mirkovic} the third author along with Baumann and Knutson show that the MV cycles yield another geometric basis of $\CC[N]$, called the MV basis.
-% 
-First note that with respect to the adjoint action of $T$ on $N$, $\CC[N]$ is graded by the set $-Q_+$ of nonpositive integer linear combinations of positive roots. 
-% 
-Now, there is a map 
-$$
-    \Psi_\lambda: \irr \overline{\Gr^\lambda\cap S^\mu_-} \to \CC[N]_{\mu - \lambda}
-$$ 
-that factors through $\overline{S^0_+\cap S^\nu_-}$ for $\nu = \lambda - \mu$ in the sense that for any $\lambda',\mu'$ such that $\lambda' - \mu' = \lambda - \mu$, the irreducible components of $\Gr^\lambda\cap S^\mu$ are in bijection with those of $\Gr^{\lambda'}\cap S^{\mu'}_-$ according to their Lusztig data, and if $Z,Z'$ are two such matching components, then $\Psi_\lambda(Z) = \Psi_{\lambda'}(Z')$.
-
+
+Let $N\subset\GL_m$ be the unipotent subgroup of upper-triangular matrices with 1s on the diagonal.
+In \cite{baumann2019mirkovic} the third author along with Baumann and Knutson show that the MV cycles yield a basis of the coordinate ring $\CC[N]$ called the MV basis.
+% 
+% First note that with respect to the adjoint action of $T$ on $N$, $\CC[N]$ is graded by the set $-Q_+$ of nonpositive integer linear combinations of positive roots. 
+%
+
+Given $\lambda\ge\mu\in\ZZ^m$ with $\lambda$ dominant, denote by $V(\lambda)$ the irreducible representation of $\GL_m$ of highest weight $\lambda$ and by $V(\lambda)_\mu$ its $\mu$-weight space. 
+There is an injective map $ \Psi_\lambda: V(\lambda) \to \CC[N]$ realizing $V(\lambda)$ as a subspace of $\CC[N]$.
+
+The geometric Satake correspondence says that 
+% $V(\lambda) = IH(\overline\Gr^\lambda)$ and  
+$V(\lambda)_\mu = H_{\rho(\lambda-\mu)}(\overline{\Gr^\lambda\cap S^\mu_-})$ where $H_d$ denotes $d$-dimensional Borel--Moore homology. 
+In particular, the MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$ give a basis of $V(\lambda)$. We denote this set of MV cycles $\cZ(\lambda)$. 
+%
+
+Let $Q_+$ denote the set of nonnegative integer combinations of positive roots. \acom{$Q_+$ should be defined earlier?}
+The \new{stable} MV cycles of coweight $\nu\in Q_+$ are defined to be irreducible components of $\overline{S^0_+ \cap S^\nu_-}$.
+By a theorem of Anderson, MV cycles in $\overline{\Gr^\lambda\cap S^{\nu + \lambda}_-}$ are in bijection with stable MV cycles of coweight $\nu$ that are contained in $\overline\Gr^\lambda$.
+We denote the set of all stable MV cycles $\cZ(\infty)$.
+
+\begin{theorem}
+    (BKK~Proposition 6.1)
+    For each $Z\in\cZ(\infty)$ there is a unique element $b_Z\in\CC[N]$ such that for any $\lambda$ dominant, if $t^\lambda Z\in\cZ(\lambda)$ then $\Psi_\lambda([t^\lambda Z]) = b_Z$ and the collection of all such elements is called the \new{MV basis}.
+\end{theorem}
+
+% Given $\epsilon\in\ZZ^m$ denote by $t^\epsilon:V(\lambda) \to V(\lambda + \epsilon)$ the map resulting from multiplication by the coweight $t^\epsilon$ in $\Gr$.
+By BKK, $\Psi_{\lambda + \epsilon} \circ t^\epsilon - \Psi_\lambda = 0$.
+
+% Together these facts imply the following commutative square.
+% \[
+% \begin{tikzcd}
+% L(\lambda) \ar[r] & \CC[N] \\
+% \Gr^\lambda \cap S^\mu_- \ar[r,"t^{-\lambda}"] \ar[u] & S^0 \cap S^{\mu - \lambda}_-\ar[u]
+% \end{tikzcd}
+% \]
 \jcom{This paragraph is a bit confusing.
@@
 }
-% 
-In other words, there is a bijection given by multiplication by $t^\lambda$ from $\{Z\in \irr \overline{S^0_+\cap S^\nu_-} : t^\lambda Z \subset\overline\Gr^\lambda\}$ to $\irr \overline{\Gr^\lambda\cap S^\mu_-} $.
-(Note that the induced map on $\cup L(\lambda)\to\CC[N]$ is not injective.)
-% 
-The irreducible components of $ \cup_{\nu\in Q_+}\overline{S^0_+\cap S^{-\nu}_-}$ are called \new{stable MV cycles} and the \new{MV basis} of $\CC[N]$ is $\cup_{\nu\in Q_+}\{b_Z = \Psi_0(Z) \in \CC[N]_{-\nu}: Z \in \irr \overline{S^0_+\cap S^{-\nu}_-} \}$.
-Moreover, the structure constants of the MV basis are given by intersection multiplicities with multiplication in $\CC[N]$ corresponding to fusion in $\Gr$.
+\acom{Not sure which square to draw or if it is necessary.
+I guess you want something like what's pictured below, where what we're about to describe are the blue arrows.
+Specifically the rightmost downward pointing blue.
+Which, by commutativity, will determine the middle downward pointing blue.}
+\[
+\begin{tikzcd}
+\CC[N] & \ar[l] \cZ(\infty) \ar[r,"n_\bullet"] \ar[d,bend left,blue] & \NN^{\Delta_+} \ar[l,blue,bend left] \ar[d,bend left,blue]\\ 
+L(\lambda) \ar[u,"\Psi_\lambda"] & \ar[l] \cZ(\lambda) \ar[r] \ar[u,"t^{-\lambda}"] & YT(\lambda) \ar[u,"n_\bullet"] \ar[l,blue,bend left]
+\end{tikzcd}
+\]
+% 
+\acom{Recalling intersection multiplicity:} 
+We have the zero fibre in $\Grbd$ as effective divisor $D$, and the fusion of subscheme $V = X\ast_\AA Y\subset\Grbd$ as a finite-dimensional irreducible variety not contained in the support of $D$, and finally an irreducible component $Z$ of $D\cdot V = X\ast_0 Y$, codimension 1 in $V$.
+Denote by $\iota(Z,D\cdot V)$ the intersection multiplicity of $Z$.
+% 
+The structure constants of $\CC[N]$ with respect to the MV basis are given by intersection multiplicities. 
 %
@@
 \begin{theorem}
-    (\cite[Theorem~7.11]{baumann2019mirkovic}) \acom{We haven't said how to fuse stable MV cycles..}
-$$
-b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} \iota\left(
-    Z, Z' \ast_0 Z''
-    % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
-\right) b_Z 
-$$
+    (\cite[Theorem~7.11]{baumann2019mirkovic}) Given $Z',Z''\in\cZ(\infty)$ 
+    % of coweight $\nu',\nu''$ respectively 
+$$
+b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)} \iota\left(Z, Z' \ast_0 Z''\right) b_Z 
+$$
+where note the summation is finite since... \acom{Don't want to introduce the notation $\cZ(\infty)_\nu$ if we can avoid it.}
+Moreover, there exists $\lambda',\lambda''$ dominant effective and $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$  
+\[
+b_{Z'} b_{Z''} = \sum_{Z\in\cZ(\lambda' + \lambda'')} \iota (Z, Z(\tau')\ast_0 Z(\tau''))
+\]
 \end{theorem}
@@
 
+\acom{To quote from BFZ for a concise definition: Cluster algebras are a class of commutative rings defined axiomatically in terms of a distinguished family of generators called cluster variables.
+Say also what is a seed, what is a mutation, what is a cluster, what is a cluster monomial, and finally for the stubbornly ignorant clarify that 'the cluster monomials' refers to cluster monomials for all possible clusters!}
+
+$\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
+% that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
+
+\acom{Background on cluster:}
+In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
+This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
+Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
+
 In the appendix to \cite{baumann2019mirkovic} the second and third author along with Morton-Ferguson check that the MV basis differs from the dual semicanonical basis (at the Kashiwara--Saito counterexample).
@@
 
-\acom{Which cluster monomials? The ones considered by GLS corresp to certain modules? iiuc they are interchangeable, but it is helpful to anchor one. Roger? Joel? Feel free to reword.} 
-\rcom{I don't understand the question. There is only one set of cluster monomials in $\CC[N]$.}
-
 We note that both of these bases are \new{biperfect} bases of $\CC[N]$ and in type $A_n$ with $n\le 3$ there is a unique biperfect basis of $\CC[N]$.
 
-For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor, and hence \acom{by BKK?}\rcom{I reworded it.} is in the MV basis \cite{kato2011polytopal}.
+For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor  \cite{kato2011polytopal}, and hence
+% \acom{by BKK?}\rcom{I reworded it.} 
+is in the MV basis. 
 % as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
@@
 Conversely, suppose we have a seed $(x_1,\dots,x_r)$ such that each $x_i$ is in the MV basis, i.e.\ for each $i$ there exists a stable MV cycle $Z_i$ such that $x_i = b_{Z_i}\in\CC[N]$.
-To show that all cluster variables \acom{for this seed?}\rcom{No, all of them.} are also in the MV basis it suffices to show that if $x_i$ is mutable then its mutation $x_i^*$ is also in the MV basis.
-This observation is based on the exchange relation:
+To show that all cluster variables
+% \acom{for this seed?}\rcom{No, all of them.} 
+are also in the MV basis it suffices to show that if $x_i$ is mutable then its mutation $x_i^*$ is also in the MV basis. This observation is based on the exchange relation:
 \[
@@
 where $x_+,x_-$ are monomials in $ (x_1, \dots, x_r)\setminus x_i$ determined by the cluster structure on $\CC[N]$. 
-\acom{the structure of interest?
+% \acom{the structure of interest?
 or are all cluster structures on this ring the same?} \rcom{The structure is derived from an initial seed coming from a reduced word {\bf i}.
@@
 So if we can find a stable MV cycle $Z_i^*$ such that $b_{Z_i}b_{Z_i^*} = x_+ + x_-$ for each $i$ then we will have checked the conjecture. 
-\acom{And we do not need to assume the special condition of BGL?}\rcom{They deal with cluster monomials in certain clusters while this deals with all cluster variables, so neither one completely implies the other.}
-% \acom{Roger says that $x_i x_i^* = \sum{b_{ij} > 0} x_j + \sum{b_{ij} < 0} x_j$ Do we have a recursion? Explicit candidates for $x_\pm$ starting with $Z_1$}
-
-The following examples give evidence that the mutation $x_i^*$ is in the MV basis. \acom{Roger, reword?}\rcom{Something like this?}
+% \acom{And we do not need to assume the special condition of BGL?}\rcom{They deal with cluster monomials in certain clusters while this deals with all cluster variables, so neither one completely implies the other.}
+
+The following examples give evidence that the mutation $x_i^*$ is in the MV basis. \acom{Roger, reword?}\rcom{Something like this?} \acom{Sure!}
 
@@
 % Consider the product $Z_1 * Z_2$, so the tableaux are
-Consider the product % $Z({{\scriptsize\young(2)}})*Z({\scriptsize\young(1,3)})$
+% Consider the product % $Z({{\scriptsize\young(2)}})*Z({\scriptsize\young(1,3)})$
 % \[
@@
 % \]
-$\young(2) * \young(1,3)$.
-Our matrix is
+% $\young(2) * \young(1,3)$.
+$\young(2) *_0 \young(1,3) = \young(3) + \young(2,3)$: 
+% 
+The requirement that 
 \[
-X = \left[\begin{BMAT}(e){c;c;c}{c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c}{c;c;c}
     s & A_{12}^1 & A_{13}^1 \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(2) *_\AA \young(1,3) 
+% \Rightarrow 
+% \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
+%     X_3 & A_{12}^1A_{23}^1+sA_{13}^1
+% \end{tabular}
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices. 
 \begin{table}[H]
@@
 % \]
-\noindent Hence, our ideals are
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
 \begin{table}[H]
@@
   \begin{tabular}{Q} 
-    \text{Ideal} & \text{Tableau} \\
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
     \midrule 
-    \langle A_{12}^1,s \rangle & \young(13,2) \equiv \young(3) \\
-    \langle A_{23}^1,s \rangle & \young(12,3) \equiv \young(2,3)
+    (A_{12}^1,s) & \young(13,2) \BS \\ % \equiv \young(3) \\
+    ( A_{23}^1,s) & \young(12,3) \TS % \equiv \young(2,3)
     \end{tabular}
@@
 % so $Z_1 * Z_2 = Z_{1 \leftarrow 2} + Z_{1 \rightarrow 2}$.
-\noindent so $\young(2) * \young(1,3) = \young(3) + \young(2,3)$.
+% \noindent so $\young(2) * \young(1,3) = \young(3) + \young(2,3)$.
 \end{example}
@@
 \begin{example}
-Consider the product $Z_2 * Z_3$, so the tableaux are 
+% Consider the product $Z_2 * Z_3$, so the tableaux are 
+% \[
+% \young(1,3) \text{ and } \young(1,2,4).
+% \]
+% Our matrix is 
+$\young(1,3) *_0 \young(1,2,4) = \young(1,4) + \young(1,3,4):$ The requirement that
 \[
-\young(1,3) \text{ and } \young(1,2,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
+A = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
     0 & 1 & & & \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(1,3) *_\AA \young(1,2,4)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s) & \young(11,24,3) \BS \\
+    (A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s) & \young(11,23,4) \TS 
+    \end{tabular}
+\end{table}
 % \[
@@
 % 
-\noindent Hence, our ideal decomposes into 
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle &\leadsto \young(11,24,3) &\equiv \young(1,4) &\leadsto Z_{2 \leftarrow 3} \\ 
+%     \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(11,23,4) &\equiv \young(1,3,4) &\leadsto Z_{2 \rightarrow 3}
+% \end{array}
+% \]
+% so $Z_2 * Z_3 = Z_{2 \leftarrow 3} + Z_{2 \rightarrow 3}$.
+\end{example}
+
+\begin{example}
+$\young(2) *_0 \young(1,3,4) = \young(2,3,4) + \young(13,2,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle &\leadsto \young(11,24,3) &\equiv \young(1,4) &\leadsto Z_{2 \leftarrow 3} \\ 
-    \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(11,23,4) &\equiv \young(1,3,4) &\leadsto Z_{2 \rightarrow 3}
-\end{array}
-\]
-so $Z_2 * Z_3 = Z_{2 \leftarrow 3} + Z_{2 \rightarrow 3}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_1 * Z_{2 \rightarrow 3}$, so the tableaux are 
-\[
-\young(2) \text{ and } \young(1,3,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
     s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(2) *_\AA \young(1,3,4)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{23}^1,A_{24}^1,A_{34}^1,s) & \young(12,3,4) \BS \\
+    (A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s) & \young(13,2,4) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_1 * Z_{2 \rightarrow 3}$, so the tableaux are 
+% \[
+% \young(2) \text{ and } \young(1,3,4).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+%     s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+%      & 0 & A_{23}^1 & A_{24}^1 \\
+%      & & s & A_{34}^1 \\
+%      & & & s
+% \end{BMAT}
+% \right].
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
 %     X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
-% \end{array}.
-% \]
-\noindent Hence, our ideal decomposes into 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
+% %     X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
+% % \end{array}.
+% % \]
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(12,3,4) &\equiv \young(2,3,4) &\leadsto Z_{P_1} \\ 
+%     \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
+% \end{array}
+% \]
+% so $Z_1 * Z_{2 \rightarrow 3} = Z_{P_1} + Z_{out}$.
+\end{example}
+
+\begin{example}
+$\young(2) *_0 \young(11,24,3) = \young(4) + \young(2,4):$ The requirement that
 \[
-\langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(12,3,4) &\equiv \young(2,3,4) &\leadsto Z_{P_1} \\ 
-    \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
-\end{array}
-\]
-so $Z_1 * Z_{2 \rightarrow 3} = Z_{P_1} + Z_{out}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_1 * Z_{2 \leftarrow 3}$, so the tableaux are 
-\[
-\young(2) \text{ and } \young(1,4).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(2) \text{ and } \young(11,24,3).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+A = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
     0 & 1 & & & & \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(2) *_\AA \young(11,24,3)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s) & \young(114,22,3) \BS \\
+    (A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s) & \young(112,24,3) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_1 * Z_{2 \leftarrow 3}$, so the tableaux are 
+% \[
+% \young(2) \text{ and } \young(1,4).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(2) \text{ and } \young(11,24,3).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+%     0 & 1 & & & & \\
+%     -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
+%      & & 0 & 1 & & \\
+%      & & & s & A_{23}^1 & A_{24}^1 \\
+%      & & & & s & A_{34}^1 \\
+%      & & & & & s
+% \end{BMAT}
+% \right].
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
+%     X_2 & A_{12}^1 + sA_{12}^2 \\
+%     X_3 & A_{13}^1, A_{23}^1 \\
+%     X_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
+%     \end{tabular}
+% \end{table}
 % \[
@@
 % \]
-\noindent Hence, our ideal decomposes into 
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(114,22,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
+%     \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(2,4) &\leadsto Z_{in}
+% \end{array}
+% \]
+% so $Z_1 * Z_{2 \leftarrow 3} = Z_{P_3} + Z_{in}$.
+\end{example}
+
+\begin{example}
+$\young(1,2,4) *_0 \young(12,3) = \young(1,4) + \young(1,3,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(114,22,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
-    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(2,4) &\leadsto Z_{in}
-\end{array}
-\]
-so $Z_1 * Z_{2 \leftarrow 3} = Z_{P_3} + Z_{in}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_3 * Z_{1 \rightarrow 2}$, so the tableaux are 
-\[
-\young(1,2,4) \text{ and } \young(2,3).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(1,2,4) \text{ and } \young(12,3).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+A = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
     0 & 1 & & & & \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(1,2,4) *_\AA \young(12,3)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s) & \young(112,24,3) \BS \\
+    (A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s) & \young(112,23,4) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_3 * Z_{1 \rightarrow 2}$, so the tableaux are 
+% \[
+% \young(1,2,4) \text{ and } \young(2,3).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(1,2,4) \text{ and } \young(12,3).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+%     0 & 1 & & & & \\
+%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
+%      & & 0 & 1 & & \\
+%      & & & s & A_{23}^1 & A_{24}^1 \\
+%      & & & & s & A_{34}^1 \\
+%      & & & & & 0
+% \end{BMAT}
+% \right].
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_2 & A_{12}^1 \\
@@
 %     X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
-% \end{array}.
-% \]
-\noindent Hence, our ideal decomposes into 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1 \\
+% %     X_3 & A_{23}^1 \\
+% %     X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
+% % \end{array}.
+% % \]
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(1,4) &\leadsto Z_{in} \\ 
+%     \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(112,23,4) &\equiv \young(1,3,4) &\leadsto Z_{P_1}
+% \end{array}
+% \]
+% so $Z_3 * Z_{1 \rightarrow 2} = Z_{in} + Z_{P_1}$.
+\end{example}
+
+\begin{example}
+$\young(1,2,4) *_0 \young(3) = \young(4) + \young(13,2,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(1,4) &\leadsto Z_{in} \\ 
-    \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(112,23,4) &\equiv \young(1,3,4) &\leadsto Z_{P_1}
-\end{array}
-\]
-so $Z_3 * Z_{1 \rightarrow 2} = Z_{in} + Z_{P_1}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_3 * Z_{1 \leftarrow 2}$, so the tableaux are 
-\[
-\young(1,2,4) \text{ and } \young(3).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(1,2,4) *_\AA \young(3)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{13}^1,A_{23}^1,s) & \young(14,2,3) \BS \\
+    (A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s) & \young(13,2,4) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_3 * Z_{1 \leftarrow 2}$, so the tableaux are 
+% \[
+% \young(1,2,4) \text{ and } \young(3).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+%     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+%      & 0 & A_{23}^1 & A_{24}^1 \\
+%      & & s & A_{34}^1 \\
+%      & & & 0
+% \end{BMAT}
+% \right].
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_2 & A_{12}^1 \\
 %     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
-% \end{array}.
-% \]
-\noindent Hence, our ideal decomposes into 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1 \\
+% %     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
+% % \end{array}.
+% % \]
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(14,2,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
+%     \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
+% \end{array}
+% \]
+% so $Z_3 * Z_{1 \leftarrow 2} = Z_{P_3} + Z_{out}$.
+\end{example}
+
+\begin{example}
+$\young(13,2) *_0 \young(1,4) = \young(14,3) + \young(3,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(14,2,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
-    \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
-\end{array}
-\]
-so $Z_3 * Z_{1 \leftarrow 2} = Z_{P_3} + Z_{out}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3}$, so the tableaux are 
-\[
-\young(3) \text{ and } \young(1,4).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(13,2) \text{ and } \young(1,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
+A = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
     0 & 1 & & & \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(13,2) *_\AA \young(1,4)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{13}^1,s) & \young(114,23) \BS \\
+    (A_{12}^1,A_{34}^1,s) & \young(113,24) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3}$, so the tableaux are 
+% \[
+% \young(3) \text{ and } \young(1,4).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(13,2) \text{ and } \young(1,4).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
+%     0 & 1 & & & \\
+%      & s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+%      & & 0 & A_{23}^1 & A_{24}^1 \\
+%      & & & 0 & A_{34}^1 \\
+%      & & & & s
+% \end{BMAT}
+% \right].
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_2 & A_{12}^1 \\
 %     X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
-% \end{array}.
-% \]
-\noindent Hence, our ideal is 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1 \\
+% %     X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
+% % \end{array}.
+% % \]
+% \noindent Hence, our ideal is 
+% \[
+% \langle A_{12}^1,A_{13}^1A_{34}^1+sA_{14}^1,s \rangle
+% = \langle A_{12}^1,A_{13}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{13}^1,s \rangle &\leadsto \young(114,23) &\equiv \young(14,3) &\leadsto Z_2 Z_{P_3} \\ 
+%     \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(113,24) &\equiv \young(3,4) &\leadsto Z_{P_2}
+% \end{array}
+% \]
+% so $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3} = Z_2 Z_{P_3} + Z_{P_2}$.
+\end{example}
+
+\begin{example}
+$\young(12,23) *_0 \young(1,3,4) = \young(3,4) + \young(12,33,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{13}^1A_{34}^1+sA_{14}^1,s \rangle
-= \langle A_{12}^1,A_{13}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{13}^1,s \rangle &\leadsto \young(114,23) &\equiv \young(14,3) &\leadsto Z_2 Z_{P_3} \\ 
-    \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(113,24) &\equiv \young(3,4) &\leadsto Z_{P_2}
-\end{array}
-\]
-so $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3} = Z_2 Z_{P_3} + Z_{P_2}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3}$, so the tableaux are 
-\[
-\young(2,3) \text{ and } \young(1,3,4).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(12,23) \text{ and } \young(1,3,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+A = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
     0 & 1 & & & & & \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(12,23) *_\AA \young(1,3,4)
 \]
-% 
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s) & \young(113,224,3) \BS \\
+    (A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s) & \young(112,233,4) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3}$, so the tableaux are 
+% \[
+% \young(2,3) \text{ and } \young(1,3,4).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(12,23) \text{ and } \young(1,3,4).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+%     0 & 1 & & & & & \\
+%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
+%      & & 0 & 1 & & & \\
+%      & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
+%      & & & & 0 & 1 & \\
+%      & & & & & s & A_{34}^1 \\
+%      & & & & & & s
+% \end{BMAT}
+% \right].
+% \]
+% % 
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_2 & A_{12}^1 \\
@@
 %     X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
-% \end{array}.
-% \]
-% 
-\noindent Hence, our ideal decomposes into 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1 \\
+% %     X_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
+% %     X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
+% % \end{array}.
+% % \]
+% % 
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
+%     \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle &\leadsto \young(112,233,4) &\equiv \young(12,33,4) &\leadsto Z_2 Z_{P_1}
+% \end{array}
+% \]
+% so $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3} = Z_{P_2} + Z_2 Z_{P_1}$.
+\end{example}
+
+\begin{example}
+$\young(11,23) *_0 \young(13,2,4) = \young(3,4) + \young(1,3,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
-    \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle &\leadsto \young(112,233,4) &\equiv \young(12,33,4) &\leadsto Z_2 Z_{P_1}
-\end{array}
-\]
-so $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3} = Z_{P_2} + Z_2 Z_{P_1}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_2 * Z_{out}$, so the tableaux are 
-\[
-\young(1,3) \text{ and } \young(13,2,4).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(11,23) \text{ and } \young(13,2,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
+A = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
     0 & 1 & & & & & & \\
@@
 \end{BMAT}
-\right]
+\right] \text{ is contained in } \young(11,23) *_\AA \young(13,2,4)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s) & \young(1113,224,3) \BS \\
+    (A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s) & \young(1113,223,4) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_2 * Z_{out}$, so the tableaux are 
+% \[
+% \young(1,3) \text{ and } \young(13,2,4).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(11,23) \text{ and } \young(13,2,4).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
+%     0 & 1 & & & & & & \\
+%      & 0 & 1 & & & & & \\
+%      & & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
+%      & & & 0 & 1 & & & \\
+%      & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
+%      & & & & & 0 & 1 & \\
+%      & & & & & & s & A_{34}^1 \\
+%      & & & & & & & s
+% \end{BMAT}
+% \right]
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_2 & A_{12}^1, A_{12}^2 \\
@@
 %     X_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
-% \end{array}.
-% \]
-\noindent Hence, our ideal decomposes into 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1, A_{12}^2 \\
+% %     X_3 & A_{13}^1 \\
+% %     X_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
+% % \end{array}.
+% % \]
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(1113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
+%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(1113,223,4) &\equiv \young(1,3,4) &\leadsto Z_{1 \leftarrow 2} Z_{2 \rightarrow 3}
+% \end{array}
+% \]
+% so $Z_2 * Z_{out} = Z_{P_2} + Z_{1 \leftarrow 2} Z_{2 \rightarrow 3}$.
+\end{example}
+
+\begin{example}
+$\young(1,3) *_0 \young(2,4) = \young(3,4) + \young(12,34):$ The requirement that
 \[
-\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(1113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
-    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(1113,223,4) &\equiv \young(1,3,4) &\leadsto Z_{1 \leftarrow 2} Z_{2 \rightarrow 3}
-\end{array}
-\]
-so $Z_2 * Z_{out} = Z_{P_2} + Z_{1 \leftarrow 2} Z_{2 \rightarrow 3}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_2 * Z_{in}$, so the tableaux are 
-\[
-\young(1,3) \text{ and } \young(2,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(1,3) *_\AA \young(2,4)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{34}^1,s) & \young(13,24) \BS \\
+    (A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s) & \young(12,34) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_2 * Z_{in}$, so the tableaux are 
+% \[
+% \young(1,3) \text{ and } \young(2,4).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+%     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+%      & s & A_{23}^1 & A_{24}^1 \\
+%      & & 0 & A_{34}^1 \\
+%      & & & s
+% \end{BMAT}
+% \right].
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
 %     X_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
-% \end{array}.
-% \]
-\noindent Hence, our ideal decomposes into 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
+% %     X_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
+% % \end{array}.
+% % \]
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{34}^1,s \rangle \cap \langle A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(13,24) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
+%     \langle A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s \rangle &\leadsto \young(12,34) & &\leadsto Z_{1 \rightarrow 2} Z_{2 \leftarrow 3}
+% \end{array}
+% \]
+% so $Z_2 * Z_{in} = Z_{P_2} + Z_{1 \rightarrow 2} Z_{2 \leftarrow 3}$.
+\end{example}
+
+\begin{example}
+$\young(13,2,4) *_0 \young(12,3) = \young(23,4) + \young(23,3,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{34}^1,s \rangle \cap \langle A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(13,24) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
-    \langle A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s \rangle &\leadsto \young(12,34) & &\leadsto Z_{1 \rightarrow 2} Z_{2 \leftarrow 3}
-\end{array}
-\]
-so $Z_2 * Z_{in} = Z_{P_2} + Z_{1 \rightarrow 2} Z_{2 \leftarrow 3}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_{out} * Z_{1 \rightarrow 2}$, so the tableaux are 
-\[
-\young(13,2,4) \text{ and } \young(2,3).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(13,2,4) \text{ and } \young(12,3).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+A = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
     0 & 1 & & & & & \\
@@
 \end{BMAT}
-\right]
+\right] \text{ is contained in } \young(13,2,4) *_\AA \young(12,3)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s) & \young(1123,24,3) \BS \\
+    (A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s) & \young(1123,23,4) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_{out} * Z_{1 \rightarrow 2}$, so the tableaux are 
+% \[
+% \young(13,2,4) \text{ and } \young(2,3).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(13,2,4) \text{ and } \young(12,3).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+%     0 & 1 & & & & & \\
+%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
+%      & & 0 & 1 & & & \\
+%      & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
+%      & & & & 0 & 1 & \\
+%      & & & & & s & A_{34}^1 \\
+%      & & & & & & 0
+% \end{BMAT}
+% \right]
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_2 & A_{12}^1 \\
@@
 %     X_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
-% \end{array}.
-% \]
-\noindent Hence, our ideal decomposes into 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1 \\
+% %     X_3 & A_{23}^1 +sA_{23}^2 \\
+% %     X_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
+% % \end{array}.
+% % \]
+% \noindent Hence, our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(1112,24,3) &\equiv \young(23,4) &\leadsto Z_1 Z_{P_2} \\ 
+%     \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(1123,23,4) &\equiv \young(23,3,4) &\leadsto Z_{1 \leftarrow 2} Z_{P_1}
+% \end{array}
+% \]
+% so $Z_{out} * Z_{1 \rightarrow 2} = Z_1 Z_{P_2} + Z_{1 \leftarrow 2} Z_{P_1}$.
+\end{example}
+
+\begin{example}
+$\young(2,4) *_0 \young(1,3) = \young(24,3) + \young(23,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(1112,24,3) &\equiv \young(23,4) &\leadsto Z_1 Z_{P_2} \\ 
-    \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(1123,23,4) &\equiv \young(23,3,4) &\leadsto Z_{1 \leftarrow 2} Z_{P_1}
-\end{array}
-\]
-so $Z_{out} * Z_{1 \rightarrow 2} = Z_1 Z_{P_2} + Z_{1 \leftarrow 2} Z_{P_1}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_{in} * Z_{1 \leftarrow 2}$, so the tableaux are
-\[
-\young(2,4) \text{ and } \young(3).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(2,4) \text{ and } \young(13).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
      s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(2,4) *_\AA \young(1,3)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{23}^1,s) & \young(124,3) \BS \\
+    (A_{34}^1,s) & \young(123,4) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_{in} * Z_{1 \leftarrow 2}$, so the tableaux are
+% \[
+% \young(2,4) \text{ and } \young(3).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(2,4) \text{ and } \young(13).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+%      s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+%      & 0 & A_{23}^1 & A_{24}^1 \\
+%      & & s & A_{34}^1 \\
+%      & & & 0
+% \end{BMAT}
+% \right].
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %      X_4 & A_{23}^1A_{34}^1 - sA_{24}^1
-% \end{array}.
-% \]
-\noindent Hence, our ideal is 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1
+% % \end{array}.
+% % \]
+% \noindent Hence, our ideal is 
+% \[
+% \langle A_{23}^1A_{34}^1 - sA_{24}^1,s \rangle
+% = \langle A_{23}^1,s \rangle \cap \langle A_{34}^1,s \rangle.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{23}^1,s \rangle &\leadsto \young(124,3) &\equiv \young(24,3) &\leadsto Z_{1 \rightarrow 2} Z_{P_3} \\ 
+%     \langle A_{34}^1,s \rangle &\leadsto \young(123,4) &\equiv \young(23,4) &\leadsto Z_1 Z_{P_2}
+% \end{array}
+% \]
+% so $Z_{in} * Z_{1 \leftarrow 2} = Z_{1 \rightarrow 2} Z_{P_3} + Z_1 Z_{P_2}$.
+\end{example}
+
+\begin{example}
+$\young(11,24,3) *_0 \young(13,2,4) = \young(14,3,4) + \young(13,24,4):$ The requirement that
 \[
-\langle A_{23}^1A_{34}^1 - sA_{24}^1,s \rangle
-= \langle A_{23}^1,s \rangle \cap \langle A_{34}^1,s \rangle.
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{23}^1,s \rangle &\leadsto \young(124,3) &\equiv \young(24,3) &\leadsto Z_{1 \rightarrow 2} Z_{P_3} \\ 
-    \langle A_{34}^1,s \rangle &\leadsto \young(123,4) &\equiv \young(23,4) &\leadsto Z_1 Z_{P_2}
-\end{array}
-\]
-so $Z_{in} * Z_{1 \leftarrow 2} = Z_{1 \rightarrow 2} Z_{P_3} + Z_1 Z_{P_2}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_{out} * Z_{2 \leftarrow 3}$, so the tableaux are 
-\[
-\young(1,4) \text{ and } \young(13,2,4).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(11,24,3) \text{ and } \young(13,2,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
+A = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
     0 & 1 & & & & & & & \\
@@
 \end{BMAT}
-\right]
+\right] \text{ is contained in } \young(11,24,3) *_\AA \young(13,2,4)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
 % 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s) & \young(1114,223,34) \BS \\
+    \begin{array}{c}
+     (A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s) 
+\end{array}& \young(1113,224,34) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_{out} * Z_{2 \leftarrow 3}$, so the tableaux are 
+% \[
+% \young(1,4) \text{ and } \young(13,2,4).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(11,24,3) \text{ and } \young(13,2,4).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
+%     0 & 1 & & & & & & & \\
+%      & 0 & 1 & & & & & & \\
+%      & & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
+%      & & & 0 & 1 & & & & \\
+%      & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
+%      & & & & & 0 & 1 & & \\
+%      & & & & & & s & A_{34}^1 & A_{34}^2 \\
+%      & & & & & & & 0 & 1 \\
+%      & & & & & & & & s
+% \end{BMAT}
+% \right]
+% \]
+% The relations from the submatrices are:
+% % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %     X_2 & A_{12}^1,A_{12}^2 \\
 %     X_3 & A_{13}^1, A_{23}^1 \\
-%     X_4 & \begin{array}{c}
-%          A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1,  \\
-%          A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
-%          A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2
+%     X_4 & A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
+%         & A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2 
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1,A_{12}^2 \\
+% %     X_3 & A_{13}^1, A_{23}^1 \\
+% %     X_4 & \begin{array}{c}
+% %          A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1,  \\
+% %          A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
+% %          A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2
+% %     \end{array}
+% % \end{array}.
+% % \]
+% Hence our ideal decomposes into 
+% \[
+% \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s \rangle \cap \begin{array}{c}
+%      \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
+%      A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s \rangle. 
 % \end{array}
-% \end{array}.
-% \]
-Hence our ideal decomposes into 
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(1114,223,34) &\equiv \young(14,3,4) &\leadsto Z_{2 \rightarrow 3} Z_{P_3} \\ 
+%     \begin{array}{c}
+%      \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
+%      A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s \rangle. 
+% \end{array}&\leadsto \young(1113,224,34) &\equiv \young(13,24,4) &\leadsto Z_3 Z_{P_2}
+% \end{array}
+% \]
+% so $Z_{out} * Z_{2 \leftarrow 3} = Z_{2 \rightarrow 3} Z_{P_3} + Z_3 Z_{P_2}$.
+\end{example}
+
+\begin{example}
+$\young(12,24,3) *_0 \young(1,3,4) = \young(13,24,4) + \young(12,34,4):$ The requirement that
 \[
-\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s \rangle \cap \begin{array}{c}
-     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s \rangle. 
-\end{array}
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(1114,223,34) &\equiv \young(14,3,4) &\leadsto Z_{2 \rightarrow 3} Z_{P_3} \\ 
-    \begin{array}{c}
-     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s \rangle. 
-\end{array}&\leadsto \young(1113,224,34) &\equiv \young(13,24,4) &\leadsto Z_3 Z_{P_2}
-\end{array}
-\]
-so $Z_{out} * Z_{2 \leftarrow 3} = Z_{2 \rightarrow 3} Z_{P_3} + Z_3 Z_{P_2}$.
-\end{example}
-
-\begin{example}
-Consider the product $Z_{in} * Z_{2 \rightarrow 3}$, so the tableaux are 
-\[
-\young(2,4) \text{ and } \young(1,3,4).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(12,24,3) \text{ and } \young(1,3,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
+A = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
     0 & 1 & & & & & & \\
@@
 \end{BMAT}
-\right].
+\right] \text{ is contained in } \young(12,24,3) *_\AA \young(1,3,4)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
+% 
 \begin{table}[H]
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    \begin{array}{c}
+     (A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s)  
+\end{array} & \young(113,224,34) \BS \\
+    \begin{array}{c}
+      (A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
+      A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s) 
+ \end{array} & \young(112,234,34) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_{in} * Z_{2 \rightarrow 3}$, so the tableaux are 
+% \[
+% \young(2,4) \text{ and } \young(1,3,4).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(12,24,3) \text{ and } \young(1,3,4).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
+%     0 & 1 & & & & & & \\
+%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
+%      & & 0 & 1 & & & & \\
+%      & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
+%      & & & & 0 & 1 & & \\
+%      & & & & & s & A_{34}^1 & A_{34}^2 \\
+%      & & & & & & 0 & 1 \\
+%      & & & & & & & s
+% \end{BMAT}
+% \right].
+% \]
+% The relations from the submatrices are:
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %   X_2 & A_{12}^1 \\
 %     X_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
-%     X_4 & \begin{array}{c}
+%     X_4 & 
 %          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-%          A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2,  \\
-%          A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
-%          A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1 
+%         & A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2, A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
+%         & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1 \\
+% %     X_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
+% %     X_4 & \begin{array}{c}
+% %          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+% %          A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2,  \\
+% %          A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
+% %          A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1 
+% %     \end{array} 
+% % \end{array}.
+% % \]
+% Hence our ideal decomposes into 
+% \[\begin{array}{c}
+%      \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+%      A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s \rangle  
 % \end{array}
-% \end{array}.
-% \]
-Hence our ideal decomposes into 
-\[\begin{array}{c}
-     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s \rangle  
-\end{array}
- \cap \begin{array}{c}
-      \langle A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
-      A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s \rangle. 
- \end{array} 
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \begin{array}{c}
-     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s \rangle  
-\end{array} &\leadsto \young(113,224,34) &\equiv \young(13,24,4) &\leadsto Z_3 Z_{P_2} \\ 
-    \begin{array}{c}
-      \langle A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
-      A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s \rangle. 
- \end{array} &\leadsto \young(112,234,34) &\equiv \young(12,34,4) &\leadsto Z_{2 \leftarrow 3} Z_{P_1}
-\end{array}
-\]
-so $Z_{in} * Z_{2 \rightarrow 3} = Z_3 Z_{P_2} + Z_{2 \leftarrow 3} Z_{P_1}$.
+%  \cap \begin{array}{c}
+%       \langle A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
+%       A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s \rangle. 
+%  \end{array} 
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \begin{array}{c}
+%      \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+%      A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s \rangle  
+% \end{array} &\leadsto \young(113,224,34) &\equiv \young(13,24,4) &\leadsto Z_3 Z_{P_2} \\ 
+%     \begin{array}{c}
+%       \langle A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
+%       A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s \rangle. 
+%  \end{array} &\leadsto \young(112,234,34) &\equiv \young(12,34,4) &\leadsto Z_{2 \leftarrow 3} Z_{P_1}
+% \end{array}
+% \]
+% so $Z_{in} * Z_{2 \rightarrow 3} = Z_3 Z_{P_2} + Z_{2 \leftarrow 3} Z_{P_1}$.
 \end{example}
@@
 \begin{example}
-Consider the product $Z_{in} * Z_{out}$, so the tableaux are 
+$\young(112,24,3) *_0 \young(13,2,4) = \young(24,3,4) + \young(123,24,4):$ The requirement that
 \[
-\young(2,4) \text{ and } \young(13,2,4).
-\]
-As the sum of the weights is not dominant, we will instead be using the tableaux
-\[
-\young(112,24,3) \text{ and } \young(13,2,4).
-\]
-Our matrix is 
-\[
-X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
+A = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
     0 & 1 & & & & & & & & \\
@@
 \end{BMAT}
-\right]
+\right] \text{ is contained in } \young(112,24,3) *_\AA \young(13,2,4)
 \]
-The relations from the submatrices are:
+results in the following relations on submatrices:
+% 
 \begin{table}[H]
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    % \text{Ideal} & \text{Tableau} \\
+    X(\tau) & \tau \\ 
+    \midrule 
+    (A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s) & \young(11124,223,34) \BS \\
+    \begin{array}{c}
+     (A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s). 
+\end{array} & \young(11123,224,34) \TS
+    \end{tabular}
+\end{table}
+% Consider the product $Z_{in} * Z_{out}$, so the tableaux are 
+% \[
+% \young(2,4) \text{ and } \young(13,2,4).
+% \]
+% As the sum of the weights is not dominant, we will instead be using the tableaux
+% \[
+% \young(112,24,3) \text{ and } \young(13,2,4).
+% \]
+% Our matrix is 
+% \[
+% X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
+%     0 & 1 & & & & & & & & \\
+%      & 0 & 1 & & & & & & & \\
+%      & & s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
+%      & & & 0 & 1 & & & & & \\
+%      & & & & 0 & 1 & & & & \\
+%      & & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
+%      & & & & & & 0 & 1 & & \\
+%      & & & & & & & s & A_{34}^1 & A_{34}^2 \\
+%      & & & & & & & & 0 & 1 \\
+%      & & & & & & & & & s
+% \end{BMAT}
+% \right]
+% \]
+% The relations from the submatrices are:
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
 %   X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
 %     X_3 & A_{13}^1,A_{23}^1 \\
-%     X_4 & \begin{array}{c}
-%          A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-%          A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
-%          A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
-%          A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
-%          A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
+%     X_4 & A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+%         & A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
+%         & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
+%         & A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
+%         & A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
+%     \end{tabular}
+% \end{table}
+% % \[
+% % \begin{array}{c|c}
+% %     \text{Submatrix} & \text{Relations} \\ \hline
+% %     X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
+% %     X_3 & A_{13}^1,A_{23}^1 \\
+% %     X_4 & \begin{array}{c}
+% %          A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+% %          A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
+% %          A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
+% %          A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
+% %          A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
+% %     \end{array} 
+% % \end{array}.
+% % \]
+% Hence our ideal decomposes into \acom{formatting funny; can just list irrecs?}
+% \[
+% \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
+% \cap \begin{array}{c}
+%      \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+%      A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
 % \end{array} 
-% \end{array}.
-% \]
-Hence our ideal decomposes into \acom{formatting funny; can just list irrecs?}
-\[
-\langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
-\cap \begin{array}{c}
-     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
-\end{array} 
-\]
-The tableau for each ideal is
-\[\begin{array}{cccc}\vspace{1mm}
-    \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
-    \begin{array}{c}
-     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
-\end{array} &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
-\end{array}
-\]
-so $Z_{in} * Z_{out} = Z_{P_1} Z_{P_3} + Z_1 Z_3 Z_{P_2}$.
+% \]
+% The tableau for each ideal is
+% \[\begin{array}{cccc}\vspace{1mm}
+%     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
+%     \begin{array}{c}
+%      \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
+%      A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
+% \end{array} &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
+% \end{array}
+% \]
+% so $Z_{in} * Z_{out} = Z_{P_1} Z_{P_3} + Z_1 Z_3 Z_{P_2}$.
 \end{example}

### 2021-06-02 draft.tex
Editted examples

@@
     \item For any $ 
-    \gamma \subset [m] $, we have $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
+    \gamma \subset [m] $, we have 
+    $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
     \item For any $ \gamma_1 \subset \gamma_2 \subset [m]$, we have $$ (L_{\gamma_2})_{\gamma_1} = L_{\gamma_1}
@@
 Therefore, as $i$ varies, we see that the pair $(L(0),L(s))\in S^{\mu'}\times S^{\mu''}$ is such that 
-$$(L_{[1,i]}(0),L_{[1,i]}(s))  = (L(0)_{[1,i]},L(s)_{[1,i]}) \in \Gr^{\lambda'(i)}\times\Gr^{\lambda''(i)}$$ 
+$$
+(L_{[1,i]}(0),L_{[1,i]}(s))  = (L(0)_{[1,i]},L(s)_{[1,i]}) \in \Gr^{\lambda'(i)}\times\Gr^{\lambda''(i)}
+$$ 
 and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$. The argument can be reversed for
@@
     % The image of $\mathring X(\tau',\tau'')_{0,0}$ in $\mathring Z(\tau')\ast_0 \mathring Z(\tau'')$ is dense. In particular 
-    $\iota(X(\tau), X(\tau',\tau'')_{0,0}) = \iota( Z(\tau), Z(\tau')\ast_0 \mathring Z(\tau''))\,.$
+    $\iota(X(\tau), X(\tau',\tau'')_{0,0}) = \iota( Z(\tau), Z(\tau')\ast_0 Z(\tau''))\,.$
 \end{corollary}
@@
 %Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ and $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?} irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties.
-We can compute intersection multiplicities by passing to dense constructible subsets.  By
-the isomorphisms of \Cref{lem:XtZt} and \Cref{pr:XttZtt}, $X(\tau) $ is a dense constructible subset of $ Z(\tau) $ and $ X(\tau', \tau'')_{0,0} $ is a dense constructible subset of $ Z(\tau') \ast_0 Z(\tau'') $.
+We can compute intersection multiplicities by passing to dense constructible subsets.  
+By the isomorphisms of \Cref{lem:XtZt} and \Cref{pr:XttZtt}, $X(\tau) $ is a dense constructible subset of $ Z(\tau) $ and $ X(\tau', \tau'')_{0,0} $ is a dense constructible subset of $ Z(\tau') \ast_0 Z(\tau'') $.
 %  
@@
     \begin{equation}
-        \iota(Z(\tau), Z(\tau') \arfu Z(\tau'')) = 1 \,. 
+        \iota(Z(\tau), Z(\tau') \geofu Z(\tau'')) = 1 \,. 
     \end{equation}
@@
 % $V(\lambda) = IH(\overline\Gr^\lambda)$ and  
-$V(\lambda)_\mu = H_{\rho(\lambda-\mu)}(\overline{\Gr^\lambda\cap S^\mu_-})$ where $H_d$ denotes $d$-dimensional Borel--Moore homology. 
-In particular, the MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$ give a basis of $V(\lambda)$. We denote this set of MV cycles $\cZ(\lambda)$. 
+$V(\lambda)_\mu = H_{2\rho(\lambda-\mu)}(\overline{\Gr^\lambda\cap S^\mu_-})$ where $H_d$ denotes $d$-dimensional Borel--Moore homology. 
+In particular, the MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$ give a basis of $V(\lambda)$. We denote this set of MV cycles $\cZ(\lambda)$, $\{[Z] : ..  \}$.
+\acom{$\cZ(\lambda)$ can go earlier}
 %
@@
 Which, by commutativity, will determine the middle downward pointing blue.}
+\jcom{Yes, I like this diagram.  Maybe the two rightward arrow should point leftward, since we did already define $ \tau \mapsto Z(\tau)$.}
+
 \[
@@
 \]
+Explain that fibres contain tableaux related by padding.
+$Z(\tau)$ is defined even when $\mu$ is not dominant.
+We choose a section for which $\mu$ is dominant (Lemma 9) because $X(\tau)$ doesn't make sense when it isn't, but when we come back to $Z(\infty)$ we can renormalize so $\mu$ is not dominant.
 % 
@@
     Let $n_\bullet$ be a Lusztig datum of coweight $\nu$.
-There exist $\lambda,\mu$ smallest such that $n_\bullet$ is the Lusztig datum of a tableau $\tau\in YT(\lambda)_\mu$.
+There exist $\lambda,\mu$ dominant effective smallest such that $n_\bullet$ is the Lusztig datum of a tableau $\tau\in YT(\lambda)_\mu$.
 They are determined by the following minimization problem.
@@
 $$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s]}{\langle A_{12}^1+sA_{12}^2, A_{12}^2A_{23}^1+sA_{13}^1, A_{12}^1A_{23}^1+s^2A_{13}^1, s\rangle} \cong \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,b_3,s]}{\langle A_{12}^1, A_{12}^2\rangle \cap \langle A_{12}^1, A_{23}^1 \rangle}.$$
-\acom{TODO: put ideals of $\arfu$ and their tableaux into tables; also divide into 2 sections, $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with `rising action'?}
+% 
+\acom{TODO: put ideals of arithmetic fusion and their tableaux into tables; also divide into 2 sections, $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with rising action?}
+% 
 We see that the 0-fibre is reducible with two components. The tableau corresponding to each ideal is
@@
 There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables.
-We list the corresponding tableaux, coordinate ring of the generalized orbital variety $X(\tau)$, and Lusztig-datum below:
-
+We will take the initial cluster $(x_1,\dots,x_6)$, with $x_4,x_5,x_6$ being frozen, coming from the reduced word ${\bf i} = (1,2,3,1,2,1)$.
+We list the corresponding tableaux, coordinate ring of the generalized orbital variety $X(\tau)$, Lusztig-datum, and cluster variable as a Laurent polynomial in the $x_i$ below:
+
+\acom{Add dominant version column}
 % \jcom{This is a nice table.  But these are the coordinate rings of $ X(\tau)$, not of $ Z(\tau) $.}
@@
   \centering
-  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}>{$}l<{$}}
+  \newcolumntype{Q}{>{$}l<{$}>{$}c<{$}>{$}l<{$}>{$}l<{$}>{$}c<{$}}
   \begin{tabular}{Q} 
-    \tau & \text{Coordinate ring of }X(\tau) & \text{Lusztig-datum} \\
+    \tau' & \tau = \text{Dominant }\tau' & \text{Coordinate ring of }X(\tau) & \text{Lusztig-datum} & \text{Cluster variable} \\
     \midrule 
-\young(2) & \CC[A_{12}^1] & (1,0,0,0,0,0) \rule{0pt}{3ex}\\
-\young(1,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1,A_{13}^1 \rangle} & (0,0,0,1,0,0) \TS\BS\\
-\young(1,2,4) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 \rangle} & (0,0,0,0,0,1) \TS\BS\\
-\young(3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1 \rangle} & (1,0,0,1,0,0) \TS\BS\\
-\young(2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{23}^1 \rangle} & (0,1,0,0,0,0) \TS\BS\\
-\young(1,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 \rangle} & (0,0,0,1,0,1) \TS\BS\\
-\young(1,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 \rangle} & (0,0,0,0,1,0) \TS\BS\\
-\young(2,4) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 \rangle} & (0,1,0,0,0,1) \TS\BS\\
-\young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 \rangle} & (1,0,0,0,1,0) \TS\BS\\
-\young(2,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{23}^1,A_{24}^1,A_{34}^1 \rangle} & (0,0,1,0,0,0) \TS\BS\\
-\young(3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1 \rangle} & (0,1,0,0,1,0) \TS\BS\\
-\young(4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle} & (1,0,0,1,0,1) \TS\BS\\
+\young(2) & \young(12) & \CC[A_{12}^1] & (1,0,0,0,0,0) & x_1 \rule{0pt}{3ex}\\
+\young(1,3) & \young(11,23) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1,A_{13}^1 \rangle} & (0,0,0,1,0,0) & \frac{x_2 + x_3}{x_1} \TS\BS\\
+\young(1,2,4) & \young(11,22,34) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 \rangle} & (0,0,0,0,0,1) & \frac{x_2x_4 + x_3x_6 + x_1x_5}{x_2x_3} \TS\BS\\
+\young(3) & \young(13,2) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1 \rangle} & (1,0,0,1,0,0) & x_2 \TS\BS\\
+\young(2,3) & \young(12,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{23}^1 \rangle} & (0,1,0,0,0,0) & x_3 \TS\BS\\
+\young(1,4) & \young(11,24,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 \rangle} & (0,0,0,1,0,1) & \frac{x_1x_5 + x_6(x_2+x_3)}{x_1x_2} \TS\BS\\
+\young(1,3,4) & \young(11,23,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 \rangle} & (0,0,0,0,1,0) & \frac{x_1x_5 + x_4(x_2+x_3)}{x_1x_3}\TS\BS\\
+\young(2,4) & \young(112,24,3) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 \rangle} & (0,1,0,0,0,1) & \frac{x_3x_6+x_1x_5}{x_2} \TS\BS\\
+\young(13,2,4) & \young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 \rangle} & (1,0,0,0,1,0) & \frac{x_2x_4 + x_1x_5}{x_3} \TS\BS\\
+\young(2,3,4) & \young(12,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{23}^1,A_{24}^1,A_{34}^1 \rangle} & (0,0,1,0,0,0) & x_4 \TS\BS\\
+\young(3,4) & \young(13,24) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1 \rangle} & (0,1,0,0,1,0) & x_5 \TS\BS\\
+\young(4) & \young(14,2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle} & (1,0,0,1,0,1) & x_6 \TS\BS\\
   \end{tabular}
 \end{table}
-
 % \[
@@
 
+Instead of writing the exchange relations in terms of $b_{Z(\tau)}$ or the fusion product in terms of $Z(\tau)$, we will use $\tau$ for both situations.
+
 \jcom{I think that you should clarify what you mean by ``our ideal'' below.  I think that it is the ideal of $ X(\tau', \tau'')_{0,0}$, is that correct?}
@@
 % $\young(2) * \young(1,3)$.
-$\young(2) *_0 \young(1,3) = \young(3) + \young(2,3)$: 
+$\young(2) \cdot \young(1,3) = \young(3) + \young(2,3)$: 
 % 
@@
 \[
-A = \left[\begin{BMAT}(e){c;c;c}{c;c;c}
+X = \left[\begin{BMAT}(e){c;c;c}{c;c;c}
     s & A_{12}^1 & A_{13}^1 \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2) *_\AA \young(1,3) 
+\right] \text{ is contained in } \young(2) *_{\AA \setminus \{0\}} \young(1,3) 
 % \Rightarrow 
@@
     % \text{Ideal} & \text{Tableau} \\
-    X(\tau) & \tau \\ 
+    \text{Ideal of } X(\tau) & \tau \\ 
     \midrule 
@@
 % Our matrix is 
-$\young(1,3) *_0 \young(1,2,4) = \young(1,4) + \young(1,3,4):$ The requirement that
+$\young(1,3) \cdot \young(1,2,4) = \young(1,4) + \young(1,3,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
+X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
     0 & 1 & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1,3) *_\AA \young(1,2,4)
+\right] \text{ is contained in } \young(1,3) *_{\AA \setminus \{0\}} \young(1,2,4)
 \]
@@
 \begin{example}
-$\young(2) *_0 \young(1,3,4) = \young(2,3,4) + \young(13,2,4):$ The requirement that
+$\young(2) \cdot \young(1,3,4) = \young(2,3,4) + \young(13,2,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
     s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2) *_\AA \young(1,3,4)
+\right] \text{ is contained in } \young(2) *_{\AA \setminus \{0\}} \young(1,3,4)
 \]
@@
 \begin{example}
-$\young(2) *_0 \young(11,24,3) = \young(4) + \young(2,4):$ The requirement that
+$\young(2) \cdot \young(11,24,3) = \young(4) + \young(2,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
     0 & 1 & & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2) *_\AA \young(11,24,3)
+\right] \text{ is contained in } \young(2) *_{\AA \setminus \{0\}} \young(11,24,3)
 \]
@@
 \begin{example}
-$\young(1,2,4) *_0 \young(12,3) = \young(1,4) + \young(1,3,4):$ The requirement that
+$\young(1,2,4) \cdot \young(12,3) = \young(1,4) + \young(1,3,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
     0 & 1 & & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1,2,4) *_\AA \young(12,3)
+\right] \text{ is contained in } \young(1,2,4) *_{\AA \setminus \{0\}} \young(12,3)
 \]
@@
 \begin{example}
-$\young(1,2,4) *_0 \young(3) = \young(4) + \young(13,2,4):$ The requirement that
+$\young(1,2,4) \cdot \young(3) = \young(4) + \young(13,2,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1,2,4) *_\AA \young(3)
+\right] \text{ is contained in } \young(1,2,4) *_{\AA \setminus \{0\}} \young(3)
 \]
@@
 \begin{example}
-$\young(13,2) *_0 \young(1,4) = \young(14,3) + \young(3,4):$ The requirement that
+$\young(13,2) \cdot \young(1,4) = \young(14,3) + \young(3,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
+X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
     0 & 1 & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(13,2) *_\AA \young(1,4)
+\right] \text{ is contained in } \young(13,2) *_{\AA \setminus \{0\}} \young(1,4)
 \]
@@
 \begin{example}
-$\young(12,23) *_0 \young(1,3,4) = \young(3,4) + \young(12,33,4):$ The requirement that
+$\young(12,23) \cdot \young(1,3,4) = \young(3,4) + \young(12,33,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
     0 & 1 & & & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(12,23) *_\AA \young(1,3,4)
+\right] \text{ is contained in } \young(12,23) *_{\AA \setminus \{0\}} \young(1,3,4)
 \]
@@
 \begin{example}
-$\young(11,23) *_0 \young(13,2,4) = \young(3,4) + \young(1,3,4):$ The requirement that
+$\young(11,23) \cdot \young(13,2,4) = \young(3,4) + \young(1,3,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
+X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
     0 & 1 & & & & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,23) *_\AA \young(13,2,4)
+\right] \text{ is contained in } \young(11,23) *_{\AA \setminus \{0\}} \young(13,2,4)
 \]
@@
 \begin{example}
-$\young(1,3) *_0 \young(2,4) = \young(3,4) + \young(12,34):$ The requirement that
+$\young(1,3) \cdot \young(2,4) = \young(3,4) + \young(12,34):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1,3) *_\AA \young(2,4)
+\right] \text{ is contained in } \young(1,3) *_{\AA \setminus \{0\}} \young(2,4)
 \]
@@
 \begin{example}
-$\young(13,2,4) *_0 \young(12,3) = \young(23,4) + \young(23,3,4):$ The requirement that
+$\young(13,2,4) \cdot \young(12,3) = \young(23,4) + \young(23,3,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
     0 & 1 & & & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(13,2,4) *_\AA \young(12,3)
+\right] \text{ is contained in } \young(13,2,4) *_{\AA \setminus \{0\}} \young(12,3)
 \]
@@
 \begin{example}
-$\young(2,4) *_0 \young(1,3) = \young(24,3) + \young(23,4):$ The requirement that
+$\young(2,4) \cdot \young(1,3) = \young(24,3) + \young(23,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
      s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2,4) *_\AA \young(1,3)
+\right] \text{ is contained in } \young(2,4) *_{\AA \setminus \{0\}} \young(1,3)
 \]
@@
 \begin{example}
-$\young(11,24,3) *_0 \young(13,2,4) = \young(14,3,4) + \young(13,24,4):$ The requirement that
+$\young(11,24,3) \cdot \young(13,2,4) = \young(14,3,4) + \young(13,24,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
+X = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
     0 & 1 & & & & & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,24,3) *_\AA \young(13,2,4)
+\right] \text{ is contained in } \young(11,24,3) *_{\AA \setminus \{0\}} \young(13,2,4)
 \]
@@
 \begin{example}
-$\young(12,24,3) *_0 \young(1,3,4) = \young(13,24,4) + \young(12,34,4):$ The requirement that
+$\young(12,24,3) \cdot \young(1,3,4) = \young(13,24,4) + \young(12,34,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
+X = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
     0 & 1 & & & & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(12,24,3) *_\AA \young(1,3,4)
+\right] \text{ is contained in } \young(12,24,3) *_{\AA \setminus \{0\}} \young(1,3,4)
 \]
@@
 \begin{example}
-$\young(112,24,3) *_0 \young(13,2,4) = \young(24,3,4) + \young(123,24,4):$ The requirement that
+$\young(112,24,3) \cdot \young(13,2,4) = \young(24,3,4) + \young(123,24,4):$ The requirement that
 \[
-A = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
+X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
     0 & 1 & & & & & & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(112,24,3) *_\AA \young(13,2,4)
+\right] \text{ is contained in } \young(112,24,3) *_{\AA \setminus \{0\}} \young(13,2,4)
 \]

### 2021-06-03 draft.tex
changed superficial stuff added tmp toc and todolist

@@
 \maketitle
+\tableofcontents
+
+\section{Todolist}
+\begin{itemize}
+    \item Remove the TOC 
+    \item Edit the intro 
+    \item We are using the word [geometric] fusion just for the central fibre, we also have arithmetic fusion (aka multiplication in $\CC[N]$), and BD family: $X\geofu Y, b(X) \arfu b(Y), X \bdfamc Y\supset X\bdfamo Y$
+    \item Which MVy paper to cite? 
+    \item Super repetitive about lambdas and mus 
+    \item Formatting could be bit better, e.g.\ some stuff goes outside the margin
+    \item Fix numbering so that theorems, defs etc share a counter and are restarted by section 
+    \item tableau of weight/filling? box of weight/filling? I prefer weight but don't mind filling 
+    \item Recalling intersection multiplicity, checking that the definitions allow passing to open sets
+\end{itemize}
 
@@
 One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!
+
+{\color{blue}
+\acom{To quote from BFZ for a concise definition: Cluster algebras are a class of commutative rings defined axiomatically in terms of a distinguished family of generators called cluster variables.
+Say also what is a seed, what is a mutation, what is a cluster, what is a cluster monomial, and finally for the stubbornly ignorant clarify that 'the cluster monomials' refers to cluster monomials for all possible clusters!}
+
+$\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
+% that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
+
+\acom{Background on cluster:}
+In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
+This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
+Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
+
+In the appendix to \cite{baumann2019mirkovic} the second and third author along with Morton-Ferguson check that the MV basis differs from the dual semicanonical basis (at the Kashiwara--Saito counterexample).
+Yet, the two bases have enough in common (c.f.\ BKT,...?), that we have the following conjecture.
+
+\begin{conjecture}
+    The dual semicanonical basis and the MV basis overlap on the cluster monomials. In particular, the cluster monomials are contained in the MV basis. 
+\end{conjecture}
+
+We note that both of these bases are \new{biperfect} bases of $\CC[N]$ and in type $A_n$ with $n\le 3$ there is a unique biperfect basis of $\CC[N]$. }
 
@@
 We will also consider $\cO_s = \CC\xt[t-s]$ and its fraction field $\cK_s=\CC\xT[t-s]$, for any 
-$ s \in \CC\setminus\{0\} $, as well as $ \Oinf = \CC\xt[t^{-1}] $ and $\Kinf = \CC\xT[t^{-1}]$. For any $ s \in \PP = \PP^1$, 
+$ s \in \CC\setminus\{0\} $, as well as $ \Oinf = \CC\xt[t^{-1}] $ and $\Kinf = \CC\xT[t^{-1}]$. For any point $ s \in \PP = \PP^1$, 
 % TODO: Identifying $s\in\CC$ and the line $s\in\PP$ containing it right?
@@
 
-Note that for $ s \in \CC $, we have an obvious isomorphisms  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$. 
+Note that for $ s \in \CC $, we have an obvious isomorphisms  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$. % ok technically the point s is in P and the coordinate s is valued in C 
 % 
@@
         G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,;$$
-        \item in terms of lattices, it is given by $(L,s)\mapsto L$, using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on ambient spaces. 
+        \item in terms of lattices as $$(L,s)\mapsto L\,,$$ using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on ambient spaces. 
     \end{enumerate}
@@
 % \acom{Begun. Not sure if it is what you had in mind.}
-
-\jcom{I reorganized a bit.  This last point is not really much of a result, so removed the ``proposition'' label.}
+% \jcom{I reorganized a bit.  This last point is not really much of a result, so removed the ``proposition'' label.}
+% \acom{Ok}
 
@@
 
-Let $ \Gr_{0, \AA^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.  
+Let $ \Gr_{0, \AA^\times} $ denote the preimage of $\Ax = \AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.  
 % 
@@
 
-Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $$ X_1 \ast_{\Cx} X_2 := \theta^{-1}(X_1 \times X_2) \subset \Gr_{0, \AA^\times} $$
+Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme 
+$$ 
+    X_1 \bdfamo X_2 := \theta^{-1}(X_1 \times X_2) \subset \Gr_{0, \AA^\times} 
+$$
+called the \new{open family} of $X_1$ and $X_2$. 
 % 
@@
 % \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
-For $ s \in \Cx$, we write $ X_1 \ast_s X_2  $ for the fibres of $ X_1 \ast_{\Cx} X_2 $ over $ s$.
-By construction, the map $ \theta_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$
+Given a point $ s \in \Ax$, we write $ X_1 \bdfamf X_2  $ for the fibre of $ X_1 \bdfamo X_2 $ over $s$.
+The map $ \theta_s$ identifies $ X_1 \bdfamf X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.
 
@@
 
-The fibre $ X_1 \ast_0 X_2$ of $ X_1 \ast_{\AA} X_2 $ over $0$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
-We call this subscheme the \new{fusion} of $ X_1 $ and $ X_2$.
+The fibre $ X_1 \geofu X_2$ of $ X_1 \ast_{\AA} X_2 $ over $0$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
+We call this subscheme the (geometric) \new{fusion} of $ X_1 $ and $ X_2$.
 
@@
 \label{ss:subgrs}
-Now fix effective dominant coweights $\lambda', \lambda'' $ of sizes $N',N''$  and their sum $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
+\acom{Recall the positive root cone, as well as the dominance order on coweights.}
+
+Going forward, we fix a pair of arbitrary effective dominant coweights $\lambda', \lambda'' $ of sizes $N',N''$ and a pair of (not necessarily dominant) effective coweights $\mu',\mu''$ also of sizes $N',N''$ such that $\mu = \mu' + \mu''$ is dominant.
+Let $ \lambda = \lambda' + \lambda'' $ and $ N = N'+N''$.
+% 
 % Coweights define elements in the various affine Grassmannians which we consider.
@@
 % the right cosets which they represent are clear from the context.
-We consider the following subschemes of the affine Grassmannians.
+
+% We consider the following subschemes of the affine Grassmannians.
+Using $\lambda,\lambda',\lambda''$ and $\mu,\mu',\mu''$ we define the subschemes of $\Gr$, $\Grth$, and $\Grbd$ which will be considered, give some properties, and say how they are related.  
 % 
@@
 \label{def:sphfus}
-    The \new{BD family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.
+    The \new{family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \bdfamc \overline{\Gr}^{\lambda''} $.
     % $$ 
@@
 \end{definition}
-\jcom{It used to say ``fusion'' of two spherical Schubert varieties, but we are using the word fusion just for the central fibre, so we need a different name.} 
-\acom{Family is good. We should put BD on p. 4.}
+% \jcom{It used to say ``fusion'' of two spherical Schubert varieties, but we are using the word fusion just for the central fibre, so we need a different name.} 
+% \acom{Family is good. We should put BD on p. 4.}
 % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
@@
 % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
-By a Theorem of Zhu \cite[Proposition 3.1.14]{zhu2016introduction}, $ \overline{\Gr}^{\lambda'} \ast_0 \overline{\Gr}^{\lambda''} $ is reduced and equal to  $ \overline{\Gr}^{\lambda' + \lambda''}$.
+By a Theorem of Zhu, $ \overline{\Gr}^{\lambda'} \geofu \overline{\Gr}^{\lambda''} $ is reduced and equal to $ \overline{\Gr}^{\lambda' + \lambda''}$ \cite[Proposition 3.1.14]{zhu2016introduction}.
 % Suppose that $ s \ne 0$.  
-If $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''} =  \Gr^{\lambda'} \ast_s \Gr^{\lambda''} $
-% \acom{reference \cref{it:grs-gr}?} 
-This open locus is a $ G(\CC[t])$-orbit
+If $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''} =  \Gr^{\lambda'} \bdfamf \Gr^{\lambda''} $ a $ G(\CC[t])$-orbit
 % .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
@@
 % \acom{Why $G(\CC[t])$. Because we are on the left side!}
-
 % \acom{Sorry I keep changing (abbreviating) ``By a theorem of Zhu'', but is the citation not sufficient?}
@@
 % \acom{Ok}
-
+% 
 Because we consider effective dominant coweights, the spherical Schubert varieties and their fusions lie in the positive part of the (thick) affine Grassmannian.
@@
 
-Now fix two effective (possibly non-dominant) coweights $ \mu', \mu''$ of sizes $N',N''$ such that $ \mu = \mu' + \mu'' $ is dominant. 
+% Now fix two effective (possibly non-dominant) coweights $ \mu', \mu''$ of sizes $N',N''$ such that $ \mu = \mu' + \mu'' $ is dominant. 
 % (We do not require $ \mu', \mu'' $ to be dominant.) 
-Using $ \mu, \mu', \mu''$, we define the following subschemes.
+% Using $ \mu, \mu', \mu''$, we define the following subschemes.
 
@@
 %
+
+\acom{Comment why the above doesn't make sense for $\mu$ not dominant?}
 
@@
 \begin{definition} 
-\label{def:inftyorbits}
-    The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $ and the \new{family of two semi-infinite orbits} 
+\label{def:inftyorbit}
+    The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $
+\end{definition}
+\acom{and its closure?}
+\begin{definition} 
+\label{def:inftyorbitfam}
+    The \new{family of two semi-infinite orbits} 
  $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
- which we define to have fibres $ S^{\mu'} \ast_s S^{\mu''}_s $ for $ s \ne 0$ and fibre $ S^{\mu}$ over $ s = 0 $.
+ which we define to have fibres $ S^{\mu', \mu''}_{0,s} \cong S^{\mu'}\times S^{\mu''} $ for $ s \ne 0$ and fibre $ S^{\mu}$ over $ s = 0 $.
 \end{definition}
@@
 If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
+
+\acom{Don't we want this to be the definition?}
 $$
@@
 $$
-See section 5.2 of \cite{baumann2020bases} for further details.
+See \cite[Section~5.2]{baumann2020bases} for further details.
 
@@
 % 
-We now consider some subvarieties of the space of $ N\times N$ matrices, again using the $ \lambda, \lambda', \lambda'', \mu, \mu', \mu''$ defined in the previous section.
+We now consider some subvarieties of the space of $ N\times N$ matrices, again using the coweights $ \lambda, \lambda', \lambda'', \mu, \mu', \mu''$ fixed in the previous section. 
 Recall that $\lambda, \mu $ are partitions of $ N$.
 
-Given $ s \in \AA$ we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
+Given a point $ s \in \AA$ we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
 
@@
 We will now describe these fibres.
-\acom{departing slightly from ES's lingo/notations..}
+% departing slightly from the notation of \cite{eisenbud1989rank}.
 
@@
 $$
-\jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
-\acom{I don't think that there is any need to swap back.
+% \jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
+% \acom{I don't think that there is any need to swap back.
 But maybe we could use $c$ (for column) isntead of $i$, since we use $i$ in the same context quite a bit to denote a letter in the alphabet $\{1,\dots,m\}$.}
-\jcom{Sure, that is a good idea.}
-\acom{Ok, switched some letters. Think $d$ is good as `delta'.}
+% \jcom{Sure, that is a good idea.}
+% \acom{Ok, switched some letters. Think $d$ is good as `delta'.}
 %\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
@@
 \]
-for some $A_{ij}^k\in\AA$. 
+for some $A_{ij}^k\in\CC$. 
 % \[
@@
 % $ g(A) = \left( g(A)_{ij} \right)$ 
-$g(A)$ in $ M_m(\AA[t]) $ whose $(i,j)$th entry is defined as follows.
+$g(A)$ in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
 \begin{equation}
@@
 
-In other words, the $ \mu_i\times\mu_j$ block of $ A $ is used to produce a polynomial which is inserted in the $(j,i)$ entry of $ g(A)$.
+In other words, the $ \mu_i\times\mu_j$ block of $ A $ is used to produce a polynomial which is inserted in the $(j,i)$ entry of the $m\times m$ matrix $ g(A)$.
 
 In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.
-\begin{definition} The ``\new{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
+\begin{definition} The \new{upper-triangular} \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $ is defined by
 $$
@@
 \end{definition}
-So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
+So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $\{t^{\mu'_{i}} (t-s)^{\mu''_{i}} : i=1,\dots,m\}$.
 
@@
 \label{le:linalg} % aka solution 
-Let $ V $ be a $ \CC[t]$-module which is finite-dimensional as a $ \CC$ vector space.  For any  $ a \in \CC$, the map
+Let $ V $ be a $ \CC[t]$-module which is finite-dimensional as a complex vector space.  For any  $ a \in \AA$, the map
 $$ 
@@
 \begin{proof}
-    For any $ b \in \CC$, let $ E_b $ denote the generalized $b$-eigenspace of $t$.
+    For any $ b \in \AA$, let $ E_b $ denote the generalized $b$-eigenspace of $t$.
 Then $ V = \oplus_{b \in \CC} E_b$.
@@
 
-    Fix $ i$ and suppose that for some $ j$, $ \mu_j < \mu_i$.
-In this case, we can alter our basis to $ v'_i = v_i - r v_j$ for some polynomial $r \in \CC[t]$.
-This gives us new polynomials $ p'_{ij} = p_{ij} - r (t^{\mu_j} + p_{jj}) $.
-In this way, we can ensure that $ p_{ij} $ has degree less than $ \min(\mu_i, \mu_j)$.
+    Fix $ i$ and suppose that for some $ j$, $ \mu_j < \mu_i$.  In this case, we can alter our basis to $ v'_i = v_i - r v_j$ for some polynomial $r \in \CC[t]$.  
+    \acom{More like a quotient than a remainder, better $q$ than $r$?}
+    This gives us new polynomials $ p'_{ij} = p_{ij} - r (t^{\mu_j} + p_{jj}) $.  In this way, we can ensure that $ p_{ij} $ has degree less than $ \min(\mu_i, \mu_j)$.  
     Thus \cref{it:slice} implies \cref{it:basis}.
@@
 It is easy to see that $ L = \Sp_\cO(v_1, \dots, v_m) $ and so $ L \in \cW_\mu$.
-
-    To show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, $ t^{\mu_i} e_i  \in \Sp_\CC(  t^k e_i : 0 \le k < \mu_i, 1 \le i \le m) + L$. 
+    % 
+    To show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, 
+    $$ t^{\mu_i} e_i  \in \Sp_\CC(  t^k e_i : 0 \le k < \mu_i, 1 \le i \le m) + L\,.$$
     % 
@@
 Note that $ h \in T_1(\Oinf)$.
-    Moreover,
-    $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
-    Note that 
+    Moreover, $L = h (h^{-1} g h) t^{\mu}\CC[t]^m$. 
+    % $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
+    Since 
     % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
-    $h^{-1} g h \in N_-(\cK_\infty)$ and so we can factor $ h^{-1} g h$ as $n_1 n_2$ for some $ n_1 \in {(N_-)}_1(\Oinf), n_2 \in {N_-}(\CC[t]) $.
-
-    Since $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t]) $. % \CC\xt[t^{-1}]s
+    $h^{-1} g h \in N_-(\cK_\infty)$ we can factor $ h^{-1} g h$ as $n_1 n_2$ for some $ n_1 \in {(N_-)}_1(\Oinf), n_2 \in {N_-}(\CC[t]) $.
+
+    As $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t]) $, and so 
+     % \CC\xt[t^{-1}]s
     % 
@@
     % 
-    Thus, $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
+    $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
 \end{proof}
@@
 The following result is called the Mirkovic--Vybornov isomorphism \cite{mirkovic2007quiver}.
-In the following form, it can be found in \cite[Theorem 3.2]{cautis2018categorical}, except that we have tweaked both maps with a matrix transpose $ \tr$.
-
-\jcom{I'm not sure which of the Mirkovic--Vybornov papers to cite.} \acom{can say 07, rewritten in 19?}
+In the following form, it can be found in \cite[Theorem 3.2]{cautis2018categorical}, except that we have tweaked both maps with a matrix transpose $[?]^\tr$.
+
+% \jcom{I'm not sure which of the Mirkovic--Vybornov papers to cite.} \acom{can say 07, rewritten in 19?}
 % 
@@
 % lattice).
-In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$. 
+In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective \acom{emphasis is on the almost injectivity/glass half full no?} map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$.
 % (for example the fibre of this map over $ 0 $ is $ \CC $). 
@@
 
-The following refinement of Mirkovic-Vybornov isomorphism is a special case of \cite[Theorem 5.3]{mirkovic2007quiver}.
+The following refinement of the \mvy isomorphism is a special case of \cite[Theorem 5.3]{mirkovic2007quiver}. \acom{Wait isn't 5.3 a special case of this?}
 \begin{theorem} 
@@
 \begin{proof}
-We could prove this by observing the both sides are the attracting locus of an appropriate $ \AA^\times$ action. However, we will give the following more algebraic proof.
+We could prove this by observing the both sides are the attracting locus of an appropriate $ \Cx$ action. However, we will give the following more algebraic proof.
 
@@
 
-Restricting to the zero fibre and applying $\theta_0$ we recover \cite[Corollary~5.2.2]{dthesis}. 
+Restricting to the zero fibre and applying $\theta_0$ together with \Cref{prop:adjoint} we recover a result of the second author. 
 %itself a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}, the ordinary affine Grassmannian version of \Cref{th:OGrl}. 
@@
 \begin{corollary}
-    \label{cor:mvy}
-The map $ A \mapsto g(A)\OO^m$ gives an isomorphism    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu_-$.
+    \label{cor:mvy} (\cite[Corollary~5.2.2]{dthesis})
+The map $ A \mapsto g(A)\cO^m$ gives an isomorphism 
+$$\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu_-\,.$$
 \end{corollary}
+% 
 %The closures of the irreducible components of the righthand side are \new{MV cycles of type $\lambda$ and weight $\mu$}.
@@
 \subsection{MV cycles}
-Let $\lambda\ge\mu$ be dominant effective and effective coweights of $\GL_m$ respectively. 
+Continuing with the notation of the previous sections we add the assumption that $\lambda\ge\mu$ and forget the assumption that $\mu$ is dominant. 
 % 
@@
 The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \new{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
-\acom{For Joel: weight or filling? See line below.}
+% \acom{For Joel: weight or filling? See line below.}
 $$
@@
 
-The following result is closely related to Theorem 4 from \cite{dranowski2020generalized}.
+The following result is closely related to  Theorem 5.4.3.
+from \cite{dthesis}.
 It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2004mirkovic} (see Section 9 in \cite{kamnitzer2010mirkovic}).
-A different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.
+We remeark that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.
 
@@
 \begin{proof}
-    The proof of this theorem follows the same strategy as in \cite{dranowski2020generalized}.
+    The proof of this theorem follows the same strategy as in \cite{dthesis}.
 % \jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}    
@@
 equals $|YT^\lambda_\mu|$, thus on the left hand side, each $ \mathring Z(\tau)$ can only have one irreducible component of dimension $ \rho(\lambda - \mu)$.
-
+% 
 %\jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}
-
+% 
 % See computation 5.3.9 and Lemma 5.4.2 (ignore its proof) of \url{http://www.math.toronto.edu/adranows/athesis.pdf}. 
@@
 \end{lemma}
-\jcom{We should add a proof here.  It will be very similar to Prop 5 below.} \acom{Ca marche?}
-\jcom{Oui.  J'ai fait des petites revisions.}
+% \jcom{We should add a proof here.  It will be very similar to Prop 5 below.} \acom{Ca marche?}
+% \jcom{Oui.  J'ai fait des petites revisions.}
 \begin{proof}
@@
 It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu \cap \n$ and will be called a \new{generalized orbital variety}.
-
-\jcom{We should give a more specific citation to \cite{dthesis} here and below.
+% 
+% \jcom{We should give a more specific citation to \cite{dthesis} here and below.
 Also, throughout this paper, we should either cite your paper or your thesis, but not both (unless there is a very good reason to do so).
@@
 Feel free to add a bit more exposition.}
-\acom{Just posted to arXiv. Will re-ref shortly. Also made citation more specific.}
-
+% \acom{Just posted to arXiv. Will re-ref shortly. Also made citation more specific.}
+% 
 In fact, these are all the generalized orbital varieties:
@@
     \label{pr:govsasirrecs}
-    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
+    $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$ is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
 \end{theorem}
@@
 % 
-Let $\lambda',\lambda''$ be dominant effective and $\mu',\mu''$ effective such that $\lambda = \lambda' + \lambda''$ and $\mu = \mu' + \mu''$ as in previous sections.
-\jcom{I think that this is can move earlier, with the caveat that I mentioned earlier about $ \mu $ being non-dominant in 6.1 and dominant here.} \acom{Yes.} \acom{But we only start to need the primes now.}
-
-% 
-Given $s\in\AA^\times$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
+Let $\lambda,\lambda',\lambda''$ and $\mu \mu',\mu''$ be as in previous sections, once again assuming that $\mu$ is dominant.
+% \jcom{I think that this is can move earlier, with the caveat that I mentioned earlier about $ \mu $ being non-dominant in 6.1 and dominant here.} \acom{Yes.} \acom{But we only start to need the primes now.}
+
+% 
+Given $s\in\Ax$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
 % 
@@
     \label{pr:XttZtt}
-    The image of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_\Cx \mathring Z(\tau''))$. 
+    The image of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_\Cx \mathring Z(\tau'')$. 
     % \[
@@
 
-Now, in analogy with the Beilinson--Drinfeld fusion construction of \Cref{ss:fuscon}
+Now, in analogy with the geometric fusion of \Cref{ss:fuscon}
 % \acom{add loc cit} \jcom{I think just add a reference our fusion section} \acom{Yeah that's what I meant, taking loc cit literally}
 we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ in $M_N(\CC)\times\CC$.
-% 
+By \Cref{prop:adjoint} it is contained in $\overline\OO^\lambda\cap\TT_\mu\cap\n$, so by Theorem 4 its irreducible components are generalized orbital varieties.
+%
+
+\acom{Recalling intersection multiplicity:}
+
+We have the zero fibre in $\Grbd$ as effective divisor $D$, and the fusion of subscheme $V = X\ast_\AA Y\subset\Grbd$ as a finite-dimensional irreducible variety not contained in the support of $D$, and finally an irreducible component $Z$ of $D\cdot V = X\ast_0 Y$, codimension 1 in $V$.
+Denote by $\iota(Z,D\cdot V)$ the intersection multiplicity of $Z$.
 \begin{corollary}
@@
 %  
-\acom{Hm, I guess you are right, it is easier than what I had, we just need that the arguments on either side match up, and not that the arguments on one side are related.
+% \acom{Hm, I guess you are right, it is easier than what I had, we just need that the arguments on either side match up, and not that the arguments on one side are related.
 Though do we really not use that $X(\tau)$ may be contained in $X(\tau',\tau'')_{0,0}$ as an irreducible component?}
@@
 % 
+\acom{A tuppence about this conjecture?}
 \begin{conjecture}
@@
 \subsection{Connection to cluster structure on $\CC[N]$}
-\jcom{Maybe we need a word about Langlands duality here.
-Since we are working with $ GL_m$, it is not really necessary, but it would be nice to point this out.
+\jcom{Maybe we need a word about Langlands duality here.  Since we are working with $ GL_m$, it is not really necessary, but it would be nice to point this out.  
 Also a general comment: maybe it would be best to first talk about multiplication in $\CC[N]$ incl.
@@
 % 
-\acom{Recalling intersection multiplicity:} 
-We have the zero fibre in $\Grbd$ as effective divisor $D$, and the fusion of subscheme $V = X\ast_\AA Y\subset\Grbd$ as a finite-dimensional irreducible variety not contained in the support of $D$, and finally an irreducible component $Z$ of $D\cdot V = X\ast_0 Y$, codimension 1 in $V$.
-Denote by $\iota(Z,D\cdot V)$ the intersection multiplicity of $Z$.
-% 
 The structure constants of $\CC[N]$ with respect to the MV basis are given by intersection multiplicities. 
@@
 
-\acom{To quote from BFZ for a concise definition: Cluster algebras are a class of commutative rings defined axiomatically in terms of a distinguished family of generators called cluster variables.
-Say also what is a seed, what is a mutation, what is a cluster, what is a cluster monomial, and finally for the stubbornly ignorant clarify that 'the cluster monomials' refers to cluster monomials for all possible clusters!}
-
-$\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
-% that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
-
-\acom{Background on cluster:}
-In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
-This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
-Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
-
-In the appendix to \cite{baumann2019mirkovic} the second and third author along with Morton-Ferguson check that the MV basis differs from the dual semicanonical basis (at the Kashiwara--Saito counterexample).
-Yet, the two bases have enough in common (c.f.\ BKT,...?), that we have the following conjecture.
-
-\begin{conjecture}
-    The dual semicanonical basis and the MV basis overlap on the cluster monomials. In particular, the cluster monomials are contained in the MV basis. 
-\end{conjecture}
-
-We note that both of these bases are \new{biperfect} bases of $\CC[N]$ and in type $A_n$ with $n\le 3$ there is a unique biperfect basis of $\CC[N]$.
-
+\section{Cluster questions}
+\label{s:clusterqus}
+% 
 For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor  \cite{kato2011polytopal}, and hence
@@
 
+\subsection{Type $A_2$}
+
 \begin{example}
@@
 
+\subsection{Type $A_3$}
+
 Let $G = \GL_4$.
@@
 
-\acom{Add dominant version column}
+% \acom{Add dominant version column}
 % \jcom{This is a nice table.  But these are the coordinate rings of $ X(\tau)$, not of $ Z(\tau) $.}
 % \renewcommand{\arraystretch}{1.5}
-\begin{table}[ht!]
+\begin{table}[ht!]%[H]
   \centering
@@
 \end{table}
+\acom{Say what $x_i$ are: $\begin{bmatrix}
+    1 & x_1 & x_2 & x_3 \\
+    & 1 \\
+    & & 1 \\
+    & & & 1 
+\end{bmatrix}$}
+
 % \[

### 2021-06-03 draft.tex
joels last changes

@@
     \item Formatting could be bit better, e.g.\ some stuff goes outside the margin
+    \item Fix section titles and other organizational seasoning  
     \item Fix numbering so that theorems, defs etc share a counter and are restarted by section 
@@
 % 
-Throughout this paper (unless indicated otherwise) the base field is $\CC$, but it does not have to be?
+%Throughout this paper (unless indicated otherwise) the base field is $\CC$, but it does not have to be?
+
+The geometric Satake equivalence of Mirkovic-Vilonen \cite{mirkovic2007geometric} provided an equivalence of categories between the category of spherical perverse sheaves in the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.
+This foundational result provides a powerful tool to study representation theory using geometry.
+In particular, under this equivalence, the Mirkovic-Vilonen cycles in the affine Grassmannian of $ G $ index bases for irreducible representations of $ G^\vee $.
+In this paper we work with $ G =GL_m$ and identify $ G^\vee = GL_m$ as well.
 
@@
 and to Nakajima quiver varieties on the other hand.
-This paper generalizes the first of these relations (an isomorphism) to families of slices in the Beilinson--Drinfeld Grassmannian. 
-Essential to \cite{mirkovic2007geometric}, this space is used to define a fusion (aka convolution) product on sheaves (representations) but can also be used to define a fusion product on certain cycles (bases).
-% 
-This product structure makes the vector space spanned by the Mirkovi\'c--Vilonen cycles into a commutative algebra isomorphic to the ring of functions on the unipotent subgroup (conjectured in \cite{anderson2003polytope} and proved in \cite{baumann2019mirkovic}).
-% conjectured by JEA and proved by BKK
-% 
-To quote from \cite{mirkovic2007geometric}:
-\begin{quotation}
-    However, we make crucial use of an idea of Drinfeld, going back to around 1990.
+This extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of matrices with two eigenvalues.
+Via this equivalence, the Mirkovic-Vilonen cycles are identified with certain varieties of matrices, called generalized orbital varieties (see \cite{dthesis}).
+%This paper generalizes the first of these relations (an isomorphism) to families of slices in the Beilinson--Drinfeld Grassmannian.
+\jcom{I changed this because MVy did consider the BD Grassmannian as well.}
+
+Essential to \cite{mirkovic2007geometric}, the Beilinson-Drinfeld Grassmannian is used to define a fusion product on the category of spherical perverse sheaves on the affine Grassmannian.
+In \cite{anderson2003polytope}, Anderson used the BD Grassmannian to define a fusion of Mirkovic-Vilonen cycles.
+He conjectured that this fusion product matches the muliplication in the coordinate ring of the unipotent subgroup $ N \subset GL_m$.
+This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that these MV cycles give a basis for $ \CC[N]$.
+% 
+%To quote from \cite{mirkovic2007geometric}:
+%\begin{quotation}
+%    However, we make crucial use of an idea of Drinfeld, going back to around 1990.
 He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
-\end{quotation}
-%
-The purpose of this paper is to give a conceptually elementary way to compute this product in type $A$.
-We do not know how fruitful this work might be in the larger landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is computationally expensive.
-%
-
-One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!
+%\end{quotation}
+%
+
+Unfortunately, performing computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.
+A few such computations were done by Anderson-Kogan in \cite{anderson2006algebra} in a somewhat ad-hoc fashion.
+
+The purpose of this paper is to give a conceptually elementary way to compute this product by transferring it to a fusion product of generalized orbital varieties.  Our main result is the following.
+
+\begin{theorem}
+    Let $ Z, Z' $ be MV cycles.
+The structure constants for the multiplication of $ b_Z b_{Z'}$ in $\CC[N]$ are equal to the intersection multiplicities in the fusion of the generalized orbital varieties corresponding to $ Z, Z'$.
+\end{theorem}
+% 
+\jcom{I wanted to state a precise theorem, but it is not so easy without introducing a lot of notation.}
+
+%One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!
 
@@
 \acom{Comment why the above doesn't make sense for $\mu$ not dominant?}
+\jcom{It does make sense when $ \mu $ is not dominant.
+The reason for restricting to dominant $ \mu $ is so that $ S^\mu \subset \cW^\mu$.
+I agree that we should mention this, but I'm not sure where.}
 
@@
 \acom{and its closure?}
+\jcom{I don't think that we use the closure in this paper, do we?}
 \begin{definition} 
@@
 % lattice).
-In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the non-injective \acom{emphasis is on the almost injectivity/glass half full no?} map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$.
+In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the ``almost injective'' \acom{emphasis is on the almost injectivity/glass half full no?} \jcom{ok, I changed it} map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$.
 % (for example the fibre of this map over $ 0 $ is $ \CC $). 
@@
 
-The following refinement of the \mvy isomorphism is a special case of \cite[Theorem 5.3]{mirkovic2007quiver}. \acom{Wait isn't 5.3 a special case of this?}
+The following refinement of the \mvy isomorphism is a special case of \cite[Theorem 5.3]{mirkovic2007quiver}.
+\acom{Wait isn't 5.3 a special case of this?}  \jcom{No, they deal with the more general setting of more points.}
 \begin{theorem} 
@@
 We record the following easy observations.
-\begin{lemma} \label{le:rdimTrans} Let $ L \in \Gr_+$ \acom{(or $\Grth_+$)}.
+\begin{lemma} \label{le:rdimTrans} Let $ L \in \Gr_+$ or $\Grth_+$.
 \begin{enumerate}
@@
 
-For any $ L \in \Gr_+ $ \acom{(or $\Grth_+$)} and $\gamma \subset [m]$, we define $ D_\gamma(L) := \rdim L^\gamma = \rdim L - \rdim L_{\gamma^c}$.
-(By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.)
+For any $ L \in \Gr_+ $ and $\gamma \subset [m]$, we define $ D_\gamma(L) := \rdim L^\gamma = \rdim L - \rdim L_{\gamma^c}$.
+(By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper; in \textit{loc.
+cit.} these functions are used to compute the hyperplanes of the associated MV polytopes.)
 % \acom{We should introduce $D_\gamma$ briefly.}
@@
 
-\section{Denouement}
-\label{s:denouement}
-\subsection{Examples}
+\section{Examples}
+\label{s:examples}
 

### 2021-06-03 draft.tex
so slow moving with section 7

@@
 \subsection{MV cycles}
-Continuing with the notation of the previous sections we add the assumption that $\lambda\ge\mu$ and forget the assumption that $\mu$ is dominant. 
+Let $Q_+$ denote the $\ZZ_{\ge 0}$-span of the positive coroots. 
+Recall the \new{dominance order} on $\ZZ^m$ defined by declaring that $\mu\le\lambda$ if $\lambda - \mu\in Q_+$ for any $\lambda,\mu$.
+
+Continuing now with the notation of the previous sections we add the assumption that $\mu\le\lambda$ and forget the assumption that $\mu$ is dominant. 
 % 
@@
 
-By \cite[Theorem~3.2(b)]{mirkovic2007geometric}, each MV cycle has in $\overline\Gr^\lambda$ of coweight $\mu$ has dimension $ \rho(\lambda - \mu)$ where $\rho$ is the half sum of positive roots.
+By \cite[Theorem~3.2(b)]{mirkovic2007geometric}, each MV cycle in $\overline\Gr^\lambda$ of coweight $\mu$ has dimension $ \rho(\lambda - \mu)$ where $\rho$ is the half sum of positive roots.
 Normalizing $ \rho = (m, m-1, \dots, 1)$ and identifying $P \cong P^\vee$ the pairing $P\times P^\vee\to\ZZ $ is given by the ordinary dot product.
+We denote by $\cZ(\lambda)$ the collection of all MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$.
 
@@
 
-In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic--Vilonen polytopes, or equivalently Lusztig data, which are sequences in $\NN^{\Delta_+}$ which depend on a choice of reduced expression.
+In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic--Vilonen polytopes, or equivalently Lusztig data, which are sequences in $\NN^{\Delta_+}$ that depend on a choice of reduced expression.
 For $\GL_m$ and the standard reduced word, this description can be reworded in terms of Young tableaux.
@@
 
-We now introduce some notation related to Young tableaux. Denote by $YT(\lambda)_\mu$ the set of (possibly semistandard) Young tableaux of shape $\lambda$ and weight $\mu$. 
+We now introduce some notation related to Young tableaux.
+Denote by $YT(\lambda)$ the set of (possibly semi-standard) Young tableaux of shape $\lambda$ and by $YT(\lambda)_\mu$ the subset of $YT(\lambda)$ of tableaux having weight $\mu$.
 %Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
@@
 % 
-\subsection{Connection to cluster structure on $\CC[N]$}
-\jcom{Maybe we need a word about Langlands duality here.  Since we are working with $ GL_m$, it is not really necessary, but it would be nice to point this out.  
-Also a general comment: maybe it would be best to first talk about multiplication in $\CC[N]$ incl.
+\subsection{Representations in $\CC[N]$}
+\label{ss:CN}
+% 
+% \jcom{
+% Maybe we need a word about Langlands duality here.  Since we are working with $ GL_m$, it is not really necessary, but it would be nice to point this out.  
+% Also a general comment: maybe it would be best to first talk about multiplication in $\CC[N]$ incl.
 Theorem 7.11 from mvbasis, and then talk about cluster algebras.
 Right now, it is a bit confusing, since we go back and forth.
-Also some of the motivation stuff about the semicanonical basis, etc, will be moved to the intro.}
+Also some of the motivation stuff about the semicanonical basis, etc, will be moved to the intro.
+% }
+In this section we will need to recall that representations of the Langlands dual group $G^\vee$ of an arbitrary complex reductive group $G$ can be constructed from the affine Grassmannian of $G$, and studied in $\CC[N^\vee]$ the ring of functions on the maximal unipotent subgroup $N^\vee$ of $G^\vee$.
+%
+
+We use the convenient fact that $\GL_m^\vee = \GL_m$ and ignore the distinction, referring to points $t^\lambda$ as coweights for $\lambda\in\ZZ^m$ weights. 
+%
+
+\acom{So far we have been saying ``coweight'' $\lambda$, etc.
+We could say coweight for $t^\lambda$ and weight for $\lambda$ starting now?
+Also, maybe add a warning that some of the theorems we rely on hold more generally?
+Like the MV basis theorem..}
 
@@
 In \cite{baumann2019mirkovic} the third author along with Baumann and Knutson show that the MV cycles yield a basis of the coordinate ring $\CC[N]$ called the MV basis.
+Note that with respect to the action of the maximal torus $T$ of $\GL_m$ by conjugation on $N$, $\CC[N]$ acquires a homogeneous grading by $Q_+$.
 % 
@@
 
-Given $\lambda\ge\mu\in\ZZ^m$ with $\lambda$ dominant, denote by $V(\lambda)$ the irreducible representation of $\GL_m$ of highest weight $\lambda$ and by $V(\lambda)_\mu$ its $\mu$-weight space. 
-There is an injective map $ \Psi_\lambda: V(\lambda) \to \CC[N]$ realizing $V(\lambda)$ as a subspace of $\CC[N]$.
+Given weights $\mu\le\lambda$ with $\lambda$ dominant, denote by $V(\lambda)$ the irreducible representation of $\GL_m$ of highest weight $\lambda$ and by $V(\lambda)_\mu$ its $\mu$-weight space. 
+There is an injective map $ \Psi_\lambda: V(\lambda) \to \CC[N]$ realizing $V(\lambda)$ as a subspace of $\CC[N]$ and sending $v\in V(\lambda)_\mu$ to $\CC[N]_{\mu - \lambda}$.
 
@@
 $V(\lambda)_\mu = H_{2\rho(\lambda-\mu)}(\overline{\Gr^\lambda\cap S^\mu_-})$ where $H_d$ denotes $d$-dimensional Borel--Moore homology.
-In particular, the MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$ give a basis of $V(\lambda)$. We denote this set of MV cycles $\cZ(\lambda)$, $\{[Z] : ..  \}$.
-\acom{$\cZ(\lambda)$ can go earlier}
-%
-
-Let $Q_+$ denote the set of nonnegative integer combinations of positive roots. \acom{$Q_+$ should be defined earlier?}
+In particular, the set $\{[Z] : Z\in\cZ(\lambda)\}$ gives a basis of $V(\lambda)$ with $[Z]$ denoting the class of $Z$ in the appropriate homology group.
+
+\acom{Warning! Earlier we defined the MV cycles as irreducible components of $\overline{\Gr^\lambda}\cap S^\mu$}
+% In particular, the MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$ give a basis of $V(\lambda)$. 
+%
+
 The \new{stable} MV cycles of coweight $\nu\in Q_+$ are defined to be irreducible components of $\overline{S^0_+ \cap S^\nu_-}$.
-By a theorem of Anderson, MV cycles in $\overline{\Gr^\lambda\cap S^{\nu + \lambda}_-}$ are in bijection with stable MV cycles of coweight $\nu$ that are contained in $\overline\Gr^\lambda$.
+By a theorem of Anderson, MV cycles in $\overline{\Gr^\lambda\cap S^{\nu + \lambda}_-}$ are in bijection with stable MV cycles of coweight $\nu$ that are contained in $\overline\Gr^\lambda$ \cite[Proposition~3]{anderson2003polytope}.
 We denote the set of all stable MV cycles $\cZ(\infty)$.
+% Recall that MV cycles can be described combinatorially by Lusztig data. 
+By a theorem of the third author, a stable MV cycle is uniquely determined by its Lusztig datum and the sets $\cZ(\infty)$ and $\NN^{\Delta_+}$ are in bijection. 
+% Recall that Lusztig data, like elements of $\CC[N]$, are weighted by $Q_+$. 
+With a little bit more work one can string together the maps $\Psi_\lambda$ and the geometric Satake isomoprhisms to show that the stable MV cycles yield a basis of $\CC[N]$.
 
 \begin{theorem}
-    (BKK~Proposition 6.1)
-    For each $Z\in\cZ(\infty)$ there is a unique element $b_Z\in\CC[N]$ such that for any $\lambda$ dominant, if $t^\lambda Z\in\cZ(\lambda)$ then $\Psi_\lambda([t^\lambda Z]) = b_Z$ and the collection of all such elements is called the \new{MV basis}.
+    (A special case of \cite[Proposition~6.1]{baumann2019mirkovic})
+    For each $Z\in\cZ(\infty)$ there is a unique element $b_Z\in\CC[N]$ such that for any dominant weight $\lambda$, if $t^\lambda Z\in\cZ(\lambda)$ then $\Psi_\lambda([t^\lambda Z]) = b_Z$ and the collection of all such elements is called the \new{MV basis}.
 \end{theorem}
-
+% 
+Furthermore, the structure constants of multiplication in $\CC[N]$ with respect to the MV basis are given by intersection multiplicities. 
+% 
+\begin{theorem}
+    (A special case of \cite[Theorem~7.11]{baumann2019mirkovic}) Given $Z',Z''\in\cZ(\infty)$, 
+    % of coweight $\nu',\nu''$ respectively 
+$$
+b_{Z'}\arfu b_{Z''} = \sum_{Z\in\cZ(\infty)} \iota\left(Z, Z' \geofu Z''\right) b_Z 
+$$
+in $\CC[N]$. \acom{The summation is finite since 7.1?... Don't want to introduce the notation $\cZ(\infty)_\nu$ if we can avoid it.}
+Moreover, there exist $\lambda',\lambda''$ dominant effective and a pair of tableaux $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$ such that 
+\begin{equation}
+    \label{eq:multingovs}
+    % b_{Z'} \arfu b_{Z''} = \sum_{Z\in\cZ(\lambda)} \iota (Z, Z(\tau')\geofu Z(\tau''))b_{t^{-\lambda}Z}
+    b_{Z'} \arfu b_{Z''} = \sum_{\tau\in YT(\lambda)} \iota (X(\tau), X(\tau',\tau'')_{0,0})b_{t^{-\lambda}Z(\tau)}
+\end{equation}
+% 
+for $\lambda = \lambda' + \lambda''$. 
+\end{theorem}
 % Given $\epsilon\in\ZZ^m$ denote by $t^\epsilon:V(\lambda) \to V(\lambda + \epsilon)$ the map resulting from multiplication by the coweight $t^\epsilon$ in $\Gr$.
 By BKK, $\Psi_{\lambda + \epsilon} \circ t^\epsilon - \Psi_\lambda = 0$.
-
+% 
 % Together these facts imply the following commutative square.
@@
 % \]
-\jcom{This paragraph is a bit confusing.
+% \jcom{This paragraph is a bit confusing.
 Maybe it would be best to first define $ V(\lambda) \rightarrow \CC[N]$ and then $ H_{top}(\overline{Gr}^\lambda \cap S^\mu) \rightarrow \CC[N]$, rather than doing them in one step.
@@
 }
-\acom{Not sure which square to draw or if it is necessary.
+% \acom{Not sure which square to draw or if it is necessary.
 I guess you want something like what's pictured below, where what we're about to describe are the blue arrows.
@@
 Which, by commutativity, will determine the middle downward pointing blue.}
-\jcom{Yes, I like this diagram.  Maybe the two rightward arrow should point leftward, since we did already define $ \tau \mapsto Z(\tau)$.}
-
+% \jcom{Yes, I like this diagram.  Maybe the two rightward arrow should point leftward, since we did already define $ \tau \mapsto Z(\tau)$.}
+% 
+In \Cref{s:examples} we will identify elements $b_Z$ with certain \textit{minimal} tableaux (instead of Lusztig data) and view $\CC[N]$ as an algebra in these tableaux, abbreviating \Cref{eq:multingovs} as equation in these tableaux.
+
+Before we describe how to choose representative generalized orbital varieties in order to expand a product of MV basis elements $b_{Z'}\arfu b_{Z''}$ in $\CC[N]$ we summarize our approach in the following commutative diagram.
 \[
+% \begin{tikzcd}
+% \CC[N] & \ar[l] \cZ(\infty) \ar[r,"n_\bullet"] \ar[d,bend left,blue] & \NN^{\Delta_+} \ar[l,blue,bend left] \ar[d,bend left,blue]\\ 
+% L(\lambda) \ar[u,"\Psi_\lambda"] & \ar[l] \cZ(\lambda) \ar[r] \ar[u,"t^{-\lambda}"] & YT(\lambda) \ar[u,"n_\bullet"] \ar[l,blue,bend left]
+% \end{tikzcd}
 \begin{tikzcd}
-\CC[N] & \ar[l] \cZ(\infty) \ar[r,"n_\bullet"] \ar[d,bend left,blue] & \NN^{\Delta_+} \ar[l,blue,bend left] \ar[d,bend left,blue]\\ 
-L(\lambda) \ar[u,"\Psi_\lambda"] & \ar[l] \cZ(\lambda) \ar[r] \ar[u,"t^{-\lambda}"] & YT(\lambda) \ar[u,"n_\bullet"] \ar[l,blue,bend left]
+    YT(\lambda) \ar[r] \ar[d,"n_\bullet"] & \cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & L(\lambda) \ar[d, "\Psi_\lambda"] \\ %  description
+    \NN^{\Delta_+} \ar[r] \ar[u,dashed,bend left,"\sigma_\lambda"] & \cZ(\infty) \ar[r] & \CC[N]
 \end{tikzcd}
 \]
-Explain that fibres contain tableaux related by padding.
-$Z(\tau)$ is defined even when $\mu$ is not dominant.
-We choose a section for which $\mu$ is dominant (Lemma 9) because $X(\tau)$ doesn't make sense when it isn't, but when we come back to $Z(\infty)$ we can renormalize so $\mu$ is not dominant.
-% 
-The structure constants of $\CC[N]$ with respect to the MV basis are given by intersection multiplicities. 
-%
-
-\begin{theorem}
-    (\cite[Theorem~7.11]{baumann2019mirkovic}) Given $Z',Z''\in\cZ(\infty)$ 
-    % of coweight $\nu',\nu''$ respectively 
-$$
-b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)} \iota\left(Z, Z' \ast_0 Z''\right) b_Z 
-$$
-where note the summation is finite since... \acom{Don't want to introduce the notation $\cZ(\infty)_\nu$ if we can avoid it.}
-Moreover, there exists $\lambda',\lambda''$ dominant effective and $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$  
-\[
-b_{Z'} b_{Z''} = \sum_{Z\in\cZ(\lambda' + \lambda'')} \iota (Z, Z(\tau')\ast_0 Z(\tau''))
-\]
-\end{theorem}
-\jcom{In principle, the notation $ Z' \ast_0 Z''$ has been defined, since we defined the fusion of any two subschemes of $ \Gr$.
+The fibres of $n_\bullet$ \acom{in $\cup YT(\lambda)$} contain tableaux related by padding. 
+While $Z(\tau)$ is defined even when $\mu$ is not dominant, $X(\tau)$ is not, and so we need to choose a section $\sigma_\lambda$ of $n_\bullet$ with image in the set of tableaux having dominant weight.
+%
+
+\acom{Should I adjust the diagram so that its from unions over $\lambda$}
+
+% \jcom{In principle, the notation $ Z' \ast_0 Z''$ has been defined, since we defined the fusion of any two subschemes of $ \Gr$.
 We should just note that the fusion of the stable MV cycles matches the fusion of MV cycles after translation by $ t^\lambda$.
@@
 
-\section{Cluster questions}
-\label{s:clusterqus}
-% 
-For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor  \cite{kato2011polytopal}, and hence
-% \acom{by BKK?}\rcom{I reworded it.} 
-is in the MV basis. 
-% as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
-\acom{what's the subscript $r$?
-also what're the last 2 citations for?
-Neither BFZ nor GLS link generalized minors and MV cycles}
-If the reduced expression satisfies a special condition, then cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
-
-Conversely, suppose we have a seed $(x_1,\dots,x_r)$ such that each $x_i$ is in the MV basis, i.e.\ for each $i$ there exists a stable MV cycle $Z_i$ such that $x_i = b_{Z_i}\in\CC[N]$.
-To show that all cluster variables
-% \acom{for this seed?}\rcom{No, all of them.} 
-are also in the MV basis it suffices to show that if $x_i$ is mutable then its mutation $x_i^*$ is also in the MV basis. This observation is based on the exchange relation:
-\[
-    x_i x_i^* = x_+ + x_- 
-\]
-where $x_+,x_-$ are monomials in $ (x_1, \dots, x_r)\setminus x_i$ determined by the cluster structure on $\CC[N]$. 
-% \acom{the structure of interest?
-or are all cluster structures on this ring the same?} \rcom{The structure is derived from an initial seed coming from a reduced word {\bf i}.
-Each of these are equivalent to each other.}
-So if we can find a stable MV cycle $Z_i^*$ such that $b_{Z_i}b_{Z_i^*} = x_+ + x_-$ for each $i$ then we will have checked the conjecture. 
-% \acom{And we do not need to assume the special condition of BGL?}\rcom{They deal with cluster monomials in certain clusters while this deals with all cluster variables, so neither one completely implies the other.}
-
-The following examples give evidence that the mutation $x_i^*$ is in the MV basis. \acom{Roger, reword?}\rcom{Something like this?} \acom{Sure!}
-
-% \jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
-% \acom{Begun}
-
-Before we begin we will need some lemmas, notions and notations. 
-\begin{itemize}
-    \item we have only seen how to fuse ordinary MV cycles; to mutliply MV basis vectors which are indexed by stable MV cycles we'll therefore need a way to represent stable by ordinary; hence:
-    \item a notion/choice of fission 
-    \item the fission lemmas 
-    \item with lemmas in hand, a proposition: given $Z',Z''$ stable with LD... there exist $\tau',\tau''$ (min) such that $b_{Z'} b_{Z''} = b(\tau')  b(\tau'')$
-    \item a shorthand: in examples, instead of writing $Z(\tau)$ for the MV cycle corresponding to the tableau $\tau$ we will only the tableau $\tau$! 
-\end{itemize}
 \begin{lemma}
@@
 \end{proposition}
+
+\section{Cluster questions}
+\label{s:clusterqus}
+% 
+For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor  \cite{kato2011polytopal}, and hence
+% \acom{by BKK?}\rcom{I reworded it.} 
+is in the MV basis. 
+% as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
+\acom{what's the subscript $r$?
+also what're the last 2 citations for?
+Neither BFZ nor GLS link generalized minors and MV cycles}
+If the reduced expression satisfies a special condition, then cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
+
+Conversely, suppose we have a seed $(x_1,\dots,x_r)$ such that each $x_i$ is in the MV basis, i.e.\ for each $i$ there exists a stable MV cycle $Z_i$ such that $x_i = b_{Z_i}\in\CC[N]$.
+To show that all cluster variables
+% \acom{for this seed?}\rcom{No, all of them.} 
+are also in the MV basis it suffices to show that if $x_i$ is mutable then its mutation $x_i^*$ is also in the MV basis. This observation is based on the exchange relation:
+\[
+    x_i x_i^* = x_+ + x_- 
+\]
+where $x_+,x_-$ are monomials in $ (x_1, \dots, x_r)\setminus x_i$ determined by the cluster structure on $\CC[N]$. 
+% \acom{the structure of interest?
+or are all cluster structures on this ring the same?} \rcom{The structure is derived from an initial seed coming from a reduced word {\bf i}.
+Each of these are equivalent to each other.}
+So if we can find a stable MV cycle $Z_i^*$ such that $b_{Z_i}b_{Z_i^*} = x_+ + x_-$ for each $i$ then we will have checked the conjecture. 
+% \acom{And we do not need to assume the special condition of BGL?}\rcom{They deal with cluster monomials in certain clusters while this deals with all cluster variables, so neither one completely implies the other.}
+
+The following examples give evidence that the mutation $x_i^*$ is in the MV basis. \acom{Roger, reword?}\rcom{Something like this?} \acom{Sure!}
+
+% \jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
+% \acom{Begun}
+
+Before we begin we will need some lemmas, notions and notations. 
+\begin{itemize}
+    \item we have only seen how to fuse ordinary MV cycles; to mutliply MV basis vectors which are indexed by stable MV cycles we'll therefore need a way to represent stable by ordinary; hence:
+    \item a notion/choice of fission 
+    \item the fission lemmas 
+    \item with lemmas in hand, a proposition: given $Z',Z''$ stable with LD... there exist $\tau',\tau''$ (min) such that $b_{Z'} b_{Z''} = b(\tau')  b(\tau'')$
+    \item a shorthand: in examples, instead of writing $Z(\tau)$ for the MV cycle corresponding to the tableau $\tau$ we will only the tableau $\tau$! 
+\end{itemize}
 

### 2021-06-03 draft.tex
Editted examples

@@
 We will take the initial cluster $(x_1,\dots,x_6)$, with $x_4,x_5,x_6$ being frozen, coming from the reduced word ${\bf i} = (1,2,3,1,2,1)$.
+If we view $\CC[N] \cong \CC[x_{ij} : i < j]$, then
+\[
+\begin{array}{ccc}
+    x_1 = x_{12} & x_2 = x_{13} & x_3 = x_{12}x_{23}-x_{13} \\
+    x_4 = x_{12}x_{23}x_{34} - x_{12}x_{24} - x_{13}x_{34} + x_{14} & x_5 = x_{13}x_{24}-x_{14}x_{23} & x_6 = x_{14} 
+\end{array}
+\]
 We list the corresponding tableaux, coordinate ring of the generalized orbital variety $X(\tau)$, Lusztig-datum, and cluster variable as a Laurent polynomial in the $x_i$ below:
@@
 \young(2) & \young(12) & \CC[A_{12}^1] & (1,0,0,0,0,0) & x_1 \rule{0pt}{3ex}\\
-\young(1,3) & \young(11,23) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1,A_{13}^1 \rangle} & (0,0,0,1,0,0) & \frac{x_2 + x_3}{x_1} \TS\BS\\
-\young(1,2,4) & \young(11,22,34) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 \rangle} & (0,0,0,0,0,1) & \frac{x_2x_4 + x_3x_6 + x_1x_5}{x_2x_3} \TS\BS\\
-\young(3) & \young(13,2) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1 \rangle} & (1,0,0,1,0,0) & x_2 \TS\BS\\
-\young(2,3) & \young(12,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{23}^1 \rangle} & (0,1,0,0,0,0) & x_3 \TS\BS\\
-\young(1,4) & \young(11,24,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 \rangle} & (0,0,0,1,0,1) & \frac{x_1x_5 + x_6(x_2+x_3)}{x_1x_2} \TS\BS\\
-\young(1,3,4) & \young(11,23,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 \rangle} & (0,0,0,0,1,0) & \frac{x_1x_5 + x_4(x_2+x_3)}{x_1x_3}\TS\BS\\
-\young(2,4) & \young(112,24,3) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 \rangle} & (0,1,0,0,0,1) & \frac{x_3x_6+x_1x_5}{x_2} \TS\BS\\
-\young(13,2,4) & \young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 \rangle} & (1,0,0,0,1,0) & \frac{x_2x_4 + x_1x_5}{x_3} \TS\BS\\
-\young(2,3,4) & \young(12,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{23}^1,A_{24}^1,A_{34}^1 \rangle} & (0,0,1,0,0,0) & x_4 \TS\BS\\
-\young(3,4) & \young(13,24) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1 \rangle} & (0,1,0,0,1,0) & x_5 \TS\BS\\
-\young(4) & \young(14,2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle} & (1,0,0,1,0,1) & x_6 \TS\BS\\
+\young(1,3) & \young(11,23) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1,A_{13}^1 )} & (0,0,0,1,0,0) & \frac{x_2 + x_3}{x_1} \TS\BS\\
+\young(1,2,4) & \young(11,22,34) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 )} & (0,0,0,0,0,1) & \frac{x_2x_4 + x_3x_6 + x_1x_5}{x_2x_3} \TS\BS\\
+\young(3) & \young(13,2) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1 )} & (1,0,0,1,0,0) & x_2 \TS\BS\\
+\young(2,3) & \young(12,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{23}^1 )} & (0,1,0,0,0,0) & x_3 \TS\BS\\
+\young(1,4) & \young(11,24,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 )} & (0,0,0,1,0,1) & \frac{x_1x_5 + x_6(x_2+x_3)}{x_1x_2} \TS\BS\\
+\young(1,3,4) & \young(11,23,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 )} & (0,0,0,0,1,0) & \frac{x_1x_5 + x_4(x_2+x_3)}{x_1x_3}\TS\BS\\
+\young(2,4) & \young(112,24,3) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 )} & (0,1,0,0,0,1) & \frac{x_3x_6+x_1x_5}{x_2} \TS\BS\\
+\young(13,2,4) & \young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 )} & (1,0,0,0,1,0) & \frac{x_2x_4 + x_1x_5}{x_3} \TS\BS\\
+\young(2,3,4) & \young(12,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{23}^1,A_{24}^1,A_{34}^1 )} & (0,0,1,0,0,0) & x_4 \TS\BS\\
+\young(3,4) & \young(13,24) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1 )} & (0,1,0,0,1,0) & x_5 \TS\BS\\
+\young(4) & \young(14,2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1 )} & (1,0,0,1,0,1) & x_6 \TS\BS\\
   \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){c;c;c}{c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c}{c;c;c}
     s & A_{12}^1 & A_{13}^1 \\
@@
     \midrule 
-    X_3 & A_{12}^1A_{23}^1+sA_{13}^1
+    A_3 & A_{12}^1A_{23}^1+sA_{13}^1
     \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
+A = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
     0 & 1 & & & \\
@@
     \midrule 
-    X_2 & A_{12}^1 \\
-    X_3 & A_{13}^1 \\
-    X_4 & A_{14}^1, A_{23}^1A_{34}^1 + sA_{24}^1
+    A_2 & A_{12}^1 \\
+    A_3 & A_{13}^1 \\
+    A_4 & A_{14}^1, A_{23}^1A_{34}^1 + sA_{24}^1
     \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
     s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
     \midrule 
-    X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
-    X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
+    A_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
+    A_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
     \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
+A = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
     0 & 1 & & & & \\
@@
     \midrule 
-    X_2 & A_{12}^1 + sA_{12}^2 \\
-    X_3 & A_{13}^1, A_{23}^1 \\
-    X_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
+    A_2 & A_{12}^1 + sA_{12}^2 \\
+    A_3 & A_{13}^1, A_{23}^1 \\
+    A_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
     \end{tabular}
@@
     \midrule 
-    X_2 & A_{12}^1 \\
-    X_3 & A_{23}^1 \\
-    X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
+    A_2 & A_{12}^1 \\
+    A_3 & A_{23}^1 \\
+    A_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
     \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
     \midrule 
-    X_2 & A_{12}^1 \\
-    X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
+    A_2 & A_{12}^1 \\
+    A_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
     \end{tabular}
@@
     \midrule 
-    X_2 & A_{12}^1 \\
-    X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
+    A_2 & A_{12}^1 \\
+    A_4 & A_{13}^1A_{34}^1 + sA_{14}^1
     \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
+A = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
     0 & 1 & & & & & \\
@@
     \midrule 
-    X_2 & A_{12}^1 \\
-    X_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
-    X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
+    A_2 & A_{12}^1 \\
+    A_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
+    A_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
     \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
+A = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
     0 & 1 & & & & & & \\
@@
     \midrule 
-    X_2 & A_{12}^1, A_{12}^2 \\
-    X_3 & A_{13}^1 \\
-    X_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
+    A_2 & A_{12}^1, A_{12}^2 \\
+    A_3 & A_{13}^1 \\
+    A_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
     \end{tabular}
@@
     \midrule 
-    X_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
-    X_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
+    A_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
+    A_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
     \end{tabular}
@@
     \midrule 
-    X_2 & A_{12}^1 \\
-    X_3 & A_{23}^1 +sA_{23}^2 \\
-    X_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
+    A_2 & A_{12}^1 \\
+    A_3 & A_{23}^1 +sA_{23}^2 \\
+    A_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
     \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
+A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
      s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
@@
     \midrule 
-     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1
+     A_4 & A_{23}^1A_{34}^1 - sA_{24}^1
     \end{tabular}
@@
 \[
-X = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
+A = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
     0 & 1 & & & & & & & \\
@@
     \midrule 
-    X_2 & A_{12}^1,A_{12}^2 \\
-    X_3 & A_{13}^1, A_{23}^1 \\
-    X_4 & A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
+    A_2 & A_{12}^1,A_{12}^2 \\
+    A_3 & A_{13}^1, A_{23}^1 \\
+    A_4 & A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
         & A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2 
@@
 \[
-X = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
+A = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
     0 & 1 & & & & & & \\
@@
     \midrule 
-   X_2 & A_{12}^1 \\
-    X_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
-    X_4 & 
+   A_2 & A_{12}^1 \\
+    A_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
+    A_4 & 
          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
@@
 \[
-X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
+A = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
     0 & 1 & & & & & & & & \\
@@
     \midrule 
-   X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
-    X_3 & A_{13}^1,A_{23}^1 \\
-    X_4 & A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+   A_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
+    A_3 & A_{13}^1,A_{23}^1 \\
+    A_4 & A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
         & A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\

### 2021-06-04 draft.tex
joel worked on intro and stuff

@@
 Given weights $\mu\le\lambda$ with $\lambda$ dominant, denote by $V(\lambda)$ the irreducible representation of $\GL_m$ of highest weight $\lambda$ and by $V(\lambda)_\mu$ its $\mu$-weight space. 
-There is an injective map $ \Psi_\lambda: V(\lambda) \to \CC[N]$ realizing $V(\lambda)$ as a subspace of $\CC[N]$ and sending $v\in V(\lambda)_\mu$ to $\CC[N]_{\mu - \lambda}$.
+There is an injective map $ \Psi_\lambda: V(\lambda) \to \CC[N]$ realizing $V(\lambda)$ as a subspace of $\CC[N]$ and sending $ V(\lambda)_\mu$ to $\CC[N]_{\mu - \lambda}$.
 
@@
 
-\acom{Warning! Earlier we defined the MV cycles as irreducible components of $\overline{\Gr^\lambda}\cap S^\mu$}
+\acom{Warning!
+Earlier we defined the MV cycles as irreducible components of $\overline{\Gr^\lambda}\cap S^\mu$} \jcom{Good point.
+We should be consistent.
+I will think about the best way to fixe this and correct it.}
 % In particular, the MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$ give a basis of $V(\lambda)$. 
@@
 The \new{stable} MV cycles of coweight $\nu\in Q_+$ are defined to be irreducible components of $\overline{S^0_+ \cap S^\nu_-}$.
-By a theorem of Anderson, MV cycles in $\overline{\Gr^\lambda\cap S^{\nu + \lambda}_-}$ are in bijection with stable MV cycles of coweight $\nu$ that are contained in $\overline\Gr^\lambda$ \cite[Proposition~3]{anderson2003polytope}.
+Multiplication by $ t^\lambda $ defines an isomorphism $\overline{S^0_+ \cap S^\nu_-} \cong \overline{S^\lambda_+ \cap S^{\lambda+\nu}_-} $.
+By a theorem of Anderson, MV cycles in $\overline{\Gr^\lambda\cap S^{\nu + \lambda}_-}$ consist of those irreducible components of $ \overline{S^\lambda_+ \cap S^{\lambda+\nu}_-} $ that are contained in $\overline\Gr^\lambda$ \cite[Proposition~3]{anderson2003polytope}.
 We denote the set of all stable MV cycles $\cZ(\infty)$.
@@
     (A special case of \cite[Proposition~6.1]{baumann2019mirkovic})
-    For each $Z\in\cZ(\infty)$ there is a unique element $b_Z\in\CC[N]$ such that for any dominant weight $\lambda$, if $t^\lambda Z\in\cZ(\lambda)$ then $\Psi_\lambda([t^\lambda Z]) = b_Z$ and the collection of all such elements is called the \new{MV basis}.
+    For each $Z\in\cZ(\infty)$ there is a unique element $b_Z\in\CC[N]$ such that for any dominant weight $\lambda$, if $t^\lambda Z\in\cZ(\lambda)$ then $\Psi_\lambda([t^\lambda Z]) = b_Z$.
 \end{theorem}
+The set $ \{b_Z : Z \in \cZ(\infty) \}$ is called the \new{MV basis} of $ \CC[N]$.
+\jcom{I took the definition out of the theorem statement.}
 % 
@@
 $$
-in $\CC[N]$. \acom{The summation is finite since 7.1?... Don't want to introduce the notation $\cZ(\infty)_\nu$ if we can avoid it.}
+in $\CC[N]$. \acom{The summation is finite since 7.1?... Don't want to introduce the notation $\cZ(\infty)_\nu$ if we can avoid it.} \jcom{The sum is finite for weight reasons.}
 Moreover, there exist $\lambda',\lambda''$ dominant effective and a pair of tableaux $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$ such that 
@@
 \end{theorem}
+\jcom{I would take the second part ``Moreover'' out of the statement of the theorem and state it as a corollary, maybe after Prop 7.3.}
 % Given $\epsilon\in\ZZ^m$ denote by $t^\epsilon:V(\lambda) \to V(\lambda + \epsilon)$ the map resulting from multiplication by the coweight $t^\epsilon$ in $\Gr$.
@@
 \acom{Should I adjust the diagram so that its from unions over $\lambda$}
+\jcom{I think so.
+Also somewhere we should indicate that the map $YT(\lambda) \rightarrow Z(\lambda) $ takes $ \tau $ to $ Z(\tau)$.
+In principal we could increase the size of this diagram and include somehow the map taking ``dominant tableaux'' to generalized orbital varieties, but I don't see how to do this without making it unwieldly.}
 
@@
     \label{prop:minwts}
-    Given two Lusztig data $n_\bullet',n_\bullet''$ there is a smallest choice of effective coweights $\mu',\mu''$ and effective dominant coweights $\lambda',\lambda''$ such that $\mu = \mu' + \mu''$ is effective dominant and $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ are semistandard Young tableaux with the prescribed Lusztig data.
+    Given two Lusztig data $n_\bullet',n_\bullet''$ there is a smallest choice of effective coweights $\mu',\mu''$ and effective dominant coweights $\lambda',\lambda''$ such that $\mu = \mu' + \mu''$ is effective dominant and $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ have the prescribed Lusztig data.
 They are got by choosing the minimum $\lambda,\mu$ for $n_\bullet = n_\bullet ' + n_\bullet ''$ afforded by \Cref{lem:mintab}, and then breaking off $n_{r,c}'$ boxes of weight $r$ from each row $c<r$ of $\tau$ to form a $\tau'_0$ an intermediate tableau.

### 2021-06-05 draft.tex
Cluster stuff in intro

@@
     \item Recalling intersection multiplicity, checking that the definitions allow passing to open sets
+    \item in examples put ideals of arithmetic fusion and their tableaux into tables; also split examples into 2 sections: $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with rising action?
 \end{itemize}
@@
 
-The geometric Satake equivalence of Mirkovic-Vilonen \cite{mirkovic2007geometric} provided an equivalence of categories between the category of spherical perverse sheaves in the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.
+The geometric Satake equivalence of Mirkovi\'c and Vilonen \cite{mirkovic2007geometric} provides an equivalence of categories between the category of spherical perverse sheaves in the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.
 This foundational result provides a powerful tool to study representation theory using geometry.
-In particular, under this equivalence, the Mirkovic-Vilonen cycles in the affine Grassmannian of $ G $ index bases for irreducible representations of $ G^\vee $.
-In this paper we work with $ G =GL_m$ and identify $ G^\vee = GL_m$ as well.
+In particular, under this equivalence, the Mirkovi\'c--Vilonen cycles in the affine Grassmannian of $ G $ index bases for irreducible representations of $ G^\vee $.
+In this paper we work with $ G = \GL_m$ and identify $ G^\vee = \GL_m$ as well.
 
@@
 and to Nakajima quiver varieties on the other hand.
-This extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of matrices with two eigenvalues.
-Via this equivalence, the Mirkovic-Vilonen cycles are identified with certain varieties of matrices, called generalized orbital varieties (see \cite{dthesis}).
+The second author showed \cite{dthesis} that under the Mirkovi\'c-Vybornov isomorphism, the  Mirkovi\'c--Vilonen cycles are identified with certain varieties of matrices, called generalized orbital varieties.
+
+%This extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of matrices with two eigenvalues. 
 %This paper generalizes the first of these relations (an isomorphism) to families of slices in the Beilinson--Drinfeld Grassmannian.
@@
 
-Essential to \cite{mirkovic2007geometric}, the Beilinson-Drinfeld Grassmannian is used to define a fusion product on the category of spherical perverse sheaves on the affine Grassmannian.
-In \cite{anderson2003polytope}, Anderson used the BD Grassmannian to define a fusion of Mirkovic-Vilonen cycles.
-He conjectured that this fusion product matches the muliplication in the coordinate ring of the unipotent subgroup $ N \subset GL_m$.
-This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that these MV cycles give a basis for $ \CC[N]$.
+Essential to \cite{mirkovic2007geometric}, the Beilinson--Drinfeld Grassmannian is used to define a fusion product on the category of spherical perverse sheaves on the affine Grassmannian.
+In \cite{anderson2003polytope}, Anderson used the Beilinson--Drinfeld Grassmannian to define a fusion of Mirkovi\'c--Vilonen cycles.
+He conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup $ N \subset\GL_m$.
+This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that the Mirkovi\'c--Vilonen cycles give a basis for $ \CC[N]$, which we call the MV basis.
 % 
@@
 
-Unfortunately, performing computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.
+Unfortunately, computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.
 A few such computations were done by Anderson-Kogan in \cite{anderson2006algebra} in a somewhat ad-hoc fashion.
-
-The purpose of this paper is to give a conceptually elementary way to compute this product by transferring it to a fusion product of generalized orbital varieties.  Our main result is the following.
-
-\begin{theorem}
+Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann-Gaussent-Littelmann \cite{baumann2020bases}.
+
+The purpose of this paper is to give a conceptually elementary way to compute this product by transferring it to a fusion product of generalized orbital varieties.
+To do so, we use that the Mirkovic-Vybornov isomorphism extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of matrices with two eigenvalues.
+Our main result is the following.
+
+\begin{maintheorem}
     Let $ Z, Z' $ be MV cycles.
 The structure constants for the multiplication of $ b_Z b_{Z'}$ in $\CC[N]$ are equal to the intersection multiplicities in the fusion of the generalized orbital varieties corresponding to $ Z, Z'$.
-\end{theorem}
+\end{maintheorem}
 % 
@@
 
-{\color{blue}
-\acom{To quote from BFZ for a concise definition: Cluster algebras are a class of commutative rings defined axiomatically in terms of a distinguished family of generators called cluster variables.
+An application of this result is to relate the cluster algebra structure in $\CC[N]$ to the MV basis.
+Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{berenstein2005cluster3} and \cite{geiss2007initial} that $\CC[N]$ has a natural cluster algebra structure.
+
+This structure starts with an initial seed $\Sigma = ((x_1,\cdots,x_r),B)$ where $x_i \in \CC[N]$ and $B$ is some matrix.
+We obtain new variables through a process called mutation where for a mutable variable $x_i$, its mutation is the unique element $x_i^* \in \CC[N]$ such that $$x_ix_i^* = x_+ + x_-.$$
+This equation is called an exchange relation and the terms $x_+$ and $x_-$ are some product in the $x_j$, $j\neq i$, that is determined by $B$.
+We then obtain a new seed $$\mu_i(\Sigma) = ((x_1,\cdots, x_{i-1}, x_i^*, x_{i+1},\cdots,x_r), \mu_i(B))$$ and can acquire possibly new variables through further mutations.
+
+The variables $x_1,\cdots,x_r$ as well as all possible variables that are obtained through successive mutations are known as cluster variables.
+The cluster monomials are products of cluster variables that are supported on a single seed.
+
+It has been shown that the cluster monomials are in certain interesting bases such as the dual canonical basis \cite{lusztig1990canonicalbases}\cite{kang2018monoidal} and the dual semicanonical basis \cite{lusztig2000semicanonical}\cite{geiss2006rigid}.
+As these elements are defined in a combinatorial way, it allows efficient computation of several elements of these bases.
+
+Although the MV basis and the above mentioned bases are in general different from each other \cite{baumann2019mirkovic}, it is believed that they at least all contain the cluster monomials, leading to the following conjecture.
+
+\begin{conjecture}\label{conj:cluster in MV}
+    %The dual semicanonical basis and the MV basis overlap on the cluster monomials. 
+    The cluster monomials are contained in the MV basis. 
+\end{conjecture}
+
+The conjecture is true in type $A_n$ with $n\leq 3$ as in these cases, the MV basis agrees with the dual semicanonical and dual canonical bases \cite{baumann2019mirkovic}.
+It has also been shown that cluster monomials supported on seeds satisfying a special condition are also in the MV basis \cite{baumann2020bases}.
+In addition, cluster variables coming from the initial seeds constructed in \cite{berenstein2005cluster3} are also in the MV basis \cite{kato2011polytopal}.
+
+This leads to the following idea to show that the cluster variables are in the MV basis.
+Given a seed $((x_1,\cdots,x_r),B)$ with each of the $x_i$ in the MV basis, say corresponding to MV cycles $Z_i^*$, and an exchange relation $x_ix_i^* = x_+ + x_-$, it suffices to find an MV cycle $Z_i^*$ such that the fusion product of $Z_i$ and $Z_i^*$ gives $Z_+$ and $Z_-$, corresponding respectively to $x_+$ and $x_-$.
+In this case, we are able to conclude that $x_i^*$ is in the MV basis corresponding to the MV cycle $Z_i^*$.
+Inducting on mutation, we conclude that all cluster variables are in the MV basis.
+
+We show in Section \ref{ss:GL4 examples} that this is indeed the case in type $A_3$ by directly computing each fusion product corresponding to an exchange relation.
+
+% {\color{blue}
+% \acom{To quote from BFZ for a concise definition: Cluster algebras are a class of commutative rings defined axiomatically in terms of a distinguished family of generators called cluster variables.
 Say also what is a seed, what is a mutation, what is a cluster, what is a cluster monomial, and finally for the stubbornly ignorant clarify that 'the cluster monomials' refers to cluster monomials for all possible clusters!}
 
-$\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
-% that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
-
-\acom{Background on cluster:}
-In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
+% $\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
+% % that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
+
+% \acom{Background on cluster:}
+% In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
 This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
-Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
-
-In the appendix to \cite{baumann2019mirkovic} the second and third author along with Morton-Ferguson check that the MV basis differs from the dual semicanonical basis (at the Kashiwara--Saito counterexample).
-Yet, the two bases have enough in common (c.f.\ BKT,...?), that we have the following conjecture.
-
-\begin{conjecture}
-    The dual semicanonical basis and the MV basis overlap on the cluster monomials. In particular, the cluster monomials are contained in the MV basis. 
-\end{conjecture}
-
-We note that both of these bases are \new{biperfect} bases of $\CC[N]$ and in type $A_n$ with $n\le 3$ there is a unique biperfect basis of $\CC[N]$. }
-
-Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
-% and they conjectured a formula for many of them.
-
-It's not clear how this work helps with/relates to AK/their conjectures.
-
-The generalized \mvy is interesting in its own right. \acom{is it?}
-
-Computing fusion still hard but at least boiled down to linear algebra.
+% Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
+
+% In the appendix to \cite{baumann2019mirkovic} the second and third author along with Morton-Ferguson check that the MV basis differs from the dual semicanonical basis (at the Kashiwara--Saito counterexample).
+% Yet, the two bases have enough in common (c.f.\ BKT,...?), that we have the following conjecture.
+
+% \begin{conjecture}
+%     The dual semicanonical basis and the MV basis overlap on the cluster monomials. In particular, the cluster monomials are contained in the MV basis. 
+% \end{conjecture}
+
+% We note that both of these bases are \new{biperfect} bases of $\CC[N]$ and in type $A_n$ with $n\le 3$ there is a unique biperfect basis of $\CC[N]$. }
+
+% Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
+% % and they conjectured a formula for many of them.
+
+% It's not clear how this work helps with/relates to AK/their conjectures.
+
+% The generalized \mvy is interesting in its own right. \acom{is it?}
+
+% Computing fusion still hard but at least boiled down to linear algebra.
 Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
 
-Interesting combinatorics?
+% Interesting combinatorics?
 Presumably it is related to Feigin and Loktev's generalized Kostka polynomials?
@@
 
-Exchange relations only work on cluster modules where one is a mutation of the other (i.e.\ those corresponding to cluster monomials which are related by mutation).
+% Exchange relations only work on cluster modules where one is a mutation of the other (i.e.\ those corresponding to cluster monomials which are related by mutation).
 Of course this gives me everything.
@@
 
-The hope (conjecture) is that this paper gives a way to compute on such modules.
+% The hope (conjecture) is that this paper gives a way to compute on such modules.
 Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is a cluster monomial belonging to both bases and $c_Y$ is the square of a cluster monomial ($b'$ say) belonging to both bases.
@@
 
-% No; $x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
-
-Representation theory?
+% % No; $x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
+
+% Representation theory?
 
@@
 % 
-If $\nu\in\ZZ^m$ is both effective and dominant then it is a partition of size $|\nu| = \nu_1 + \cdots + \nu_m\in\NN$.
+If $\nu\in\ZZ^m$ is both effective and dominant then it is a partition of size $|\nu| = \nu_1 + \cdots + \nu_m\in\NN$.  Let $ Q_+ \subset \ZZ^m$ denote the positive root cone, explicitly we have
+$$
+Q_+ = \{ (\nu_1, \dots, \nu_m) : \nu_1 + \cdots + \nu_j \ge 0 \text{ for $j = 1, \dots, m-1 $ and } \nu_1 + \dots + \nu_m = 0 \}
+$$
+We define a partial order on $ \ZZ^m$ by $ \lambda \ge \mu $ if and only if $ \lambda - \mu \in Q_+ $.
+
 %We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights. 
@@
         \item in modular terms as $$(V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty}) \, ;$$
-        \item in the fibres over $ s \in \AA$ as the inclusion $$
+        \item in the fibre over $ s \in \AA$ as the inclusion $$
         G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,;$$
@@
 $$
-called the \new{open family} of $X_1$ and $X_2$. 
+%called the \new{open family} of $X_1$ and $X_2$. 
 % 
@@
 
-We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  X_1 \ast_{\Cx} X_2 $ in $ \Grbd $. By construction, this is a flat family over $ \AA$.
+We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  X_1 \bdfamo X_2 $ in $ \Grbd $. By construction, this is a flat family over $ \AA$.
 
@@
 \label{ss:subgrs}
-\acom{Recall the positive root cone, as well as the dominance order on coweights.}
 
@@
 % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
-By a Theorem of Zhu, $ \overline{\Gr}^{\lambda'} \geofu \overline{\Gr}^{\lambda''} $ is reduced and equal to $ \overline{\Gr}^{\lambda' + \lambda''}$ \cite[Proposition 3.1.14]{zhu2016introduction}.
+By a theorem of Zhu, $ \overline{\Gr}^{\lambda'} \geofu \overline{\Gr}^{\lambda''} $ is reduced and equal to $ \overline{\Gr}^{\lambda}$ \cite[Proposition 3.1.14]{zhu2016introduction}.
 % Suppose that $ s \ne 0$.  
-If $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''} =  \Gr^{\lambda'} \bdfamf \Gr^{\lambda''} $ a $ G(\CC[t])$-orbit
+If $s\ne0$, then the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ contains the open locus $ \Gr_{0,s}^{\lambda', \lambda''} =  \Gr^{\lambda'} \bdfamf \Gr^{\lambda''} $ a $ G(\CC[t])$-orbit
 % .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
@@
 The reason for restricting to dominant $ \mu $ is so that $ S^\mu \subset \cW^\mu$.
-I agree that we should mention this, but I'm not sure where.}
-
+I agree that we should mention this, but I'm not sure where.} \acom{Yes, sorry.
+We could say it here?}
+% 
 % \acom{First lattice description that doesn't come for free?}
@@
 \end{definition}
-\acom{and its closure?}
-\jcom{I don't think that we use the closure in this paper, do we?}
+% \acom{and its closure?}
+% \jcom{I don't think that we use the closure in this paper, do we?}
+% \acom{No you are right we do not.}
 \begin{definition} 
@@
  $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
- which we define to have fibres $ S^{\mu', \mu''}_{0,s} \cong S^{\mu'}\times S^{\mu''} $ for $ s \ne 0$ and fibre $ S^{\mu}$ over $ s = 0 $.
+ which we define to have fibres $ S^{\mu', \mu''}_{0,s} := \theta_s^{-1}( S^{\mu'}\times S^{\mu''}) $ for $ s \ne 0$ and fibre $ \theta_0^{-1}(S^{\mu})$ over $ s = 0 $.
 \end{definition}
-Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.
+%Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.
 % 
@@
 % 
-If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
-
-\acom{Don't we want this to be the definition?}
-$$
-% S^{\mu', \mu''}_{0,s} = 
-    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
-$$
-See \cite[Section~5.2]{baumann2020bases} for further details.
+We can also describe the fibres as orbits
+$$
+ S^{\mu', \mu''}_{0,s} = 
+    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
+$$
+See \cite[Section~5.2]{baumann2020bases} for further details where this fibre is also described as the attracting locus for a $\Cx$ action.
+
+In \cite[Prop~2.6]{kamnitzer2014yangians}, we observed that $ S^\mu \subset \cW^\mu$ (this uses that $\mu$ dominant, which is the reason why we make this assumption).
+More generally, we have the following result.
+
+\jcom{Following Anne's comment above about dominant $ \mu$, I decided to move this result here.}
+
+\begin{lemma}
+\label{le:inftyfusiskl} % as in lands in KL slice 
+    Under the map $ \Grbd \rightarrow \Grth$ the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
+\end{lemma}
+%\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?} Update: added this above.}
+% Resolved?
+the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too..
+Anyway I think that you address this below Joel.
+
+\begin{proof}
+    Let $ L $ 
+    % lie in this image.  
+    be a lattice in the image of $S^{\mu',\mu''}_{0,\AA}$.
+Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $.
+Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.
+Note that $ h \in T_1(\Oinf)$.
+    Moreover, $L = h (h^{-1} g h) t^{\mu}\CC[t]^m$. 
+    % $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
+    Since 
+    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
+    $h^{-1} g h \in N_-(\cK_\infty)$ we can factor $ h^{-1} g h$ as $n_1 n_2$ for some $ n_1 \in {(N_-)}_1(\Oinf), n_2 \in {N_-}(\CC[t]) $.
+
+    As $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t]) $, and so 
+     % \CC\xt[t^{-1}]s
+    % 
+    % \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?} % 
+    % \acom{Si.}
+    % 
+    $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
+\end{proof}
 
@@
 $$
-    \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^c \le N - \#\text{~boxes in first $c$ columns of }\lambda \}
+    \overline{\OO}^\lambda = \{ A \in M_N(\CC) : \rk A^c \le N - \#\text{~boxes in first $c$ columns of }\lambda,  \text{ for $ c \in \NN$} \}
 $$
@@
     % 
-    \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^i &\le N - 
-    \#\text{~boxes in first $c$ columns of }\lambda' \\
-    \rk (A-s)^c &\le N - \#\text{~boxes in first $c$ columns of }\lambda'' \}\,. 
+    \overline{\OO}^{\lambda', \lambda''}_{0,s} = \{ A \in M_N(\CC) : \rk A^c &\le N - 
+    \#\text{~boxes in first $c$ columns of }\lambda',  \text{ for $ c \in \NN$} \\
+    \rk (A-s)^c &\le N - \#\text{~boxes in first $c$ columns of }\lambda'',  \text{ for $ c \in \NN$} \}\,. 
 \end{split}
@@
 Some of the coordinates of $z$ may be equal so we introduce the following data to keep track of these equalities.
-There exist a sequence of integers $k_\bullet = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, a sequence of points $s_\bullet = (s_1, \dots, s_\ell )\in\AA^\ell$ such that $s_a\ne s_b$ for any $a\ne b$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
+Let $ \ell$ denote the number of distinct coordinates of $ z $.
+There exist a sequence of integers $k = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, and $ s \in\AA^\ell$, such that $s_a\ne s_b$ for any $a\ne b$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
 $$ 
@@
 for each $a = 1,\dots,\ell$. 
-Given the choice of $ s_\bullet$ we require that $ p $ is of minimal length. 
-Then, given $z$, the data $k_\bullet, s_\bullet, p$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
+Given the choice of $ s$ we require that $ p $ is of minimal length. 
+Given $z$, the data $k, s, p$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
 % 
@@
 % 
-Define 
+For $ c\in \NN$, let
 $$
@@
 \begin{cases}
-    z(s)_{p(c)} = 0 &  c = 1, \dots, k_1 \\
-    z(s)_{p(c)} = s &  c = k_1 + 1, \dots, k\,.
+    z(a)_{p(c)} = 0 &  c = 1, \dots, k_1 \\
+    z(a)_{p(c)} = s &  c = k_1 + 1, \dots, k\,.
 \end{cases}    
@@
 For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of 
-\(\ell =2\), \(k_\bullet = (0,\lambda_1')\), \(s_\bullet = (0,s)\) and the permutation $p$.
+\(\ell =2\), \(k = (0,\lambda_1')\), \(s_1 = 0, s_2 = s\) and the permutation $p$.
 % $ \ell = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
@@
 % a $\mu$ Jordan form matrix plus 
-$J_{0,\mu} + x$ where $x$ is a $\mu\times\mu$ block matrix with possibly nonzero entries $A_{ij}^1,\dots,A_{ij}^{\min(\mu_i,\mu_j)}$ in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
+$A = J_{0,\mu} + X$ where $X$ is a $\mu\times\mu$ block matrix with possibly nonzero entries $A_{ij}^1,\dots,A_{ij}^{\min(\mu_i,\mu_j)}$ in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
 % $\dim \TT_\mu = N^2 - \dim \OO_\mu$.
@@
 
-    Fix $ i$ and suppose that for some $ j$, $ \mu_j < \mu_i$.  In this case, we can alter our basis to $ v'_i = v_i - r v_j$ for some polynomial $r \in \CC[t]$.  
-    \acom{More like a quotient than a remainder, better $q$ than $r$?}
-    This gives us new polynomials $ p'_{ij} = p_{ij} - r (t^{\mu_j} + p_{jj}) $.  In this way, we can ensure that $ p_{ij} $ has degree less than $ \min(\mu_i, \mu_j)$.  
+    Fix $ i$ and suppose that for some $ j$, $ \mu_j < \mu_i$.  In this case, we can alter our basis to $ v'_i = v_i - q v_j$ for some polynomial $q \in \CC[t]$.  
+    This gives us new polynomials $ p'_{ij} = p_{ij} - q (t^{\mu_j} + p_{jj}) $.  In this way, we can ensure that $ p_{ij} $ has degree less than $ \min(\mu_i, \mu_j)$.  
     Thus \cref{it:slice} implies \cref{it:basis}.
@@
 %\acom{Don't have $P$ notation, replacing (in lemma below) with $\ZZ^m$ for now..}
-\begin{lemma}
-\label{le:inftyfusiskl} % as in lands in KL slice 
-    Under the map $ \Grbd \rightarrow \Grth$ the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
-\end{lemma}
-%\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?} Update: added this above.}
-% Resolved?
-the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too..
-Anyway I think that you address this below Joel.
-
-\begin{proof}
-    Let $ L $ 
-    % lie in this image.  
-    be a lattice in the image of $S^{\mu',\mu''}_{0,\AA}$.
-Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $.
-Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.
-Note that $ h \in T_1(\Oinf)$.
-    Moreover, $L = h (h^{-1} g h) t^{\mu}\CC[t]^m$. 
-    % $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
-    Since 
-    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
-    $h^{-1} g h \in N_-(\cK_\infty)$ we can factor $ h^{-1} g h$ as $n_1 n_2$ for some $ n_1 \in {(N_-)}_1(\Oinf), n_2 \in {N_-}(\CC[t]) $.
-
-    As $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t]) $, and so 
-     % \CC\xt[t^{-1}]s
-    % 
-    % \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?} % 
-    % \acom{Si.}
-    % 
-    $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
-\end{proof}
+
 % 
@@
 % lattice).
-In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the ``almost injective'' \acom{emphasis is on the almost injectivity/glass half full no?} \jcom{ok, I changed it} map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$.
+In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the ``almost injective'' 
+% \acom{emphasis is on the almost injectivity/glass half full no?} \jcom{ok, I changed it} \acom{Yay!}
+map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$. 
 % (for example the fibre of this map over $ 0 $ is $ \CC $). 
@@
 The following refinement of the \mvy isomorphism is a special case of \cite[Theorem 5.3]{mirkovic2007quiver}. 
-\acom{Wait isn't 5.3 a special case of this?}  \jcom{No, they deal with the more general setting of more points.}
+\acom{Wait isn't 5.3 a special case of this?}  \jcom{No, they deal with the more general setting of more points.} \acom{Ok, but I don't think that they establish this exact fact..they have Lemma~4.4.2 and Corollary 4.5 which uses the convolution grassmannian.}
 \begin{theorem} 
@@
 \section{\sout{Falling Action}} % Resolution  
+\label{se:falling}
 \subsection{MV cycles}
-Let $Q_+$ denote the $\ZZ_{\ge 0}$-span of the positive coroots. 
-Recall the \new{dominance order} on $\ZZ^m$ defined by declaring that $\mu\le\lambda$ if $\lambda - \mu\in Q_+$ for any $\lambda,\mu$.
-
-Continuing now with the notation of the previous sections we add the assumption that $\mu\le\lambda$ and forget the assumption that $\mu$ is dominant. 
+%Let $Q_+$ denote the $\ZZ_{\ge 0}$-span of the positive coroots. 
+%Recall the \new{dominance order} on $\ZZ^m$ defined by declaring that $\mu\le\lambda$ if $\lambda - \mu\in Q_+$ for any $\lambda,\mu$.
+
+Continuing now with the notation of the previous sections, we add the assumption that $\mu\le\lambda$ and forget the assumption that $\mu$ is dominant. 
 % 
@@
 \begin{definition}
-An irreducible component of $\overline{\Gr}^\lambda \cap S^\mu$ is called an \new{Mirkovic--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$. 
+An irreducible component of $\overline{\Gr^\lambda \cap S^\mu}$ is called an \new{Mirkovic--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$. 
 \end{definition}
@@
 
-By \cite[Theorem~3.2(b)]{mirkovic2007geometric}, each MV cycle in $\overline\Gr^\lambda$ of coweight $\mu$ has dimension $ \rho(\lambda - \mu)$ where $\rho$ is the half sum of positive roots.
-Normalizing $ \rho = (m, m-1, \dots, 1)$ and identifying $P \cong P^\vee$ the pairing $P\times P^\vee\to\ZZ $ is given by the ordinary dot product.
+By \cite[Theorem~3.2(b)]{mirkovic2007geometric}, each MV cycle in $\overline\Gr^\lambda$ of coweight $\mu$ has dimension $ \rho(\lambda - \mu)$ where $ \rho = (m, m-1, \dots, 1)$ and we use the ordinary dot product on $\ZZ^m$.
 We denote by $\cZ(\lambda)$ the collection of all MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$.
@@
 
-In this section only, \acom{possibly also the next} we will write $ S^\mu_- = N_-(\cK) t^\mu$ (with a subscript), because we will also need the opposite semi-infinite cell $S^\mu_+ := N(\cK)t^\mu$.
+From now on, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (with a subscript), because we will also need the opposite semi-infinite cell $S^\mu_+ := N(\cK)t^\mu$.
 %\acom{HB, ``..we will write.., because we will need the opposite cell..''}
@@
 From the definition of $ \mathring Z(\tau)_1 $, we see that $ f_i(\mathring Z(\tau)_1 )= \mathring Z(\tau(i))_1$.  
-From above/again $ \Gr^{\lambda(i)} \cap f_i(\mathring Z(\tau(i))_1)$ is a dense constructible subset of $\mathring Z(\tau(i))_1$.  
+From above, $  f_i(\mathring Z(\tau(i))_1) \cap \Gr^{\lambda(i)}$ is a dense constructible subset of $\mathring Z(\tau(i))_1$.  
 Since $ \mathring Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)}_- \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ 
@@
 % \acom{of max dim?} \jcom{it is pure dimensional, as mentioned at the beginning of section 6.1} 
-equals $|YT^\lambda_\mu|$, thus on the left hand side, each $ \mathring Z(\tau)$ can only have one irreducible component of dimension $ \rho(\lambda - \mu)$.
+equals $|YT(\lambda)_\mu|$, thus on the left hand side, each $ \mathring Z(\tau)$ can only have one irreducible component of dimension $ \rho(\lambda - \mu)$.
 % 
@@
 % 
-\subsection{Fusion of MVCs via BD MVy}
+\subsection{Fusion of MV cycles via fusion of generalized orbital varieties}
 
@@
 
-Conversely, let $ L \in \mathring Z(\tau) $.  By \Cref{cor:mvy}, $ L = g(A)$ for some $ A \in \TT_\mu \cap \n $.  Running the above argument in reverse, we see that $ A \in \mathring X(\tau)$. 
+Conversely, let $ L \in \mathring Z(\tau) $.  By \Cref{cor:mvy}, $ L = g(A)\cO^m$ for some $ A \in \TT_\mu \cap \n $.  Running the above argument in reverse, we see that $ A \in \mathring X(\tau)$. 
 \end{proof}
@@
 
-% \jcom{Please add a reference to your paper here and also a lemma which states that under the Mirkovic-Vybornov isomorphism $ \mathring X(\tau) $ is mapped isomorphically onto $ \mathring Z(\tau) $.}
+% \jcom{Please add a reference to your paper here and also a lemma which states that under the Mirkovi\'c--Vybornov isomorphism $ \mathring X(\tau) $ is mapped isomorphically onto $ \mathring Z(\tau) $.}
 % 
@@
 % 
-Let $\lambda,\lambda',\lambda''$ and $\mu \mu',\mu''$ be as in previous sections, once again assuming that $\mu$ is dominant.
+Let $\lambda,\lambda',\lambda''$ and $\mu, \mu',\mu''$ be as in previous sections, once again assuming that $\mu$ is dominant.
 % \jcom{I think that this is can move earlier, with the caveat that I mentioned earlier about $ \mu $ being non-dominant in 6.1 and dominant here.} \acom{Yes.} \acom{But we only start to need the primes now.}
@@
     \left\{
-        (A,s)\in M_N(\CC) \times \AA^\times: 
+        (A,s)\in M_N \times \AA^\times: 
         A \in \mathring X(\tau',\tau'')_{0,s} 
@@
     \label{pr:XttZtt}
-    The image of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_\Cx \mathring Z(\tau'')$. 
+    The image of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_{\AA^\times} \mathring Z(\tau'')$. 
     % \[
@@
 $$ 
-and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$. The argument can be reversed for
-$L\in\mathring Z(\tau')\ast_\Cx \mathring Z(\tau'')$.
+and so $(L(0),L(s))\in \mathring Z(\tau')\times \mathring Z(\tau'')$.
+
+Conversely, given
+$L\in\mathring Z(\tau')\ast_s \mathring Z(\tau'')$, we can write $ L = g(A)\CC[t]^m$ by  \Cref{th:OGrl}.  Then reversing the above logic, we conclude that $ A \in \mathring X(\tau',\tau'')_{0,s}$.
 % \theta^{-1}(\mathring Z(\tau')\times Z(\tau''))$.
@@
 % \acom{add loc cit} \jcom{I think just add a reference our fusion section} \acom{Yeah that's what I meant, taking loc cit literally}
-we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ in $M_N(\CC)\times\CC$.
-By \Cref{prop:adjoint} it is contained in $\overline\OO^\lambda\cap\TT_\mu\cap\n$, so by Theorem 4 its irreducible components are generalized orbital varieties.
-%
-
-\acom{Recalling intersection multiplicity:}
-
-We have the zero fibre in $\Grbd$ as effective divisor $D$, and the fusion of subscheme $V = X\ast_\AA Y\subset\Grbd$ as a finite-dimensional irreducible variety not contained in the support of $D$, and finally an irreducible component $Z$ of $D\cdot V = X\ast_0 Y$, codimension 1 in $V$.
-Denote by $\iota(Z,D\cdot V)$ the intersection multiplicity of $Z$.
+we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ in $M_N \times\AA$.
+By \Cref{prop:adjoint}, it is contained in $\overline\OO^\lambda\cap\TT_\mu\cap\n$.
+%so by Theorem 4 its irreducible components are generalized orbital varieties. 
+%\jcom{I removed the last part because maybe it has smaller dimensional components and anyway, I don't think that it is relevant}
+
+We quickly recall the
+definition of intersection multiplicity that we will need following \cite[Eg. 2.6.5]{Fulton}. We consider a fibre square of $\CC$-schemes
+$$
+\begin{tikzcd}
+   W\ar[r]\ar[d]&V\ar[d]\\D\ar[r]&Y
+\end{tikzcd}
+$$
+with $i$ the inclusion of an effective Cartier divisor and $V$ an
+irreducible variety of dimension $k$. We assume that $V$ is not contained
+in the support of $D$. Let $Z$ be an irreducible component of $W$;
+it is a subvariety of $V$ of codimension $1$. The \textbf{multiplicity}
+of $Z$ in the product $D\cdot V$ is defined to be the length of the
+module $\mathcal O_{V,Z}/(f)$ over the local ring $\mathcal O_{V,Z}$
+of $V$ along $Z$, where $f$ is a local equation of $D|_V$ on an affine
+open subset of $V$ which meets $Z$. Following \cite[chap.~7]{Fulton},
+this multiplicity is denoted by $i(Z,D\cdot V)$.
+
+For our purposes, the zero fibre in $\Grbd$ is an effective divisor $D$.
+For $ Z', Z'' $ subvarieties of $ \Gr $, $V = Z'\ast_\AA Z''\subset\Grbd$ is a variety not contained in the support of $D$.
+Then we choose an irreducible component $Z$ of $W := D \cap V = X\ast_0 Y$.
+Thus, we may consider the intersection multiplicity $ i(Z, X \ast_0 Y) := i(Z, D \cdot V)$.
+We will be particularly interested in the case when $ Z, Z', Z''$ are MV cycles.
+
+In a similar way, we may consider the intersection multiplicities of a generalized orbital variety $ X$ in $X(\tau', \tau'')_{0,0} = M_N \times \{0\} \cap X(\tau', \tau'')_{0, \AA}$.
 \begin{corollary}
@@
 %Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ and $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?} irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties.
-We can compute intersection multiplicities by passing to dense constructible subsets.  
-By the isomorphisms of \Cref{lem:XtZt} and \Cref{pr:XttZtt}, $X(\tau) $ is a dense constructible subset of $ Z(\tau) $ and $ X(\tau', \tau'')_{0,0} $ is a dense constructible subset of $ Z(\tau') \ast_0 Z(\tau'') $.
+By the isomorphisms of \Cref{lem:XtZt} and \Cref{pr:XttZtt}, $X(\tau) $ is a dense constructible subset of $ Z(\tau) $ and $ X(\tau', \tau'')_{0,\AA} $ is a dense constructible subset of $ Z(\tau') \ast_\AA Z(\tau'') $.
+From the definition of intersection multiplicity, it is clear that the multiplicity can be computed locally and so the result follows.
 %  
@@
 % 
-\acom{A tuppence about this conjecture?}
+\acom{This conjecture comes out of nowhere}
 \begin{conjecture}
@@
 
-We use the convenient fact that $\GL_m^\vee = \GL_m$ and ignore the distinction, referring to points $t^\lambda$ as coweights for $\lambda\in\ZZ^m$ weights. 
+We use the convenient fact that $\GL_m^\vee = \GL_m$ and ignore the distinction between weights and coweights.
+
+%referring to points $t^\lambda$ as coweights for $\lambda\in\ZZ^m$ weights. 
 %
@@
 Also, maybe add a warning that some of the theorems we rely on hold more generally?
-Like the MV basis theorem..}
+Like the MV basis theorem..} \jcom{I don't think that is necessary.}
 
@@
 % Recall that MV cycles can be described combinatorially by Lusztig data. 
-By a theorem of the third author, a stable MV cycle is uniquely determined by its Lusztig datum and the sets $\cZ(\infty)$ and $\NN^{\Delta_+}$ are in bijection. 
+By a theorem of the third author, given a choice a reduced word for $ w_0 $, there is a bijection $ \cZ(\infty) \rightarrow \NN^{\Delta_+} $ called the Lusztig datum.
+For our purposes we will always use the standard reduced word.
+
+%a stable MV cycle is uniquely determined by its Lusztig datum and the sets $\cZ(\infty)$ and $\NN^{\Delta_+}$ are in bijection. 
 % Recall that Lusztig data, like elements of $\CC[N]$, are weighted by $Q_+$. 
-With a little bit more work one can string together the maps $\Psi_\lambda$ and the geometric Satake isomoprhisms to show that the stable MV cycles yield a basis of $\CC[N]$.
+One can string together the maps $\Psi_\lambda$ and the geometric Satake isomoprhisms to show that the stable MV cycles yield a basis of $\CC[N]$.
 
@@
 The set $ \{b_Z : Z \in \cZ(\infty) \}$ is called the \new{MV basis} of $ \CC[N]$.
-\jcom{I took the definition out of the theorem statement.}
+% \jcom{I took the definition out of the theorem statement.}
+% \acom{Ok}
 % 
@@
 $$
-in $\CC[N]$. \acom{The summation is finite since 7.1?... Don't want to introduce the notation $\cZ(\infty)_\nu$ if we can avoid it.} \jcom{The sum is finite for weight reasons.}
-Moreover, there exist $\lambda',\lambda''$ dominant effective and a pair of tableaux $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$ such that 
-\begin{equation}
-    \label{eq:multingovs}
-    % b_{Z'} \arfu b_{Z''} = \sum_{Z\in\cZ(\lambda)} \iota (Z, Z(\tau')\geofu Z(\tau''))b_{t^{-\lambda}Z}
-    b_{Z'} \arfu b_{Z''} = \sum_{\tau\in YT(\lambda)} \iota (X(\tau), X(\tau',\tau'')_{0,0})b_{t^{-\lambda}Z(\tau)}
-\end{equation}
-% 
-for $\lambda = \lambda' + \lambda''$. 
+in $\CC[N]$. 
+% \acom{The summation is finite since 7.1?... Don't want to introduce the notation $\cZ(\infty)_\nu$ if we can avoid it.} \jcom{The sum is finite for weight reasons.} 
+% 
 \end{theorem}
 \jcom{I would take the second part ``Moreover'' out of the statement of the theorem and state it as a corollary, maybe after Prop 7.3.}
-% Given $\epsilon\in\ZZ^m$ denote by $t^\epsilon:V(\lambda) \to V(\lambda + \epsilon)$ the map resulting from multiplication by the coweight $t^\epsilon$ in $\Gr$.
-By BKK, $\Psi_{\lambda + \epsilon} \circ t^\epsilon - \Psi_\lambda = 0$.
-% 
-% Together these facts imply the following commutative square.
-% \[
-% \begin{tikzcd}
-% L(\lambda) \ar[r] & \CC[N] \\
-% \Gr^\lambda \cap S^\mu_- \ar[r,"t^{-\lambda}"] \ar[u] & S^0 \cap S^{\mu - \lambda}_-\ar[u]
-% \end{tikzcd}
-% \]
+% 
 % \jcom{This paragraph is a bit confusing.
@@
 %
+
 In \Cref{s:examples} we will identify elements $b_Z$ with certain \textit{minimal} tableaux (instead of Lusztig data) and view $\CC[N]$ as an algebra in these tableaux, abbreviating \Cref{eq:multingovs} as equation in these tableaux.
@@
 \[
-% \begin{tikzcd}
-% \CC[N] & \ar[l] \cZ(\infty) \ar[r,"n_\bullet"] \ar[d,bend left,blue] & \NN^{\Delta_+} \ar[l,blue,bend left] \ar[d,bend left,blue]\\ 
-% L(\lambda) \ar[u,"\Psi_\lambda"] & \ar[l] \cZ(\lambda) \ar[r] \ar[u,"t^{-\lambda}"] & YT(\lambda) \ar[u,"n_\bullet"] \ar[l,blue,bend left]
-% \end{tikzcd}
 \begin{tikzcd}
-    YT(\lambda) \ar[r] \ar[d,"n_\bullet"] & \cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & L(\lambda) \ar[d, "\Psi_\lambda"] \\ %  description
+   \bigcup YT(\lambda)_+\ar[r,"\tau\mapsto X(\tau)"] & \bigcup \mathcal X(\lambda) & \\
+   \bigcup YT(\lambda) \ar[r,"\tau\mapsto Z(\tau)"] \ar[d,"n_\bullet"] & \bigcup\cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & \bigcup L(\lambda) \ar[d, "\Psi_\lambda"] \\ %  description
     \NN^{\Delta_+} \ar[r] \ar[u,dashed,bend left,"\sigma_\lambda"] & \cZ(\infty) \ar[r] & \CC[N]
@@
 
+    \acom{Grrr, padding might not work.}
+
     \acom{To be completed. We require a notion of ``smallest'' pair of factor tableaux associated to a given tableau --- that is if we care to include our $B(\infty)\to B(\lambda)$ map. 
@@
 \end{proposition}
+
+\begin{corollary}
+Moreover, there exist $\lambda',\lambda''$ dominant effective and a pair of tableaux $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$ such that 
+\begin{equation}
+    \label{eq:multingovs}
+    % b_{Z'} \arfu b_{Z''} = \sum_{Z\in\cZ(\lambda)} \iota (Z, Z(\tau')\geofu Z(\tau''))b_{t^{-\lambda}Z}
+    b_{Z'} \arfu b_{Z''} = \sum_{\tau\in YT(\lambda)} \iota (X(\tau), X(\tau',\tau'')_{0,0})b_{t^{-\lambda}Z(\tau)}
+\end{equation}
+% 
+for $\lambda = \lambda' + \lambda''$. 
+\end{corollary}
 
@@
 \begin{example}
-Let $G = \GL_3$ and consider the tableaux
-$$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$
-
-Lustig data: $(100)$ for $\tau'$, $(001)$ for $\tau''$.
+% Let $G = \GL_3$ and consider the tableaux
+% $$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$
+
+% Lustig data: $(100)$ for $\tau'$, $(001)$ for $\tau''$.
+$\young(2)\arfu\young(1,3)$:
 
@@
 $$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s]}{\langle A_{12}^1+sA_{12}^2, A_{12}^2A_{23}^1+sA_{13}^1, A_{12}^1A_{23}^1+s^2A_{13}^1, s\rangle} \cong \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,b_3,s]}{\langle A_{12}^1, A_{12}^2\rangle \cap \langle A_{12}^1, A_{23}^1 \rangle}.$$
-% 
-\acom{TODO: put ideals of arithmetic fusion and their tableaux into tables; also divide into 2 sections, $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with rising action?}
 % 
@@
 \begin{example}
+$\young(22)\arfu\young(11,33)$:
 
@@
 
-\subsection{Type $A_3$}
+\subsection{Type $A_3$}\label{ss:GL4 examples}
 
@@
 There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables.
-We will take the initial cluster $(x_1,\dots,x_6)$, with $x_4,x_5,x_6$ being frozen, coming from the reduced word ${\bf i} = (1,2,3,1,2,1)$.
+We will take the initial cluster $(x_1,\dots,x_6)$ coming from the reduced word ${\bf i} = (1,2,3,1,2,1)$.
 If we view $\CC[N] \cong \CC[x_{ij} : i < j]$, then
@@
 \end{table}
-\acom{Say what $x_i$ are: $\begin{bmatrix}
-    1 & x_1 & x_2 & x_3 \\
-    & 1 \\
-    & & 1 \\
-    & & & 1 
-\end{bmatrix}$}
 
@@
 We show that the cluster relations in $\CC[N]$ are also true for the fusion product of the corresponding MV cycles.
-
 For each of the 15 exchange relations, we state the associated matrix $X$, the relations acquired from each submatrix $X_i$, the ideal generated by said relations, and the corresponding tableaux from the ideal.
-
 Instead of writing the exchange relations in terms of $b_{Z(\tau)}$ or the fusion product in terms of $Z(\tau)$, we will use $\tau$ for both situations.
@@
 
+\acom{The example below is an $A_2$ example, the same as the first $A_2$ example above.}
 \begin{example}
@@
 \begin{example}
+\acom{Let's redo this as $\young(2,3)\arfu\young(11,2,4)$.}
+
 $\young(1,2,4) \cdot \young(12,3) = \young(1,4) + \young(1,3,4):$ The requirement that
@@
 \begin{example}
+\acom{Let's redo this as $\young(3)\arfu\young(11,24)$}
+
 $\young(13,2) \cdot \young(1,4) = \young(14,3) + \young(3,4):$ The requirement that
@@
 \begin{example}
+\acom{Let's redo this as $\young(2,3)\arfu\young(11,23,4)$.}
+
 $\young(12,23) \cdot \young(1,3,4) = \young(3,4) + \young(12,33,4):$ The requirement that
@@
 \begin{example}
+\acom{Let's redo this as $\young(1,3)\arfu\young(113,22,4)$.}
+
 $\young(11,23) \cdot \young(13,2,4) = \young(3,4) + \young(1,3,4):$ The requirement that
@@
 \begin{example}
+\acom{Let's redo this as $\young(2,3)\arfu\young(113,2,4)$.}
+
 $\young(13,2,4) \cdot \young(12,3) = \young(23,4) + \young(23,3,4):$ The requirement that
@@
 \begin{example}
+\acom{Let's redo this as $\young(1,4)\arfu\young(113,22,34)$.}
+
 $\young(11,24,3) \cdot \young(13,2,4) = \young(14,3,4) + \young(13,24,4):$ The requirement that
@@
 \begin{example}
+\acom{Let's redo this as $\young(2,4)\arfu\young(11,23,34)$.}
+
 $\young(12,24,3) \cdot \young(1,3,4) = \young(13,24,4) + \young(12,34,4):$ The requirement that
@@
 \begin{example}
+\acom{Let's redo this as $\young(2,4)\arfu\young(1113,22,34)$.}
+
 $\young(112,24,3) \cdot \young(13,2,4) = \young(24,3,4) + \young(123,24,4):$ The requirement that

### 2021-06-05 draft.tex
Editted examples

@@
 
-\acom{So far we have been saying ``coweight'' $\lambda$, etc.
-We could say coweight for $t^\lambda$ and weight for $\lambda$ starting now?
-Also, maybe add a warning that some of the theorems we rely on hold more generally?
-Like the MV basis theorem..} \jcom{I don't think that is necessary.}
+\acom{So far we have been saying ``coweight'' $\lambda$, etc. We could say coweight for $t^\lambda$ and weight for $\lambda$ starting now?}
+% \acom{Also, maybe add a warning that some of the theorems we rely on hold more generally? Like the MV basis theorem..} \jcom{I don't think that is necessary.}
 
@@
 
-\acom{Warning!
+% \acom{Warning!
 Earlier we defined the MV cycles as irreducible components of $\overline{\Gr^\lambda}\cap S^\mu$} \jcom{Good point.
@@
 I will think about the best way to fixe this and correct it.}
+% 
 % In particular, the MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$ give a basis of $V(\lambda)$. 
@@
 \end{theorem}
-\jcom{I would take the second part ``Moreover'' out of the statement of the theorem and state it as a corollary, maybe after Prop 7.3.}
+% \jcom{I would take the second part ``Moreover'' out of the statement of the theorem and state it as a corollary, maybe after Prop 7.3.}
+% \acom{Done}
 % 
@@
 
-In \Cref{s:examples} we will identify elements $b_Z$ with certain \textit{minimal} tableaux (instead of Lusztig data) and view $\CC[N]$ as an algebra in these tableaux, abbreviating \Cref{eq:multingovs} as equation in these tableaux.
-
-Before we describe how to choose representative generalized orbital varieties in order to expand a product of MV basis elements $b_{Z'}\arfu b_{Z''}$ in $\CC[N]$ we summarize our approach in the following commutative diagram.
+In \Cref{s:examples} we will identify elements $b_Z$ with certain \textit{minimal} tableaux (instead of Lusztig data) and view $\CC[N]$ as an algebra in these tableaux, rewriting (abbreviating) \Cref{eq:multingovs} as as equation in semistandard Young tableaux.
+We can do this because of 
+% Before we describe how to choose representative generalized orbital varieties in order to expand a product of MV basis elements 
+% $b_{Z'}\arfu b_{Z''}$
+% in $\CC[N]$ we summarize our approach in 
+the following commutative diagram. 
 \[
@@
 \]
-The fibres of $n_\bullet$ \acom{in $\cup YT(\lambda)$} contain tableaux related by padding. 
-While $Z(\tau)$ is defined even when $\mu$ is not dominant, $X(\tau)$ is not, and so we need to choose a section $\sigma_\lambda$ of $n_\bullet$ with image in the set of tableaux having dominant weight.
-%
-
 \acom{Should I adjust the diagram so that its from unions over $\lambda$}
@@
 
-% \jcom{In principle, the notation $ Z' \ast_0 Z''$ has been defined, since we defined the fusion of any two subschemes of $ \Gr$.
-We should just note that the fusion of the stable MV cycles matches the fusion of MV cycles after translation by $ t^\lambda$.
-I don't think that $ \iota$ has been defined anywhere, has it?}
+Two tableaux have equal Lusztig data if they differ by any number of boxes of weight $r$ in row $r$ for any $r$.
+We call this relation \new{padding}.
+In other words, the fibres of $n_\bullet$ contain tableaux related by padding.
+For example $\young(2,4)$ and $\young(112,24,3)$ have equal Lusztig data.
+
+While $Z(\tau)$ is defined even when $\mu$ is not dominant, $X(\tau)$ is not.
+To compute intersection multiplicities using generalized orbital varieties we therefore need to choose a section $\sigma_\lambda$ of $n_\bullet$ with image in the set of tableaux having dominant weight.
+%
 
 \begin{lemma}
-    \label{lem:mintab}
-    Let $n_\bullet$ be a Lusztig datum of coweight $\nu$.
-There exist $\lambda,\mu$ dominant effective smallest such that $n_\bullet$ is the Lusztig datum of a tableau $\tau\in YT(\lambda)_\mu$.
-They are determined by the following minimization problem.
-Regard $n_\bullet$ as a strictly lower triangular matrix with $(r,c)$th entry $n_{r,c}$ is equal to the number of boxes of weight $r$ in row $c$ of $\tau$.
-Note that since $r > c$ this data does not account for the number of boxes of weight $r$ in row $r$.
-Let $\mu^0$ be the diagonal matrix whose $(r,r)$th entry $\mu^0_r$ is equal to the number of boxes of weight $r$ in row $r$ of $\tau$.
-Note that the sum of the rows of $n_\bullet + \mu^0$ is the shape $\lambda$ of $\tau$, and the sum of the columns of $n_\bullet + \mu^0$ is the weight $\mu$ of $\tau$.
-The solution to the minimization problem
+\label{lem:almostmintab}
+Let $n_\bullet = (n_{(a,b)})$ be a Lusztig datum of coweight $\nu$ viewed as a strictly lower-triangular $m\times m$ matrix with 
+% $(w,r)$
+$(a,b)$th entry equal to the number of boxes of weight $a$ in row $b$ for $1\le b < a \le m$. 
+Let $\mu^0$ be a diagonal matrix with $a$th diagonal entry denoted $\mu^0_a$. The solution to the minimization problem 
 \[
-        \begin{gathered}
-        % 
-        \text{minimize }\mu^0\text{ such that} \\
-        % \text{the sum of the rows of }n_\bullet + \mu^0\text{ is non-increasing},
-        % \text{the sum of the columns of }n_\bullet + \mu^0\text{ is non-increasing}
-        \text{both }\lambda,\mu\text{ are non-increasing}
-        \end{gathered} 
+\text{minimize }\mu^0\text{ such that } \lambda = (\sum_b n_{(a,b)} + \mu^0_b)_a \text{ and } \mu = (\sum_a n_{(a,b)} + \mu^0_a)_b
+% sum rows and sum columns
+\text{ are dominant effective}
 \]
-    is got recursively from % setting $\mu^0_m = 0$, 
+is 
 \[
@@
 for $i = 1,\dots,m-2$. 
-    In words, given a Luszig datum $n_\bullet$, if we wish to produce a minimal SSYT for it, 
+\end{lemma}
+
+In words, if we wish to produce a dominant weight tableau with Lusztig datum $n_\bullet$ of smallest possible shape and weight 
     \begin{itemize}
@@
     \end{itemize}
-\end{lemma}
+
+[Proposition]
+
+To write down an expansion in $\CC[N]$ we choose a section $\bar\sigma_\lambda$ valued in smallest (not necessarily dominant) representative tableaux.
+
+% \jcom{In principle, the notation $ Z' \ast_0 Z''$ has been defined, since we defined the fusion of any two subschemes of $ \Gr$.
+We should just note that the fusion of the stable MV cycles matches the fusion of MV cycles after translation by $ t^\lambda$.
+I don't think that $ \iota$ has been defined anywhere, has it?}
+
+% \begin{lemma}
+%     \label{lem:mintab}
+%     Let $n_\bullet$ be a Lusztig datum of coweight $\nu$.
+There exist $\lambda,\mu$ dominant effective smallest such that $n_\bullet$ is the Lusztig datum of a tableau $\tau\in YT(\lambda)_\mu$.
+They are determined by the following minimization problem.
+Regard $n_\bullet$ as a strictly lower triangular matrix with $(r,c)$th entry $n_{r,c}$ is equal to the number of boxes of weight $r$ in row $c$ of $\tau$.
+Note that since $r > c$ this data does not account for the number of boxes of weight $r$ in row $r$.
+Let $\mu^0$ be the diagonal matrix whose $(r,r)$th entry $\mu^0_r$ is equal to the number of boxes of weight $r$ in row $r$ of $\tau$.
+Note that the sum of the rows of $n_\bullet + \mu^0$ is the shape $\lambda$ of $\tau$, and the sum of the columns of $n_\bullet + \mu^0$ is the weight $\mu$ of $\tau$.
+The solution to the minimization problem
+%     \[
+%         \begin{gathered}
+%         % 
+%         \text{minimize }\mu^0\text{ such that} \\
+%         % \text{the sum of the rows of }n_\bullet + \mu^0\text{ is non-increasing},
+%         % \text{the sum of the columns of }n_\bullet + \mu^0\text{ is non-increasing}
+%         \text{both }\lambda,\mu\text{ are non-increasing}
+%         \end{gathered} 
+%     \]
+%     is got recursively from % setting $\mu^0_m = 0$, 
+%     \[
+%         \begin{gathered}
+%             \mu^0_{m} = 0 \\ 
+%             \mu^0_{m-1} = \max\{0 , \sum n_{m,c} - \sum n_{m-1,c}\} \\ 
+%             \mu^0_i = \max\{0, \mu^0_{i+1} + \sum n_{i+1,c} - \sum n_{i,c} , \mu_{i+1}^0 + \sum n_{r,i+1} - \sum n_{r,i}\}
+%         \end{gathered}
+%     \]
+%     for $i = 1,\dots,m-2$. 
+% \end{lemma}
 
@@
 \begin{example}
-\acom{Let's redo this as $\young(2,3)\arfu\young(11,2,4)$.}
-
-$\young(1,2,4) \cdot \young(12,3) = \young(1,4) + \young(1,3,4):$ The requirement that
+% \acom{Let's redo this as $\young(2,3)\arfu\young(11,2,4)$.}
+
+$\young(11,2,4) \cdot \young(2,3) = \young(1,4) + \young(1,3,4):$ The requirement that
 \[
@@
     0 & 1 & & & & \\
-     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
+     & 0 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
      & & 0 & 1 & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1,2,4) *_{\AA \setminus \{0\}} \young(12,3)
+\right] \text{ is contained in } \young(11,2,4) *_{\AA \setminus \{0\}} \young(2,3)
 \]
@@
 \begin{example}
-\acom{Let's redo this as $\young(3)\arfu\young(11,24)$}
-
-$\young(13,2) \cdot \young(1,4) = \young(14,3) + \young(3,4):$ The requirement that
+% \acom{Let's redo this as $\young(3)\arfu\young(11,24)$}
+
+$\young(11,24) \cdot \young(3) = \young(14,3) + \young(3,4):$ The requirement that
 \[
@@
     0 & 1 & & & \\
-     & s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
+     & 0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
      & & 0 & A_{23}^1 & A_{24}^1 \\
-     & & & 0 & A_{34}^1 \\
-     & & & & s
+     & & & s & A_{34}^1 \\
+     & & & & 0
 \end{BMAT}
-\right] \text{ is contained in } \young(13,2) *_{\AA \setminus \{0\}} \young(1,4)
+\right] \text{ is contained in } \young(11,24) *_{\AA \setminus \{0\}} \young(3)
 \]
@@
     A_2 & A_{12}^1 \\
-    A_4 & A_{13}^1A_{34}^1 + sA_{14}^1
+    A_4 & A_{13}^1A_{34}^1 - sA_{14}^1
     \end{tabular}
@@
 \begin{example}
-\acom{Let's redo this as $\young(2,3)\arfu\young(11,23,4)$.}
-
-$\young(12,23) \cdot \young(1,3,4) = \young(3,4) + \young(12,33,4):$ The requirement that
+% \acom{Let's redo this as $\young(2,3)\arfu\young(11,23,4)$.}
+
+$\young(11,23,4) \cdot \young(2,3) = \young(3,4) + \young(12,33,4):$ The requirement that
 \[
@@
     0 & 1 & & & & & \\
-     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
+     & 0 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
      & & 0 & 1 & & & \\
-     & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
+     & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
      & & & & 0 & 1 & \\
      & & & & & s & A_{34}^1 \\
-     & & & & & & s
+     & & & & & & 0
 \end{BMAT}
-\right] \text{ is contained in } \young(12,23) *_{\AA \setminus \{0\}} \young(1,3,4)
+\right] \text{ is contained in } \young(11,23,4) *_{\AA \setminus \{0\}} \young(2,3)
 \]
@@
 % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
+%     A_2 & A_{12}^1 \\
+%     A_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
+%     A_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
+%     \end{tabular}
+% \end{table}
 \begin{table}[H]
@@
     A_2 & A_{12}^1 \\
-    A_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
-    A_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
+    A_3 & A_{12}^2A_{23}^1 - sA_{13}^1, A_{23}^1 + sA_{23}^2, A_{12}^2A_{23}^2+A_{13}^1 \\
+    A_4 & A_{34}^1, A_{12}^2A_{24}^1 - sA_{14}^1, A_{14}^1A_{23}^1 - A_{13}^1A_{24}^1
     \end{tabular}
@@
 \begin{example}
-\acom{Let's redo this as $\young(1,3)\arfu\young(113,22,4)$.}
-
-$\young(11,23) \cdot \young(13,2,4) = \young(3,4) + \young(1,3,4):$ The requirement that
+% \acom{Let's redo this as $\young(1,3)\arfu\young(113,22,4)$.}
+
+$\young(113,22,4) \cdot \young(1,3) = \young(3,4) + \young(1,3,4):$ The requirement that
 \[
@@
      & & & 0 & 1 & & & \\
-     & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
+     & & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
      & & & & & 0 & 1 & \\
      & & & & & & s & A_{34}^1 \\
-     & & & & & & & s
+     & & & & & & & 0
 \end{BMAT}
-\right] \text{ is contained in } \young(11,23) *_{\AA \setminus \{0\}} \young(13,2,4)
+\right] \text{ is contained in } \young(113,22,4) *_{\AA \setminus \{0\}} \young(1,3)
 \]
@@
 % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
+%     A_2 & A_{12}^1, A_{12}^2 \\
+%     A_3 & A_{13}^1 \\
+%     A_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
+%     \end{tabular}
+% \end{table}
 \begin{table}[H]
@@
     A_2 & A_{12}^1, A_{12}^2 \\
-    A_3 & A_{13}^1 \\
-    A_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
+    A_3 & A_{13}^1 + sA_{13}^2 \\
+    A_4 & A_{34}^1, A_{14}^1 A_{23}^1 - A_{13}^1 A_{24}^1
     \end{tabular}
@@
 \begin{example}
-\acom{Let's redo this as $\young(2,3)\arfu\young(113,2,4)$.}
-
-$\young(13,2,4) \cdot \young(12,3) = \young(23,4) + \young(23,3,4):$ The requirement that
+% \acom{Let's redo this as $\young(2,3)\arfu\young(113,2,4)$.}
+
+$\young(113,2,4) \cdot \young(2,3) = \young(23,4) + \young(23,3,4):$ The requirement that
 \[
@@
     0 & 1 & & & & & \\
-     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
+     & 0 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
      & & 0 & 1 & & & \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(13,2,4) *_{\AA \setminus \{0\}} \young(12,3)
+\right] \text{ is contained in } \young(113,2,4) *_{\AA \setminus \{0\}} \young(2,3)
 \]
@@
 \begin{example}
-\acom{Let's redo this as $\young(1,4)\arfu\young(113,22,34)$.}
-
-$\young(11,24,3) \cdot \young(13,2,4) = \young(14,3,4) + \young(13,24,4):$ The requirement that
+% \acom{Let's redo this as $\young(1,4)\arfu\young(113,22,34)$.}
+
+$\young(113,22,34) \cdot \young(1,4) = \young(14,3,4) + \young(13,24,4):$ The requirement that
 \[
@@
      & & & 0 & 1 & & & & \\
-     & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
+     & & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
      & & & & & 0 & 1 & & \\
-     & & & & & & s & A_{34}^1 & A_{34}^2 \\
+     & & & & & & 0 & A_{34}^1 & A_{34}^2 \\
      & & & & & & & 0 & 1 \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,24,3) *_{\AA \setminus \{0\}} \young(13,2,4)
+\right] \text{ is contained in } \young(113,22,34) *_{\AA \setminus \{0\}} \young(1,4)
 \]
@@
 % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
+%     A_2 & A_{12}^1,A_{12}^2 \\
+%     A_3 & A_{13}^1, A_{23}^1 \\
+%     A_4 & A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
+%         & A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2 
+%     \end{tabular}
+% \end{table}
 \begin{table}[H]
@@
     A_3 & A_{13}^1, A_{23}^1 \\
-    A_4 & A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
-        & A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2 
+    A_4 & A_{34}^1, A_{13}^2 A_{34}^2 + A_{14}^1 + sA_{14}^2, A_{14}^1 A_{23}^2 - A_{13}^2 A_{24}^1
     \end{tabular}
@@
 \begin{example}
-\acom{Let's redo this as $\young(2,4)\arfu\young(11,23,34)$.}
-
-$\young(12,24,3) \cdot \young(1,3,4) = \young(13,24,4) + \young(12,34,4):$ The requirement that
+% \acom{Let's redo this as $\young(2,4)\arfu\young(11,23,34)$.}
+
+$\young(11,23,34) \cdot \young(2,4) = \young(13,24,4) + \young(12,34,4):$ The requirement that
 \[
@@
     0 & 1 & & & & & & \\
-     & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
+     & 0 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
      & & 0 & 1 & & & & \\
-     & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
+     & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
      & & & & 0 & 1 & & \\
-     & & & & & s & A_{34}^1 & A_{34}^2 \\
+     & & & & & 0 & A_{34}^1 & A_{34}^2 \\
      & & & & & & 0 & 1 \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(12,24,3) *_{\AA \setminus \{0\}} \young(1,3,4)
+\right] \text{ is contained in } \young(11,23,34) *_{\AA \setminus \{0\}} \young(2,4)
 \]
@@
 % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
+%   A_2 & A_{12}^1 \\
+%     A_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
+%     A_4 & 
+%          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+%         & A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2, A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
+%         & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1
+%     \end{tabular}
+% \end{table}
 \begin{table}[H]
@@
     A_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
-    A_4 & 
-         A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-        & A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2, A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
-        & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1
+    A_4 & A_{34}^1, A_{23}^2 A_{34}^2 + A_{24}^1 + sA_{24}^2, A_{12}^2 A_{24}^2 + A_{13}^2 A_{34}^2 + A_{14}^1, A_{12}^2 A_{24}^1 - sA_{14}^1, \\
+    & A_{14}^1 A_{23}^2 - A_{13}^2 A_{24}^1, A_{13}^2 A_{24}^1 A_{34}^2 + A_{14}^1 A_{24}^1 + sA_{14}^1 A_{24}^2
     \end{tabular}
@@
 \begin{example}
-\acom{Let's redo this as $\young(2,4)\arfu\young(1113,22,34)$.}
-
-$\young(112,24,3) \cdot \young(13,2,4) = \young(24,3,4) + \young(123,24,4):$ The requirement that
+% \acom{Let's redo this as $\young(2,4)\arfu\young(1113,22,34)$.}
+
+$\young(1113,22,34) \cdot \young(2,4) = \young(24,3,4) + \young(123,24,4):$ The requirement that
 \[
@@
      & 0 & 1 & & & & & & & \\
-     & & s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
+     & & 0 & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
      & & & 0 & 1 & & & & & \\
@@
      & & & & & & 0 & 1 & & \\
-     & & & & & & & s & A_{34}^1 & A_{34}^2 \\
+     & & & & & & & 0 & A_{34}^1 & A_{34}^2 \\
      & & & & & & & & 0 & 1 \\
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(112,24,3) *_{\AA \setminus \{0\}} \young(13,2,4)
+\right] \text{ is contained in } \young(1113,22,34) *_{\AA \setminus \{0\}} \young(2,4)
 \]
@@
 % 
+% \begin{table}[H]
+%   \centering
+%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+%   \begin{tabular}{Q} 
+%     \text{Submatrix} & \text{Relations} \\
+%     \midrule 
+%   A_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
+%     A_3 & A_{13}^1,A_{23}^1 \\
+%     A_4 & A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
+%         & A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
+%         & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
+%         & A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
+%         & A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
+%     \end{tabular}
+% \end{table}
 \begin{table}[H]
@@
     \midrule 
-   A_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
+   A_2 & A_{12}^1, A_{12}^2 \\
     A_3 & A_{13}^1,A_{23}^1 \\
-    A_4 & A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-        & A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
-        & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
-        & A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
-        & A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
+    A_4 & A_{34}^1, A_{23}^2 A_{34}^2 + A_{24}^1 + sA_{24}^2, A_{14}^1 A_{23}^2 - A_{13}^2 A_{24}^1, A_{13}^2 A_{24}^1 A_{34}^2 + A_{14}^1 A_{24}^1 + sA_{14}^1 A_{24}^2
     \end{tabular}

### 2021-06-07 draft.tex
Editted examples section

@@
     \item Remove the TOC 
+    \item a shorthand: in examples, instead of writing $Z(\tau)$ for the MV cycle corresponding to the tableau $\tau$ we will only the tableau $\tau$!
+    \item our $B(\infty) \to B(\lambda)$ does not match that of Claxton--Tingley or Hong--Lee but discussing how the two are related might be irrelevant since we don't worry about the crystal structure on MV cycles anyway (let alone investigate possible compatibility with the crystal structure on SSYT given $\tau\mapsto Z(\tau)$); \acom{perhaps we could mention that we don't know if this map is compatible with crystal structures} (but suspect there is a way of making it so);
     \item Edit the intro 
     \item We are using the word [geometric] fusion just for the central fibre, we also have arithmetic fusion (aka multiplication in $\CC[N]$), and BD family: $X\geofu Y, b(X) \arfu b(Y), X \bdfamc Y\supset X\bdfamo Y$
-    \item Which MVy paper to cite? 
+    \item[\checkmark] Which MVy paper to cite? Both
     \item Super repetitive about lambdas and mus 
@@
     \item Recalling intersection multiplicity, checking that the definitions allow passing to open sets
-    \item in examples put ideals of arithmetic fusion and their tableaux into tables; also split examples into 2 sections: $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with rising action?
+    \item[\checkmark] in examples put ideals of arithmetic fusion and their tableaux into tables; also split examples into 2 sections: $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with rising action?
 \end{itemize}
@@
 %Throughout this paper (unless indicated otherwise) the base field is $\CC$, but it does not have to be?  
-
+\subsection{Geometric Satake and Mirkovic--Vilonen cycles}
 The geometric Satake equivalence of Mirkovi\'c and Vilonen \cite{mirkovic2007geometric} provides an equivalence of categories between the category of spherical perverse sheaves in the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.
@@
 % The Mirkovi\'c--Vybornov isomorphism
-In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_N)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $N\times N$ nilpotent orbits on the one hand
+In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_N)$ dualities.
+They relate Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $N\times N$ nilpotent orbits on the one hand,
 % conjugacy classes of nilpotent matrices 
 and to Nakajima quiver varieties on the other hand.
-The second author showed \cite{dthesis} that under the Mirkovi\'c-Vybornov isomorphism, the  Mirkovi\'c--Vilonen cycles are identified with certain varieties of matrices, called generalized orbital varieties.
+The second author \cite{dthesis} showed  that under the Mirkovi\'c-Vybornov isomorphism, the MV cycles are identified with certain varieties of matrices, called generalized orbital varieties.
 
@@
 In \cite{anderson2003polytope}, Anderson used the Beilinson--Drinfeld Grassmannian to define a fusion of Mirkovi\'c--Vilonen cycles.
-He conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup $ N \subset\GL_m$.
-This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that the Mirkovi\'c--Vilonen cycles give a basis for $ \CC[N]$, which we call the MV basis.
+He constructed a family where the general fibre is a Cartesian product of two MV cycles, and the special fibre, called the fusion, is a (non-reduced) union of MV cycles.
+Anderson conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup $ N \subset\GL_m$.
+This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that the MV cycles give a basis for $ \CC[N]$.
 % 
@@
 
-Unfortunately, computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.
+\subsection{Fusion using generalized orbital varieties}
+% \acom{imho, fortune has nothing to do with it :)}
+% Unfortunately, c
+Computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.
 A few such computations were done by Anderson-Kogan in \cite{anderson2006algebra} in a somewhat ad-hoc fashion.
-Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann-Gaussent-Littelmann \cite{baumann2020bases}.
+Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann, Gaussent \& Littelmann \cite{baumann2020bases}.
 
 The purpose of this paper is to give a conceptually elementary way to compute this product by transferring it to a fusion product of generalized orbital varieties.
-To do so, we use that the Mirkovic-Vybornov isomorphism extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of matrices with two eigenvalues.
+To do so, we use that the Mirkovic-Vybornov isomorphism extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of slices of matrices with two eigenvalues.
 Our main result is the following.
 
-\begin{maintheorem}
+\begin{theorem}
     Let $ Z, Z' $ be MV cycles.
-The structure constants for the multiplication of $ b_Z b_{Z'}$ in $\CC[N]$ are equal to the intersection multiplicities in the fusion of the generalized orbital varieties corresponding to $ Z, Z'$.
-\end{maintheorem}
+The structure constants for the multiplication $ b_Z b_{Z'}$ in $\CC[N]$ are equal to the intersection multiplicities in the fusion of the generalized orbital varieties corresponding to $ Z, Z'$.
+\end{theorem}
 % 
 \jcom{I wanted to state a precise theorem, but it is not so easy without introducing a lot of notation.}
+\acom{Are you ok with the 'maintheorem' environemnt?}
+
+Since these generalized orbital varieties are subschemes of affine spaces of matrices defined by certain rank conditions, the fusion of generalized orbital varieties can be computed by elementary commutative algebra.
 
 %One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!
-
-An application of this result is to relate the cluster algebra structure in $\CC[N]$ to the MV basis.
-Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{berenstein2005cluster3} and \cite{geiss2007initial} that $\CC[N]$ has a natural cluster algebra structure.
-
-This structure starts with an initial seed $\Sigma = ((x_1,\cdots,x_r),B)$ where $x_i \in \CC[N]$ and $B$ is some matrix.
+\subsection{Cluster algebras and MV cycles}
+One motivation for computing products of MV basis elements is to relate the cluster algebra structure on $\CC[N]$ to the MV basis.
+Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{geiss2007initial}, using the construction of \cite{berenstein2005cluster3}, that $\CC[N]$ has a natural cluster algebra structure.
+\acom{As a reader I am confused - did both of them show it independently?
+Can I go to either source to find out how this works?
+I suggest ``in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}''} \rcom{I agree with the suggestion.}
+
+This structure starts with an initial seed $\Sigma = ((x_1,\dots,x_r),B)$, where $x_i \in \CC[N]$, $B$ is a certain matrix, and $ r = m(m-1)/2$ ($=\#\Delta_+$).
 We obtain new variables through a process called mutation where for a mutable variable $x_i$, its mutation is the unique element $x_i^* \in \CC[N]$ such that $$x_ix_i^* = x_+ + x_-.$$
-This equation is called an exchange relation and the terms $x_+$ and $x_-$ are some product in the $x_j$, $j\neq i$, that is determined by $B$.
-We then obtain a new seed $$\mu_i(\Sigma) = ((x_1,\cdots, x_{i-1}, x_i^*, x_{i+1},\cdots,x_r), \mu_i(B))$$ and can acquire possibly new variables through further mutations.
+This equation is called an exchange relation and the terms $x_+$ and $x_-$ are certain monomials in the $x_j$, $j\neq i$,  determined by $B$. 
+%We then obtain a new seed $$\mu_i(\Sigma) = ((x_1,\cdots, x_{i-1}, x_i^*, x_{i+1},\cdots,x_r), \mu_i(B))$$ and can acquire possibly new variables through further mutations.
 
@@
 
-It has been shown that the cluster monomials are in certain interesting bases such as the dual canonical basis \cite{lusztig1990canonicalbases}\cite{kang2018monoidal} and the dual semicanonical basis \cite{lusztig2000semicanonical}\cite{geiss2006rigid}.
+\acom{It would be nice to add a line to set up this paragraph.
+Else the canonical bases come out of nowhere?
+Like ``There is another nice structure on $\CC[N]$, that of a \new{perfect basis} introduced by/studied by...; and heaps of work (or just the following two sources) suggests that the two structures are inextricably linked.'' Because it's a paper and not a talk.}
+\rcom{Something along these lines?}
+There are two well-known bases of $\CC[N]$ whose relationship with the cluster structure has been studied heavily: the dual canonical basis \cite{lusztig1990canonicalbases} and the dual semicanonical basis \cite{lusztig2000semicanonical}.
+Kang, Kashiwara, Kim \& Oh showed that all cluster monomials are contained in the dual canonical basis \cite{kang2018monoidal} while Gei\ss, Leclerc, \& Schr\"oer proved that they are all contained in the dual semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
+% 
+%It has been shown that the cluster monomials are in certain interesting bases such as the dual canonical basis \cite{lusztig1990canonicalbases}\cite{kang2018monoidal} and the dual semicanonical basis \cite{lusztig2000semicanonical}\cite{geiss2006rigid}.
 As these elements are defined in a combinatorial way, it allows efficient computation of several elements of these bases.
-
-Although the MV basis and the above mentioned bases are in general different from each other \cite{baumann2019mirkovic}, it is believed that they at least all contain the cluster monomials, leading to the following conjecture.
+% 
+%\acom{Re: above paragraph, I actually dug up the precise references in rewriting this so maybe we can preserve that...}
+%a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
+This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
+%Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.}
+%
+
+Although the MV basis differs from these bases (at least at the Kashiwara--Saito counterexample \cite[Appendix]{baumann2019mirkovic}), they are all examples of biperfect bases \cite{baumann2019mirkovic}.
+% and the above mentioned bases are in general different from each other \cite{baumann2019mirkovic}, 
+\acom{can we say something other than ``it is believed'', like ``Evidence/calculations/etc.\ suggests''}
+%along with evidence suggests that they all contain the cluster monomials, leading to the following conjecture.
+This then leads to the following conjecture.
 
@@
 
-The conjecture is true in type $A_n$ with $n\leq 3$ as in these cases, the MV basis agrees with the dual semicanonical and dual canonical bases \cite{baumann2019mirkovic}.
-It has also been shown that cluster monomials supported on seeds satisfying a special condition are also in the MV basis \cite{baumann2020bases}.
-In addition, cluster variables coming from the initial seeds constructed in \cite{berenstein2005cluster3} are also in the MV basis \cite{kato2011polytopal}.
-
-This leads to the following idea to show that the cluster variables are in the MV basis.
+The conjecture is true in type $A_n$ for $n\leq 3$ 
+% as the MV basis and the dual semicanonical basis agree in these cases 
+since in these cases $\CC[N]$ has a unique biperfect basis (C.f.\ \cite{baumann2019mirkovic}).
+% 
+More generally, cluster monomials supported on seeds satisfying certain extra conditions were shown to be in the MV basis in \cite{baumann2020bases}. 
+Also, cluster variables coming from the initial seeds constructed in \cite{berenstein2005cluster3} are in the MV basis \cite{baumann2019mirkovic}.
+
+% \acom{Re the above paragraph, I like how it was: It has been shown in \cite{kato2011polytopal} that for initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word in the Weyl group for $G$, each $x_i$ is in the MV basis as these correspond to generalized minors introduced in \cite{berenstein2005cluster3} created in \cite{geiss2007initial} for the dual semicanonical basis.
+If the reduced expression satisfies a special condition, then the cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.}
+
+%This leads to the following idea to show that the cluster variables are in the MV basis.
 Given a seed $((x_1,\cdots,x_r),B)$ with each of the $x_i$ in the MV basis, say corresponding to MV cycles $Z_i^*$, and an exchange relation $x_ix_i^* = x_+ + x_-$, it suffices to find an MV cycle $Z_i^*$ such that the fusion product of $Z_i$ and $Z_i^*$ gives $Z_+$ and $Z_-$, corresponding respectively to $x_+$ and $x_-$.
@@
 
-We show in Section \ref{ss:GL4 examples} that this is indeed the case in type $A_3$ by directly computing each fusion product corresponding to an exchange relation.
+In particular, we hope that each exchange relation can be realized using the fusion of MV cycles.
+If so, we are then able to conclude that all cluster variables are in the MV basis.
+We show in Section \ref{ss:GL4 examples} that this is indeed the case in type $A_3$, by directly computing each fusion product corresponding to an exchange relation.
 
@@
 % $\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
-% % that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
+% that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
 
 % \acom{Background on cluster:}
-% In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
-This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
-% Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
 
@@
 
-\section{Players}
+\section{Supporting Cast}
 \label{s:players}
@@
 
-\subsection{Affine Grassmannians} 
-\label{ss:affgrs}
+\section{Affine Grassmannians} 
+\label{s:affgrs}
 % To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
@@
 
-\acom{Comment why the above doesn't make sense for $\mu$ not dominant?}
-\jcom{It does make sense when $ \mu $ is not dominant.
+% \acom{Comment why the above doesn't make sense for $\mu$ not dominant?}
+% \jcom{It does make sense when $ \mu $ is not dominant.
 The reason for restricting to dominant $ \mu $ is so that $ S^\mu \subset \cW^\mu$.
@@
 
-\jcom{Following Anne's comment above about dominant $ \mu$, I decided to move this result here.}
+% \jcom{Following Anne's comment above about dominant $ \mu$, I decided to move this result here.}
+% \acom{The observation is verified in Anne's thesis}
 
@@
 \section{Rising Action} 
-\label{s:theproblem}
-
+\label{s:rising}
+
+\subsection{Linear Operators from Affine Grassmannians}
+\label{s:latticefacts}
+% 
 Throughout this section, we continue our notation of the previous sections.
@@
 % 
-\section{Climax}
-\label{s:climax}
+% \section{Climax}
+% \label{s:climax}
+\subsection{Matrices from Affine Grassmannians}
+\label{ss:mvyisos}
+% 
 Throughout this section, we continue our notation of the previous sections.
@@
 
-\section{\sout{Falling Action}} % Resolution  
-\label{se:falling}
+% \section{\sout{Falling Action}} % Resolution  
+% \label{se:falling}
+\section{Climax}
+\label{s:climax}
 \subsection{MV cycles}
+\label{ss:mvcs}
 %Let $Q_+$ denote the $\ZZ_{\ge 0}$-span of the positive coroots. 
@@
 
-The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \new{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
+The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \new{Gelfand--Tsetlin pattern} (see \cite[Sect.~4]{berenstein1988tensor}) $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
 % \acom{For Joel: weight or filling? See line below.}
@@
 Below is an example with $\lambda = (4,2)$ and $\mu = (3,2,1)$.
-\acom{GT patterns were introduced in \cite{berenstein1988tensor} to study branching?
-In particular \S 4 of that paper introduces the map from tableaux to patterns.
-Note that the map is not 1-to-1.}
+% \acom{GT patterns were introduced in \cite{berenstein1988tensor} to study branching? In particular \S 4 of that paper introduces the map from tableaux to patterns. Note that the map is not 1-to-1.}
 
@@
 It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2004mirkovic} (see Section 9 in \cite{kamnitzer2010mirkovic}).
-We remeark that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.
+We remark that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.
 
@@
 % 
-In fact, these are all the generalized orbital varieties:
+% In fact, these are all the generalized orbital varieties:
 \begin{theorem}(\cite[Theorem~4.8.2]{dthesis})
@@
 We quickly recall the
-definition of intersection multiplicity that we will need following \cite[Eg. 2.6.5]{Fulton}. We consider a fibre square of $\CC$-schemes
+definition of intersection multiplicity that we will need following \cite[Example~2.6.5]{fulton2016intersection}. We consider a fibre square of $\CC$-schemes
 $$
@@
 of $V$ along $Z$, where $f$ is a local equation of $D|_V$ on an affine
-open subset of $V$ which meets $Z$. Following \cite[chap.~7]{Fulton},
+open subset of $V$ which meets $Z$. Following \cite[chap.~7]{fulton2016intersection},
 this multiplicity is denoted by $i(Z,D\cdot V)$.
@@
 For $ Z', Z'' $ subvarieties of $ \Gr $, $V = Z'\ast_\AA Z''\subset\Grbd$ is a variety not contained in the support of $D$.
-Then we choose an irreducible component $Z$ of $W := D \cap V = X\ast_0 Y$.
-Thus, we may consider the intersection multiplicity $ i(Z, X \ast_0 Y) := i(Z, D \cdot V)$.
+Then we choose an irreducible component $Z$ of $W := D \cap V = Z'\ast_0 Z''$.
+Thus, we may consider the intersection multiplicity $ i(Z, Z'\ast_0 Z'') := i(Z, D \cdot V)$.
 We will be particularly interested in the case when $ Z, Z', Z''$ are MV cycles.
@@
 \begin{corollary}
-\label{cor:iota}
+\label{cor:intmul}
     % The image of $\mathring X(\tau',\tau'')_{0,0}$ in $\mathring Z(\tau')\ast_0 \mathring Z(\tau'')$ is dense. In particular 
-    $\iota(X(\tau), X(\tau',\tau'')_{0,0}) = \iota( Z(\tau), Z(\tau')\ast_0 Z(\tau''))\,.$
+    $i(X(\tau), X(\tau',\tau'')_{0,0}) = i( Z(\tau), Z(\tau')\ast_0 Z(\tau''))\,.$
 \end{corollary}
@@
 % 
-\acom{This conjecture comes out of nowhere}
-\begin{conjecture}
-    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
-    Let $\tau$ be the tableau got by taking the union of the rows of $\tau'$ and $\tau''$ and ordering the entries in each row smallest to largest. 
-    % Note that $\tau$ has shape $\lambda$, weight $\mu$, and  Lusztig datum equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
-    Then 
-    \begin{equation}
-        \iota(Z(\tau), Z(\tau') \geofu Z(\tau'')) = 1 \,. 
-    \end{equation}
-\end{conjecture}
+% \acom{This conjecture comes out of nowhere}
+% \begin{conjecture}
+%     % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
+%     Let $\tau$ be the tableau got by taking the union of the rows of $\tau'$ and $\tau''$ and ordering the entries in each row smallest to largest. 
+%     % Note that $\tau$ has shape $\lambda$, weight $\mu$, and  Lusztig datum equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
+%     Then 
+%     \begin{equation}
+%         i(Z(\tau), Z(\tau') \geofu Z(\tau'')) = 1 \,. 
+%     \end{equation}
+% \end{conjecture}
 % 
@@
 
-\acom{So far we have been saying ``coweight'' $\lambda$, etc. We could say coweight for $t^\lambda$ and weight for $\lambda$ starting now?}
+% \acom{So far we have been saying ``coweight'' $\lambda$, etc. We could say coweight for $t^\lambda$ and weight for $\lambda$ starting now?}
 % \acom{Also, maybe add a warning that some of the theorems we rely on hold more generally? Like the MV basis theorem..} \jcom{I don't think that is necessary.}
@@
 $$
-b_{Z'}\arfu b_{Z''} = \sum_{Z\in\cZ(\infty)} \iota\left(Z, Z' \geofu Z''\right) b_Z 
+b_{Z'}\arfu b_{Z''} = \sum_{Z\in\cZ(\infty)} i\left(Z, Z' \geofu Z''\right) b_Z 
 $$
@@
 
-In \Cref{s:examples} we will identify elements $b_Z$ with certain \textit{minimal} tableaux (instead of Lusztig data) and view $\CC[N]$ as an algebra in these tableaux, rewriting (abbreviating) \Cref{eq:multingovs} as as equation in semistandard Young tableaux.
+In \Cref{s:examples} we will identify elements $b_Z$ with certain \textit{minimal} tableaux (instead of Lusztig data) and view $\CC[N]$ as an algebra in these tableaux, rewriting (abbreviating) \Cref{eq:multingovs} as an equation in semistandard Young tableaux.
 We can do this because of 
@@
 \begin{tikzcd}
-   \bigcup YT(\lambda)_+\ar[r,"\tau\mapsto X(\tau)"] & \bigcup \mathcal X(\lambda) & \\
-   \bigcup YT(\lambda) \ar[r,"\tau\mapsto Z(\tau)"] \ar[d,"n_\bullet"] & \bigcup\cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & \bigcup L(\lambda) \ar[d, "\Psi_\lambda"] \\ %  description
-    \NN^{\Delta_+} \ar[r] \ar[u,dashed,bend left,"\sigma_\lambda"] & \cZ(\infty) \ar[r] & \CC[N]
+   \bigcup YT(\lambda)_+\ar[r,"\tau\mapsto X(\tau)"]\ar[d,hook] & \bigcup \mathcal X(\lambda) \ar[d,hook,"\text{\Cref{lem:XtZt}}"] & \\
+   \bigcup YT(\lambda) \ar[r,"\tau\mapsto Z(\tau)"] \ar[d,"n_\bullet"] & \bigcup\cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & \bigoplus L(\lambda) \ar[d, "\Psi_\lambda"] \\ %  description
+    \NN^{\Delta_+} \ar[r] \ar[u,dashed,bend left,"\sigma"] \ar[uu,dashed,bend left = 60, "\sigma_+"] & \cZ(\infty) \ar[r] & \CC[N]
 \end{tikzcd}
 \]
-\acom{Should I adjust the diagram so that its from unions over $\lambda$}
-\jcom{I think so.
+% \acom{Should I adjust the diagram so that its from unions over $\lambda$}
+% \jcom{I think so.
 Also somewhere we should indicate that the map $YT(\lambda) \rightarrow Z(\lambda) $ takes $ \tau $ to $ Z(\tau)$.
-In principal we could increase the size of this diagram and include somehow the map taking ``dominant tableaux'' to generalized orbital varieties, but I don't see how to do this without making it unwieldly.}
-
-Two tableaux have equal Lusztig data if they differ by any number of boxes of weight $r$ in row $r$ for any $r$.
-We call this relation \new{padding}.
-In other words, the fibres of $n_\bullet$ contain tableaux related by padding.
-For example $\young(2,4)$ and $\young(112,24,3)$ have equal Lusztig data.
+In principal we could increase the size of this diagram and include somehow the map taking ``dominant tableaux'' to generalized orbital varieties, but I don't see how to do this without making it unwieldy.}
+
+The 
+% set
+sequence $\mu^0 = (\mu^0_r)$ keeping track of the number 
+of boxes of weight $r$ in row $r$ of a given tableau is called its \new{padding}. 
+Two tableaux have equal Lusztig data if they differ by padding. 
+% In other words, the fibres of $n_\bullet$ contain tableaux related by padding. 
+For example $\young(2,4)$ and $\young(112,24,3)$ have equal Lusztig data, because if we ignore the padding of the latter tableau, $(2,1,3)$,... to be continued.
 
@@
 \label{lem:almostmintab}
-Let $n_\bullet = (n_{(a,b)})$ be a Lusztig datum of coweight $\nu$ viewed as a strictly lower-triangular $m\times m$ matrix with 
-% $(w,r)$
-$(a,b)$th entry equal to the number of boxes of weight $a$ in row $b$ for $1\le b < a \le m$. 
-Let $\mu^0$ be a diagonal matrix with $a$th diagonal entry denoted $\mu^0_a$. The solution to the minimization problem 
+Given a Lusztig datum $n_\bullet = (n_{(a,b)})$ 
+% be the Lusztig datum (of a tableau)
+% viewed as a strictly lower-triangular $m\times m$ matrix with 
+% $(a,b)$th entry equal to the number of boxes of weight $a$ in row $b$ for $1\le b < a \le m$. 
+the smallest padding $\mu^0$ a padding be a diagonal matrix with $a$th diagonal entry denoted $\mu^0_a$. The smallest $\mu^0$
+\begin{itemize}
+    \item 
+\end{itemize}
+The solution to the minimization problem 
 \[
@@
     \mu^0_{m} = 0 \\ 
-    \mu^0_{m-1} = \max\{0 , \sum n_{m,c} - \sum n_{m-1,c}\} \\ 
-    \mu^0_i = \max\{0, \mu^0_{i+1} + \sum n_{i+1,c} - \sum n_{i,c} , \mu_{i+1}^0 + \sum n_{r,i+1} - \sum n_{r,i}\}
+    \mu^0_{m-1} = \max\{0 , \sum_b n_{(m,b} - \sum_b n_{(m-1,b)}\} \\ 
+    \mu^0_i = \max\{0, \mu^0_{i+1} + \sum_b n_{(i+1,b)} - \sum_b n_{(i,b)} , \mu_{i+1}^0 + \sum_a n_{(a,i+1)} - \sum_a n_{(a,i)}\}
 \end{gathered}
@@
         \item we can always take the number of $m$'s in row $m$ to be zero; 
-        \item we can take the number of $m-1$'s in row $m-1$ to be zero, unless $n_\bullet$ tells us that there are more $m$'s the first $m-1$ rows than there are $m-1$'s in the first $m-2$ rows, and in that case we take $\mu^0_{m-1}$ so that it exactly offsets the difference;
-        \item we can take the number of $m-2$'s in row $m-2$ to be zero, unless $n_\bullet$ tells us there are more $m-1$'s in the first $m-1$ rows (building off the last step) than there are $m-2$'s in the first $m-3$ rows, or, that there are more boxes in row $m-1$ than there are in row $m-2$, and then we take $\mu^0_{m-2}$ to offset the minimum of the two differences;
+        \item we can take the number of $m-1$'s in row $m-1$ to be zero, unless $n_\bullet$ tells us that there are more $m$'s in the first $m-1$ rows than there are $m-1$'s in the first $m-2$ rows, and in that case we take $\mu^0_{m-1}$ so that it exactly offsets the difference;
+        \item we can take the number of $m-2$'s in row $m-2$ to be zero, unless $n_\bullet$ tells us there are more $m-1$'s in the first $m-2$ rows than there are $m-2$'s in the first $m-3$ rows (exactly as in the last step), or that there are more boxes in row $m-1$ than there are in row $m-2$, and then we take $\mu^0_{m-2}$ to offset the maximum of the two differences;
         \item induct up to $\mu^0_1$. 
@@
 
-[Proposition]
-
-To write down an expansion in $\CC[N]$ we choose a section $\bar\sigma_\lambda$ valued in smallest (not necessarily dominant) representative tableaux.
+For example, if $n_\bullet = (1,0,0,1,0,1)$ then 
+\[
+n_\bullet + \mu^0 = 
+\begin{bmatrix}
+    \mu^0_1\\
+    1 & \mu^0_2 \\
+    0 & 1 & \mu^0_3 \\
+    0 & 0 & 1 & \mu^0_4 
+\end{bmatrix} \quad \lambda = (\mu_1^0 + 1, \mu_2^0 + 1, \mu_3^0 + 1, \mu_4^0) \quad \mu = (\mu_1^0, 1 + \mu_2^0, 1 + \mu_3^0, 1 + \mu_4^0) 
+\]
+and the solution to the minimization problem is 
+\begin{gather*}
+    \mu^0_4 = 0 \\
+    \mu^0_3 = \max\{0,\sum_c n_{(4,c)} - \sum_c n_{(3,c)} \} = \max\{0,1- 1\} = 0 \\
+    \mu^0_2 = \max \{0, \mu_3^0 + \sum_c n_{(3,c)} - \sum_c n_{(2,c)}, \mu_3^0 + \sum_r n_{(r,3)} - \sum_r n_{(r,2)}\} = \max\{0,1-1,1-1\} = 0 \\
+    \mu^0_1 = \max \{0, \mu_2^0 + \sum_c n_{(2,c)}, \mu_2^0 + \sum_r n_{(r,2)} - \sum_r n_{(r,1)}\} = \max \{0,1,1-1\} = 1 
+\end{gather*}
+In terms of GT-patterns and tableaux, the information of $n_\bullet$ together with $\mu^0$ define
+\[
+\gt = \begin{matrix}
+\mu_1^0 \\
+1 + \mu_1^0 & \mu_2^0 \\
+1 + \mu_1^0 & 1 + \mu_2^0 & \mu_3^0 \\
+1 + \mu_1^0 & 1 + \mu_2^0 & 1 + \mu_3^0 & \mu_4^0 
+\end{matrix} = \begin{matrix}
+1 \\
+2 & 0\\
+2 & 1 & 0 \\
+2 & 1 & 1 & 0 
+\end{matrix} \qquad
+\tau = \young(12,3,4)
+\]
+% m-1 = 3: are there more 4s in the first 3 rows than there are 3s in the first 2 rows? 
+% m-2 = i = 2: are there more 3s in the first 2 rows than there are 2s in the first row? or are there more boxes in row 3 than there are in row 2?
+
+% \begin{proposition}
+%     \label{prop:fis}
+%     Given two Lusztig data $n_\bullet',n_\bullet''$ there is a smallest pair of tableaux $\tau',\tau''$ such that $n_\bullet(\tau') = n_\bullet'$ and $n_\bullet(\tau'') = n_\bullet''$ and the weight of $\tau'$ and $\tau''$ combined is dominant.
+%     By smallest we mean that if $t',t''$ are two other tableaux meeting these conditions 
+%     % with $n_\bullet(t') = n_\bullet'$ and $n_\bullet(t'') = n_\bullet''$ 
+%     then the size of $\tau'$ is smaller than the size of $t'$ and the size of $\tau'$ and $\tau''$ combined is smaller than the size of $t'$ and $t''$ combined.
+% \end{proposition}
+
+% \begin{proof}[Sketch.]
+% % Let $n_\bullet = n_\bullet' + n_\bullet''$. 
+% By \Cref{lem:almostmintab} there is a smallest tableau $\tau$ such that $n_\bullet(\tau) = n_\bullet' + n_\bullet''$ and the weight of $\tau$ is dominant.
+
+% From $\tau$ we can form two pairs of arrays of boxes as follows.
+One pair is got by breaking off $(n_\bullet')_{(a,b)}$ boxes of weight $a$ from row $b$ of $\tau$, and the other is got by breaking off $(n_\bullet'')_{(a,b)}$ boxes of weight $a$ from row $b$ of $\tau$.
+
+% If any of the resulting arrays is not a tableau we pad it until it becomes one.
+In padding we may change (increase) the total weight of the pair.
+So we must take care to keep the total weight dominant.
+
+% Finally we have two pairs of tableaux. We take the pair that has smallest total size, and smallest smallest member. 
+% \end{proof}
+
+For example, if $n' = (1,0,0,0,0,0)$ and $n'' = (0,0,0,1,0,1)$ then 
+% as we already saw the smallest dominant $\tau$ with datum $n' + n''$ is $\young(12,3,4)$ 
+% and it gives rise to the following two pairs of arrays of boxes:
+% $$
+% \young(2),\young(1,3,4) \qquad \young(\varnothing,3,4) , \young(12)
+% $$
+% In this case we need only pad the second pair (by adding a 1 in the $\varnothing$ slot above the 3) to get two pairs of tableaux. The smallest pair is the first. 
+% Note however that the second (padded) pair of tableaux is actually equivalent to the first, as we can safely delete the 1 in $\young(12)$ without affecting Lusztig data, or weight.
+
+Compare this with $n' = (0,0,0,0,0,1)$ and $n'' = (1,0,0,1,0,0)$. 
+% The total Lusztig datum is the same and so the tableau supplied by \Cref{lem:almostmintab} is the same. The two pairs of arrays of boxes are different:
+% \[
+% \young(\varnothing,\varnothing,4), \young(12,3) \qquad \young(2,3),\young(1,\varnothing,4)
+% \]
+% The pairs are equivalent since we can shuffle their 1s between their members. So let's just examine the second pair. 
+% \[
+% \young(2,3),\young(1,\varnothing,4) \overset{+\scriptsize{\young(2)}}{\equiv} \young(2,3),\young(1,2,4) \overset{+\scriptsize{\young(1)}}{\equiv} \young(2,3),\young(11,2,4) 
+% \]
+% This time, we had to offset the necessary padding of an empty slot with an extra 1 to maintain dominant total weight.
+Moreover, this time we see that the ``total tableaux'' of the pair we have produced is weightier than the one guaranteed by \Cref{lem:almostmintab}.
 
@@
 
-\begin{proposition}
-    \label{prop:minwts}
-    Given two Lusztig data $n_\bullet',n_\bullet''$ there is a smallest choice of effective coweights $\mu',\mu''$ and effective dominant coweights $\lambda',\lambda''$ such that $\mu = \mu' + \mu''$ is effective dominant and $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ have the prescribed Lusztig data.
+% \begin{proposition}
+%     \label{prop:minwts}
+%     Given two Lusztig data $n_\bullet',n_\bullet''$ there is a smallest choice of effective coweights $\mu',\mu''$ and effective dominant coweights $\lambda',\lambda''$ such that $\mu = \mu' + \mu''$ is effective dominant and $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ have the prescribed Lusztig data.
 They are got by choosing the minimum $\lambda,\mu$ for $n_\bullet = n_\bullet ' + n_\bullet ''$ afforded by \Cref{lem:mintab}, and then breaking off $n_{r,c}'$ boxes of weight $r$ from each row $c<r$ of $\tau$ to form a $\tau'_0$ an intermediate tableau.
@@
 
-    \acom{Grrr, padding might not work.}
-
-    \acom{To be completed. We require a notion of ``smallest'' pair of factor tableaux associated to a given tableau --- that is if we care to include our $B(\infty)\to B(\lambda)$ map. 
-    As the examples show, there may be more than one way to break up a ``minimal'' tableau for $n_\bullet = n_\bullet ' + n_\bullet ''$ into two tableaux with data $n_\bullet' $ and $n_\bullet''$ resp.\ The practical notion of min is such that the generalized nonzero eigenspace has the smallest possible dimension.}
-    \acom{Reference Claxton--Tingley multisegments, Hong--Lee marignally large tableaux for comparison.}
-\end{proposition}
+%     \acom{Grrr, padding might not work.}
+
+% \acom{To be completed. We require a notion of ``smallest'' pair of factor tableaux associated to a given tableau --- that is if we care to include our $B(\infty)\to B(\lambda)$ map. 
+% As the examples show, there may be more than one way to break up a ``minimal'' tableau for $n_\bullet = n_\bullet ' + n_\bullet ''$ into two tableaux with data $n_\bullet' $ and $n_\bullet''$ resp.\ The practical notion of min is such that the generalized nonzero eigenspace has the smallest possible dimension.}
+% \end{proposition}
 
 \begin{corollary}
-Moreover, there exist $\lambda',\lambda''$ dominant effective and a pair of tableaux $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$ such that 
+Given two stable MV cycles $Z',Z''$ with Lusztig data $n_\bullet',n_\bullet''$ resp.\ there exist $\lambda',\lambda''$ dominant effective and a pair of tableaux $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$ such that
 \begin{equation}
@@
     % b_{Z'} \arfu b_{Z''} = \sum_{Z\in\cZ(\lambda)} \iota (Z, Z(\tau')\geofu Z(\tau''))b_{t^{-\lambda}Z}
-    b_{Z'} \arfu b_{Z''} = \sum_{\tau\in YT(\lambda)} \iota (X(\tau), X(\tau',\tau'')_{0,0})b_{t^{-\lambda}Z(\tau)}
+    b_{Z'} \arfu b_{Z''} = \sum_{\tau\in YT(\lambda)} i (X(\tau), X(\tau',\tau'')_{0,0})b_{t^{-\lambda}Z(\tau)}
 \end{equation}
 % 
-for $\lambda = \lambda' + \lambda''$. 
+where $\lambda = \lambda' + \lambda''$. 
 \end{corollary}
 
-\section{Cluster questions}
-\label{s:clusterqus}
-% 
-For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor  \cite{kato2011polytopal}, and hence
-% \acom{by BKK?}\rcom{I reworded it.} 
-is in the MV basis. 
-% as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
+To write down an expansion in $\CC[N]$ we choose a section $\bar\sigma_\lambda$ valued in smallest (not necessarily dominant) representative tableaux.
+
+% \begin{comment}
+% \section{Cluster questions}
+% \label{s:clusterqus}
+% % 
+% For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor  \cite{berenstein2005cluster3}, and hence
+% % \acom{by BKK?}\rcom{I reworded it.} 
+% is in the MV basis \cite{baumann2019mirkovic}. 
+% % as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
 \acom{what's the subscript $r$?
@@
 Neither BFZ nor GLS link generalized minors and MV cycles}
-If the reduced expression satisfies a special condition, then cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
-
-Conversely, suppose we have a seed $(x_1,\dots,x_r)$ such that each $x_i$ is in the MV basis, i.e.\ for each $i$ there exists a stable MV cycle $Z_i$ such that $x_i = b_{Z_i}\in\CC[N]$.
+% If the reduced expression satisfies a special condition, then cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
+
+% Conversely, suppose we have a seed $(x_1,\dots,x_r)$ such that each $x_i$ is in the MV basis, i.e.\ for each $i$ there exists a stable MV cycle $Z_i$ such that $x_i = b_{Z_i}\in\CC[N]$.
 To show that all cluster variables
-% \acom{for this seed?}\rcom{No, all of them.} 
-are also in the MV basis it suffices to show that if $x_i$ is mutable then its mutation $x_i^*$ is also in the MV basis. This observation is based on the exchange relation:
-\[
-    x_i x_i^* = x_+ + x_- 
-\]
-where $x_+,x_-$ are monomials in $ (x_1, \dots, x_r)\setminus x_i$ determined by the cluster structure on $\CC[N]$. 
-% \acom{the structure of interest?
+% % \acom{for this seed?}\rcom{No, all of them.} 
+% are also in the MV basis it suffices to show that if $x_i$ is mutable then its mutation $x_i^*$ is also in the MV basis. This observation is based on the exchange relation:
+% \[
+%     x_i x_i^* = x_+ + x_- 
+% \]
+% where $x_+,x_-$ are monomials in $ (x_1, \dots, x_r)\setminus x_i$ determined by the cluster structure on $\CC[N]$. 
+% % \acom{the structure of interest?
 or are all cluster structures on this ring the same?} \rcom{The structure is derived from an initial seed coming from a reduced word {\bf i}.
 Each of these are equivalent to each other.}
-So if we can find a stable MV cycle $Z_i^*$ such that $b_{Z_i}b_{Z_i^*} = x_+ + x_-$ for each $i$ then we will have checked the conjecture. 
-% \acom{And we do not need to assume the special condition of BGL?}\rcom{They deal with cluster monomials in certain clusters while this deals with all cluster variables, so neither one completely implies the other.}
-
-The following examples give evidence that the mutation $x_i^*$ is in the MV basis. \acom{Roger, reword?}\rcom{Something like this?} \acom{Sure!}
-
-% \jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
-% \acom{Begun}
-
-Before we begin we will need some lemmas, notions and notations. 
-\begin{itemize}
-    \item we have only seen how to fuse ordinary MV cycles; to mutliply MV basis vectors which are indexed by stable MV cycles we'll therefore need a way to represent stable by ordinary; hence:
-    \item a notion/choice of fission 
-    \item the fission lemmas 
-    \item with lemmas in hand, a proposition: given $Z',Z''$ stable with LD... there exist $\tau',\tau''$ (min) such that $b_{Z'} b_{Z''} = b(\tau')  b(\tau'')$
-    \item a shorthand: in examples, instead of writing $Z(\tau)$ for the MV cycle corresponding to the tableau $\tau$ we will only the tableau $\tau$! 
-\end{itemize}
+% So if we can find a stable MV cycle $Z_i^*$ such that $b_{Z_i}b_{Z_i^*} = x_+ + x_-$ for each $i$ then we will have checked the conjecture. 
+% % \acom{And we do not need to assume the special condition of BGL?}\rcom{They deal with cluster monomials in certain clusters while this deals with all cluster variables, so neither one completely implies the other.}
+
+% The following examples give evidence that the mutation $x_i^*$ is in the MV basis. \acom{Roger, reword?}\rcom{Something like this?} \acom{Sure!}
+
+% % \jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
+% % \acom{Begun}
+
+% Before we begin we will need some lemmas, notions and notations. 
+% \begin{itemize}
+%     \item we have only seen how to fuse ordinary MV cycles; to mutliply MV basis vectors which are indexed by stable MV cycles we'll therefore need a way to represent stable by ordinary; hence:
+%     \item a notion/choice of fission 
+%     \item the fission lemmas 
+%     \item with lemmas in hand, a proposition: given $Z',Z''$ stable with LD... there exist $\tau',\tau''$ (min) such that $b_{Z'} b_{Z''} = b(\tau')  b(\tau'')$
+%     \item a shorthand: in examples, instead of writing $Z(\tau)$ for the MV cycle corresponding to the tableau $\tau$ we will only the tableau $\tau$! 
+% \end{itemize}
+% \end{comment}
 
@@
 \label{s:examples}
-
+\acom{Rewrite in view of fusion section. Relations dictated by $\tau$. Can mostly refer the reader to the previous section for this background, now.}
 % \acom{Plus fusion product of fake MV cycles for a fourth!}
-\acom{TODO: review/rewrite now that we have \S 6.2}
-We view MV cycles as semi-standard young tableaux.
+
+As stated in the previous section, we will label MV cycles as semi-standard young tableaux.
 Suppose we have two tableaux $\tau'$ and $\tau''$, with respective weights $\lambda'$, $\mu'$ and $\lambda''$, $\mu''$, and we wished to take their fusion product.
-We consider a generic matrix $X \in \UU^{\mu',\mu''}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda',\lambda''}_{0,s}$.
-\acom{Relations dictated by $\tau$.
-Can mostly refer the reader to the previous section for this background, now.}
-
-Consider the subtableaux $\tau'(i)$ of $\tau'$ and $\tau''(i)$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$.
+We consider a generic matrix $A \in \UU^{\mu',\mu''}_{0,s}$ as well as its submatrices $A_i := A\big|_{\CC^{|\mu(i)|}} \in \UU^{\mu'(i), \mu''(i)}_{0,s}$ for each $i=1, \dots, m$.
+
+% and see what relations on the variables in $A$ occur when also asking for it to be in $\OO^{\lambda',\lambda''}_{0,s}$.
+
+% Consider the subtableaux $\tau'(i)$ of $\tau'$ and $\tau''(i)$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$.
 Let $\lambda'(i)$ and $\lambda''(i)$ be the corresponding sizes and $\mu'(i)$ and $\mu'(i)$ be the corresponding weights of the subtableaux.
-For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu'(i), \mu''(i)}_{0,s}$ of $X$.
-These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda'(i), \lambda''(i)}_{0,s}$, which allows us to deduce relations on the variables in $X$.
-The relations must also include the new variables in the latest block and cannot have $s$ as a factor.
-
-To find the MV cycles, equivalently tableaux, in the $0$-fibre of the fusion, we consider the ring generated by all the variables of $X$ and quotient out the ideal generated by the relations from the vanishing minors as well as the minimal polynomial of $X$.
+For each $i$, we obtain a corresponding submatrix $A_i \in \UU^{\mu'(i), \mu''(i)}_{0,s}$ of $A$.
+
+The requirement that each $A_i \in \OO^{\lambda'(i), \lambda''(i)}_{0,s}$ imposes rank conditions, equivalently vanishing and non-vanishing minors, which translates to relations in the coordinate ring $\CC[s, s^{-1}, A_{ij}^k : 1 \leq i,j \leq m, k \geq 1]$.
+\rcom{Would $\CC[A_{ij}^k, s, s^{-1}]$ be enough?}
+Let $I$ be the ideal generated by these relations.
+Then $$J = (I \cap \CC[A_{ij}^k,s]) + (s)$$ gives us the ideal for the fusion.
+Taking the primary decomposition of $J$ gives us the ideal for each generalized orbital variety, which we then translate to a tableau, and finally to an MV cycle.
+
+% To find the MV cycles, equivalently tableaux, in the $0$-fibre of the fusion, we consider the ring generated by all the variables of $A$ and quotient out the ideal generated by the relations from the vanishing minors as well as the minimal polynomial of $A$.
 We then add $s$ into the ideal.
-Each piece in the primary decomposition of this ideal will correspond to a tableaux, and subsequently a MV cycle.
+Each piece in the primary decomposition of this ideal will correspond to a tableaux, and subsequently an MV cycle.
+
+\jcom{More precisely, we have $ I \subset \CC[a_i, s, s^{-1}] $ then form $ I \cap \CC[a_i, s]$ and then quotient by $ s$.
+This corresponds to taking the closure $ X(\tau',\tau'')_{0,\AA}$ and then taking the fibre.}
 
@@
 
-\acom{If we start with $n_\bullet ' = (0,1,0)$ and $n_\bullet'' = (1,0,1)$ then the smallest $\tau$ for $n_\bullet = (1,1,1)$ is $\young(1123,23)$ and hence the smallest $\mu,\lambda$ are $(2,2,2),(4,2,0)$.
+% \acom{If we start with $n_\bullet ' = (0,1,0)$ and $n_\bullet'' = (1,0,1)$ then the smallest $\tau$ for $n_\bullet = (1,1,1)$ is $\young(1123,23)$ and hence the smallest $\mu,\lambda$ are $(2,2,2),(4,2,0)$.
 So far so good.
@@
 \subsection{Type $A_2$}
-
-\begin{example}
-% Let $G = \GL_3$ and consider the tableaux
-% $$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$
-
-% Lustig data: $(100)$ for $\tau'$, $(001)$ for $\tau''$.
-$\young(2)\arfu\young(1,3)$:
-
-\acom{This time the smallest $\tau$ is actually $\young(12,3)$ and the smallest fission is $\young(1,3),\young(2)$. For Joel: this time the our $\lambda$ matches \cite{claxton2015young}'s.}
-
-Dimensions: $(1,-1,0)$ for $\tau'$, $(0,1,-1)$ for $\tau''$.
-
-The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.
-We have the weights to be $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (1,1,0)$, and $\mu'' = (2,1,1)$. The matrix under consideration is therefore
-\[
-X = \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c}
-    0 & 1 & & & & \\
-     & 0 & 1 & & & \\
-     & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
-     & & & 0 & 1 & \\
-     & & & & s & A_{23}^1 \\
-     & & & & & s
-\end{BMAT}
-\right].
-\]
-There are no relations from looking at the submatrix $X_1$. From the submatrix $X_2$, we require $$A_{12}^1 + sA_{12}^2 = 0.$$
-From $X$, we further obtain the relations $$A_{12}^2A_{23}^1 + sA_{13}^1 = 0, A_{12}^1A_{23}^1 + s^2A_{13}^1 = 0.$$
-Then the quotient ring we find is
-$$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s]}{\langle A_{12}^1+sA_{12}^2, A_{12}^2A_{23}^1+sA_{13}^1, A_{12}^1A_{23}^1+s^2A_{13}^1, s\rangle} \cong \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,b_3,s]}{\langle A_{12}^1, A_{12}^2\rangle \cap \langle A_{12}^1, A_{23}^1 \rangle}.$$
-% 
-We see that the 0-fibre is reducible with two components. The tableau corresponding to each ideal is
-$$\begin{array}{cccc} \vspace{1mm}
-    \young(1113,22) & \text{for } \langle A_{12}^1, A_{12}^2 \rangle & \text{Lusztig: }(101) & \dim = (1,0,-1)\\ 
-    \young(1112,23) & \text{for } \langle A_{12}^1, A_{23}^1 \rangle & \text{Lusztig: }(010) & \dim = (1,0,-1).
-\end{array}$$
-Each of these tableaux corresponds to a MV cycle isomorphic to $\PP^2$ so the generic fibre $\PP^1 \times \PP^1$ degenerates to two copies of $\PP^2$.
-\end{example}
+\label{ss:a2}
+% 
+% \begin{example} \rcom{Get rid.}
+% % Let $G = \GL_3$ and consider the tableaux
+% % $$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$
+
+% % Lustig data: $(100)$ for $\tau'$, $(001)$ for $\tau''$.
+% $\young(2)\arfu\young(1,3)$:
+
+% % \acom{This time the smallest $\tau$ is actually $\young(12,3)$ and the smallest fission is $\young(1,3),\young(2)$. For Joel: this time the our $\lambda$ matches \cite{claxton2015young}'s.}
+
+% % Dimensions: $(1,-1,0)$ for $\tau'$, $(0,1,-1)$ for $\tau''$.
+
+% The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.
+% We have the weights to be $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (1,1,0)$, and $\mu'' = (2,1,1)$. The matrix under consideration is therefore
+% \[
+% A = \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c}
+%     0 & 1 & & & & \\
+%      & 0 & 1 & & & \\
+%      & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
+%      & & & 0 & 1 & \\
+%      & & & & s & A_{23}^1 \\
+%      & & & & & s
+% \end{BMAT}
+% \right].
+% \]
+% There are no relations from looking at the submatrix $A_1$. From the submatrix $A_2$, we require $$A_{12}^1 + sA_{12}^2 = 0.$$
+% From $A$, we further obtain the relations $$A_{12}^2A_{23}^1 + sA_{13}^1 = 0, A_{12}^1A_{23}^1 + s^2A_{13}^1 = 0.$$
+% Then the quotient ring we find is
+% $$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s]}{( A_{12}^1+sA_{12}^2, A_{12}^2A_{23}^1+sA_{13}^1, A_{12}^1A_{23}^1+s^2A_{13}^1, s)} \cong \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s]}{( A_{12}^1, A_{12}^2,s) \cap ( A_{12}^1, A_{23}^1,s )}.$$
+% % 
+% We see that the 0-fibre is reducible with two components. The tableau corresponding to each ideal is
+% $$\begin{array}{cccc} \vspace{1mm}
+%     \young(1113,22) & \text{for } ( A_{12}^1, A_{12}^2,s ) & \text{Lusztig: }(101) & \dim = (1,0,-1)\\ 
+%     \young(1112,23) & \text{for } ( A_{12}^1, A_{23}^1,s ) & \text{Lusztig: }(010) & \dim = (1,0,-1).
+% \end{array}$$
+% Each of these tableaux corresponds to a MV cycle isomorphic to $\PP^2$ so the generic fibre $\PP^1 \times \PP^1$ degenerates to two copies of $\PP^2$.
+% \end{example}
 
@@
 \[
-X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
+A = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
     0 & 1 & & & & & & & & & & \\
@@
 \begin{array}{cl}
-    I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
-    I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
-    I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
+    I_1 = & ( A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s ) \\
+    I_2 = & ( A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s ) \\
+    I_3 = & ( A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s ).
 \end{array}
 $$
-It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same.
-The tableau corresponding to each ideal is
+It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} 
+\acom{:o}
+so the 0-fibre has 4 components, two of which are the same. The tableau corresponding to each ideal is
 $$
@@
 
-\acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{claxton2015young}}
+% \acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{claxton2015young}}
 
@@
 \[
-X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
+A = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
     0 & 1 & & & & \\
@@
 \begin{array}{cl}
-    I_1 = & \langle A_{12}^1, A_{12}^2 \rangle \\
-    I_2 = & \langle A_{23}^1, A_{23}^2 \rangle \\
-    I_3 = & \langle (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2 \rangle. 
+    I_1 = & ( A_{12}^1, A_{12}^2,s ) \\
+    I_2 = & ( A_{23}^1, A_{23}^2,s ) \\
+    I_3 = & ( (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2,s ). 
 \end{array}
@@
 $$
-and the MV cycles corresponding to each are isomorphic to $\PP^2 \times \PP^2$.
+Note that the ideal $I_3$ has multiplicity 2 so our equation in $\CC[N]$ becomes
+\[
+\young(22) \cdot \young(11,33) = \young(33) + \young(22,33) + 2\cdot \young(23,3).
+\]
 \end{example}
@@
 We will take the initial cluster $(x_1,\dots,x_6)$ coming from the reduced word ${\bf i} = (1,2,3,1,2,1)$.
-If we view $\CC[N] \cong \CC[x_{ij} : i < j]$, then
+If we view $\CC[N] \cong \CC[x_{ij} : 1 \leq i < j \leq 4]$, then
 \[
@@
 \]
-We list the corresponding tableaux, coordinate ring of the generalized orbital variety $X(\tau)$, Lusztig-datum, and cluster variable as a Laurent polynomial in the $x_i$ below:
+We list the corresponding tableaux, coordinate ring of the generalized orbital variety $X(\tau)$, a variety that $Z(\tau)$ is isomorphic to, the Lusztig-datum, and the cluster variable as a Laurent polynomial in the $x_i$ below:
 
@@
   \centering
-  \newcolumntype{Q}{>{$}l<{$}>{$}c<{$}>{$}l<{$}>{$}l<{$}>{$}c<{$}}
+  \newcolumntype{Q}{>{$}l<{$}>{$}c<{$}>{$}l<{$}>{$}l<{$}>{$}c<{$}>{$}l<{$}}
   \begin{tabular}{Q} 
-    \tau' & \tau = \text{Dominant }\tau' & \text{Coordinate ring of }X(\tau) & \text{Lusztig-datum} & \text{Cluster variable} \\
+    \overline \tau & \tau = \text{Dom. } \overline \tau & \text{Coordinate ring of }X(\tau) & Z(\tau) & \text{Lusztig-datum} & \text{Cluster variable} \\
     \midrule 
-\young(2) & \young(12) & \CC[A_{12}^1] & (1,0,0,0,0,0) & x_1 \rule{0pt}{3ex}\\
-\young(1,3) & \young(11,23) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1,A_{13}^1 )} & (0,0,0,1,0,0) & \frac{x_2 + x_3}{x_1} \TS\BS\\
-\young(1,2,4) & \young(11,22,34) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 )} & (0,0,0,0,0,1) & \frac{x_2x_4 + x_3x_6 + x_1x_5}{x_2x_3} \TS\BS\\
-\young(3) & \young(13,2) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1 )} & (1,0,0,1,0,0) & x_2 \TS\BS\\
-\young(2,3) & \young(12,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{23}^1 )} & (0,1,0,0,0,0) & x_3 \TS\BS\\
-\young(1,4) & \young(11,24,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 )} & (0,0,0,1,0,1) & \frac{x_1x_5 + x_6(x_2+x_3)}{x_1x_2} \TS\BS\\
-\young(1,3,4) & \young(11,23,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 )} & (0,0,0,0,1,0) & \frac{x_1x_5 + x_4(x_2+x_3)}{x_1x_3}\TS\BS\\
-\young(2,4) & \young(112,24,3) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 )} & (0,1,0,0,0,1) & \frac{x_3x_6+x_1x_5}{x_2} \TS\BS\\
-\young(13,2,4) & \young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 )} & (1,0,0,0,1,0) & \frac{x_2x_4 + x_1x_5}{x_3} \TS\BS\\
-\young(2,3,4) & \young(12,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{23}^1,A_{24}^1,A_{34}^1 )} & (0,0,1,0,0,0) & x_4 \TS\BS\\
-\young(3,4) & \young(13,24) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1 )} & (0,1,0,0,1,0) & x_5 \TS\BS\\
-\young(4) & \young(14,2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1 )} & (1,0,0,1,0,1) & x_6 \TS\BS\\
+\young(2) & \young(12) & \CC[A_{12}^1] & \PP^1 & (1,0,0,0,0,0) & x_1 \rule{0pt}{3ex}\\
+\young(1,3) & \young(11,23) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1,A_{13}^1 )} & \PP^1 & (0,0,0,1,0,0) & \frac{x_2 + x_3}{x_1} \TS\BS\\
+\young(1,2,4) & \young(11,22,34) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 )} & \PP^1 & (0,0,0,0,0,1) & \frac{x_2x_4 + x_3x_6 + x_1x_5}{x_2x_3} \TS\BS\\
+\young(3) & \young(13,2) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1 )} & \PP^2 & (1,0,0,1,0,0) & x_2 \TS\BS\\
+\young(2,3) & \young(12,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{23}^1 )} & \PP^2 & (0,1,0,0,0,0) & x_3 \TS\BS\\
+\young(1,4) & \young(11,24,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 )} & \PP^2 & (0,0,0,1,0,1) & \frac{x_1x_5 + x_6(x_2+x_3)}{x_1x_2} \TS\BS\\
+\young(1,3,4) & \young(11,23,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 )} & \PP^2 & (0,0,0,0,1,0) & \frac{x_1x_5 + x_4(x_2+x_3)}{x_1x_3}\TS\BS\\
+\young(2,4) & \young(112,24,3) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 )} & S(2,4) & (0,1,0,0,0,1) & \frac{x_3x_6+x_1x_5}{x_2} \TS\BS\\
+\young(13,2,4) & \young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 )} & S(2,4) & (1,0,0,0,1,0) & \frac{x_2x_4 + x_1x_5}{x_3} \TS\BS\\
+\young(2,3,4) & \young(12,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{23}^1,A_{24}^1,A_{34}^1 )} & \PP^3 & (0,0,1,0,0,0) & x_4 \TS\BS\\
+\young(3,4) & \young(13,24) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1 )} & Gr(2,4) & (0,1,0,0,1,0) & x_5 \TS\BS\\
+\young(4) & \young(14,2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1 )} & \PP^3 & (1,0,0,1,0,1) & x_6 \TS\BS\\
   \end{tabular}
 \end{table}
+
+The variety $S(2,4)$ denotes the non-smooth Schubert divisor in the usual Grassmannian $Gr(2,4)$.
 
@@
 We show that the cluster relations in $\CC[N]$ are also true for the fusion product of the corresponding MV cycles.
-For each of the 15 exchange relations, we state the associated matrix $X$, the relations acquired from each submatrix $X_i$, the ideal generated by said relations, and the corresponding tableaux from the ideal.
+For each of the 15 exchange relations, we state the associated matrix $A$, the relations acquired from each submatrix $A_i$, the ideal generated by said relations, and the corresponding tableaux from the ideal.
 Instead of writing the exchange relations in terms of $b_{Z(\tau)}$ or the fusion product in terms of $Z(\tau)$, we will use $\tau$ for both situations.
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2) *_{\AA \setminus \{0\}} \young(1,3) 
+\right] \text{ is contained in } \young(2) \bdfamo \young(1,3) 
 % \Rightarrow 
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1,3) *_{\AA \setminus \{0\}} \young(1,2,4)
+\right] \text{ is contained in } \young(1,3) \bdfamo \young(1,2,4)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2) *_{\AA \setminus \{0\}} \young(1,3,4)
+\right] \text{ is contained in } \young(2) \bdfamo \young(1,3,4)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2) *_{\AA \setminus \{0\}} \young(11,24,3)
+\right] \text{ is contained in } \young(2) \bdfamo \young(11,24,3)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,2,4) *_{\AA \setminus \{0\}} \young(2,3)
+\right] \text{ is contained in } \young(11,2,4) \bdfamo \young(2,3)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1,2,4) *_{\AA \setminus \{0\}} \young(3)
+\right] \text{ is contained in } \young(1,2,4) \bdfamo \young(3)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,24) *_{\AA \setminus \{0\}} \young(3)
+\right] \text{ is contained in } \young(11,24) \bdfamo \young(3)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,23,4) *_{\AA \setminus \{0\}} \young(2,3)
+\right] \text{ is contained in } \young(11,23,4) \bdfamo \young(2,3)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(113,22,4) *_{\AA \setminus \{0\}} \young(1,3)
+\right] \text{ is contained in } \young(113,22,4) \bdfamo \young(1,3)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1,3) *_{\AA \setminus \{0\}} \young(2,4)
+\right] \text{ is contained in } \young(1,3) \bdfamo \young(2,4)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(113,2,4) *_{\AA \setminus \{0\}} \young(2,3)
+\right] \text{ is contained in } \young(113,2,4) \bdfamo \young(2,3)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2,4) *_{\AA \setminus \{0\}} \young(1,3)
+\right] \text{ is contained in } \young(2,4) \bdfamo \young(1,3)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(113,22,34) *_{\AA \setminus \{0\}} \young(1,4)
+\right] \text{ is contained in } \young(113,22,34) \bdfamo \young(1,4)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,23,34) *_{\AA \setminus \{0\}} \young(2,4)
+\right] \text{ is contained in } \young(11,23,34) \bdfamo \young(2,4)
 \]
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1113,22,34) *_{\AA \setminus \{0\}} \young(2,4)
+\right] \text{ is contained in } \young(1113,22,34) \bdfamo \young(2,4)
 \]

### 2021-06-08 draft.tex
Editted examples

@@
 %
-\jcom{I wanted to state a precise theorem, but it is not so easy without introducing a lot of notation.}
-\acom{Are you ok with the 'maintheorem' environemnt?}
 
@@
 Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{geiss2007initial}, using the construction of \cite{berenstein2005cluster3}, that $\CC[N]$ has a natural cluster algebra structure.
-\acom{As a reader I am confused - did both of them show it independently?
+%\acom{As a reader I am confused - did both of them show it independently?
 Can I go to either source to find out how this works?
@@
 
-This structure starts with an initial seed $\Sigma = ((x_1,\dots,x_r),B)$, where $x_i \in \CC[N]$, $B$ is a certain matrix, and $ r = m(m-1)/2$ ($=\#\Delta_+$).
+This structure starts with an initial seed $\Sigma = ((x_1,\dots,x_r),B)$, where $x_i \in \CC[N]$, $B$ is a certain matrix, and $ r = m(m-1)/2$.
+% ($=\#\Delta_+$)
 We obtain new variables through a process called mutation where for a mutable variable $x_i$, its mutation is the unique element $x_i^* \in \CC[N]$ such that $$x_ix_i^* = x_+ + x_-.$$
@@
 
-\acom{It would be nice to add a line to set up this paragraph.
+%\acom{It would be nice to add a line to set up this paragraph.
 Else the canonical bases come out of nowhere?
 Like ``There is another nice structure on $\CC[N]$, that of a \new{perfect basis} introduced by/studied by...; and heaps of work (or just the following two sources) suggests that the two structures are inextricably linked.'' Because it's a paper and not a talk.}
-\rcom{Something along these lines?}
+%\rcom{Something along these lines?}
 There are two well-known bases of $\CC[N]$ whose relationship with the cluster structure has been studied heavily: the dual canonical basis \cite{lusztig1990canonicalbases} and the dual semicanonical basis \cite{lusztig2000semicanonical}.
-Kang, Kashiwara, Kim \& Oh showed that all cluster monomials are contained in the dual canonical basis \cite{kang2018monoidal} while Gei\ss, Leclerc, \& Schr\"oer proved that they are all contained in the dual semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
+Kang, Kashiwara, Kim \& Oh showed that all cluster monomials are contained in the dual canonical basis \cite{kang2018monoidal}, while Gei\ss, Leclerc, \& Schr\"oer proved that they are all contained in the dual semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
 % 
@@
 
-Although the MV basis differs from these bases (at least at the Kashiwara--Saito counterexample \cite[Appendix]{baumann2019mirkovic}), they are all examples of biperfect bases \cite{baumann2019mirkovic}.
-% and the above mentioned bases are in general different from each other \cite{baumann2019mirkovic}, 
-\acom{can we say something other than ``it is believed'', like ``Evidence/calculations/etc.\ suggests''}
-%along with evidence suggests that they all contain the cluster monomials, leading to the following conjecture.
-This then leads to the following conjecture.
-
+The MV basis, the dual canonical basis, and the dual semicanonical basis are all examples of biperfect bases \cite{baumann2019mirkovic}.
+In \cite[Appendix]{baumann2019mirkovic}, we showed that the the MV basis differs from the dual semicanonical basis.
+Since the basis vector at which these bases differ is not a cluster monomial, this gives evidence for the following conjecture of Anderson and Kogan \cite[Conjecture 5.1]{anderson2006algebra}.
 \begin{conjecture}\label{conj:cluster in MV}
@@
 The following refinement of the \mvy isomorphism is a special case of \cite[Theorem 5.3]{mirkovic2007quiver}. 
-\acom{Wait isn't 5.3 a special case of this?}  \jcom{No, they deal with the more general setting of more points.} \acom{Ok, but I don't think that they establish this exact fact..they have Lemma~4.4.2 and Corollary 4.5 which uses the convolution grassmannian.}
+% \acom{Wait isn't 5.3 a special case of this?}  \jcom{No, they deal with the more general setting of more points.} \acom{Ok, but I don't think that they establish this exact fact..they have Lemma~4.4.2 and Corollary 4.5 which uses the convolution grassmannian.
+Still not sure about this..}
 \begin{theorem} 
@@
 
-In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic--Vilonen polytopes, or equivalently Lusztig data, which are sequences in $\NN^{\Delta_+}$ that depend on a choice of reduced expression.
+In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic--Vilonen polytopes, or equivalently Lusztig data, which are sequences in $\NN^{r}$ that depend on a choice of reduced expression.
 For $\GL_m$ and the standard reduced word, this description can be reworded in terms of Young tableaux.
@@
 Denote by $YT(\lambda)$ the set of (possibly semi-standard) Young tableaux of shape $\lambda$ and by $YT(\lambda)_\mu$ the subset of $YT(\lambda)$ of tableaux having weight $\mu$.
+Let $YT = \bigcup_\lambda YT(\lambda)$ and denote by $YT_+\subset YT$ those tableaux having dominant weight.
 %Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
@@
 We write $ X(\tau)$ for the closure of this component.
-It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu \cap \n$ and will be called a \new{generalized orbital variety}.
+It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu \cap \n$ and will be called a \new{generalized orbital variety of type $\lambda$}.
+% 
+The collection of all possible generalized orbital varieties of type $\lambda$ will be denoted $\cX(\lambda)$. 
 % 
@@
     \label{pr:govsasirrecs}
-    $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$ is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
+    % $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$ 
+    $\{X\in\cX(\lambda):X\subset\TT_\mu\}$
+    is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
 \end{theorem}
@@
 % 
-\subsection{Representations in $\CC[N]$}
+\subsection{Multiplying MV basis elements in $\CC[N]$}
 \label{ss:CN}
@@
 % Recall that MV cycles can be described combinatorially by Lusztig data. 
-By a theorem of the third author, given a choice a reduced word for $ w_0 $, there is a bijection $ \cZ(\infty) \rightarrow \NN^{\Delta_+} $ called the Lusztig datum.
+By a theorem of the third author, given a choice a reduced word for $ w_0 $, there is a bijection $ \cZ(\infty) \rightarrow \NN^{r} $ called the Lusztig datum.
 For our purposes we will always use the standard reduced word.
@@
     % of coweight $\nu',\nu''$ respectively 
-$$
+\begin{equation}
+    \label{eq:btimesb}
 b_{Z'}\arfu b_{Z''} = \sum_{Z\in\cZ(\infty)} i\left(Z, Z' \geofu Z''\right) b_Z 
-$$
+\end{equation}
 in $\CC[N]$. 
@@
 
-In \Cref{s:examples} we will identify elements $b_Z$ with certain \textit{minimal} tableaux (instead of Lusztig data) and view $\CC[N]$ as an algebra in these tableaux, rewriting (abbreviating) \Cref{eq:multingovs} as an equation in semistandard Young tableaux.
-We can do this because of 
+% In \Cref{s:examples} we will abbreviate MV basis elements to associated tableaux and view $\CC[N]$ as an algebra in these, rewriting \Cref{eq:btimesb} as an equation in tableaux.
+% \jcom{I don't think that we really need this sentence here.}
+% 
+% We can do this by choosing a section of $n_\bullet$, because 
+The following diagram commutes.
 % Before we describe how to choose representative generalized orbital varieties in order to expand a product of MV basis elements 
@@
 % in $\CC[N]$ we summarize our approach in 
-the following commutative diagram. 
+% \bigcup YT(\lambda)_+
+% \bigcup YT(\lambda)
 \[
 \begin{tikzcd}
-   \bigcup YT(\lambda)_+\ar[r,"\tau\mapsto X(\tau)"]\ar[d,hook] & \bigcup \mathcal X(\lambda) \ar[d,hook,"\text{\Cref{lem:XtZt}}"] & \\
-   \bigcup YT(\lambda) \ar[r,"\tau\mapsto Z(\tau)"] \ar[d,"n_\bullet"] & \bigcup\cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & \bigoplus L(\lambda) \ar[d, "\Psi_\lambda"] \\ %  description
-    \NN^{\Delta_+} \ar[r] \ar[u,dashed,bend left,"\sigma"] \ar[uu,dashed,bend left = 60, "\sigma_+"] & \cZ(\infty) \ar[r] & \CC[N]
+%   YT_+ \ar[r,"\tau\mapsto X(\tau)"]\ar[d,hook] & \bigcup \mathcal X(\lambda) \ar[d,hook,"\text{\Cref{lem:XtZt}}"] & \\
+% \ar[u,dashed,bend left,"(\phantom{-})_+"]
+   YT  \ar[r,"\tau\mapsto Z(\tau)"] \ar[d,"n_\bullet"] & \bigcup\cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & \bigoplus V(\lambda) \ar[d, "\Psi_\lambda"] \\ 
+    \NN^{r} \ar[r] \ar[u,dashed,bend left,"\sigma"] & \cZ(\infty) \ar[r] & \CC[N] % \ar[uu,dashed,bend left = 60, "\sigma_+"] 
 \end{tikzcd}
 \]
+\jcom{Did we define $ YT_+ $ and $ \mathcal X(\lambda)$?}
+\acom{Yup}
+
+% Let us describe how we make this choice.
 % \acom{Should I adjust the diagram so that its from unions over $\lambda$}
@@
 % set
-sequence $\mu^0 = (\mu^0_r)$ keeping track of the number 
-of boxes of weight $r$ in row $r$ of a given tableau is called its \new{padding}. 
-Two tableaux have equal Lusztig data if they differ by padding. 
-% In other words, the fibres of $n_\bullet$ contain tableaux related by padding. 
-For example $\young(2,4)$ and $\young(112,24,3)$ have equal Lusztig data, because if we ignore the padding of the latter tableau, $(2,1,3)$,... to be continued.
-
-While $Z(\tau)$ is defined even when $\mu$ is not dominant, $X(\tau)$ is not.
-To compute intersection multiplicities using generalized orbital varieties we therefore need to choose a section $\sigma_\lambda$ of $n_\bullet$ with image in the set of tableaux having dominant weight.
-%
+sequence $\mu^0 = (\mu^0_1,\dots,\mu^0_{m-1})$ keeping track of the number 
+of boxes of weight $i$ in row $i$ of a given tableau is called its \new{padding weight} and the set of boxes contributing to the padding weight is called its \new{padding}. 
+Two tableaux have equal Lusztig data if and only if they are related by padding, which is to say that we can change the padding of one to recreate the other.
+Moreover, a tableau is completely determined by its Lusztig datum and padding.
+
+For example 
+$$\bar \tau = \young(2,4) \quad \text{ and} \quad \tau = \young(112,24,3)$$ 
+% whose padding weight is $(2,1,1)$ 
+% whose padding weight is $(0,0,0)$ and $
+have equal Lusztig data, since we can increase the padding of $\bar\tau$
+% , which has padding weight $(0,0,0)$, 
+by the padding weight of $\tau$ to get $\tau$, or decrease the padding of $\tau$ by its padding weight 
+% $(2,1,1)$ 
+to get $\bar\tau$.
 
@@
 \label{lem:almostmintab}
-Given a Lusztig datum $n_\bullet = (n_{(a,b)})$ 
+Let $n_\bullet = (n_{(a,b)})$ be a Lusztig datum and let $\mu^0 = (\mu^0_i)$ be a padding weight. If $\lambda = (\sum_b n_{(a,b)} + \mu^0_b)_a $ 
+% and $\mu = (\sum_a n_{(a,b)} + \mu^0_a)_b$ 
+then 
 % be the Lusztig datum (of a tableau)
@@
 % $(a,b)$th entry equal to the number of boxes of weight $a$ in row $b$ for $1\le b < a \le m$. 
-the smallest padding $\mu^0$ a padding be a diagonal matrix with $a$th diagonal entry denoted $\mu^0_a$. The smallest $\mu^0$
+% \begin{itemize}
+    % \item 
+    the smallest $\mu^0$ such that $\lambda$ is dominant effective (and $\mu$ is effective) is:
+    $$\begin{gathered}
+        \mu^0_{m}, \mu^0_{m-1} = 0 \\
+        \mu^0_i = \max\{0, \mu_{i+1}^0 + \sum_a n_{(a,i+1)} - \sum_a n_{(a,i)}\} \quad i = 1,\dots,m-2
+    \end{gathered}$$
+and $\mu^0$ defines a section $\sigma:\NN^{r} \to YT$.
+%     \item the smallest $\mu^0$ such that $\lambda$ and $\mu$ are dominant effective is: 
+%     $$\begin{gathered}
+%     \mu^0_{m} = 0 \\ 
+%     \mu^0_{m-1} = \max\{0 , \sum_b n_{(m,b)} - \sum_b n_{(m-1,b)}\} \\ 
+%     \mu^0_i = \max\{0, \mu^0_{i+1} + \sum_b n_{(i+1,b)} - \sum_b n_{(i,b)} , \mu_{i+1}^0 + \sum_a n_{(a,i+1)} - \sum_a n_{(a,i)}\} \quad i = 1,\dots, m-2
+%     \end{gathered}$$
+% and $\mu^0$ defines a section $\sigma_+:\NN^{r} \to YT_+$.
+% \end{itemize}
+% The solution to the minimization problem 
+% \[
+% \text{minimize }\mu^0\text{ such that } \lambda = (\sum_b n_{(a,b)} + \mu^0_b)_a \text{ and } \mu = (\sum_a n_{(a,b)} + \mu^0_a)_b
+% \text{ are dominant effective}
+% \]
+% is 
+% \[
+% \begin{gathered}
+%     \mu^0_{m} = 0 \\ 
+%     \mu^0_{m-1} = \max\{0 , \sum_b n_{(m,b} - \sum_b n_{(m-1,b)}\} \\ 
+%     \mu^0_i = \max\{0, \mu^0_{i+1} + \sum_b n_{(i+1,b)} - \sum_b n_{(i,b)} , \mu_{i+1}^0 + \sum_a n_{(a,i+1)} - \sum_a n_{(a,i)}\}
+% \end{gathered}
+% \]
+\end{lemma}
+\begin{proof}[Proof sketch.]
+% We explain the formula in the $\mu$ dominant case, and leave the $\mu$ non-dominant case to the reader. 
+To produce a tableau with Lusztig datum $n_\bullet$ of smallest possible shape and weight:
     \begin{itemize}
-    \item 
+        \item we can always take the number of $m$'s in row $m$, and the number of $m-1$'s in row $m-1$ to be zero; 
+        % \item we can take the number of $m-1$'s in row $m-1$ to be zero, unless $n_\bullet$ tells us that there are more $m$'s in the first $m-1$ rows than there are $m-1$'s in the first $m-2$ rows, and in that case we take $\mu^0_{m-1}$ so that it exactly offsets the difference;
+        \item we can take the number of $m-2$'s in row $m-2$ to be zero, unless $n_\bullet$ tells us 
+        % there are more $m-1$'s in the first $m-2$ rows than there are $m-2$'s in the first $m-3$ rows (exactly as in the last step), or 
+        that there are more boxes in row $m-1$ than there are in row $m-2$, and then we take $\mu^0_{m-2}$ to offset the difference; 
+        % the maximum of the two differences; 
+        % \item induct up to $\mu^0_1$. 
     \end{itemize}
-The solution to the minimization problem 
-\[
-\text{minimize }\mu^0\text{ such that } \lambda = (\sum_b n_{(a,b)} + \mu^0_b)_a \text{ and } \mu = (\sum_a n_{(a,b)} + \mu^0_a)_b
-% sum rows and sum columns
-\text{ are dominant effective}
-\]
-is 
-\[
-\begin{gathered}
-    \mu^0_{m} = 0 \\ 
-    \mu^0_{m-1} = \max\{0 , \sum_b n_{(m,b} - \sum_b n_{(m-1,b)}\} \\ 
-    \mu^0_i = \max\{0, \mu^0_{i+1} + \sum_b n_{(i+1,b)} - \sum_b n_{(i,b)} , \mu_{i+1}^0 + \sum_a n_{(a,i+1)} - \sum_a n_{(a,i)}\}
-\end{gathered}
-\]
-for $i = 1,\dots,m-2$. 
-\end{lemma}
-
-In words, if we wish to produce a dominant weight tableau with Lusztig datum $n_\bullet$ of smallest possible shape and weight 
-    \begin{itemize}
-        \item we can always take the number of $m$'s in row $m$ to be zero; 
-        \item we can take the number of $m-1$'s in row $m-1$ to be zero, unless $n_\bullet$ tells us that there are more $m$'s in the first $m-1$ rows than there are $m-1$'s in the first $m-2$ rows, and in that case we take $\mu^0_{m-1}$ so that it exactly offsets the difference;
-        \item we can take the number of $m-2$'s in row $m-2$ to be zero, unless $n_\bullet$ tells us there are more $m-1$'s in the first $m-2$ rows than there are $m-2$'s in the first $m-3$ rows (exactly as in the last step), or that there are more boxes in row $m-1$ than there are in row $m-2$, and then we take $\mu^0_{m-2}$ to offset the maximum of the two differences;
-        \item induct up to $\mu^0_1$. 
-    \end{itemize}
-
-For example, if $n_\bullet = (1,0,0,1,0,1)$ then 
-\[
-n_\bullet + \mu^0 = 
-\begin{bmatrix}
-    \mu^0_1\\
-    1 & \mu^0_2 \\
-    0 & 1 & \mu^0_3 \\
-    0 & 0 & 1 & \mu^0_4 
-\end{bmatrix} \quad \lambda = (\mu_1^0 + 1, \mu_2^0 + 1, \mu_3^0 + 1, \mu_4^0) \quad \mu = (\mu_1^0, 1 + \mu_2^0, 1 + \mu_3^0, 1 + \mu_4^0) 
-\]
-and the solution to the minimization problem is 
-\begin{gather*}
-    \mu^0_4 = 0 \\
-    \mu^0_3 = \max\{0,\sum_c n_{(4,c)} - \sum_c n_{(3,c)} \} = \max\{0,1- 1\} = 0 \\
-    \mu^0_2 = \max \{0, \mu_3^0 + \sum_c n_{(3,c)} - \sum_c n_{(2,c)}, \mu_3^0 + \sum_r n_{(r,3)} - \sum_r n_{(r,2)}\} = \max\{0,1-1,1-1\} = 0 \\
-    \mu^0_1 = \max \{0, \mu_2^0 + \sum_c n_{(2,c)}, \mu_2^0 + \sum_r n_{(r,2)} - \sum_r n_{(r,1)}\} = \max \{0,1,1-1\} = 1 
-\end{gather*}
-In terms of GT-patterns and tableaux, the information of $n_\bullet$ together with $\mu^0$ define
-\[
-\gt = \begin{matrix}
-\mu_1^0 \\
-1 + \mu_1^0 & \mu_2^0 \\
-1 + \mu_1^0 & 1 + \mu_2^0 & \mu_3^0 \\
-1 + \mu_1^0 & 1 + \mu_2^0 & 1 + \mu_3^0 & \mu_4^0 
-\end{matrix} = \begin{matrix}
-1 \\
-2 & 0\\
-2 & 1 & 0 \\
-2 & 1 & 1 & 0 
-\end{matrix} \qquad
-\tau = \young(12,3,4)
-\]
+    and continue up to $\mu^0_1$. 
+\end{proof}
+% 
+% For example, if $n_\bullet = (1,0,0,1,0,1)$ then 
+% \[
+% n_\bullet + \mu^0 = 
+% \begin{bmatrix}
+%     \mu^0_1\\
+%     1 & \mu^0_2 \\
+%     0 & 1 & \mu^0_3 \\
+%     0 & 0 & 1 & \mu^0_4 
+% \end{bmatrix} \quad \lambda = (\mu_1^0 + 1, \mu_2^0 + 1, \mu_3^0 + 1, \mu_4^0) \quad \mu = (\mu_1^0, 1 + \mu_2^0, 1 + \mu_3^0, 1 + \mu_4^0) 
+% \]
+% and the solution to the minimization problem is 
+% \begin{gather*}
+%     \mu^0_4 = 0 \\
+%     \mu^0_3 = \max\{0,\sum_c n_{(4,c)} - \sum_c n_{(3,c)} \} = \max\{0,1- 1\} = 0 \\
+%     \mu^0_2 = \max \{0, \mu_3^0 + \sum_c n_{(3,c)} - \sum_c n_{(2,c)}, \mu_3^0 + \sum_r n_{(r,3)} - \sum_r n_{(r,2)}\} = \max\{0,1-1,1-1\} = 0 \\
+%     \mu^0_1 = \max \{0, \mu_2^0 + \sum_c n_{(2,c)}, \mu_2^0 + \sum_r n_{(r,2)} - \sum_r n_{(r,1)}\} = \max \{0,1,1-1\} = 1 
+% \end{gather*}
+% In terms of GT-patterns and tableaux, the information of $n_\bullet$ together with $\mu^0$ define
+% Thus
+% \[
+% \gt = \begin{matrix}
+% \mu_1^0 \\
+% 1 + \mu_1^0 & \mu_2^0 \\
+% 1 + \mu_1^0 & 1 + \mu_2^0 & \mu_3^0 \\
+% 1 + \mu_1^0 & 1 + \mu_2^0 & 1 + \mu_3^0 & \mu_4^0 
+% \end{matrix} = \begin{matrix}
+% 1 \\
+% 2 & 0\\
+% 2 & 1 & 0 \\
+% 2 & 1 & 1 & 0 
+% \end{matrix} \qquad
+% \sigma_+(n_\bullet) = \young(12,3,4)
+% \]
 % m-1 = 3: are there more 4s in the first 3 rows than there are 3s in the first 2 rows? 
@@
 
-For example, if $n' = (1,0,0,0,0,0)$ and $n'' = (0,0,0,1,0,1)$ then 
+% \acom{Omitting this example..}
+% For example, if $n' = (1,0,0,0,0,0)$ and $n'' = (0,0,0,1,0,1)$ then 
 % as we already saw the smallest dominant $\tau$ with datum $n' + n''$ is $\young(12,3,4)$ 
@@
 % Note however that the second (padded) pair of tableaux is actually equivalent to the first, as we can safely delete the 1 in $\young(12)$ without affecting Lusztig data, or weight.
-
-Compare this with $n' = (0,0,0,0,0,1)$ and $n'' = (1,0,0,1,0,0)$. 
+% 
 % The total Lusztig datum is the same and so the tableau supplied by \Cref{lem:almostmintab} is the same. The two pairs of arrays of boxes are different:
@@
 
+% So given two stable MV cycles $Z',Z''$ of type $\lambda',\lambda''$ the \acom{above lemma} gives us two tableaux $\tau',\tau''$ of weight $\mu',\mu''$ such that $Z'= t^{-\lambda'}Z(\tau'), Z'' = t^{-\lambda''} Z(\tau'')$.
+% So we are almost ready to compute intersection multiplicities in $Z'\geofu Z''$
+% $Z'\geofu Z''\cong Z(\tau')\geofu Z(\tau'')$ \jcom{I don't understand this equation} \acom{is it not true?}
+% using generalized orbital varieties (\Cref{cor:intmul}).
+Recall however that $X(\tau',\tau'')_{0,0}$ only makes sense for $\tau',\tau''$ having total weight $\mu = \mu' + \mu''$ dominant.
+If this is not the case, we take the bigger of the two tableaux and apply the padding map $(\phantom{-})_+:YT\to YT_+$ increasing its padding weight by $\mu^0 = (\max(0,\mu_2-\mu_1),\max(0,\mu_3 - \mu_2),\dots,\max(0,\mu_m-\mu_{m-1}))$.
+%
+% For ease of computation we will choose our sections as small as possible.
+
 \begin{corollary}
-Given two stable MV cycles $Z',Z''$ with Lusztig data $n_\bullet',n_\bullet''$ resp.\ there exist $\lambda',\lambda''$ dominant effective and a pair of tableaux $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$ such that
+Given two stable MV cycles $Z',Z''$ with Lusztig data $n_\bullet',n_\bullet''$ resp.\ there exists a pair of tableaux $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ for some $\lambda',\lambda''$ dominant effective and some $\mu',\mu''$ effective, such that $\mu = \mu' + \mu''$ is dominant and if $\lambda = \lambda' + \lambda''$ then
 \begin{equation}
@@
 % 
-where $\lambda = \lambda' + \lambda''$. 
+% where $\lambda = \lambda' + \lambda''$. 
 \end{corollary}
-
-To write down an expansion in $\CC[N]$ we choose a section $\bar\sigma_\lambda$ valued in smallest (not necessarily dominant) representative tableaux.
+\begin{proof}
+Choose $\tau' = \sigma(n_\bullet')$, $\tau'' = \sigma(n_\bullet'')$ and suppose $\tau'\in YT(\lambda')_{\mu'}$, $\tau'' \in YT(\lambda'')_{\mu''}$. 
+Note that $Z'= t^{-\lambda'}Z(\tau'), Z'' = t^{-\lambda''} Z(\tau'')$ so the intersection multiplicity of a stable MV cycle $Z$ in $Z'\geofu Z''$ can be computed as the intersection multiplicity of an MV cycle $Z(\tau)$ in $Z(\tau')\geofu Z(\tau'')$.
+
+In case $\mu$ is not dominant, increase its padding weight of the larger of the two tableaux by $(\max(0,\mu_2-\mu_1),\max(0,\mu_3 - \mu_2),\dots,\max(0,\mu_m-\mu_{m-1}))$. 
+% Note that this does not change the Lusztig datum, still rerpesents the same stable MV cycle!
+
+Now \Cref{cor:intmul} ensures that the intersection multiplicity of $Z(\tau)$ in $Z(\tau')\geofu Z(\tau'')$ can in turn be computed as the intersection multiplicity of the generalized orbital variety $X(\tau)$ in $X(\tau',\tau'')_{0,0}$.
+\end{proof}
+
+\jcom{From what you wrote it sounds like you are padding to make the weight of $ \tau' $ dominant.
+This doesn't seem right to me.
+Just because the weight of $\tau'$ is dominant, it doesn't mean that the weight of their sum will be.
+}
+% 
+% \acom{I think it's fine. I am making $\tau'$ bigger but using $\mu$ not $\mu'$. Oh I see..}
+\acom{Ok, now I think it is better. However I don't end up really needing $()_+$ or $\sigma_+$ because we don't really need ``the total tableau'' only the total weight of two tableaux.}
+\jcom{Yes, it is better now, but maybe you could write ``intersection multiplicity of $ Z(\tau)$ in $Z(\tau') \ast_0 Z(\tau'')$'' etc.}
+
+% 
+% For example, if $n_\bullet' = (0,0,0,0,0,1)$ and $n_\bullet'' = (1,0,0,1,0,0)$, then 
+% $$
+% \sigma(n_\bullet') = \young(1,2,4) \qquad 
+% \sigma(n_\bullet'') = \young(2,3)
+% $$
+
+% To write down an expansion in $\CC[N]$ we choose a section $\bar\sigma_\lambda$ valued in smallest (not necessarily dominant) representative tableaux.
 
@@
 \label{s:examples}
-\acom{Rewrite in view of fusion section. Relations dictated by $\tau$. Can mostly refer the reader to the previous section for this background, now.}
+% \acom{Rewrite in view of fusion section. Relations dictated by $\tau$. Can mostly refer the reader to the previous section for this background, now.}
 % \acom{Plus fusion product of fake MV cycles for a fourth!}
 
-As stated in the previous section, we will label MV cycles as semi-standard young tableaux.
-Suppose we have two tableaux $\tau'$ and $\tau''$, with respective weights $\lambda'$, $\mu'$ and $\lambda''$, $\mu''$, and we wished to take their fusion product.
+We will abbreviate MV basis elements to their $\sigma$ tableaux and view $\CC[N]$ as an algebra in these, rewriting \Cref{eq:btimesb} as an equation in tableaux. 
+Suppose we have two tableaux $\tau'$ and $\tau''$, with respective weights $\lambda'$, $\mu'$ and $\lambda''$, $\mu''$, and we wish to take their fusion product.
 We consider a generic matrix $A \in \UU^{\mu',\mu''}_{0,s}$ as well as its submatrices $A_i := A\big|_{\CC^{|\mu(i)|}} \in \UU^{\mu'(i), \mu''(i)}_{0,s}$ for each $i=1, \dots, m$.
@@
 
-The requirement that each $A_i \in \OO^{\lambda'(i), \lambda''(i)}_{0,s}$ imposes rank conditions, equivalently vanishing and non-vanishing minors, which translates to relations in the coordinate ring $\CC[s, s^{-1}, A_{ij}^k : 1 \leq i,j \leq m, k \geq 1]$.
-\rcom{Would $\CC[A_{ij}^k, s, s^{-1}]$ be enough?}
+The requirement that each $A_i \in \OO^{\lambda'(i), \lambda''(i)}_{0,s}$ imposes rank conditions, equivalently vanishing and non-vanishing minors, which translates to relations in the coordinate ring $\CC[A_{ij}^k, s^\pm]$
+% $\CC[s, s^{-1}, A_{ij}^k : 1 \leq i,j \leq m, k \geq 1]$. 
+% \rcom{Would $\CC[A_{ij}^k, s, s^{-1}]$ be enough?} \jcom{Yes, I think so, you could also use $ s^\pm$ instead of $ s, s^{-1} $}
 Let $I$ be the ideal generated by these relations.
-Then $$J = (I \cap \CC[A_{ij}^k,s]) + (s)$$ gives us the ideal for the fusion.
-Taking the primary decomposition of $J$ gives us the ideal for each generalized orbital variety, which we then translate to a tableau, and finally to an MV cycle.
+Then $$J = (I \cap \CC[A_{ij}^k,s]) + (s)$$ gives us the ideal for the fusion $ X(\tau', \tau'')_{0,0}$.
+Taking the primary decomposition of $J$ gives us ideals $J_1,\dots,J_n$, each corresponding to a generalized orbital variety occurring in the fusion.
+We then translate each of the $J_i$ to a tableau and finally to an MV cycle.
+Each $J_i$ also tells us the multiplicity of each MV cycle in the fusion product, where we have multiplicity 1 if and only if $J_i = \sqrt {J_i}$.
+
+\jcom{This is much better now.
+The only problem is that the phrase ``the ideal'' occurs many times in this paragraph and sometimes refers to different ideals, so I think you could make this a bit more precise.
+Especially ``gives us the ideal for each generalized orbital variety'' is quite confusing, maybe change to ``for those g.o.v.
+occurring in the fusion''.
+I made one edit.}
 
@@
 
-\jcom{More precisely, we have $ I \subset \CC[a_i, s, s^{-1}] $ then form $ I \cap \CC[a_i, s]$ and then quotient by $ s$.
+%\jcom{More precisely, we have $ I \subset \CC[a_i, s, s^{-1}] $ then form $ I \cap \CC[a_i, s]$ and then quotient by $ s$.
 This corresponds to taking the closure $ X(\tau',\tau'')_{0,\AA}$ and then taking the fibre.}
@@
 \begin{example}
-$\young(22)\arfu\young(11,33)$:
-
+$\young(22)\arfu\young(11,33)= \young(33) + \young(22,33) + 2\cdot \young(23,3)$:
+% 
 % \acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{claxton2015young}}
-
-Let $G = \GL_3$. Consider the tableaux
-$$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
-Then the weights are $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (0,2,0)$, and $\mu'' = (2,0,2)$. Our matrix $X$ is now
+% 
+% Let $G = \GL_3$. 
+% 
+% Consider the tableaux
+% $$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
+% Then the weights are $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (0,2,0)$, and $\mu'' = (2,0,2)$. Our matrix $X$ is now
+
+The requirement that 
 \[
@@
 \end{BMAT}
-\right].
+\right]\text{ is contained in } \young(22)\bdfamo \young(11,33)
 \]
-Using a computer, the ideals we get are
-$$
-\begin{array}{cl}
-    I_1 = & ( A_{12}^1, A_{12}^2,s ) \\
-    I_2 = & ( A_{23}^1, A_{23}^2,s ) \\
-    I_3 = & ( (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2,s ). 
-\end{array}
-$$
-The tableaux corresponding to each ideal is
-$$
-\begin{array}{cc}\vspace{1mm}
-    \young(1133,22) & \text{for } I_1 \\ \vspace{1mm}
-    \young(1122,33) & \text{for } I_2 \\ \vspace{1mm}
-    \young(1123,23) & \text{for } I_3
-\end{array}
-$$
-Note that the ideal $I_3$ has multiplicity 2 so our equation in $\CC[N]$ becomes
-\[
-\young(22) \cdot \young(11,33) = \young(33) + \young(22,33) + 2\cdot \young(23,3).
-\]
+results in the following relations on submatrices.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Submatrix} & \text{Relations} \\
+    \midrule 
+    A_2 & \text{None}  \BS \\ 
+    A_3 & 2 A_{12}^2 A_{23}^2 s + 3 A_{13}^2 s^2 + A_{12}^2 A_{23}^1 + A_{12}^1 A_{23}^2 + 2 A_{13}^1 s, \\
+     & A_{13}^2 s^3 - A_{12}^2 A_{23}^1 s - A_{12}^1 A_{23}^2 s - 2 A_{12}^1 A_{23}^1, \\ 
+     & A_{12}^2 A_{13}^2 A_{23}^1 s^2 + A_{12}^1 A_{13}^2 A_{23}^2 s^2 - (A_{12}^2 A_{23}^1)^2 + 2 A_{12}^1 A_{12}^2 A_{23}^1 A_{23}^2 - (A_{12}^1 A_{23}^2)^2 \\
+     & + 6 A_{12}^1 A_{13}^2 A_{23}^1 s + 4 A_{12}^1 A_{13}^1 A_{23}^1, \\
+     & A_{12}^1 A_{13}^2 (A_{23}^2)^2 s^2 - (A_{12}^2 A_{23}^1)^2 A_{23}^2 + 2 A_{12}^1 A_{12}^2 A_{23}^1 (A_{23}^2)^2 - (A_{12}^1)^2 (A_{23}^2)^3 \\ 
+     & - 2 A_{12}^2 A_{13}^2 (A_{23}^1)^2 s + 4 A_{12}^1 A_{13}^2 A_{23}^1 A_{23}^2 s - A_{13}^1 A_{13}^2 A_{23}^1 s^2 - 3 A_{12}^1 A_{13}^2 (A_{23}^1)^2 \\
+     & + 4 A_{12}^1 A_{13}^1 A_{23}^1 A_{23}^2, \\
+     & (A_{12}^2)^3 (A_{23}^1)^2 A_{23}^2 - 2 A_{12}^1 A_{23}^1 (A_{12}^2 A_{23}^2)^2 + A_{12}^2 (A_{12}^1)^2 (A_{23}^2)^3 + 2 A_{13}^2 (A_{12}^2 A_{23}^1)^2 s \\
+     & + 2 A_{13}^2 (A_{12}^1 A_{23}^2)^2 s + 3 A_{12}^1 (A_{13}^2)^2 A_{23}^1 s^2 + A_{13}^1 (A_{12}^2 A_{23}^1)^2 + 4 A_{12}^1 A_{12}^2 A_{13}^2 (A_{23}^1)^2  \\
+     & - 6 A_{12}^1 A_{12}^2 A_{13}^1 A_{23}^1 A_{23}^2 + 4 (A_{12}^1)^2 A_{13}^2 A_{23}^1 A_{23}^2  - 4 A_{12}^1 A_{13}^1 A_{13}^2 A_{23}^1 s - 4 A_{12}^1 (A_{13}^1)^2 A_{23}^1 \\
+     & + A_{13}^1 (A_{12}^1 A_{23}^2)^2
+    \end{tabular}
+\end{table}
+At $s=0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Ideal of }X(\tau) & \tau \\
+    \midrule 
+    ( A_{12}^1, A_{12}^2,s ) & \young(1133,22)  \BS \\ 
+    ( A_{23}^1, A_{23}^2,s ) & \young(1122,33) \BS\TS \\
+    ( (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2,s ) & \young(1123,23) \TS
+    \end{tabular}
+\end{table}
+% $$
+% \begin{array}{cl}
+    % I_1 = & ( A_{12}^1, A_{12}^2,s ) \\
+    % I_2 = & ( A_{23}^1, A_{23}^2,s ) \\
+    % I_3 = & ( (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2,s ). 
+% \end{array}
+% $$
+% The tableaux corresponding to each ideal is
+% $$
+% \begin{array}{cc}\vspace{1mm}
+%     \young(1133,22) & \text{for } I_1 \\ \vspace{1mm}
+%     \young(1122,33) & \text{for } I_2 \\ \vspace{1mm}
+%     \young(1123,23) & \text{for } I_3
+% \end{array}
+% $$
+The latter component occurs with multiplicity 2.
 \end{example}
@@
 
-\jcom{I think that you should clarify what you mean by ``our ideal'' below.  I think that it is the ideal of $ X(\tau', \tau'')_{0,0}$, is that correct?}
-
-\acom{The example below is an $A_2$ example, the same as the first $A_2$ example above.}
+% \jcom{I think that you should clarify what you mean by ``our ideal'' below.  I think that it is the ideal of $ X(\tau', \tau'')_{0,0}$, is that correct?}
+
+% \acom{The example below is an $A_2$ example, the same as the first $A_2$ example above.}
 \begin{example}

### 2021-06-11 submission.tex
ready steady

--- 2021-06-05 draft.tex
@@
 % 
-\documentclass{article} % [draft] TODO: use this at the end to check for overfills 
+\documentclass{article} 
 \usepackage{basic}
-\usepackage{emoji}
 \usepackage{float}
-% TODO: The matrix is lower triangular and the lower-triangular matrix is
-% \setemojifont{Apple Color Emoji}
-% Working title: 
-\title{How to compute the fusion product of MV cycles in type $A$}
+\title{Computing fusion products of MV cycles using the Mirkovi\'c--Vybornov isomorphism}
 \author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
-% \date{October 2020}
 \date{\today}
@@
 \maketitle
-\tableofcontents
-
-\section{Todolist}
-\begin{itemize}
-    \item Remove the TOC 
-    \item Edit the intro 
-    \item We are using the word [geometric] fusion just for the central fibre, we also have arithmetic fusion (aka multiplication in $\CC[N]$), and BD family: $X\geofu Y, b(X) \arfu b(Y), X \bdfamc Y\supset X\bdfamo Y$
-    \item Which MVy paper to cite? 
-    \item Super repetitive about lambdas and mus 
-    \item Formatting could be bit better, e.g.\ some stuff goes outside the margin
-    \item Fix section titles and other organizational seasoning  
-    \item Fix numbering so that theorems, defs etc share a counter and are restarted by section 
-    \item tableau of weight/filling? box of weight/filling? I prefer weight but don't mind filling 
-    \item Recalling intersection multiplicity, checking that the definitions allow passing to open sets
-    \item in examples put ideals of arithmetic fusion and their tableaux into tables; also split examples into 2 sections: $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with rising action?
-\end{itemize}
+% \tableofcontents
+\begin{abstract}
+    Motivated by a conjecture of Anderson describing the structure of the ring of functions on a unipotent subgroup as an algebra spanned by the Mirkovi\'c--Vilonen cycles for the Langlands dual group with respect to the fusion product, we give a conceptually elementary approach to computing this product in type $A$.
+
+    We do so with the help of the Mirkovi\'c--Vybornov isomorphism (one of several established in \cite{mirkovic2007quiver}), which relates slices in the affine Grassmannian of $\GL_m$ and slices in nilpotent orbits of $N\times N$ matrices.
+
+    Extending this isomoprhism to one relating families of slices in the two point Beilinson--Drinfeld Grassmannian and families of slices in orbits of matrices having two eigenvalues, we are able to transfer the fusion product of cycles to a fusion of matrices.
+
+    As an application, we confirm that the cluster variables in $\CC[N]$ are contained in its Mirkovi\'c--Vilonen basis when $m=4$. 
+\end{abstract}
 
@@
 % 
-%Throughout this paper (unless indicated otherwise) the base field is $\CC$, but it does not have to be?
-
-The geometric Satake equivalence of Mirkovi\'c and Vilonen \cite{mirkovic2007geometric} provides an equivalence of categories between the category of spherical perverse sheaves in the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.
+\subsection{Geometric Satake and Mirkovi\'c--Vilonen cycles}
+\label{ss:gsmv}
+% 
+The geometric Satake equivalence of Mirkovi\'c and Vilonen \cite{mirkovic2007geometric} is an equivalence of categories between the category of spherical perverse sheaves on the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.
 This foundational result provides a powerful tool to study representation theory using geometry.
-In particular, under this equivalence, the Mirkovi\'c--Vilonen cycles in the affine Grassmannian of $ G $ index bases for irreducible representations of $ G^\vee $.
+In particular, under this equivalence, the MV cycles (short for Mirkovi\'c--Vilonen) in the affine Grassmannian of $ G $ index bases for irreducible representations of $ G^\vee $.
 In this paper we work with $ G = \GL_m$ and identify $ G^\vee = \GL_m$ as well.
 
-% The Mirkovi\'c--Vybornov isomorphism
-In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_N)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $N\times N$ nilpotent orbits on the one hand
-% conjugacy classes of nilpotent matrices 
-and to Nakajima quiver varieties on the other hand.
-The second author showed \cite{dthesis} that under the Mirkovi\'c-Vybornov isomorphism, the  Mirkovi\'c--Vilonen cycles are identified with certain varieties of matrices, called generalized orbital varieties.
-
-%This extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of matrices with two eigenvalues. 
-%This paper generalizes the first of these relations (an isomorphism) to families of slices in the Beilinson--Drinfeld Grassmannian.
-\jcom{I changed this because MVy did consider the BD Grassmannian as well.}
-
-Essential to \cite{mirkovic2007geometric}, the Beilinson--Drinfeld Grassmannian is used to define a fusion product on the category of spherical perverse sheaves on the affine Grassmannian.
-In \cite{anderson2003polytope}, Anderson used the Beilinson--Drinfeld Grassmannian to define a fusion of Mirkovi\'c--Vilonen cycles.
-He conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup $ N \subset\GL_m$.
-This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that the Mirkovi\'c--Vilonen cycles give a basis for $ \CC[N]$, which we call the MV basis.
-% 
-%To quote from \cite{mirkovic2007geometric}:
-%\begin{quotation}
-%    However, we make crucial use of an idea of Drinfeld, going back to around 1990.
-He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
-%\end{quotation}
-%
-
-Unfortunately, computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.
-A few such computations were done by Anderson-Kogan in \cite{anderson2006algebra} in a somewhat ad-hoc fashion.
-Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann-Gaussent-Littelmann \cite{baumann2020bases}.
+In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov supply a geometric version of symmetric and skew Howe $(\GL_m,\GL_N)$ dualities.
+They relate Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $N\times N$ nilpotent orbits on the one hand, and to Nakajima quiver varieties on the other hand.
+The second author \cite{dthesis} showed  that under the Mirkovi\'c--Vybornov isomorphism, the MV cycles are identified with certain varieties of matrices, called generalized orbital varieties.
+
+Essential to the geometric Satake equivalence, the BD Grassmannian (short for Beilinson--Drinfeld) is used to define a fusion product on the category of spherical perverse sheaves on the affine Grassmannian.
+In \cite{anderson2003polytope}, Anderson used the BD Grassmannian to define a fusion of MV cycles.
+He constructed a family where the general fibre is a Cartesian product of two MV cycles, and the special fibre, called the fusion, is a (non-reduced) union of MV cycles.
+Anderson conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup $ N \subset\GL_m$.
+This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that the MV cycles give a basis for $ \CC[N]$.
+
+\subsection{Fusion using generalized orbital varieties}
+\label{ss:fugov}
+% 
+Computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.
+A few such computations were done by Anderson and Kogan in \cite{anderson2006algebra} in a somewhat ad-hoc fashion.
+Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann, Gaussent and Littelmann \cite{baumann2020bases}.
 
 The purpose of this paper is to give a conceptually elementary way to compute this product by transferring it to a fusion product of generalized orbital varieties.
-To do so, we use that the Mirkovic-Vybornov isomorphism extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of matrices with two eigenvalues.
-Our main result is the following.
-
-\begin{maintheorem}
-    Let $ Z, Z' $ be MV cycles.
-The structure constants for the multiplication of $ b_Z b_{Z'}$ in $\CC[N]$ are equal to the intersection multiplicities in the fusion of the generalized orbital varieties corresponding to $ Z, Z'$.
-\end{maintheorem}
-% 
-\jcom{I wanted to state a precise theorem, but it is not so easy without introducing a lot of notation.}
-
-%One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!
-
-An application of this result is to relate the cluster algebra structure in $\CC[N]$ to the MV basis.
-Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{berenstein2005cluster3} and \cite{geiss2007initial} that $\CC[N]$ has a natural cluster algebra structure.
-
-This structure starts with an initial seed $\Sigma = ((x_1,\cdots,x_r),B)$ where $x_i \in \CC[N]$ and $B$ is some matrix.
-We obtain new variables through a process called mutation where for a mutable variable $x_i$, its mutation is the unique element $x_i^* \in \CC[N]$ such that $$x_ix_i^* = x_+ + x_-.$$
-This equation is called an exchange relation and the terms $x_+$ and $x_-$ are some product in the $x_j$, $j\neq i$, that is determined by $B$.
-We then obtain a new seed $$\mu_i(\Sigma) = ((x_1,\cdots, x_{i-1}, x_i^*, x_{i+1},\cdots,x_r), \mu_i(B))$$ and can acquire possibly new variables through further mutations.
-
-The variables $x_1,\cdots,x_r$ as well as all possible variables that are obtained through successive mutations are known as cluster variables.
-The cluster monomials are products of cluster variables that are supported on a single seed.
-
-It has been shown that the cluster monomials are in certain interesting bases such as the dual canonical basis \cite{lusztig1990canonicalbases}\cite{kang2018monoidal} and the dual semicanonical basis \cite{lusztig2000semicanonical}\cite{geiss2006rigid}.
-As these elements are defined in a combinatorial way, it allows efficient computation of several elements of these bases.
-
-Although the MV basis and the above mentioned bases are in general different from each other \cite{baumann2019mirkovic}, it is believed that they at least all contain the cluster monomials, leading to the following conjecture.
-
+To do so, we use that the Mirkovi\'c--Vybornov isomorphism extends to an isomorphism between families of slices in the BD Grassmannian and families of slices of matrices with two eigenvalues.
+Our main result is the following (see \Cref{cor:goodreps} for a more precise statement).
+
+\begin{theorem}
+    Let $ Z', Z'' $ be MV cycles.
+The structure constants for the multiplication $ b_{Z'} b_{Z''}$ in $\CC[N]$ are equal to the intersection multiplicities of generalized orbital varieties in the fusion of the generalized orbital varieties corresponding to $ Z', Z''$.
+\end{theorem}
+
+Since these generalized orbital varieties are subschemes of affine spaces of matrices defined by certain rank conditions, the fusion of generalized orbital varieties can be computed by elementary commutative algebra.
+
+\subsection{Cluster algebras and MV cycles}
+One motivation for computing products of MV basis elements is to relate the cluster algebra structure on $\CC[N]$ to the MV basis.
+Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{geiss2007initial}, using a construction of \cite{berenstein2005cluster3}, that $\CC[N]$ has a natural cluster algebra structure.
+
+This structure starts with an initial seed $\Sigma = (\{x_1,\dots,x_r\},B)$, where $x_i \in \CC[N]$ are a cluster of variables, $B$ is a certain matrix, and $ r = m(m-1)/2$.
+We obtain new variables through a process called mutation, where for a mutable variable $x_i$, its mutation is the unique element $x_i^* \in \CC[N]$ such that 
+$$
+    x_ix_i^* = x_+ + x_- \,.
+$$
+This equation is called an exchange relation, and the terms $x_+$ and $x_-$ are certain monomials in the $x_j$, $j\neq i$,  determined by $B$. 
+It gives us the new cluster $\{x_1, \dots, x_i^*, \dots, x_r\}$.
+
+The initial cluster $\{x_1,\dots,x_r\}$ as well as all possible variables that are obtained through successive mutations are known as cluster variables. 
+The cluster monomials are products of cluster variables that are supported on a single cluster.
+
+There are two well-known bases of $\CC[N]$ whose relationship with the cluster structure has been heavily studied: the dual canonical basis of \cite{lusztig1990canonicalbases} and the dual semicanonical basis of \cite{lusztig2000semicanonical}.
+In \cite{kang2018monoidal}, Kang, Kashiwara, Kim and Oh showed that the cluster monomials are contained in the dual canonical basis, while, in \cite{geiss2006rigid}, Gei\ss, Leclerc and Schr\"oer proved that they are all contained in the dual semicanonical basis.
+% \cite[Theorem~2.8(3)]{geiss2006rigid}.
+%
+
+The MV basis, the dual canonical basis, and the dual semicanonical basis are all examples of biperfect bases of $\CC[N]$ \cite[Section 2]{baumann2019mirkovic}.
+In particular, they share a crystal structure.
+In \cite[Appendix]{baumann2019mirkovic}, we showed that the MV basis differs from the dual semicanonical basis at the same point in the underlying crystal as where the dual semicanonical basis differs from the dual canonical basis.
+% 
+The fact that this point at which each of these bases differ is not a cluster monomial in any of these bases, gives evidence for the following conjecture of Anderson and Kogan \cite[Conjecture 5.1]{anderson2006algebra}.
 \begin{conjecture}\label{conj:cluster in MV}
-    %The dual semicanonical basis and the MV basis overlap on the cluster monomials. 
     The cluster monomials are contained in the MV basis. 
@@
 
-The conjecture is true in type $A_n$ with $n\leq 3$ as in these cases, the MV basis agrees with the dual semicanonical and dual canonical bases \cite{baumann2019mirkovic}.
-It has also been shown that cluster monomials supported on seeds satisfying a special condition are also in the MV basis \cite{baumann2020bases}.
-In addition, cluster variables coming from the initial seeds constructed in \cite{berenstein2005cluster3} are also in the MV basis \cite{kato2011polytopal}.
-
-This leads to the following idea to show that the cluster variables are in the MV basis.
-Given a seed $((x_1,\cdots,x_r),B)$ with each of the $x_i$ in the MV basis, say corresponding to MV cycles $Z_i^*$, and an exchange relation $x_ix_i^* = x_+ + x_-$, it suffices to find an MV cycle $Z_i^*$ such that the fusion product of $Z_i$ and $Z_i^*$ gives $Z_+$ and $Z_-$, corresponding respectively to $x_+$ and $x_-$.
-In this case, we are able to conclude that $x_i^*$ is in the MV basis corresponding to the MV cycle $Z_i^*$.
-Inducting on mutation, we conclude that all cluster variables are in the MV basis.
-
-We show in Section \ref{ss:GL4 examples} that this is indeed the case in type $A_3$ by directly computing each fusion product corresponding to an exchange relation.
-
-% {\color{blue}
-% \acom{To quote from BFZ for a concise definition: Cluster algebras are a class of commutative rings defined axiomatically in terms of a distinguished family of generators called cluster variables.
-Say also what is a seed, what is a mutation, what is a cluster, what is a cluster monomial, and finally for the stubbornly ignorant clarify that 'the cluster monomials' refers to cluster monomials for all possible clusters!}
-
-% $\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
-% % that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.
-
-% \acom{Background on cluster:}
-% In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis.
-This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$.
-% Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
-
-% In the appendix to \cite{baumann2019mirkovic} the second and third author along with Morton-Ferguson check that the MV basis differs from the dual semicanonical basis (at the Kashiwara--Saito counterexample).
-% Yet, the two bases have enough in common (c.f.\ BKT,...?), that we have the following conjecture.
-
-% \begin{conjecture}
-%     The dual semicanonical basis and the MV basis overlap on the cluster monomials. In particular, the cluster monomials are contained in the MV basis. 
-% \end{conjecture}
-
-% We note that both of these bases are \new{biperfect} bases of $\CC[N]$ and in type $A_n$ with $n\le 3$ there is a unique biperfect basis of $\CC[N]$. }
-
-% Anderson and Kogan conjectured in \cite{anderson2006algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
-% % and they conjectured a formula for many of them.
-
-% It's not clear how this work helps with/relates to AK/their conjectures.
-
-% The generalized \mvy is interesting in its own right. \acom{is it?}
-
-% Computing fusion still hard but at least boiled down to linear algebra.
-Cf.\ fusion product as it appears in \cite{beilinson1991quantization,feigin2generalized,mirkovic2007geometric,anderson2006algebra,bezrukavnikov2005equivariant}.
-
-% Interesting combinatorics?
-Presumably it is related to Feigin and Loktev's generalized Kostka polynomials?
-Though Joel says that the product on SSYT that we are witnessing is unlikely to have a combinatorial description.
-
-% Exchange relations only work on cluster modules where one is a mutation of the other (i.e.\ those corresponding to cluster monomials which are related by mutation).
-Of course this gives me everything.
-Up to $A_4$ as in type $A_5$ there exist indecomposable modules which are not cluster, so exchange relations do not apply.
-
-% The hope (conjecture) is that this paper gives a way to compute on such modules.
-Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is a cluster monomial belonging to both bases and $c_Y$ is the square of a cluster monomial ($b'$ say) belonging to both bases.
-The $\barD$ equation suggests that $(b')^2 = b_Z + 2b$.
-We can try to check this using Roger's script.
-Such calculations bring us closer to answering two questions.
-First, how forgetful is $\barD$.
-Second, on the level of modules, are the terms appearing in the fusion product determined by $\Ext^1$ of the factors.
-By Roger's thesis this is true if the factors are cluster modules related by a mutation.
-
-% % No; $x*y=\sum z\Rightarrow y = \frac 1 x \sum z$.
-
-% Representation theory?
-
-\section{Players}
+The conjecture is true in type $A_n$ for $n\leq 3$ since in these cases $\CC[N]$ has a unique biperfect basis \cite[Section 2.3]{baumann2019mirkovic}.
+% 
+More generally, cluster variables called flag minors, coming from initial seeds constructed in \cite[Definitions~2.2--2.3]{berenstein2005cluster3}, belong to each biperfect basis of $\CC[N]$ \cite[Remark~2.10]{baumann2019mirkovic}.
+And recently in \cite[Proposition 7.2]{baumann2020bases} cluster monomials supported on clusters of flag minors satisfying a certain combinatorial condition where shown to be in the MV basis.
+
+Our hope is that each exchange relation can be realized using the fusion of MV cycles.
+This would imply that all cluster variables are in the MV basis.
+In \Cref{ss:GL4 examples} we verify that this is indeed the case in type $A_3$ by directly computing each fusion product corresponding to an exchange relation.
+
+\section{Supporting Cast}
 \label{s:players}
+% 
 \subsection{Rings and discs}
@@
 Set $\cO = \cO_0 = \CC\xt$ and $\cK = \cK_0 = \CC\xT$.
-% TODO: I rearranged this sentence, because starting it with 'for any other' presupposes we have introduced s 
-%  For any other 
-We will also consider $\cO_s = \CC\xt[t-s]$ and its fraction field $\cK_s=\CC\xT[t-s]$, for any 
-$ s \in \CC\setminus\{0\} $, as well as $ \Oinf = \CC\xt[t^{-1}] $ and $\Kinf = \CC\xT[t^{-1}]$. For any point $ s \in \PP = \PP^1$, 
-% TODO: Identifying $s\in\CC$ and the line $s\in\PP$ containing it right?
-$ \cO_s$ is the completion of the local ring $ \mathcal O_{\PP, s} $ and thus the formal spectrum of $ \cO_s$ is the formal neighbourhood $ D_s$ of $ s $ (also called the formal disc centered at $ s$).
-Similarly the formal spectrum of the field $\cK_s$ is the deleted formal neighbourhood (or punctured disc), denoted $ D_s^\times$.
-
-Note that for $ s \in \CC $, we have an obvious isomorphisms  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$. % ok technically the point s is in P and the coordinate s is valued in C 
-% 
+We will also consider $\cO_s = \CC\xt[t-s]$ and its fraction field $\cK_s=\CC\xT[t-s]$, for any $ s \in \CC\setminus\{0\} $, as well as $ \Oinf = \CC\xt[t^{-1}] $ and $\Kinf = \CC\xT[t^{-1}]$.
+For any point $ s \in \PP = \PP^1$, $ \cO_s$ is the completion of the local ring $ \mathcal O_{\PP, s} $ and thus the formal spectrum of $ \cO_s$ is the formal neighbourhood $ D_s$ of $ s $ (also called the formal disc centered at $ s$).
+Similarly, the formal spectrum of the field $\cK_s$ is the deleted formal neighbourhood (or punctured disc), denoted $ D_s^\times$.
+
+Note that for $ s \in \AA $, we have an obvious isomorphism  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$. 
+%
+
 \subsection{Groups}
@@
 Let $H $ be an algebraic group over $ \CC $.  We will be interested in $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  
-% 
-% \acom{random question, I know $H(R)$ is supposed to mean functor of points of the scheme $H$ but can it also be viewed as a base change from $\CC$ to $\RR$?}
-% \jcom{Usually $ H_R$ is the notation used for the base change, so using $ H(R)$ here is a bit of an abuse, but it is common and harmless.}
 % 
@@
 We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$.
-% \acom{Add $G_1$}
-%\acom{TODO: Algebraic groups over rings, i.e.\ the meaning of $G(K)$.
-The affine space of $m\times m$ matrices which we denote $ M_m$.
-The first congruence subgroup $G_1$ and why we take $\Oinf$ points instead of $\CC[t]$ points as some of the lit does.}
-
-Throughout the paper, we fix $ m \in \NN$.  We let $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
-% are there other possibilities?? :S 
-We identify $\ZZ^m$ with the coweight lattice of $G$ and say that a coweight 
-% The coweight lattice of $ G $ is $ \ZZ^m = \Hom(\AA^\times,T)$.
-% TODO: Thank you - resolved!
-% \acom{This identification assumes we are taking $\CC$ points of $G$ right?
-i.e.\ it's really $P(T(\CC)) = \Hom(\AA^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?}
-% \jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}
-% 
-% The \new{dominant coweights} of $ G $ are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) \in \ZZ^m $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
-% 
-% A coweight $ \mu = (\mu_1, \dots, \mu_m) \in \ZZ^m$ is called \new{effective} if $ \mu_j \ge 0 $ for all $ j$.
-% 
-$\nu = (\nu_1,\dots,\nu_m)$ is \new{dominant} if $\nu_1\ge\cdots\ge\nu_m$ and \new{effective} if $\nu_j\ge 0$ for all $j$.
-% We also need the notion of effective dominant coweight, 
-% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
-%which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  
-% \acom{1.
-No boldface on this new term.
-Proceed with selective boldfacing?
-2.
-Since we sometimes need $\Peff$ which contains $P_{++} = \Peff\cap\Pdom$, how about just using the notation $\Peff,\Pdom$ instead of $P_+, P_{++}$ for a change?}
-% \jcom{I added the definition of effective coweight.
-I actually don't think that we need any special notation $ P, P_+, P_{dom}$ etc !
-Later we can just write ``$ \lambda \in \ZZ^m$ a dominant or effective coweight'' etc}
-% TODO: it's settled then, no special notation fro coweights!
-% 
-If $\nu\in\ZZ^m$ is both effective and dominant then it is a partition of size $|\nu| = \nu_1 + \cdots + \nu_m\in\NN$.  Let $ Q_+ \subset \ZZ^m$ denote the positive root cone, explicitly we have
-$$
-Q_+ = \{ (\nu_1, \dots, \nu_m) : \nu_1 + \cdots + \nu_j \ge 0 \text{ for $j = 1, \dots, m-1 $ and } \nu_1 + \dots + \nu_m = 0 \}
+
+Throughout the paper, we fix $ m \in \NN$.  We let $G = \GL_m$ and we let $T\subset G$ be the maximal torus of diagonal matrices. 
+We identify $\ZZ^m$ with the coweight lattice of $G$ and say that a coweight $\nu = (\nu_1,\dots,\nu_m)$ is \new{dominant} if $\nu_1\ge\cdots\ge\nu_m$ and \new{effective} if $\nu_j\ge 0$ for all $j$.
+% 
+If $\nu$ is both effective and dominant, then it is a partition of size $|\nu| = \nu_1 + \cdots + \nu_m\in\NN$.  Let $ Q_+ \subset \ZZ^m$ denote the positive root cone, explicitly we have
+$$
+    Q_+ = \{ (\nu_1, \dots, \nu_m) : \nu_1 + \cdots + \nu_j \ge 0 \text{ for $j = 1, \dots, m-1 $ and } \nu_1 + \dots + \nu_m = 0 \}\,. 
 $$
@@
 
-%We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights. 
-% 
-% nicematrix test
-% $\begin{bNiceArray}{ccc|c}[margin]
-%     \Block{3-3}<\Large>{A} & & & 0 \\
-%     & \hspace*{1cm} & & \Vdots \\
-%     & & & 0 \\
-%     \hline
-%     0 & \Cdots& 0 & 0
-%     \end{bNiceArray}$
-% 
-% $\begin{pNiceMatrix}
-%     \frac12 & -\frac12 \\
-%     \frac13 & \frac14 \\
-%     \end{pNiceMatrix}$
-% 
-% Set $\AA = \AA^1_x$ (the subscript denoting the chosen local coordinate) and fix $s\in \AA - \{0\}$. 
-% 
-% Given a coweight $\mu \in \ZZ^m$ and a point $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
 Given $s\in\CC$ we define $(t-s)^\nu$ to be the diagonal matrix 
-% with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
-% \[
-%     \begin{pNiceMatrix}[nullify-dots,xdots/line-style=loosely dotted]
-%         (t-s)^{\mu_1} & 0             & \Cdots & 0 \\
-%         0             & (t-s)^{\mu_2} & \Ddots & \Vdots \\
-%         % 0 & b & a & \Ddots & & \\
-%         \Vdots              & \Ddots        & \Ddots & 0 \\
-%         % \Vdots & & & & \\
-%         0             & \Cdots        &   0    & (t-s)^{\mu_m}
-%     \end{pNiceMatrix}
-% \]
 \[
@@
 \]
-which we can view in 
-% $\GL_m(K) $ 
-$G(K)$ for any ring $ K $ containing $(t-s)^{-1}$ and $\CC[t]$. For example, $(t-s)^\nu\in G(K)$ for $ K = \Ks$ or $\CC(t)$. % A: Think R sb K; changed it
-
-% Resolved
-% \acom{We will also sometimes write $(t-s)^\mu$ for its image in $G(K)/G(R)$ and we hope it will be clear? Only we haven't introduced this space yet.}
-% \jcom{I think that we do this infrequently enough that it is not a problem and there is no need to mention it here.}
-% Resolved
-% 2.
-Change notation $\mu = (\mu_1,\dots,\mu_m)$ since we also have $\mu = \mu_1 + \mu_2$.
-We could do $\mu = \mu' + \mu''$ or $\mu = a + b$?
-The notation $\mu^{(i)}$ is already taken to mean sth.
-Ofc all can be changed.
-Can also do $\mu = {}_{1}\mu + {}_{2}\mu$.
-\emoji{sweat-smile}}
-
-We will also be interested in the affine space $ M_m$ of $m\times m$ matrices.  Note that for any $ \CC$-algebra $ R $, 
-% $\GL_m(R) $ 
-$G(R)$ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$. Thus for example $ (t-s)^\mu\in M_m(\CC[t])$ for all effective $ \mu \in \ZZ^m$ but 
-% $ t^\lambda \in \GL_m(\CC[t]) $ 
-$(t-s)^\mu\in G(\CC[t])$ if and only if $ \mu = 0 $.
-%
-
-% \acom{Maybe add that it's the same for $G(\cO)$. Also, we are using the notation $G(R)$ in one paragraph and defining it in the next. Maybe introduced $M_m$ first?}
-% \jcom{I don't consider that to be the definition of $ G(R)$.  The definition is the invertible $ m \times m$ matrices with coefficients in $ R $.  So I think that everything is fine.}
+which we can view in $G(K)$ for any ring $ K $ containing $(t-s)^{-1}$ and $\CC[t]$. For example, $(t-s)^\nu\in G(K)$ for $ K = \Ks$ or $\CC(t)$.
+
+We will also be interested in the affine space $ M_m$ of $m\times m$ matrices.
+Note that for any $ \CC$-algebra $ R $, $G(R)$ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
+Thus for example $ (t-s)^\mu\in M_m(\CC[t])$ for all effective $ \mu \in \ZZ^m$ but $(t-s)^\mu\in G(\CC[t])$ if and only if $ \mu = 0 $.
+%
 
@@
 \label{ss:lat}
+% 
 We will use the lattice model for the affine Grassmannian, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
-% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
 Consider $ K^m $ as a $K$-module.
-% \acom{left or right, doesn't matter? I think we are in a situation where they are the same, i.e.\ our rings are commutative.} 
-By restriction $ K^m$ can be viewed as an $R$-module.  An \new{$R$-lattice} in $K^m$ 
-% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
-is an $R$-submodule $ L \subset K^m$ 
-% such that $ L $ 
-which is a free $R$-module of rank $ m $ and satisfies $ L \otimes_R K = K^m $. Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. 
-% 
-\begin{comment}
-\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
-\acom{Roger has proved that what is written is ok.}
-\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear we that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$.
-Since $L\otimes K = K^m$, these also generate $K^m$ over $K$.
-Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$.
-Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis.
-I think the only thing that is needed is that the rings are commutative.}
-\jcom{Great.}
-\end{comment}
-
-% The trivial lattice is 
-% No more: L_0(R) = 
+By restriction $ K^m$ can be viewed as an $R$-module.
+An \new{$R$-lattice} in $K^m$ is an $R$-submodule $ L \subset K^m$ which is a free $R$-module of rank $ m $ and satisfies $ L \otimes_R K = K^m $.
+Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.
+%
+
 $ R^m \subset K^m $ is called the standard lattice.
-% We will abuse notation and denote $L_0(R)$ simply $L_0$ in the hope that the ring $R$ will be understood from the context. 
-The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
-% the set of such lattices 
-this set and $\GL_m(K)/\GL_m(R)$, since $ \GL_m(R) $ is the stabilizer of the standard lattice. 
-%\acom{For example, we will frequently make use of the lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$ given $\lambda\in P$. If $e_1,\dots,e_m$ denote the standard basis elements of 
-% $L_0(\cO)$ then 
-%$\cO^m$ then 
-%$$ 
-%L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
-%$$}
+The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between this set and $\GL_m(K)/\GL_m(R)$, since $ \GL_m(R) $ is the stabilizer of the standard lattice.
 
 We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.
-% TODO: 
-% \acom{Wait, I thought $\CC(t)$ is used in the Ran space version of the BD Gr.}
 Given such a lattice $ L $ and a point $ a \in \CC$, the \new{specialization} of $ L $ at $ a $ is the lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $.
 If $L(a) = \cO_a^m$ then $L$ is said to be \new{trivial at $a$}. 
-% We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
-% \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
 For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$, since $ t-s $ is invertible in $ \cO_a$.
-% \acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}
-
-% \acom{Should we also mention our interest in $\cO$-lattices in $\cK^m$?}
-% \jcom{I don't think that it is necessary.  I just put the part about $ \CC(t)$ to set up the notation for this specialization.}
-
-% \jcom{I wasn't sure of the notation to use here, but I wanted something which didn't conflict with $ L_0$.}
-
-% \acom{I think that MVy use this notation also: }
-
-% \acom{We are using fixed $m$ in the definitions here.}
-% \jcom{Added sentence fixing $m $ above.}
-
-\subsection{Affine Grassmannians} 
-\label{ss:affgrs}
-% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
-% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
-%Set $\AA = \AA^1$ viewed as the subset $\PP\setminus \{\infty\}$ of $\PP$. Let $\Vtriv$ denote the trivial rank $ m $ vector bundle. 
+
+\section{Affine Grassmannians} 
+\label{s:affgrs}
 % 
@@
 
-In these definitions, $ \Vtriv$ denote the trivial rank $ m $ vector bundle.
-
-%\acom{Can we review what exactly is meant by ``terms''? I think that we have (1) a coset space, (2) a moduli space, and (3) a torsor? ``Geometrically'', they are all the same?}
-
-%\jcom{Yes, that is true.
-But what is the problem?
-It is nice to describe spaces in different ways.
-Technically, none of our definitions are ``precise'', since we only describe the $ \CC$-points.
-We should describe each one a functor, if we wanted to be completely precise.
-And then we would have three isomorphic functors.
-But let's not do this.}
-
-% \acom{Oh, I meant could we review for my own benefit.
-But I do think it is also nice, for readability, to use (slightly) different words to describe the different descriptions.
-Hence my suggestions following Def.\ 1.}
-
-% \jcom{I made some changes}
+In these definitions, $ \Vtriv$ denotes the trivial rank $ m $ vector bundle.
 
@@
 It is the moduli space of vector bundles with trivializations,
-%\acom{Can we introduce the first of these restatements as ``As a moduli space it is the set of..''}
 $$
@@
 It is also a moduli space of lattices, 
-% \acom{And this one as ``As a $G$-space..''}
 $$ 
@@
 $$
-% 
 We obtain a lattice from a pair $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.  
@@
 \label{def:grs}
- For any $ s \in \CC $, 
-    the \new{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ \new{at} $ s $. 
+    For any $ s \in \CC $, the \new{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ \new{at} $ s $. 
 \end{definition}  
+% 
 As above, we have modular and lattice descriptions:
+% 
 \begin{gather*}
@@
 \end{gather*}
-% 
-% TODO:
-% consider decorating lattice, modular, group-theoretic descriptions? 
-% paper too short for it, ok. 
-% but it's a little weird how we do 
-% $$ X = A \\ X = Y $$ 
-% Hmm.. maybe it's alright
-% I was going to suggest we do $$ X = A \\ = B $$ instead 
 % 
@@
     \right\}\,.
-    % \CC\xT[t^{-1}]^m 
 \end{gather*}
-% \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?
-Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?} \jcom{That's a good point!
-Maybe we could use some kind of bold  Gr (``thick'' letters) or maybe that would be too confusing.} \acom{Ok, it's tentative.}
 % 
@@
 The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
-% \rcom{why do we have the $s\ne 0$ restriction here} \jcom{it would work when $ s = 0$, but it looks a bit strange there.}
 % 
@@
 $$
-% \acom{What is the modular description of the fibre?} \jcom{That is written above (just fix $ s$).}
-% 
-% \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
-% \jcom{Yes, that is one reason.
-But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).
-For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
-% \acom{lol}
 We also have the lattice descriptions:
@@
 \begin{gather*}
-    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO)\,,\,\, % \\
-    % \text{ and }      
+    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO)\,,\,\, 
     \text{resp.\ } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. 
@@
 In lattice terms, $ \Gr^+$ (resp.\ ${\Grth}^+$) contains those lattices $L$ which are contained in $\cO^m$ (resp.\ $\CC[t]^m$).
-% TODO: can we? 
-% \acom{Maybe we can do without parentheses here.}
-% \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.
-But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.}
-% \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
-% lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.
-% 
+%
+
 \subsection{Relations between different affine Grassmannians}
@@
 
-The following result is the factorization property of the Beilinson--Drinfeld Grassmannian (see \cite[Prop. 3.13]{zhu2016introduction}).
+The following result is the factorization property of the BD Grassmannian (see \cite[Prop. 3.13]{zhu2016introduction}).
 \begin{proposition}
     \label{pr:polyno-taylor}
-    The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
+    The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as 
     \begin{equation*}
-    % \label{eq:grbdgrs}
     \Gr_{0,s} \cong 
@@
     \end{equation*}
+    % 
     In the modular realization, this isomorphism is given by restricting the vector bundle and trivialization.
@@
 
-%\begin{proposition}
- %   \label{pr:grs-gr}
-
 There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$. 
 % 
-    Combining with the \Cref{pr:polyno-taylor}, we obtain an isomorphism
+Combining with \Cref{pr:polyno-taylor}, we obtain an isomorphism
 $$
@@
 $$
-%\end{proposition}
-
-% \begin{enumerate}
-    % TODO: I think it makes more sense to put the first point at the end; it just relates (fibres of) the BD Gr to the ordinary Gr
-    % \item There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
-\begin{comment}
-    \item \label{it:bd-th}
-    %We have a map from the two point Beilinson--Drinfeld affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $.
-    % $$ \Grbd \rightarrow \Grth $$ 
-    We define a map $ \Grbd \rightarrow \Grth $ by 
-    % \acom{Don't we also want to restrict $V$} 
-    % Joel says nope, restriction of vector bundle corresponds to specialization of lattice; here the map is inclusion  
-    $$
-        (V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty})\,.
-    $$
-    % 
-    % It is given in modular terms by restricting the trivialization to $ D_\infty$. \acom{Does it mean $(V,\varphi,s)\mapsto (V\big|_{D_\infty},\varphi\big|_{D_\infty})$}
-    In group-theoretic terms, on the fibre over $ s $, this is the inclusion
-    $$
-        G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,. 
-    $$
-    % \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
-    % \jcom{Permission granted!}
-    % \acom{replaced}
-    % 
-    Finally, it is given in lattice terms on the fibre over $s$ as the identity on the lattice $(L,s)\mapsto L$ and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
-\end{comment}
-\begin{comment}
-    \item \label{it:polyno-taylor}
-    The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
-    \begin{equation*}
-    % \label{eq:grbdgrs}
-    \Gr_{0,s} \cong 
-        \begin{cases} 
-            \Gr \times \Gr_s & s \ne 0 \\
-            \Gr              & s = 0\,.
-        \end{cases}
-    \end{equation*}
-    This isomorphism is given in the modular realization by restricting the vector bundle and trivialization.
-
-    Suppose that $ s \ne 0 $.  In the lattice realization, this is given by forming the specializations 
-    $$
-        L \mapsto (L(0), L(s))\,.
-    $$
-    Note that if $ L = g \CC[t]^m$ for $ g \in G([t,t^{-1}, (t-s)^{-1}])$, then 
-    $$
-        (L(0), L(s)) = (g \cO^m, g\cO^m_s)\,. 
-    $$
-    % 
-    % \jcom{I restated this again.  I think that it is simpler and more clear like this.  And I think that this is the fact that we end up using later.}
-    % 
-    % in the $ s \ne 0 $ case.
-    % \jcom{Maybe we should introduce some notation for this isomorphism.}
-    % \acom{Ok. Question: how is the isomorphism given at $s=0$?}
-    % \acom{Ok.
-TODO.
-Also write this in group theoretic terms.
-Probably $[g] \mapsto ([g],[g])$ is ok.
-Since $g\CC[t]\otimes_{\CC[t]}\cO_s \cong g\cO_s $ for some reason, where $g\in\CC[t,t^{-1},(t-s)^{-1}]$ can be viewed as $g\in\cK_s$.}
-    % 
-    %    Finally, in group-theoretic terms, it is given (on representatives) by $g\mapsto (g,g)$.
-\acom{Reinstated the map.
-Choosing to supress the coset in our notation makes it potentially ambiguous.
-Maybe we can say inclusion $\times$ inclusion?
-In any case we should say something.
-Else, what are we referring to when we say ``This is compatible'' in the next line?}
-    %    This is compatible with the lattice description since for $ g \in G(\CC[t, t^{-1}, (t-s)^{-1}]) $, we have
-    %    $$
-    %    \left( g \CC[t]^m \right) \otimes_{\CC[t]} \cO \cong g \cO^m
-    %    $$
-    %    and similarly for $ L(s)$.
-    % 
-    In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
-\end{comment}
-\begin{comment}
-    \item \label{it:grs-gr} There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$.
-
-    Combining with the above point, we obtain an isomorphism
-    $$
-    \tau_s : \Gr_{0,s} \rightarrow \Gr \times \Gr 
-    $$
-    % 
-    %    \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
-\end{comment}
-% \end{enumerate}
-
-% \jcom{I moved the ``composition'' of 2 and 3 into 3 and named it $ \tau_s$, since we will use it later quite a bit.
-I'm not that happy with the layout of this section, so feel free to reorganize it (maybe into Propositions?)}
-
-% \acom{Begun. Not sure if it is what you had in mind.}
-% \jcom{I reorganized a bit.  This last point is not really much of a result, so removed the ``proposition'' label.}
-% \acom{Ok}
+%
 
@@
 \label{ss:fuscon}
-% \jcom{We should probably be consistent with $ \AA$ vs $\CC$.  I'm happy with either.}
-% \acom{Do you mean that if we go with $\AA$ we should change $\AA^\times$ as well?
-Also, would you agree that the distinction is the topology?
-So $\AA$ is better if we were using ``generic'' to describe $s\ne 0$, which we are not.}
-% \jcom{Yes, either we should write $ \AA, \AA^\times $ or $ \CC, \AA^\times$.  There is no distinction.  Always in this paper, we work with the Zariski topology whether we write $ \AA $ or $ \CC$.}
-% \acom{Ok, let's be fancy and write $\AA$.
-(So if someone writes $s\to 0$ you don't think of it as $s$ approaches $0$ in the metric topology, but really as the limit of ideals $(s)\supset (s^2)\supset \cdots$ which, I hope, is the zero ideal?) Tentatively remapped our command for $\mathbb C$ to give $\AA$.
-It looks really funny to use it as notation for a field/conflate field and scheme---is there really no distinction?
-Surely $\AA = \spec \AA[t]$ is not great practice?}
-% \jcom{I think that it would be more typical to use $ \CC $ for the field and use $ \AA$ for the affine line.  I changed $ \CC $ back to $\CC$.}
 
@@
 Let $ \Gr_{0, \AA^\times} $ denote the preimage of $\Ax = \AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.
-% 
-%Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (\cref{it:polyno-taylor,it:grs-gr} of \cref{ss:relsbtwgrs} preceding), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
-% TODO: cf https://tex.stackexchange.com/questions/256849/cleveref-change-behaviour-of-cref-to-use-the-abbreviated-form
-% 
+
 The isomorphisms $ \theta_s $ defined above glue together to a projection map
@@
 \end{equation}
-(This $\theta$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \AA^\times$ instead of the complement of the diagonal in $ \AA^2 $.)
-%  TODO: outstanding
-% \acom{Question for Joel: What is the benefit of working with diagonals? Letting two points vary? What is an example of a structure that you can't see letting just one point vary as we do.}
+(This $\theta$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \AA^\times$ instead of the complement of the diagonal in $ \AA\times\AA $.)
 
@@
 $$
-%called the \new{open family} of $X_1$ and $X_2$. 
-% 
-% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
-% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
 Given a point $ s \in \Ax$, we write $ X_1 \bdfamf X_2  $ for the fibre of $ X_1 \bdfamo X_2 $ over $s$.
@@
 
-% TODO: outstanding 
-% \acom{Well you might not want but I think it would be good to tell the reader why we use the notation $\AA^\times$ for $\AA\setminus 0$ in $\AA$ or why we use the notation $\AA$ at all..
-E.g.\ do we know what happens for $\GL_m(k)$ over some other base field $k$.}
-
 We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  X_1 \bdfamo X_2 $ in $ \Grbd $. By construction, this is a flat family over $ \AA$.
@@
 We call this subscheme the (geometric) \new{fusion} of $ X_1 $ and $ X_2$.
-
-% \jcom{I rewrote this to introduce the $ X_1 \ast_s X_2 $ notation that we need for later.
-In doing so, $ X_1 \circ X_2 $ became obsolete, since we now have $ X_1 \ast_0 X_2$, but if you like we could just define $X_1 \circ X_2 = X_1 \ast_0 X_2 $.}
-% 
-% Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
-% $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
-% \begin{equation*}
-    % \label{deservesdisplay}
-%    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
-% \end{equation*}
-% which we call the \new{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  
-% 
-% By construction, 
-% \acom{technically, there were two given above, so *these* constructions?} 
-% $X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.
-
-% \acom{Ah, sorry --- so do we introduce a even more general notion of $\ast_\AA$ for arbitrary flat families?
-Looking at Eisenbud's geoemtry of schemes (where flat iff tor-free actually shows up as Exercise II-33!) there does not seem to be anything quite like $\ast_\AA$ or $\circ$ defined.}
-
-% \jcom{I'm not sure how a general notion would be defined.  In our case, we are using the special fact that the general fibre is a product.}
-
-% \acom{I mean exactly in the case of this special fact, which is not special to the BD Gr.}
-
-% Cf. https://math.stackexchange.com/questions/1681680/flat-family-limit-of-intersection-vs-intersection-of-limits
-% 
-% 
-% Begin OLD
-%\acom{Question abt general fact: why is scheme-theoretic closure of product flat?} \jcom{See Hartshorne Proposition III.9.8.
-I just taught this on the last day of my algebraic geometry class!} \acom{Cool!
-That Proposition is a bit more general too..}
-% 
-% \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
-% \jcom{Now answered above.}
-% 
-%\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper and it is the most convenient way to define $\Gr^{\lambda_1, \lambda_2}$.
-I don't know what notation we should use.}
-% 
-%\acom{Roger and I have been using $\ast$ to denote fusion.
-Do we need a notation for the scheme-theoretic closure of $X_1\times X_2\times\AA^\times$?
-If not then I like $X_1\ast X_2 = \overline{X_1 \times X_2 \times \AA^\times}\cap \pi^{-1}(0)$.}
-%\jcom{I think that we will need notations for both things, but I'm happy to use $ \ast$ for the central fibre and use something else for the whole family.} \acom{Ok, I have changed it to notation from Roger's thesis/AK.
-Only now I am confused as to what is being called fusion---why do we not take the top dimensional subscheme?}
-%\jcom{I guess that there are two things that one could mean by fusion of MV cycles.
-This scheme $ X_1 \circ X_2$ or the expression which appear in Theorem 7.11 of mvbasis, which is a linear combination of the top-dimensional components of this scheme with multiplicites.
-In the general context of this section ($X_1, X_2$ are not necessarily MV cycles), then I guess it is best to talk about the subscheme.
-Maybe we can call the expression appearing Theorem 7.11 the ``numerical fusion'' of MV cycles.
-By the way, somewhere in this paper we should explain Theorem 7.11 and say that this gives us motivation to study fusion of MV cycles.}
-%\acom{Sure! It is quoted at the end, in \Cref{s:denouement} as an application. Addendum: for the numerical fusion I suggest simply $[Z_1][Z_2]$. This is what I will use in my talk. }
-% END OLD
-% 
-\subsection{Some subvarieties of affine Grassmannians}
+%
+
+\subsection{Some subschemes of affine Grassmannians}
 \label{ss:subgrs}
@@
 %
-% Coweights define elements in the various affine Grassmannians which we consider.
-Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent.
-% the right cosets which they represent are clear from the context.
-
-% We consider the following subschemes of the affine Grassmannians.
+
 Using $\lambda,\lambda',\lambda''$ and $\mu,\mu',\mu''$ we define the subschemes of $\Gr$, $\Grth$, and $\Grbd$ which will be considered, give some properties, and say how they are related.  
@@
 \end{definition}
-    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
 % 
@@
     The \new{family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \bdfamc \overline{\Gr}^{\lambda''} $.
-    % $$ 
-    %     \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.
-    % $$
 \end{definition}
-% \jcom{It used to say ``fusion'' of two spherical Schubert varieties, but we are using the word fusion just for the central fibre, so we need a different name.} 
-% \acom{Family is good. We should put BD on p. 4.}
-% \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
-%\acom{should we also subsript this family with $0,\AA$?}
-%By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ of $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA}$ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.
-% By \cite[Proposition 3.1.14]{zhu2016introduction},
-% Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
-% the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
-By a theorem of Zhu, $ \overline{\Gr}^{\lambda'} \geofu \overline{\Gr}^{\lambda''} $ is reduced and equal to $ \overline{\Gr}^{\lambda}$ \cite[Proposition 3.1.14]{zhu2016introduction}.
-% Suppose that $ s \ne 0$.  
-If $s\ne0$, then the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ contains the open locus $ \Gr_{0,s}^{\lambda', \lambda''} =  \Gr^{\lambda'} \bdfamf \Gr^{\lambda''} $ a $ G(\CC[t])$-orbit
-% .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
-whose lattice description is given in \Cref{le:Grl1l2} below.
-% \acom{Why $G(\CC[t])$. Because we are on the left side!}
-% \acom{Sorry I keep changing (abbreviating) ``By a theorem of Zhu'', but is the citation not sufficient?}
-% \jcom{I like to say a person's name when I cite their work!}
-% \acom{Ok}
-% 
-Because we consider effective dominant coweights, the spherical Schubert varieties and their fusions lie in the positive part of the (thick) affine Grassmannian.
+% 
+By a theorem of Zhu, $ \overline{\Gr}^{\lambda'} \geofu \overline{\Gr}^{\lambda''} $ is reduced and equal to $ \overline{\Gr}^{\lambda}$ (\cite[Proposition 3.1.14]{zhu2016introduction}).
+If $s\ne0$, then the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ contains the open locus $ \Gr_{0,s}^{\lambda', \lambda''} =  \Gr^{\lambda'} \bdfamf \Gr^{\lambda''} $ a $ G(\CC[t])$-orbit whose lattice description is given in \Cref{le:Grl1l2} below.
+% 
+Because we consider effective dominant $\lambda',\lambda''$, the spherical Schubert varieties and their fusions lie in the positive part of the thick affine Grassmannian.
 % 
@@
 \end{proof}
-% TODO: yes the answer is yes, note to self
-% \acom{Does $M_m(\CC[t])\cap G\xT[t^{-1}] = \{g\in M(\CC[t]):\det g\in\CC[t]\setminus0\}$?}
-
-% \acom{why ``and so''? bc orbits are connected?}
-% \jcom{I turned this into a Lemma.}
-
-%As above, since $ \lambda', \lambda'' $ are effective, the map $ \acom{What is ``as above''? Also, we have only described the open loci in fibres over $s\ne0$.}
-
-% Now fix two effective (possibly non-dominant) coweights $ \mu', \mu''$ of sizes $N',N''$ such that $ \mu = \mu' + \mu'' $ is dominant. 
-% (We do not require $ \mu', \mu'' $ to be dominant.) 
-% Using $ \mu, \mu', \mu''$, we define the following subschemes.
-
+% 
 \begin{definition}
@@
 % 
-
-\acom{Comment why the above doesn't make sense for $\mu$ not dominant?}
-\jcom{It does make sense when $ \mu $ is not dominant.
-The reason for restricting to dominant $ \mu $ is so that $ S^\mu \subset \cW^\mu$.
-I agree that we should mention this, but I'm not sure where.} \acom{Yes, sorry.
-We could say it here?}
-% 
-% \acom{First lattice description that doesn't come for free?}
-% 
-% \acom{que est-ce?} \jcom{It's not very relevant for this paper.
-Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.
-We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.
-Maybe ``preserves'' is not the best word above.}
-% A: Ok thanks!
-% 
 \begin{definition} 
 \label{def:inftyorbit}
-    The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $
+    The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $.
 \end{definition}
-% \acom{and its closure?}
-% \jcom{I don't think that we use the closure in this paper, do we?}
-% \acom{No you are right we do not.}
+% 
 \begin{definition} 
 \label{def:inftyorbitfam}
-    The \new{family of two semi-infinite orbits} 
- $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
- which we define to have fibres $ S^{\mu', \mu''}_{0,s} := \theta_s^{-1}( S^{\mu'}\times S^{\mu''}) $ for $ s \ne 0$ and fibre $ \theta_0^{-1}(S^{\mu})$ over $ s = 0 $.
+    The \new{family of two semi-infinite orbits} $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$ which we define to have fibres $ S^{\mu', \mu''}_{0,s} := \theta_s^{-1}( S^{\mu'}\times S^{\mu''}) $ for $ s \ne 0$ and fibre $ \theta_0^{-1}(S^{\mu})$ over $ s = 0 $.
 \end{definition}
-%Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.
-% 
-%\acom{Commented out fusion part for now.
-Unsure about defining it as the family whose 0 fibre is $S^{\mu' + \mu''}$ and whose generic fibre is $S^{\mu'}\times S^{\mu''}$ up to $\tau$.
-Baumann--Riche consider the attracting set of $C_\mu = \sqcup_{\mu' + \mu'' = \mu } m(\tilde C_{\mu',\mu''})$ where $\tilde C_{\mu',\mu''}$ is a connected component of fixed points in $\Grbd\tilde\times\Grbd$.
-Maybe we can consider the attracting set of just one of these?}
 % 
@@
     S^{\mu', \mu''}_{0,s} = 
-    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
+    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. 
 $$
@@
 
-In \cite[Prop~2.6]{kamnitzer2014yangians}, we observed that $ S^\mu \subset \cW^\mu$ (this uses that $\mu$ dominant, which is the reason why we make this assumption).
+In \cite[Prop~2.6]{kamnitzer2014yangians}, we observed that $ S^\mu \subset \cW_\mu$ (this uses that $\mu$ dominant, which is the reason why we make this assumption).
 More generally, we have the following result.
 
-\jcom{Following Anne's comment above about dominant $ \mu$, I decided to move this result here.}
-
 \begin{lemma}
-\label{le:inftyfusiskl} % as in lands in KL slice 
-    Under the map $ \Grbd \rightarrow \Grth$ the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
+\label{le:inftyfusiskl} 
+    Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
 \end{lemma}
-%\acom{Probably it is worth writing down the map $ \Grbd \rightarrow \Grth$ just before this first occurence? \textit{is it $(L,s)\mapsto L$?} Update: added this above.}
-% Resolved?
-the map $ \Grbd \rightarrow \Grth$ caused some confusion in my talk as on the left we have a family and on the right we have the thick affine Grassmannian --- Jiuzu kept thinking aloud that we can make $\Grth$ a family too..
-Anyway I think that you address this below Joel.
-
+% 
 \begin{proof}
-    Let $ L $ 
-    % lie in this image.  
-    be a lattice in the image of $S^{\mu',\mu''}_{0,\AA}$.
-Then $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $.
-Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.
-Note that $ h \in T_1(\Oinf)$.
+    Let $ L \in\Grth$ be a lattice in the image of $S^{\mu',\mu''}_{0,\AA}$. So we can write $ L = g t^{\mu'} (t-s)^{\mu''}\CC[t]^m$ for some $ g \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $.
+
+    Let $ h =(t-s)^{\mu''} t^{-\mu''}  $.  Note that $ h \in T_1(\Oinf)$. 
     Moreover, $L = h (h^{-1} g h) t^{\mu}\CC[t]^m$. 
-    % $$ L = h (h^{-1} g h) t^{\mu}\CC[t]^m\,. $$
-    Since 
-    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
-    $h^{-1} g h \in N_-(\cK_\infty)$ we can factor $ h^{-1} g h$ as $n_1 n_2$ for some $ n_1 \in {(N_-)}_1(\Oinf), n_2 \in {N_-}(\CC[t]) $.
-
-    As $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t]) $, and so 
-     % \CC\xt[t^{-1}]s
-    % 
-    % \rcom{I think we want $\mu$ antidominant here or should the $N$'s be $N_-$'s?} % 
-    % \acom{Si.}
-    % 
-    $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. % \CC\xt[t^{-1}]
+    Since $h^{-1} g h \in N_-(\cK_\infty)$ we can factor $ h^{-1} g h$ as $n_1 n_2$ for some $ n_1 \in {(N_-)}_1(\Oinf)$ and $n_2 \in {N_-}(\CC[t]) $.
+
+    As $ \mu $ is dominant, we see that $ t^{-\mu} n_2 t^\mu \in N_-(\CC[t]) $, and so $ L = h n_1 t^\mu \CC[t]^m$.  Since $ hn_1 \in G_1(\Oinf)$, the result follows. 
 \end{proof}
-
-% TODO: resolve
-% \jcom{Maybe we should introduce the $ L_{\mu', \mu''} $ notation, but I'm not sure it is necessary.}
-%On the other hand, if $ s = 0$, then the fibre $S^{\mu', \mu''}_{0,0} $ equals $ S^{\mu' + \mu''}$. 
-% TODO: resolve
-% \acom{changed $\mu$ to $\mu' + \mu''$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda', \lambda''} $}
 %
@@
 % 
+We now consider some subvarieties of the space of $ N\times N$ matrices, again using the coweights $ \lambda, \lambda', \lambda'', \mu, \mu', \mu''$ fixed in the previous section.
+
 \subsection{Adjoint orbits and their deformations}
@@
 % 
-We now consider some subvarieties of the space of $ N\times N$ matrices, again using the coweights $ \lambda, \lambda', \lambda'', \mu, \mu', \mu''$ fixed in the previous section. 
-Recall that $\lambda, \mu $ are partitions of $ N$.
-
+Recall that $\lambda=(\lambda_1,\dots,\lambda_m)$ is a partition of $ N$.
+% 
 Given a point $ s \in \AA$ we write $ J_{s,\lambda}$ for the Jordan form matrix with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
@@
 % 
-% Temporarily commenting out, don't use
-% Its closure is $ \overline{\OO}^\lambda = \bigcup_{\gamma \le \lambda} \OO^{\gamma}$.
-% 
 \begin{definition}
 \label{def:Olamlam}
-    For $ s \in \CC, s \ne 0$, the (adjoint) orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
+    For $ s \in \Ax$, the (adjoint) orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
     These matrices and the linear operators they represent will be said to have Jordan type $((0,\lambda'), (s,\lambda''))$.
@@
 %
-
-%A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda'), (s,\lambda''))$ if its matrix representatives lie in $ \OO^{\lambda', \lambda''}_{0,s}$.
-% \acom{secret definition; add `a matrix is likewise said to have Jordan type...if it lies in'?}
-% \jcom{Is that better?}
-% \acom{Yay.}
-%
-
-% The closure $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ is $\bigcup_{\gamma' \le \lambda', \gamma'' \le \lambda''} \OO^{\gamma', \gamma''}_{0,s}$.     
-% \jcom{Do we need this?}
 
@@
 
-Let $ r $ be a decreasing, concave, non-negative function of $\NN$ with $r(0) = N$ called a \new{rank function}.  Let $k $ be maximal such that $ r(k) \ne 0 $.
-% \jcom{I don't know if it is really necessary to introduce this $ k$.
-Later it will be the number of columns of $ \lambda$, but we could just regard $ \lambda$ to have some columns of size 0.} \acom{And make it $N$?
-Was $k = m$ replaced because $m$ is already used?} \jcom{Yes and yes} \acom{I like the idea of making it $N$}
+Let $ r $ be a decreasing, concave, non-negative function of $\NN$ with $r(0) = N$, called a \new{rank function}.  Let $k $ be maximal such that $ r(k) \ne 0 $.
 % 
@@
 We will now describe these fibres.
-% departing slightly from the notation of \cite{eisenbud1989rank}.
 
 Let $ z \in \AA^k$ be a point.
-Some of the coordinates of $z$ may be equal so we introduce the following data to keep track of these equalities.
+Some of the coordinates of $z$ may be equal, so we introduce the following data to keep track of these equalities.
 Let $ \ell$ denote the number of distinct coordinates of $ z $.
-There exist a sequence of integers $k = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, and $ s \in\AA^\ell$, such that $s_a\ne s_b$ for any $a\ne b$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
+There exist a sequence of integers $k = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, a point $ s \in\AA^\ell$, such that $s_a\ne s_b$ for any $a\ne b$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
 $$ 
@@
 %
-%\jcom{Eisenbud--Saltman don't introduce this $ s_j$ notation, but I find it helpful.}
-% 
-%\acom{Agreed. Maybe we mention that the point of $p$ is to group the repeated eigenvalues? It wouldn't be the most obvious thing we point out.}
-%\jcom{That is what I was trying to say with ``introduce some data \dots''  Maybe it could be more clear.  I also clarified the uniqueness.}
-%\acom{Oh, sorry, I see it. Maybe because it was the start of a new paragraph I didn't connect `data' and `ranks' at first glance.}
-
-Next for $ a = 1, \dots \ell $ and $ c = 1, \dots, k_{j+1} - k_j$, we define
-$$
-    % r_{z,j}(i):= N - r(p(m_j)) + r(p(m_j + i)) 
+
+Next for $ a = 1, \dots, \ell $ and $ c = 1, \dots, k_{j+1} - k_j$, we define
+$$
     r_{z,a}(c):= N + \sum_{d = 1}^c r(p(k_a + d)) - r(p(k_a + d) - 1)  \, . 
 $$
-% \jcom{This is the same as what ES denote $r(i,j)$ except the roles of $ i, j$ swapped.  We could swap them back.}
-% \acom{I don't think that there is any need to swap back.
-But maybe we could use $c$ (for column) isntead of $i$, since we use $i$ in the same context quite a bit to denote a letter in the alphabet $\{1,\dots,m\}$.}
-% \jcom{Sure, that is a good idea.}
-% \acom{Ok, switched some letters. Think $d$ is good as `delta'.}
-%\jcom{I fixed it now.  I didn't want to use ES's $a_i$.} 
-%\acom{\emoji{+1}}
-
-% 
 By \cite[Corollary 2.2]{eisenbud1989rank}, the fibre of the flat family $ X_{r,W} $ over $ z$ is given by
@@
 % 
-%\begin{lemma}
-%    \label{lem:es}
-%    Let $\lambda = \lambda' + \lambda''$ be partitions.
-There exists a permutation of the columns of $\lambda$ such that the first $\lambda'_1$ columns are precisely the columns of $\lambda'$ and the last $\lambda''_1$ columns are precisely the columns of $\lambda''$.
-%\end{lemma}
-%Recall that $\lambda' + \lambda'' = \lambda$ is a partition of $N$. 
-% 
 For $ c\in \NN$, let
@@
 It is easy to see that this is a rank function, with $ k = \lambda_1$, the number of columns of $ \lambda$.
-%\begin{lemma}
-%   The function $r$
-%    defined by $r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$ 
-%is a rank function. 
-%\end{lemma}
 
@@
 \begin{cases}
-    z(a)_{p(c)} = 0 &  c = 1, \dots, k_1 \\
-    z(a)_{p(c)} = s &  c = k_1 + 1, \dots, k\,.
+    z(s)_{p(c)} = 0 &  c = 1, \dots, k_1 \\
+    z(s)_{p(c)} = s &  c = k_1 + 1, \dots, k\,.
 \end{cases}    
 \]
-% $ z(s)_{p(j)} = 0 $ for $ j = 1, \dots, k_1 $ and $ z(s)_{p(j)} = s $ for $ j = k_1 + 1, \dots, k$.
-
-For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of 
-\(\ell =2\), \(k = (0,\lambda_1')\), \(s_1 = 0, s_2 = s\) and the permutation $p$.
-% $ \ell = 2$, $k_1$, $s_1 = 0$, $s_2 = s$, and the permutation $p $.
+
+For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of \(\ell = 2\), \(k = (0,\lambda_1')\), \(s_1 = 0, s_2 = s\) and the permutation $p$.
 We also see that
@@
 On the other hand, for $z(0)$, we get that $ \ell = 1$ and that 
-% \acom{This was $r = 1$ but I think it should be $\ell = 1$.} \jcom{Yes, you are correct.}
 \begin{equation} 
@@
 \end{equation}
-%\jcom{Someone should check that I chose the notation correctly to make this work out.}
-% 
-%\acom{What do we mean by equalities in $z(s)$ reproduce $p$?
-I thought $z(s)$ was defined by $p$.
-Also, $r_{z(s),1}(i) = N- r(p(k_1)) + r(p(k_1 + i)) = N - (N-\#\text{boxes in first }p(k_1)\text{ cols} + \cdots)\ne $~\Cref{eq:rcols}.
-We want to apply $p$ to $\{1,\dots,i\}$ and not just $i$.
-I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$.
-For a minute I thought it was actually fine, but what we have is: $r_{z(s),j}(i) = N - (\#\text{boxes in cols }1,\dots,p(k_j + i) - \#\text{boxes in cols }1,\dots,p(k_j))$ and what we want is $\dots (\#\text{boxes in cols }p(1),\dots,p(k_j + i) - \#\text{boxes in cols }p(1),\dots,p(k_j + i))$ right?}
-% 
-%\jcom{I fixed the definition of $ r_{z,j}(i)$, so now it is correct, I believe.
-I changed the wording of ``reproduce''.
-I'm trying to say that $ p$ is used to define $ z(s)$ and the we get $ p $ back from $ z(s)$ as the permutation coming from the equalities.}
-%\acom{\emoji{+1}}
-% 
-Let $ W = \{ z(s) : s \in \CC \}$. Combining \Cref{eq:ranks,eq:ESfibre,eq:rcols,eq:rcol2},
-% (\ref{eq:ranks}), (\ref{eq:ESfibre}), (\ref{eq:rcols}), (\ref{eq:rcols2}) 
-we see that the Eisenbud--Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
+% 
+Let $ W = \{ z(s) : s \in \CC \}$.
+Combining \Cref{eq:ranks,eq:ESfibre,eq:rcols,eq:rcol2}, we see that the Eisenbud--Saltman family $ X_{r, W} \rightarrow W $ gives our family $ \overline{\OO}^{\lambda', \lambda''}_{0, \AA}$.
 \end{proof}
-% 
-% 
-% The family of adjoint orbits $  whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda', \lambda''}_{0,s}$ and whose \acom{Claim:} fibre over 0 is $\overline{\OO}^\lambda$ (a consequence of Eisenbud and Salten's characterization of ``rank varieties'' as proved in \Cref{cor:es}).
-\acom{TODO: make into definition to be x-referenced in proof of description of fibres}
-% 
-% \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
-%\acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
-%in $\AA_s\times \AA_{\det}$? 
-%so the set of $A$ which are conjugate to
-%$J_{0,\lambda'} \oplus J_{s,\lambda''}$
-%by a matrix whose determinant is divisible by $s$ is also closed?}
-%\jcom{I didn't follow your argument.
-One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda', \lambda''}_{0,s} $ and then set $ s =0$.
-For example, take $ \lambda' = (1) = \lambda'' $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.
-I am hoping that we can find a reference for this result somewhere.}
-%\acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda'}\oplus J_{s,\lambda''}$ limit to matrices which are conjugate to $J_\lambda$.
-In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}
-% 
-% TODO: delete commented out remark and subcomment!
-% \begin{remark}
-\begin{comment}
-Base case $m = 1$: by a slight abuse of notation let $\lambda', \lambda_2 \in \NN$. Claim: $J=J_{0,\lambda'} \oplus J_{s,\lambda_2}$ is conjugate to
-
-% $\begin{pNiceArray}{CC|CC}[first-row,last-row=5,first-col,last-col,nullify-dots]
-% & C_1 & \Cdots & & C_4 & \\
-% L_1 & a_{11} & a_{12} & a_{13} & a_{14} & L_1 \\
-% \Vdots & a_{21} & a_{22} & a_{23} & a_{24} & \Vdots \\
-% \hline
-% & a_{31} & a_{32} & a_{33} & a_{34} & \\
-% L_4 & a_{41} & a_{42} & a_{43} & a_{44} & L_4 \\
-% & C_1 & \Cdots & & C_4 &
-% \end{pNiceArray}$
-\[
-A = \begin{bNiceArray}{ccc|ccc}[columns-width = auto,first-row,last-col,code-for-first-row = \color{blue}\scriptstyle\rotate,code-for-last-col = \color{blue}\scriptstyle,nullify-dots,xdots/line-style=loosely dotted]
-1 & \Cdots & \lambda_1 & \lambda_1 + 1 & \Cdots & \lambda_1 + \lambda_2 \\
-0 & 1 & 0 & 0 & 0 & 0 & 1\\
-0 & \Ddots & 1 & 0 & 0 & 0 & \Vdots \\
-0 & 0 & 0 & 1 & 0 & 0 & \lambda_1 \\
-\hline
-    & & & s & 1 & 0 & \lambda_1 + 1 \\
-    & & & 0 & \Ddots & 1 & \Vdots \\
-    & & & 0 & 0 & s & \lambda_1 + \lambda_2 
-\end{bNiceArray} 
-\]
-\end{comment}
-% Denote by $R_i$ the $i$th row of $J$ 
-%Let $g = E_{\lambda_2}\cdots E_1$ be the product of elementary matrices $E_i$ which correspond to the elementary row operations 
-%$$R_{\lambda_1 + i - 1} \leftarrow R_{\lambda_1 + i-1} + \frac 1s R_{\lambda_1 + i}$$ 
-%for $i = 1,\dots,\lambda_2$. Then $gJg^{-1} = A$. For the next part we introduce the notation $A_{\lambda_1+\lambda_2}$ for this matrix $A$. 
-% 
-%Now let $\lambda_1,\lambda_2$ be arbitrary. Clearly $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to 
-%$$\bigoplus_{i=1}^m (J_{\lambda_{1,i}}\oplus J_{\lambda_{2,i}})\,.$$ 
-%Moreover each block $J_{\lambda_{1,i}}\oplus J_{\lambda_{2,i}}$ is conjugate to $A_{\lambda_{1,i}+\lambda_{2,i}}$.
-Altogether $J_{0,\lambda_1} \oplus J_{0,\lambda_2}$ is conjugate to $\bigoplus_{i = 1}^m A_{\lambda_{1,i}+\lambda_{2,i}}$ and this latter matrix specializes to the Jordan normal form $J_{0,\lambda_1 + \lambda_2}$ at $s=0$.
-% 
-% By Tanisaki $A\in \OO^\lambda$ iff the coefficients of $z^m$ in $k\times k$ minors of $zI - A$ for any $m\le p_\lambda(k) - 1$ and for any $k = 1\dots |\lambda|$ vanish.
-Here $p_\lambda(k) = \lambda_{n-k+1} + \cdots + b_n$ and $k = 1,\dots,n$.
-So $p_\lambda(k) = \#$ boxes in the last $k$ rows of $\lambda$.
-% 
-% In particular this result describes the ideal $I_i$ of $N_i\times N_i$ matrices $A_i$ such that $A_i - \delta_{i,2}s$ is conjugate to $J_{\delta_{i,2} s, \lambda_i}$ for $i = 1,2$.
-Let $A_1,A_2$ be such a pair of matrices.
-Clearly $A_1 \oplus A_2$ is conjugate to $J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.
-Let $g$ be such that $g(J_{0,\lambda_1} \oplus J_{s,\lambda_2})g^{-1} = \bigoplus_{i = 1}^m A_{\lambda_{1,i}+\lambda_{2,i}}$.
-% 
-% If we apply the change of basis $g$ to the ideal $I=I_1 + I_2$ and set $s = 0$ (if possible) do we recover the ideal of $\OO^{\lambda_1 + \lambda_2}$? Let $A^g = g(A_1 \oplus A_2) g^{-1}$...
-% \end{remark}
 % 
@@
 % 
-% Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. 
-% \acom{I don't suppose we need this basis now that we're just describing $\TT_\mu$ in words.}
-% 
-% \begin{definition}
-Recall that $\mu=(\mu_1,\dots,\mu_m)$ is a partition of $N$. The \new{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is the affine space of $N\times N$ matrices of the form
-% defined as the set of $A\in M_N(\CC)$ such that 
-% \[
-%     \begin{aligned}
-%         &\text{for all } 1 \le a,s\le m\,,
-%         \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
-%         &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
-%         &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
-%     \end{aligned}    
-% \]
-% \end{definition}
-% \jcom{I'm not a huge fan of this description, but I don't know how to write it better.}
-% 
-% \acom{Agree. Happy to just have the in-words description.}
-% 
-% In words, $A$ 
-% a $\mu$ Jordan form matrix plus 
-$A = J_{0,\mu} + X$ where $X$ is a $\mu\times\mu$ block matrix with possibly nonzero entries $A_{ij}^1,\dots,A_{ij}^{\min(\mu_i,\mu_j)}$ in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
-% $\dim \TT_\mu = N^2 - \dim \OO_\mu$.
-
-By example, if 
-% $\mu=(3,2,2,1)$, 
-$\mu = (3,2)$ then $A\in\TT_\mu$ looks like 
+Recall that $\mu=(\mu_1,\dots,\mu_m)$ is a partition of $N$.
+The \new{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is the affine space of $N\times N$ matrices of the form $A = J_{0,\mu} + X$ where $X$ is a $\mu\times\mu$ block matrix with possibly nonzero entries $A_{ij}^1,\dots,A_{ij}^{\min(\mu_i,\mu_j)}$ in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block.
+
+By example, if $\mu = (3,2)$ then $A\in\TT_\mu$ looks like 
 \[
@@
         \end{BMAT}\right] 
-    % TODO: REDO 
-    % \left[
-    %     \begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
-    %         & 1 & & & & & \\
-    %         &  & 1 & & & & \\
-    %     A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
-    %         &  & &  & 1 & & \\
-    %         A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
-    %         A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
-    %         A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
-    % \end{BMAT}
-    % \right] % \,. 
 \]
 for some $A_{ij}^k\in\CC$.
-% \[
-%     \left[\begin{BMAT}(e){c;cc;cc;ccc}{c;cc;cc;ccc} 
-%         0 & A_0 & A_1 & A_2 & A_3 & A_4 & A_5 & A_6\\
-%         0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
-%         0 & 0 & 0 & A_7 & A_8 & A_9 & A_{10} & A_{11}\\
-%         0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
-%         0 & 0 & 0 & 0 & 0 & A_{12} & A_{13} & A_{14}\\
-%         0 & 0 & 0 & 0 & 0 & 0 & 1 & 0\\
-%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
-%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
-%         \end{BMAT}\right]
-% \]
-%
-
-To $ A \in \TT_\mu$ we will associate the $m\times m$ matrix of polynomials 
-% $ g(A) = \left( g(A)_{ij} \right)$ 
-$g(A)$ in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
+
+To $ A \in \TT_\mu$ we will associate the $m\times m$ matrix of polynomials $g(A)$ in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
 \begin{equation}
@@
     g(A)_{ij} = 
-\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j\,, \\
-    % A^k_{ji} t^{k-1} & i = j \\
-        % \text{ if $ i = j$} \\
-        - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j\,. 
-    %  \text{ if $ i \ne j$ }
+        \begin{cases} 
+            t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j     \,, \\
+            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}           & i \ne j   \,. 
         \end{cases}
 \end{equation}
-% $A^k_{ji}$ denotes the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
-%
 
@@
 \[
-    % A = \left[
-    %     \begin{BMAT}(e){ccc;cc}{ccc;cc} 
-    %     0 & 1 & 0 & 0 & 0\\
-    %     0 & 0 & 1 & 0 & 0\\
-    %     A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
-    %     0 & 0 & 0 & 0 & 1\\
-    %     A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
-    %     \end{BMAT}\right]    
-    % \Longrightarrow 
     g(A) = 
-        \left[\begin{array}{rr}
+    \begin{bmatrix}
         t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1    & -A_{21}^2t - A_{21}^1         \\
         -A_{12}^2 t - A_{12}^1                          & t^{2} - A_{22}^2 t - A_{22}^1
-        \end{array}
-        \right]\,. 
-    % TODO: REDO
-\]
-% For example, the $A$ above will define 
-% \acom{the transpose of! TODO. Had script?}
-% \[
-% \begin{bmatrix}
-%     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
-%     & t^2 \\
-%     & & t \\
-%     & & & t 
-% \end{bmatrix}    
-% \]
-% 
-% \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
-% \acom{Ok.}
-%
+    \end{bmatrix}\,. 
+\]
 
@@
     \right] \,.   
-% TODO: REDO
 \]
@@
 
-%\acom{Mention that any other decomposition $\nu' + \nu''$ of $\mu' + \mu''$ will give a slice $\UU^{\nu',\nu''}_{0,\AA}$ with the same zero fibre.}
-
-% \acom{These $\UU$'s should also have attr descriptions. What are they?}
-% \jcom{I don't think that it is very interesting. Just take a diagonal matrix, constant on each block.  Then $\UU$ will be the attracting set of the block diagonal matrix for this action.}
-% A: Ok
-
-% \jcom{Instead of $\TT^+$ maybe a different letter would be best?
-I'm moved all $\lambda, \mu$ to upper indices for consistency (except for $ \cW_\mu, \TT_\mu$) and also to let us put $ s $ or $ \AA$ in the lower index.
-I haven't been very consistent about $ \AA $ vs $ \CC$.
-Which do you prefer?}
-% 
-% \acom{Maybe $\UU$ for a different letter?
-And, I guess we do not need $\AA$ but it is a nice letter to have around.
-It also serves to distinguish the $\CC$ over which $R,K$ are defined from the $\AA$ over which $\Grbd$ is defined?}
-% \jcom{Sure $\UU$ is good.}
-% \acom{And, sorry, ignore my other comment; it's the same $\CC$ (or $\AA$) nothing to distinguish.}
-% 
-% TODO: place this better? 
-% \acom{The following is a rough note.} 
-\begin{comment}
-\subsubsection{Detour of rank varieties}
-% \begin{theorem}(\cite{eisenbud1989rank})
-    % \label{thm:es}
-Let $r$ be a decreasing concave non-negative integral function with $r(0) = N$.
-Such a function is called a rank function.
-Eisenbud and Saltment associate to a rank function the vareity of $N\times N$ matrices
-% The relevant result from Eisenbud--Saltman seems to be that 
-$$X_r = X_{r,0} = \{A:\rk A^i \le r(i) \}$$ 
-and show that it is the flat limit of a certain family 
-% $$X_{r,\lambda} = \{A : \rk (A-\lambda_i)^j\le r(i,j)\}$$
-$$X_{r,z} = \{A : \rk (A-z_i)^j\le r(i,j)\}$$
-with $r(i,j)$ determined by $r(i)$.  
-% \end{theorem}
-
-\acom{Don't know how much of this setup to recall but here are the parts that will appear in the quoted theorem.}
-% 
-More precisely, they show that 
-\begin{enumerate}
-    \item $X_r$ is a normal variety
-    \item $X_r$ is Gorenstein with rational singularities
-    \item $X_r$ fits into a flat family over $\AA^m$ of normal varieties whose fibre over a point $(z_1,\dots,z_m)$ such that the $z_i$ are all distinct is 
-\end{enumerate}
-\[
-. 
-\]
-They construct a simultaneous resolution of singularities and use the resolution of $X_r$ to describe the tangent space to $X_r$ at a point corresponding to an endomorphism $A$ such that $\rk A^i = r_i$ for all $i$.
-As an application of the tangent space computation they show that the general fiber of this family can be written as the scheme-theoretic intersection of varieties like $X_r$.
-
-To construct the resolution, they take $m$ to be the largest number such that $r(m) \ne r(m+1)$
-and consider the affine space $\AA^m$ with coordinates $(x_1,\dots, x_m)$. Given $W\subset \AA^m$ a linear subvariety, 
-% TODO: clarify that linear subvariety means to them a (translate of subvectorspace)
-they introduce $\mathcal X_{r,W}\subset\End(V) \times W \times F_r$ where $F_r$ is the (paritial) flag variety $F_r = \{(V = V_0 \supset V_1 \supset \cdots \supset V_m \supset 0 ) : \dim V_i = r(i)\}$.
-% 
-$\mathcal X_{r,W}\subset\End(V) \times W \times F$ is defined to be the subvariety of triples $(A,\vec z,\{V_i\})$ such that $(A-z_i) V_{i-1} \subset V_i$ for $z_i = x_i(\vec z)$ and $i = 1,\dots,m$. 
-The (reduced image of) projection of $\mathcal X_{r,W}$ down to $\End(V) \times W$ is denoted $X_{r,W}$ and it is a closed affine subvariety. 
-% 
-\begin{theorem}
-    (\cite[Theorem~2.1 iii)]{eisenbud1989rank})
-    $X_{r,W}$ is the restriction of $X_{r,\AA^m}$ to $W$ and as such it is flat over $W$. 
-\end{theorem}
-
-This result is applied to study the fibers of the family $X_{r,\AA^m}$ over points $\vec z \in \AA^m$ for $z_i$ not necessarily distinct.
-The coordinates $z_i$ of $\vec z$ are partitioned by equality with the help of a permutation $p$ of $\{1,\dots,m\}$ such that
-\begin{align*}
-    z_{p(1)} &= \cdots = z_{p(m_1)} , \\
-    z_{p(m_1 + 1)} &= \cdots = z_{p(m_2)} , \\ 
-    \dots \\
-    z_{p(m_s + 1)} &= \cdots = z_{p(m_s + 1)}
-\end{align*}
-and $p$ preserves the order within each interval $m_i + 1,\dots,m_{i+1}$. \acom{Not sure what this means. Order of coordinates?} With this notation in place Eisenbud and Saltman define the numbers
-
-% 
-\begin{corollary}
-    \label{cor:es}
-    The family $\OO^{\lambda',\lambda''}_{0,\AA}$ defined above has zero fibre $\OO^\lambda$. 
-\end{corollary}\begin{gather*}
-    r(i,j):= \dim V - a_{p(m_i + 1)} - \cdots - a_{p(m_i + j )} \\
-    \qquad \qquad \qquad \qquad \qquad \text{ for } i = 1,\dots,s \text{ and } j = 1,\dots , m_{i + 1 } - m_i 
-\end{gather*}
-where $a_i = r(i-1) - r(i)$.
-It is through the $r(i,j)$ that the rank function $r$ determines the Jordan types of the generalized eigenspaces of the vector of (generalized) eigenvalues $\vec z$. 
-\begin{proposition}
-    (\cite[Corollary~2.2]{eisenbud1989rank})
-    \label{prop:es}
-    The scheme-theoretic fibre of $X_{r,W}$ over $\vec z\in W$ is 
-    \[
-        X_{r,\vec z} = \{A \in \End(V) : \rk (A-z_i)^j\le r(i,j) \text{ for all } i , j \}\,. 
-    \]
-\end{proposition}
-% 
-The only work we have to do to apply \Cref{prop:es} is to determine the rank function that will allow us to realize $\OO^\lambda$ as a rank variety, and the family $\OO^{\lambda',\lambda''}_{0,\AA}$ as a deformation of it.
-%  
-\begin{lemma}
-    \label{lem:es}
-    Let $\lambda = \lambda' + \lambda''$ be partitions.
-There exists a permutation of the columns of $\lambda$ such that the first $\lambda'_1$ columns are precisely the columns of $\lambda'$ and the last $\lambda''_1$ columns are precisely the columns of $\lambda''$.
-\end{lemma}
-Recall that $\lambda' + \lambda'' = \lambda$ is a partition of $N$. 
-% Let $m_i = \lambda_{i,1}$ ($i = 1,2$), $m = m_1 + m_2$, and define
-Let $m = \lambda_1' + \lambda_2'$ and define 
-$$r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$$
-on $j = 1,\dots,m$. 
-\begin{lemma}
-   The function $r$
-%    defined by $r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda$ 
-is a rank function. 
-\end{lemma}
-
-The case that we are interested in is the case of two generalized eigenvalues, i.e.\ $\vec z = (z_1,z_2) = (0,s)$. 
-\acom{Does order matter?} 
-% Let me change notation so that $\lambda_i$ are shapes and 
-We begin by considering the open loci where the rank conditions are strict.
-
-Note that $r(j-1) - r(j) = : a_j$ is the length of the $j$th column of $\lambda$. 
-% As in \cite{eisenbud1989rank} we will denote this quantity $a_j$. 
-% 
-% 
-Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(\lambda_1')}$ are the (lengths of) columns of $\lambda'$ and $a_{p(\lambda_1' + 1)},\dots, a_{p(m)}$ are the (lengths of) columns of $\lambda''$.
-Then the functions 
-$$
-\begin{aligned}
-r(1,j) &= N - a_{p(1)} - \cdots - a_{p(j)} \\
-% \text{ and } 
-r(2,j) &= N - a_{p(\lambda_1' + 1)} - \cdots - a_{p(\lambda_1' + j)}
-\end{aligned}
-$$
-are such that 
-\begin{align*}
-    \OO^{\lambda',\lambda''}_{0,s} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots, \lambda_1' \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = \lambda_1' + 1 ,\dots, m \}
-\end{align*}
-and according to \cite[Theorem 2.1(iii)]{eisenbud1989rank} the family $X_{r,(0,s)}$ is flat over $W = \{x_1 = \cdots = x_{\lambda_1'} = 0 , x_{\lambda_1'} = \cdots = x_m\}$ (a linear subvariety of $\AA^m$) with zero fibre $X_{r,(0,0)} = \OO^\lambda$ as desired.
-\acom{Do you need to permute the indices defining $W$?}
-% $X_{r,\AA^m}$ is flat over $\AA^m$ with zero fibre $X_{r,0} = \OO^\lambda$ as desired.
-I guess we need to carefully choose the $W \subset \AA^m$ defining our family, which is smaller than the family $X_{r,\AA^m}$.
-Well, $W$ is just cut out by $0 = x_1 = x_2 = \cdots = x_{m_1}$ and $ x_{m_1 + 1} = \cdots = x_m$, or some permutation thereof to match the permutation $p$ above.
-
-% On the one hand, we know that $r(i,j)$ should be equal to $N$ minus the number of boxes in the first $j$ columns of $\lambda_i$.
-On the other hand, ES define $r(i,j)$ to be $N$ minus the $i$th chunk of $j$ columns determined by the rank function $r(i)$.
-Also, we would like for $r(i)$ to determine the shape $\lambda = \lambda' + \lambda''$.
-Take for example $\lambda' = \lambda'' = (2,1)$.
-Then $\lambda = (4,2)$ and so $r\{0,1,2,3,4\}=\{6,4,2,1,0\}$ and
-% $$\{a_1,a_2,a_3,a_4\} = \{6-4,4-2,2-1,1-0\}=\{2,2,1,1\}\,.$$
-
-% For another example take $\lambda' = (1)$ and $\lambda'' = (1,1)$. Then $\lambda = (2,1)$ and $r\{0,1,2\} = \{3,1,0\}$ so $\{a_1,a_2\} = \{2,1\}$.
-
-% Again too small.
-The problem is I don't think that it is in general true that some permutation of the list $r(i-1) - r(i)$ will be the list of lengths of columns of $\lambda'$ followed by the list of lengths of columns of $\lambda''$ which is what we are looking for.
-For one thing there's in general more than one way to write a partition as a sum of two partitions.
-Ok, concretely, a third example.
-Take $\lambda' = (a,b)$ and $\lambda'' = (c,d)$ then $\lambda = (a + c, b + d)$ and
-% $$r\{0,1,\dots,a + c\} = \{N, N-2, \dots, N-2(b+d), N-2(b+d) - 1,\dots, 0\}$$
-% so 
-% $$\{a_1,a_2,\dots\} = \{2,2,\dots,2,1,1,\dots,1\}$$
-% with $b+d$ 2s and $a+c - b - d$ 1s.
-Wait a minute, nevermind, of course this is true.
-We have two partitions $\lambda'$ and $\lambda''$ and one way to form the partition $\lambda = \lambda' + \lambda''$ is to break $\lambda_i$ down into columns, order the columns by length, and recombine.
-Cool.
-I think it's fine.
-% \acom{That's it for the note.}
-\end{comment}
-
-% \section{Exposition}
-% \label{s:exposition}
-% %
-
-% \acom{This whole section is a big question mark.
-The beginning of the rising action section is more expository, developmental, and the climax is in turn more of a rising action.
-The true climax is probably the fusion section, section 7.}
-
-% \jcom{Yes, I think that this section should be deleted and the content moved into the introduction.}
-
 \section{Rising Action} 
-\label{s:theproblem}
-
+\label{s:rising}
 Throughout this section, we continue our notation of the previous sections.
-So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights for $ \GL_m$, with $ \lambda' + \lambda'' = \lambda$.
+So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights, with $ \lambda' + \lambda'' = \lambda$.
 Also $ \mu, \mu', \mu''$ are effective coweights with $ \mu = \mu' + \mu''$ and we assume that $ \mu$ is dominant.
+
+\subsection{Linear Operators from lattices}
+\label{s:latticefacts}
+%
 
@@
 \label{le:Grl1l2}
-    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
+    Let $ L \in \Grth^+ $.  Let $ s \in \Ax$. The following are equivalent:
     \begin{enumerate}[label=(\roman*)]
-        \item \label{it:schub-pos} $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. %\acom{Should we describe this map somewhere? Earlier?}
+        \item \label{it:schub-pos} $ L $ is in the image of the map $ \Gr^{\lambda', \lambda''}_{0,s} \rightarrow \Grth^+$. 
         \item \label{it:schub-jt} The linear operator $ t $ on $ \CC[t]^m/L$ has Jordan type $((0,\lambda'), (s,\lambda''))$.
         \item \label{it:schub-lat} $ L \in G(\CC[t]) t^{\lambda'} (t-s)^{\lambda''}$.
-        % \acom{why no $G(\CC[t])$-coset?}
     \end{enumerate}
@@
 First we recall that for $ L \in \Gr^+$, $ L \in \Gr^{\lambda} = G(\cO)t^\lambda $ if and only if $ t |_{\cO^m/L} $ has Jordan type $ \lambda$.
-% \acom{Change $L_0$}
-
-Now assume that $ (L, s) \in \Gr^{\lambda', \lambda''}_{0,s}$.  By definition, $ L(0) \in \Gr^{\lambda'}$ and $L(s) \in \Gr^{\lambda''} $.  This means that $t $ acting on 
-% $ \CC\xt^m / L(0)$ 
-$\cO^m/L(0)$ has Jordan type $ \lambda'$ and $ t$ acting on 
-% $ \CC\xt[t-s]^m / L(s) $ 
-$\cO_s^m/L(s)$ has Jordan type $ \lambda''$.  For $ a = 0, s$,  we see that $$\CC[t]^m/L \otimes_{\CC[t]} \cO_a \cong \cO_a^m / L(a). $$
-Thus, Lemma \ref{le:linalg} shows that the map
-% $ L_0 / L \rightarrow \CC\xt^m / L(0)$ 
-$\CC[t]^m/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.
+
+Now assume that $ (L, s) \in \Gr^{\lambda', \lambda''}_{0,s}$.
+By definition, $ L(0) \in \Gr^{\lambda'}$ and $L(s) \in \Gr^{\lambda''} $.
+This means that $t $ acting on $\cO^m/L(0)$ has Jordan type $ \lambda'$ and $ t$ acting on $\cO_s^m/L(s)$ has Jordan type $ \lambda''$.
+For $ a = 0, s$,  we see that $$\CC[t]^m/L \otimes_{\CC[t]} \cO_a \cong \cO_a^m / L(a).
+$$
+\Cref{le:linalg} shows that the map $\CC[t]^m/L\to \cO^m/L(0)$ induces an isomorphism between the $0$-generalized eigenspace of $ t$ and $ \cO^m / L(0)$.
 The same thing holds for the $s$-generalized eigenspace of $t $ and $ \cO_s^m/L(s)$.
 This shows that \cref{it:schub-pos} implies \cref{it:schub-jt} and the logic can be reversed to see that \cref{it:schub-jt} implies \cref{it:schub-pos}.
-% \acom{is this map $v + L \mapsto v + L(0)$?} \jcom{yes} \marginpar[]{*}
-% todo
-
-On the other hand, if $ L = g t^{\lambda'} (t-s)^{\lambda''} \CC[t]^m$ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda'}\cO^m $ since 
-% $ (t-s)^{\lambda''} \in G(\CC\xt)$. 
-$ (t-s)^{\lambda''} \in G(\cO)$. In this way, we see that \cref{it:schub-lat} implies \cref{it:schub-jt} and the logic can be reversed to get equivalence.
+
+On the other hand, if $ L = g t^{\lambda'} (t-s)^{\lambda''} \CC[t]^m$ for some $ g \in G(\CC[t])$, then $ L(0) = g t^{\lambda'}\cO^m $ since $ (t-s)^{\lambda''} \in G(\cO)$.
+In this way, we see that \cref{it:schub-lat} implies \cref{it:schub-jt} and the logic can be reversed to get equivalence.
 \end{proof}
@@
 \begin{lemma} 
-\label{le:linalg} % aka solution 
+\label{le:linalg} 
 Let $ V $ be a $ \CC[t]$-module which is finite-dimensional as a complex vector space.  For any  $ a \in \AA$, the map
@@
 %
+
+\subsection{Matrices from lattices}
+\label{ss:mvyisos}
+
 \begin{lemma} 
@@
 % 
-% \jcom{I realized the meaning of the ``extra'' condition from the paper with Sabin and I added it into point 3.}
-% \acom{Technically though the extra condition in that paper is weaker? $W_{\mu_i}$ being the span of $e_j,te_j,\dots,t^{\mu_i-1}e_j$ or the complement of $t^{\mu_i}\cO^m$ in $\cO^m$.}
-% 
 \begin{proof}
@@
     To show that $ \beta_\mu$ forms a basis for $ \CC[t]^m/L$, it suffices to show that for each $ i$, 
-    $$ t^{\mu_i} e_i  \in \Sp_\CC(  t^k e_i : 0 \le k < \mu_i, 1 \le i \le m) + L\,.$$
-    % 
-    % \rcom{Preimage of $\beta_\mu$}  
-    % 
-    % \acom{I guess that this is the ``$\mu$-numeration'' of the standard basis of $\CC^N$ that I commented out.}
-    % 
-    This follows immediately from \cref{it:t-act}.
-    % 
+    $$ t^{\mu_i} e_i  \in \Sp_\CC(  t^k e_i : 0 \le k < \mu_i, 1 \le i \le m) + L\,.$$ This follows immediately from \cref{it:t-act}.
 \end{proof}
-% \acom{note-to-self, skipped this; return to it.}
-% 
-%\acom{Don't have $P$ notation, replacing (in lemma below) with $\ZZ^m$ for now..}
-
-% 
-\section{Climax}
-\label{s:climax}
-Throughout this section, we continue our notation of the previous sections.
-So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights for $ \GL_m$, with $ \lambda' + \lambda'' = \lambda$.
-Also $ \mu, \mu', \mu''$ are effective coweights with $ \mu = \mu' + \mu''$ and we assume that $ \mu$ is dominant.
+%
 
 Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.  Note that $g(A)t^{-\mu} \in G_1(\Oinf)$.
-% section ??.  
 Since $ g(A) \in M_m(\CC[t]) \cap G_1(\Oinf)t^\mu$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.
@@
 
-The following result is called the Mirkovic--Vybornov isomorphism \cite{mirkovic2007quiver}.
-In the following form, it can be found in \cite[Theorem 3.2]{cautis2018categorical}, except that we have tweaked both maps with a matrix transpose $[?]^\tr$.
-
-% \jcom{I'm not sure which of the Mirkovic--Vybornov papers to cite.} \acom{can say 07, rewritten in 19?}
-% 
+The following result is called the Mirkovi\'c--Vybornov isomorphism \cite{mirkovic2007quiver}.
+In its present form, it can be found in \cite[Theorem 3.2]{cautis2018categorical}, except that we have tweaked both maps with a matrix transpose $[\phantom{A}]^\tr$.
+%
+
 \begin{theorem} 
@@
 \end{theorem}
-% 
-%\acom{Should we say what $^{tr}$ means?}
-
+
+\subsection{Upper-triangularity and the Mirkovic-Vybornov isomorphism}
 For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ with $\cW_\mu$.
@@
 This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective.
-% Joel: The only non-injectivity comes from the fact that we forget the data
-% of s.  So the map is non-injective over the locus where s is not
-% actually an eigenvalue (in lattice terms where L(s) is the standard
-% lattice).
-In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the ``almost injective'' 
-% \acom{emphasis is on the almost injectivity/glass half full no?} \jcom{ok, I changed it} \acom{Yay!}
-map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$. 
-% (for example the fibre of this map over $ 0 $ is $ \CC $). 
-% \acom{Grammar of `write using the map' is iffy. Also, is the fibre over 0 just a copy of the zero matrix in every $s$-fibre?}
+In a similar way, we will write $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \cap \TT_\mu$ using the ``almost injective'' map $ \overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow M_N(\CC)$.
 
 The following refinement of the \mvy isomorphism is a special case of \cite[Theorem 5.3]{mirkovic2007quiver}. 
-\acom{Wait isn't 5.3 a special case of this?}  \jcom{No, they deal with the more general setting of more points.} \acom{Ok, but I don't think that they establish this exact fact..they have Lemma~4.4.2 and Corollary 4.5 which uses the convolution grassmannian.}
+% 
 \begin{theorem} 
@@
 \end{theorem}
-% \acom{Joel, you stopped writing $X_{0,\AA}$ in favour of $X_\AA$ --- should we do this everywhere?}
-% \jcom{Oops, no I think that we should stick with $ X_{0, \AA}$.}
-% TODO: comb the doc at the end for this notation 
+% 
 \begin{proof}
@@
 % 
-% \acom{We need to assume that $\mu' +\mu''$ is dominant in the theorem below. The assumption for \Cref{th:TmuWmu} is also missing.} 
-% 
-% \jcom{I added a reminder at the beginning of the section.}
-% 
 \begin{theorem}
 \label{th:OTGrW}
-The isomorphism from \Cref{th:OGrl} 
-% \acom{should ``Theorem'' etc.\ be capitalized when it appears in the middle of a sentence?} Yup.
-restricts to an isomorphism
+The isomorphism from \Cref{th:OGrl} restricts to an isomorphism
 $$ 
@@
 \end{theorem}
-% 
-%\jcom{I was thinking about the proof of this result.
-It is enough to prove that for $ A \in \OO^{\lambda', \lambda''}_s \cap \TT_\mu $, $g(A) \in S^{\mu', \mu''}_s $ if and only if $ A \in T^+$.
-It is easy to show that if $ A \in \UU$, then $ g(A) \in S^{\mu', \mu''}_s $.
-But the converse is not so obvious.
-(I think Anne's paper/thesis might be incomplete on this point.)  I thought of two approaches: first to write down the lattice interpretation of $S^{\mu', \mu''}$ (similar to what is in my thesis in the Anderson-Kogan comparison section) or think about both $S^{\mu', \mu''}$ and $\UU$ as attracting sets for a $\AA^\times$ action.
-Which do you prefer?}
-% 
-%\acom{Assuming Theorem 2 we think this follows by application of Roger's lemma. Also, I think my thesis is complete on this point.}
-% 
-%\jcom{I thought about this and I agree with you now.  I will write this up soon.} 
-% 
-%\acom{But I am also curious about the attracting set approach.}
 % 
@@
 Let $ A \in \TT_\mu$ and $ s \in \CC $. We must show that  $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $ if and only if $ (g(A)\CC[t]^m,s) \in S^{\mu', \mu''}_{0,\AA} $.
-%\acom{not $g(A)\CC[t]^m$}
 
 On the one hand, if $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA} $, then $ g(A)$ is lower-triangular with diagonal $ t^{\mu'} (t-s)^{\mu''}$, and so $ g(A) \in N_-[t, t^{-1}, (t-s)^{-1}] t^{\mu'} (t-s)^{\mu''}$.
-% \acom{not $g(A)\CC[t]^m$}
-% \jcom{This one isn't a point in $ \Gr$, the others I changed.}
 
@@
 $$
-for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\Oinf) $. % was CC\xt[]
-Note that $ h^{-1}n h \in N_-(\Kinf)$, 
-% ((t^{-1}))
-so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_{-,1}(\Oinf), n_2 \in N_-(\CC[t])$.  So then after doing a bit of algebra, we reach
+for some $ r \in G(\CC[t]), n \in N_-(\CC[t, t^{-1}, (t-s)^{-1}]) $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu''} t^{-\mu''}$ which lies in $ T_1(\Oinf) $. 
+Note that $ h^{-1}n h \in N_-(\Kinf)$, so we can factor it as $ h^{-1} n h  = n_1 n_2 $, where $ n_1 \in N_{-,1}(\Oinf), n_2 \in N_-(\CC[t])$.  So then after doing a bit of algebra, we reach
 $$
@@
 $$
-% $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
-Thus, we deduce that $ g^{-1} h n_1 \in N_{-,1}(\Oinf)$ 
-% $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
-and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''}N_{-,1}(\Oinf) $.  
-% Given that we know that 
+Thus, we deduce that $ g^{-1} h n_1 \in N_{-,1}(\Oinf)$ and hence $ g(A) \in t^{\mu'} (t-s)^{\mu''}N_{-,1}(\Oinf) $.
 Since $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu', \mu''}_{0,\AA}$ as desired.
 \end{proof}
-% 
-% \jcom{In this proof, I made some statements about $\mu$ dominant, which are incorrect (as Anne knows).
-To make them correct we should either switch to having $ \mu$ being antidominant or switch $ N$ to $ N_-$.
-In this proof $ g(A)$ generally denotes a group element, rather than an affine Grassmannian element which conflicts a bit with earlier usage.}
-% 
-%\acom{What was the answer to Roger's question why is $g^{-1}hn_1 \in G_1 (\Oinf)$}
-% 
-%\rcom{So if we look at $g = g(A)t^{-\mu}$, since $A \in \TT_\mu$, the entries of $g(A)_{ij}$ are polynomials of degree $\min(\mu_i-1,\mu_j-1)$ when $i \neq j$, otherwise of degree $\mu_i$.
-When we multiply by $t^{-\mu}$, we scale the $i$th column by $t^{-\mu_i}$.
-So the diagonal entries are $1 + p$ where $p \in t^{-1}\CC[t^{-1}]$ while the off-diagonal entries in column $i$ have highest (in $t$) degree $\min(\mu_i-1, \mu_j-1) - \mu_i < 0$.
-Hence $g \in G_1(\cO_\infty)$.}
-%
-
-Restricting to the zero fibre and applying $\theta_0$ together with \Cref{prop:adjoint} we recover a result of the second author. 
-%itself a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}, the ordinary affine Grassmannian version of \Cref{th:OGrl}. 
-% 
-% \acom{The ordinary Gr should be called static. Really onomotopoeic. In opposition with moving. }
-% 
+
+Restricting to the zero fibre and applying $\theta_0$ together with \Cref{prop:adjoint}, we recover a result of the second author. 
 \begin{corollary}
@@
 %
-%The closures of the irreducible components of the righthand side are \new{MV cycles of type $\lambda$ and weight $\mu$}.
-By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \new{perfect basis} of $\CC[N]$.
-
-%\acom{We are ready for applications! One of the motivations for this paper is... Abstractly multiplication is $\ast_s$... To compute we now carry this across \Cref{th:OTGrW}.}
-
-\section{\sout{Falling Action}} % Resolution  
-\label{se:falling}
-\subsection{MV cycles}
-%Let $Q_+$ denote the $\ZZ_{\ge 0}$-span of the positive coroots. 
-%Recall the \new{dominance order} on $\ZZ^m$ defined by declaring that $\mu\le\lambda$ if $\lambda - \mu\in Q_+$ for any $\lambda,\mu$.
+
+\section{Climax}
+\label{s:climax}
+% 
+\subsection{MV cycles and tableaux}
+\label{ss:mvcs}
+%
 
 Continuing now with the notation of the previous sections, we add the assumption that $\mu\le\lambda$ and forget the assumption that $\mu$ is dominant. 
-% 
-% We need to decide on the order in section 7. How about:
-% 
-% 1. MV cycles and tableaux (7.1)
-% 2. GOVs and relation to MV cycles, including fusion (7.2)
-% 3. Stable MV cycles and multiplication  in C[N]
 % 
@@
 
-% \jcom{In this section, I think that $ \mu$ is not necessarily dominant.  So I think that we should we recall our previous notation, but say that $ \mu $ might not be dominant here.}
-% \acom{Ok.}
-
 By \cite[Theorem~3.2(b)]{mirkovic2007geometric}, each MV cycle in $\overline\Gr^\lambda$ of coweight $\mu$ has dimension $ \rho(\lambda - \mu)$ where $ \rho = (m, m-1, \dots, 1)$ and we use the ordinary dot product on $\ZZ^m$.
@@
 
-% \jcom{We could put some stuff here about stable MV cycles and multiplication, but maybe we can have this in a later section.}
-
-% \acom{With this definition here what do we do about the sentence after \Cref{cor:mvy} above?}
-% \jcom{I just cut it.  I think that it was a bit out of place there.}
-
-% \acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis.
-Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with.
-This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
-%
-
-In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic--Vilonen polytopes, or equivalently Lusztig data, which are sequences in $\NN^{\Delta_+}$ that depend on a choice of reduced expression.
-For $\GL_m$ and the standard reduced word, this description can be reworded in terms of Young tableaux.
-% \jcom{Maybe add something here about Lusztig data and the standard reduced word, $\vi = (1,2,\dots,m-1,\dots,1,2,1)$.}
-
-Denote by $[a,b]$ the interval $\{a,a+1,\dots,b-1,b\}\subset\NN$. 
-% 
-We begin with the following definitions.
+In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic--Vilonen polytopes, or, equivalently, Lusztig data, which are sequences in $\NN^{r}$ that depend on a choice of reduced expression for the longest element of the Weyl group of $G$.
+We will now explain how to use these results to index MV cycles for $ \GL_m$ using Young tableaux.
+(For any $ G$, we use $ r $ for the number of positive roots; in the case of $ \GL_m$, $ r = m(m-1)/2$.)
+
+Denote by $[a,b]$ the interval $\{a,a+1,\dots,b-1,b\}\subset\NN$. We begin with the following definitions.
+% 
 \begin{definition}
@@
 % 
-If $ \gamma \subset [1,m]$, we define two lattices $ L^\gamma, L_\gamma $ in $ \cO^\gamma := \Sp_{\cO}(e_i : i \in \gamma) $ by
+If $ \gamma \subset [1,m]$, we define two lattices $ L^\gamma, L_\gamma $ in $ \cO^\gamma := \Sp_{\cO}(e_i : i \in \gamma)$ by
 \begin{gather*}
-%    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
-L^\gamma:= L \cap \cO^\gamma  \qquad L_\gamma := L / L^{\gamma^c} \subset \cO^m / \cO^{\gamma^c} = \cO^\gamma
+    L^\gamma:= L \cap \cO^\gamma  \qquad L_\gamma := L / L^{\gamma^c} 
+    % \subset \cO^m / \cO^{\gamma^c} = \cO^\gamma
 \end{gather*}
@@
 % 
-% \acom{I suggest replacing $\mathbb O$ by $R$, and $L/L^{\gamma^c}$ by $(L + R^{\gamma^c})/R^{\gamma^c}$ because that's what we're doing.
-In a lower triangular $g(A)$ columns ${i+1..m}$ cannot be used to eliminate entries in rows ${i+1..m}$ in the first $i$ columns over $\CC[t]$ or $\CC\xt$.}
-% \jcom{If you think that it sounds better with $ \OO $ replaced by $ R$, then I won't object to the change.
-Note that the first sentence won't quite make sense ``let $ L \subset \OO^m$ be a point in $ \Gr_+$'', we would have to write ``let $ L \subset R^m$ be a lattice''.}
-% \jcom{$ L /L^{\gamma^c} $ is the image of $ L $ in $ \OO^m / \OO^{\gamma^c}$ since the kernel of the map $ L \rightarrow \OO^m / \OO^{\gamma^c}$ is precisely $L^{\gamma^c} $, so I don't think that there is any problem here.
-Again, if you think that it is better, I won't object to your suggested change.}
-% \jcom{Your question made me wonder about the following: how do we know that $ L_\gamma$ is a lattice?  (or $ L^\gamma$ for that matter)}
 \end{definition}
@@
 We record the following easy observations.
-\begin{lemma} \label{le:rdimTrans} Let $ L \in \Gr_+$ or $\Grth_+$.
+\begin{lemma} 
+\label{le:rdimTrans} 
+Let $ L \in \Gr_+$ or $\Grth_+$.
 \begin{enumerate}
-    \item For any $ 
-    \gamma \subset [m] $, we have 
-    $$ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.$$
-    \item For any $ \gamma_1 \subset \gamma_2 \subset [m]$, we have $$ (L_{\gamma_2})_{\gamma_1} = L_{\gamma_1}
+    \item For any $ \gamma \subset [m] $, we have 
+    $$ 
+        \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L \,.
+    $$
+    \item For any $ \gamma_1 \subset \gamma_2 \subset [m]$, we have 
+    $$ 
+        (L_{\gamma_2})_{\gamma_1} = L_{\gamma_1}\,.
     $$
@@
 \end{lemma}
-% \acom{Doesn't the identification $G(K)/G(O) \to G(O)\ G(K)$ coming from $g\mapsto g^{-1}$ give us a minus sign somewhere, since we are sending $S^\mu_w$ to $S^{-\mu}_w$, so $D_{\omega_i}(L) = -\rdim L_{[1,i]}$.
-Ignoring the minus sign for now, for $j\le i\le m$, and $L_{[1,i]}$ in $S^{\mu(i)}_- \cap S^{\lambda(i)}_+$ we’d like $D_{\omega_j}(L_{[1,i]}) = \rdim (L_{[1,i]})_{[1,j]} = \lambda(i)_j + \cdots + \lambda(i)_i$ whereas the claim $(L_{[1,i]})_{[1,j]} = L_{[1,j]}$ hides that this lattice also depends on $i$?
-I'm sure I'm missing something here so I will look at it again later.
-$n_{(a,b)} (L_{[1,i]}) = -D_{[a+1,b]} - D_{[a , b-1]} + D_{[a + 1, b-1]} + D_{[a,b]} = - \rdim L_{[a+1,b]} - \rdim L_{[a,b-1]} + \rdim L_{[a+1,b-1]} + \rdim L_{[a,b]}$}
-% \jcom{I warned you when we talked on Tuesday that there might be some problems, but I think that we shouldn't dig any deeper here.} 
-% \acom{Well, it's not that deep..
-it's just that $(L_{\gamma_1})_{\gamma_2}$ involves taking $\gamma_2^c\subset \gamma_1$ and landing in $\cO^{\gamma_1\cap\gamma_2}$ whereas $L_{\gamma_2}$ involves taking $\gamma_2^c\subset[m]$ and landing in $\cO^{\gamma_2}$ ...so I think the change makes it true.}
-% \jcom{But I assumed that $ \gamma_1 \subset \gamma_2$, so I don' think that taking intersection is necessary.}
-% \acom{Even so?
-What was written before was $(L_{\gamma_1})_{\gamma_2} = L_{\gamma_2} $ and if $\gamma_1\subset\gamma_2$ then the intersection is $\gamma_1$.
-Anyway I don't think we ever use Lem.
-6(2), so we can do without it?}
-% \jcom{Oh, I guess there was a typo.  I fixed it now.  It is used in the proof of Prop 4, I will add a reference.}
-
+% 
 For any $ L \in \Gr_+ $ and $\gamma \subset [m]$, we define $ D_\gamma(L) := \rdim L^\gamma = \rdim L - \rdim L_{\gamma^c}$.
@@
 cit.} these functions are used to compute the hyperplanes of the associated MV polytopes.)
-% \acom{We should introduce $D_\gamma$ briefly.}
-% \jcom{I think that this is sufficient, since it doesn't really play any role in our paper.}
-% \acom{Ok; I was thinking just another half-sentence, like these are some valuation functions and/or they are used to characterise combinatorially the MV cycles.}
 
 From now on, we will write $ S^\mu_- = N_-(\cK) t^\mu$ (with a subscript), because we will also need the opposite semi-infinite cell $S^\mu_+ := N(\cK)t^\mu$.
-%\acom{HB, ``..we will write.., because we will need the opposite cell..''}
-% \acom{Maybe we shouldn't decorate $S^\mu$ with a subscript $-$ after all since we certainly won't want to add to $S^{\mu',\mu''}_{0,\AA}$ in underscores.}
-% \jcom{I agree.  Is the above solution ok?}
-% \acom{Sure.}
-% 
-% \jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
-% \acom{For it.}
-% \acom{As was checked in \cite{dranowski2020generalized} $S^\mu_w = \{D_{w\omega_i} = \langle \mu , w w_0 \omega_i\rangle \}$ so $S^\mu_+ = \{D_{\omega_i}(L) = \rdim L^{w_0\omega_i} \}$} 
-% \jcom{But that was for a different identification of the left and right quotients.  I'm certain that the statements in the Lemma below are correct.}
 
@@
         \item $ L \in S_+^\mu$ \label{Srdim1}
-        \item $ \rdim L^{[1,i]} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $. \label{Srdim2} % \acom{$\rdim L^{[m-i+1,m]} = \mu_{m-i+1} + \cdots + \mu_m$}
-        \item $ \rdim L_{[i+1,m]} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$. \label{Srdim3} % \acom{$\rdim L_{[m-i]}=\mu_1 + \cdots + \mu_{m-i}$}
+        \item $ \rdim L^{[1,i]} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $. \label{Srdim2} 
+        \item $ \rdim L_{[i+1,m]} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$. \label{Srdim3}
     \end{enumerate}
@@
 \end{lemma}
-
+% 
 \begin{proof}
 We prove the first statement as the second is similar.
-Let $ L = n t^\mu \CC[t]^m$ for $ n \in N_+(\cK)$ and let $ v_1, \dots, v_m $ denote the columns of the matrix $ nt^\mu$.
+Let $ L = n t^\mu \CC[t]^m$ for some $ n \in N_+(\cK)$ and let $ v_1, \dots, v_m $ denote the columns of the matrix $ nt^\mu$.
 Then $ L = \Sp_{\cO}(v_1, \dots, v_m)$.
-Fix some $ i \le m$.
+Fix $ i \le m$.
 Then $ L^{[1,i]} = \Sp_{\cO}(w_1, \dots, w_i) $ where $ w_j $ denotes the first $ i $ entries of $ v_j $ (by upper-triangularity, the rest of the entries are 0, in any case).
@@
 Assume that $L \subset \cO^m$.
-Then $ L^{[1,i]} \subset \cO^i$ and $ \rdim L^{[1,i]} $ is the valuation of the determinant of the matrix with columns $ w_1, \dots, w_i$.
+Then $ L^{[1,i]} \subset \cO^i$ and $ \rdim L^{[1,i]} $ is the valuation of the determinant of the matrix whose columns are $ w_1, \dots, w_i$.
 Since this matrix is upper-triangular with diagonal entries $ t^{\mu_1}, \dots, t^{\mu_i}$, this determinant is $ t^{\mu_1 + \dots + \mu_i} $ and hence $ \rdim L^{[1,i]} = \mu_1 + \dots + \mu_i$.
 
-Thus \ref{Srdim1} implies \ref{Srdim2}.  The converse follows from the fact that every $ L$ lies in some $ S_+^\nu$ and by the above reasoning, $ \nu$ is determined by the values of $ \dim L^{[1,i]}$.
-
-The equivalence of \ref{Srdim2} and \ref{Srdim3} follows from Lemma \ref{le:rdimTrans}.
+Thus \cref{Srdim1} implies \cref{Srdim2}.
+The converse follows from the fact that every $ L$ lies in some $ S_+^\nu$ and by the above reasoning, $ \nu$ is determined by the values of $ \dim L^{[1,i]}$.
+
+The equivalence of \cref{Srdim2} and \cref{Srdim3} follows from \Cref{le:rdimTrans}.
 \end{proof}
-% \jcom{I added a proof.  We can get delete and just put a reference to mvcycle if you prefer.}
-
-% \acom{No no this is good! Thanks for other additions}
+
+% \acom{Maybe a new section here?}
+% \jcom{I thought about that too.  Either way is fine for me.}
 
@@
 Denote by $YT(\lambda)$ the set of (possibly semi-standard) Young tableaux of shape $\lambda$ and by $YT(\lambda)_\mu$ the subset of $YT(\lambda)$ of tableaux having weight $\mu$.
-%Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
-% For the sake of making a definition, we momentarily put some letters of our alphabet in unexpected roles, and ask you to suspend your disbelief.
-Given an arbitrary tableau $t$ having weight $w$ and shape $s$, we denote by $s(i)$ (resp.\ $w(i)$) the shape (resp.\ the weight) of $t(i)$, the tableau got from $t$ by discarding all boxes of weight exceeding $i$.
+Let $YT = \bigcup_\lambda YT(\lambda)$ and denote by $YT_+\subset YT$ the subset of those tableaux having dominant weight.
 
@@
 
-The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \new{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
-% \acom{For Joel: weight or filling? See line below.}
-$$
-\begin{aligned}
-% n_\bullet(\tau)_{i,j} &= \lambda(i+1)_j - \lambda(i)_j = \text{ \# of boxes on the $j$th row of $\tau $ filled with $ i+1$}  \\
-% (i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
-% (2,2),\dots,(m-1,2),%\\
-% \dots,%\\
-% (m-1,m-1)
-n_\bullet(\tau)_{(a,b)} &= \lambda(b)_a - \lambda(b-1)_a = \text{ \# of boxes on the $a$th row of $\tau $ filled with/of weight $b$}  \\
-% (i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
-% (2,2),\dots,(m-1,2),%\\
-% \dots,%\\
-% (m-1,m-1)
-(a,b) &=  (1,2),(1,3),\dots,(1,m),%\\
-(2,3),\dots,(2,m),%\\
-\dots,%\\
+The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $r= m(m-1)/2$ non-negative integers defined from its \new{Gelfand--Tsetlin pattern} (see \cite[Sect.~4]{berenstein1988tensor}) $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula
+$$
+\begin{gathered}
+    n_\bullet(\tau)_{(a,b)} = \lambda(b)_a - \lambda(b-1)_a = \text{ \# of boxes on row $a$ of $\tau $ of weight $b$}  \\
+    % \qquad 
+    % \text{for } 
+    (a,b)                   =  (1,2),\dots,(1,m),
+                                (2,3),\dots,(2,m),
+                                \dots,
                                 (m-1,m)\,. 
-\end{aligned}
-% (i,j) = \begin{smallmatrix}
-% \\
-% (1,1) \\
-% (2,1) & (2,2) \\
-% \vdots & & \ddots \\
-% (m-1,1) & (m-1,2) & \dots & (m-1,m-1) 
-% \end{smallmatrix}
-$$
+\end{gathered}
+$$
+% 
 Note that $ \lambda - \mu = \displaystyle{\sum_{1 \le a < b \le m}n_\bullet(\tau)_{(a,b)} \beta_{a,b}} $ where $ \beta_{a,b} $ denotes the positive root of $ G$ with a $ 1 $ in the $a $ slot and a $-1$ in the $ b $ slot.
-% for 
-% $(i,j) = (1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2),\dots,(m-1,m-1)$. 
-% 
-The pattern $\gt(\tau)$ is recorded as a lower-triangular matrix (the array of shapes of subtableaux $\tau(i)$) and the datum $n_\bullet(\tau)$ is recorded as a sequence.
+The pattern $\gt(\tau)$ is recorded as a lower-triangular matrix (the array of shapes of subtableaux $\tau(i)$) and the datum $n_\bullet(\tau)$ is recorded as a sequence, unless noted otherwise.
 Below is an example with $\lambda = (4,2)$ and $\mu = (3,2,1)$.
-\acom{GT patterns were introduced in \cite{berenstein1988tensor} to study branching?
-In particular \S 4 of that paper introduces the map from tableaux to patterns.
-Note that the map is not 1-to-1.}
-
-% \jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}
-
-% \acom{Yes $i = m$ doesn't make sense.
-Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2,\dots,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things.
-Right?}
-
-% \begin{example}
-    \[
-        \tau = \young(1112,23) \qquad \gt(\tau) = \begin{matrix}
+\[
+    \tau = \young(1112,23) \qquad \gt(\tau) = 
+    \begin{matrix}
         3 \\
@@
 \]
-% \end{example}
-% For example, if 
-% \[
-%     \tau = \young(1112,23) 
-% \]
-% then
-% \begin{gather*}
-% %    \text{if } \tau = \young(1112,23) \text{ then } 
-% \gt(\tau) = \begin{matrix}
-%        3 \\
-%        4 & 1 \\ 
-%        4 & 2 & 0 
-%    \end{matrix} \text{ and }
-%    n_\bullet(\tau) = (1,0,1)\,. 
-% \end{gather*}
-% 
-%This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
-% 
-% \acom{In this case $L = \langle t^3 e_1 - ate_2 - be_3 , t^2 e_2, te_3\rangle$ so $\rdim L^{w_0\omega_i} = \{1,3,6\} = \langle \mu , w_0 \omega_i\rangle = D_{\omega_i}(L)$}
-
-% \jcom{$L \in S_-^{(3,2,1)}$, so $ \rdim L^{[3,3]} = 1 $ in accordance with the lemma above.}
 
@@
 \end{equation*}
-% and $Z(\tau) = \overline{\mathring Z(\tau)}$. 
-% 
-% \jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}
-% \acom{And $\{1,\dots,i\}$ etc.}
-
-The following result is closely related to  Theorem 5.4.3.
-from \cite{dthesis}.
-It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2004mirkovic} (see Section 9 in \cite{kamnitzer2010mirkovic}).
-We remeark that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.
+\begin{remark} \label{rem:claxton}
+Theorem 4.2 of \cite{claxton2015young} shows that the map $ YT(\lambda) \rightarrow \NN^r $ is the canonical crystal embedding $ B(\lambda) \rightarrow B(\infty)$.
+\end{remark}
+
+The following result is closely related to  Theorem 5.4.3 from \cite{dthesis}.
+It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2004mirkovic} (see \cite[Section 9]{kamnitzer2010mirkovic}).
+We remark that a different map from Young tableaux to MV cycles was obtained by Gaussent, Littelmann and Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.
 
@@
 \end{proposition}
-\begin{remark}
-We believe that $ \mathring Z(\tau)$ is irreducible so that in fact $ Z(\tau) = \overline{ \mathring Z(\tau)}$.
+% 
+\begin{remark} \label{rem:irreducible}
+We believe that $ \mathring Z(\tau)$ is irreducible, so that in fact $ Z(\tau) = \overline{ \mathring Z(\tau)}$.
 \end{remark}
@@
 \begin{proof}
-    The proof of this theorem follows the same strategy as in \cite{dthesis}.
-% \jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}    
-% \acom{I've been meaning to update the paper. It's peppered with ``typos''.}
-% 
+The proof of this proposition follows the same strategy as in \cite{dthesis}.
 First, we consider 
-% \acom{add \texttt{mathring}'s to these $Z$'s?} \jcom{Sure.}
 \begin{equation*}
     \mathring Z(\tau)_1 := \{ L \in S^\mu_- \cap \Gr_+ : L_{[1,i]} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
-%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
 \end{equation*}
@@
 where note that $ \lambda(b)_a + \dots + \lambda(b)_b$ is the number of boxes on rows $ a, \dots, b$ of weight $ 1, \dots, b $.
-% \jcom{We could write that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ filled with $ 1, \dots, i $.}
-% \acom{\emoji{thumbsup}}
-
-From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ \mathring Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in Sect.\ 4.3 of \cite{kamnitzer2010mirkovic}.
-In particular, it is irreducible.
-Thus, its closure is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
+
+From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ \mathring Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in  \cite[Sect.\ 4.3]{kamnitzer2010mirkovic}.
+In particular, it is irreducible and of dimension $ \rho(\lambda- \mu)$.
+Moreover, its closure is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.
 (The reader is warned that in \cite{kamnitzer2010mirkovic} the third author worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using the map $ G(\cO) g \mapsto g^{-1} G(\cO)$.)
-% \acom{Maybe we should avoid using square brackets as we haven't used them yet?}
-% 
-Now, by results of \cite{kamnitzer2008hives}, (see especially the proof of Theorem 1.4,) we note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$. 
-% Explanation: 
-% MV polytopes giving tensor product multiplicity of V(\nu) in
-% V(\lambda) \otimes V(\mu)
-% with
-% Hives with bdy \lambda, \mu, \nu.
-% 
-% If we take \mu and \nu to be sufficiently large compared to \lambda,
-% then this becomes a bijection
-% MV polytopes for the weight multiplicity V(\lambda)_{\nu - \mu}
-% with
-% Young tableaux YT(\lambda)_{\nu - \mu}
-% 
-% Even better, in that paper, I worked geometrically, and I gave a
-% bijection from components of the fibre of the convolution morphism to
-% hives.  Again, taking \mu, \nu large compared to \lambda, this fibre
-% of the convolution morphism becomes Gr^\lambda \cap S^{\nu - \mu}.  So
-% that paper actually does give a bijection from components of
-% Gr^\lambda \cap S^{\nu - \mu} to tableaux.
+% 
+Now, by results of \cite{kamnitzer2008hives} (see especially the proof of Theorem 1.4), we note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$.
+(This can also be deduced by combining \Cref{rem:claxton} with \cite[Proposition 6]{anderson2003polytope}.)
 
@@
 From above, $  f_i(\mathring Z(\tau(i))_1) \cap \Gr^{\lambda(i)}$ is a dense constructible subset of $\mathring Z(\tau(i))_1$.  
-Since $ \mathring Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)}_- \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ 
-% \acom{$\cap \mathring Z(\tau)_1$?} \jcom{The domain of $ f_i$ is $ \mathring Z(\tau)_1$, so automatically, these preimages are contained in $ Z(\tau)_1)$.} 
-is a dense constructible subset of $ \mathring Z(\tau)_1 $.
+Since $ \mathring Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)}_- \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ is a dense constructible subset of $ \mathring Z(\tau)_1 $.
 
@@
 $$
-is a dense constructible subset of $\mathring Z(\tau)_1$. 
-% \acom{Again are we maybe missing capping with $Z$ in the above $:=$?} 
-Thus $\overline{\mathring Z(\tau)_2} = \overline{\mathring Z(\tau)_1}$.
+is a dense constructible subset of $\mathring Z(\tau)_1$. Thus $\overline{\mathring Z(\tau)_2} = \overline{\mathring Z(\tau)_1}$.
 
@@
 $$
-\mathring Z(\tau)_2 \subset \mathring Z(\tau). % \{ L \in S^\mu : L_{[i]} \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
+    \mathring Z(\tau)_2 \subset \mathring Z(\tau).
 $$
@@
 $$ \bigsqcup_{\tau \in YT(\lambda)_\mu} \mathring Z(\tau) \subset \Gr^\lambda \cap S_-^\mu$$
-and the number of irreducible components of the right hand side 
-% \acom{of max dim?} \jcom{it is pure dimensional, as mentioned at the beginning of section 6.1} 
-equals $|YT(\lambda)_\mu|$, thus on the left hand side, each $ \mathring Z(\tau)$ can only have one irreducible component of dimension $ \rho(\lambda - \mu)$.
-% 
-%\jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}
-% 
-% See computation 5.3.9 and Lemma 5.4.2 (ignore its proof) of \url{http://www.math.toronto.edu/adranows/athesis.pdf}. 
+and the number of irreducible components of the right hand side equals $|YT(\lambda)_\mu|$, thus on the left hand side, each $ \mathring Z(\tau)$ can only have one irreducible component of dimension $ \rho(\lambda - \mu)$.
 \end{proof}
-% This gives us the dimension of Gr^\lambda \cap Gr_\mu \cap S^\mu.
-% Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all
-% % but its first $i$ boxes
-% boxes of weight exceeding $i$. 
-% % If the tableau contains repeated entries then first means leftmost.
-% 
-% \jcom{I don't think that you should mention this partial inverse here.
-I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
-% \acom{Ok, I moved it.}
-
-% Denote the image of $\tau$ in $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ by $X(\tau)$ and in $\overline{\Gr}^\lambda\cap S^\mu_-$ by $Z(\tau)$. Thus $Z(\tau) = \phi(X(\tau))$. \acom{Out of place?} 
-% \rcom{What is $\phi$?}
-% 
-% 
-% TODO: Not yet, that would be the algo stuff that we are holding off on 
-% In this section we explain how to determine the ideal of $Z'\ast_\AA Z''$ from the minimal pair $(\tau',\tau'')$ corresponding to $(n_\bullet(Z'),n_\bullet(Z''))$.
-% 
-% In particular, we prove that ``the generalized Spaltenstein map'' produces MV cycles. 
-% 
-% and recall the $\mu$-numeration of the standard basis of $\CC^N$. 
-% TODO: can't we do without it^^
-
-% 
-% In this section we demonstrate how to put the main results of this paper into practice.
-% 
-% 
 \subsection{Fusion of MV cycles via fusion of generalized orbital varieties}
-
-% \jcom{Anne, can you reorganize this section to start with $ X(\tau) $ and then do the fusion afterwards?}
 
@@
 If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$.
-% \acom{Change $\CC$'s to $\AA$'s?} No.
-% TODO: address 
-% \acom{We could also use a more compact notation like $A_{(p)}$}
-% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}
-
-Let $\tau\in YT(\lambda)_\mu$ with $\mu$ dominant. 
-We define
+
+Let $\tau\in YT(\lambda)_\mu$ with $\mu$ dominant. We define
 \[
 \mathring X(\tau) = 
-% \overline{
     \{
@@
 \end{lemma}
-% \jcom{We should add a proof here.  It will be very similar to Prop 5 below.} \acom{Ca marche?}
-% \jcom{Oui.  J'ai fait des petites revisions.}
 \begin{proof}
@@
 
-By \cite[Prop.\ 4.5.4]{dthesis}, $ \mathring X(\tau) $ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.
+By \cite[Prop.\ 4.5.4]{dthesis} (or \Cref{pr:newmvdes} above), $ \mathring X(\tau) $ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.
 We write $ X(\tau)$ for the closure of this component.
-It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu \cap \n$ and will be called a \new{generalized orbital variety}.
-% 
-% \jcom{We should give a more specific citation to \cite{dthesis} here and below.
-Also, throughout this paper, we should either cite your paper or your thesis, but not both (unless there is a very good reason to do so).
-I reorganized this section a bit.
-Feel free to add a bit more exposition.}
-% \acom{Just posted to arXiv. Will re-ref shortly. Also made citation more specific.}
-% 
-In fact, these are all the generalized orbital varieties:
+It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu \cap \n$ and will be called a \new{generalized orbital variety of type $\lambda$}.
+% 
+The collection of all possible generalized orbital varieties of type $\lambda$ will be denoted $\cX(\lambda)$. 
+% 
 \begin{theorem}(\cite[Theorem~4.8.2]{dthesis})
-    \label{pr:govsasirrecs}
-    $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$ is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
+\label{pr:generalized orbital varietiesasirrecs}
+    % $\{X\in\cX(\lambda):X\subset\TT_\mu\}$ 
+    $\{X(\tau) : \tau \in YT(\lambda)_\mu \}$
+    is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
 \end{theorem}
-%
-
-% \jcom{Please add a reference to your paper here and also a lemma which states that under the Mirkovi\'c--Vybornov isomorphism $ \mathring X(\tau) $ is mapped isomorphically onto $ \mathring Z(\tau) $.}
-% 
-Our goal is to describe the fusion of two MV cycles using ``fusion'' of generalized orbital varieties, which we will now define. 
-% \acom{So we \textit{are} calling this a fusion?} \jcom{I think that you used this word already here.  I just reorganized your sentence.} \acom{I agree, but I thought that you were opposed, Joel.}
-% 
+
+% 
+Our next goal is to describe the fusion of two MV cycles using a ``fusion'' of generalized orbital varieties, which we will now define. 
 Let $\lambda,\lambda',\lambda''$ and $\mu, \mu',\mu''$ be as in previous sections, once again assuming that $\mu$ is dominant.
-% \jcom{I think that this is can move earlier, with the caveat that I mentioned earlier about $ \mu $ being non-dominant in 6.1 and dominant here.} \acom{Yes.} \acom{But we only start to need the primes now.}
-
-% 
-Given $s\in\Ax$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
+%
+
+Given a point $s\in\Ax$ and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
 % 
 \begin{equation*}
-    \mathring X(\tau',\tau'')_{0,s} 
-    % X(\tau')\ast_s \mathring X(\tau'') 
-    = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} 
-    \text{ has Jordan type } ((\lambda'(i), 0), (\lambda''(i), s))
-    % \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} 
-    \text{ for } i=1,\dots,N\right\}
+    \mathring X(\tau',\tau'')_{0,s} = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} 
+    \text{ has Jordan type } ((\lambda'(i), 0), (\lambda''(i), s)) \text{ for } i=1,\dots,m\right\}
 \end{equation*}
-% 
-% \jcom{Maybe instead write ``$A \big|_{\CC^{|\mu(i)|}}$ has Jordan type $ (\lambda'(i), 0), (\lambda''(i), s)$} \acom{Okay. So no need for the first paragraph of this section?}
 % 
@@
 \begin{equation*}
-        % X(\tau')\ast_{\AA^\times} X(\tau'') = 
     \mathring X(\tau',\tau'')_{0,\AA^\times} = 
@@
 Note that elements $A\in\mathring X(\tau',\tau'')$ do not in general correspond to pairs $(A',A'')\in\mathring X(\tau')\times X(\tau'')$ because if $\mu'$ (resp.\ $\mu''$) is not dominant then $X(\tau')$ (resp.\ $X(\tau'')$) is not well-defined.
-% The space we have defined may therefore not be a true fusion in the sense that it may not come from two obvious spaces. \acom{Joel?} 
-% \jcom{Even if $ \mu', \mu'$ are dominant, it is not obvious how $ A $ corresponds to a pair $(A', A'')$.
-And since I don't think that ``true fusion'' is a well-defined thing, I think that we can delete the last sentence.}
-% \acom{Ok. By choosing bases of generalized eigenspaces?}
-
-% 
-% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
-% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
-% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}.
-Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing.
-May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s..
-which is ok, as in not a loss of generality.
-Still..}
-% 
-% \jcom{Now that we have $ \ast_s$ defined in the fusion section, we can refer to that here.}
-%Recall the map $\theta : \Gr_{0, \AA^\times} \rightarrow \Gr \times \Gr$ from \Cref{ss:affgrs}. 
+% 
 \begin{proposition}
@@
     The image of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_{\AA^\times} \mathring Z(\tau'')$. 
-    % \[
-    % \overline{\phi(X(\tau',\tau''))} 
-    % = Z'\ast_s Z'' \,. 
-    % \]
 \end{proposition}
 %
-% \jcom{Do you want the ``blocky'' or ``boxy'' description here?
-I mean, do you want $ i = 1, \dots, N$ or $ i =1, \dots, m$?
-I'm not so sure that ``boxy'' will work, since with those $s$ in the matrix, it doesn't preserves all the $ \CC^i$.}
-
-% \acom{Fixed.}
-
-%\jcom{We never quite defined $\mathring Z(\tau')\ast_{\AA^\times} \mathring Z(\tau'')$ so maybe we should write this down somewhere.
-Once we do this, I'm pretty sure that we will not get ``dense'' but an equality.}
-
-%\acom{Should we just use $\tau^{-1}(\mathring Z(\tau') \times \mathring Z(\tau''))$ instead?}
-
-%\jcom{Yes, maybe that is a good idea.
-We should recall $ \tau $, and I suppose since we have two $ \tau$s, we had better change notation.
-Maybe we can use a different letter for the $\tau$ used to define fusion and keep $ \tau $ for tableau.}
-
-% \acom{Changed it to $\theta$ \emoji{worried}}
-% \jcom{I went ahead and defined $ \ast_\Cx$ in the fusion section so now we can use it.}
-% \acom{TYVM}
 
@@
 Let $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denote the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
-% \acom{Probably don't need to repeat this.}
 
@@
 So, $l \in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$ by \Cref{th:OTGrW}.
-On the other hand, 
-% also by definition of $\UU^{\mu',\mu''}_{0,\AA}$, we have 
-since $L\in S^{\mu',\mu''}_{0,s}$, $l\in S^{\mu'(i),\mu''(i)}_{0,s}$.
+On the other hand, since $L\in S^{\mu',\mu''}_{0,s}$, $l\in S^{\mu'(i),\mu''(i)}_{0,s}$.
 
@@
 $L\in\mathring Z(\tau')\ast_s \mathring Z(\tau'')$, we can write $ L = g(A)\CC[t]^m$ by  \Cref{th:OGrl}. Then reversing the above logic, we conclude that $ A \in \mathring X(\tau',\tau'')_{0,s}$.
-% \theta^{-1}(\mathring Z(\tau')\times Z(\tau''))$.
-% 
-% For the converse we use the fact that the map $A\mapsto g(A)$ is an isomorphism of $\overline{\OO}^{\lambda',\lambda''}_{0,\AA}\cap\UU^{\mu',\mu''}_{0,\AA}$ and $\overline{\Gr}^{\lambda',\lambda''}_{0,\AA}\cap S^{\mu',\mu''}_{0,\AA}$ which restricts to an isomorphism of generalized orbital varieties and MV cycles in fibres.
-% \acom{Better way to say?} \jcom{I think that you can just rewrite this first half as if and only if and drop the second half. }
-% Given $L\in\mathring Z(\tau') \ast_{\AA^\times}\mathring Z(\tau'')$ let $A$ be such that $L = g(A)\CC[t]^i$. \acom{But, is it clear that $A\in\mathring X(\tau',\tau'')_{0,s}$?} 
-% Do we need that there exists $(A',A'')\in M_{N'}\times M_{N''}$ such that $L(0) = g(A')\cO^m$ and $L(s) = g(A'')\cO^m$, and that we could take $A'\oplus A''=A$ up to some conjugation that puts $A'\oplus A''\in\TT_\mu$ which is possible because $\TT_\mu$ intersects $\OO^{\lambda',\lambda''}_{0,\AA}$ transversely?
 \end{proof}
@@
 
-Now, in analogy with the geometric fusion of \Cref{ss:fuscon}
-% \acom{add loc cit} \jcom{I think just add a reference our fusion section} \acom{Yeah that's what I meant, taking loc cit literally}
-we define $X(\tau', \tau'')_{0,0} $ to be the zero fibre of the Zariski closure of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ in $M_N \times\AA$.
+Now, in analogy with the fusion of \Cref{ss:fuscon} we define $X(\tau',\tau'')_{0,\AA}$ to be the Zariski closure of the unique top-dimensional component of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ in $M_N \times\AA$.
+(As noted in \cref{rem:irreducible}, we expect that all these varieties $ \mathring X(\tau) \cong \mathring Z(\tau) $ are irreducible, which would mean that taking this ``top-dimensional component'' irrelevant.)  Then we define the fusion of generalized orbital varieties to be the scheme-theoretic intersection
+$$ X(\tau', \tau'')_{0,0}  = X(\tau',\tau'')_{0,\AA} \cap M_N \times \{0\} \text{ in $M_N \times\AA$} $$
 By \Cref{prop:adjoint}, it is contained in $\overline\OO^\lambda\cap\TT_\mu\cap\n$.
-%so by Theorem 4 its irreducible components are generalized orbital varieties. 
-%\jcom{I removed the last part because maybe it has smaller dimensional components and anyway, I don't think that it is relevant}
-
-We quickly recall the
-definition of intersection multiplicity that we will need following \cite[Eg. 2.6.5]{Fulton}. We consider a fibre square of $\CC$-schemes
+
+We quickly recall the definition of intersection multiplicity that we will need following \cite[Example~2.6.5]{fulton2016intersection}. We consider a fibre square of $\CC$-schemes
 $$
@@
 $$
-with $i$ the inclusion of an effective Cartier divisor and $V$ an
+with $D $ an effective Cartier divisor and $V$ an
 irreducible variety of dimension $k$. We assume that $V$ is not contained
@@
 it is a subvariety of $V$ of codimension $1$. The \textbf{multiplicity}
-of $Z$ in the product $D\cdot V$ is defined to be the length of the
+of $Z$ in the intersection $D\cap V$ is defined to be the length of the
 module $\mathcal O_{V,Z}/(f)$ over the local ring $\mathcal O_{V,Z}$
 of $V$ along $Z$, where $f$ is a local equation of $D|_V$ on an affine
-open subset of $V$ which meets $Z$. Following \cite[chap.~7]{Fulton},
+open subset of $V$ which meets $Z$. Following \cite[chap.~7]{fulton2016intersection},
 this multiplicity is denoted by $i(Z,D\cdot V)$.
@@
 For $ Z', Z'' $ subvarieties of $ \Gr $, $V = Z'\ast_\AA Z''\subset\Grbd$ is a variety not contained in the support of $D$.
-Then we choose an irreducible component $Z$ of $W := D \cap V = X\ast_0 Y$.
-Thus, we may consider the intersection multiplicity $ i(Z, X \ast_0 Y) := i(Z, D \cdot V)$.
+Then we choose an irreducible component $Z$ of $W := D \cap V = Z'\ast_0 Z''$.
+Thus, we may consider the intersection multiplicity $ i(Z, Z'\ast_0 Z'') := i(Z, D \cdot V)$.
 We will be particularly interested in the case when $ Z, Z', Z''$ are MV cycles.
 
-In a similar way, we may consider the intersection multiplicities of a generalized orbital variety $ X$ in $X(\tau', \tau'')_{0,0} = M_N \times \{0\} \cap X(\tau', \tau'')_{0, \AA}$.
+In a similar way, we may consider the intersection multiplicities of generalized orbital varieties in $X(\tau', \tau'')_{0,0} = M_N \times \{0\} \cap X(\tau', \tau'')_{0, \AA}$.
 \begin{corollary}
-\label{cor:iota}
-    % The image of $\mathring X(\tau',\tau'')_{0,0}$ in $\mathring Z(\tau')\ast_0 \mathring Z(\tau'')$ is dense. In particular 
-    $\iota(X(\tau), X(\tau',\tau'')_{0,0}) = \iota( Z(\tau), Z(\tau')\ast_0 Z(\tau''))\,.$
+\label{cor:intmul}
+    $i(X(\tau), X(\tau',\tau'')_{0,0}) = i( Z(\tau), Z(\tau')\ast_0 Z(\tau''))\,.$
 \end{corollary}
-%\acom{Do we need to introduce $X(\tau',\tau'')_{0,0}$ to state the theorem or can we state it on $\mathring X$'s and $\mathring Z$'s again?}
-%\jcom{I changed the statement. I will edit the proof later. }
-%
 
 \begin{proof}
-%[Proof of~\Cref{cor:iota}]
-%Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ and $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?} irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties.
-By the isomorphisms of \Cref{lem:XtZt} and \Cref{pr:XttZtt}, $X(\tau) $ is a dense constructible subset of $ Z(\tau) $ and $ X(\tau', \tau'')_{0,\AA} $ is a dense constructible subset of $ Z(\tau') \ast_\AA Z(\tau'') $.
+By the isomorphism of \Cref{lem:XtZt}, $X(\tau) $ is a dense constructible subset of $ Z(\tau) $.
+On the other hand, \Cref{pr:XttZtt} gives us an identification of $ \mathring X(\tau',\tau'')_{0, \Ax}$ and $ \mathring Z(\tau') \ast_{\Ax} Z(\tau'')$; the schemes $ X(\tau', \tau'')_{0,\AA} $ and $ Z(\tau') \ast_\AA Z(\tau'') $ are constructed from these by taking the top-dimensional irreducible component and then closure.
+Thus, we conclude that $ X(\tau', \tau'')_{0,\AA} $ is a dense constructible subset of $ Z(\tau') \ast_\AA Z(\tau'') $.
 From the definition of intersection multiplicity, it is clear that the multiplicity can be computed locally and so the result follows.
-%  
-% \acom{Hm, I guess you are right, it is easier than what I had, we just need that the arguments on either side match up, and not that the arguments on one side are related.
-Though do we really not use that $X(\tau)$ may be contained in $X(\tau',\tau'')_{0,0}$ as an irreducible component?}
 \end{proof}
 %
-\acom{This conjecture comes out of nowhere}
-\begin{conjecture}
-    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
-    Let $\tau$ be the tableau got by taking the union of the rows of $\tau'$ and $\tau''$ and ordering the entries in each row smallest to largest. 
-    % Note that $\tau$ has shape $\lambda$, weight $\mu$, and  Lusztig datum equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
-    Then 
-    \begin{equation}
-        \iota(Z(\tau), Z(\tau') \geofu Z(\tau'')) = 1 \,. 
-    \end{equation}
-\end{conjecture}
-% 
-% RESOLVED COMMENTS
-% \jcom{Rather than adding the Lusztig data, how can you produce $\tau$ directly from $\tau', \tau''$?
-I guess you can just add the GT patterns, so for tableaux you just take the union of the rows, is that right?}
-% 
-% \acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
-% 
-\subsection{Representations in $\CC[N]$}
+
+% 
+\subsection{Multiplying MV basis elements in \texorpdfstring{$\CC[N]$}{C[N]}}
 \label{ss:CN}
 % 
-% \jcom{
-% Maybe we need a word about Langlands duality here.  Since we are working with $ GL_m$, it is not really necessary, but it would be nice to point this out.  
-% Also a general comment: maybe it would be best to first talk about multiplication in $\CC[N]$ incl.
-Theorem 7.11 from mvbasis, and then talk about cluster algebras.
-Right now, it is a bit confusing, since we go back and forth.
-Also some of the motivation stuff about the semicanonical basis, etc, will be moved to the intro.
-% }
-In this section we will need to recall that representations of the Langlands dual group $G^\vee$ of an arbitrary complex reductive group $G$ can be constructed from the affine Grassmannian of $G$, and studied in $\CC[N^\vee]$ the ring of functions on the maximal unipotent subgroup $N^\vee$ of $G^\vee$.
-%
-
-We use the convenient fact that $\GL_m^\vee = \GL_m$ and ignore the distinction between weights and coweights.
-
-%referring to points $t^\lambda$ as coweights for $\lambda\in\ZZ^m$ weights. 
-%
-
-\acom{So far we have been saying ``coweight'' $\lambda$, etc. We could say coweight for $t^\lambda$ and weight for $\lambda$ starting now?}
-% \acom{Also, maybe add a warning that some of the theorems we rely on hold more generally? Like the MV basis theorem..} \jcom{I don't think that is necessary.}
-
-Let $N\subset\GL_m$ be the unipotent subgroup of upper-triangular matrices with 1s on the diagonal.
+In this section we will need to recall that representations of the Langlands dual group $G^\vee$ of an arbitrary complex reductive group $G$ can be constructed from the affine Grassmannian of $G$, and studied in $\CC[N^\vee]$, the ring of functions on the maximal unipotent subgroup $N^\vee$ of $G^\vee$.
+%
+
+We use the convenient fact that $\GL_m^\vee = \GL_m$ (so also $N^\vee = N$) and ignore the distinction between weights and coweights.
+
+Let $N\subset G$ be the unipotent subgroup of upper-triangular matrices with 1s on the diagonal.
 In \cite{baumann2019mirkovic} the third author along with Baumann and Knutson show that the MV cycles yield a basis of the coordinate ring $\CC[N]$ called the MV basis.
-Note that with respect to the action of the maximal torus $T$ of $\GL_m$ by conjugation on $N$, $\CC[N]$ acquires a homogeneous grading by $Q_+$.
-% 
-% First note that with respect to the adjoint action of $T$ on $N$, $\CC[N]$ is graded by the set $-Q_+$ of nonpositive integer linear combinations of positive roots. 
-%
-
-Given weights $\mu\le\lambda$ with $\lambda$ dominant, denote by $V(\lambda)$ the irreducible representation of $\GL_m$ of highest weight $\lambda$ and by $V(\lambda)_\mu$ its $\mu$-weight space. 
+Note that with respect to the action of the maximal torus $T$ of $G$ by conjugation on $N$, $\CC[N]$ acquires a homogeneous grading by $Q_+$.
+%
+
+Given weights $\mu\le\lambda$ with $\lambda$ dominant, denote by $V(\lambda)$ the irreducible representation of $G$ of highest weight $\lambda$ and by $V(\lambda)_\mu$ its $\mu$-weight space. 
 There is an injective map $ \Psi_\lambda: V(\lambda) \to \CC[N]$ realizing $V(\lambda)$ as a subspace of $\CC[N]$ and sending $ V(\lambda)_\mu$ to $\CC[N]_{\mu - \lambda}$.
 
-The geometric Satake correspondence says that 
-% $V(\lambda) = IH(\overline\Gr^\lambda)$ and  
-$V(\lambda)_\mu = H_{2\rho(\lambda-\mu)}(\overline{\Gr^\lambda\cap S^\mu_-})$ where $H_d$ denotes $d$-dimensional Borel--Moore homology.
+The geometric Satake correspondence says that $V(\lambda)_\mu = H_{2\rho(\lambda-\mu)}(\overline{\Gr^\lambda\cap S^\mu_-})$.
 In particular, the set $\{[Z] : Z\in\cZ(\lambda)\}$ gives a basis of $V(\lambda)$ with $[Z]$ denoting the class of $Z$ in the appropriate homology group.
-
-% \acom{Warning!
-Earlier we defined the MV cycles as irreducible components of $\overline{\Gr^\lambda}\cap S^\mu$} \jcom{Good point.
-We should be consistent.
-I will think about the best way to fixe this and correct it.}
-% 
-% In particular, the MV cycles in $\overline{\Gr}^\lambda$ of coweight $\mu\le\lambda$ give a basis of $V(\lambda)$. 
-%
-
+%
+
+By a theorem of Anderson, MV cycles in $\overline{\Gr^\lambda\cap S^{\nu + \lambda}_-}$ consist of those irreducible components of $ \overline{S^\lambda_+ \cap S^{\lambda+\nu}_-} $ that are contained in $\overline\Gr^\lambda$ \cite[Proposition~3]{anderson2003polytope}.
 The \new{stable} MV cycles of coweight $\nu\in Q_+$ are defined to be irreducible components of $\overline{S^0_+ \cap S^\nu_-}$.
 Multiplication by $ t^\lambda $ defines an isomorphism $\overline{S^0_+ \cap S^\nu_-} \cong \overline{S^\lambda_+ \cap S^{\lambda+\nu}_-} $.
-By a theorem of Anderson, MV cycles in $\overline{\Gr^\lambda\cap S^{\nu + \lambda}_-}$ consist of those irreducible components of $ \overline{S^\lambda_+ \cap S^{\lambda+\nu}_-} $ that are contained in $\overline\Gr^\lambda$ \cite[Proposition~3]{anderson2003polytope}.
 We denote the set of all stable MV cycles $\cZ(\infty)$.
-% Recall that MV cycles can be described combinatorially by Lusztig data. 
-By a theorem of the third author, given a choice a reduced word for $ w_0 $, there is a bijection $ \cZ(\infty) \rightarrow \NN^{\Delta_+} $ called the Lusztig datum.
+% 
+By a theorem of the third author, given a choice a reduced word for $ w_0 $, there is a bijection $ \cZ(\infty) \rightarrow \NN^{r} $ called the Lusztig datum.
 For our purposes we will always use the standard reduced word.
-
-%a stable MV cycle is uniquely determined by its Lusztig datum and the sets $\cZ(\infty)$ and $\NN^{\Delta_+}$ are in bijection. 
-% Recall that Lusztig data, like elements of $\CC[N]$, are weighted by $Q_+$. 
+% \acom{As mentioned above we kind of already said this last bit in \Cref{ss:mvcs}}
+% \jcom{I think that I reduced the duplication a bit now.}
+
 One can string together the maps $\Psi_\lambda$ and the geometric Satake isomoprhisms to show that the stable MV cycles yield a basis of $\CC[N]$.
@@
 \begin{theorem}
-    (A special case of \cite[Proposition~6.1]{baumann2019mirkovic})
+(\cite[Proposition~6.1]{baumann2019mirkovic})
     For each $Z\in\cZ(\infty)$ there is a unique element $b_Z\in\CC[N]$ such that for any dominant weight $\lambda$, if $t^\lambda Z\in\cZ(\lambda)$ then $\Psi_\lambda([t^\lambda Z]) = b_Z$.
 \end{theorem}
+% 
 The set $ \{b_Z : Z \in \cZ(\infty) \}$ is called the \new{MV basis} of $ \CC[N]$.
-% \jcom{I took the definition out of the theorem statement.}
-% \acom{Ok}
-% 
-Furthermore, the structure constants of multiplication in $\CC[N]$ with respect to the MV basis are given by intersection multiplicities. 
+The structure constants of multiplication in $\CC[N]$ with respect to the MV basis are given by intersection multiplicities.
 % 
 \begin{theorem}
-    (A special case of \cite[Theorem~7.11]{baumann2019mirkovic}) Given $Z',Z''\in\cZ(\infty)$, 
-    % of coweight $\nu',\nu''$ respectively 
-$$
-b_{Z'}\arfu b_{Z''} = \sum_{Z\in\cZ(\infty)} \iota\left(Z, Z' \geofu Z''\right) b_Z 
-$$
+(\cite[Theorem~7.11]{baumann2019mirkovic}) 
+    Given $Z',Z''\in\cZ(\infty)$, 
+\begin{equation}
+\label{eq:btimesb}
+    b_{Z'}\arfu b_{Z''} = \sum_{Z\in\cZ(\infty)} i\left(Z, Z' \geofu Z''\right) b_Z 
+\end{equation}
 in $\CC[N]$. 
-% \acom{The summation is finite since 7.1?... Don't want to introduce the notation $\cZ(\infty)_\nu$ if we can avoid it.} \jcom{The sum is finite for weight reasons.} 
-% 
 \end{theorem}
-% \jcom{I would take the second part ``Moreover'' out of the statement of the theorem and state it as a corollary, maybe after Prop 7.3.}
-% \acom{Done}
-% 
-% \jcom{This paragraph is a bit confusing.
-Maybe it would be best to first define $ V(\lambda) \rightarrow \CC[N]$ and then $ H_{top}(\overline{Gr}^\lambda \cap S^\mu) \rightarrow \CC[N]$, rather than doing them in one step.
-Then we can draw a commutative square with $ S^0_+ \cap S_-^\nu$ as well.
-}
-% \acom{Not sure which square to draw or if it is necessary.
-I guess you want something like what's pictured below, where what we're about to describe are the blue arrows.
-Specifically the rightmost downward pointing blue.
-Which, by commutativity, will determine the middle downward pointing blue.}
-% \jcom{Yes, I like this diagram.  Maybe the two rightward arrow should point leftward, since we did already define $ \tau \mapsto Z(\tau)$.}
-%
-
-In \Cref{s:examples} we will identify elements $b_Z$ with certain \textit{minimal} tableaux (instead of Lusztig data) and view $\CC[N]$ as an algebra in these tableaux, rewriting (abbreviating) \Cref{eq:multingovs} as as equation in semistandard Young tableaux.
-We can do this because of 
-% Before we describe how to choose representative generalized orbital varieties in order to expand a product of MV basis elements 
-% $b_{Z'}\arfu b_{Z''}$
-% in $\CC[N]$ we summarize our approach in 
-the following commutative diagram. 
+Our next goal is to show that these structure constants can be computed using generalized orbital varieties. Consider the following commutative diagram.
 \[
 \begin{tikzcd}
-   \bigcup YT(\lambda)_+\ar[r,"\tau\mapsto X(\tau)"] & \bigcup \mathcal X(\lambda) & \\
-   \bigcup YT(\lambda) \ar[r,"\tau\mapsto Z(\tau)"] \ar[d,"n_\bullet"] & \bigcup\cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & \bigcup L(\lambda) \ar[d, "\Psi_\lambda"] \\ %  description
-    \NN^{\Delta_+} \ar[r] \ar[u,dashed,bend left,"\sigma_\lambda"] & \cZ(\infty) \ar[r] & \CC[N]
+    YT_+ \ar[r,"\tau\mapsto X(\tau)"]\ar[d,hook] & \bigcup \mathcal X(\lambda) \ar[d,hook,"\text{\Cref{lem:XtZt}}"] & \\
+    YT      \ar[r,"\tau\mapsto Z(\tau)"] \ar[d,"n_\bullet"] & \bigcup\cZ(\lambda) \ar[r] \ar[d, "t^{-\lambda}"] & \bigoplus V(\lambda) \ar[d, "\Psi_\lambda"] \\ 
+    \NN^{r} \ar[r] \ar[u,dashed,bend left,"\sigma"]         & \cZ(\infty) \ar[r]                                & \CC[N] 
 \end{tikzcd}
 \]
-\acom{Should I adjust the diagram so that its from unions over $\lambda$}
-\jcom{I think so.
-Also somewhere we should indicate that the map $YT(\lambda) \rightarrow Z(\lambda) $ takes $ \tau $ to $ Z(\tau)$.
-In principal we could increase the size of this diagram and include somehow the map taking ``dominant tableaux'' to generalized orbital varieties, but I don't see how to do this without making it unwieldly.}
-
-Two tableaux have equal Lusztig data if they differ by any number of boxes of weight $r$ in row $r$ for any $r$.
-We call this relation \new{padding}.
-In other words, the fibres of $n_\bullet$ contain tableaux related by padding.
-For example $\young(2,4)$ and $\young(112,24,3)$ have equal Lusztig data.
-
-While $Z(\tau)$ is defined even when $\mu$ is not dominant, $X(\tau)$ is not.
-To compute intersection multiplicities using generalized orbital varieties we therefore need to choose a section $\sigma_\lambda$ of $n_\bullet$ with image in the set of tableaux having dominant weight.
-%
+
+The sequence $\mu^0 = (\mu^0_1,\dots,\mu^0_{m-1})$ keeping track of the number of boxes of weight $i$ in row $i$ of a given tableau is called its \new{padding}. 
+Two tableaux have equal Lusztig data if and only if they are related by padding, which is to say that we can change the padding of one (removing or adding boxes) to recreate the other.
+Moreover, a tableau is completely determined by its Lusztig datum and padding.
+
+For example 
+$$
+    \bar \tau = \young(2,4) \quad \text{ and} \quad \tau = \young(112,24,3)
+$$ 
+have equal Lusztig data, since we can increase the padding of $\bar\tau$ (by adding to it the padding of $\tau$) to get $\tau$, or forget the padding of $\tau$ to get $\bar\tau$.
+
+We call a tableau \new{stable} if its padding cannot be decreased. The following lemma shows that stable tableaux are in bijection with Lusztig data.
 
@@
 \label{lem:almostmintab}
-Let $n_\bullet = (n_{(a,b)})$ be a Lusztig datum of coweight $\nu$ viewed as a strictly lower-triangular $m\times m$ matrix with 
-% $(w,r)$
-$(a,b)$th entry equal to the number of boxes of weight $a$ in row $b$ for $1\le b < a \le m$. 
-Let $\mu^0$ be a diagonal matrix with $a$th diagonal entry denoted $\mu^0_a$. The solution to the minimization problem 
-\[
-\text{minimize }\mu^0\text{ such that } \lambda = (\sum_b n_{(a,b)} + \mu^0_b)_a \text{ and } \mu = (\sum_a n_{(a,b)} + \mu^0_a)_b
-% sum rows and sum columns
-\text{ are dominant effective}
-\]
-is 
-\[
+Let $n_\bullet = (n_{(a,b)})$ be a Lusztig datum and let $\mu^0 = (\mu^0_i)$ be a padding.
+If $\lambda = (\sum_b n_{(a,b)} + \mu^0_a)_a $ then the smallest $\mu^0$ such that $\lambda$ is dominant effective (and $\mu$ is effective) is:
+$$
 \begin{gathered}
-    \mu^0_{m} = 0 \\ 
-    \mu^0_{m-1} = \max\{0 , \sum n_{m,c} - \sum n_{m-1,c}\} \\ 
-    \mu^0_i = \max\{0, \mu^0_{i+1} + \sum n_{i+1,c} - \sum n_{i,c} , \mu_{i+1}^0 + \sum n_{r,i+1} - \sum n_{r,i}\}
+        \mu^0_{m}, \mu^0_{m-1} = 0 \\
+        \mu^0_i = \max\{0, \mu_{i+1}^0 + \sum_a n_{(a,i+1)} - \sum_a n_{(a,i)}\} \quad i = 1,\dots,m-2
 \end{gathered}
-\]
-for $i = 1,\dots,m-2$. 
+$$
+This choice of $\mu^0$ defines a section $\sigma:\NN^{r} \to YT$.
 \end{lemma}
-
-In words, if we wish to produce a dominant weight tableau with Lusztig datum $n_\bullet$ of smallest possible shape and weight 
+% 
+\begin{proof}[Proof sketch.]
+To produce a tableau with Lusztig datum $n_\bullet$ of smallest possible shape and weight:
 \begin{itemize}
-        \item we can always take the number of $m$'s in row $m$ to be zero; 
-        \item we can take the number of $m-1$'s in row $m-1$ to be zero, unless $n_\bullet$ tells us that there are more $m$'s the first $m-1$ rows than there are $m-1$'s in the first $m-2$ rows, and in that case we take $\mu^0_{m-1}$ so that it exactly offsets the difference;
-        \item we can take the number of $m-2$'s in row $m-2$ to be zero, unless $n_\bullet$ tells us there are more $m-1$'s in the first $m-1$ rows (building off the last step) than there are $m-2$'s in the first $m-3$ rows, or, that there are more boxes in row $m-1$ than there are in row $m-2$, and then we take $\mu^0_{m-2}$ to offset the minimum of the two differences;
-        \item induct up to $\mu^0_1$. 
+    \item we can always take the number of $m$'s in row $m$, and the number of $m-1$'s in row $m-1$ to be zero; 
+    \item we can take the number of $m-2$'s in row $m-2$ to be zero, unless $n_\bullet$ tells us that there are more boxes in row $m-1$ than there are in row $m-2$, and then we take $\mu^0_{m-2}$ to offset the difference;
 \end{itemize}
-
-[Proposition]
-
-To write down an expansion in $\CC[N]$ we choose a section $\bar\sigma_\lambda$ valued in smallest (not necessarily dominant) representative tableaux.
-
-% \jcom{In principle, the notation $ Z' \ast_0 Z''$ has been defined, since we defined the fusion of any two subschemes of $ \Gr$.
-We should just note that the fusion of the stable MV cycles matches the fusion of MV cycles after translation by $ t^\lambda$.
-I don't think that $ \iota$ has been defined anywhere, has it?}
-
-% \begin{lemma}
-%     \label{lem:mintab}
-%     Let $n_\bullet$ be a Lusztig datum of coweight $\nu$.
-There exist $\lambda,\mu$ dominant effective smallest such that $n_\bullet$ is the Lusztig datum of a tableau $\tau\in YT(\lambda)_\mu$.
-They are determined by the following minimization problem.
-Regard $n_\bullet$ as a strictly lower triangular matrix with $(r,c)$th entry $n_{r,c}$ is equal to the number of boxes of weight $r$ in row $c$ of $\tau$.
-Note that since $r > c$ this data does not account for the number of boxes of weight $r$ in row $r$.
-Let $\mu^0$ be the diagonal matrix whose $(r,r)$th entry $\mu^0_r$ is equal to the number of boxes of weight $r$ in row $r$ of $\tau$.
-Note that the sum of the rows of $n_\bullet + \mu^0$ is the shape $\lambda$ of $\tau$, and the sum of the columns of $n_\bullet + \mu^0$ is the weight $\mu$ of $\tau$.
-The solution to the minimization problem
-%     \[
-%         \begin{gathered}
-%         % 
-%         \text{minimize }\mu^0\text{ such that} \\
-%         % \text{the sum of the rows of }n_\bullet + \mu^0\text{ is non-increasing},
-%         % \text{the sum of the columns of }n_\bullet + \mu^0\text{ is non-increasing}
-%         \text{both }\lambda,\mu\text{ are non-increasing}
-%         \end{gathered} 
-%     \]
-%     is got recursively from % setting $\mu^0_m = 0$, 
-%     \[
-%         \begin{gathered}
-%             \mu^0_{m} = 0 \\ 
-%             \mu^0_{m-1} = \max\{0 , \sum n_{m,c} - \sum n_{m-1,c}\} \\ 
-%             \mu^0_i = \max\{0, \mu^0_{i+1} + \sum n_{i+1,c} - \sum n_{i,c} , \mu_{i+1}^0 + \sum n_{r,i+1} - \sum n_{r,i}\}
-%         \end{gathered}
-%     \]
-%     for $i = 1,\dots,m-2$. 
-% \end{lemma}
-
-\begin{proposition}
-    \label{prop:minwts}
-    Given two Lusztig data $n_\bullet',n_\bullet''$ there is a smallest choice of effective coweights $\mu',\mu''$ and effective dominant coweights $\lambda',\lambda''$ such that $\mu = \mu' + \mu''$ is effective dominant and $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ have the prescribed Lusztig data.
-They are got by choosing the minimum $\lambda,\mu$ for $n_\bullet = n_\bullet ' + n_\bullet ''$ afforded by \Cref{lem:mintab}, and then breaking off $n_{r,c}'$ boxes of weight $r$ from each row $c<r$ of $\tau$ to form a $\tau'_0$ an intermediate tableau.
-If $\tau'_0$ is of an acceptable shape then we keep it.
-If it is not, then we correct it by padding it using some boxes of weight $r$ in row $r$ of what remains of $\tau$.
-
-    \acom{Grrr, padding might not work.}
-
-    \acom{To be completed. We require a notion of ``smallest'' pair of factor tableaux associated to a given tableau --- that is if we care to include our $B(\infty)\to B(\lambda)$ map. 
-    As the examples show, there may be more than one way to break up a ``minimal'' tableau for $n_\bullet = n_\bullet ' + n_\bullet ''$ into two tableaux with data $n_\bullet' $ and $n_\bullet''$ resp.\ The practical notion of min is such that the generalized nonzero eigenspace has the smallest possible dimension.}
-    \acom{Reference Claxton--Tingley multisegments, Hong--Lee marignally large tableaux for comparison.}
-\end{proposition}
-
+and iterate the last step up to $\mu^0_1$. 
+\end{proof}
+% 
 \begin{corollary}
-Moreover, there exist $\lambda',\lambda''$ dominant effective and a pair of tableaux $(\tau',\tau'')\in YT(\lambda')\times YT(\lambda'')$ such that 
+\label{cor:goodreps}
+Given two stable MV cycles $Z',Z''$ with Lusztig data $n_\bullet',n_\bullet''$ resp.\ there exists a pair of tableaux $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ for some $\lambda',\lambda''$ dominant effective and some $\mu',\mu''$ effective, such that $\mu = \mu' + \mu''\le \lambda = \lambda' + \lambda''$ are partitions and
 \begin{equation}
-    \label{eq:multingovs}
-    % b_{Z'} \arfu b_{Z''} = \sum_{Z\in\cZ(\lambda)} \iota (Z, Z(\tau')\geofu Z(\tau''))b_{t^{-\lambda}Z}
-    b_{Z'} \arfu b_{Z''} = \sum_{\tau\in YT(\lambda)} \iota (X(\tau), X(\tau',\tau'')_{0,0})b_{t^{-\lambda}Z(\tau)}
+    \label{eq:multingeneralized orbital varieties}
+    b_{Z'} \arfu b_{Z''} = \sum_{\tau\in YT(\lambda)} i (X(\tau), X(\tau',\tau'')_{0,0})b_{t^{-\lambda}Z(\tau)}
 \end{equation}
-% 
-for $\lambda = \lambda' + \lambda''$. 
 \end{corollary}
-
-\section{Cluster questions}
-\label{s:clusterqus}
-% 
-For initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word (length $r = \#\Delta_+$) in the Weyl group for $G$, each $x_i$ is a generalized minor  \cite{kato2011polytopal}, and hence
-% \acom{by BKK?}\rcom{I reworded it.} 
-is in the MV basis. 
-% as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
-\acom{what's the subscript $r$?
-also what're the last 2 citations for?
-Neither BFZ nor GLS link generalized minors and MV cycles}
-If the reduced expression satisfies a special condition, then cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
-
-Conversely, suppose we have a seed $(x_1,\dots,x_r)$ such that each $x_i$ is in the MV basis, i.e.\ for each $i$ there exists a stable MV cycle $Z_i$ such that $x_i = b_{Z_i}\in\CC[N]$.
-To show that all cluster variables
-% \acom{for this seed?}\rcom{No, all of them.} 
-are also in the MV basis it suffices to show that if $x_i$ is mutable then its mutation $x_i^*$ is also in the MV basis. This observation is based on the exchange relation:
-\[
-    x_i x_i^* = x_+ + x_- 
-\]
-where $x_+,x_-$ are monomials in $ (x_1, \dots, x_r)\setminus x_i$ determined by the cluster structure on $\CC[N]$. 
-% \acom{the structure of interest?
-or are all cluster structures on this ring the same?} \rcom{The structure is derived from an initial seed coming from a reduced word {\bf i}.
-Each of these are equivalent to each other.}
-So if we can find a stable MV cycle $Z_i^*$ such that $b_{Z_i}b_{Z_i^*} = x_+ + x_-$ for each $i$ then we will have checked the conjecture. 
-% \acom{And we do not need to assume the special condition of BGL?}\rcom{They deal with cluster monomials in certain clusters while this deals with all cluster variables, so neither one completely implies the other.}
-
-The following examples give evidence that the mutation $x_i^*$ is in the MV basis. \acom{Roger, reword?}\rcom{Something like this?} \acom{Sure!}
-
-% \jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
-% \acom{Begun}
-
-Before we begin we will need some lemmas, notions and notations. 
-\begin{itemize}
-    \item we have only seen how to fuse ordinary MV cycles; to mutliply MV basis vectors which are indexed by stable MV cycles we'll therefore need a way to represent stable by ordinary; hence:
-    \item a notion/choice of fission 
-    \item the fission lemmas 
-    \item with lemmas in hand, a proposition: given $Z',Z''$ stable with LD... there exist $\tau',\tau''$ (min) such that $b_{Z'} b_{Z''} = b(\tau')  b(\tau'')$
-    \item a shorthand: in examples, instead of writing $Z(\tau)$ for the MV cycle corresponding to the tableau $\tau$ we will only the tableau $\tau$! 
-\end{itemize}
-
-% Let's wait for Gerhard before we discuss our computations any further
-% \subsection{Pseudocode}
-% 
-% \section{Cluster Algebras}
-% One of the main motivations for this paper is computing certain fusion products that are associated to exchange relations in the cluster algebra structure of $\CC[N]$. 
-% 
-% A basis of $\CC[N]$, called the dual semicanonical basis, was originally constructed in \cite{lusztig2000semicanonical} while a cluster algebra structure for $\CC[N]$ was shown in \cite{berenstein2005cluster3} and \cite{geiss2007initial}.
-% A natural question was whether the cluster monomials were elements of the dual semicanonical basis, proved in the positive in \cite{geiss2006rigid}.
-
-% Another basis for $\CC[N]$ was constructed in \cite{mirkovic2007geometric} called the MV basis.
-This basis is indexed by the MV cycles and the product of basis elements corresponds to the fusion product of the associated MV cycles.
-While this basis is different from the dual semicanonical basis, as shown in \cite{baumann2019mirkovic}, they seemed to share a lot of common elements, such as various cluster variables, which led to the following conjecture.
-
-% \begin{conjecture}\label{conj:cluster in MV}
-%     The cluster monomials of $\CC[N]$ are elements of the MV basis.
-% \end{conjecture}
-
-% Conjecture \ref{conj:cluster in MV} is known for type $A_n$, $n \leq 3$, as in this case, there is a unique biperfect basis for $\CC[N]$ \cite{baumann2019mirkovic}, so the dual semicanonical basis and MV basis are the same.
-
-% It has been shown in \cite{kato2011polytopal} that for initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word in the Weyl group for $G$, each $x_i$ is in the MV basis as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}.
-If the reduced expression satisfies a special condition, then the cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.
-
-% Suppose we have a seed $(x_1, \dots, x_r)$ where each $x_i$ is already in the MV basis.
-To show all the other cluster variables are in the MV basis, it suffices to show that for a mutable variable $x_i$, its mutation $x_i^*$ is also in the MV basis.
-The exchange relation corresponding to $x_i$ and $x_i^*$ is of the form
-% $$x_ix_i^* = x_+ + x_-$$
-% where $x_+$ and $x_-$ are monomials in the $x_j,j\neq i$. Let $Z_i$ be the MV cycle corresponding to $x_i$, so $x_i = b_{Z_i}$. If we are able to find an MV cycle $Z_i^*$ such that
-% $$b_{Z_i} b_{Z_i^*} = x_+ + x_-,$$
-% then this means $x_i^* = b_{Z_i^*}$ so it is in the MV basis with associated MV cycle $Z_i^*$. In Section \ref{s:denouement}, we present examples showcasing this is indeed true for type $A_3$.
-
+% 
+\begin{proof}
+Choose $\tau' = \sigma(n_\bullet')$, $\tau'' = \sigma(n_\bullet'')$ and suppose $\tau'\in YT(\lambda')_{\mu'}$, $\tau'' \in YT(\lambda'')_{\mu''}$. 
+Note that $Z'= t^{-\lambda'}Z(\tau'), Z'' = t^{-\lambda''} Z(\tau'')$ so the intersection multiplicity of a stable MV cycle $Z$ in $Z'\geofu Z''$ can be computed as the intersection multiplicity of an MV cycle $Z(\tau)$ in $Z(\tau')\geofu Z(\tau'')$ for some $\tau\in YT(\lambda)_\mu$, because these two situations isomorphic by translation by $ t^\lambda$.
+
+In case $\mu$ is not dominant, increase the padding of the larger of the two tableaux by $(\max(0,\mu_2-\mu_1),\max(0,\mu_3 - \mu_2),\dots,\max(0,\mu_m-\mu_{m-1}))$.
+
+Now, by \Cref{cor:intmul}, the intersection multiplicity of $Z(\tau)$ in $Z(\tau')\geofu Z(\tau'')$ can in turn be computed as the intersection multiplicity of the generalized orbital variety $X(\tau)$ in $X(\tau',\tau'')_{0,0}$.
+(We have ensured $ \mu $ is dominant, in order so that $X(\tau)$ will be defined.)
+\end{proof}
+% 
 \section{Examples}
@@
 
-% \acom{Plus fusion product of fake MV cycles for a fourth!}
-\acom{TODO: review/rewrite now that we have \S 6.2}
-We view MV cycles as semi-standard young tableaux.
-Suppose we have two tableaux $\tau'$ and $\tau''$, with respective weights $\lambda'$, $\mu'$ and $\lambda''$, $\mu''$, and we wished to take their fusion product.
-We consider a generic matrix $X \in \UU^{\mu',\mu''}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda',\lambda''}_{0,s}$.
-\acom{Relations dictated by $\tau$.
-Can mostly refer the reader to the previous section for this background, now.}
-
-Consider the subtableaux $\tau'(i)$ of $\tau'$ and $\tau''(i)$ of $\tau''$ where we take the boxes of $\tau'$ and $\tau''$ containing the numbers $1,\dots,i$.
-Let $\lambda'(i)$ and $\lambda''(i)$ be the corresponding sizes and $\mu'(i)$ and $\mu'(i)$ be the corresponding weights of the subtableaux.
-For each $i$, we obtain a corresponding submatrix $X_i \in \UU^{\mu'(i), \mu''(i)}_{0,s}$ of $X$.
-These subtableaux impose rank conditions, equivalently vanishing minors, on each $X_i$ when asking them to be in $\OO^{\lambda'(i), \lambda''(i)}_{0,s}$, which allows us to deduce relations on the variables in $X$.
-The relations must also include the new variables in the latest block and cannot have $s$ as a factor.
-
-To find the MV cycles, equivalently tableaux, in the $0$-fibre of the fusion, we consider the ring generated by all the variables of $X$ and quotient out the ideal generated by the relations from the vanishing minors as well as the minimal polynomial of $X$.
-We then add $s$ into the ideal.
-Each piece in the primary decomposition of this ideal will correspond to a tableaux, and subsequently a MV cycle.
-
-% \begin{example}
-% Let $G = \GL_3$ and consider the tableaux
-% $$\tau' = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau''=\young(13,2).$$
-
-% Lusztig data: $(010)$ for $\tau'$, $(101)$ for $\tau''$
-
-\acom{If we start with $n_\bullet ' = (0,1,0)$ and $n_\bullet'' = (1,0,1)$ then the smallest $\tau$ for $n_\bullet = (1,1,1)$ is $\young(1123,23)$ and hence the smallest $\mu,\lambda$ are $(2,2,2),(4,2,0)$.
-So far so good.
-However, the ``smallest'' ``fission'' of $\tau$ is $\young(112,23) , \young(3)$.
-We could define ``smallest'' to mean minimizing the dimension of the generalized $s$-eigenspace.
-What do you guys think?
-If we agree to do this we should amend this example.
-For Joel: this is an example where our $B(\infty) \to B(\lambda)$ does not match that of Claxton--Tingley (quoted in my thesis).
-They would get $\lambda = (3,1)$.
-I think that their map satisfies $\lambda$ dominant and $\mu$ such that each $\mu_i\ge 1$.}
-
-% Dimensions: $(1,0,-1)$ for both.
-
-% The MV cycles corresponding to $\tau'$ and $\tau''$ are both isomorphic to $\PP^2$.
-% The weights are $\lambda' = \lambda'' = (2,1,0)$ and $\mu' = \mu'' = (1,1,1)$. Hence the matrix in consideration is 
-% \[
-% X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
-%     0 & 1 & & & & \\
-%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 \\
-%      & & 0 & 1 & & \\
-%      & & & s & A_{23}^1 & A_{23}^2 \\
-%      & & & & 0 & 1 \\
-%      & & & & & s
-% \end{BMAT}
-% \right].
-% \]
-
-% For the first entry of $\mu'$ and $\mu''$, we have the following subtableaux to consider:
-% $$\young(1) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1).$$
-% Let $X_1$ be the top-left $2 \times 2$ submatrix of $X$. The subtableaux imposes the conditions $\dim \ker X_1 = 1$ and $\dim \ker (X_1-s) = 1$. We see that we do not obtain any relations from this.
-
-% For the first two entries of $\mu'$ and $\mu''$, we have the following subtableaux:
-% $$\young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \young(1,2).$$
-% Let $X_2$ be the top-left $4 \times 4$ submatrix of $X$.
-The left subtableau imposes the conditions $\dim \ker X_2 = 1$ and $\dim \ker X_2^2 = 2$ while the right subtableau imposes the condition that $\dim \ker (X_2 -s) = 2$.
-These conditions force the relation $$A_{12}^1 + sA_{12}^2 = 0.$$
-
-% The original tableaux for $X$ imposes the conditions that $\dim \ker X = 2$, $\dim \ker X^2 = 3$, $\dim \ker (X-s) = 2$, and $\dim \ker (X-s)^2 = 3$. These force the relation $$A_{23}^1 = 0.$$
-
-% Hence we consider the quotient
-% $$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2,s]}{\langle A_{12}^1+sA_{12}^2,A_{23}^1,s \rangle} \cong
-% \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{23}^2]}{\langle A_{12}^1,A_{23}^1 \rangle}.$$
-% We see already that the $0$-fibre is irreducible. The tableau corresponding to the ideal $\langle A_{12}^1,A_{23}^1 \rangle$ is 
-% $$\young(1123,23)$$
-% which corresponds to the MV cycle that is the product of the MV cycles corresponding to $\tau'$ and $\tau''$.
-
-% Lusztig datum: $(111)$
-
-% Dimension: $(2,0,-2)$
-% \end{example}
-
-\subsection{Type $A_2$}
-
+In this section, we will compute some examples of multiplication of MV basis elements using the method provided by \Cref{cor:goodreps}.
+
+We use the section defined by \Cref{lem:almostmintab} to abbreviate MV basis elements to tableaux and view $\CC[N]$ as an algebra in these, rewriting \Cref{eq:btimesb} as an equation in tableaux.
+The coefficients are found using generalized orbital varieties.
+Suppose we have two tableaux $\tau'$ and $\tau''$, with respective weights $\lambda'$, $\mu'$ and $\lambda''$, $\mu''$, and we wish to form their (geometric) fusion product.
+Once we have applied any necessary padding (as in the proof of \Cref{cor:goodreps}) so that $\mu = \mu' + \mu''$ is dominant, we take a generic matrix $A \in X(\tau', \tau'')_{0,s}$.
+
+The requirement that $ A_i := A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda'(i), \lambda''(i)}_{0,s}$ for each $i$ imposes rank conditions on $A$ in the form of vanishing and non-vanishing minors.
+We form the ideal $I\subset \CC[A_{ij}^k, s^\pm] = \CC[\UU_{0, \Ax}^{\mu', \mu''}]$ generated by these relations.
+The ideal of the fusion $ X(\tau', \tau'')_{0,0}$ is
+$$
+    J = (I \cap \CC[A_{ij}^k,s]) + (s)\,.
+$$ 
+Taking the primary decomposition (to account for possible multiplicities) of $J$ gives us ideals $J_1,\dots,J_n$, each corresponding to a generalized orbital variety occurring in the fusion.
+We use \Cref{pr:generalized orbital varietiesasirrecs} to find a tableau for each $J_i$ and then forget all unnecessary padding to get the corresponding stable MV cycle.
+Each $J_i$ also tells us the multiplicity of each MV cycle in the fusion product, where we have multiplicity 1 if and only if $J_i = \sqrt {J_i}$.
+
+\subsection{Type \texorpdfstring{$A_2$}{A2}}
+\label{ss:a2}
+% 
 \begin{example}
-% Let $G = \GL_3$ and consider the tableaux
-% $$\tau' = \young(12) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,23).$$
-
-% Lustig data: $(100)$ for $\tau'$, $(001)$ for $\tau''$.
-$\young(2)\arfu\young(1,3)$:
-
-\acom{This time the smallest $\tau$ is actually $\young(12,3)$ and the smallest fission is $\young(1,3),\young(2)$. For Joel: this time the our $\lambda$ matches \cite{claxton2015young}'s.}
-
-Dimensions: $(1,-1,0)$ for $\tau'$, $(0,1,-1)$ for $\tau''$.
-
-The MV cycles corresponding to the above tableaux are each isomorphic to $\PP^1$.
-We have the weights to be $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (1,1,0)$, and $\mu'' = (2,1,1)$. The matrix under consideration is therefore
-\[
-X = \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c}
-    0 & 1 & & & & \\
-     & 0 & 1 & & & \\
-     & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
-     & & & 0 & 1 & \\
-     & & & & s & A_{23}^1 \\
-     & & & & & s
-\end{BMAT}
-\right].
-\]
-There are no relations from looking at the submatrix $X_1$. From the submatrix $X_2$, we require $$A_{12}^1 + sA_{12}^2 = 0.$$
-From $X$, we further obtain the relations $$A_{12}^2A_{23}^1 + sA_{13}^1 = 0, A_{12}^1A_{23}^1 + s^2A_{13}^1 = 0.$$
-Then the quotient ring we find is
-$$\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s]}{\langle A_{12}^1+sA_{12}^2, A_{12}^2A_{23}^1+sA_{13}^1, A_{12}^1A_{23}^1+s^2A_{13}^1, s\rangle} \cong \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,b_3,s]}{\langle A_{12}^1, A_{12}^2\rangle \cap \langle A_{12}^1, A_{23}^1 \rangle}.$$
-% 
-We see that the 0-fibre is reducible with two components. The tableau corresponding to each ideal is
-$$\begin{array}{cccc} \vspace{1mm}
-    \young(1113,22) & \text{for } \langle A_{12}^1, A_{12}^2 \rangle & \text{Lusztig: }(101) & \dim = (1,0,-1)\\ 
-    \young(1112,23) & \text{for } \langle A_{12}^1, A_{23}^1 \rangle & \text{Lusztig: }(010) & \dim = (1,0,-1).
-\end{array}$$
-Each of these tableaux corresponds to a MV cycle isomorphic to $\PP^2$ so the generic fibre $\PP^1 \times \PP^1$ degenerates to two copies of $\PP^2$.
-\end{example}
-
-\begin{comment}
-\begin{example}
-Let $G = SL_3$ and consider the following tableaux:
-$$\tau' = \young(1122) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(1111,2233).$$
-
-Lusztig data: $(200)$ for $\tau'$, $(002)$ for $\tau''$.
-
-Dimensions: $(2,-2,0)$ for $\tau'$, $(0,2,-2)$ for $\tau''$.
-
-The MV cycles corresponding to these tableaux are each isomorphic to $\PP^1 \times \PP^1$. 
-The weights are then $\lambda' = (4,0,0)$, $\lambda'' = (4,4,0)$, $\mu' = (2,2,0)$, and $\mu'' = (4,2,2)$.
-Then we are considering the following matrix:
-\[
-X = \left[\begin{BMAT}(e){cccccc;cccc;cc}{cccccc;cccc;cc}
-    0 & 1 & & & & & & & & & & \\
-     & 0 & 1 & & & & & & & & & \\
-     & & 0 & 1 & & & & & & & & \\
-     & & & 0 & 1 & & & & & & & \\
-     & & & & 0 & 1 & & & & & & \\
-     & & -s^4 & 3s^3 & -6s^2 & 4s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{12}^4 & A_{13}^1 & A_{13}^2 \\
-     & & & & & & 0 & 1 & & & & \\
-     & & & & & & & 0 & 1 & & & \\
-     & & & & & & & & 0 & 1 & & \\
-     & & & & & & & & -s^2 & 2s & A_{23}^1 & A_{23}^2 \\
-     & & & & & & & & & & 0 & 1 \\
-     & & & & & & & & & & -s^2 & 2s
-\end{BMAT}
-\right].
-\]
-By computer, it can be checked that we obtain the following 3 ideals:
-$$
-\begin{array}{cl}
-    I_1 = & \langle A_{12}^1, A_{12}^2, A_{12}^3, A_{12}^4, s \rangle \\
-    I_2 = & \langle A_{12}^1, A_{12}^2, A_{23}^1, A_{23}^2, s \rangle \\
-    I_3 = & \langle A_{12}^1, A_{12}^2, (A_{23}^1)^2, A_{12}^4A_{23}^1 + A_{12}^3A_{23}^2, A_{12}^3A_{23}^1, (A_{12}^3)^2, s \rangle.
-\end{array}
-$$
-It can be checked that $I_3$ has multiplicity 2 \rcom{Not sure how to make this precise and how to check it.} so the 0-fibre has 4 components, two of which are the same.
-The tableau corresponding to each ideal is
-$$
-\begin{array}{cccc}\vspace{1mm}
-    \young(11111133,2222) & \text{for } I_1 & \text{Lusztig: }(202) & \dim = (2,0,-2) \\ \vspace{1mm}
-    \young(11111122,2233) & \text{for } I_2 & \text{Lusztig: }(020) & \dim = (2,0,-2) \\ \vspace{1mm}
-    \young(11111123,2223) & \text{for } I_3 & \text{Lusztig: }(111) & \dim = (2,0,-2).
-\end{array}
-$$
-The MV cycle for each ideal is isomorphic to $\PP^2 \times \PP^2$.
-\end{example}
-\end{comment}
-
-\begin{example}
-$\young(22)\arfu\young(11,33)$:
-
-\acom{Here the fission is the smallest if we set out to minimize the dimension of the zero eigenspace. For Joel: this $\lambda(n_\bullet)$ again matches that of \cite{claxton2015young}}
-
-Let $G = \GL_3$. Consider the tableaux
-$$\tau' = \young(22) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau'' = \young(11,33).$$
-Then the weights are $\lambda' = (2,0,0)$, $\lambda'' = (2,2,0)$, $\mu' = (0,2,0)$, and $\mu'' = (2,0,2)$. Our matrix $X$ is now
-\[
-X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
+$\young(22)\arfu\young(11,33)= \young(33) + \young(22,33) + 2\cdot \young(23,3)$:
+% 
+The requirement that 
+\[
+A = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
     0 & 1 & & & & \\
@@
 \end{BMAT}
-\right].
-\]
-Using a computer, the ideals we get are
-$$
-\begin{array}{cl}
-    I_1 = & \langle A_{12}^1, A_{12}^2 \rangle \\
-    I_2 = & \langle A_{23}^1, A_{23}^2 \rangle \\
-    I_3 = & \langle (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2 \rangle. 
-\end{array}
-$$
-The tableaux corresponding to each ideal is
-$$
-\begin{array}{cc}\vspace{1mm}
-    \young(1133,22) & \text{for } I_1 \\ \vspace{1mm}
-    \young(1122,33) & \text{for } I_2 \\ \vspace{1mm}
-    \young(1123,23) & \text{for } I_3
-\end{array}
-$$
-and the MV cycles corresponding to each are isomorphic to $\PP^2 \times \PP^2$.
+\right]\text{ is contained in } \young(22)\bdfamo \young(11,33)
+\]
+imposes the following nontrivial relations on $A$. 
+{\small
+$$
+\begin{aligned}
+    & 2 A_{12}^2 A_{23}^2 s + 3 A_{13}^2 s^2 + A_{12}^2 A_{23}^1 + A_{12}^1 A_{23}^2 + 2 A_{13}^1 s, A_{13}^2 s^3 - A_{12}^2 A_{23}^1 s - A_{12}^1 A_{23}^2 s - 2 A_{12}^1 A_{23}^1, \\ 
+     & A_{12}^2 A_{13}^2 A_{23}^1 s^2 + A_{12}^1 A_{13}^2 A_{23}^2 s^2 - (A_{12}^2 A_{23}^1)^2 + 2 A_{12}^1 A_{12}^2 A_{23}^1 A_{23}^2 - (A_{12}^1 A_{23}^2)^2 + 6 A_{12}^1 A_{13}^2 A_{23}^1 s + 4 A_{12}^1 A_{13}^1 A_{23}^1, \\
+     & A_{12}^1 A_{13}^2 (A_{23}^2)^2 s^2 - (A_{12}^2 A_{23}^1)^2 A_{23}^2 + 2 A_{12}^1 A_{12}^2 A_{23}^1 (A_{23}^2)^2 - (A_{12}^1)^2 (A_{23}^2)^3 - 2 A_{12}^2 A_{13}^2 (A_{23}^1)^2 s \\
+     & \quad + 4 A_{12}^1 A_{13}^2 A_{23}^1 A_{23}^2 s - A_{13}^1 A_{13}^2 A_{23}^1 s^2 - 3 A_{12}^1 A_{13}^2 (A_{23}^1)^2 + 4 A_{12}^1 A_{13}^1 A_{23}^1 A_{23}^2, \\
+     & (A_{12}^2)^3 (A_{23}^1)^2 A_{23}^2 - 2 A_{12}^1 A_{23}^1 (A_{12}^2 A_{23}^2)^2 + A_{12}^2 (A_{12}^1)^2 (A_{23}^2)^3 + 2 A_{13}^2 (A_{12}^2 A_{23}^1)^2 s + 2 A_{13}^2 (A_{12}^1 A_{23}^2)^2 s \\
+     & \quad + 3 A_{12}^1 (A_{13}^2)^2 A_{23}^1 s^2 + A_{13}^1 (A_{12}^2 A_{23}^1)^2 + 4 A_{12}^1 A_{12}^2 A_{13}^2 (A_{23}^1)^2 - 6 A_{12}^1 A_{12}^2 A_{13}^1 A_{23}^1 A_{23}^2 \\
+     &\quad + 4 (A_{12}^1)^2 A_{13}^2 A_{23}^1 A_{23}^2  - 4 A_{12}^1 A_{13}^1 A_{13}^2 A_{23}^1 s - 4 A_{12}^1 (A_{13}^1)^2 A_{23}^1 + A_{13}^1 (A_{12}^1 A_{23}^2)^2
+\end{aligned}
+$$}
+% 
+At $s=0$ the ideal generated by the above relations decomposes as a union of the following generalized orbital varieties, where the last component occurs with multiplicity 2. % TODO INDENT FUNNY 
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$\small}l<{$}}
+  \begin{tabular}{Q} 
+    \text{Ideal of }X(\tau) & \tau \\
+    \midrule 
+    ( A_{12}^1, A_{12}^2,s ) & \young(1133,22)  \BS \\ 
+    ( A_{23}^1, A_{23}^2,s ) & \young(1122,33) \BS\TS \\
+    \sqrt{( (A_{23}^1)^2, A_{12}^2A_{23}^1 + A_{12}^1A_{23}^2, A_{12}^1A_{23}^1, (A_{12}^1)^2,s )} & \young(1123,23) \TS
+    \end{tabular}
+\end{table}
 \end{example}
 
-\subsection{Type $A_3$}\label{ss:GL4 examples}
-
-Let $G = \GL_4$.
-There is a cluster structure on $\CC[N]$ consisting of 12 cluster variables.
-We will take the initial cluster $(x_1,\dots,x_6)$ coming from the reduced word ${\bf i} = (1,2,3,1,2,1)$.
-If we view $\CC[N] \cong \CC[x_{ij} : i < j]$, then
+\subsection{Type \texorpdfstring{$A_3$}{A3}}
+\label{ss:GL4 examples}
+% 
+There is a cluster structure on $\CC[N] \cong \CC[x_{ij} : 1 \leq i < j \leq 4]$ consisting of 12 cluster variables. The initial cluster coming from the standard reduced word is
 \[
@@
 \]
-We list the corresponding tableaux, coordinate ring of the generalized orbital variety $X(\tau)$, Lusztig-datum, and cluster variable as a Laurent polynomial in the $x_i$ below:
-
-% \acom{Add dominant version column}
-% \jcom{This is a nice table.  But these are the coordinate rings of $ X(\tau)$, not of $ Z(\tau) $.}
-% \renewcommand{\arraystretch}{1.5}
-\begin{table}[ht!]%[H]
-  \centering
-  \newcolumntype{Q}{>{$}l<{$}>{$}c<{$}>{$}l<{$}>{$}l<{$}>{$}c<{$}}
-  \begin{tabular}{Q} 
-    \tau' & \tau = \text{Dominant }\tau' & \text{Coordinate ring of }X(\tau) & \text{Lusztig-datum} & \text{Cluster variable} \\
-    \midrule 
-\young(2) & \young(12) & \CC[A_{12}^1] & (1,0,0,0,0,0) & x_1 \rule{0pt}{3ex}\\
-\young(1,3) & \young(11,23) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1,A_{13}^1 )} & (0,0,0,1,0,0) & \frac{x_2 + x_3}{x_1} \TS\BS\\
-\young(1,2,4) & \young(11,22,34) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 )} & (0,0,0,0,0,1) & \frac{x_2x_4 + x_3x_6 + x_1x_5}{x_2x_3} \TS\BS\\
-\young(3) & \young(13,2) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1 )} & (1,0,0,1,0,0) & x_2 \TS\BS\\
-\young(2,3) & \young(12,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{23}^1 )} & (0,1,0,0,0,0) & x_3 \TS\BS\\
-\young(1,4) & \young(11,24,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 )} & (0,0,0,1,0,1) & \frac{x_1x_5 + x_6(x_2+x_3)}{x_1x_2} \TS\BS\\
-\young(1,3,4) & \young(11,23,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 )} & (0,0,0,0,1,0) & \frac{x_1x_5 + x_4(x_2+x_3)}{x_1x_3}\TS\BS\\
-\young(2,4) & \young(112,24,3) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 )} & (0,1,0,0,0,1) & \frac{x_3x_6+x_1x_5}{x_2} \TS\BS\\
-\young(13,2,4) & \young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 )} & (1,0,0,0,1,0) & \frac{x_2x_4 + x_1x_5}{x_3} \TS\BS\\
-\young(2,3,4) & \young(12,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{23}^1,A_{24}^1,A_{34}^1 )} & (0,0,1,0,0,0) & x_4 \TS\BS\\
-\young(3,4) & \young(13,24) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1 )} & (0,1,0,0,1,0) & x_5 \TS\BS\\
-\young(4) & \young(14,2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1 )} & (1,0,0,1,0,1) & x_6 \TS\BS\\
-  \end{tabular}
-\end{table}
-
-% \[
-% \begin{array}{ccc} 
-% \tau & \text{Coordinate ring of }X(\tau) & \text{Lusztig-datum} \\ \hline
-% \young(2) & \CC[A_{12}^1] & (1,0,0,0,0,0) \rule{0pt}{3ex}\\
-% \young(1,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1,A_{13}^1 \rangle} & (0,0,0,1,0,0) \TS\BS\\
-% \young(1,2,4) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 \rangle} & (0,0,0,0,0,1) \TS\BS\\
-% \young(3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1 \rangle} & (1,0,0,1,0,0) \TS\BS\\
-% \young(2,3) & \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{23}^1 \rangle} & (0,1,0,0,0,0) \TS\BS\\
-% \young(1,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 \rangle} & (0,0,0,1,0,1) \TS\BS\\
-% \young(1,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 \rangle} & (0,0,0,0,1,0) \TS\BS\\
-% \young(2,4) & \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 \rangle} & (0,1,0,0,0,1) \TS\BS\\
-% \young(13,2,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 \rangle} & (1,0,0,0,1,0) \TS\BS\\
-% \young(2,3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{23}^1,A_{24}^1,A_{34}^1 \rangle} & (0,0,1,0,0,0) \TS\BS\\
-% \young(3,4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1 \rangle} & (0,1,0,0,1,0) \TS\BS\\
-% \young(4) & \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle} & (1,0,0,1,0,1) \TS\BS\\
-% \end{array}
-% \]
-
-% \begin{table}[]
-% \centering
-% \begin{tabular}{l|c|c}
-% $\tau$ & Coordinate ring of $Z(\tau)$ & Lusztig-datum \\ \hline
-% \young(2) & $\CC[A_{12}^1]$ & (1,0,0,0,0,0) \\
-% \young(1,3) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1,A_{13}^1 \rangle}$ & (0,0,0,1,0,0) \\
-% \young(1,2,4) & $\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 \rangle}$ & (0,0,0,0,0,1) \\
-% \young(3) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{12}^1 \rangle}$ & (1,0,0,1,0,0) \\
-% \young(2,3) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{\langle A_{23}^1 \rangle}$ & (0,1,0,0,0,0) \\
-% \young(1,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 \rangle}$ & (0,0,0,1,0,1) \\
-% \young(1,3,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 \rangle}$ & (0,0,0,0,1,0) \\
-% \young(2,4) & $\frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 \rangle}$ & (0,1,0,0,0,1) \\
-% \young(13,2,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 \rangle}$ & (1,0,0,0,1,0) \\
-% \young(2,3,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{23}^1,A_{24}^1,A_{34}^1 \rangle}$ & (0,0,1,0,0,0) \\
-% \young(3,4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{34}^1 \rangle}$ & (0,1,0,0,1,0) \\
-% \young(4) & $\frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{\langle A_{12}^1,A_{13}^1,A_{23}^1 \rangle}$ & (1,0,0,1,0,1) \\
-% \end{tabular}
-% \end{table}
-
-% \[\begin{array}{cccccc} \vspace{1mm}
-%     Z_1 &\leadsto \young(2) & Z_2 &\leadsto \young(1,3) & Z_3 &\leadsto \young(1,2,4) \\ \vspace{1mm}
-%     Z_{1 \leftarrow 2} &\leadsto \young(3) & Z_{1 \rightarrow 2} &\leadsto \young(2,3) & Z_{2 \leftarrow 3} &\leadsto \young(1,4) \\ \vspace{1mm}
-%      Z_{2 \rightarrow 3} &\leadsto \young(1,3,4) & Z_{in} &\leadsto \young(2,4) & Z_{out} &\leadsto \young(13,2,4)  \\
-%     Z_{P_1} &\leadsto \young(2,3,4) & Z_{P_2} &\leadsto \young(3,4) & Z_{P_3} &\leadsto \young(4)
-% \end{array}\]
-
-We show that the cluster relations in $\CC[N]$ are also true for the fusion product of the corresponding MV cycles.
-For each of the 15 exchange relations, we state the associated matrix $X$, the relations acquired from each submatrix $X_i$, the ideal generated by said relations, and the corresponding tableaux from the ideal.
-Instead of writing the exchange relations in terms of $b_{Z(\tau)}$ or the fusion product in terms of $Z(\tau)$, we will use $\tau$ for both situations.
-
-\jcom{I think that you should clarify what you mean by ``our ideal'' below.  I think that it is the ideal of $ X(\tau', \tau'')_{0,0}$, is that correct?}
-
-\acom{The example below is an $A_2$ example, the same as the first $A_2$ example above.}
+We summarize our findings in the table below, listing each cluster variable along with its stable tableau, the coordinate ring of its generalized orbital variety, and the geometry of its MV cycle.  
+% 
+\newcolumntype{H}{>{\setbox0=\hbox\bgroup$}c<{$\egroup}@{}}
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}H>{$\small}l<{$}>{$}l<{$}>{$}l<{$}>{$}l<{$}}
+  \begin{tabular}{Q} 
+    n_\bullet & \tau = \text{Dom. } \overline \tau & \tau  & \text{Coordinate ring of }X(\tau) & Z &  \text{Cluster variable} \\
+    \midrule 
+(1,0,0,0,0,0) &\young(12) & \young(2) &  \CC[A_{12}^1] & \PP^1 &  x_1 \rule{0pt}{3ex}\\
+(0,0,0,1,0,0) & \young(11,23) & \young(1,3) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1,A_{13}^1 )} & \PP^1 &  \frac{x_2 + x_3}{x_1} \TS\BS\\
+(0,0,0,0,0,1) & \young(11,22,34) & \young(1,2,4) &  \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1 )} & \PP^1 &  \frac{x_2x_4 + x_3x_6 + x_1x_5}{x_2x_3} \TS\BS\\
+(1,0,0,1,0,0) & \young(13,2) & \young(3) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{12}^1 )} & \PP^2 &  x_2 \TS\BS\\
+(0,1,0,0,0,0) & \young(12,3) & \young(2,3) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{23}^1]}{( A_{23}^1 )} & \PP^2 &  x_3 \TS\BS\\
+(0,0,0,1,0,1) & \young(11,24,3) & \young(1,4) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1 )} & \PP^2 &  \frac{x_1x_5 + x_6(x_2+x_3)}{x_1x_2} \TS\BS\\
+(0,0,0,0,1,0) & \young(11,23,4) & \young(1,3,4) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1 )} & \PP^2 &  \frac{x_1x_5 + x_4(x_2+x_3)}{x_1x_3}\TS\BS\\
+(0,1,0,0,0,1) & \young(112,24,3) & \young(2,4) &  \frac{\CC[A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1 )} & S(2,4) &  \frac{x_3x_6+x_1x_5}{x_2} \TS\BS\\
+(1,0,0,0,1,0) & \young(13,2,4) & \young(13,2,4) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1 )} & S(2,4) &  \frac{x_2x_4 + x_1x_5}{x_3} \TS\BS\\
+(0,0,1,0,0,0) & \young(12,3,4) & \young(2,3,4) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{23}^1,A_{24}^1,A_{34}^1 )} & \PP^3 &  x_4 \TS\BS\\
+(0,1,0,0,1,0) & \young(13,24) & \young(3,4) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{34}^1 )} & Gr(2,4) &  x_5 \TS\BS\\
+(1,0,0,1,0,1) & \young(14,2,3) & \young(4) &  \frac{\CC[A_{12}^1,A_{13}^1,A_{14}^1,A_{23}^1,A_{24}^1,A_{34}^1]}{( A_{12}^1,A_{13}^1,A_{23}^1 )} & \PP^3 & x_6 \TS\BS\\
+  \end{tabular}
+  \caption{The variety $S(2,4)$ denotes the non-smooth Schubert divisor in $Gr(2,4)$ the Grassmannian of planes in $\CC^4$}
+\end{table}
+
+In what follows we check that the exchange relations satisfied by the above cluster variables in $\CC[N]$ are corroborated by the fusion of the corresponding MV cycles.
+% 
 \begin{example}
-% Consider the product $Z_1 * Z_2$, so the tableaux are
-% Consider the product % $Z({{\scriptsize\young(2)}})*Z({\scriptsize\young(1,3)})$
-% \[
-% \young(2) \text{ and } \young(1,3).
-% \]
-% $\young(2) * \young(1,3)$.
 $\young(2) \cdot \young(1,3) = \young(3) + \young(2,3)$: 
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(2) *_{\AA \setminus \{0\}} \young(1,3) 
-% \Rightarrow 
-% \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_3 & A_{12}^1A_{23}^1+sA_{13}^1
-% \end{tabular}
-\]
-results in the following relations on submatrices. 
+\right] \text{ is contained in } \young(2) \bdfamo \young(1,3) 
+\]
+imposes the relation $A_{12}^1A_{23}^1+sA_{13}^1$ on $A$ and at $s = 0$ the ideal generated by this relation decomposes as a union of the following generalized orbital varieties.
 \begin{table}[H]
@@
   \begin{tabular}{Q} 
-    \text{Submatrix} & \text{Relations} \\
-    \midrule 
-    A_3 & A_{12}^1A_{23}^1+sA_{13}^1
-    \end{tabular}
-\end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
-%     X_3 & A_{12}^1A_{23}^1+sA_{13}^1
-% \end{array}.
-% \]
-\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
-\begin{table}[H]
-  \centering
-  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-  \begin{tabular}{Q} 
-    % \text{Ideal} & \text{Tableau} \\
     \text{Ideal of } X(\tau) & \tau \\ 
     \midrule 
-    (A_{12}^1,s) & \young(13,2) \BS \\ % \equiv \young(3) \\
-    ( A_{23}^1,s) & \young(12,3) \TS % \equiv \young(2,3)
-    \end{tabular}
-\end{table}
-% $$\langle A_{12}^1A_{23}^1+sA_{13}^1,s \rangle = 
-% \langle A_{12}^1,s \rangle \cap \langle A_{23}^1,s \rangle.$$
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,s \rangle &\leadsto \young(13,2) &\equiv \young(3) &\leadsto {Z_{1 \leftarrow 2}} \\ 
-%     \langle A_{23}^1,s \rangle &\leadsto \young(12,3) &\equiv \young(2,3) &\leadsto{Z_{1 \rightarrow 2}}
-% \end{array}
-% \]
-% so $Z_1 * Z_2 = Z_{1 \leftarrow 2} + Z_{1 \rightarrow 2}$.
-% \noindent so $\young(2) * \young(1,3) = \young(3) + \young(2,3)$.
+    (A_{12}^1,s) & \young(13,2) \BS \\
+    ( A_{23}^1,s) & \young(12,3) \TS
+    \end{tabular}
+\end{table}
 \end{example}
@@
 \begin{example}
-% Consider the product $Z_2 * Z_3$, so the tableaux are 
-% \[
-% \young(1,3) \text{ and } \young(1,2,4).
-% \]
-% Our matrix is 
 $\young(1,3) \cdot \young(1,2,4) = \young(1,4) + \young(1,3,4):$ The requirement that
@@
 \end{table}
-\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
-\begin{table}[H]
-  \centering
-  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-  \begin{tabular}{Q} 
-    % \text{Ideal} & \text{Tableau} \\
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following generalized orbital varieties.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$\small }l<{$}}
+  \begin{tabular}{Q} 
     \text{Ideal of } X(\tau) & \tau \\ 
@@
 \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
-%     X_2 & A_{12}^1 \\
-%     X_3 & A_{13}^1 \\
-%     X_4 & A_{14}^1, A_{23}^1A_{34}^1 + sA_{24}^1
-% \end{array}.
-% \]
-% 
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{14}^1,s \rangle &\leadsto \young(11,24,3) &\equiv \young(1,4) &\leadsto Z_{2 \leftarrow 3} \\ 
-%     \langle A_{12}^1,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(11,23,4) &\equiv \young(1,3,4) &\leadsto Z_{2 \rightarrow 3}
-% \end{array}
-% \]
-% so $Z_2 * Z_3 = Z_{2 \leftarrow 3} + Z_{2 \rightarrow 3}$.
 \end{example}
@@
 \end{table}
-\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following GOVs.
-\begin{table}[H]
-  \centering
-  \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-  \begin{tabular}{Q} 
-    % \text{Ideal} & \text{Tableau} \\
+\noindent At $s = 0$ the ideal generated by the above relations decomposes as a union of the following generalized orbital varieties.
+\begin{table}[H]
+  \centering
+  \newcolumntype{Q}{>{$}l<{$}>{$\small}l<{$}}
+  \begin{tabular}{Q} 
     \text{Ideal of } X(\tau) & \tau \\ 
@@
 \end{table}
-% Consider the product $Z_1 * Z_{2 \rightarrow 3}$, so the tableaux are 
-% \[
-% \young(2) \text{ and } \young(1,3,4).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
-%     s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
-%      & 0 & A_{23}^1 & A_{24}^1 \\
-%      & & s & A_{34}^1 \\
-%      & & & s
-% \end{BMAT}
-% \right].
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
-%     X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_3 & A_{12}^1A_{23}^1 + sA_{13}^1 \\
-% %     X_4 & A_{34}^1, A_{12}^1A_{24}^1 + sA_{14}^1, A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1
-% % \end{array}.
-% % \]
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(12,3,4) &\equiv \young(2,3,4) &\leadsto Z_{P_1} \\ 
-%     \langle A_{12}^1,A_{34}^1,A_{23}^1A_{14}^1 - A_{13}^1A_{24}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
-% \end{array}
-% \]
-% so $Z_1 * Z_{2 \rightarrow 3} = Z_{P_1} + Z_{out}$.
 \end{example}
@@
 \end{table}
-% Consider the product $Z_1 * Z_{2 \leftarrow 3}$, so the tableaux are 
-% \[
-% \young(2) \text{ and } \young(1,4).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(2) \text{ and } \young(11,24,3).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
-%     0 & 1 & & & & \\
-%     -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
-%      & & 0 & 1 & & \\
-%      & & & s & A_{23}^1 & A_{24}^1 \\
-%      & & & & s & A_{34}^1 \\
-%      & & & & & s
-% \end{BMAT}
-% \right].
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_2 & A_{12}^1 + sA_{12}^2 \\
-%     X_3 & A_{13}^1, A_{23}^1 \\
-%     X_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
-%     \end{tabular}
-% \end{table}
-% \[
-% \begin{array}{c|c}
-%     \text{Submatrix} & \text{Relations} \\ \hline
-%     X_2 & A_{12}^1 + sA_{12}^2 \\
-%     X_3 & A_{13}^1, A_{23}^1 \\
-%     X_4 & A_{12}^2A_{24}^1 + sA_{14}^1, A_{12}^1A_{24}^1 - s^2A_{14}^1 
-% \end{array}.
-% \]
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(114,22,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
-%     \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(2,4) &\leadsto Z_{in}
-% \end{array}
-% \]
-% so $Z_1 * Z_{2 \leftarrow 3} = Z_{P_3} + Z_{in}$.
 \end{example}
@@
 \begin{example}
-% \acom{Let's redo this as $\young(2,3)\arfu\young(11,2,4)$.}
 
@@
 \end{table}
-% Consider the product $Z_3 * Z_{1 \rightarrow 2}$, so the tableaux are 
-% \[
-% \young(1,2,4) \text{ and } \young(2,3).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(1,2,4) \text{ and } \young(12,3).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){cc;cc;c;c}{cc;cc;c;c}
-%     0 & 1 & & & & \\
-%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
-%      & & 0 & 1 & & \\
-%      & & & s & A_{23}^1 & A_{24}^1 \\
-%      & & & & s & A_{34}^1 \\
-%      & & & & & 0
-% \end{BMAT}
-% \right].
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_2 & A_{12}^1 \\
-%     X_3 & A_{23}^1 \\
-%     X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1 \\
-% %     X_3 & A_{23}^1 \\
-% %     X_4 & A_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1 
-% % \end{array}.
-% % \]
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{24}^1,s \rangle &\leadsto \young(112,24,3) &\equiv \young(1,4) &\leadsto Z_{in} \\ 
-%     \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(112,23,4) &\equiv \young(1,3,4) &\leadsto Z_{P_1}
-% \end{array}
-% \]
-% so $Z_3 * Z_{1 \rightarrow 2} = Z_{in} + Z_{P_1}$.
 \end{example}
@@
 \end{table}
-% Consider the product $Z_3 * Z_{1 \leftarrow 2}$, so the tableaux are 
-% \[
-% \young(1,2,4) \text{ and } \young(3).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
-%     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
-%      & 0 & A_{23}^1 & A_{24}^1 \\
-%      & & s & A_{34}^1 \\
-%      & & & 0
-% \end{BMAT}
-% \right].
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_2 & A_{12}^1 \\
-%     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1 \\
-% %     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1, A_{13}^1A_{34}^1 - sA_{14}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
-% % \end{array}.
-% % \]
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{13}^1,A_{23}^1,s \rangle &\leadsto \young(14,2,3) &\equiv \young(4) &\leadsto Z_{P_3} \\ 
-%     \langle A_{12}^1,A_{34}^1,A_{13}^1A_{24}^1-A_{23}^1A_{14}^1,s \rangle &\leadsto \young(13,2,4) & &\leadsto Z_{out}
-% \end{array}
-% \]
-% so $Z_3 * Z_{1 \leftarrow 2} = Z_{P_3} + Z_{out}$.
 \end{example}
@@
 \begin{example}
-% \acom{Let's redo this as $\young(3)\arfu\young(11,24)$}
 
@@
 \end{table}
-% Consider the product $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3}$, so the tableaux are 
-% \[
-% \young(3) \text{ and } \young(1,4).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(13,2) \text{ and } \young(1,4).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){cc;c;c;c}{cc;c;c;c}
-%     0 & 1 & & & \\
-%      & s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
-%      & & 0 & A_{23}^1 & A_{24}^1 \\
-%      & & & 0 & A_{34}^1 \\
-%      & & & & s
-% \end{BMAT}
-% \right].
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_2 & A_{12}^1 \\
-%     X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1 \\
-% %     X_4 & A_{13}^1A_{34}^1 + sA_{14}^1
-% % \end{array}.
-% % \]
-% \noindent Hence, our ideal is 
-% \[
-% \langle A_{12}^1,A_{13}^1A_{34}^1+sA_{14}^1,s \rangle
-% = \langle A_{12}^1,A_{13}^1,s \rangle \cap \langle A_{12}^1,A_{34}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{13}^1,s \rangle &\leadsto \young(114,23) &\equiv \young(14,3) &\leadsto Z_2 Z_{P_3} \\ 
-%     \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(113,24) &\equiv \young(3,4) &\leadsto Z_{P_2}
-% \end{array}
-% \]
-% so $Z_{1 \leftarrow 2} * Z_{2 \leftarrow 3} = Z_2 Z_{P_3} + Z_{P_2}$.
 \end{example}
@@
 \begin{example}
-% \acom{Let's redo this as $\young(2,3)\arfu\young(11,23,4)$.}
 
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,23,4) *_{\AA \setminus \{0\}} \young(2,3)
+\right] \text{ is contained in } \young(11,23,4) \bdfamo \young(2,3)
 \]
 results in the following relations on submatrices:
-% 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     A_2 & A_{12}^1 \\
-%     A_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
-%     A_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
-%     \end{tabular}
-% \end{table}
 \begin{table}[H]
@@
 \end{table}
-% Consider the product $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3}$, so the tableaux are 
-% \[
-% \young(2,3) \text{ and } \young(1,3,4).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(12,23) \text{ and } \young(1,3,4).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
-%     0 & 1 & & & & & \\
-%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
-%      & & 0 & 1 & & & \\
-%      & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
-%      & & & & 0 & 1 & \\
-%      & & & & & s & A_{34}^1 \\
-%      & & & & & & s
-% \end{BMAT}
-% \right].
-% \]
-% % 
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_2 & A_{12}^1 \\
-%     X_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
-%     X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1 \\
-% %     X_3 & A_{23}^1, A_{12}^2A_{23}^2 + A_{13}^1 + sA_{13}^2 \\
-% %     X_4 & A_{34}^1, A_{12}^2A_{24}^1 + sA_{14}^1, sA_{23}^2A_{14}^1 - sA_{13}^2A_{24}^1 - A_{13}^1A_{24}^1
-% % \end{array}.
-% % \]
-% % 
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
-%     \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,A_{12}^2A_{23}^2+A_{13}^1,s \rangle &\leadsto \young(112,233,4) &\equiv \young(12,33,4) &\leadsto Z_2 Z_{P_1}
-% \end{array}
-% \]
-% so $Z_{1 \rightarrow 2} * Z_{2 \rightarrow 3} = Z_{P_2} + Z_2 Z_{P_1}$.
 \end{example}
@@
 \begin{example}
-% \acom{Let's redo this as $\young(1,3)\arfu\young(113,22,4)$.}
-
-$\young(113,22,4) \cdot \young(1,3) = \young(3,4) + \young(1,3,4):$ The requirement that
+$\young(113,22,4) \cdot \young(1,3) = \young(3,4) + \young(13,3,4) = \young(3,4) + \young(1,3,4)\arfu\young(3):$ The requirement that
 \[
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(113,22,4) *_{\AA \setminus \{0\}} \young(1,3)
+\right] \text{ is contained in } \young(113,22,4) \bdfamo \young(1,3)
 \]
 results in the following relations on submatrices:
-% 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     A_2 & A_{12}^1, A_{12}^2 \\
-%     A_3 & A_{13}^1 \\
-%     A_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
-%     \end{tabular}
-% \end{table}
 \begin{table}[H]
@@
 \end{table}
-% Consider the product $Z_2 * Z_{out}$, so the tableaux are 
-% \[
-% \young(1,3) \text{ and } \young(13,2,4).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(11,23) \text{ and } \young(13,2,4).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){ccc;cc;cc;c}{ccc;cc;cc;c}
-%     0 & 1 & & & & & & \\
-%      & 0 & 1 & & & & & \\
-%      & & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
-%      & & & 0 & 1 & & & \\
-%      & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
-%      & & & & & 0 & 1 & \\
-%      & & & & & & s & A_{34}^1 \\
-%      & & & & & & & s
-% \end{BMAT}
-% \right]
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_2 & A_{12}^1, A_{12}^2 \\
-%     X_3 & A_{13}^1 \\
-%     X_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1, A_{12}^2 \\
-% %     X_3 & A_{13}^1 \\
-% %     X_4 & A_{34}^1, A_{23}^1A_{14}^1 + s(A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1) 
-% % \end{array}.
-% % \]
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(1113,224,3) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
-%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(1113,223,4) &\equiv \young(1,3,4) &\leadsto Z_{1 \leftarrow 2} Z_{2 \rightarrow 3}
-% \end{array}
-% \]
-% so $Z_2 * Z_{out} = Z_{P_2} + Z_{1 \leftarrow 2} Z_{2 \rightarrow 3}$.
 \end{example}
@@
 \end{table}
-% Consider the product $Z_2 * Z_{in}$, so the tableaux are 
-% \[
-% \young(1,3) \text{ and } \young(2,4).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
-%     0 & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
-%      & s & A_{23}^1 & A_{24}^1 \\
-%      & & 0 & A_{34}^1 \\
-%      & & & s
-% \end{BMAT}
-% \right].
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
-%     X_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_3 & A_{12}^1A_{23}^1 - sA_{13}^1 \\
-% %     X_4 & A_{23}^1A_{34}^1 + sA_{24}^1, A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1
-% % \end{array}.
-% % \]
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{34}^1,s \rangle \cap \langle A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{34}^1,s \rangle &\leadsto \young(13,24) &\equiv \young(3,4) &\leadsto Z_{P_2} \\ 
-%     \langle A_{23}^1,A_{12}^1A_{24}^1 + A_{13}^1A_{34}^1,s \rangle &\leadsto \young(12,34) & &\leadsto Z_{1 \rightarrow 2} Z_{2 \leftarrow 3}
-% \end{array}
-% \]
-% so $Z_2 * Z_{in} = Z_{P_2} + Z_{1 \rightarrow 2} Z_{2 \leftarrow 3}$.
 \end{example}
@@
 \begin{example}
-% \acom{Let's redo this as $\young(2,3)\arfu\young(113,2,4)$.}
 
@@
 \end{table}
-% Consider the product $Z_{out} * Z_{1 \rightarrow 2}$, so the tableaux are 
-% \[
-% \young(13,2,4) \text{ and } \young(2,3).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(13,2,4) \text{ and } \young(12,3).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
-%     0 & 1 & & & & & \\
-%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 \\
-%      & & 0 & 1 & & & \\
-%      & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 \\
-%      & & & & 0 & 1 & \\
-%      & & & & & s & A_{34}^1 \\
-%      & & & & & & 0
-% \end{BMAT}
-% \right]
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_2 & A_{12}^1 \\
-%     X_3 & A_{23}^1 +sA_{23}^2 \\
-%     X_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1 \\
-% %     X_3 & A_{23}^1 +sA_{23}^2 \\
-% %     X_4 & A_{34}^1, A_{13}^1A_{24}^1 - A_{23}^1A_{14}^1 
-% % \end{array}.
-% % \]
-% \noindent Hence, our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle \cap \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{13}^1,A_{23}^1,A_{34}^1,s \rangle &\leadsto \young(1112,24,3) &\equiv \young(23,4) &\leadsto Z_1 Z_{P_2} \\ 
-%     \langle A_{12}^1,A_{23}^1,A_{24}^1,A_{34}^1,s \rangle &\leadsto \young(1123,23,4) &\equiv \young(23,3,4) &\leadsto Z_{1 \leftarrow 2} Z_{P_1}
-% \end{array}
-% \]
-% so $Z_{out} * Z_{1 \rightarrow 2} = Z_1 Z_{P_2} + Z_{1 \leftarrow 2} Z_{P_1}$.
 \end{example}
@@
 \end{table}
-% Consider the product $Z_{in} * Z_{1 \leftarrow 2}$, so the tableaux are
-% \[
-% \young(2,4) \text{ and } \young(3).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(2,4) \text{ and } \young(13).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c}
-%      s & A_{12}^1 & A_{13}^1 & A_{14}^1 \\
-%      & 0 & A_{23}^1 & A_{24}^1 \\
-%      & & s & A_{34}^1 \\
-%      & & & 0
-% \end{BMAT}
-% \right].
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%      X_4 & A_{23}^1A_{34}^1 - sA_{24}^1
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_4 & A_{23}^1A_{34}^1 - sA_{24}^1
-% % \end{array}.
-% % \]
-% \noindent Hence, our ideal is 
-% \[
-% \langle A_{23}^1A_{34}^1 - sA_{24}^1,s \rangle
-% = \langle A_{23}^1,s \rangle \cap \langle A_{34}^1,s \rangle.
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{23}^1,s \rangle &\leadsto \young(124,3) &\equiv \young(24,3) &\leadsto Z_{1 \rightarrow 2} Z_{P_3} \\ 
-%     \langle A_{34}^1,s \rangle &\leadsto \young(123,4) &\equiv \young(23,4) &\leadsto Z_1 Z_{P_2}
-% \end{array}
-% \]
-% so $Z_{in} * Z_{1 \leftarrow 2} = Z_{1 \rightarrow 2} Z_{P_3} + Z_1 Z_{P_2}$.
 \end{example}
@@
 \begin{example}
-% \acom{Let's redo this as $\young(1,4)\arfu\young(113,22,34)$.}
 
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(113,22,34) *_{\AA \setminus \{0\}} \young(1,4)
+\right] \text{ is contained in } \young(113,22,34) \bdfamo \young(1,4)
 \]
 results in the following relations on submatrices:
-% 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     A_2 & A_{12}^1,A_{12}^2 \\
-%     A_3 & A_{13}^1, A_{23}^1 \\
-%     A_4 & A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
-%         & A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2 
-%     \end{tabular}
-% \end{table}
 \begin{table}[H]
@@
     (A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s) & \young(1114,223,34) \BS \\
-    \begin{array}{c}
-     (A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s) 
-\end{array}& \young(1113,224,34) \TS
-    \end{tabular}
-\end{table}
-% Consider the product $Z_{out} * Z_{2 \leftarrow 3}$, so the tableaux are 
-% \[
-% \young(1,4) \text{ and } \young(13,2,4).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(11,24,3) \text{ and } \young(13,2,4).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
-%     0 & 1 & & & & & & & \\
-%      & 0 & 1 & & & & & & \\
-%      & & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
-%      & & & 0 & 1 & & & & \\
-%      & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
-%      & & & & & 0 & 1 & & \\
-%      & & & & & & s & A_{34}^1 & A_{34}^2 \\
-%      & & & & & & & 0 & 1 \\
-%      & & & & & & & & s
-% \end{BMAT}
-% \right]
-% \]
-% The relations from the submatrices are:
-% % 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%     X_2 & A_{12}^1,A_{12}^2 \\
-%     X_3 & A_{13}^1, A_{23}^1 \\
-%     X_4 & A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
-%         & A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2 
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1,A_{12}^2 \\
-% %     X_3 & A_{13}^1, A_{23}^1 \\
-% %     X_4 & \begin{array}{c}
-% %          A_{13}^2A_{34}^1 - sA_{14}^1, A_{34}^1 + sA_{34}^2, A_{13}^2A_{34}^2 + A_{14}^1,  \\
-% %          A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\ 
-% %          A_{14}^2A_{23}^2A_{34}^1 - A_{14}^1A_{23}^2A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^1A_{24}^2
-% %     \end{array}
-% % \end{array}.
-% % \]
-% Hence our ideal decomposes into 
-% \[
-% \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s \rangle \cap \begin{array}{c}
-%      \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
-%      A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s \rangle. 
-% \end{array}
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{13}^2,A_{23}^1,A_{14}^1,A_{34}^1,s \rangle &\leadsto \young(1114,223,34) &\equiv \young(14,3,4) &\leadsto Z_{2 \rightarrow 3} Z_{P_3} \\ 
-%     \begin{array}{c}
-%      \langle A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,  \\
-%      A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s \rangle. 
-% \end{array}&\leadsto \young(1113,224,34) &\equiv \young(13,24,4) &\leadsto Z_3 Z_{P_2}
-% \end{array}
-% \]
-% so $Z_{out} * Z_{2 \leftarrow 3} = Z_{2 \rightarrow 3} Z_{P_3} + Z_3 Z_{P_2}$.
+     (A_{12}^1,A_{12}^2,A_{13}^1,A_{23}^1,A_{34}^1,A_{23}^2A_{34}^2 + A_{24}^1,   A_{13}^2A_{34}^2+A_{14}^1,A_{13}^2A_{24}^1-A_{23}^2A_{14}^1,s)  & \young(1113,224,34) \TS
+    \end{tabular}
+\end{table}
 \end{example}
@@
 \begin{example}
-% \acom{Let's redo this as $\young(2,4)\arfu\young(11,23,34)$.}
 
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(11,23,34) *_{\AA \setminus \{0\}} \young(2,4)
+\right] \text{ is contained in } \young(11,23,34) \bdfamo \young(2,4)
 \]
 results in the following relations on submatrices:
-% 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%   A_2 & A_{12}^1 \\
-%     A_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
-%     A_4 & 
-%          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-%         & A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2, A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
-%         & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1
-%     \end{tabular}
-% \end{table}
 \begin{table}[H]
@@
 \end{table}
-% Consider the product $Z_{in} * Z_{2 \rightarrow 3}$, so the tableaux are 
-% \[
-% \young(2,4) \text{ and } \young(1,3,4).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(12,24,3) \text{ and } \young(1,3,4).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){cc;cc;cc;cc}{cc;cc;cc;cc}
-%     0 & 1 & & & & & & \\
-%      & s & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
-%      & & 0 & 1 & & & & \\
-%      & & & 0 & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
-%      & & & & 0 & 1 & & \\
-%      & & & & & s & A_{34}^1 & A_{34}^2 \\
-%      & & & & & & 0 & 1 \\
-%      & & & & & & & s
-% \end{BMAT}
-% \right].
-% \]
-% The relations from the submatrices are:
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%   X_2 & A_{12}^1 \\
-%     X_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
-%     X_4 & 
-%          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-%         & A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2, A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
-%         & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1 \\
-% %     X_3 & A_{13}^1, A_{23}^1, A_{12}^2A_{23}^2 + sA_{13}^2 \\
-% %     X_4 & \begin{array}{c}
-% %          A_{23}^2A_{34}^1 - sA_{24}^1, A_{12}^2A_{24}^1 + A_{13}^2A_{34}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-% %          A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1 + sA_{14}^2,  \\
-% %          A_{23}^2A_{14}^1 - A_{13}^2A_{24}^1 + s(A_{23}^2A_{14}^2 - A_{13}^2A_{24}^2), \\
-% %          A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1 
-% %     \end{array} 
-% % \end{array}.
-% % \]
-% Hence our ideal decomposes into 
-% \[\begin{array}{c}
-%      \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-%      A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s \rangle  
-% \end{array}
-%  \cap \begin{array}{c}
-%       \langle A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
-%       A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s \rangle. 
-%  \end{array} 
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \begin{array}{c}
-%      \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-%      A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1,s \rangle  
-% \end{array} &\leadsto \young(113,224,34) &\equiv \young(13,24,4) &\leadsto Z_3 Z_{P_2} \\ 
-%     \begin{array}{c}
-%       \langle A_{12}^1, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1,  \\
-%       A_{34}^1, A_{12}^2A_{24}^2 + A_{13}^2A_{34}^2 + A_{14}^1,s \rangle. 
-%  \end{array} &\leadsto \young(112,234,34) &\equiv \young(12,34,4) &\leadsto Z_{2 \leftarrow 3} Z_{P_1}
-% \end{array}
-% \]
-% so $Z_{in} * Z_{2 \rightarrow 3} = Z_3 Z_{P_2} + Z_{2 \leftarrow 3} Z_{P_1}$.
 \end{example}
@@
 \begin{example}
-% \acom{Let's redo this as $\young(2,4)\arfu\young(1113,22,34)$.}
 
@@
 \end{BMAT}
-\right] \text{ is contained in } \young(1113,22,34) *_{\AA \setminus \{0\}} \young(2,4)
+\right] \text{ is contained in } \young(1113,22,34) \bdfamo \young(2,4)
 \]
 results in the following relations on submatrices:
-% 
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%   A_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
-%     A_3 & A_{13}^1,A_{23}^1 \\
-%     A_4 & A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-%         & A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
-%         & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
-%         & A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
-%         & A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
-%     \end{tabular}
-% \end{table}
 \begin{table}[H]
@@
     (A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s) & \young(11124,223,34) \BS \\
-    \begin{array}{c}
-     (A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-     A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s). 
-\end{array} & \young(11123,224,34) \TS
-    \end{tabular}
-\end{table}
-% Consider the product $Z_{in} * Z_{out}$, so the tableaux are 
-% \[
-% \young(2,4) \text{ and } \young(13,2,4).
-% \]
-% As the sum of the weights is not dominant, we will instead be using the tableaux
-% \[
-% \young(112,24,3) \text{ and } \young(13,2,4).
-% \]
-% Our matrix is 
-% \[
-% X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
-%     0 & 1 & & & & & & & & \\
-%      & 0 & 1 & & & & & & & \\
-%      & & s & A_{12}^1 & A_{12}^2 & A_{12}^3 & A_{13}^1 & A_{13}^2 & A_{14}^1 & A_{14}^2 \\
-%      & & & 0 & 1 & & & & & \\
-%      & & & & 0 & 1 & & & & \\
-%      & & & & & s & A_{23}^1 & A_{23}^2 & A_{24}^1 & A_{24}^2 \\
-%      & & & & & & 0 & 1 & & \\
-%      & & & & & & & s & A_{34}^1 & A_{34}^2 \\
-%      & & & & & & & & 0 & 1 \\
-%      & & & & & & & & & s
-% \end{BMAT}
-% \right]
-% \]
-% The relations from the submatrices are:
-% \begin{table}[H]
-%   \centering
-%   \newcolumntype{Q}{>{$}l<{$}>{$}l<{$}}
-%   \begin{tabular}{Q} 
-%     \text{Submatrix} & \text{Relations} \\
-%     \midrule 
-%   X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
-%     X_3 & A_{13}^1,A_{23}^1 \\
-%     X_4 & A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-%         & A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
-%         & A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
-%         & A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
-%         & A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
-%     \end{tabular}
-% \end{table}
-% % \[
-% % \begin{array}{c|c}
-% %     \text{Submatrix} & \text{Relations} \\ \hline
-% %     X_2 & A_{12}^1, A_{12}^2+sA_{12}^3 \\
-% %     X_3 & A_{13}^1,A_{23}^1 \\
-% %     X_4 & \begin{array}{c}
-% %          A_{23}^2A_{34}^1 - sA_{24}^1, A_{34}^1 + sA_{34}^2, A_{23}^2A_{34}^2 + A_{24}^1, \\
-% %          A_{12}^3A_{34}^1 - A_{12}^2A_{34}^2, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1 + s(A_{13}^2A_{24}^2 - A_{23}^2A_{14}^2), \\
-% %          A_{13}^2A_{24}^2A_{34}^1 - A_{13}^2A_{24}^1A_{34}^2 - A_{14}^1A_{24}^1 - sA_{14}^2A_{24}^1, \\
-% %          A_{12}^3A_{23}^2A_{14}^1 - A_{12}^2A_{23}^2A_{14}^2 - A_{12}^3A_{13}^2A_{24}^1 + A_{12}^2A_{13}^2A_{24}^2,  \\
-% %          A_{12}^3A_{13}^2A_{24}^1A_{34}^2 - A_{12}^2A_{13}^2A_{24}^2A_{34}^2 + A_{12}^3A_{14}^1A_{24}^1 - A_{12}^2A_{14}^2A_{24}^1
-% %     \end{array} 
-% % \end{array}.
-% % \]
-% Hence our ideal decomposes into \acom{formatting funny; can just list irrecs?}
-% \[
-% \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle
-% \cap \begin{array}{c}
-%      \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-%      A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
-% \end{array} 
-% \]
-% The tableau for each ideal is
-% \[\begin{array}{cccc}\vspace{1mm}
-%     \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{23}^2, A_{24}^1, A_{34}^1,s \rangle &\leadsto \young(11124,223,34) &\equiv \young(24,3,4) &\leadsto Z_{P_1} Z_{P_3} \\ 
-%     \begin{array}{c}
-%      \langle A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1,  \\
-%      A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s \rangle. 
-% \end{array} &\leadsto \young(11123,224,34) &\equiv \young(123,24,4) &\leadsto Z_1 Z_3 Z_{P_2}
-% \end{array}
-% \]
-% so $Z_{in} * Z_{out} = Z_{P_1} Z_{P_3} + Z_1 Z_3 Z_{P_2}$.
+     (A_{12}^1, A_{12}^2, A_{13}^1, A_{23}^1, A_{34}^1, A_{23}^2A_{34}^2 + A_{24}^1, A_{13}^2A_{34}^2 + A_{14}^1, A_{13}^2A_{24}^1 - A_{23}^2A_{14}^1, s)& \young(11123,224,34) \TS
+    \end{tabular}
+\end{table}
 \end{example}

### 2021-06-13 submission.tex
posting to arxiv

@@
 \begin{abstract}
-    Motivated by a conjecture of Anderson describing the structure of the ring of functions on a unipotent subgroup as an algebra spanned by the Mirkovi\'c--Vilonen cycles for the Langlands dual group with respect to the fusion product, we give a conceptually elementary approach to computing this product in type $A$.
-
-    We do so with the help of the Mirkovi\'c--Vybornov isomorphism (one of several established in \cite{mirkovic2007quiver}), which relates slices in the affine Grassmannian of $\GL_m$ and slices in nilpotent orbits of $N\times N$ matrices.
-
-    Extending this isomoprhism to one relating families of slices in the two point Beilinson--Drinfeld Grassmannian and families of slices in orbits of matrices having two eigenvalues, we are able to transfer the fusion product of cycles to a fusion of matrices.
-
-    As an application, we confirm that the cluster variables in $\CC[N]$ are contained in its Mirkovi\'c--Vilonen basis when $m=4$. 
+    The fusion of two Mirkovi\'c--Vilonen cycles is a degeneration of their product, defined using the Beilinson--Drinfeld Grassmannian.
+In this paper, we put in place a conceptually elementary approach to computing this product in type $A$.
+We do so by transferring the problem to a fusion of generalized orbital varieties using the Mirkovi\'c--Vybornov isomorphism.
+As an application, we explicitly compute all cluster exchange relations in the coordinate ring of the upper-triangular subgroup of $ \GL_4$, confirming that all the cluster variables are contained in the Mirkovi\'c--Vilonen basis.
 \end{abstract}
@@
     Let $ Z', Z'' $ be MV cycles.
-The structure constants for the multiplication $ b_{Z'} b_{Z''}$ in $\CC[N]$ are equal to the intersection multiplicities of generalized orbital varieties in the fusion of the generalized orbital varieties corresponding to $ Z', Z''$.
+The structure constants for the of the corresponding MV basis vectors in $\CC[N]$ are equal to the intersection multiplicities of generalized orbital varieties in the fusion of the generalized orbital varieties corresponding to $ Z', Z''$.
 \end{theorem}
@@
 
-Note that for $ s \in \AA $, we have an obvious isomorphism  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$. 
+Note that for $ s \in \AA = \AA^1$, we have an obvious isomorphism  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$. 
 %
@@
 
-Throughout the paper, we fix $ m \in \NN$.  We let $G = \GL_m$ and we let $T\subset G$ be the maximal torus of diagonal matrices. 
+Throughout the paper, we fix $ m \in \NN$.
+We let $G = \GL_m$ and we let $T\subset G$ be the maximal torus of diagonal matrices.
+Let $ N, N_- \subset G$ denote the subgroups of upper and lower triangular matrices with 1s on the diagonal.
 We identify $\ZZ^m$ with the coweight lattice of $G$ and say that a coweight $\nu = (\nu_1,\dots,\nu_m)$ is \new{dominant} if $\nu_1\ge\cdots\ge\nu_m$ and \new{effective} if $\nu_j\ge 0$ for all $j$.
@@
 
-There is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$. 
+For $ s \ne 0$, there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$. 
 % 
@@
 $$
+
+Similarly, we write $ \theta_0$ for the isomorphism $ \Gr_{0,0} \xrightarrow{\sim} \Gr $.
 %
@@
 
-In modular terms, $\cW_\mu$ corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
+In modular terms, $\cW_\mu$ corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the vector bundle $ \cO_{\PP}(\mu_1) \oplus \cdots \oplus \cO_{\PP}(\mu_m)$, and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.
 The lattice description of $ \cW_\mu \cap \Grth_+$ is given in Lemma \ref{le:Wmu} below.
@@
 
-In \cite[Prop~2.6]{kamnitzer2014yangians}, we observed that $ S^\mu \subset \cW_\mu$ (this uses that $\mu$ dominant, which is the reason why we make this assumption).
+In \cite[Prop~2.6]{kamnitzer2014yangians}, we observed that $ S^\mu \subset \cW_\mu$ (this uses that $\mu$ is dominant, which is the reason why we make this assumption).
 More generally, we have the following result.
@@
 
-Let $ r $ be a decreasing, concave, non-negative function of $\NN$ with $r(0) = N$, called a \new{rank function}.  Let $k $ be maximal such that $ r(k) \ne 0 $.
+Let $ r $ be a decreasing, non-negative function of $\NN$ with $r(0) = N$, called a \new{rank function}.  Let $k $ be maximal such that $ r(k) \ne 0 $.
 % 
@@
 Let $ \ell$ denote the number of distinct coordinates of $ z $.
-There exist a sequence of integers $k = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, a point $ s \in\AA^\ell$, such that $s_a\ne s_b$ for any $a\ne b$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
+There exist a sequence of integers $\underline{k} = (k_0,\dots,k_\ell)$ such that $ 0=k_0< k_1< \dots < k_\ell = k $, a point $ \underline s \in\AA^\ell$, such that $s_a\ne s_b$ for any $a\ne b$, and a permutation  $ p $ of $ \{1, \dots, k\}$ such that
 $$ 
@@
 for each $a = 1,\dots,\ell$. 
-Given the choice of $ s$ we require that $ p $ is of minimal length. 
-Given $z$, the data $k, s, p$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
-%
-
-Next for $ a = 1, \dots, \ell $ and $ c = 1, \dots, k_{j+1} - k_j$, we define
+Given the choice of $ \underline s$ we require that $ p $ is of minimal length. 
+Given $z$, the data $\underline{k}, \underline s, p$ is unique up to a permutation of $ \{1, \dots, \ell\}$.
+%
+
+Next for $ a = 1, \dots, \ell $ and $ c = 1, \dots, k_{a+1} - k_a$, we define
 $$
@@
 
-For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of \(\ell = 2\), \(k = (0,\lambda_1')\), \(s_1 = 0, s_2 = s\) and the permutation $p$.
+For $ s \ne 0$, we see that the equalities in $ z(s) $ give rise to the data of \(\ell = 2\), \(\underline k = (0,\lambda_1')\), \(\underline s = ( 0, s)\) and the permutation $p$.
 We also see that
@@
 \begin{proof}
-We could prove this by observing the both sides are the attracting locus of an appropriate $ \Cx$ action. However, we will give the following more algebraic proof.
+We could prove this by observing that both sides are the attracting locus of an appropriate $ \Cx$ action. However, we will give the following more algebraic proof.
 
@@
 \begin{definition}
-    An irreducible component of $\overline{\Gr^\lambda \cap S^\mu}$ is called an \new{Mirkovic--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$. 
+    An irreducible component of $\overline{\Gr^\lambda \cap S^\mu}$ is called an \new{Mirkovi\'c--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$. 
 \end{definition}
@@
 
-In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic--Vilonen polytopes, or, equivalently, Lusztig data, which are sequences in $\NN^{r}$ that depend on a choice of reduced expression for the longest element of the Weyl group of $G$.
+In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovi\'c--Vilonen polytopes, or, equivalently, Lusztig data, which are sequences in $\NN^{r}$ that depend on a choice of reduced expression for the longest element of the Weyl group of $G$.
 We will now explain how to use these results to index MV cycles for $ \GL_m$ using Young tableaux.

### 2021-06-13 submission.tex
changed some delimiters

@@
-%!TEX program = lualatex
 % 
@@
     The fusion of two Mirkovi\'c--Vilonen cycles is a degeneration of their product, defined using the Beilinson--Drinfeld Grassmannian.
-In this paper, we put in place a conceptually elementary approach to computing this product in type $A$.
+In this paper, we put in place a conceptually elementary approach to computing this product in type \(A\).
 We do so by transferring the problem to a fusion of generalized orbital varieties using the Mirkovi\'c--Vybornov isomorphism.
-As an application, we explicitly compute all cluster exchange relations in the coordinate ring of the upper-triangular subgroup of $ \GL_4$, confirming that all the cluster variables are contained in the Mirkovi\'c--Vilonen basis.
+As an application, we explicitly compute all cluster exchange relations in the coordinate ring of the upper-triangular subgroup of \( \GL_4\), confirming that all the cluster variables are contained in the Mirkovi\'c--Vilonen basis.
 \end{abstract}
 
-\section{Introduction}
-\label{s:intro}
-% 
-\subsection{Geometric Satake and Mirkovi\'c--Vilonen cycles}
-\label{ss:gsmv}
-% 
-The geometric Satake equivalence of Mirkovi\'c and Vilonen \cite{mirkovic2007geometric} is an equivalence of categories between the category of spherical perverse sheaves on the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.
+\section{Introduction}\label{s:intro}
+% 
+\subsection{Geometric Satake and Mirkovi\'c--Vilonen cycles}\label{ss:gsmv}
+% 
+The geometric Satake equivalence of Mirkovi\'c and Vilonen~\cite{mirkovic2007geometric} is an equivalence of categories between the category of spherical perverse sheaves on the affine Grassmannian of a reductive group \( G \) and the category of representations of its Langlands dual group \(G^\vee \).
 This foundational result provides a powerful tool to study representation theory using geometry.
-In particular, under this equivalence, the MV cycles (short for Mirkovi\'c--Vilonen) in the affine Grassmannian of $ G $ index bases for irreducible representations of $ G^\vee $.
-In this paper we work with $ G = \GL_m$ and identify $ G^\vee = \GL_m$ as well.
-
-In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov supply a geometric version of symmetric and skew Howe $(\GL_m,\GL_N)$ dualities.
-They relate Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $N\times N$ nilpotent orbits on the one hand, and to Nakajima quiver varieties on the other hand.
-The second author \cite{dthesis} showed  that under the Mirkovi\'c--Vybornov isomorphism, the MV cycles are identified with certain varieties of matrices, called generalized orbital varieties.
+In particular, under this equivalence, the MV cycles (short for Mirkovi\'c--Vilonen) in the affine Grassmannian of \( G \) index bases for irreducible representations of \( G^\vee \).
+In this paper we work with \( G = \GL_m\) and identify \( G^\vee = \GL_m\) as well.
+
+In~\cite{mirkovic2007quiver} (see also the recent sequel~\cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov supply a geometric version of symmetric and skew Howe \((\GL_m,\GL_N)\) dualities.
+They relate Kazhdan--Lusztig slices in the affine Grassmannian of \(\GL_m\) to slices in \(N\times N\) nilpotent orbits on the one hand, and to Nakajima quiver varieties on the other hand.
+The second author~\cite{dthesis} showed  that under the Mirkovi\'c--Vybornov isomorphism, the MV cycles are identified with certain varieties of matrices, called generalized orbital varieties.
 
 Essential to the geometric Satake equivalence, the BD Grassmannian (short for Beilinson--Drinfeld) is used to define a fusion product on the category of spherical perverse sheaves on the affine Grassmannian.
-In \cite{anderson2003polytope}, Anderson used the BD Grassmannian to define a fusion of MV cycles.
+In~\cite{anderson2003polytope}, Anderson used the BD Grassmannian to define a fusion of MV cycles.
 He constructed a family where the general fibre is a Cartesian product of two MV cycles, and the special fibre, called the fusion, is a (non-reduced) union of MV cycles.
-Anderson conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup $ N \subset\GL_m$.
-This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that the MV cycles give a basis for $ \CC[N]$.
-
-\subsection{Fusion using generalized orbital varieties}
-\label{ss:fugov}
+Anderson conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup \( N \subset\GL_m\).
+This conjecture was proven in~\cite{baumann2019mirkovic}, where it was also established that the MV cycles give a basis for \( \CC[N]\).
+
+\subsection{Fusion using generalized orbital varieties}\label{ss:fugov}
 % 
 Computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.
-A few such computations were done by Anderson and Kogan in \cite{anderson2006algebra} in a somewhat ad-hoc fashion.
-Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann, Gaussent and Littelmann \cite{baumann2020bases}.
+A few such computations were done by Anderson and Kogan in~\cite{anderson2006algebra} in a somewhat ad-hoc fashion.
+Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann, Gaussent and Littelmann~\cite{baumann2020bases}.
 
@@
 
-\begin{theorem}
-    Let $ Z', Z'' $ be MV cycles.
-The structure constants for the of the corresponding MV basis vectors in $\CC[N]$ are equal to the intersection multiplicities of generalized orbital varieties in the fusion of the generalized orbital varieties corresponding to $ Z', Z''$.
+\begin{theorem}\label{thm:main}
+    Let \( Z', Z'' \) be MV cycles.
+The structure constants for the of the corresponding MV basis vectors in \(\CC[N]\) are equal to the intersection multiplicities of generalized orbital varieties in the fusion of the generalized orbital varieties corresponding to \( Z', Z''\).
 \end{theorem}
@@
 
-\subsection{Cluster algebras and MV cycles}
-One motivation for computing products of MV basis elements is to relate the cluster algebra structure on $\CC[N]$ to the MV basis.
-Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{geiss2007initial}, using a construction of \cite{berenstein2005cluster3}, that $\CC[N]$ has a natural cluster algebra structure.
-
-This structure starts with an initial seed $\Sigma = (\{x_1,\dots,x_r\},B)$, where $x_i \in \CC[N]$ are a cluster of variables, $B$ is a certain matrix, and $ r = m(m-1)/2$.
-We obtain new variables through a process called mutation, where for a mutable variable $x_i$, its mutation is the unique element $x_i^* \in \CC[N]$ such that 
-$$
-    x_ix_i^* = x_+ + x_- \,.
-$$
-This equation is called an exchange relation, and the terms $x_+$ and $x_-$ are certain monomials in the $x_j$, $j\neq i$,  determined by $B$. 
-It gives us the new cluster $\{x_1, \dots, x_i^*, \dots, x_r\}$.
-
-The initial cluster $\{x_1,\dots,x_r\}$ as well as all possible variables that are obtained through successive mutations are known as cluster variables. 
+\subsection{Cluster algebras and MV cycles}\label{ss:clmv}
+% 
+One motivation for computing products of MV basis elements is to relate the cluster algebra structure on \(\CC[N]\) to the MV basis.
+Cluster algebras were introduced by Fomin and Zelevinsky in~\cite{fomin2002cluster1} and it was shown in~\cite{geiss2007initial}, using a construction of~\cite{berenstein2005cluster3}, that \(\CC[N]\) has a natural cluster algebra structure.
+
+This structure starts with an initial seed \(\Sigma = (\{x_1,\dots,x_r\},B)\), where \(x_i \in \CC[N]\) are a cluster of variables, \(B\) is a certain matrix, and \( r = m(m-1)/2 \).
+We obtain new variables through a process called mutation, where for a mutable variable \(x_i\), its mutation is the unique element \(x_i^* \in \CC[N]\) such that 
+\[
+    x_i x_i^* = x_+ + x_- \,.
+\]
+This equation is called an exchange relation, and the terms \(x_+\) and \(x_-\) are certain monomials in the \(x_j\), \(j\neq i\),  determined by \(B\). 
+It gives us the new cluster \(\{x_1, \dots, x_i^*, \dots, x_r\}\).
+
+The initial cluster \(\{x_1,\dots,x_r\}\) as well as all possible variables that are obtained through successive mutations are known as cluster variables. 
 The cluster monomials are products of cluster variables that are supported on a single cluster.
 
-There are two well-known bases of $\CC[N]$ whose relationship with the cluster structure has been heavily studied: the dual canonical basis of \cite{lusztig1990canonicalbases} and the dual semicanonical basis of \cite{lusztig2000semicanonical}.
-In \cite{kang2018monoidal}, Kang, Kashiwara, Kim and Oh showed that the cluster monomials are contained in the dual canonical basis, while, in \cite{geiss2006rigid}, Gei\ss, Leclerc and Schr\"oer proved that they are all contained in the dual semicanonical basis.
+There are two well-known bases of \(\CC[N]\) whose relationship with the cluster structure has been heavily studied: the dual canonical basis of~\cite{lusztig1990canonicalbases} and the dual semicanonical basis of~\cite{lusztig2000semicanonical}.
+In~\cite{kang2018monoidal}, Kang, Kashiwara, Kim and Oh showed that the cluster monomials are contained in the dual canonical basis, while, in~\cite{geiss2006rigid}, Gei\ss, Leclerc and Schr\"oer proved that they are all contained in the dual semicanonical basis.
 % \cite[Theorem~2.8(3)]{geiss2006rigid}.
@@
 
-The MV basis, the dual canonical basis, and the dual semicanonical basis are all examples of biperfect bases of $\CC[N]$ \cite[Section 2]{baumann2019mirkovic}.
+The MV basis, the dual canonical basis, and the dual semicanonical basis are all examples of biperfect bases of \(\CC[N]\)~\cite[Section 2]{baumann2019mirkovic}.
 In particular, they share a crystal structure.
-In \cite[Appendix]{baumann2019mirkovic}, we showed that the MV basis differs from the dual semicanonical basis at the same point in the underlying crystal as where the dual semicanonical basis differs from the dual canonical basis.
-% 
-The fact that this point at which each of these bases differ is not a cluster monomial in any of these bases, gives evidence for the following conjecture of Anderson and Kogan \cite[Conjecture 5.1]{anderson2006algebra}.
+In~\cite[Appendix]{baumann2019mirkovic}, we showed that the MV basis differs from the dual semicanonical basis at the same point in the underlying crystal as where the dual semicanonical basis differs from the dual canonical basis.
+% 
+The fact that this point at which each of these bases differ is not a cluster monomial in any of these bases, gives evidence for the following conjecture of Anderson and Kogan~\cite[Conjecture 5.1]{anderson2006algebra}.
 \begin{conjecture}\label{conj:cluster in MV}
@@
 
-The conjecture is true in type $A_n$ for $n\leq 3$ since in these cases $\CC[N]$ has a unique biperfect basis \cite[Section 2.3]{baumann2019mirkovic}.
-% 
-More generally, cluster variables called flag minors, coming from initial seeds constructed in \cite[Definitions~2.2--2.3]{berenstein2005cluster3}, belong to each biperfect basis of $\CC[N]$ \cite[Remark~2.10]{baumann2019mirkovic}.
+The conjecture is true in type \(A_n\) for \(n\leq 3\) since in these cases \(\CC[N]\) has a unique biperfect basis \cite[Section 2.3]{baumann2019mirkovic}.
+% 
+More generally, cluster variables called flag minors, coming from initial seeds constructed in \cite[Definitions~2.2--2.3]{berenstein2005cluster3}, belong to each biperfect basis of \(\CC[N]\) \cite[Remark~2.10]{baumann2019mirkovic}.
 And recently in \cite[Proposition 7.2]{baumann2020bases} cluster monomials supported on clusters of flag minors satisfying a certain combinatorial condition where shown to be in the MV basis.
@@
 This would imply that all cluster variables are in the MV basis.
-In \Cref{ss:GL4 examples} we verify that this is indeed the case in type $A_3$ by directly computing each fusion product corresponding to an exchange relation.
-
-\section{Supporting Cast}
-\label{s:players}
-% 
-\subsection{Rings and discs}
-\label{ss:rings}
-Set $\cO = \cO_0 = \CC\xt$ and $\cK = \cK_0 = \CC\xT$.
-We will also consider $\cO_s = \CC\xt[t-s]$ and its fraction field $\cK_s=\CC\xT[t-s]$, for any $ s \in \CC\setminus\{0\} $, as well as $ \Oinf = \CC\xt[t^{-1}] $ and $\Kinf = \CC\xT[t^{-1}]$.
-For any point $ s \in \PP = \PP^1$, $ \cO_s$ is the completion of the local ring $ \mathcal O_{\PP, s} $ and thus the formal spectrum of $ \cO_s$ is the formal neighbourhood $ D_s$ of $ s $ (also called the formal disc centered at $ s$).
-Similarly, the formal spectrum of the field $\cK_s$ is the deleted formal neighbourhood (or punctured disc), denoted $ D_s^\times$.
-
-Note that for $ s \in \AA = \AA^1$, we have an obvious isomorphism  $\cO_s \cong \cO$ and $\cK_s\cong\cK$ taking $ t-s $ to $ t$. 
-%
-
-\subsection{Groups}
-\label{ss:groups}
-% 
-Let $H $ be an algebraic group over $ \CC $.  We will be interested in $ H(R)$ where $ R $ is a $\CC$-algebra, for example $R = \CC[t], \cO_s$, etc.  
-% 
-Note that evaluation at $ t = s$ provides a group homomorphism $ H(\cO_s) \rightarrow H$.
-We denote the kernel of this map by $ H_1(\cO_s)$, often called the  first congruence subgroup.
-We will be particularly interested in this construction in the case $ s = \infty$, which gives us the group $ H_1(\Oinf)$.
-
-Throughout the paper, we fix $ m \in \NN$.
-We let $G = \GL_m$ and we let $T\subset G$ be the maximal torus of diagonal matrices.
-Let $ N, N_- \subset G$ denote the subgroups of upper and lower triangular matrices with 1s on the diagonal.
-We identify $\ZZ^m$ with the coweight lattice of $G$ and say that a coweight $\nu = (\nu_1,\dots,\nu_m)$ is \new{dominant} if $\nu_1\ge\cdots\ge\nu_m$ and \new{effective} if $\nu_j\ge 0$ for all $j$.
-% 
-If $\nu$ is both effective and dominant, then it is a partition of size $|\nu| = \nu_1 + \cdots + \nu_m\in\NN$.  Let $ Q_+ \subset \ZZ^m$ denote the positive root cone, explicitly we have
-$$
-    Q_+ = \{ (\nu_1, \dots, \nu_m) : \nu_1 + \cdots + \nu_j \ge 0 \text{ for $j = 1, \dots, m-1 $ and } \nu_1 + \dots + \nu_m = 0 \}\,. 
-$$
-We define a partial order on $ \ZZ^m$ by $ \lambda \ge \mu $ if and only if $ \lambda - \mu \in Q_+ $.
-
-Given $s\in\CC$ we define $(t-s)^\nu$ to be the diagonal matrix 
+In \Cref{ss:GL4 examples} we verify that this is indeed the case in type \(A_3\) by directly computing each fusion product corresponding to an exchange relation.
+
+\section{Supporting Cast}\label{s:players}
+% 
+\subsection{Rings and discs}\label{ss:rings}
+% 
+Set \(\cO = \cO_0 = \CC\xt\) and \(\cK = \cK_0 = \CC\xT\).
+We will also consider \(\cO_s = \CC\xt[t-s]\) and its fraction field \(\cK_s=\CC\xT[t-s]\), for any \( s \in \CC\setminus\{0\} \), as well as \( \Oinf = \CC\xt[t^{-1}] \) and \(\Kinf = \CC\xT[t^{-1}]\).
+For any point \( s \in \PP = \PP^1\), \( \cO_s\) is the completion of the local ring \( \mathcal O_{\PP, s} \) and thus the formal spectrum of \( \cO_s\) is the formal neighbourhood \( D_s\) of \( s \) (also called the formal disc centered at \( s\)).
+Similarly, the formal spectrum of the field \(\cK_s\) is the deleted formal neighbourhood (or punctured disc), denoted \( D_s^\times\).
+
+Note that for \( s \in \AA = \AA^1\), we have an obvious isomorphism  \(\cO_s \cong \cO\) and \(\cK_s\cong\cK\) taking \( t-s \) to \( t\). 
+%
+
+\subsection{Groups}\label{ss:groups}
+% 
+Let \(H \) be an algebraic group over \( \CC \).  We will be interested in \( H(R)\) where \( R \) is a \(\CC\)-algebra, for example \(R = \CC[t], \cO_s\), etc.  
+% 
+Note that evaluation at \( t = s\) provides a group homomorphism \( H(\cO_s) \rightarrow H\).
+We denote the kernel of this map by \( H_1(\cO_s)\), often called the  first congruence subgroup.
+We will be particularly interested in this construction in the case \( s = \infty\), which gives us the group \( H_1(\Oinf)\).
+
+Throughout the paper, we fix \( m \in \NN\).
+We let \(G = \GL_m\) and we let \(T\subset G\) be the maximal torus of diagonal matrices.
+Let \( N, N_- \subset G\) denote the subgroups of upper and lower triangular matrices with 1s on the diagonal.
+We identify \(\ZZ^m\) with the coweight lattice of \(G\) and say that a coweight \(\nu = (\nu_1,\dots,\nu_m)\) is \new{dominant} if \(\nu_1\ge\cdots\ge\nu_m\) and \new{effective} if \(\nu_j\ge 0\) for all \(j\).
+% 
+If \(\nu\) is both effective and dominant, then it is a partition of size \(|\nu| = \nu_1 + \cdots + \nu_m\in\NN\).  Let \( Q_+ \subset \ZZ^m\) denote the positive root cone, explicitly we have
+\[
+    Q_+ = \{ (\nu_1, \dots, \nu_m) : \nu_1 + \cdots + \nu_j \ge 0 \text{ for }j = 1, \dots, m-1 \text{ and } \nu_1 + \dots + \nu_m = 0 \} \,. 
+\]
+We define a partial order on \( \ZZ^m\) by \( \lambda \ge \mu \) if and only if \( \lambda - \mu \in Q_+ \).
+
+Given \(s\in\CC\) we define \((t-s)^\nu\) to be the diagonal matrix 
 \[
@@
 \]
-which we can view in $G(K)$ for any ring $ K $ containing $(t-s)^{-1}$ and $\CC[t]$. For example, $(t-s)^\nu\in G(K)$ for $ K = \Ks$ or $\CC(t)$.
-
-We will also be interested in the affine space $ M_m$ of $m\times m$ matrices.
-Note that for any $ \CC$-algebra $ R $, $G(R)$ consists of those matrices $ g \in M_m(R) $ whose determinant is invertible in $ R$.
-Thus for example $ (t-s)^\mu\in M_m(\CC[t])$ for all effective $ \mu \in \ZZ^m$ but $(t-s)^\mu\in G(\CC[t])$ if and only if $ \mu = 0 $.
-%
-
-\subsection{Lattices}
-\label{ss:lat}
-% 
-We will use the lattice model for the affine Grassmannian, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
-Consider $ K^m $ as a $K$-module.
-By restriction $ K^m$ can be viewed as an $R$-module.
-An \new{$R$-lattice} in $K^m$ is an $R$-submodule $ L \subset K^m$ which is a free $R$-module of rank $ m $ and satisfies $ L \otimes_R K = K^m $.
-Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.
-%
-
-$ R^m \subset K^m $ is called the standard lattice.
-The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between this set and $\GL_m(K)/\GL_m(R)$, since $ \GL_m(R) $ is the stabilizer of the standard lattice.
-
-We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.
-Given such a lattice $ L $ and a point $ a \in \CC$, the \new{specialization} of $ L $ at $ a $ is the lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $.
-If $L(a) = \cO_a^m$ then $L$ is said to be \new{trivial at $a$}. 
-For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$, since $ t-s $ is invertible in $ \cO_a$.
-
-\section{Affine Grassmannians} 
-\label{s:affgrs}
+which we can view in \(G(K)\) for any ring \( K \) containing \((t-s)^{-1}\) and \(\CC[t]\). For example, \((t-s)^\nu\in G(K)\) for \( K = \Ks\) or \(\CC(t)\).
+
+We will also be interested in the affine space \( M_m\) of \(m\times m\) matrices.
+Note that for any \( \CC\)-algebra \( R \), \(G(R)\) consists of those matrices \( g \in M_m(R) \) whose determinant is invertible in \( R\).
+Thus for example \( (t-s)^\mu\in M_m(\CC[t])\) for all effective \( \mu \in \ZZ^m\) but \((t-s)^\mu\in G(\CC[t])\) if and only if \( \mu = 0 \).
+%
+
+\subsection{Lattices}\label{ss:lat}
+% 
+We will use the lattice model for the affine Grassmannian, so it is useful to recall the following definition.
+Let \( R \subset K\) be two \(\CC\)-algebras (usually, but not always, \(K\) will be a field).
+Consider \( K^m \) as a \(K\)-module.
+By restriction \( K^m\) can be viewed as an \(R\)-module.
+An \new{\(R\)-lattice} in \(K^m\) is an \(R\)-submodule \( L \subset K^m\) which is a free \(R\)-module of rank \( m \) and satisfies \( L \otimes_R K = K^m \).
+Equivalently, \( L = \Sp_R(v_1, \dots, v_m)\) where \(v_1, \dots, v_m\) are free generators of \(K^m\).
+%
+
+\( R^m \subset K^m \) is called the standard lattice.
+The group \(\GL_m(K) \) acts transitively on the set of \(R\)-lattices in \(K^m\), thus giving a bijection between this set and \(\GL_m(K)/\GL_m(R)\), since \( \GL_m(R) \) is the stabilizer of the standard lattice.
+
+We will be particularly interested in \(\CC[t]\)-lattices in \( \CC(t)^m\).
+Given such a lattice \( L \) and a point \( a \in \CC\), the \new{specialization} of \( L \) at \( a \) is the lattice in \(\cK_a^m\) defined as \( L(a) := L \otimes_{\CC[t]} \cO_a \).
+If \(L(a) = \cO_a^m\) then \(L\) is said to be \new{trivial at \(a\)}. 
+For example, the lattice \((t-s)^{-1}\CC[t] \subset \CC(t)\) is trivial at any \(a\ne s\), since \( t-s \) is invertible in \( \cO_a\).
+
+\section{Affine Grassmannians}\label{s:affgrs}
 % 
@@
 
-In these definitions, $ \Vtriv$ denotes the trivial rank $ m $ vector bundle.
-
-\begin{definition}
-\label{def:gr}
-     The \new{ordinary affine Grassmannian} $\Gr = G(\cK)/G(\cO)$.
+In these definitions, \( \Vtriv\) denotes the trivial rank \( m \) vector bundle.
+
+\begin{definition}\label{def:gr}
+     The \new{ordinary affine Grassmannian} \(\Gr = G(\cK)/G(\cO)\).
 \end{definition}    
 It is the moduli space of vector bundles with trivializations,
-$$
+\[
 \Gr = 
-    \left\{ 
-        (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_0^\times $} 
-    \right\} \,. 
-$$
+    \left \{ 
+        (V, \varphi) : \text{\(V\) is a rank \(m\) vector bundle on \( D_0 \), \(\varphi : V \xrightarrow{\sim} \Vtriv \) on \( D_0^\times \)} 
+    \right \} \,. 
+\]
 It is also a moduli space of lattices, 
-$$ 
+\[ 
 \Gr = 
-    \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
-$$
-We obtain a lattice from a pair $ (V,\varphi) $ by setting $ L = \Gamma(D_0, V)$ which is embedded into $ \cK^m = \Gamma(D_0^\times, \Vtriv)$ using $ \varphi$.  
-On the other hand, to get a lattice from the group-theoretic description $ G(\cK) / G(\cO) $ we set $ L = g \cO^m$ for $ g \in G(\cK)$.
-% 
-\begin{definition}
-\label{def:grs}
-    For any $ s \in \CC $, the \new{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ \new{at} $ s $. 
+    \left\{ L \subset \cK^m : \text{ \(L\) is a \(\cO\)-lattice} \right\}\,.
+\]
+We obtain a lattice from a pair \( (V,\varphi) \) by setting \( L = \Gamma(D_0, V)\) which is embedded into \( \cK^m = \Gamma(D_0^\times, \Vtriv)\) using \( \varphi\).  
+On the other hand, to get a lattice from the group-theoretic description \( G(\cK) / G(\cO) \) we set \( L = g \cO^m\) for \( g \in G(\cK)\).
+% 
+\begin{definition}\label{def:grs}
+    For any \( s \in \CC \), the \new{ordinary affine Grassmannian} \(\Gr_s = G(\cK_s)/G(\cO_s)\) \new{at} \( s \). 
 \end{definition}  
@@
     \left\{ (
-        V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D^\times_s $} 
+        V, \varphi) : \text{\(V\) is a rank \(m\) vector bundle on \( D_s \), \(\varphi : V \xrightarrow{\sim} \Vtriv \) on \( D^\times_s \)} 
     \right\}\,, \\
@@
     \left\{ 
-        L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} 
+        L \subset \cK_s^m : \text{ \(L\) is a \(\cO_s\)-lattice} 
     \right\} \,. 
@@
 % 
-\begin{definition}
-\label{def:grth}
-    The \new{thick affine Grassmannian} $\Grth = G(\Kinf)/G(\CC[t])$.
+\begin{definition}\label{def:grth}
+    The \new{thick affine Grassmannian} \(\Grth = G(\Kinf)/G(\CC[t])\).
 \end{definition}
@@
     \left\{ 
-        (V, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} \Vtriv $ on $ D_\infty $ } 
+        (V, \varphi) : \text{\(V\) is a rank \(m\) vector bundle on \( \PP \), \(\varphi : V \xrightarrow{\sim} \Vtriv \) on \( D_\infty \) } 
     \right\}\,, \\
@@
     \left\{ 
-        L : L \subset  \Kinf^m \text{ is a $\CC[t]$-lattice} 
+        L : L \subset  \Kinf^m \text{ is a \(\CC[t]\)-lattice} 
     \right\}\,.
@@
 % 
-\begin{definition} 
-\label{def:bdgr}
-    The two point \new{Beilinson--Drinfeld Grassmannian} $$\pi : \Grbd\to \AA$$ with one point fixed at 0, and the second point $s\in\AA$ varying.
+\begin{definition}\label{def:bdgr}
+    The two point \new{Beilinson--Drinfeld Grassmannian} \[\pi : \Grbd\to \AA\] with one point fixed at 0, and the second point \(s\in\AA\) varying.
 \end{definition}
@@
 It is described in modular terms by 
-$$
+\[
 \Grbd = 
     \left\{ 
-        (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} \Vtriv \text{ on } \PP \setminus \{0, s\}  
+        (V,\varphi,s) : V\text{ is a rank \(m\) vector bundle on }\PP, \varphi : V \xrightarrow{\sim} \Vtriv \text{ on } \PP \setminus \{0, s\}  
     \right\}\,. 
-$$
-% 
-The fibre of $\Grbd \to \AA$ over $ s \in \AA $ will be denoted $ \Gr_{0,s} $ and is given by
-% 
-$$ 
-    G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
-$$
+\]
+% 
+The fibre of \(\Grbd \to \AA\) over \( s \in \AA \) will be denoted \( \Gr_{0,s} \) and is given by
+% 
+\[  
+    G(\CC[t, t^{-1}, {(t-s)}^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
+\]
 We also have the lattice descriptions:
@@
 \Grbd = 
-    \left\{ 
-        (L,s) : L \subset  \CC(t)^m\text{ is a $\CC[t]$-lattice trivial at any }a \ne 0, s 
-    \right\}\,, \\
+    \left \{ 
+        (L,s) : L \subset  \CC(t)^m\text{ is a \(\CC[t]\)-lattice trivial at any }a \ne 0, s 
+    \right \} \,, \\
 % , $L$ is 
 \Gr_{0,s} = 
-    \left\{ 
-        L : L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m \text{ is a $\CC[t]$-lattice} 
-    \right\}\,.
+    \left \{ 
+        L : L \subset  {\CC[t,t^{-1},{(t-s)}^{-1}]}^m \text{ is a \(\CC[t]\)-lattice} 
+    \right \} \,.
 \end{gather*}
 % 
-\begin{definition} 
-\label{def:grplus}
-The \new{positive part} of $\Gr $, resp.\ $\Grth$, is defined by 
+\begin{definition}\label{def:grplus}
+The \new{positive part} of \(\Gr \), resp.\ \(\Grth\), is defined by 
 \begin{gather*}
@@
 % 
-In modular terms, $\Gr^+$ (resp.\ ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow \Vtriv $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp.\ over $ \PP$).
-
-In lattice terms, $ \Gr^+$ (resp.\ ${\Grth}^+$) contains those lattices $L$ which are contained in $\cO^m$ (resp.\ $\CC[t]^m$).
-%
-
-\subsection{Relations between different affine Grassmannians}
-\label{ss:relsbtwgrs}
+In modular terms, \(\Gr^+\) (resp.\ \({\Grth}^+\)) is the set of those \( (V, \varphi)\) where \( \varphi : V \rightarrow \Vtriv \) extends to an inclusion of coherent sheaves over \( D_0 \) (resp.\ over \( \PP\)).
+
+In lattice terms, \( \Gr^+\) (resp.\ \({\Grth}^+\)) contains those lattices \(L\) which are contained in \(\cO^m\) (resp.\ \(\CC[t]^m\)).
+%
+
+\subsection{Relations between different affine Grassmannians}\label{ss:relsbtwgrs}
 % 
@@
 % 
-\begin{proposition}
-    \label{pr:bd-th}
-    There is a map $\Grbd \rightarrow \Grth $ defined in the following equivalent ways:
+\begin{proposition}\label{pr:bd-th}
+    There is a map \(\Grbd \rightarrow \Grth \) defined in the following equivalent ways:
     \begin{enumerate}
-        \item in modular terms as $$(V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty}) \, ;$$
-        \item in the fibre over $ s \in \AA$ as the inclusion $$
-        G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,;$$
-        \item in terms of lattices as $$(L,s)\mapsto L\,,$$ using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on ambient spaces. 
+        \item in modular terms as \[(V,\varphi,s)\mapsto (V, \varphi \big|_{D_\infty}) \, ;\]
+        \item in the fibre over \( s \in \AA\) as the inclusion 
+        \[
+            G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,;
+        \]
+        \item in terms of lattices as \[ (L,s)\mapsto L \,,\] using the inclusion \(\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m\) on ambient spaces. 
     \end{enumerate}
@@
 The following result is the factorization property of the BD Grassmannian (see \cite[Prop. 3.13]{zhu2016introduction}).
-\begin{proposition}
-    \label{pr:polyno-taylor}
-    The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as 
+\begin{proposition}\label{pr:polyno-taylor}
+    The fibres \( \Gr_{0,s}\) of \( \Grbd \rightarrow \AA\) can be described as 
     \begin{equation*}
@@
 
-    Suppose that $ s \ne 0 $. In the lattice realization, this is given by forming the specializations 
+    Suppose that \( s \ne 0 \). In the lattice realization, this is given by forming the specializations 
     $$
@@
     $$
-    Note that if $ L = g \CC[t]^m$ for $ g \in G([t,t^{-1}, (t-s)^{-1}])$, then 
+    Note that if \( L = g \CC[t]^m\) for \( g \in G([t,t^{-1}, (t-s)^{-1}])\), then 
     $$
@@
     $$
-    In the $ s = 0 $ case, the isomorphism is described in the same way, except that we just need to form $ L(0)$.
+    In the \( s = 0 \) case, the isomorphism is described in the same way, except that we just need to form \( L(0)\).
 \end{proposition}
 
-For $ s \ne 0$, there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \Ks \cong \cK$. 
+For \( s \ne 0\), there is an isomorphism \( \Gr_s \cong \Gr \) coming from the isomorphism \( \Ks \cong \cK\). 
 % 
@@
 
-Similarly, we write $ \theta_0$ for the isomorphism $ \Gr_{0,0} \xrightarrow{\sim} \Gr $.
-%
-
-\subsection{The fusion construction}
-\label{ss:fuscon}
-
+Similarly, we write \( \theta_0\) for the isomorphism \( \Gr_{0,0} \xrightarrow{\sim} \Gr \).
+%
+
+\subsection{The fusion construction}\label{ss:fuscon}
+% 
 The following construction will be very important in this paper.
 
-Let $ \Gr_{0, \AA^\times} $ denote the preimage of $\Ax = \AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.
-
-The isomorphisms $ \theta_s $ defined above glue together to a projection map
-\begin{equation}
-\label{eq:mvitau}
+Let \( \Gr_{0, \AA^\times} \) denote the preimage of \(\Ax = \AA \setminus \{0\}\) under the map \(\Gr_{0,\AA} \rightarrow \AA \).
+
+The isomorphisms \( \theta_s \) defined above glue together to a projection map
+\begin{equation}\label{eq:mvitau}
     \theta : \Gr_{0, \AA^\times} \rightarrow \Gr \times \Gr \, .
 \end{equation}
-(This $\theta$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \AA^\times$ instead of the complement of the diagonal in $ \AA\times\AA $.)
-
-Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme 
+(This \(\theta\) matches the map \( \tau \) of \cite{mirkovic2007geometric}, except that we are working over \( \{0 \} \times \AA^\times\) instead of the complement of the diagonal in \( \AA\times\AA \).)
+
+Let \( X_1, X_2 \subset \Gr\) be two subschemes, and consider the subscheme 
 $$ 
@@
 $$
-Given a point $ s \in \Ax$, we write $ X_1 \bdfamf X_2  $ for the fibre of $ X_1 \bdfamo X_2 $ over $s$.
-The map $ \theta_s$ identifies $ X_1 \bdfamf X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.
-
-We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  X_1 \bdfamo X_2 $ in $ \Grbd $. By construction, this is a flat family over $ \AA$.
-
-The fibre $ X_1 \geofu X_2$ of $ X_1 \ast_{\AA} X_2 $ over $0$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.
-We call this subscheme the (geometric) \new{fusion} of $ X_1 $ and $ X_2$.
-%
-
-\subsection{Some subschemes of affine Grassmannians}
-\label{ss:subgrs}
+Given a point \( s \in \Ax\), we write \( X_1 \bdfamf X_2  \) for the fibre of \( X_1 \bdfamo X_2 \) over \(s\).
+The map \( \theta_s\) identifies \( X_1 \bdfamf X_2 \subset \Gr_{0,s}\) with \( X_1 \times X_2 \subset \Gr \times \Gr\).
+
+We define \( X_1 \ast_{\AA} X_2 \) to be the scheme-theoretic closure of \(  X_1 \bdfamo X_2 \) in \( \Grbd \). By construction, this is a flat family over \( \AA\).
+
+The fibre \( X_1 \geofu X_2\) of \( X_1 \ast_{\AA} X_2 \) over \(0\) is a subscheme of \( \Gr_{0,0} \), but regarded as a subscheme of \( \Gr \) using {the isomorphism} \(\Gr_{0,0} \cong \Gr \).
+We call this subscheme the (geometric) \new{fusion} of \( X_1 \) and \( X_2\).
+%
+
+\subsection{Some subschemes of affine Grassmannians}\label{ss:subgrs}
 
@@
 % 
-\begin{definition}
-\label{def:sphschub}
+\begin{definition}\label{def:sphschub}
     The \new{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
@@
 % 
-\begin{definition}
-\label{def:sphfus}
+\begin{definition}\label{def:sphfus}
     The \new{family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \bdfamc \overline{\Gr}^{\lambda''} $.
@@
 % 
-\begin{lemma}
-\label{le:sphfusispos}
+\begin{lemma}\label{le:sphfusispos}
     The map $ \Gr_{0, \AA} \rightarrow \Grth$ restricts to a map $ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} \rightarrow \Grth^+$.
 \end{lemma}
+% 
 \begin{proof}
@@
 % 
-\begin{definition}
-\label{def:klslice}
+\begin{definition}\label{def:klslice}
     The \new{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.
@@
 % 
-\begin{definition} 
-\label{def:inftyorbit}
+\begin{definition}\label{def:inftyorbit}
     The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $.
@@
 % 
-\begin{definition} 
-\label{def:inftyorbitfam}
+\begin{definition}\label{def:inftyorbitfam}
     The \new{family of two semi-infinite orbits} $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$ which we define to have fibres $ S^{\mu', \mu''}_{0,s} := \theta_s^{-1}( S^{\mu'}\times S^{\mu''}) $ for $ s \ne 0$ and fibre $ \theta_0^{-1}(S^{\mu})$ over $ s = 0 $.
@@
 
-\begin{lemma}
-\label{le:inftyfusiskl} 
+\begin{lemma}\label{le:inftyfusiskl} 
     Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu', \mu''}_{0,\AA}$ lands in $ \cW_\mu$.
@@
 
-\section{Matrices}
-\label{s:mats}
+\section{Matrices}\label{s:mats}
 % 
@@
 
-\subsection{Adjoint orbits and their deformations}
-\label{ss:familiesofadjointorbits}
+\subsection{Adjoint orbits and their deformations}\label{ss:familiesofadjointorbits}
 % 
@@
 
-\begin{definition}
-\label{def:Olam}
+\begin{definition}\label{def:Olam}
 The nilpotent (adjoint) orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.
@@
 % 
-\begin{definition}
-\label{def:Olamlam}
+\begin{definition}\label{def:Olamlam}
     For $ s \in \Ax$, the (adjoint) orbit $ \OO^{\lambda', \lambda''}_{0,s}$ of matrices conjugate to $ J_{0,\lambda'} \oplus J_{s,\lambda''}$.
@@
 and
-\begin{equation} 
-\label{eq:ranks}
+\begin{equation}\label{eq:ranks}
 \begin{split}
@@
 The following fact seems to be well-known but we could not find this exact statement in the literature.
-\begin{proposition} 
-    \label{prop:adjoint}
+\begin{proposition}\label{prop:adjoint}
     There exists a flat family $\overline{\OO}^{\lambda', \lambda''}_{0,\AA} \rightarrow \AA$ whose fibre over $s \in \AA$ is reduced and given by $\overline{\OO}^{\lambda', \lambda''}_{0,s}$ if $s \ne 0 $ and $\overline{\OO}^\lambda $ if $ s = 0$.
@@
 By \cite[Corollary 2.2]{eisenbud1989rank}, the fibre of the flat family $ X_{r,W} $ over $ z$ is given by
-\begin{equation} 
-    \label{eq:ESfibre}
+\begin{equation}\label{eq:ESfibre}
     X_{r,z} = \{ A \in M_N(\CC) :\rk (A-s_a)^c\le r_{z,a}(c) \text{ for all } c , a \text{ as above}\}.
@@
 We also see that
-\begin{equation} 
-\label{eq:rcols}
+\begin{equation}\label{eq:rcols}
     \begin{split}
@@
 On the other hand, for $z(0)$, we get that $ \ell = 1$ and that 
-\begin{equation} 
-\label{eq:rcol2}
+\begin{equation}\label{eq:rcol2}
     r_{z(0),1}(c) = 
@@
 % 
-\subsection{The Mirkovi\'c--Vybornov slice}
-\label{ss:mvyslice} 
+\subsection{The Mirkovi\'c--Vybornov slice}\label{ss:mvyslice} 
 % 
@@
 To $ A \in \TT_\mu$ we will associate the $m\times m$ matrix of polynomials $g(A)$ in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
-\begin{equation}
-\label{eq:mvyofa}
+\begin{equation}\label{eq:mvyofa}
     g(A)_{ij} = 
@@
 In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.
-\begin{definition} The \new{upper-triangular} \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $ is defined by
+% 
+\begin{definition} 
+The \new{upper-triangular} \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $ is defined by
 $$
@@
 
-\section{Rising Action} 
-\label{s:rising}
+\section{Rising Action}\label{s:rising}
 Throughout this section, we continue our notation of the previous sections.
@@
 
-\subsection{Linear Operators from lattices}
-\label{s:latticefacts}
-%
-
-\begin{lemma} 
-\label{le:Grl1l2}
+\subsection{Linear Operators from lattices}\label{s:latticefacts}
+% 
+\begin{lemma}\label{le:Grl1l2}
     Let $ L \in \Grth^+ $.  Let $ s \in \Ax$. The following are equivalent:
@@
 
-\begin{lemma} 
-\label{le:linalg} 
+\begin{lemma}\label{le:linalg} 
 Let $ V $ be a $ \CC[t]$-module which is finite-dimensional as a complex vector space.  For any  $ a \in \AA$, the map
@@
 
-\subsection{Matrices from lattices}
-\label{ss:mvyisos}
-
-\begin{lemma} 
-\label{le:Wmu}
+\subsection{Matrices from lattices}\label{ss:mvyisos}
+
+\begin{lemma}\label{le:Wmu}
 Let $ L \in \Grth^+$.  The following are equivalent:
@@
 
-\begin{theorem} 
-\label{th:TmuWmu}
+\begin{theorem}\label{th:TmuWmu}
 The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
@@
 
-\subsection{Upper-triangularity and the Mirkovic-Vybornov isomorphism}
+\subsection{Upper-triangularity and the Mirkovic-Vybornov isomorphism}\label{ss:upmvy}
+% 
 For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda', \lambda''}_{0,\AA} $ with $\cW_\mu$.
@@
 % 
-\begin{theorem} 
-\label{th:OGrl}
+\begin{theorem}\label{th:OGrl}
 There is an isomorphism
@@
 % 
-\begin{theorem}
-\label{th:OTGrW}
+\begin{theorem}\label{th:OTGrW}
 The isomorphism from \Cref{th:OGrl} restricts to an isomorphism
@@
 Restricting to the zero fibre and applying $\theta_0$ together with \Cref{prop:adjoint}, we recover a result of the second author. 
-\begin{corollary}
-    \label{cor:mvy} (\cite[Corollary~5.2.2]{dthesis})
+\begin{corollary}\label{cor:mvy} (\cite[Corollary~5.2.2]{dthesis})
     The map $ A \mapsto g(A)\cO^m$ gives an isomorphism 
@@
 % 
-
-\section{Climax}
-\label{s:climax}
-% 
-\subsection{MV cycles and tableaux}
-\label{ss:mvcs}
-%
-
+% 
+\section{Climax}\label{s:climax}
+% 
+\subsection{MV cycles and tableaux}\label{ss:mvcs}
+% 
+% 
 Continuing now with the notation of the previous sections, we add the assumption that $\mu\le\lambda$ and forget the assumption that $\mu$ is dominant. 
@@
 We record the following easy observations.
-\begin{lemma} 
-\label{le:rdimTrans} 
+\begin{lemma}\label{le:rdimTrans} 
 Let $ L \in \Gr_+$ or $\Grth_+$.
@@
 
-\begin{lemma} \label{le:Srdim}
+\begin{lemma}\label{le:Srdim}
     Let $ L \in \Gr_+$.  The following are equivalent:
@@
 % 
-Note that $ \lambda - \mu = \displaystyle{\sum_{1 \le a < b \le m}n_\bullet(\tau)_{(a,b)} \beta_{a,b}} $ where $ \beta_{a,b} $ denotes the positive root of $ G$ with a $ 1 $ in the $a $ slot and a $-1$ in the $ b $ slot.
+Note that $$ \lambda - \mu = \displaystyle{\sum_{1 \le a < b \le m}n_\bullet(\tau)_{(a,b)} \beta_{a,b}} $$ where $ \beta_{a,b} $ denotes the positive root of $ G$ with a $ 1 $ in the $a $ slot and a $-1$ in the $ b $ slot.
 The pattern $\gt(\tau)$ is recorded as a lower-triangular matrix (the array of shapes of subtableaux $\tau(i)$) and the datum $n_\bullet(\tau)$ is recorded as a sequence, unless noted otherwise.
+
 Below is an example with $\lambda = (4,2)$ and $\mu = (3,2,1)$. 
@@
 
-\begin{proposition}
-    \label{pr:newmvdes}
+\begin{proposition}\label{pr:newmvdes}
     $ \mathring Z(\tau)$ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.  Let $ Z(\tau)$ denote the closure of this component.  Then, 
@@
 % 
-\begin{remark} \label{rem:irreducible}
+\begin{remark}\label{rem:irreducible}
 We believe that $ \mathring Z(\tau)$ is irreducible, so that in fact $ Z(\tau) = \overline{ \mathring Z(\tau)}$.
@@
 
-\begin{lemma}
-    \label{lem:XtZt}
+\begin{lemma}\label{lem:XtZt}
     Under the Mirkovi\'c--Vybornov isomorphism $\mathring X(\tau)$ is mapped isomorphically onto $\mathring Z(\tau)$. 
 \end{lemma}
+% 
 \begin{proof}
@@
 % 
-\begin{theorem}(\cite[Theorem~4.8.2]{dthesis})
-\label{pr:generalized orbital varietiesasirrecs}
+\begin{theorem}\label{pr:generalized orbital varietiesasirrecs} (\cite[Theorem~4.8.2]{dthesis})
     % $\{X\in\cX(\lambda):X\subset\TT_\mu\}$ 
-    $\{X(\tau) : \tau \in YT(\lambda)_\mu \}$
-    is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
+    $\{X(\tau) : \tau \in YT(\lambda)_\mu \}$ is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
 \end{theorem}
-
 % 
@@
 % 
-\begin{proposition}
-\label{pr:XttZtt}
+\begin{proposition}\label{pr:XttZtt}
     The image of $\mathring X(\tau',\tau'')_{0,\AA^\times}$ under the isomorphism of \Cref{th:OTGrW} is $\mathring Z(\tau')\ast_{\AA^\times} \mathring Z(\tau'')$. 
@@
 
-Conversely, given
-$L\in\mathring Z(\tau')\ast_s \mathring Z(\tau'')$, we can write $ L = g(A)\CC[t]^m$ by  \Cref{th:OGrl}. Then reversing the above logic, we conclude that $ A \in \mathring X(\tau',\tau'')_{0,s}$.
+Conversely, given $L\in\mathring Z(\tau')\ast_s \mathring Z(\tau'')$, we can write $ L = g(A)\CC[t]^m$ by  \Cref{th:OGrl}.
+Then reversing the above logic, we conclude that $ A \in \mathring X(\tau',\tau'')_{0,s}$.
 \end{proof}
@@
 In a similar way, we may consider the intersection multiplicities of generalized orbital varieties in $X(\tau', \tau'')_{0,0} = M_N \times \{0\} \cap X(\tau', \tau'')_{0, \AA}$.
-\begin{corollary}
-\label{cor:intmul}
+\begin{corollary}\label{cor:intmul}
     $i(X(\tau), X(\tau',\tau'')_{0,0}) = i( Z(\tau), Z(\tau')\ast_0 Z(\tau''))\,.$
@@
     Given $Z',Z''\in\cZ(\infty)$, 
-\begin{equation}
-\label{eq:btimesb}
+\begin{equation}\label{eq:btimesb}
     b_{Z'}\arfu b_{Z''} = \sum_{Z\in\cZ(\infty)} i\left(Z, Z' \geofu Z''\right) b_Z 
@@
 
-\begin{lemma}
-\label{lem:almostmintab}
+\begin{lemma}\label{lem:almostmintab}
 Let $n_\bullet = (n_{(a,b)})$ be a Lusztig datum and let $\mu^0 = (\mu^0_i)$ be a padding.
@@
 % 
-\begin{corollary}
-\label{cor:goodreps}
+\begin{corollary}\label{cor:goodreps}
 Given two stable MV cycles $Z',Z''$ with Lusztig data $n_\bullet',n_\bullet''$ resp.\ there exists a pair of tableaux $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ for some $\lambda',\lambda''$ dominant effective and some $\mu',\mu''$ effective, such that $\mu = \mu' + \mu''\le \lambda = \lambda' + \lambda''$ are partitions and
-\begin{equation}
-    \label{eq:multingeneralized orbital varieties}
+% 
+\begin{equation}\label{eq:multingeneralized orbital varieties}
     b_{Z'} \arfu b_{Z''} = \sum_{\tau\in YT(\lambda)} i (X(\tau), X(\tau',\tau'')_{0,0})b_{t^{-\lambda}Z(\tau)}
@@
 % 
-\section{Examples}
-\label{s:examples}
+\section{Examples}\label{s:examples}
 
@@
 The ideal of the fusion $ X(\tau', \tau'')_{0,0}$ is
+% 
 $$
@@
 $$ 
+% 
 Taking the primary decomposition (to account for possible multiplicities) of $J$ gives us ideals $J_1,\dots,J_n$, each corresponding to a generalized orbital variety occurring in the fusion.
@@
 
-\subsection{Type \texorpdfstring{$A_2$}{A2}}
-\label{ss:a2}
+\subsection{Type \texorpdfstring{$A_2$}{A2}}\label{ss:a2}
 % 
@@
 
-\subsection{Type \texorpdfstring{$A_3$}{A3}}
-\label{ss:GL4 examples}
+\subsection{Type \texorpdfstring{$A_3$}{A3}}\label{ss:GL4 examples}
 % 
